### 2019-06-26 Backup/Paper_neural_coarse_graining_of_consciousness_backpuBeforeDeleteWritingMaterials.tex
Updates from Overleaf

\documentclass[utf8]{article}
\usepackage{import}
\usepackage{WritingToolsByAcer}

\excludeversion{WritingMaterials}
\excludeversion{backup}

%% ================================== acronym ================================= %
\usepackage{acronym}
\newacro{ntic}[NTIC]{non-trivial informational closure}
\newacro{ic}{informational closure}
\newacro{cg}{coarse-grain}
\newacro{cging}{coarse-graining}
\newacro{cged}{coarse-grained}
\newacro{ncg}{neural coarse-graining}
\newacro{OurTheory}[NCGTC]{The Neural Coarse-graining Theory of Consciousness}

% ============================================================================ %
%                                     Title                                    %
% ============================================================================ %
\title{A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness }

% ============================================================================ %
%                                    Authors                                   %
% ============================================================================ %
\author[]{Acer Y.C. Chang\thanks{acercyc@araya.org}}
\author[]{Martin Biehl\thanks{martin@araya.org}}
\author[]{Yen Yu\thanks{yen.yu@araya.org}}
\author[]{Ryota Kanai\thanks{kanair@araya.org }}
\affil[]{ARAYA, Inc., Tokyo, Japan}

% ============================================================================ %
%                                     Body                                     %
% ============================================================================ %
\begin{document}
	\maketitle
	\tableofcontents

	\begin{abstract}
		Neural systems process information through different levels of organisation in a hierarchical manner. Information at lower levels is finer-grained and can be coarse-grained for higher level computation. However, one is aware of information processed only at specific levels. Theorists have addressed this issue. For example, the intermediate level theory of consciousness suggests that the intermediate level seems to be privileged with respect to consciousness. It is true that we do not experience information processed by individual neurons which is always highly noisy. In addition, we have no conscious experience from interpersonal activities despite massive interactions among individuals. Instead, neurophysiological evidence has been showing that conscious experience tends to co-vary with information encoded in coarse-grained neural states such as neural population codes. We argue that the content of consciousness is determined by neural variables that obey informational closure and that other brain processes remain unconscious. Out theory provides a quantitative distinction between conscious and unconscious processing. 
		% Sorry the last part should have been deleted
	\end{abstract}

	\section*{Keywords:}
	Keywords: theory of consciousness, informational closure, neural coarse-graining, level of analysis

    \newpage
    \section*{Not decided terminology}
        \begin{ants}
            @ information * in the NTIC process
            @ Full and short name of this theory
            @ core "?" (entity) for conscious content 
            @ our theory? framework? proposal? 
            @ system? process?
            @ variable? node? element? member?
            @ TODO:
                @@ Change coarse-graining function to "aggregation function"
            @ Decided
                @@ "form" NTIC
        \end{ants}

	% ============================================================================ %
	%                                     Start                                    %
	% ============================================================================ %

    \newpage
	\section{Introduction}

		%% Story about a cell
		Imagine you are a neuron in Alice's brain. Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials along axons. However, you have no idea that you are one of neurons in Alice's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup. You are ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.
		A similar story also happens to Alice's conscious mind. To grab a cup, for example, Alice is conscious of her intention and visuosensory experience of this action. However, her conscious experience does not reflect the dynamic of your membrane potential or the action potentials you send to other neurons every second. That is, information in Alice's conscious experience does not contain information involved in your information processing.

		\toWrite{maybe need a transition sentence here}

		%% scale
		It seems to be true that we are unable to consciously access information processed at every scale in the neural system. Only information at certain levels of coarse-graining can become conscious contents. At microscopic levels of neural systems, information processing in individual neurons is noisy and state transitions of neurons are stochastic \citep{Goldwyn2011, White2000}. However, instead of stochastic action potentials and fluctuation of random noise at microscopic levels, what we are aware of in our conscious mind shows astonishing stability and robustness against the ubiquitous noise in the neural system \citep{mathis1995computational}. Alongside, some parts of the neural system contribute very little to conscious experience (the cerebellum for example \citep{lemon2010life}), also suggesting that conscious contents do not have one-to-one mapping to all parts of the brains. Likewise, experience does not associate with states of the macroscopic brain level because state space of conscious experience is much larger than what a single coarse-grained variable can represent. Additionally, we do not experience "super-consciousness" when we have massive inter-individual interactions with other human-beings. Even though evidence has shown several types of collective information processed at human social groups levels exist \citep{malone2015handbook}, information processed at this level seems to depart from our individual conscious contents.
        \idea{I still think this social example is fine. But the question will become what do we care about? Physical scale or coarse-graining? They are defined in different ways.}

		%% our argument
		In this article, we propose a new theory of consciousness, called \ac{OurTheory}. This proposal states that consciousness does not rest on particular neural architectures or locations in the neural systems. Instead, we argue that consciousness correlates with information processing at a certain coarse-grained level where the neural systems create a high degree of non-trivial informational closure (NTIC)\footnote{In the following NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}. We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC and the \textit{contents} of consciousness corresponds to the state of the NTIC process (for the level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).

		% information-based claim 
		\ac{OurTheory} takes a strong position that consciousness is an information-based phenomenon. I.e. the current proposal can be considered as an information correlate of consciousness (ICC). Based on the presumption, we construct our theory with two core concepts: non-trivial informational closure and neural coarse-graining. In this article, we first introduce non-trivial informational closure and its importance to information processing for human scale agents. We next argue that through coarse-graining the neural system can achieve high degree of non-trivial informational closure at a specific coarse-grained level. We then propose that the state of the informationally closed process correlates with the state of consciousness for both levels and contents which can be explained, quantified, and predicted computationally by our theory. We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies and reconcile several current major theories of consciousness. Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from this theory to the current consciousness science.

		\begin{figure}[H]
		    \centering
			\includegraphics[width=\textwidth]{WritingMaterials/Fig_ScaleProblemOfConsciousness/ScaleProblemOfConsciousness.pdf}
			\caption{The scale problem of consciousness}
	   	\end{figure}

		%% backup point
		\begin{WritingMaterials}
			@ consciousness is information

			@ conscious contents
				@@ \toWrite{lower level}
				@@ Information processing of individual neurons are noisy.
				@@ We don't have conscious content changes when individual neurons fire action potentials.
				@@ Don't even mention ion channel dynamic.

				@@ \toWrite{Higher-level dynamic}

			@ For human, physics at our body scale are nearly follow classic physics, which is deterministic.

			@ \toWrite{Human tendency for active prediction }
				@@ \cite{Stahl2015} \rewrite{
					Given the overwhelming quantity of information available from the environment, how do young learners know what to learn about and what to ignore? We found that 11-month-old infants (N = 110) used violations of prior expectations as special opportunities for learning. The infants were shown events that violated expectations about object behavior or events that were nearly identical but did not violate expectations. The sight of an object that violated expectations enhanced learning and promoted information-seeking behaviors; specifically, infants learned more effectively about objects that committed violations, explored those objects more, and engaged in hypothesis-testing behaviors that reflected the particular kind of violation seen. Thus, early in life, expectancy violations offer a wedge into the problem of what to learn.}

			@ Intuitive physics \needref{Intuitive physics}

		\end{WritingMaterials}

	\section{Non-trivial informational closure} \label{sec:Non-trivial informational closure}
		The notion of non-trivial informational closure (NTIC) is introduced by \cite{BERTSCHINGER.2006}. The concept of closure is closely related to system identification in systems theory. One can distinguish a system from its environment by computing the closedness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}. The closedness can be further quantified by information theory.

		\begin{WritingMaterials}
			@ Consciousness as an intrinsic information. Therefore, information should be self-define. This means the boundary of conscious content should be related to informational closure.

			@ \idea{should we describe the intuition of boundary problem here?}

			@ ============================================================================

			@ \rewrite{
				The notion of closure plays a prominent role in systems theory where it is used to identify or define the system in distinction from its environment} \cite{BERTSCHINGER.2006}

			@ \rewrite{
				Our theoretical interest concerns the type of system that is a unity for and by itself and not only for an external observer distinguishing some entity from the rest of the world. This requires a system that can be described as a whole without reference to its environment. In systems theory, this property is usually referred to as closure.}\citep{BERTSCHINGER.2006}

			@ \rewrite{
				These concepts of closure play an important role in the architecture of systems
				theory, because they are used to
				1. define the system (in distinction to its environment) and to
				2. explain the autonomy of the system.}\citep{BERTSCHINGER.2006}

			@ \rewrite{
				Informational closure: The higher process is informationally closed, i.e., there is no information flow from the lower to the higher level. Knowledge of the microstate will not improve predictions of the macrostate.} \citep[p. 4]{PFANTE.2014}

		\end{WritingMaterials}

		% Definition of informational closure
			\noindent
			Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network in Figure~\ref{fig:SystemAndEnv}. Then, information flow $J_{t}$ from the environment $E$ to a system $Y$ at time $t$ can be defined as the conditional mutual information $I$ between the current environment state $E_{t}$  and the future system state $Y_{t+1}$ given the current system state $Y_{t}$

				\begin{equation}
    				\label{eq:InformationFlow}
    				\left.\begin{array}
    				{rl}{J_{t}(E \rightarrow Y )} & {:= I(Y_{t+1};E_{t}|Y_{t})} \\
    				%{ } & { \ = H(Y_{t+1}|Y_{t})-H(Y_{t+1}|Y_{t},E_{t})} \\
    				%{ } & { \ = H(E_{t}|Y_{t})-H(Y_{t}|Y_{t},Y_{t+1})} \\
    				%{ } & { \ = H(E_{t}|Y_{t})-H(E_{t}|Y_{t},Y_{t+1})}\\
    				{ } & { \ = I(Y_{t+1};E_{t}) - (I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}))}
    				\end{array}\right.
				\end{equation}

				\begin{figure}
					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv.pdf}
					\caption{Figure adapted from \cite{BERTSCHINGER.2006}}
					\label{fig:SystemAndEnv}
				\end{figure}

			\noindent
			\cite{BERTSCHINGER.2006} defines that a system is informationally closed when information flow from the environment to the system is close to zero.

				\begin{equation}
				J_{t}(E \rightarrow Y )=0
				\end{equation}

			% ------------------------------- trivial case ------------------------------- %
			\noindent
			Information closure (minimising $J_t$) is trivial if the environment and the system are entirely independent of each other.

				\begin{equation}
				\begin{aligned}
				{I(Y_{t+1};E_{t})=0}&&{\Rightarrow}&&{J_{t}(E \rightarrow Y )=0}
				\end{aligned}
				\end{equation}

			% -------------------------------- non-trivial ------------------------------- %
			\noindent
			However, informational closure can be achieved non-trivially. In the non-trivial case, even a system that contains (or encodes) information about the environment is still informationally closed. This means

				\begin{equation}
				I(Y_{t+1};E_{t}) > 0
				\end{equation}

			\noindent
			This also implies
				\begin{equation}
					I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}) > 0
				\end{equation}

			\noindent
			And, non-trivial informational closure can be defined as
				\begin{equation}
				\label{eq:NTIC}
    				\left.\begin{array}
    				{rl}{NTIC} & {:=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t})}
    				\end{array} \right.
				\end{equation}

			\noindent
            The definition can also be re-arranged as 
				\begin{equation}
				\label{eq:NTIC2}
    				\left.\begin{array}
    				{rl}{\qquad} & {\ =I(Y_{t+1};E_{t})-I(Y_{t+1};E_{t}|Y_{t})}
    				\end{array} \right.
				\end{equation}

			\noindent
			Hence, maximising NTIC amounts to
				\begin{equation}
    				\label{eq:nticObjective}
    				\begin{aligned}
    				& \text{maximising} & { } & I(Y_{t+1};Y_{t}) & { } & \text{and} \\
    				& \text{minimising} & { } & I(Y_{t+1};Y_{t}|E_{t}) & { }
    				\end{aligned}
				\end{equation}

			\noindent
			This implies the system contains in itself all the information about its own future and the self-predictive information is gained from the information about the environment. Therefore, to achieve NTIC, the system can internalise and synchronise the dynamics of the environment, i.e. modelling the environment. Furthermore, having high degrees of NTIC entails having high predictive power about the environment. This gives biological agents a great functional and evolutionary advantage. Practically, \cite{guttenberg2016neural} proposed that NTIC can be achieved by maximising the predictive power about the environment and the self-predictive information of the system concurrently.

			% Biological evidence of informational closure in the neural system
			Despite the significant advantage for biological systems to achieve NTIC, to our knowledge, studies directly examining NTIC in biological systems are limited. However,  recent studies have shown relevant properties in the visual system of salamanders. By examining the salamander retina, in two studies \citep{Palmer2015, sederberg2018learning} the authors found that the a large groups of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states (see Figure~\ref{fig:sederberg2018learning}), therefore, in line with the characteristic of NTIC. Therefore, the self-predictive information of the neural populations can guide prediction about external stimuli without reference to stimulus parameters explicitly. Moreover, the internal predictability can be generalised to different stimulus classes suggesting the tendency to internalise the information of environmental dynamics in the neural populations. \toWrite{Add Some ending sentences}

			\begin{figure}[H]
				\includegraphics[width=\textwidth]{WritingMaterials/Fig_Sederberg/Fig_Sederberg.pdf}
				\caption{Figure adapted from \cite{sederberg2018learning}}
				\label{fig:sederberg2018learning}
			\end{figure}

			\begin{comment}
				@ ===

				@ \rewrite{
					Internal information reflects the spatial and temporal correlations in the stimulus.}

				@ \rewrite{predictive information is encoded synergistically.}

				@ \rewrite{
					in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }

				@ \rewrite{
					We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}

				@ \rewrite{
					We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }

				@ \rewrite{
					Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal. This suggests that bottom-up prediction may play an important role in sensory processing}

				@ \rewrite{
					Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}

				@ \rewrite{
					Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}

				@ They also showed generalization of internal predictability across stimulus. This suggests .... what?

				@ \rewrite{
					The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}

				@ \cite{Palmer2015}
				@ \rewrite{
					Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}

				@ \rewrite{
					It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig. 3, but the brain has no direct access to visual stimuli except that provided by the retina. Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs? More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + delta t in the future? The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +delta t j w t Þ } \url{http://tinyurl.com/y9zmhlln}

				@ \rewrite{
					larger groups of cells carry predictive information for hundreds of milliseconds, }

			\end{comment}

			%% backup
			\begin{comment}
				@ Accurately model deterministic environment
				@ \rewrite{
					This demonstrates that a system exhibiting certain internal regularities as measured by $A^* = MI(Sn+1; Sn)$ can achieve informational closure either by gaining information about the environment or by increased autonomy, i.e. by becoming unpredictable or uncontrollable from the (13) environment. Therefore, information about the environment, i.e. modelling, and autonomy can be considered as complementary strategies for achieving informational closure.}

				@ By Action

				@ In the next section, we claim that the neural system achieve NTIC through coarse-graining.
			\end{comment}

	\section{Neural coarse-graining}

		%% stochasticity at microscopic levels
		To create NTIC in a highly stochastic system (e.g., the neural system) is challenging. The more a system is influenced by the environment the more information about the environment's state it has to contain itself. This however requires the predictability of the environment state and is therefore impeded by noisy environments.  Information processing at the microscopic levels (the cellular levels) in the neural system suffers from multiple environmental noise sources throughout, including sensory, cellular, electrical, and synaptic noises. Previous studies have shown that states of neurons have large trial-to-trial variability at the cellular level. That is, the same pattern of activity never occurs twice even when the same stimulus is presented. Neurons are inevitably subject to thermal fluctuations and other physical noises \citep{faisal2008noise}. Furthermore, environmental information is always only partial observable to individual sensors and neurons which only receive little amount of information from the environment. Therefore, information about the environment state at the cellular level is difficult to represent. It is implausible to construct NTIC processes at microscopic levels.

        %% Our argument
        \critical{Need Discussion}
		However, we argue that, neural systems can form NTIC at certain macroscopic levels by coarse-graining microscopic neural states. Despite the microscopic levels in the neural system is stochastic and difficult to form NTIC processes, one solution to overcome the difficulty is to coarse-grain and encode information in coarse-grained variable to form stable and robust representation in the system. Coarse-graining refers to many-to-one functions that map microscopic states to macroscopic states.\needref{Do we need reference?}. In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}. This is a common neural coding strategy that we can see in large number of previous neurophysiological studies. For example, in the temporal domain, neural spikes across time can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}. Neurons encode stimulus intensity by increasing or decreasing firing rate. \citep{kandel2000principles}. In this coding scheme, individual neural spikes in a transient time span are not meaningful and stochastic \citep{stein2005neuronal}. In contrast, rate codes are relatively stable and are highly robust against noise caused by the variation of inter-spike intervals.

		% population code
		Another example of coding strategy using coarse-graining is population coding. In this coding scheme, information is represented by joint spatiotemporal activities of several neurons. Therefore, the information is encoded in coarse-grained variables whose values are jointly determined by neural activation patterns within a neural population \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}. In such cases, activities of every single neuron is not informative and stochastic. Instead, coarse-grained variables (such as population averaging and population vector) are able to represent information more stably. Encoding information at coarse-grained levels allow the neural system to ignore certain causal interactions relevant to fine-grained level of description \citep{Woodward2007-WOOCWA}.

		% neural coarse-graining by Nic
		As mentioned above, it has been empirically shown that NTIC can be achieved by coarse-graining sensory inputs in artificial neural networks. \citep{guttenberg2016neural} proposed a "neural coarse-graining (NCG)" architecture (fig.\ref{fig:NCG}) which aims to capture the emergent large-scale dynamics in the environment. The NCG network learns to coarse-grain input signals and extract latent parameters which are both predictive and predictable in the input signal and therefore achieves NTIC by building a higher-level representation of the underlying dynamics in the deep layers. More importantly, using this architecture, agents can process information and act at coarse-grained macroscopic levels.

		\begin{WritingMaterials}
    		% --- This figure is not necessary now ---
    		\begin{figure}
    			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/Fig_temp/PDFXCview_2018-06-08_14-24-03.png}
    			\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
    			\label{fig:NCG}
    		\end{figure}		
    	\end{WritingMaterials}

		%% not monotonic
		It is important to note that NTIC can be a non-monotonic function of scale of coarse-graining. If macroscopic variable is overly coarse-grained the system states can result in low degrees of NTIC. For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus looses the self and environmental predictive power. The non-monotonic relationship is also supported by empirical evidence. \cite{sederberg2018learning} showed that the efficiency of reading out self-predictive information of neural population is higher when the number of cells in a populations is 4 than it is when that number is 7 or 10 cells. This implies an optimal coarse-graining scale for NTIC processes. % Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}\citep{sederberg2018learning}

        %% Link to consciousness
        At the physical scale which human beings live in, the environmental dynamics is nearly deterministic following the laws of classical physics. This suggests that information in the environment is nearly closed at a right spatial-temporal scale. Therefore, this gives agents living at this physical scale great advantages if the agents form a NTIC process internally. Therefore, coarse-graining becomes necessary to map microscopic sensory and neuronal states into macroscopic NTIC process.

        %This means that it is possible for agents to live at this physical scale to build NTIC process internally.
    % More importantly, the information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.

		\begin{WritingMaterials}
			@ \rewrite{
				Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}

			@ neural system use population coding and temporal coding to fight against noise.

			@ Therefore, even though the low level information processing is noisy, it is possible that the neural system achieve NTIC at a coarse-grained level.

			@ This implies that the information about the environmental dynamic should be represented at a certain coarse-grained level rather then other levels.

			%% Microscopy Deterministic
			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions are nearly deterministic.

			@ \idea{Need something here}

			%% coarse-graining is necessary
			@ Hence, to coarse-grain states of microscopic levels is necessary to represent and model the human-scale environment state and dynamics.

			@ Coarse-graining is necessary to resist noise

			@ \rewrite{ The population will therefore be relatively insensitive to the loss of
				cells or noise in a small number of cells} \cite{eurich2000multidimensional}

			@ Studies have shown that coarse-graining is a common way that the neural system cope with inevitable noise at microscopic levels.

			@ \rewrite{Because the sequence of action potentials generated by a given stimulus varies from trial to trial, neuronal responses are typically treated statistically or probabilistically}

			@ Note that, information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.

			@ Population coding

				@@ review ref

					@@@ \cite{Stanley2013}

					@@@ \cite{QuianQuiroga2009}

				@@ \rewrite{
					Averaging is used in many neural systems in which information is encoded as patterns of activity across a population of neurons that all subserve a similar function (for example, see REFs 140,141 )}
									140. Georgopoulos, A., Schwartz, A. \& Kettner, R. Neuronal population coding of movement direction. Science 233, 1416–1419 (1986). 141. Lee, C., Rohrer, W. H. \& Sparks, D. L. Population coding of saccadic eye movements by neurons in the superior colliculus. Nature 332, 357–360 (1988).

				@@ \rewrite{
					Electrophysiological studies in the monkey have shown that behaviourally relevant signals are averaged not only across neuronal populations but also over time in the formation of a behavioural decision 156 .} 156. Gold, J. I. \& Shadlen, M. N. Representation of a perceptual decision in developing oculomotor commands. Nature 404, 390–394 (2000).

				@@ \rewrite{A distributed representation of information of this type is more robust to the effects of noise.}

				@@ \rewrite{
					Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli. These features consist of spatial-temporal sequences of action potentials distributed across neurons and/or time.}

				@@ The diverse response selectivity of sensory neurons

				@@ \rewrite{
					How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}

				@ sensory hierarchy
					@@ sensory hierarchy also shows characteristic of coarse-graining

					@@ Due to partial information that sensors can receive

					@@ To form complex representation like shape, objects, coarse-graining is necessary.

					@@ Through coarse-graining, \highlightAndComment{higher level}{might be confusing, need to think about the terminology here} cortical areas can integrate those partial information to infer hidden causes.

				@ Through two objectives during training, the model can achieve NTIC.

				@ this can be achieved by maximising the self-predictive power of deep layers and its entropy through all training data.

				@ With the objectives, NCG network learns to coarse-grain input signals and  extract latent parameters which are both predictive and predictable in the input signal and therefore achieves NTIC by building a higher-level representation of the underlying dynamics in the deep layers.

                @ \ideaBox{Consider the two points}
                @ ----------------------------------------------------------------------------
                @ Achieving NTIC is the key objective to to extract out latent control parameters in the environment.
				@ Agents can process information and act at abstract levels
				@ ----------------------------------------------------------------------------

				@ At the physical scale which human being live, the environmental dynamics is nearly deterministic following the laws of classical physics. This means that it is possible for agents living at this physical scale to build NTIC process internally.

				@ When the information in individual sensory channel is noisy and partial, coarse-graining becomes necessary for achieve NTIC.
			\end{WritingMaterials}

% ============================================================================ %
%               A neural coarse graining theory of consciousness               %
% ============================================================================ %
	\section{A neural coarse graining theory of consciousness}

        In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory} \todo{We really need a good name}. The Theory offers two propositions:
        \begin{enumerate}
            \item We argue that the existence of an NTIC process within a system is sufficient for information processing to be conscious.
            \item  For the neural system that achieves NTIC must necessarily satisfy coarse-graining
        \end{enumerate}

        In what follows, we will first establish two presumptions on which this Theory depends. Then, we will develop the propositions in detail.

        The first presumption is that every human conscious precept is highly informative. Here, "informative" refers to the resolution of uncertainty. Being in a certain conscious state rules out an enormous number of other possible conscious states. This is in line with the impression that our conscious experience consist of highly multidimensional information and usually involves information from multiple modalities. Therefore, every conscious precept resolves a huge amount of uncertainty and provides considerable information.

        This presumption is in agreement with one of the axioms, \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p. 2]{oizumi2014phenomenology}.

        Based on this presumption, we postulate that the amount of (self-)information possessed by a conscious percept should be equal to the (self-)information of a particular event or entity in the physical reality. In this theory, we consider information is the common language between conscious experience and the physical reality. We further take a radical standpoint and postulate that consciousness is fundamentally associated with specific kind of information, i.e., the information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}) and discard the notion of neural correlates of consciousness(NCC).

        The second presumption is that the amount of information in consciousness is bounded. Even though information involved in every conscious percept is extremely rich, it is still limited and we do not consciously feel everything in this universe. This leads to the boundary problems of consciousness \cite{goff2006experiences}. There should exist information boundaries for every conscious entity. If consciousness is an information-based phenomenon, we should be able to identify the boundaries with measures of information theory. Specifically, we claim here that boundaries are defined by information closure. Therefore, information closure should be observed in physical systems with consciousness .

        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level. Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}. 
        Information closure also implies that the system is ignorant of information outside of the system. Therefore, if a coarse-grained level achieves information closure, it suggests the NTIC process at the coarse-grained level is ignorant of information processing happening at microscopic levels and also higher coarse-grained levels. This virtually makes the informational closed macroscopic levels as a complete reality. 
        \todo{Due to my concern mentioned last week, I think I should also mention the closure is not only to the environment but also to the microscopic levels}

        Finally, our conscious experience always reflects some information about environment and bodily states, i.e. non-trivial information. To account for the information-based considerations, we propose that NTIC is a fundamental informational property associated with consciousness.

        \ideaBox{Informational closure and level identification}

        \begin{WritingMaterials}
        For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between. Assuming that Alice is conscious, the conscious experience that Alice has should not involve any information about Bob.

        \todo{Considering putting this para}
        Similarly, we can apply this scenario to brain processing between two regions. We can consider a thought experiment. 
        Imagining that in the future, one poor subject attend this experiment. We remove the subject's visual cortex from other brain areas. However, we keep all the connection between the two parts of the brain intact by replacing dendrites and axons between the two parts with micro electronic cables. Because these cables are very long, we can move the visual cortex to the surface of Mars. Now the experimenters give visual cortex a input signal. If the signal travels with the speed of light, it still takes three seconds to reach the other part on the earth. We can ask: Between the experimenters send the input signal and the information reach the part on the earth, what visual conscious content does the subject experience in the three seconds? We presume that in this three seconds subject's conscious experience should not contain any information about the visual input. Otherwise, the subject may be able to use the information to perform subsequent actions. This violates physics. This may look like a trivial questions.

        However, in many systems, it is difficult to achieve NTIC at microscopic levels due to stochasticity. Through coarse-graining, NTIC processes become possible at macroscopic levels. Therefore, coarse-graining is necessary for many biological systems to implement NTIC processes, especially for the neural system (Fig. \ref{fig:LevelOfConsciousness}). In the following, we explained this framework and provide mathematical definitions and implications of ICC.  
        \end{WritingMaterials}

		\begin{WritingMaterials}

            @ As we mentioned in Chapter 3, to form non-trivial informational closure has a huge evolutionary advantage for the creatures interacting with the environment at our scale.

            @ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}

    		@ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.

    		@ This drives the neural system to create a non-trivial informational closure.

            @ Therefore, NTIC emerges from evolutionary processes is functionally plausible.

            @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.

    		@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:LevelOfConsciousness})

            @ Therefore, the NTIC correlating conscious experience must settled at coarse-grained macroscopic levels.

    		@ Through coarse-graining, we can define a new set of variables.

            @ information is scale-dependent

    		@ If the new set of variables are informational closure, then this creates a new \textit{reality} for all the variables inside.

    		@ \textit{Reality} here means that the all the future states of the system are driven by the current information (include variables and the relationships) within the boundary.

            @ Relationship between coarse-graining, scale and interaction with environment

    		@ \rewrite{
    			This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}

    			@@ conscious perception are very stable and time invariant.
    			@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.

            @ To summaries, in our framework, consciousness is 
    			    @@ Intrinsic

    			    @@ Informative

    				@@ scale-dependent

             % our claim   
    			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.

    			@ We further postulate that level of consciousness corresponds to informational closureness of processes.

    			@ The contents of consciousness correspond to the states of the non-trivial informational closure.

    		% Following
    			@ In the following part, we....\todo{todo}

    			@ This is the same as "if a tree falls in a forest" thought experiment.

    			@ Therefore, to understand this system, you don't need more information from external environment.

    			@ It also means everything in this system is self-defined.

    			@ \critical{I need to somehow acknowledge \cite{pennartz2017consciousness}}
    				@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}

    				@@ pennartz levels are defined by functional elements call "functional ensembles". \cite{pennartz2017consciousness} \rewrite{This delineation is different from a scale-based distinction of levels, because different levels are distinguished here based on function , i.e., what each level can accomplish in terms of computation and representation, culminating in perception at the highest level.}

    			@ \rewrite{
    				Multilevel views on consciousness and cognition have been expressed before by many other theorists, such as Oppenheim and Putnam (1958), Attneave (1961), Hofstadter (1979, 1985), Churchland and Sejnowski (1992), Wimsatt (1994), and Lycan (1996).} \cite{pennartz2017consciousness}

    				@@ Oppenheim , P. , \& Putnam , H. ( 1958 ). Unity of science as a working hypothesis . In H. Feigl , G. Maxwell , \& M. Scriven (Eds.), Concepts, theories, and the mind – body problem (pp. 3 – 36 ). Minneapolis : University of Minnesota Press .
    				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
    				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
    				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
    				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
    				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
    			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.

		\end{WritingMaterials}

		\subsection{Measure of consciousness/information correlate of consciousness}	
		Based on our core assumption that NTIC is the core informational entity correlating conscious experience, we propose conscious levels and contents can be derived by computing the properties of a NTIC process. \newline

		\noindent
		We first hypothesise that, at given time $t$, the level of consciousness $C_{t}^{Level}$ corresponds to the degree of $NTIC_{t}$ at a coarse-grained level.
			\begin{equation}\label{eq:cLevel}
				C_{t}^{Level} = NTIC_{t}
			\end{equation}
		\newline
		\noindent
		We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
			\begin{equation}\label{eq:cContent}
				C_{t}^{Content} = Y_{t}
			\end{equation}

		We discuss the implications of the two hypotheses in the following. 	
	    \subsection{Level of Consciousness correlates degrees of NTIC of a process}

	    Our theory indicates that conscious levels are determined by two key elements based on the definition of NTIC (Equation \ref{eq:nticObjective}). First, to achieve high level of NTIC, one needs to maximise the channel capacity between the current internal state and the future internal state $I(Y_{t+1};Y_{t})$. This indicates that the richer self-predictive information the NTIC process contains, the higher the level of consciousness the agent has is. Considering two hypothetical systems composed of binary nodes, one has only three nodes and the other has 1 million nodes. Even though the first system can reach the maximal channel capacity, the maximal level of NTIC is only 3 bits. Compared to the first system, even though the second system does not have full self-predictability about its future state, the level of NTIC of this system can still far higher than the first system. This outcome is naturally consistent with a common intuition in which levels of consciousness usually is associated with the level of complexity of a system.\todo{Need to end this part and may need a reference} \toWrite{I want to say something about animal consciousness here}.

	    Second, one can also minimise the conditional mutual information  $I(Y_{t+1};Y_{t}|E_{t})$. This suggests that conscious level increases with the level of information about the environment dynamics that the NTIC process encodes. Therefore, an agent that forms an NTIC process lives in and adapts to a more complex environment has a higher conscious level than an agent that interacts with an environment with simpler dynamics. This also implies that agents who can explore, adapt their model, and react to diverse environments should have higher levels of consciousness.

	    Note that the non-monotonic relationship between levels of NTIC and the scale of coarse-graining suggests that there exists a scale of coarse-graining with the maximal level of NTIC. The self-predictive information is the key to achieve a high level of consciousness. If a system dynamics is highly stochastic and unpredictable, the level of consciousness should be low. As a result, information processed at neuronal scales which is heavily noisy and highly stochastic cannot form a high level of consciousness. Similarly, after coarse-graining, macro-variables loose predictive fine-grain information, the predictability become low and also the channel capacity between the current state and future state becomes very small, NTIC would be low as well. Consequently, human consciousness should be maximised at a certain coarse-grained level in the neural system.

	    Note that, the environment of a NTIC process in the neural system includes not only the\todo{Werite this}

        Finally, which coarse-grained level can achieve high NTIC? 
        agent-scale operation
        At the physical scale which human being live in, the environmental dynamics is nearly deterministic following the laws of classical physics. It gives agents living at this physical scale great advantages if the agents can build NTIC process internally. Therefore, to coarse-grain microscopic states is necessary

		\begin{figure}[H]				
    		\includegraphics[width=\textwidth]{WritingMaterials/Fig_temp/FoxitReader_2019-01-31_19-03-59.png}
    		\label{fig:LevelOfConsciousness}
    		\caption{Level of coarse-graining and level of consciousness. The degree of NTIC is not a monotonic function of coarse-graining levels, suggesting that high conscious level may exist at a certain coarse-grained level }
		\end{figure}

        % -------------  Contents Corresponding to Coarse-grained States ------------- %
		\subsection{Conscious Contents Corresponding to Coarse-grained States}\needfig{maybe I need a figure here}
        As we mentioned above, human conscious contents always consist of rich,  high dimensional, and integrated information. The state space of the correspondent physical system must have the same information capacity as the information content of consciousness.  We claim that conscious contents correspond to the state of the NTIC process.

        This claim implies that the complexity of conscious contents correlates with the amount of information contained in the NTIC process. Therefore, a crucial predict from our theory is that the larger state space of the NTIC process has the richer conscious experience the process can have (e.g., a NTIC process involving a large amount of coarse-grained variables). Crucially, even experience of full darkness contains rich information because it rules out other enormous potential alternative states of conscious contents. Equivalently, in the physical system, to know the state of the NTIC process when there is no sensory input (darkness) also requires the same amount of information from the system.

        Follow the example in the last section\todo{Do I have this example?}, a small creature lives in a simple environment with very limited environment dynamics. It may form a simple NTIC process. However, in this situation, the self-predictive information is very low and the state space of the NTIC process is small. As a result, the richness of the conscious experience this agent has will be very limited.

        Importantly, because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale, our theory supports multiple realisation thesis \needref{multiple realisation} which suggests same conscious experiences can be mapped to different physical implementations.

        \begin{WritingMaterials}
    		\begin{figure}[H]
    			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/LimitCycle/PhaseCycle.pdf}
    			\label{fig:limitCycle}
    			\caption{Example of coarse-graining by a limit cycle process}
    		\end{figure}

    		\begin{equation}\label{eq:LimitCycleExample}
                \begin{array}{l}{\dot{y_1}=y_1-y_2-y_1\left(y_1^{2}+y_2^{2} \right)+\epsilon_{y_1}} \\ {\dot{y_2}=y_1+y_2-y_2\left(y_1^{2}+y_2^{2}\right)+\epsilon_{y_2}}\end{array}
    		\end{equation}

    		The noise sources, $\epsilon_{y_1}$ and $\epsilon_{y_2}$, are i.i.d with a normal distribution with mean $\mu=0$ a and variance $\sigma^{2}=1$

            @ Our theory naturally explains the com positional nature of consciousness because the joint states of entities in the NTIC process determine the contents of consciousness.

		\end{WritingMaterials}

	    \subsection{Reconciling the levels and contents of consciousness}
	    Segregation of conscious levels and conscious contents raises a debate \citep{bayne2016there, Fazekas2016}. Our framework reconciles conscious level and conscious content. When the information encapsulated in the NTIC process is large and reaches a high NTIC,the system has high level of consciousness. Simultaneously, this provides a rich state space which is equivalent to encoding rich predictive environmental dynamic in the system. From this perspective, levels and contents of consciousness are just two different properties of NTIC processes. An important prediction from our theory is that in which the conscious level is determined by the size of the state space of the NTIC process rather the transient state of a system. For example, when we experience monotonous environment (a dark room), this does not degrade the conscious level.

	    Our framework also explains why in normal physiological states the level and the content are positively correlated \citep{laureys2005neural}\needfig{}. To achieve high NTIC, a system also needs to have high dimensionality and a large state space which guarantees rich and high dimensional information in conscious contents. Therefore, this framework well integrates the two key but debated concepts in consciousness research.

			\begin{WritingMaterials}
    			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.

    			@ This also suggests that the richness of the environment being modelled by the	NTIC process has a direct contribution to the level of consciousness.

				@ To have high level non-trivial informational closure, the states of the coarse-grained scale need to

				@ First, maximise the mutual information between environment and the representation.
				This term implies that the agent need to maximise predictive power of environmental state. This also suggest that the environmental complexity is a crucial factor to the level of consciousness. The more rich and complex environment the agent try to predict the higher level of consciousness the agent has.

				@ Consciousness and complexity \cite{Tononi1998}

				@ Second, to minimise the mutual information between environment and the representation conditional on the past state of the representation. This term suggests that the representation is self-predicable and it mimics the environmental transition.

				@ Therefore, this theory predicts that level of consciousness determined by the environment that the agent adapts to. To form a high non-trivial informational closure, the agent will need to live in a complex environment and model the environmental transition precisely.

			\end{WritingMaterials}

		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}

        It is important to note that the coarse-graining direction is not necessary aligned with \critical{Just saying anatomical is not enough. Need better expression} anatomical sensory hierarchy in the neural system. Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}. Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels. Nevertheless, to exercise causal power in actuators and environments, information needs to be read out from coarse-grained levels. \needfig{Maybe need a figure discribing brain to hand}. Therefore, the neural system still implement readout decoders for the subsequent signal output. In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system. We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.

			\begin{figure}[H]
				\includegraphics[width=\textwidth]{WritingMaterials/Fig_SeperationOfCGandCortHierachy/SeperationOfCGandCortHierachy.pdf}
				\label{fig:hierarchy}
			\end{figure}

            \begin{WritingMaterials}
    			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining

				@ For example, pooling layers in CNN is an implementation of coarse-graining function. It' is very plausible visual processing hierarchy in the neural system realises pooling layers.

				@ It is possible that the neural system represents higher-level information processing by low level physical subtract. For example, studies have found representation for summery statistics of signal and neural. population.\needref{neural representation for summery statistics}\\
				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
            \end{WritingMaterials}

        \subsection{Dynamical Boundary}
        Our theory predicts that the boundary of a conscious system is dynamical. The boundary is determined by elements forming high NTIC. This implies that when the structure of interaction between elements changes the physical boundaries supporting consciousness should also change. If some coarse-grained variables encode environmental information, they may become necessary components to form high NTIC. In such case, these coarse-grained variables are "recruited" inside the boundary of conscious processes. Note that, due to synergistic information, even recruiting some new variables may largely increase the level of NTIC. 
        This may explain why consciousness is tightly associated with binding and integration of information in human perception and cognition. Another crucial implication is that the same neural substrates may not be always involved in conscious processing rather it depends on whether it creates high NTIC with other members in the neural system. \needfig{Maybe I need a figure here as well}

% ============================================================================ %
%                    Conscious versus Unconscious Processing                   %
% ============================================================================ %
	\section{Conscious versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
	    In this section, we show how our theory can make predictions about whether a process is conscious or unconscious. While our theory is built upon a minimal set of assumptions, it possesses predictive power about the relationship between information processing in the neural system and conscious experience.

		Our theory argues that, to make information conscious, the following necessay and sufficient conditions need to be satisfied.

		\begin{enumerate}
		    \item Sufficient condition: Information is encoded in NTIC process. 
		    \item Necessary condition: The system is capable of constructing NTIC processes at coarse-grained levels. 
		\end{enumerate}

        We especially highlight the second condition because it is critically related to many empirical research results even though it is only a necessary condition. As we will describe below, this theory can well explain a varieity of previous empirical findings in consciousness science and further make predictions for future research. In this section, we discuss how the two informational-based conditions link to conscious experience.

        % ---------------------------------------------------------------------------- %
        %                            Unconscious Processing                            %
        % ---------------------------------------------------------------------------- %
        \subsection{Unconscious Processing}

        \subsubsection*{Fail to meet the 1\lowercase{st} condition}
            If a process fails to fulfil either of the two conditions, information remains unconscious. We first consider the scenario that a process fails to satisfy the first condition, i.e. the process fails to achieve high degree of NTIC. In the neural system many processes fall into this category.

        	Considering the objectives of achieving NTIC (Eq. \ref{eq:nticObjective}), if a process is unable to maximise the mutual information between its past and future states ($I(Y_{t+1};Y_{t})$), it results in low NTIC. The failure to maximise the mutual information implies the past states of the process itself has little influence on its future states. In the meantime, if environmental information is able to flow into the process, the process can still produces functional outputs based on the current state of the environment accordingly. However, in this circumstance, the future state of the process is largely determined by the environmental states. That is, the process is not informational closed (${J_{t}(E \rightarrow Y )} \not\approx 0$, Fig.\ref{fig:reflexive}).

            % or minimise $I(Y_{t+1};Y_{t}|E_{t})$

            % If the future states of the system have strong mutual information with the current environmental states ($I(Y_{t+1};E_{t})$) but have weak mutual information with the current system states ($I(Y_{t+1};Y_{t})$), the informational closeness will be small.

        	% reflexive behaviour
    		\begin{figure}[H]
    			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
    			\caption{Reflexive Behaviours}
    			\label{fig:reflexive}
    		\end{figure}

            In the neural system, this type of processes, for perception, shows the property that the perceptual processing mainly passively responds to the sensory inputs. For actions, this type of processes only produces "reflective-like" behaviours. Reflexive behaviours are commonly considered as automatic and non-conscious behavioural controls \citep{casali2013theoretically}\needref{More referene}. We argue that information carried by this type of processes is unconscious due to its failure of achieving high NTIC, i.e., the first condition.

            The same principle can be applied to blindsight and procedure memory \needref{blindsight} which are often considered as unconscious processing. Blindsight patients are able to track objects, avoid obstacles, and make above chance-level judgements without having any conscious perception about visual stimuli. We believe that these behaviours can be guided by direct stimulus-response mappings ($S\rightarrow{}R$). However, the direct $S\rightarrow{}R$ mappings also lead to non-NTIC neural processes  and, therefore, are unconscious. Similarly, in the case of procedure memory, processes always rely on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}. The information flow from the environment to the system is crucial to guide the state transition of procedural memory. Therefore, information processing of procedural memory also fails to achieve high NTIC and remain unconscious.

             This type of processing is similar to the model-free policy-based agents in the reinforcement learning framework. The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
        % @ $\pi : S \times A$\\
        % Policy
    		\begin{equation}
    			\label{eq:PolicyBasedAgent}
    			\begin{aligned}
    			    \pi(A | S)=\operatorname{Pr}\left(A_{t}=a | S_{t}=s\right)
    			\end{aligned}
    		\end{equation}

    		Our theory can explain why the patients with visual apperceptive agnosia (e.g., the famous case D.F.\cite{james2003ventral}) can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}. The online visual information can be used to perform functional actions without forming a NTIC process. Our theory also explains why unconscious processes in this category often fail when a long delay periods is introduced in the tasks. Without self-predictive information in NTIC, the policies of motor outputs largely depends on the present environmental and sensory states implying that this type of processes often can only work online. With a long, sensory information is unable to guide the delayed motor outputs and leads to failure consequences.

    		Finally, an interesting implication from our theory is that a pure feedforward neural network cannot be conscious because it is unable to maintain any form of memory so that there is no influence from the system past states to its future state. In contrast, with recurrent loops, a neural network is able to create information channels from its past to its future states and becomes capable of achieving NTIC. This result coincides with some theories of consciousness which emphasize the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
    		% if more references are needed, check Eklund_2012_RECURRENT PROCESSING AND THE CONSCIOUSNESS.pdf
    		However, we derive this conclusion from a more fundamental informational-related hypothesis indicating the more generalised principle behind it.

        % ---------------------------------------------------------------------------- %
        %                                Fail to meet 2                                %
        % ---------------------------------------------------------------------------- %

        \subsubsection*{Fail to meet the 2\lowercase{ed} condition}
        As mention above, information is level-dependent and can be virtually independent (closed) across different coarse-graining scales. If processes at some levels of a system are able to achieve high NTIC and become conscious, information at other levels still remains unconscious. The first implication of this argument is that processes at levels with high stochasticity are unable to achieve high NTIC and, therefore, unconscious. High stochasticity corrupts informational channel capacity and leads to low mutual information between past and future states of a process. In the neural system, the cellular level activities are highly noisy and are unable to reach high NTIC. Therefore, the information processed by the microscopic levels in the neural system are not conscious and we never can experience detail activities in the microscopic levels.

        We argue that many mysterious results in previous research of consciousness are originated from inappropriate biological and behavioural measurement scale. In the following, we list some examples.

        Unconscious processing in this category of

        @ Evidence suggests that the neural system is able to encode probability distribution and perform probabilistic inference in a near optimal way\needref{bayesian brain}. However, an intriguing fact is that we are nearly ignorant of all the probabilistic computation of the inference processes but are only aware of "a sample" of the posterior distributions of the inferences \citep{dehaene2017consciousness, vul2009attention, asplund2014attentional, vul2008temporal, moreno2011bayesian}. The information of all alternative possible states is unable to enter conscious contents. In short, one needs to explain why the neural system can hold the joint probability distributions of inferred variables but, however, only a realisation of the inference outcome becomes conscious. Based on our theory, we argue that the computation of statistical inference is carried out at microscopic levels of the neural system and the NTIC process correlated with conscious contents only possesses the coarse-grained information of the computation. The mapping from the microscopic to macroscopic states naturally leads to a single and stable state at the macroscopic levels.

        For example, Fig. \ref{fig:TemperatureExample} illustrates the relationship 
        At the left panel, two cups contain water with different volumes $V_t$ and temperatures $T_t$. Even though we know volumes and temperatures are coarse-grained macroscopic variables, the states of mixed water ($V_{t+1}$, $T_{t+1}$) can still be predicted without knowing any information from the microscopic levels (the molecular level),i.e., the information closure at the macroscopic level. Similarly, taking Bayesian inference as an example, the microscopic neuron populations are able to represent probabilistic distributions about inferred target variables and the neural networks perform the statistical inference to obtain the posterior distributions. However, enormous microscopic neural states can be coarse-grained into the same state of summary statistics (e.g., the mean $\mu_{t}$  and standard deviation $\sigma_{t}$) at a macroscopic level. The state transition ($\mu_{t+1}$ and $\sigma_{t}$) is also predictable without any additional information from microscopic levels. Therefore, consciousness can only "observe" the coarse-grained states without the knowledge of how the statistical inference is implemented and performed at the microscopic levels.

		\begin{figure}[H]
			\includegraphics[width=1.3\textwidth]{WritingMaterials/Fig_Temperature_Example/ExampleOfCG.pdf}
			\centering
			\caption{An Example of ...}
			\label{fig:TemperatureExample}
		\end{figure}

        The same scenario can be applied to the results from Libet's volition experimental paradigm \citep{Libet1983TimeOC, Libet1985Dec}. Experiments using similar procedures usually show that the recorded neural activities start earlier than subjects' feeling of their own intention to act in the self-determined experimental settings. We argue that free actions are initiated at the microscopic levels, for example, the random fluctuation in the neural system \citep{schurger_accumulator_2012}. However, the conscious experience of volition is information at the macroscopic level with NTIC. Due to the information closure, there is no way for the NTIC process to observe the information of the microscopic states, i.e. the initiation of actions.

        \idea{Not sure if I want to address this point}  Note that, some evidence suggests single-cell-level correlation of conscious experience, the Jennifer Aniston cell for example \citep{Quiroga2005Jun, Quiroga2012Jul}. This may seem to counter our argument that single-cell level information is incapable to be conscious. However, first, the correlations are always not the direct microscopic state changes of the cells, e.g. the action potentials. Instead, the correlated variables are always coarse-grained. The neuronal firing rate, for example, is a temporal coarse-grained variable. Second, it has been well established that heterogeneous nonlinearity is critical for neural populations to encode rich and high dimensional information. \citep{Chelaru2008, Rigotti2010Oct, Shamir2004Jun}. It is common to detecting a single neuron whose activity profile well align with a subspace which represents a single object within the state space of a population code.\needhelp{Maybe need to rewording here} We believe that multi-scale data and analyses are needed to elucidate whether single neuron behaviours are sufficiently representative for any type of conscious experience.

		\begin{WritingMaterials}
        	@ \idea{Should I write the following points? Is this too much?}
        	@  === boundary conditions  === 
        	% multistable perception
        	    @ In the case of multistable perception, at every moment, only a single macroscopic state is mapped from the microscopic levels, we can only be aware of one interpretation at every moment.

        	% Priming
        	    @ The same mechanism can also applied to unconscious priming effects. \highlight{Making state transitions at microscopic levels does not guarantee transitions at macroscopic levels.}\ideaCallout{this is the key sentence}

        	    @ Of course, this is related to what kind of coarse-grain function which can form a NTIC process at macroscopic scales. We will discuss this issue in the later section.

        	   @ The third category is the boundary conditions.

        	   % Binocular rivalry
        	   @ In binocular rivalry, either eye provides information to form a NTIC process. Once the process is NTIC, the process continue the trajectory in the state space and close system. Information from the other eye is unable to enter the process, thus it remains unconscious.

        	   @ Including information from either of objects information can achieve NTIC.

        	   @ For example, when the information of the visual stimuli both can form the NTIC.

        	   @ Our theory also explains why the conscious percepts show some kind of inertia (stably remain conscious for a period of time).

        	   @ Once the NTIC process is formed, the closureness guarantees the stability of the state transitions of the process.

            \end{WritingMaterials}

		\subsection{Conscious Processing}
		When the both conditions are fulfilled, our theory suggests that the states of a NTIC process correspond to particular conscious contents and the information incorporated in the NTIC process is conscious. Due to the predictive nature about the environment dynamics of NTIC processes, to achieve high NTIC and to construct functions within the process have a huge evolutionary advantage. It is important to emphasise that our theory does not suggest any functionalism of consciousness. Rather, we argue that information fundamentally associates with consciousness. Nevertheless, consciousness research still suggests a strong functional relation between consciousness and some specific types of cognition and behaviours \citep{Seth2009Encyclopediaofconsciousness}. We believe that this relation comes from several special properties of NTIC and these properties support the foundations of many cognitive functions in the neural system.

		First, a NTIC process encodes predictive information about environmental dynamics. This is crucial for constructing forward models for predicting future states of the environment. Therefore, cognitive functions which require agent-scale prediction are likely to be accompanied by conscious experience. This properties is required by planning and also achieving long term goals.\needref{}

		Second, a NTIC process can be considered as a close form simulation machine. With a given initial state, the process can self-evolve and follow a certain trajectory in the state space. This trajectory can be seem as a simulation about the environmental transition. Therefore, a NTIC process can serve cognitive functions as a perfect simulation engine \citep{BERTSCHINGER.2006}. Accordingly, mental simulation, imagination, computing alternative realities, and generating counterfactual outcomes can be implemented with a NTIC process. \needref{}

	    Third, an important properties of NTIC processes is its high stability. The state transitions and trajectory are highly predictable. In such case, NTIC processes are more suitable for integrating information across larger time scales (above millisecond). Therefore, tasks which require to integrate information across time above the millisecond scale are often associated with conscious experience.

	    Fourth, a NTIC process as a closed system can still provide predictive information without new information flowing into the process. This is crucial for many types of off-line processing.

	    Fifth, any state of a NTIC process can be seem as a integration of multiple sources of information. For the human scale activities, to know certain transition about the environment, the NTIC process must include a high dimensional information from multiple modalities and have the knowledge about how the high dimensional data interact to each other. Without the knowledge and information, a process may not be capable of produce a stable state transitions which mimic the environmental dynamics. Thus, cognitive functions requiring this large scale integration are likely to be conscious. Furthermore, the high dimensional integrated information is also critical for an agent to learn new behaviours to achieve flexibility and the strategic behavioural controls and decision-making.

	    In sum, we argue that having a NTIC process is critical for survival in the evolution. It is likely that biological creatures acquired NTIC process at some stages in the evolution. And due to the fundamental relationship between information and consciousness, these biological agents also acquired different degrees of consciousness depending on the physical scales and the complexity of the environments they live in. Our theory well explains why some processes and functions in the neural system are conscious and some are not with only two parsimonious conditions.

		\begin{WritingMaterials}
		    @ Previous research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.

    		    @@ Planning, achieving long term goals

    		        @@@ simulate alternative realities 
    		        @@@ multiple alternative possibilities
    		        @@@ imagination
    		        @@@ information for off-line processing

    		    @@ Cognitive control, response inhibition, flexible routing of information, overriding automatic responses

    		        @@@ flexibility and the strategic use of that information for complex operations and decision-making 
    		        @@@ flexible and adjust our behavior to different contexts and goals

    		    @@ integration,

    		    @@ integrates behaviour across time

    		        @@@ tasks for long duration

    		    @@ stabilisation

    		    @@ conscious thought, reflection, reasoning, and temporally extended sense of self.

    		    @@ complex visuomotor abilities

    		    @@ intending deciding

    		    @@ dreaming

    		    @@ reasoning interpreting

    		    @@ self

    		        @@@ reflecting
    		        @@@ self-monitoring 
            @ As mentioned in \ref{sec:Non-trivial informational closure}, achieving NTIC has a large evolutionary advantage.

                @@ Because NTIC processes encode information about environmental transition, it becomes a perfect computational core for constructing forward models for the environment, simulating the dynamics of self-environment interaction, and generating predictions.

            @ Therefore, if an agent equips a NTIC process, the process can be used to integrate information from different sources.

            @ =============================================================================

	        @ importantly, evidence suggests that those functions in some conditions do not require the involvement of consciousness. This evidences an important fact that consciousness is not necessay to these functions.

	        @@ Predictive information about the environment.

	        @@ Stability

	        @@ simulation environmental dynamics

	        @ Replaying past events

	        @ \rewrite{However, recent evidence also points out interesting dissociations between conscious and unconscious information processing when it comes to the duration, flexibility and the strategic use of that information for complex operations and decision-making} \cite{van2012role}

	    \end{WritingMaterials}

% ============================================================================ %
%                        Comparison with other theories                        %
% ============================================================================ %
	\section{Comparison with other theories}
	In this section, we compare our theory with other popular modern theories of consciousness. 1

		\subsection{Theories about multilevel views on consciousness and cognition}
		Previously, similar to our theory, several multilevel views on consciousness and cognition have been proposed. We shortly discuss two theories relevant to our current proposal.
            \subsubsection*{Level of Organisation \cite{wimsatt1994ontology}}
                As mentioned previously, the level of coarse-graining is different from the anatomical level.
                Pennartz focuses more on multimodal representation as the most important factor (See the discussion in \cite{pennartz2015brain}). Our proposal is inline with Pennartz's Neurorepresentational  theory (Neurorepresentationalism) \cite{pennartz2018consciousness,pennartz2015brain}. However, it’s crucial to note that our theory claims only the level of coarse-graining achieving NTIC matters to consciousness rather than the anatomical level of sensory hierarchy.

			\subsubsection*{Intermediate Level Theory} \label{IntermediateLevelTheory}
                One important theory tries to connect consciousness to multilevel views is the Intermediate Level Theory (ILT, \cite{jackendoff1987consciousness, prinz2007intermediate}). ILT proposes that conscious experience only correlates specific levels of representations in the hierarchy of sensory processing. ILT claims that consciousness only associates with the representation at intermediate levels (e.g., the 2.5D representation in terms of visual processing) rather than the ones at lower-level or higher-level. 
                One fundamental difference between ILT and our theory is the definitions of the level. In our theory, level is within the context of coarse-graining. However, ILT focuses more on the levels in terms of anatomical direction (see fig \ref{fig:hierarchy}). As mentioned previously, we emphasise that we doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies. This leads to an important difference that the level of coarse-graining exists virtually. However, the level of cortical representation should be referred to neural substrates. Finally, different from ILT which suggests that some neural substrates responsible for the 2.5D computation are conscious, we predict that once information carried by coarse-grained variables is involved in the NTIC process, brain areas, not exclusively within 2.5D representation, should  co-vary with conscious contents.

			\subsubsection*{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
			    Our theory shares some close concepts with Pennartz's Neurorepresentationalism \citep{pennartz2018consciousness,pennartz2015brain}. Similar to Neurorepresentationalism, our framework is also close to Marr's original distinction between the levels of analysis \citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}. However, a fundamental difference between the two theories is that Neurorepresentationalism takes more functionalist point of view and suggests NCC should serve high-level world-modeling and makes a best guess about the interaction between the body and the environment. Neurorepresentationalism also suggests conscious experience is associated with integrated representation for multimodal and situational information. Out theory suggests that the association between the functions mentioned in Neurorepresentationalism is rooted in the more fundamental relationship between information and consciousness in which NTIC plays an important role.

		        \begin{WritingMaterials}
				%% Back up materials

				@ Prinz suggested that \rewrite{as. Cells in V1 are not promising candidates, because they do not reliably respond in ways that are consistent with features that we experience consciously. } \cite{prinz2007intermediate}

				@ \rewrite{
					The intermediate level theory originally proposed by Ray Jackendoff and further defended and specified by Jesse Prinz proposes that within the hierarchy of representations that are used to describe the cognitive system, conscious experience occurs only for specific levels of representation. The theory is rooted in Jackendoff ’s analysis of different cognitive systems such as vision, language, and music and the subsequent observation that consciousness does not arise anywhere within these systems. According to Jackendoff, consciousness is not associated with low-level, nor with high-level representations, but rather with those implying intermediate levels of processing. For instance, in the domain of object recognition, it is assumed that the visual system comprises a low level with local computations of visual features, an intermediate level reflecting binding and object recognition, and a higher level computing viewpoint invariance and representing abstract categories. According to Jackendoff and Prinz, conscious experience is not comprised of a disunified picture of visual features, nor is it represented by viewinvariant categories. Rather it is composed of bound and specific instances of objects that are assumed to be computed at the intermediate level of representation. In an analogous manner, speech perception can be decomposed into three levels: an acoustic representation of speech sounds at the lower level, a high level involving abstract lexical and syntactic categories, and in between a word recognition level relying on phonological representations. This theory explains why the conscious experience associated with speech perception mostly involves phonological representations, rather than other levels of representations. In Jackendoff and Prinz’ theory,the privileged role of the intermediate level of processing is based on the need for real-time computational efficiency. Indeed, this level of representation is assumed to be the most relevant one regarding ecological and functional needs. Another important aspect of this theory concerns the central role of attention during conscious experience. Here, attention is defined as a selection process that acts as a gate to working memory mechanisms. It performs the function of selecting the relevant information that is amplified afterward and then becomes conscious. Indeed, Prinz acknowledges that activation of an intermediatelevel representation on its own cannot be a sufficient condition for consciousness, given that those representations can be activated during subliminal perception. However, this theory makes the crucial postulate that the amplification of intermediatelevel representations by attention is a necessary and sufficient condition for consciousness. In sum, for each domain of processing, the content of consciousness at a particular moment is supported by a representational structure of intermediate level for that domain, which is selected to enter short-term memory, and enriched by attentional processing.} \cite{banks2009encyclopedia}

				@ \rewrite{
					In 1987, Ray Jackendoff published Consciousness and the Computational Mind. In it, he posed an important Where question: Where, in the fl ow of information, does consciousness arise? Most cognitive scientists agree that the mind is, in some sense, a computer. It is a device that processes information by transforming representations in accordance with rules. Computational devices decompose into various interconnected subsystems, each of which performs some aspect of a complex task. Given such a decompositional analysis, we can ask: in which subsystems does consciousness arise? If we depict the mind as a vast fl ow chart, and highlight the boxes whose rules and representations are conscious, which boxes should we mark? Jackendoff ’s answer is simple and elegant. He noticed that many of our mental capacities, including our senses and our language systems, are organized hierarchically. In each of these hierarchies, it makes sense to talk about low- , intermediate- , and high- level processing systems. We break down tasks into stages. Appealing to prevailing models of these stages, Jackendoff observed that the intermediate level seems to be privileged with respect to consciousness. Consciousness seems to arise in intermediate- level processing systems and not elsewhere.} \cite{prinz2007intermediate}

				@ \cite{jackendoff1987consciousness}
				@ \cite{prinz2007intermediate}
				@ 2.5D

				@ about why it is this level
				@@ \rewrite{
					Under the computational interpretation, the “why” question means: In what sense are intermediate level representations computationally important or distinctive? Th is is a tractable question, and it may lead to insights into the function of consciousness. Representations at the intermediate level are ideally suited for real- time deliberative behavioral responses. Low- level representations fail to bind features into coherent wholes. If we are going to interact with our environment, the low level is not a good guide. Th e high level is a good deal better for action, but also suboptimal. Th e high level tells us the category of the stimuli we perceive, but from an allocentric point of view. It abstracts away from stimulus features that are crucial for action. If we encounter a predator, the high- level visual representation does not tell us if it is facing toward us or away from us. Without that knowledge, we cannot decide what course of action to take. So, I propose that the intermediate level plays a distinctive role in information processing. It delivers representations that are coherent but viewpoint specifi c. Th ese representations are useful for determining what to do here and now.arg1} \cite{prinz2007intermediate}
				@@ \rewrite{
					I conclude that the intermediate level plays a distinctive and important computational role. Some researchers find this puzzling. In wondering why the intermediate level is privileged, they note the arbitrariness of the fact that perceptual hierarchies have three levels. Could they not have two? Or a hundred? Do the 50 or so areas that contribute to visual processing really divide neatly into three levels? I think these puzzles depend on a particular understanding of what the word “intermediate” amounts to. One might get caught up in the fact that the intermediate level is the second stage in a sequence. Call this the “serial understanding of the intermediate level.” Alternatively, one might think of the intermediate level semantically. On this reading, the intermediate level is one that is not abstract and categorical, but not piecemeal or disunifi ed. Th ese notions are all in need of some refi nement, but, as a fi rst approximation, the idea is that intermediate- level representations are neither too specifi c nor too general.}\cite{prinz2007intermediate}
			\end{WritingMaterials}

		\subsection{First-order theories}
            The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}. The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
            First-order theories suggests that phenomenal consciousness is associated with fine-grained contents for the first-order processes. Different from the first-order theories, our theory suggests that, whether the early sensory activities show in the conscious content, it depends on information encoded in the early sensory areas is recruited in the NTIC process at the macroscopic level or not. As we mentioned in \ref{sec:Unconscious Processing}, if the sensory activities are only passively triggered by the environmental states, they are not able to form hign NTIC and remain unconscious. We predict that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities can contribute conscious content.

			\begin{WritingMaterials}
				@ \rewrite{
					The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations. Thus the crucial difference between the first-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity. Therefore, in the group of first-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the first-order representations, as well as scientists who hold that visual awareness depends on activity in content-specific regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26]. Most first-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g. subcortical) sensory pathways. Thus this view suggests that conscious and unconscious processing will have different functional consequences. Whereas some first-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most first-order theorists take a difference in perceptual task performance (e.g. ‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33]. In other words, they typically associate task performance with awareness..} \cite{lau2011empirical}

				@ Among those are first-order theories, on which a mental state is conscious if being in that state results in one's being conscious of something;

				@  According to first-order views, phenomenal consciousness consists in analog or fine-grained contents that are available to the first-order processes that guide thought and action. So a phenomenally-conscious percept of red, for example, consists in a state with the analog content red which is tokened in such a way as to feed into thoughts about red, or into actions that are in one way or another guided by redness.

				@ However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents. \todo{Need more here, espectially more counterintuitive predictions}

			\end{WritingMaterials}

		\subsection{Higher Order Thought theory of consciousness}
		    \ideaBox{Okay, I don't know how to deal with HOT now. I don't understand it at all}
		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations which represent agents as being in particular internal states \citep{lau2011empirical}. First-order processing needs to be observed or represented by a higher-order observer to become conscious.

		    Meta-cognition is also associated with many conscious cognitive function. However, we propose a new perspective and indicate that HOT may be a misunderstanding \critical{Very bad writing. I need to rewrite this part}.

		    This may be the result of neural coarse-graining. Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it.

		    Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation. It is true that the neural system does create  meta-representation to represent xxx\needref{Maybe come studies about confidence represenatation}. The higher-order representation may resemble coarse-grained variables. This may cause misidentify the entity which correlates conscious experience.

		    Moreover, the predictive information in NTIC is critical for other systems to build forward models for a wild range of tasks. Therefore, most of the high level cognition can utilise the state of informational closure. For example, mental planning needs a precise forward model to infer the environmental dynamics.

			\begin{WritingMaterials}
			@ Good reference: \myQuote{Higher- Order Th eories of Consciousness; PETER CARRUTHERS (The Blackwell Companion to Consciousness (Blackwell, 2007))}

		    @ In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.

		    @ Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.

		    @ It is true that the neural system does create  meta-representation to represent xxx.\needref{Maybe come studies about confidence represenatation}

		    @ The higher-order representation may resemble coarse-grained variables.

		    @ This may cause misidentify the entity which correlates conscious experience.

		    @ ----------------------------------------------------------------------------

			@ Information closure directly is critical for other systems to construct forward models.

			@ Therefore, most of the high level cognition can utilise the state of informational closure.

			@ For example, mental planning needs a precise forward model to infer the environmental dynamics.

			@ \idea{This is way HOT always involve consciousness }

			@ \cite{rosenthal2005consciousness}

            @ ============================================================================

			@ \rewrite{
				According to this view, humans not only have first-order non-conceptual and/or analog perceptions of states of their environments and bodies, they also have second-order non-conceptual and/or analog perceptions of their first-order states of perception. And the most popular version of higher-order perception theory holds, in addition, that humans (and perhaps other animals) not only have sense-organs that scan the environment/body to produce fine-grained representations that can then serve to ground thoughts and action-planning, but they also have inner senses, charged with scanning the outputs of the first-order senses (i.e. perceptual experiences) to produce equally fine-grained, but higher-order, representations of those outputs (i.e. to produce higher-order experiences). A version of this view was first proposed by the British Empiricist philosopher John Locke (1690). In our own time it has been defended especially by Armstrong (1968, 1984) and by Lycan (1996).} \url{https://plato.stanford.edu/entries/consciousness-higher/#SelRepHigOrdThe}

			@ \rewrite{
				neutral about whether conscious awareness adds significant utility or immediate impact on behavior and task performance [1,27]. This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on first-order rather than higher-order representations. Because conscious awareness can differ even if all first-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
				\ideaCallout{
					My theory would have similar prediction. Because conscious contents are coarse-grained results from low-level information. It is possible that more than two low-level neural states all coarse-grained to a high-level state.  }

			@ \rewrite{
					Metacognition: cognition that is about another cognitive process as opposed to about objects in the world. In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efficacy of a perceptual process. The capacity of sensory metacognition is sometimes empirically assessed by the correspondence between subjective report and task performance: how closely are they associated with each other on a trial-by-trial basis}\cite{lau2011empirical}

			\end{WritingMaterials}

        % ---------------------------------------------------------------------------- %
        %                            Global workspace theory                           %
        % ---------------------------------------------------------------------------- %

		\subsection{Global workspace theory}
		\needhelp{I think I need some help here. I am not sure what should I write here. Or  what position I should take. To some extent, GWT is a very qualitative theory. It kind of just summarises everything. Without any modelling work on NTIC, it's difficult to say whether we will replicate those profiles of consciousness mentioned in GWT.}
		\ideaBox{Need ending and better difference }
		Global workspace theory (GWT; \cite{baars1988cognitive, baars1997theatre, baars2002conscious}) or Global Neuronal Workspace theory (GNWT; \cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental}) states that the neural system consists of several specialised modules and a central global workspace (GW) which integrates and broadcasts information amount these modules. Only the information accessed by the global workspace can be consciously aware of. These modules competes with each other to gain the access to the GW and the information from the winner can trigger an all-or-none "ignition" in the GW. Information in the GW is able to be broadcasted to other modules. Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}.

		In many aspects, our theory can well accommodate GWT. NTIC processes shares several properties with the GW. Here we discuss three core properties, stability, broadcasting, and non-linear ignition, emphasised by the GWT.

		% === Stability ===
		Stability: GWT indicates that the conscious contents often show stronger stability which may be necessary for the neural system to integrate information from a variety of modules. Suggested by GWT, this is caused by top-down amplification from the GW to individual modules which gain the access to the GW \needref{}. In contrast, without assuming any additional mechanism, our theory argues that stability is a natural quality of NTIC due to its strong self-predictive characteristic. Our theory can even further quantify the stability of conscious contents by computing the mutual information between the current and the future states of a conscious process.

		% === Broadcasting ===
		\idea{A bit not sure about this part}Broadcasting: Because individual modules use different coding schemes, the neural system requires a mechanism for passing information between modules. GWT suggests that the GW is responsible for connecting the information source, translating the code, and finally making the information globally accessible. We argue that, because the NTIC process encodes high dimensional information about the environmental dynamics, it can be considered as an integrated informational entity \todo{Need rewording}. These with the coarse-graining variables involved in the NTIC process together. Other modules outside the NTIC process can decode and extract needed information for the current goal of the task.

        % === Non-linear ignition ===
        Non-linear ignition: Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates \needhelp{Is this statement correct?}. Therefore, a continuous state transition at microscopic levels may lead to a discrete and non-linear state transition at macroscopic levels. Based on our theory, when new information enters conscious contents, the NTIC process must undergo a corresponding state transition. This transition can trigger a significant change of the brain states and resembles non-linear ignition of brain activities

        \idea{Long distance connectivity?}
        \rewrite{(1) sudden, all-or-none ignition of prefronto-parietal networks; (2) concomitant all-or-none ampliﬁcation of sensory activation; (3) a late global P3b wave in event-related potentials; (4) late ampliﬁcation of broad-band power in the gamma range; (5) enhanced longdistance phase synchronization, particularly in the beta range; and (6) enhanced causal relations between distant areas, including a signiﬁcant top-down component. }
        Future modeling work is needed

		% -------------------------------- Difference -------------------------------- %
		\todo{Finish this part}
		However, there are still fundamental differences between the two theories. 
		In GWT, modules rival with each other to gain access to the GW. Our theory suggests that the one enters conscious contents is the one which can create the higher NTIC with other coarse-grained information. This difference leads very different predictions and implications. For GWT, to find the biological implementation of the rivalry mechanism (attention, for example) is critical. However, we do not assume any rivalry mechanism. Instead, we argue that, if  information carried by the coarse-grained variables can increase the predictability of the process and form high NTIC,  it naturally form a informational closed boundary and

		Up to now, GWT does not indicate in what conditions a process can be considered as a GW. This results in an intractable situation of finding the GW, especially when empirical data show distributed information encoded in many brain areas\citep{siegel2015cortical}.

		Another difference between our theory and GWT is that our theory does not suggest a neuronal core anatomical area for consciousness. \todo{Link to Section 4}. Coarse-grained information in NTIC is more crucial for consciousness rather than neural substrates supporting the global workspace.

		In sum, our theory is compatible with previous physiological evidence supporting GWT.

		\begin{WritingMaterials}

			@ Broadcasting: When new sensory information from a modality is involved in NTIC, the information can be preserved in the following dynamic of NTIC. The neural system can extract the information for specific task goals. This is equivalent to the function of broadcasting.

			@ the presence of contexts as stable coalitions shaping access to the workspace.

			@ e ‘all-or-none’ behaviour, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and amplified non-linearly into a full-blown state of high-level activity. This global ‘ignition’ has been proposed as a marker of conscious perception [70]. Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear amplification of activation which invades a distributed set of parietal, prefrontal and cingulate areas

			@ Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing? Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness. A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly defined brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ]. Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be fiexibly deployed.

			@ C1: Global availability of relevant information The need for integration and coordination \cite{Dehaene2017}

			@ Evidence for integration and broadcasting

			@ Stability as a feature of consciousness \rewrite{“ meta-stability ” seems to be necessary for the nervous system to integrate information from a variety of modules and then broadcast it back to them, achieving flexible cross-module routing.}

			@ \rewrite{integration of computational resources in a large-scale coordination and for the exchange of information among processors}

			@ \rewrite{Grounded on the distinction between conscious and unconscious processes, Bernard Baars’ global workspace theory is one of the most influential cognitive theories of consciousness. This theory relies on the metaphor of a theater. In this theater, unconscious specialized processors (equivalent to modules) are assumed to be the actors and the audience. While the audience represents the set of passive processors, actors represents active processors playing on the stage of the theater (i.e., the workspace). These actors are engaged in a competition for being seen by the audience: by broadcasting their information they actually compete for more broadcasting. Active processors with the highest coherent activity can form local coalitions that strengthen them in this competition process. The strongest coalition in this competition dominates the workspace, in a winner-take-all fashion, and corresponds to the content of consciousness. The workspace is equated by Baars to working-memory, in which only the most active content becomes conscious. Additionally, the dominant coalition benefits from global broadcasting, which allows it to recruit new processors from the audience in order to form a global coalition. Here, consciousness allows for the integration of computational resources in a large-scale coordination and for the exchange of information among processors that would otherwise remain separated. In this theory, each processor can operate in the conscious mode if it benefits from global broadcasting through the workspace, or it can operate in the unconscious mode when disconnected from the workspace. An important feature of the global workspace theory is the presence of contexts as stable coalitions shaping access to qeqthe workspace. Contexts are constituted of unconscious processors reflecting, in a hierarchical manner, our expectations, our beliefs, our goals, and ultimately our self. In particular, attention is implemented as a goal context in this theory. It is described as a mechanism that controls access to the workspace, acting as a filter and biasing the competition process toward a particular set of actors. At any given moment, the dominant coalition is under the spotlight of attention, and its informational content becomes the content of conscious experience. A crucial aspect of Baars’ theory is that it avoids the problem of the homunculus by reducing it to an audience of multiple unconscious processors. Here, there is no need for a hypothetical single conscious observer in the system, and thus there is no issue of infinite regression with a homunculus inside another homunculus. Instead, consciousness is considered to reflect the global broadcasting of information to an audience of unconscious processors. As the audience is unconscious, unsupervised, and receptive rather than attending to the information, it does not constitute an internal homunculus.}

		\end{WritingMaterials}

        % ---------------------------------------------------------------------------- %
        %                           Sensorimotor contingency                           %
        % ---------------------------------------------------------------------------- %
		\subsection{Sensorimotor contingency}
		Sensorimotor contingency (SMC) theory of consciousness is proposed to account for conscious perception. It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}. The theory radically rejects the view that conscious content is associated with information encoded in internal representations in the neural system. Rather, the quality of conscious perception depends on agents' mastery of SMCs. SMC emphasises that the interaction between a system (the neural system) and its environment is crucial to form any specific form of conscious experience.

	    Our theory in general rejects this proposal based on the fundamental assumptions of SMC.As we mentioned in \ref{sec:Conscious versus Unconscious Processing}, a process directly maps the sensory state space to the action space should not be able to achieve NTIC. Because learning of contingencies between sensory input and action output doesn't guarantee to form any NTIC process, our theory predicts that sensorimotor contingency is neither a necessary nor a sufficient condition for conscious experience. In fact, with extensive practice on a sensorimotor task with a fixed contingency, the task usually can be gradually performed unconsciously \needref{}. We believe that the neural system has established a process to directly map sensory evidence to action selection, and therefore, decrease the level of NTIC which against the basic assumption of SMC.

	    Nevertheless, our theory does appreciate the notion that interactions between agents and environment is crucial to shape specific types of conscious experience. This is because, for an agent to form a NTIC process with action output, the process needs to encode how agents' actions influence state transitions in the environment. Therefore, information of interaction should be encoded in the NTIC process and also determines the state of NTIC which associates a particular conscious content.

        Finally, a new version of SMC theory, Predictive Processing of SensoriMotor Contingencies (PPSMC), proposed by \cite{seth2014predictive, seth2015presence} makes some promising progress. PPSMC combines SMC and the predictive processing (see the next section) framework together and emphasises the importance of action counterfactual (i.e. the alternative and potential actions that an agent can perform) to conscious experience. We believe that the critical advance from SMC to PPSMC is to acknowledge the generative models for computing counterfactuals. The existence of generative models is the prerequisite equipped by the agents. So far, what PPSMC claims is deviating from simple $S\rightarrow{}R$ mappings and links the predictive information to consciousness. We argue that if predictive information for the computation of counterfactual is involved in the NTIC process, PPSMC will be compatable to our theory and may have strong explanatory power on some special conscious experience. \todo{Need a better ending}

		\begin{WritingMaterials}

			%% Intro about this theory
			@ O’Regan and Noë

			@ \rewrite{According to Noë, perceptual presence is explained by a “ sensorimotor theory ” on which perception depends on a practical mastery of sensorimotor dependencies or “ sensorimotor contingencies ” (SMCs) (O ’ Regan \& Noë, 2001). The theory inherits from Gibsonian notions of “ affordances ” (Gibson, 1979) and from enactive cognitive science (Thompson \& Varela, 2001) which stress the importance of brain-body-world interactions in cognitive processes. On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations. A strong point of this theory is that it suggests why there are differences in qualitative character between modalities, the reason being that different modalities instantiate different SMCs (O ’ Regan \& Noë, 2001). }

			@ In their seminal article O’Regan and Noë (2001) introduce sensorimotor contingencies (SMCs) as the basis of a sensorimotor account of conscious perception.

			@ In short, different types of SMCs give rise to different qualities of sensory experience

			@  Second, vision, audition, touch, etc., correspond to domains of knowledge of the respective SMCs that are exercised by an agent as part of its habitual behavior.This ‘‘mastery of SMCs’’ is what lets an agent perceive its environment and adapt its behavior accordingly

			@ And third, sensory awareness arises when SMCs are integrated with planning, reasoning, and generation of behavior

			@ The theory is a radical departure from the classical view that the brain constructs an internal representation of the outside world on which higher cognitive processes such as memorizing, reasoning, and planning operat

			@ perception depends on a practical mastery of sensorimotor dependencies or “sensorimotor contingencies” (SMCs)

			@ s the importance of brain-body-world interactions in cognitive processes. On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations.

			@ ways of acting or as something we do, rather than an internal phenomenal experience or an internal representation of the world (O’Regan \& Noë, 2001)

			@ \rewrite{I advance this truly astonishing hypothesis: To understand consciousness in humans and animals, we must look not inward, into the recesses of our insides; rather, we need to look to the ways in which each of us, as a whole animal, carries on the processes of living in and with and in response to the world around us . . . You are not your brain . . . Meaningful thought arises only for the whole animal dynamically engaged with its environment . . . And indeed the same is true for the quality of our conscious episodes . . . The taste of licorice is not something that happens in our brains.} (Noë, 2009, pp. 7–8)

			@ Because consciousness resides in our behavioural interactions with the world rather than in our brain, the theory postulates that consciousness does not derive from brain activity at all. Consequently, there is no need to explain how brain activity causes or constitutes consciousness, because it does not.

			@ O ’ Regan, J.K. and Noë, A. (2001) A sensorimotor account of vision and visual consciousness. Behav. Brain Sci. 24, 939 – 973

			@ SMC theory argues that consciousness arises from the execution of SMCs, resulting in brain – environmental interactions.

			@ The second variant of SMC theory postulates that ‘ it is not movement as such, but the consequences of potential movement that play a role ’ (in perceptual experience) ([5], p. 1015; see also [9,10,19,20]). This ‘ non-acute ’ or dispositional variant marks a signi fi cant shift in position because it de-emphasizes actual movement. \cite{pennartz2017consciousness}

			@ It stipulates that for us to be conscious of something in the environment (or of our way of interacting with the environment)

		\end{WritingMaterials}

        % ---------------------------------------------------------------------------- %
        %                            Predictive Processing                             %
        % ---------------------------------------------------------------------------- %
		\subsection{Predictive Processing}
    		Predictive processing is a powerful framework (PP) which integrates several influential ideas in the history of neuroscience including "perception as unconscious inference" from Helmholtz \citet{helmholtz1866concerning}, "analysis by synthesis", “predictive coding”, and "Bayesian brain hypothesis". This emerging theoretical framework of perception and brain function suggests that the neural system constantly generates predictions about incoming sensory signals and updates predictions based on prediction error between predictions and real sensory signals. According to PP, the neural system constantly performs unconscious statistical inference about hidden causes in the external environment. The perceptual contents are the "best guess" about the environment states including these hidden causes \citep{clark_2013, Hohwy2013}. Because it is well integrated with Bayesian brain hypothesis, the PP has been used to interpret conscious perception in many perceptual domain. \cite{Hohwy2013} \cite{SethPP2014}.

    		%% The gaps between pp and consciousness
    		PP is a powerful explanatory framework for diverse brain functions. However, to serve as a theory of consciousness, PP is still incomplete due to two theoretical gaps. First, there are enormous predictive mechanisms in the neural systems. It is  obvious that that not all the predictive information from these mechanisms is able to be part of conscious contents. Therefore, PP needs to explain the difference between conscious and unconscious predictive mechanisms. Second, if we closely look at a conscious predictive system, the only part can be consciously aware of is the result. Other details of the computation remain unconscious. PP also needs to explain how unconscious inferences is able to give rise to conscious results. In short, the two explanatory gaps prevent PP from been a complete theory of consciousness.

    		Here, from more fundamental principles, we  argue that our theory is able to well fill the two gaps simply by considering the two conditions mentioned in section \ref{sec:Conscious versus Unconscious Processing}.

    		First, predictive processes do not necessitate NTIC. A neural mechanisms is able to generate prediction does not guarantee it is an NTIC process. For example, an algorithm can take the current states of a target entity as the inputs and compute future states of the target. In this case, this algorithm can compute predictive information. However, the states of the internal variables are fully determined by the external input, implying that this algorithm is not informationally closed. We suggests that if a predictive process is not a NTIC process, predictions from this process will not be able to show in conscious contents (i.e., fail to meet the 1\lowercase{st} condition in section \ref{sec:Conscious versus Unconscious Processing}). In contrast, predictive information in the NTIC process is conscious and makes the process achieve information closure.

    		Second, as mentioned in section \ref{sec:Conscious versus Unconscious Processing}, if a process is not at the coarse-grained level achieving NTIC, this process will not be conscious (Fail to meet the 2\lowercase{ed} condition). We have provided an example in section \ref{sec:Conscious versus Unconscious Processing} in which computation can be implemented at microscopic levels. However, if the coarse-grained result of the computation is included in the macroscopic NTIC process, only the result rather than the process itself can be consciously aware of. Therefore, we predict that the statistical inferences under PP are implemented in microscopic levels. The NTIC process is ignorant to the detail information of their computations.

            Altogether, our theory provides more fundamental principles and explanations about the relationship between predictive mechanisms and consciousness. Moreover, the fundamental principles allow us to make more precise predictions about which types of PP should or should not be conscious. Therefore, our theory has stronger falsifiability and predictability beyond PP on consciousness research.

        \begin{WritingMaterials}
    		@ We first hypothesize that predictive processing stays unconscious is because it is not able to achieve NTIC.

    			@@ \idea{Example from PID controller?}

    		@ Second, according to our theory, it is obvious that the computation of predictive processing is unconscious and only the result is conscious. Because the computational details is not at the coarse-grained level which achieves NTIC.

    			@@ So far, many neuronal models and coding schema have been proposed to explain how to implement Bayesian inference and prediction at the neuronal level.

    			@@ However?

    		@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.

    		%% About the unconscious Bayesian processing
    		@ \cite{lamme2015predictive}
    			@@ To my knowledge, this is the first time this has been so explicitly laid out—writers on predictive coding thus far have always stayed a little vague on where exactly consciousness sits in the Bayesian framework.

    			@@ Yet the two points seem contradictory. In the Bayesian predictive coding framework, consciousness is the result of the unconscious inferential processes.

    			@@ However, these authors have so far been very reticent about how exactly consciousness fits into the PC framework. For now, there is an emerging idea that understands consciousness as the final result of unconsciousness processing. According to Hohwy (2013), perceptual consciousness fits in the PC theory as the ‘upshot’ or ‘conclusion’ of unconscious perceptual inferences. Melloni (2014) also expects that inferential processes are conducted behind the curtain of consciousness and what we experience are the ‘outcomes’ or ‘results’ of an unconsciou inferential process. Lamme (2015) agrees with the idea that consciousness is based on the relation or more precisely conjunction of current inputs and priors, which together produce posterior beliefs. Karl Friston agrees to a certain extent with this interpretation of consciousness. According to Hobson and Friston (2016), consciousness is not a phenomenon but a process, a process of optimizing beliefs through inference (consciousness, dreams, and inference; the Cartesian theater revisited; a response to our theater critics).

    		@ Link PP and c
    			@@ \cite{hobson2016response}
    			@@ \cite{Melloni2015}

    		%% ----------------------------------------------------------------------------
    		@ \cite{SethPP2014}

    		@ When uncertainty is high, we should expect an increase in the ability of ever higher-level prior beliefs to determine conscious experience. I

    		@ determine conscious experience.

    		@ PP combines and builds upon previous ideas about the role of “unconscious inference” in perception (Helmholtz, 1925; Barlow, 1961; Gregory, 1970), the process of “analysis by synthesis” in psychology (Neisser, 1967), the “predictive coding” approach in neuroscience (Srinivasan et al., 1982; Rao and Ballard, 1999; Huang and Rao, 2011) and “generative models” and related probabilistic computational principles (MacKay, 1956; Mumford, 1992; Dayan et al., 1995; Hinton, 2007a,b; Tenenbaum et al., 2011).

    		@ \rewrite{The brain is constantly confronted with a wealth of sensory information that must be processed efficiently to facilitate appropriate reactions. One way of optimizing this processing effort is to predict incoming sensory information based on previous experience so that expected information is processed efficiently and resources can be allocated to novel or surprising information. Theoretical and computational studies led to the formulation of the predictive coding framework (Friston 2005, Hawkins and Blakeslee 2004, Mumford 1992, Rao and Ballard 1999). Predictive coding states that the brain continually generates models of the world based on context and information from memory to predict sensory input. In terms of brain processing, a predictive model is created in higher cortical areas and communicated through feedback connections to lower sensory areas. In contrast, feedforward connections process and project an error signal, i.e. the mismatch between the predicted information and the actual sensory input (Rao \& Ballard, 1999). The predictive model is constantly updated according to this error signal. }

    		@ \rewrite{Predictive inference and perception The concept of PC overturns classical notions of perception as a largely ‘bottom-up’ process of evidence accumulation or feature detection, proposing instead that perceptual content is specified by top-down predictive signals that emerge from hierarchically organized generative models of the causes of sensory signals. According to PC, the brain is continuously attempting to minimize the discrepancy or ‘prediction error’ between its inputs and its emerging models of the causes of these inputs via neural computations approximating Bayesian inference (Figure 1 and Box 1). Importantly, prediction errors can be minimized either by updating generative models (perceptual inference and learning; changing the model to fit the world) or by performing actions to bring about sensory states in line with predictions (active inference; changing the world to fit the model).}

    		@ \rewrite{In terms of brain function, Hermann von Helmholtz’s 19th Century notion of perception as unconscious inference has found new momentum in modern formulations of ‘predictive processing’, the Bayesian brain, and the ‘free energy principle’ (Clark, 2013; Friston, 2010; Hohwy, 2013). On these formulations, which can all be subsumed under the general term ‘prediction error minimization’ (PEM, (Hohwy, 2013)) perceptual content is the result of probabilistic inference on the hidden causes of sensory signals. }

    		@ \rewrite{Generative models encoded by brain structure and dynamics make predictions about sensory inputs, based on prior expectations. Action (e.g., body movements) and perception conspire to reduce sensory prediction errors, giving rise to perceptual content and}

    		@ \rewrite{More informally, what we perceive is the brain’s ‘best guess’ of what’s out there (or ‘in here’, for perceptions of body and self).}

    		@ \rewrite{“ predictive processing ” (PP) 1 or the “ Bayesian brain ” this holds that perceptual content is determined by hierarchically organized generative (i.e., predictive) models (HGMs) of the external causes of sensory signals, induced by a process approximating Bayesian inference (Friston, 2009).}

    		@ Therefore, it's reasonably assume that if evolution wants to build predictive mechanisms, the mechanisms should be settled on the information at the \ac{cged} level.

    		@ More specifically, a forward model, which received state and action as input and compute transition and then output next states, should be build on the representation that forms the \acl{ic}.

    		@ Therefore, the state of predictive model can be conscious while it is linked to \acl{ic} representation.

    		@ Note that, a system showing some predictive power is not sufficient to be conscious.

    		@ For example, the proportional–integral–derivative controller (PID) controller shows predictive behaviours due to its derivative which computes and predict error value in the future. Derivative action predicts system behaviour and thus improves settling time and stability of the system.

    		@ However, the state of the whole PID system still be determined by the inputs, i.e. the states of the controlled process, thus cannot complete \acl{ic}.

    		. It can compute position, velocity, and acceleration of objects, and output control signals (action). However, the state of the PID controller is not information-closed. The state still fully determined by the input signals. Therefore, it fails to reach \ac{ic}. Hence, according to our theory, the PID system is not conscious.

    		@ Similarly, the neural system also has many circuits that show predictive power but do not have \ac{ic}.
    		@ considers the brain as a predictive machine
    		@ According to predictive processing account, conscious contents are the inference results (posterior from Bayesian inference framework) of predictive mechanism.

    		@ However, we can see that not all predictive mechanisms in the neural system can be consciously aware of.

    		@ So what's the critical difference between them in terms of consciousness?

    		@ We argue that when predictive mechanisms utilise the information in the informational closure, the predictive result is conscious.

    		@ Because the forward model build on the informational closure representation can be seen as part of the closure. \critical{IS THIS TRUE? NEED DISCUSSION}

    		@ we can consider two scenarios

    			@@ Predictive information is encoded in neuron populations but there is high entropy of conditional probability which means it's not closure. Therefore, the conscious level could be very low even though the it still has some degree of predictability.

    			@@ Another scenario is a forward model but its state fully depends on external sensory input. This system is not informational closed and therefore is not conscious.

    			@@ Based on this point of view, predictive power for a system does not guarantee consciousness.

    			@@ For example, in active inference \needref{active inference}, action is guided by prediction error so the state of the system is non-coloured
	\end{WritingMaterials}

        % ---------------------------------------------------------------------------- %
        %                                      IIT                                     %
        % ---------------------------------------------------------------------------- %

		\subsection{Integrated information theory}
		Integrated information theory (IIT) states that system's consciousness is determined by its causal properties. Consciousness is integrated information. As a computational theory of consciousness, the degree of discrimination and integration can be expressed in mathematical terms $\Phi$. Different from most of other scientific theory of consciousness, IIT asserts that the fundamental physical property associated with consciousness is causality.

		% -------------------------------- Similarity -------------------------------- %
		IIT and our theory shares common principles in many aspects. First common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness \needref{cite David Chalmers}. Therefore, both theories are capable of extrapolation and infer the states of consciousness in other systems beyond the human neural system.

		Second, both theories consider informational structure as the fundamental entities associated with the quality of conscious contents. IIT proposes that a "complex" which is defined as elements that generates a local maximum of integrated information as the core entity which determines the state space of subjective feeling (qualia space). In the current stage of our theory development, we have not proposed such sophisticated description of the mappting between informational structure and the qualia space. However, in line with this notion, we argue that the state space of a NTIC process determines the subjective experience possessed by the process.

		\ideaBox{Maybe synergy is the common part of the two theories }

		% -------------------------------- Difference -------------------------------- %
		% Different prediction
		Even though both theories are based on informational properties of a process, predictions of the two theories can be very different. Taking the split brain cases as the example, when splitting a system into two parts, IIT suggests that each part can form a new complex. Therefore, splitting creates two new conscious entities. However, according to our theory, splitting a system may totally destroy the informational structure that created NTIC. This may lead to very small degree of NTIC in both hemispheres, thereby entirely destroying consciousness of this system. Notwithstanding, more simulation work is needed to thoroughly clarify how the two theories make same and different predictions in different contexts. Fortunately, due to the computational nature of the two theories, precise differences of predictions can be made from relatively simple toy model in the future work.

		% Hoel's theory\cite{hoel2016can}}
		Alongside with the main theoretical development of IIT, \cite{hoel2016can,hoel2013quantifying} discussed the scale-dependent causal structures using IIT as a measure of causal power at different scales. The result shows a qualitative similarity to our theory. The causal power can emerge at macroscopic levels of a system. This claim is consistent with our prediction in which processes at macroscopic levels can achieve more deterministic and predictive state transitions. We expect further mathematical and empirical analysis can reveal the relationship between \ac{OurTheory} and Hoel's analyses about the causal power at different scales in a system.

		\begin{WritingMaterials}

			@ One common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness. \needref{cite David Chalmers}

			@ Our theory is different from IIT which proposes that consciousness is information integration in a system.

			@ For level of consciousness, IIT predicts a system with higher level of integration produces a higher level of consciousness. In our theory, the level of consciousness corresponds to the level of NTIC, which suggests that level of consciousness is determined by self-predictive information and the information about the environment encoded in the process.

			@ In terms of conscious content, IIT suggests that the causal structure of a system determines the quality of conscious contents. In the current version of our theory, how the state of NTIC process maps to conscious content has not been sophisticatedly specified. More work is needed to understand the relationship between the state of NTIC process and conscious contents.

		    @ --------------------------------------------------------------------
			@ \toWrite{Information integration without awareness}\cite{Mudrik_Faivre_Koch}
			@ \rewrite{consciousness is necessary for high-level but not low-level semantic integration}\cite{Mudrik_Faivre_Koch} we would argue an inverse relationship:"High-level information processing is necessary for consciousness." This is because higher-level information processing is more likely to create an informational closure representation.

			@ Similarly, it is not \rewrite{consciousness is necessary for multisensory integration}. It should be multisensory integration is more likely to create an informational closure representation. Because in most situations, multisensory signals are generated from hidden causes which may have deterministic dynamic and relation with each other. Therefore, to infer the hidden causes and represent the deterministic relations can form informational closure representation which is conscious.

		    @ Our theory is closely related to causal emergence described by Hoel et al. (2013) which was examined by a following work using integrated information theory (Hoel et al. 2016). More research on the precise mathematical relationship between causal emergence and our theory is needed

			@ \cite{hoel2016can}
			@ causal emergence
			@ \cite{hoel2013quantifying} examined causal power at different coarse-grained scale and show that causal power can be stronger at macro rather than micro levels.

			@ To answer the question about what is the best scale to compute Phi, \cite{hoel2016can} examined causal power at different coarse-grained scale.

			@ Further examination of the Hoel's theory and our theory is needed to elucidate the relationship between our theory and causal emergence.

			@ Both theory

			\end{WritingMaterials}

        % =============== Internal simulation and self-modelling theory ============== %
		\subsection{Internal simulation and self-modelling theory}
		\idea{I will skip this section unless you think this is necessary.}

% ============================================================================ %
%                                  Limitation                                  %
% ============================================================================ %
    \section{Limitation and Future work}
        % Can't solve the hard problem
        It's important to clarify that our theory does not intend to solve the hard problem of consciousness\citep{chalmers1995facing}. Our theory claims that different states of an NTIC process should map to different conscious contents. However, knowing the state of a conscious process does not allow us to answer "What is it like to be this system"\citep{nagel1974like}. We can consider a simplified version of the inverted spectrum argument \citep{Shoemaker1982-SHOTIS, Block1990-BLOIE, Locke1979-LOCTCE-2}. Two NTIC creatures (Alice "$A$" and Bob "$B$") living in a simple environment($E$) which has only two states $E_1$ and $E_2$. In this simple case, Alice and Bob should have only two states ($A_1, A_2$ and $B_1, B_2$) when they achieve the maximal level of NTIC (i.e. 1 bit). Our theory can only claim that Alice has different conscious experience $\hat{A}_1$ and $\hat{A}_2$ at state $A_1$ and $A_2$, respectively (same as for $\hat{B}_1$ and $\hat{B}_2$ map to $B_1$ and $B_2$). However, there is no way to know whether $\hat{A}_1$ is the same as $\hat{B}_1$ or $\hat{B}_2$.

        Instead, we believe that this is an ill-posed problem. Assuming that one day we know $\hat{A}_1$ is or is not the same as $\hat{b}_1$, this implies that we acquire at least 1 additional bit of information to make this judgement which does not exist within this simple system. Therefore, our theory is unable to answer the subjective quality that a conscious system feel like.

        % Finding potential coarse-graining functions
        \needhelp{I think I need Martin's help here, I don't know how much we should say about this in this paper. Or just leave this to the future studies}
        A major empirical difficulty of our theory is to find appropriate aggregation functions which map microscopic variables to macroscopic variables forming a NTIC process. In this paper, we do not speculate any form of aggregation functions. It seems very difficult to find an appropriate one among infinite candidates\citep{price2007causation}. Nevertheless, relevant research has been exploring the mathematical relationship between aggregation functions and macroscopic processes \citep{PFANTE.2014}. \cite{Gamez2016} has also
        systematically describe relevant issues in terms of finding data correlates of consciousness amount different levels of abstraction. These analyses are helpful to pin down the mathematical properties of the aggregation functions.

        Another potential approach is to examine "readout" mechanisms in the neural system. To perform action outputs, information encoded in the NTIC process needs to be decoded by certain readout mechanisms. To investigate how the neural system decodes coarse-grained information may advance more understanding of the aggregation function.\ideaCallout{REALLY???}

        Finally, with artificial neural networks as a universal function approximator, we can learn what aggregation functions the neural networks can learn when we set NTIC as the objective of training.

        Since NTIC is a relatively new concept in neuroscience. Less empirical studies have examined this or relevant properties in the neural system so far. The lack of empirical data is a bottleneck of our current theory development. More empirical research targeting NTIC in the neural system is needed in the future.

        \begin{WritingMaterials}
            % finding a suitable CG function
			@ \rewrite{
				not all causal relationships (or relationships of nomological dependency) among micro-events aggregate up to causal relationships among coarse-grained macro-events that are constituted by those micro-events. Instead, whether one gets causation at the macroscopic level will depend (among other things) on the particular coarse-graining that is chosen.} \cite{price2007causation}

			@ \rewrite{
				It may seem surprising, even counterintuitive, that causal and statistical dependence relationships involving fine grained microscopic variables do not automatically show up in causal and dependence relationships among the macroscopic variables that are realized by the fine grained variables.} \cite{price2007causation}

			@ \cite{jonas2017could} well demonstrated that it is difficult to understand higher-level information processing by the current neuroscience methods.

			@ Physiological location of NTIC

			@ Practical measure of NTIC.

		\end{WritingMaterials}

% ============================================================================ %
%                                  Conclusion                                  %
% ============================================================================ %
	\section{Conclusion}
	We introduce a new computational theory of consciousness based on two core assertions. First, consciousness occurs when a process achieves NTIC. Second, in the neural system, coarse-graining is necessary to construct a NTIC process at macroscopic scales. Therefore, consciousness only appears at a certain macroscopic level which achieve a high degree of NTIC.

	Our theory is based on parsimonious assumptions. Nevertheless, it is able to, first, explain a large number of empirical findings in consciousness research and, second, reconcile several other theories of consciousness by the fundamental principles among them.

	Our theory asserts that consciousness is informational-based phenomenon. We further emphasise that the scale-dependent nature of information processing is critical to conscious experience. We believe that many discrepancies in previous studies of neural correlates of consciousness resulted from measurements at inappropriate scales. Except where and when, future studies should also focus on "what scale" of the neural system the data are acquired at.

	The computational nature of the theory makes it feasible to extrapolate and apply to other non-human systems. Note that, even though our theory does not start from a functionalist point of view, it comes out with explanatory power on the functional aspect of consciousness and points out the evolutionary drive of having conscious processing.

	Finally, we quote the famous epistemological questions: "If a tree falls in a forest and no one is around to hear it, does it make a sound?". Now, we can ask a new version of this question: "If an action potential rises outside an informationally closed process, does it make any conscious percept to this process?" We answer: "if the process is conscious, the event occurring outside the realm of the informational closure should never become part of the conscious contents."

	% ============================================================================ %
	%                                      End                                     %
	% ============================================================================ %

	\section*{Funding}

	\section*{Acknowledgements}

	\section*{Supplemental Data}

	\bibliographystyle{authordate1}
	\bibliography{ref}

\newpage
\begin{backup}
\part*{Backup}
\addcontentsline{toc}{part}{Backup}
\setcounter{section}{0}
	\section*{Biological evidence of informational closure in neural system}
		\begin{ants}
			% ============================================================================ %
			%                             sederberg2018learning                            %
			% ============================================================================ %

			@ So far, not so much research on non-trivial informational closure in biological neural systems.

			@ However, \rewording{XXX}

			% Internal self-predictive mechanism
			@ Recent biological evidence suggests that low-level neurons encodes predictive information about external  and

			@ \toWrite{
				need to say this is exactly the non-trivial informational closure, and refer to equation XXX}

			@ \cite{sederberg2018learning}
			@ \rewrite{
				in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }

			@ \rewrite{
				We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}

			@ \rewrite{
				We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }

			@ \rewrite{
				Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal. This suggests that bottom-up prediction may play an important role in sensory processing}

			@ \rewrite{
				Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}

			@ \rewrite{
				Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}

			@ They also showed generalization of internal predictability across stimulus. This suggests .... what?

			@ \rewrite{
				The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}

			@ \cite{Palmer2015}
			@ \rewrite{
				Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}

			@ \rewrite{
				It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig. 3, but the brain has no direct access to visual stimuli except that provided by the retina. Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs? More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + delta t in the future? The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +delta t j w t Þ } \url{http://tinyurl.com/y9zmhlln}

			@ \rewrite{
				larger groups of cells carry predictive information for hundreds of milliseconds, }

		\end{ants}

	\section*{Relation to empirical findings in neuroscience and studies of consciousness}

		\subsection{Unconscious Processing}
		\begin{ants}
			@ According the theory, there are two factor that renders neural processes unconscious.

			@ First, processes are reflexive. This causes non-closured

			@ Second, the abstraction level of the information is below the non-trivial informational closure scale.
		\end{ants}

		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
		\subsubsection{Reflection}
		\begin{ants}
			@ Reflexive systems is not informational closured.
			@ Base	d on our theory,
			@ x -> s -> a
			@@ the system state is determined by environmental state, then it is not conscious.
			@ Therefore, in general, a simple policy network is not conscious.
		\end{ants}

		\subsubsection{Blindsight}
		\begin{ants}
			@ This also blindsight.
			@ Blindsight patients and still make above chance judgement without conscious awareness of visual targets.
			@ The stimulus-reaction policy network still intact, but it cannot form informational closure and therefore, patients has no conscious awareness of visual  targets
			@ Patient B.F. reactions are stimulus driven.
		\end{ants}

		\subsubsection{procedure memory}

		\subsubsection{cerebellum}
		\begin{ants}
			@ cerebellum feed-forward connections, maybe just a policy network.\needref{cerebellum}
		\end{ants}

		\subsection{Under the level of informational closure}
		\subsubsection{statistical inference}
		\begin{ants}
			@ The computation of Bayesian brain is unconscious.
		\end{ants}

		\subsubsection{subliminal perception}
		\begin{ants}
			@ Above chance performance can be performed through non-closure pathway (reflexive behaviours)

			@ Due to coarse-graining, mapping between changes of microstate
		\end{ants}
		\subsubsection{Libet Experiments}

		\subsection{Deterministic vs probabilistic}
		\cite{dehaene2017consciousness}
		\cite{vul2008temporal, moreno2011bayesian, asplund2014attentional, vul2009attention}

	\section*{About Phenomenology (conscious processing)}
\subsection{Perceptual overflow}
\subsection{Volition and freewill}
\begin{ants}
	@ Volition is a result of coarse-graining

	@ Lebel's experiment can be well explained by the experiment.
\end{ants}

\subsection{Planning}
\subsection{Imagination}
\subsection{Dream vs non-dream sleep}
\subsection{Binocular rivalry}
\subsection{Hallucinations}
\subsection{Synaesthesia}

	\section*{Theory predictions (Counter-intuitive prediction)}

\subsection{informational closure}
\begin{ants}
	@ We predict that through coarse-graining, conscious agents create
\end{ants}

\subsection{Prediction on split-brain (vs IIT)}
* IIT suggests that cutting, two subparts may both still have MIP, therefore, have two conscious mind.

* However, our theory suggests that if the cut largely destroy the \ac{ic}, then both part may not be conscious.

\end{backup}

\end{document}

### 2019-08-26 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

--- 2019-06-26 Backup/Paper_neural_coarse_graining_of_consciousness_backpuBeforeDeleteWritingMaterials.tex
@@
 
-\excludeversion{WritingMaterials}
-\excludeversion{backup}
+% \excludeversion{WritingMaterials}
+% \excludeversion{backup}
 
@@
 % ============================================================================ %
-\title{A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness }
+\title{Information Closure Theory of Consciousness}
 
@@
 \begin{document}
+    \linenumbers
 	\maketitle
@@
 For example, the intermediate level theory of consciousness suggests that the intermediate level seems to be privileged with respect to consciousness.
-It is true that we do not experience information processed by individual neurons which is always highly noisy.
+It is true that we do not experience information processed by individual neurons which is always highly stochastic noisy.
 In addition, we have no conscious experience from interpersonal activities despite massive interactions among individuals.
@@
 Out theory provides a quantitative distinction between conscious and unconscious processing.
-		% Sorry the last part should have been deleted
+
 	\end{abstract}
@@
 	\section*{Keywords:}
-	Keywords: theory of consciousness, informational closure, neural coarse-graining, level of analysis
-
+	Keywords: consciousness, informational closure, neural coarse-graining, level of analysis
+
+% ============================================================================ %
     \newpage
@@
                 @@ "form" NTIC
+            @ Replacement
+                @ correlate -> ?
+                @ information processing -> ?
+                @ achieve -> form
+        \end{ants}
+
+% ============================================================================ %
+    \newpage
+    \section*{Discussion points}
+        \begin{ants}
+            @ I can understand that an NTIC process must be coarse-graining of the "full process" (Environment + NTIC or we say {E, Y}).
+But I am still thinking is this the same as my original idea that variables forming the NTIC process are coarse-grained from microscopic variables?
+This is very critical to how we present this paper.
+
         \end{ants}
@@
 Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials along axons.
-However, you have no idea that you are one of neurons in Alice's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup.
+However, you have no idea that you are one of the neurons in Alice's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup.
 You are ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.
@@
 However, her conscious experience does not reflect the dynamic of your membrane potential or the action potentials you send to other neurons every second.
-That is, information in Alice's conscious experience does not contain information involved in your information processing.
+That is, not all information you have is available to Alice's conscious mind.
 
@@
 		%% scale
-		It seems to be true that we are unable to consciously access information processed at every scale in the neural system.
-Only information at certain levels of coarse-graining can become conscious contents.
-At microscopic levels of neural systems, information processing in individual neurons is noisy and state transitions of neurons are stochastic \citep{Goldwyn2011, White2000}.
-However, instead of stochastic action potentials and fluctuation of random noise at microscopic levels, what we are aware of in our conscious mind shows astonishing stability and robustness against the ubiquitous noise in the neural system \citep{mathis1995computational}.
-Alongside, some parts of the neural system contribute very little to conscious experience (the cerebellum for example \citep{lemon2010life}), also suggesting that conscious contents do not have one-to-one mapping to all parts of the brains.
-Likewise, experience does not associate with states of the macroscopic brain level because state space of conscious experience is much larger than what a single coarse-grained variable can represent.
-Additionally, we do not experience "super-consciousness" when we have massive inter-individual interactions with other human-beings.
-Even though evidence has shown several types of collective information processed at human social groups levels exist \citep{malone2015handbook}, information processed at this level seems to depart from our individual conscious contents.
-        \idea{I still think this social example is fine. But the question will become what do we care about? Physical scale or coarse-graining? They are defined in different ways.}
+
+		It seems to be true that we are not consciously accessing information processed at every scale in the neural system.
+There are both more microscopic and more macroscopic levels than the level corresponding to the conscious contents.
+On the one hand, dynamics of individual neurons are stochastic \citep{Goldwyn2011, White2000}.
+However, what we are aware of in our conscious mind shows astonishing stability and robustness against the ubiquitous noise in the neural system \citep{mathis1995computational}.
+In addition, some parts of the neural system contribute very little to conscious experience (the cerebellum for example \citep{lemon2010life}), also suggesting that conscious contents do not have one-to-one mapping to the entire state of the neural system.
+On the other hand, experience is more detailed than just a binary process, suggesting that the state space of conscious experience is much larger than what a single coarse-grained variable can represent.
 
 		%% our argument
-		In this article, we propose a new theory of consciousness, called \ac{OurTheory}.
-This proposal states that consciousness does not rest on particular neural architectures or locations in the neural systems.
-Instead, we argue that consciousness correlates with information processing at a certain coarse-grained level where the neural systems create a high degree of non-trivial informational closure (NTIC)\footnote{In the following NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}.
-We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC and the \textit{contents} of consciousness corresponds to the state of the NTIC process (for the level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
-
-		% information-based claim 
-		\ac{OurTheory} takes a strong position that consciousness is an information-based phenomenon.
-I.e.
-the current proposal can be considered as an information correlate of consciousness (ICC).
-Based on the presumption, we construct our theory with two core concepts: non-trivial informational closure and neural coarse-graining.
-In this article, we first introduce non-trivial informational closure and its importance to information processing for human scale agents.
-We next argue that through coarse-graining the neural system can achieve high degree of non-trivial informational closure at a specific coarse-grained level.
-We then propose that the state of the informationally closed process correlates with the state of consciousness for both levels and contents which can be explained, quantified, and predicted computationally by our theory.
-We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies and reconcile several current major theories of consciousness.
-Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from this theory to the current consciousness science.
+		In this article, we propose a new information-based theory of consciousness, called \ac{OurTheory}.
+We argue that every process with a high degree of not-trivial information closure (NTIC) has consciousness.
+This means that the state of such a process corresponds one-to-one to conscious content.
+\footnote{In the following NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}.
+We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC.
+(for the level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
+
+		In the following, we first introduce non-trivial informational closure and its importance to information processing for human scale agents \ref{sec:Non-trivial informational closure}.
+We next argue that through coarse-graining the neural system can form a high degree of non-trivial informational closure at a specific coarse-grained level\ref{sec:Neural coarse-graining}.
+We also illustrate how \ac{OurTheory} \ref{sec:OurTheory} can parsimoniously explain empirical findings from previous consciousness studies \ref{sec:Conscious versus Unconscious Processing} and reconcile several current major theories of consciousness\ref{sec:Comparison with other theories}.
+Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from this theory to the current consciousness science \ref{sec:Limitation and Future work}.
 
@@
 			\includegraphics[width=\textwidth]{WritingMaterials/Fig_ScaleProblemOfConsciousness/ScaleProblemOfConsciousness.pdf}
-			\caption{The scale problem of consciousness}
+			\caption{The scale problem of consciousness: Human conscious experience does not reflect information processed at every scale.
+Only information at a certain scale in the neural system is conscious.}
 	   	\end{figure}
 
-		%% backup point
-		\begin{WritingMaterials}
-			@ consciousness is information
-
-			@ conscious contents
-				@@ \toWrite{lower level}
-				@@ Information processing of individual neurons are noisy.
-				@@ We don't have conscious content changes when individual neurons fire action potentials.
-				@@ Don't even mention ion channel dynamic.
-
-				@@ \toWrite{Higher-level dynamic}
-
-			@ For human, physics at our body scale are nearly follow classic physics, which is deterministic.
-
-			@ \toWrite{Human tendency for active prediction }
-				@@ \cite{Stahl2015} \rewrite{
-					Given the overwhelming quantity of information available from the environment, how do young learners know what to learn about and what to ignore?
-We found that 11-month-old infants (N = 110) used violations of prior expectations as special opportunities for learning.
-The infants were shown events that violated expectations about object behavior or events that were nearly identical but did not violate expectations.
-The sight of an object that violated expectations enhanced learning and promoted information-seeking behaviors; specifically, infants learned more effectively about objects that committed violations, explored those objects more, and engaged in hypothesis-testing behaviors that reflected the particular kind of violation seen.
-Thus, early in life, expectancy violations offer a wedge into the problem of what to learn.}
-
-			@ Intuitive physics \needref{Intuitive physics}
-
-		\end{WritingMaterials}
-
+% ============================================================================ %
+%                       Non-trivial informational closure                      %
+% ============================================================================ %
 	\section{Non-trivial informational closure} \label{sec:Non-trivial informational closure}
@@
 One can distinguish a system from its environment by computing the closedness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}.
-The closedness can be further quantified by information theory.
-
-		\begin{WritingMaterials}
-			@ Consciousness as an intrinsic information. Therefore, information should be self-define. This means the boundary of conscious content should be related to informational closure.
-
-			@ \idea{should we describe the intuition of boundary problem here?}
-
-			@ ============================================================================
-
-			@ \rewrite{
-				The notion of closure plays a prominent role in systems theory where it is used to identify or define the system in distinction from its environment} \cite{BERTSCHINGER.2006}
-
-			@ \rewrite{
-				Our theoretical interest concerns the type of system that is a unity for and by itself and not only for an external observer distinguishing some entity from the rest of the world.
-This requires a system that can be described as a whole without reference to its environment.
-In systems theory, this property is usually referred to as closure.}\citep{BERTSCHINGER.2006}
-
-			@ \rewrite{
-				These concepts of closure play an important role in the architecture of systems
-				theory, because they are used to
-				1. define the system (in distinction to its environment) and to
-				2. explain the autonomy of the system.}\citep{BERTSCHINGER.2006}
-
-			@ \rewrite{
-				Informational closure: The higher process is informationally closed, i.e., there is no information flow from the lower to the higher level.
-Knowledge of the microstate will not improve predictions of the macrostate.} \citep[p.
-4]{PFANTE.2014}
-
-		\end{WritingMaterials}
+The closure can be further quantified by information theory.
 
@@
 			\noindent
-			Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network in Figure~\ref{fig:SystemAndEnv}.
+			Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network in Fig.\ref{fig:SystemAndEnv}.
 Then, information flow $J_{t}$ from the environment $E$ to a system $Y$ at time $t$ can be defined as the conditional mutual information $I$ between the current environment state $E_{t}$  and the future system state $Y_{t+1}$ given the current system state $Y_{t}$
@@
 				\end{figure}
+				\todo{Modify this figure}
 
 			\noindent
-			\cite{BERTSCHINGER.2006} defines that a system is informationally closed when information flow from the environment to the system is close to zero.
+			\cite{BERTSCHINGER.2006} defines that a system is informationally closed when information flow from the environment to the system is zero.
 
@@
 			\noindent
-			However, informational closure can be achieved non-trivially.
-In the non-trivial case, even a system that contains (or encodes) information about the environment is still informationally closed.
-This means
+			However, informational closure can be formed non-trivially.
+In the non-trivial case, even though a system contains (or encodes) information about the environmental dynamics, the system can still be informationally closed.
+In such cases, the mutual information between the current states of the environment and the future state of the system is larger than zero\footnote{Here we assume that that the environment contains more information than the system, i.e.
+$H(E|S)>0$ and $E\neq S$}.
 
@@
 			This implies the system contains in itself all the information about its own future and the self-predictive information is gained from the information about the environment.
-Therefore, to achieve NTIC, the system can internalise and synchronise the dynamics of the environment, i.e.
+Therefore, to form NTIC, the system can internalise and synchronise the dynamics of the environment, i.e.
 modelling the environment.
@@
 This gives biological agents a great functional and evolutionary advantage.
-Practically, \cite{guttenberg2016neural} proposed that NTIC can be achieved by maximising the predictive power about the environment and the self-predictive information of the system concurrently.
+Practically, \cite{guttenberg2016neural} proposed that NTIC can be formed by maximising the predictive power about the environment and the self-predictive information of the system concurrently.
 
 			% Biological evidence of informational closure in the neural system
-			Despite the significant advantage for biological systems to achieve NTIC, to our knowledge, studies directly examining NTIC in biological systems are limited.
-However,  recent studies have shown relevant properties in the visual system of salamanders.
-By examining the salamander retina, in two studies \citep{Palmer2015, sederberg2018learning} the authors found that the a large groups of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states (see Figure~\ref{fig:sederberg2018learning}), therefore, in line with the characteristic of NTIC.
+            % 			Despite the significant advantage for biological systems to form NTIC, to our knowledge, there are only a few studies directly examining NTIC in biological systems.
+Recent studies have shown relevant properties in the visual system of salamanders.
+Two studies \citep{Palmer2015, sederberg2018learning} examined salamander retina and found that the a large group of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states (see Fig.\ref{fig:sederberg2018learning}), therefore, in line with the characteristic of NTIC.
 Therefore, the self-predictive information of the neural populations can guide prediction about external stimuli without reference to stimulus parameters explicitly.
@@
 
-			\begin{figure}[H]
-				\includegraphics[width=\textwidth]{WritingMaterials/Fig_Sederberg/Fig_Sederberg.pdf}
-				\caption{Figure adapted from \cite{sederberg2018learning}}
-				\label{fig:sederberg2018learning}
-			\end{figure}
-
-			\begin{comment}
-				@ ===
-
-				@ \rewrite{
-					Internal information reflects the spatial and temporal correlations in the stimulus.}
-
-				@ \rewrite{predictive information is encoded synergistically.}
-
-				@ \rewrite{
-					in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }
-
-				@ \rewrite{
-					We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}
-
-				@ \rewrite{
-					We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }
-
-				@ \rewrite{
-					Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal.
-This suggests that bottom-up prediction may play an important role in sensory processing}
-
-				@ \rewrite{
-					Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}
-
-				@ \rewrite{
-					Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}
-
-				@ They also showed generalization of internal predictability across stimulus. This suggests .... what?
-
-				@ \rewrite{
-					The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}
-
-				@ \cite{Palmer2015}
-				@ \rewrite{
-					Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}
-
-				@ \rewrite{
-					It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig.
-3, but the brain has no direct access to visual stimuli except that provided by the retina.
-Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs?
-More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + delta t in the future?
-The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +delta t j w t Þ } \url{http://tinyurl.com/y9zmhlln}
-
-				@ \rewrite{
-					larger groups of cells carry predictive information for hundreds of milliseconds, }
-
-			\end{comment}
-
-			%% backup
-			\begin{comment}
-				@ Accurately model deterministic environment
-				@ \rewrite{
-					This demonstrates that a system exhibiting certain internal regularities as measured by $A^* = MI(Sn+1; Sn)$ can achieve informational closure either by gaining information about the environment or by increased autonomy, i.e.
-by becoming unpredictable or uncontrollable from the (13) environment.
-Therefore, information about the environment, i.e.
-modelling, and autonomy can be considered as complementary strategies for achieving informational closure.}
-
-				@ By Action
-
-				@ In the next section, we claim that the neural system achieve NTIC through coarse-graining.
-			\end{comment}
-
-	\section{Neural coarse-graining}
+            % 			\begin{figure}[H]
+            % 				\includegraphics[width=\textwidth]{WritingMaterials/Fig_Sederberg/Fig_Sederberg.pdf}
+            % 				\caption{Figure adapted from \cite{sederberg2018learning}}
+            % 				\label{fig:sederberg2018learning}
+            % 			\end{figure}
+
+% ============================================================================ %
+%                            Neural coarse-graining                            %
+% ============================================================================ %
+	\section{Coarse-graining In The Neural System} \label{sec:Neural coarse-graining}
 
 		%% stochasticity at microscopic levels
-		To create NTIC in a highly stochastic system (e.g., the neural system) is challenging.
-The more a system is influenced by the environment the more information about the environment's state it has to contain itself.
-This however requires the predictability of the environment state and is therefore impeded by noisy environments.
+		To create NTIC with a highly stochastic process is challenging.
+NTIC requires the predictability of the system state and is therefore impeded by noise in the system.
 Information processing at the microscopic levels (the cellular levels) in the neural system suffers from multiple environmental noise sources throughout, including sensory, cellular, electrical, and synaptic noises.
-Previous studies have shown that states of neurons have large trial-to-trial variability at the cellular level.
-That is, the same pattern of activity never occurs twice even when the same stimulus is presented.
-Neurons are inevitably subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
-Furthermore, environmental information is always only partial observable to individual sensors and neurons which only receive little amount of information from the environment.
-Therefore, information about the environment state at the cellular level is difficult to represent.
+For example, neurons have large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
+
+        % 		Furthermore, environmental information is always only partially observable to individual sensors and neurons which only receive little amount of information from the environment.
+Therefore, information about the environment state at the cellular level is difficult to represent at the cellular level.
 It is implausible to construct NTIC processes at microscopic levels.
@@
         %% Our argument
-        \critical{Need Discussion}
 		However, we argue that, neural systems can form NTIC at certain macroscopic levels by coarse-graining microscopic neural states.
-Despite the microscopic levels in the neural system is stochastic and difficult to form NTIC processes, one solution to overcome the difficulty is to coarse-grain and encode information in coarse-grained variable to form stable and robust representation in the system.
-Coarse-graining refers to many-to-one functions that map microscopic states to macroscopic states.\needref{Do we need reference?}.
+Although the microscopic levels in the neural system are stochastic and cannot form NTIC processes, coarse-grained variables can still form stable and robust representations in the system.
+Coarse-graining refers to many-to-one functions that map microscopic states to macroscopic states.
 In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}.
-This is a common neural coding strategy that we can see in large number of previous neurophysiological studies.
-For example, in the temporal domain, neural spikes across time can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}.
+This is a common neural coding scheme that we see in a large number of previous neurophysiological studies.
+For example, individual neural spikes in a transient time span are stochastic, but they can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}.
 Neurons encode stimulus intensity by increasing or decreasing firing rate.
 \citep{kandel2000principles}.
-In this coding scheme, individual neural spikes in a transient time span are not meaningful and stochastic \citep{stein2005neuronal}.
+\citep{stein2005neuronal}.
 In contrast, rate codes are relatively stable and are highly robust against noise caused by the variation of inter-spike intervals.
+The robustness is direct consequence of the many to one map used.
 
 		% population code
-		Another example of coding strategy using coarse-graining is population coding.
-In this coding scheme, information is represented by joint spatiotemporal activities of several neurons.
+		Another example of coarse-graining in neural systems is population coding.
+In this coding scheme, information (e.g.
+orientation of a bar) is represented by activation patterns of a population of neurons.
+Multiple activation patterns could represent the same information content.
+The subspaces of the joint state space of these neurons are the macroscopic coarse-grained variables.
 Therefore, the information is encoded in coarse-grained variables whose values are jointly determined by neural activation patterns within a neural population \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
-In such cases, activities of every single neuron is not informative and stochastic.
-Instead, coarse-grained variables (such as population averaging and population vector) are able to represent information more stably.
+In such cases, encoded information cannot be read out by the stochastic activities of a single neuron.
+Instead, coarse-grained variables (such as population averaging or population vector, i.e.
+weighted sum of the preferred directions of a population of neurons) are able to represent information more stably.
 Encoding information at coarse-grained levels allow the neural system to ignore certain causal interactions relevant to fine-grained level of description \citep{Woodward2007-WOOCWA}.
@@
 		% neural coarse-graining by Nic
-		As mentioned above, it has been empirically shown that NTIC can be achieved by coarse-graining sensory inputs in artificial neural networks.
+		The practical implementation mentioned above suggests that  NTIC can be formed by coarse-graining sensory inputs in artificial neural networks.
 \citep{guttenberg2016neural} proposed a "neural coarse-graining (NCG)" architecture (fig.\ref{fig:NCG}) which aims to capture the emergent large-scale dynamics in the environment.
-The NCG network learns to coarse-grain input signals and extract latent parameters which are both predictive and predictable in the input signal and therefore achieves NTIC by building a higher-level representation of the underlying dynamics in the deep layers.
-More importantly, using this architecture, agents can process information and act at coarse-grained macroscopic levels.
-
-		\begin{WritingMaterials}
-    		% --- This figure is not necessary now ---
-    		\begin{figure}
-    			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/Fig_temp/PDFXCview_2018-06-08_14-24-03.png}
-    			\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
-    			\label{fig:NCG}
-    		\end{figure}		
-    	\end{WritingMaterials}
+The NCG network learns to coarse-grain input signals and extract latent variables which are both predictive and predictable in the input signal and therefore form NTIC.
 
 		%% not monotonic
-		It is important to note that NTIC can be a non-monotonic function of scale of coarse-graining.
-If macroscopic variable is overly coarse-grained the system states can result in low degrees of NTIC.
+		It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+We saw above that not coarse-graining enough and therefore considering processes that are too microscopic leads to low values of NTIC.
+We also saw that coarse-graining further can increase the values of NTIC.
+However, if the macroscopic variable is overly coarse-grained the system states can result in low degrees of NTIC.
 For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus looses the self and environmental predictive power.
-The non-monotonic relationship is also supported by empirical evidence.
-\cite{sederberg2018learning} showed that the efficiency of reading out self-predictive information of neural population is higher when the number of cells in a populations is 4 than it is when that number is 7 or 10 cells.
-This implies an optimal coarse-graining scale for NTIC processes.
-% Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}\citep{sederberg2018learning}
 
         %% Link to consciousness
-        At the physical scale which human beings live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
-This suggests that information in the environment is nearly closed at a right spatial-temporal scale.
-Therefore, this gives agents living at this physical scale great advantages if the agents form a NTIC process internally.
+        % \ideaCallout{Discuss this part}
+        % At the physical scale which human beings live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
+This suggests that information in the environment is nearly closed at the right spatio-temporal scale.
+Therefore, this gives agents living at this physical scale great advantages if the agents form an NTIC process internally.
 Therefore, coarse-graining becomes necessary to map microscopic sensory and neuronal states into macroscopic NTIC process.
 
-        %This means that it is possible for agents to live at this physical scale to build NTIC process internally.
-    % More importantly, the information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
-
-		\begin{WritingMaterials}
-			@ \rewrite{
-				Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}
-
-			@ neural system use population coding and temporal coding to fight against noise.
-
-			@ Therefore, even though the low level information processing is noisy, it is possible that the neural system achieve NTIC at a coarse-grained level.
-
-			@ This implies that the information about the environmental dynamic should be represented at a certain coarse-grained level rather then other levels.
-
-			%% Microscopy Deterministic
-			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions are nearly deterministic.
-
-			@ \idea{Need something here}
-
-			%% coarse-graining is necessary
-			@ Hence, to coarse-grain states of microscopic levels is necessary to represent and model the human-scale environment state and dynamics.
-
-			@ Coarse-graining is necessary to resist noise
-
-			@ \rewrite{ The population will therefore be relatively insensitive to the loss of
-				cells or noise in a small number of cells} \cite{eurich2000multidimensional}
-
-			@ Studies have shown that coarse-graining is a common way that the neural system cope with inevitable noise at microscopic levels.
-
-			@ \rewrite{Because the sequence of action potentials generated by a given stimulus varies from trial to trial, neuronal responses are typically treated statistically or probabilistically}
-
-			@ Note that, information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
-
-			@ Population coding
-
-				@@ review ref
-
-					@@@ \cite{Stanley2013}
-
-					@@@ \cite{QuianQuiroga2009}
-
-				@@ \rewrite{
-					Averaging is used in many neural systems in which information is encoded as patterns of activity across a population of neurons that all subserve a similar function (for example, see REFs 140,141 )}
-									140.
-Georgopoulos, A., Schwartz, A.
-\& Kettner, R.
-Neuronal population coding of movement direction.
-Science 233, 1416–1419 (1986).
-141.
-Lee, C., Rohrer, W.
-H.
-\& Sparks, D.
-L.
-Population coding of saccadic eye movements by neurons in the superior colliculus.
-Nature 332, 357–360 (1988).
-
-				@@ \rewrite{
-					Electrophysiological studies in the monkey have shown that behaviourally relevant signals are averaged not only across neuronal populations but also over time in the formation of a behavioural decision 156 .} 156.
-Gold, J.
-I.
-\& Shadlen, M.
-N.
-Representation of a perceptual decision in developing oculomotor commands.
-Nature 404, 390–394 (2000).
-
-				@@ \rewrite{A distributed representation of information of this type is more robust to the effects of noise.}
-
-				@@ \rewrite{
-					Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli.
-These features consist of spatial-temporal sequences of action potentials distributed across neurons and/or time.}
-
-				@@ The diverse response selectivity of sensory neurons
-
-				@@ \rewrite{
-					How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}
-
-				@ sensory hierarchy
-					@@ sensory hierarchy also shows characteristic of coarse-graining
-
-					@@ Due to partial information that sensors can receive
-
-					@@ To form complex representation like shape, objects, coarse-graining is necessary.
-
-					@@ Through coarse-graining, \highlightAndComment{higher level}{might be confusing, need to think about the terminology here} cortical areas can integrate those partial information to infer hidden causes.
-
-				@ Through two objectives during training, the model can achieve NTIC.
-
-				@ this can be achieved by maximising the self-predictive power of deep layers and its entropy through all training data.
-
-				@ With the objectives, NCG network learns to coarse-grain input signals and  extract latent parameters which are both predictive and predictable in the input signal and therefore achieves NTIC by building a higher-level representation of the underlying dynamics in the deep layers.
-
-                @ \ideaBox{Consider the two points}
-                @ ----------------------------------------------------------------------------
-                @ Achieving NTIC is the key objective to to extract out latent control parameters in the environment.
-				@ Agents can process information and act at abstract levels
-				@ ----------------------------------------------------------------------------
-
-				@ At the physical scale which human being live, the environmental dynamics is nearly deterministic following the laws of classical physics.
-This means that it is possible for agents living at this physical scale to build NTIC process internally.
-
-				@ When the information in individual sensory channel is noisy and partial, coarse-graining becomes necessary for achieve NTIC.
-			\end{WritingMaterials}
+% ============================================================================ %
+% Boundary problem 1: Add another NTIC process
+% 1. Ignore it / maybe next paper
+% 2. Acknowledge the problem but we don't have solution now
+% 3. Write down our comment
+
+% Micro/Macro and Environment point of views
+%   Whether a process can be a part of the environment
+% ============================================================================ %
 
@@
 % ============================================================================ %
-	\section{A neural coarse graining theory of consciousness}
-
-        In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory} \todo{We really need a good name}. The Theory offers two propositions:
-        \begin{enumerate}
-            \item We argue that the existence of an NTIC process within a system is sufficient for information processing to be conscious.
-            \item  For the neural system that achieves NTIC must necessarily satisfy coarse-graining
-        \end{enumerate}
-
-        In what follows, we will first establish two presumptions on which this Theory depends. Then, we will develop the propositions in detail.
-
-        The first presumption is that every human conscious precept is highly informative.
+	\section{A neural coarse graining theory of consciousness}\label{sec:OurTheory}
+
+        In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory} \todo{We really need a good name}.
+        % \begin{enumerate}
+        %     \item We argue that the existence of an NTIC process within a system is sufficient for information processing to be conscious.
+        %     \item  A system that forms NTIC must necessarily satisfy coarse-graining
+        % \end{enumerate}
+
+        We argue that the existence of an NTIC process within a system is sufficient for information processing to be conscious.
+
+        In what follows, we will first establish two assumption on which this Theory depends. Then, we will develop the propositions in detail.
+
+        The first assumption is that every human conscious precept is informative.
 Here, "informative" refers to the resolution of uncertainty.
-Being in a certain conscious state rules out an enormous number of other possible conscious states.
-This is in line with the impression that our conscious experience consist of highly multidimensional information and usually involves information from multiple modalities.
-Therefore, every conscious precept resolves a huge amount of uncertainty and provides considerable information.
-
-        This presumption is in agreement with one of the axioms, \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
+Being in a certain conscious state rules out a  number of other possible conscious states.
+This is in line with the impression that our conscious experience consist of multi-dimensional information and usually involves information from multiple modalities.
+Therefore, every human conscious precept resolves some amount of uncertainty and provides  information.
+
+        This assumption is in agreement with the "axiom", \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
 2]{oizumi2014phenomenology}.
 
-        Based on this presumption, we postulate that the amount of (self-)information possessed by a conscious percept should be equal to the (self-)information of a particular event or entity in the physical reality.
+        We further assume that all information requires physical substrates. 
+        From these two assumptions, it follows that the amount of (self-)information possessed by a conscious percept must be equal to the (self-)information of a particular event or entity in the physical reality.
+
         In this theory, we consider information is the common language between conscious experience and the physical reality.
-We further take a radical standpoint and postulate that consciousness is fundamentally associated with specific kind of information, i.e., the information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}) and discard the notion of neural correlates of consciousness(NCC).
-
-        The second presumption is that the amount of information in consciousness is bounded.
-Even though information involved in every conscious percept is extremely rich, it is still limited and we do not consciously feel everything in this universe.
-This leads to the boundary problems of consciousness \cite{goff2006experiences}.
-There should exist information boundaries for every conscious entity.
-If consciousness is an information-based phenomenon, we should be able to identify the boundaries with measures of information theory.
-Specifically, we claim here that boundaries are defined by information closure.
-Therefore, information closure should be observed in physical systems with consciousness .
-
-        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level.
-Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}.
-        Information closure also implies that the system is ignorant of information outside of the system.
-Therefore, if a coarse-grained level achieves information closure, it suggests the NTIC process at the coarse-grained level is ignorant of information processing happening at microscopic levels and also higher coarse-grained levels.
-This virtually makes the informational closed macroscopic levels as a complete reality.
-        \todo{Due to my concern mentioned last week, I think I should also mention the closure is not only to the environment but also to the microscopic levels}
-
-        Finally, our conscious experience always reflects some information about environment and bodily states, i.e.
-non-trivial information.
-To account for the information-based considerations, we propose that NTIC is a fundamental informational property associated with consciousness.
-
-        \ideaBox{Informational closure and level identification}
-
-        \begin{WritingMaterials}
-        For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between.
-Assuming that Alice is conscious, the conscious experience that Alice has should not involve any information about Bob.
-
-        \todo{Considering putting this para}
-        Similarly, we can apply this scenario to brain processing between two regions. We can consider a thought experiment. 
-        Imagining that in the future, one poor subject attend this experiment.
-We remove the subject's visual cortex from other brain areas.
-However, we keep all the connection between the two parts of the brain intact by replacing dendrites and axons between the two parts with micro electronic cables.
-Because these cables are very long, we can move the visual cortex to the surface of Mars.
-Now the experimenters give visual cortex a input signal.
-If the signal travels with the speed of light, it still takes three seconds to reach the other part on the earth.
-We can ask: Between the experimenters send the input signal and the information reach the part on the earth, what visual conscious content does the subject experience in the three seconds?
-We presume that in this three seconds subject's conscious experience should not contain any information about the visual input.
-Otherwise, the subject may be able to use the information to perform subsequent actions.
-This violates physics.
-This may look like a trivial questions.
-
-        However, in many systems, it is difficult to achieve NTIC at microscopic levels due to stochasticity.
-Through coarse-graining, NTIC processes become possible at macroscopic levels.
-Therefore, coarse-graining is necessary for many biological systems to implement NTIC processes, especially for the neural system (Fig.
-\ref{fig:LevelOfConsciousness}).
-In the following, we explained this framework and provide mathematical definitions and implications of ICC.
-        \end{WritingMaterials}
-
-		\begin{WritingMaterials}
-
-            @ As we mentioned in Chapter 3, to form non-trivial informational closure has a huge evolutionary advantage for the creatures interacting with the environment at our scale.
-
-            @ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}
-
-    		@ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.
-
-    		@ This drives the neural system to create a non-trivial informational closure.
-
-            @ Therefore, NTIC emerges from evolutionary processes is functionally plausible.
-
-            @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.
-
-    		@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:LevelOfConsciousness})
-
-            @ Therefore, the NTIC correlating conscious experience must settled at coarse-grained macroscopic levels.
-
-    		@ Through coarse-graining, we can define a new set of variables.
-
-            @ information is scale-dependent
-
-    		@ If the new set of variables are informational closure, then this creates a new \textit{reality} for all the variables inside.
-
-    		@ \textit{Reality} here means that the all the future states of the system are driven by the current information (include variables and the relationships) within the boundary.
-
-            @ Relationship between coarse-graining, scale and interaction with environment
-
-    		@ \rewrite{
-    			This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}
-
-    			@@ conscious perception are very stable and time invariant.
-    			@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.
-
-            @ To summaries, in our framework, consciousness is 
-    			    @@ Intrinsic
-
-    			    @@ Informative
-
-    				@@ scale-dependent
-
-             % our claim   
-    			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.
-
-    			@ We further postulate that level of consciousness corresponds to informational closureness of processes.
-
-    			@ The contents of consciousness correspond to the states of the non-trivial informational closure.
-
-    		% Following
-    			@ In the following part, we....\todo{todo}
-
-    			@ This is the same as "if a tree falls in a forest" thought experiment.
-
-    			@ Therefore, to understand this system, you don't need more information from external environment.
-
-    			@ It also means everything in this system is self-defined.
-
-    			@ \critical{I need to somehow acknowledge \cite{pennartz2017consciousness}}
-    				@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}
-
-    				@@ pennartz levels are defined by functional elements call "functional ensembles".
-\cite{pennartz2017consciousness} \rewrite{This delineation is different from a scale-based distinction of levels, because different levels are distinguished here based on function , i.e., what each level can accomplish in terms of computation and representation, culminating in perception at the highest level.}
-
-    			@ \rewrite{
-    				Multilevel views on consciousness and cognition have been expressed before by many other theorists, such as Oppenheim and Putnam (1958), Attneave (1961), Hofstadter (1979, 1985), Churchland and Sejnowski (1992), Wimsatt (1994), and Lycan (1996).} \cite{pennartz2017consciousness}
-
-    				@@ Oppenheim , P.
-, \& Putnam , H.
-( 1958 ).
-Unity of science as a working hypothesis .
-In H.
-Feigl , G.
-Maxwell , \& M.
-Scriven (Eds.), Concepts, theories, and the mind – body problem (pp.
-3 – 36 ).
-Minneapolis : University of Minnesota Press .
-    				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
-    				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
-    				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
-    				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
-    				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
-    			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.
-
-		\end{WritingMaterials}
-
-		\subsection{Measure of consciousness/information correlate of consciousness}	
-		Based on our core assumption that NTIC is the core informational entity correlating conscious experience, we propose conscious levels and contents can be derived by computing the properties of a NTIC process.
+This means that consciousness is fundamentally associated with a specific kind of information, i.e., the information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}).
+
+        The third assumption is that no consciousness can contain information of the entire universe.
+Together with assumption one and two, this means that the physical representations of the contents of any consciousness must be a coarse-graining of the universe states.
+
+        Our main proposition is that the coarse-grainings that physically represent consciousnesses are those that are NTIC with respect to the universe state.
+More formally this means that every NTIC process $Y_t$ at time $t$ corresponds to a conscious process $C_t=\{C_t^{Content},C_t^{Level}\}$ such that the content $C_{t}^{Content}$ of $C_t$ is just $Y_t$:
+		\begin{equation}\label{eq:cContent}
+			C_{t}^{Content} = Y_{t}.
+		\end{equation}
+
+		\noindent
+We further propose that the level of consciousness $C_{t}^{Level}$ can be measured by the degree of $NTIC_{t}$ of $Y_t$:
+			\begin{equation}\label{eq:cLevel}
+				C_{t}^{Level} = NTIC_{t}.
+			\end{equation}
 		\newline
 
-		\noindent
-		We first hypothesise that, at given time $t$, the level of consciousness $C_{t}^{Level}$ corresponds to the degree of $NTIC_{t}$ at a coarse-grained level.
-			\begin{equation}\label{eq:cLevel}
-				C_{t}^{Level} = NTIC_{t}
-			\end{equation}
-		\newline
-		\noindent
-		We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
-			\begin{equation}\label{eq:cContent}
-				C_{t}^{Content} = Y_{t}
-			\end{equation}
-
-		We discuss the implications of the two hypotheses in the following. 	
-	    \subsection{Level of Consciousness correlates degrees of NTIC of a process}
-
-	    Our theory indicates that conscious levels are determined by two key elements based on the definition of NTIC (Equation \ref{eq:nticObjective}).
-First, to achieve high level of NTIC, one needs to maximise the channel capacity between the current internal state and the future internal state $I(Y_{t+1};Y_{t})$.
-This indicates that the richer self-predictive information the NTIC process contains, the higher the level of consciousness the agent has is.
-Considering two hypothetical systems composed of binary nodes, one has only three nodes and the other has 1 million nodes.
-Even though the first system can reach the maximal channel capacity, the maximal level of NTIC is only 3 bits.
-Compared to the first system, even though the second system does not have full self-predictability about its future state, the level of NTIC of this system can still far higher than the first system.
-This outcome is naturally consistent with a common intuition in which levels of consciousness usually is associated with the level of complexity of a system.\todo{Need to end this part and may need a reference} \toWrite{I want to say something about animal consciousness here}.
+		We discuss the implications of these propositions in the following.
+
+		% ---------------------------------------------------------------------------- %
+        %        Level of Consciousness correlates degrees of NTIC of a process        %
+        % ---------------------------------------------------------------------------- %
+	    \subsection{Level of Consciousness is equal to the degree of NTIC of a proces}
+
+	    Our theory implies that conscious levels are determined by two quantities (Equation \ref{eq:nticObjective}).
+
+	    First, to form high level of NTIC, one needs high self-predictive information $I(Y_{t+1};Y_{t})$ between the current internal state and the future internal state. 
+	    Consider two hypothetical systems composed of binary nodes.
+One has only three nodes and the other has 1 million nodes.
+Then the maximum possible self-predictive information for such systems are 3 bits and 1 million bits.
+So complex systems can potentially reach higher levels of consciousness.
+	    This outcome is naturally consistent with a common intuition in which levels of consciousness usually is associated with the level of complexity of a system.
 
@@
 	    Note that the non-monotonic relationship between levels of NTIC and the scale of coarse-graining suggests that there exists a scale of coarse-graining with the maximal level of NTIC.
-The self-predictive information is the key to achieve a high level of consciousness.
+The self-predictive information is the key to form a high level of consciousness.
 If a system dynamics is highly stochastic and unpredictable, the level of consciousness should be low.
@@
 
-	    Note that, the environment of a NTIC process in the neural system includes not only the\todo{Werite this}
-
-        Finally, which coarse-grained level can achieve high NTIC? 
+	    Note that, the environment of an NTIC process in the neural system includes not only the\todo{rerite this}
+
+        Finally, which coarse-grained level can form high NTIC? 
         agent-scale operation
-        At the physical scale which human being live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
+        At the physical scale which human being interact with, the environmental dynamics is nearly deterministic following the laws of classical physics.
 It gives agents living at this physical scale great advantages if the agents can build NTIC process internally.
@@
 
-        % -------------  Contents Corresponding to Coarse-grained States ------------- %
+        % ---------------------------------------------------------------------------- %
+        %                Contents Corresponding to Coarse-grained States               %
+        % ---------------------------------------------------------------------------- %
 		\subsection{Conscious Contents Corresponding to Coarse-grained States}\needfig{maybe I need a figure here}
@@
 
-        This claim implies that the complexity of conscious contents correlates with the amount of information contained in the NTIC process.
-Therefore, a crucial predict from our theory is that the larger state space of the NTIC process has the richer conscious experience the process can have (e.g., a NTIC process involving a large amount of coarse-grained variables).
+        This claim implies that the complexity of conscious contents is identical to the amount of information contained in the NTIC process.
+Therefore, a crucial predict from our theory is that the larger state space of the NTIC process has the richer conscious experience the process can have (e.g., an NTIC process involving a large amount of coarse variables).
 Crucially, even experience of full darkness contains rich information because it rules out other enormous potential alternative states of conscious contents.
@@
 
-        Follow the example in the last section\todo{Do I have this example?}, a small creature lives in a simple environment with very limited environment dynamics.
+        For example, a small creature lives in a simple environment with very limited environment dynamics.
 It may form a simple NTIC process.
 However, in this situation, the self-predictive information is very low and the state space of the NTIC process is small.
-As a result, the richness of the conscious experience this agent has will be very limited.
+Therefore, the richness of the conscious experience this agent has will be very limited.
 
@@
 
-        \begin{WritingMaterials}
-    		\begin{figure}[H]
-    			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/LimitCycle/PhaseCycle.pdf}
-    			\label{fig:limitCycle}
-    			\caption{Example of coarse-graining by a limit cycle process}
-    		\end{figure}
-
-    		\begin{equation}\label{eq:LimitCycleExample}
-                \begin{array}{l}{\dot{y_1}=y_1-y_2-y_1\left(y_1^{2}+y_2^{2} \right)+\epsilon_{y_1}} \\ {\dot{y_2}=y_1+y_2-y_2\left(y_1^{2}+y_2^{2}\right)+\epsilon_{y_2}}\end{array}
-    		\end{equation}
-
-    		The noise sources, $\epsilon_{y_1}$ and $\epsilon_{y_2}$, are i.i.d with a normal distribution with mean $\mu=0$ a and variance $\sigma^{2}=1$
-
-            @ Our theory naturally explains the com positional nature of consciousness because the joint states of entities in the NTIC process determine the contents of consciousness.
-
-		\end{WritingMaterials}
-
+		% ---------------------------------------------------------------------------- %
+        %             Reconciling the levels and contents of consciousness             %
+        % ---------------------------------------------------------------------------- %
 	    \subsection{Reconciling the levels and contents of consciousness}
@@
 	    Our framework also explains why in normal physiological states the level and the content are positively correlated \citep{laureys2005neural}\needfig{}.
-To achieve high NTIC, a system also needs to have high dimensionality and a large state space which guarantees rich and high dimensional information in conscious contents.
+To form high NTIC, a system also needs to have high dimensionality and a large state space which guarantees rich and high dimensional information in conscious contents.
 Therefore, this framework well integrates the two key but debated concepts in consciousness research.
 
-			\begin{WritingMaterials}
-    			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.
-
-    			@ This also suggests that the richness of the environment being modelled by the	NTIC process has a direct contribution to the level of consciousness.
-
-				@ To have high level non-trivial informational closure, the states of the coarse-grained scale need to
-
-				@ First, maximise the mutual information between environment and the representation.
-				This term implies that the agent need to maximise predictive power of environmental state.
-This also suggest that the environmental complexity is a crucial factor to the level of consciousness.
-The more rich and complex environment the agent try to predict the higher level of consciousness the agent has.
-
-				@ Consciousness and complexity \cite{Tononi1998}
-
-				@ Second, to minimise the mutual information between environment and the representation conditional on the past state of the representation.
-This term suggests that the representation is self-predicable and it mimics the environmental transition.
-
-				@ Therefore, this theory predicts that level of consciousness determined by the environment that the agent adapts to.
-To form a high non-trivial informational closure, the agent will need to live in a complex environment and model the environmental transition precisely.
-
-			\end{WritingMaterials}
-
+        % ---------------------------------------------------------------------------- %
+        %                 sensory hierarchy and neural coarse-graining                 %
+        % ---------------------------------------------------------------------------- %
 		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}
@@
 Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.
-Nevertheless, to exercise causal power in actuators and environments, information needs to be read out from coarse-grained levels.
-\needfig{Maybe need a figure discribing brain to hand}.
-Therefore, the neural system still implement readout decoders for the subsequent signal output.
 In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system.
@@
 		\begin{figure}[H]
-				\includegraphics[width=\textwidth]{WritingMaterials/Fig_SeperationOfCGandCortHierachy/SeperationOfCGandCortHierachy.pdf}
+
+			\includegraphicsTodo[width=\textwidth]{WritingMaterials/Fig_SeperationOfCGandCortHierachy/SeperationOfCGandCortHierachy.pdf}
 			\label{fig:hierarchy}
@@
 
-            \begin{WritingMaterials}
-    			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining
-
-				@ For example, pooling layers in CNN is an implementation of coarse-graining function. It' is very plausible visual processing hierarchy in the neural system realises pooling layers.
-
-				@ It is possible that the neural system represents higher-level information processing by low level physical subtract.
-For example, studies have found representation for summery statistics of signal and neural.
-population.\needref{neural representation for summery statistics}\\
-				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
-            \end{WritingMaterials}
-
+        % ---------------------------------------------------------------------------- %
+        %                              Dynamical Boundary                              %
+        % ---------------------------------------------------------------------------- %
         \subsection{Dynamical Boundary}
         Our theory predicts that the boundary of a conscious system is dynamical.
-The boundary is determined by elements forming high NTIC.
-This implies that when the structure of interaction between elements changes the physical boundaries supporting consciousness should also change.
+The boundary is determined by the NTIC process.
+This implies that when the structure of interaction between variables changes the physical boundaries supporting consciousness should also change.
 If some coarse-grained variables encode environmental information, they may become necessary components to form high NTIC.
@@
 		Our theory argues that, to make information conscious, the following necessay and sufficient conditions need to be satisfied.
-
+		\ideaCallout{Need discussion}
 		\begin{enumerate}
@@
         We especially highlight the second condition because it is critically related to many empirical research results even though it is only a necessary condition.
-As we will describe below, this theory can well explain a varieity of previous empirical findings in consciousness science and further make predictions for future research.
+As we will describe below, this theory can well explain a variety of previous empirical findings in consciousness science and further make predictions for future research.
 In this section, we discuss how the two informational-based conditions link to conscious experience.
@@
 We first consider the scenario that a process fails to satisfy the first condition, i.e.
-the process fails to achieve high degree of NTIC.
+the process fails to form high degree of NTIC.
 In the neural system many processes fall into this category.
@@
 The information flow from the environment to the system is crucial to guide the state transition of procedural memory.
-Therefore, information processing of procedural memory also fails to achieve high NTIC and remain unconscious.
+Therefore, information processing of procedural memory also fails to form high NTIC and remain unconscious.
 
@@
 The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
-        % @ $\pi : S \times A$\\
-        % Policy
     		\begin{equation}
@@
     		Our theory can explain why the patients with visual apperceptive agnosia (e.g., the famous case D.F.\cite{james2003ventral}) can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.
-The online visual information can be used to perform functional actions without forming a NTIC process.
+The online visual information can be used to perform functional actions without forming an NTIC process.
 Our theory also explains why unconscious processes in this category often fail when a long delay periods is introduced in the tasks.
@@
         % ---------------------------------------------------------------------------- %
-
         \subsubsection*{Fail to meet the 2\lowercase{ed} condition}
         As mention above, information is level-dependent and can be virtually independent (closed) across different coarse-graining scales.
-If processes at some levels of a system are able to achieve high NTIC and become conscious, information at other levels still remains unconscious.
-The first implication of this argument is that processes at levels with high stochasticity are unable to achieve high NTIC and, therefore, unconscious.
+If processes at some levels of a system are able to form high NTIC and become conscious, information at other levels still remains unconscious.
+The first implication of this argument is that processes at levels with high stochasticity are unable to form high NTIC and, therefore, unconscious.
 High stochasticity corrupts informational channel capacity and leads to low mutual information between past and future states of a process.
@@
 
-		\begin{WritingMaterials}
-        	@ \idea{Should I write the following points? Is this too much?}
-        	@  === boundary conditions  === 
-        	% multistable perception
-        	    @ In the case of multistable perception, at every moment, only a single macroscopic state is mapped from the microscopic levels, we can only be aware of one interpretation at every moment.
-
-        	% Priming
-        	    @ The same mechanism can also applied to unconscious priming effects.
-\highlight{Making state transitions at microscopic levels does not guarantee transitions at macroscopic levels.}\ideaCallout{this is the key sentence}
-
-        	    @ Of course, this is related to what kind of coarse-grain function which can form a NTIC process at macroscopic scales. We will discuss this issue in the later section.
-
-        	   @ The third category is the boundary conditions.
-
-        	   % Binocular rivalry
-        	   @ In binocular rivalry, either eye provides information to form a NTIC process.
-Once the process is NTIC, the process continue the trajectory in the state space and close system.
-Information from the other eye is unable to enter the process, thus it remains unconscious.
-
-        	   @ Including information from either of objects information can achieve NTIC.
-
-        	   @ For example, when the information of the visual stimuli both can form the NTIC.
-
-        	   @ Our theory also explains why the conscious percepts show some kind of inertia (stably remain conscious for a period of time).
-
-        	   @ Once the NTIC process is formed, the closureness guarantees the stability of the state transitions of the process.
-
-            \end{WritingMaterials}
-
+        % ---------------------------------------------------------------------------- %
+        %                             Conscious Processing                             %
+        % ---------------------------------------------------------------------------- %
 		\subsection{Conscious Processing}
-		When the both conditions are fulfilled, our theory suggests that the states of a NTIC process correspond to particular conscious contents and the information incorporated in the NTIC process is conscious.
-Due to the predictive nature about the environment dynamics of NTIC processes, to achieve high NTIC and to construct functions within the process have a huge evolutionary advantage.
+		When the both conditions are fulfilled, our theory suggests that the states of an NTIC process correspond to particular conscious contents and the information incorporated in the NTIC process is conscious.
+Due to the predictive nature about the environment dynamics of NTIC processes, to form high NTIC and to construct functions within the process have a huge evolutionary advantage.
 It is important to emphasise that our theory does not suggest any functionalism of consciousness.
@@
 
-		First, a NTIC process encodes predictive information about environmental dynamics.
+		First, an NTIC process encodes predictive information about environmental dynamics.
 This is crucial for constructing forward models for predicting future states of the environment.
@@
 
-		Second, a NTIC process can be considered as a close form simulation machine.
+		Second, an NTIC process can be considered as a close form simulation machine.
 With a given initial state, the process can self-evolve and follow a certain trajectory in the state space.
 This trajectory can be seem as a simulation about the environmental transition.
-Therefore, a NTIC process can serve cognitive functions as a perfect simulation engine \citep{BERTSCHINGER.2006}.
-Accordingly, mental simulation, imagination, computing alternative realities, and generating counterfactual outcomes can be implemented with a NTIC process.
+Therefore, an NTIC process can serve cognitive functions as a perfect simulation engine \citep{BERTSCHINGER.2006}.
+Accordingly, mental simulation, imagination, computing alternative realities, and generating counterfactual outcomes can be implemented with an NTIC process.
 \needref{}
@@
 
-	    Fourth, a NTIC process as a closed system can still provide predictive information without new information flowing into the process. This is crucial for many types of off-line processing.
-
-	    Fifth, any state of a NTIC process can be seem as a integration of multiple sources of information.
+	    Fourth, an NTIC process as a closed system can still provide predictive information without new information flowing into the process. This is crucial for many types of off-line processing.
+
+	    Fifth, any state of an NTIC process can be seem as a integration of multiple sources of information.
 For the human scale activities, to know certain transition about the environment, the NTIC process must include a high dimensional information from multiple modalities and have the knowledge about how the high dimensional data interact to each other.
@@
 
-	    In sum, we argue that having a NTIC process is critical for survival in the evolution.
+	    In sum, we argue that having an NTIC process is critical for survival in the evolution.
 It is likely that biological creatures acquired NTIC process at some stages in the evolution.
@@
 
-		\begin{WritingMaterials}
-		    @ Previous research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.
-
-    		    @@ Planning, achieving long term goals
-
-    		        @@@ simulate alternative realities 
-    		        @@@ multiple alternative possibilities
-    		        @@@ imagination
-    		        @@@ information for off-line processing
-
-    		    @@ Cognitive control, response inhibition, flexible routing of information, overriding automatic responses
-
-    		        @@@ flexibility and the strategic use of that information for complex operations and decision-making 
-    		        @@@ flexible and adjust our behavior to different contexts and goals
-
-    		    @@ integration,
-
-    		    @@ integrates behaviour across time
-
-    		        @@@ tasks for long duration
-
-    		    @@ stabilisation
-
-    		    @@ conscious thought, reflection, reasoning, and temporally extended sense of self.
-
-    		    @@ complex visuomotor abilities
-
-    		    @@ intending deciding
-
-    		    @@ dreaming
-
-    		    @@ reasoning interpreting
-
-    		    @@ self
-
-    		        @@@ reflecting
-    		        @@@ self-monitoring 
-            @ As mentioned in \ref{sec:Non-trivial informational closure}, achieving NTIC has a large evolutionary advantage.
-
-                @@ Because NTIC processes encode information about environmental transition, it becomes a perfect computational core for constructing forward models for the environment, simulating the dynamics of self-environment interaction, and generating predictions.
-
-            @ Therefore, if an agent equips a NTIC process, the process can be used to integrate information from different sources.
-
-            @ =============================================================================
-
-	        @ importantly, evidence suggests that those functions in some conditions do not require the involvement of consciousness.
-This evidences an important fact that consciousness is not necessay to these functions.
-
-	        @@ Predictive information about the environment.
-
-	        @@ Stability
-
-	        @@ simulation environmental dynamics
-
-	        @ Replaying past events
-
-	        @ \rewrite{However, recent evidence also points out interesting dissociations between conscious and unconscious information processing when it comes to the duration, flexibility and the strategic use of that information for complex operations and decision-making} \cite{van2012role}
-
-	    \end{WritingMaterials}
-
 % ============================================================================ %
@@
 % ============================================================================ %
-	\section{Comparison with other theories}
-	In this section, we compare our theory with other popular modern theories of consciousness. 1
-
+	\section{Comparison with other theories}\label{sec:Comparison with other theories}
+	In this section, we compare our theory with other popular modern theories of consciousness.
+
+        % ---------------------------------------------------------------------------- %
+        %        Theories about multilevel views on consciousness and cognition        %
+        % ---------------------------------------------------------------------------- %
 		\subsection{Theories about multilevel views on consciousness and cognition}
@@
 
-		        \begin{WritingMaterials}
-				%% Back up materials
-
-				@ Prinz suggested that \rewrite{as.
-Cells in V1 are not promising candidates, because they do not reliably respond in ways that are consistent with features that we experience consciously.
-} \cite{prinz2007intermediate}
-
-				@ \rewrite{
-					The intermediate level theory originally proposed by Ray Jackendoff and further defended and specified by Jesse Prinz proposes that within the hierarchy of representations that are used to describe the cognitive system, conscious experience occurs only for specific levels of representation.
-The theory is rooted in Jackendoff ’s analysis of different cognitive systems such as vision, language, and music and the subsequent observation that consciousness does not arise anywhere within these systems.
-According to Jackendoff, consciousness is not associated with low-level, nor with high-level representations, but rather with those implying intermediate levels of processing.
-For instance, in the domain of object recognition, it is assumed that the visual system comprises a low level with local computations of visual features, an intermediate level reflecting binding and object recognition, and a higher level computing viewpoint invariance and representing abstract categories.
-According to Jackendoff and Prinz, conscious experience is not comprised of a disunified picture of visual features, nor is it represented by viewinvariant categories.
-Rather it is composed of bound and specific instances of objects that are assumed to be computed at the intermediate level of representation.
-In an analogous manner, speech perception can be decomposed into three levels: an acoustic representation of speech sounds at the lower level, a high level involving abstract lexical and syntactic categories, and in between a word recognition level relying on phonological representations.
-This theory explains why the conscious experience associated with speech perception mostly involves phonological representations, rather than other levels of representations.
-In Jackendoff and Prinz’ theory,the privileged role of the intermediate level of processing is based on the need for real-time computational efficiency.
-Indeed, this level of representation is assumed to be the most relevant one regarding ecological and functional needs.
-Another important aspect of this theory concerns the central role of attention during conscious experience.
-Here, attention is defined as a selection process that acts as a gate to working memory mechanisms.
-It performs the function of selecting the relevant information that is amplified afterward and then becomes conscious.
-Indeed, Prinz acknowledges that activation of an intermediatelevel representation on its own cannot be a sufficient condition for consciousness, given that those representations can be activated during subliminal perception.
-However, this theory makes the crucial postulate that the amplification of intermediatelevel representations by attention is a necessary and sufficient condition for consciousness.
-In sum, for each domain of processing, the content of consciousness at a particular moment is supported by a representational structure of intermediate level for that domain, which is selected to enter short-term memory, and enriched by attentional processing.} \cite{banks2009encyclopedia}
-
-				@ \rewrite{
-					In 1987, Ray Jackendoff published Consciousness and the Computational Mind.
-In it, he posed an important Where question: Where, in the fl ow of information, does consciousness arise?
-Most cognitive scientists agree that the mind is, in some sense, a computer.
-It is a device that processes information by transforming representations in accordance with rules.
-Computational devices decompose into various interconnected subsystems, each of which performs some aspect of a complex task.
-Given such a decompositional analysis, we can ask: in which subsystems does consciousness arise?
-If we depict the mind as a vast fl ow chart, and highlight the boxes whose rules and representations are conscious, which boxes should we mark?
-Jackendoff ’s answer is simple and elegant.
-He noticed that many of our mental capacities, including our senses and our language systems, are organized hierarchically.
-In each of these hierarchies, it makes sense to talk about low- , intermediate- , and high- level processing systems.
-We break down tasks into stages.
-Appealing to prevailing models of these stages, Jackendoff observed that the intermediate level seems to be privileged with respect to consciousness.
-Consciousness seems to arise in intermediate- level processing systems and not elsewhere.} \cite{prinz2007intermediate}
-
-				@ \cite{jackendoff1987consciousness}
-				@ \cite{prinz2007intermediate}
-				@ 2.5D
-
-				@ about why it is this level
-				@@ \rewrite{
-					Under the computational interpretation, the “why” question means: In what sense are intermediate level representations computationally important or distinctive?
-Th is is a tractable question, and it may lead to insights into the function of consciousness.
-Representations at the intermediate level are ideally suited for real- time deliberative behavioral responses.
-Low- level representations fail to bind features into coherent wholes.
-If we are going to interact with our environment, the low level is not a good guide.
-Th e high level is a good deal better for action, but also suboptimal.
-Th e high level tells us the category of the stimuli we perceive, but from an allocentric point of view.
-It abstracts away from stimulus features that are crucial for action.
-If we encounter a predator, the high- level visual representation does not tell us if it is facing toward us or away from us.
-Without that knowledge, we cannot decide what course of action to take.
-So, I propose that the intermediate level plays a distinctive role in information processing.
-It delivers representations that are coherent but viewpoint specifi c.
-Th ese representations are useful for determining what to do here and now.arg1} \cite{prinz2007intermediate}
-				@@ \rewrite{
-					I conclude that the intermediate level plays a distinctive and important computational role.
-Some researchers find this puzzling.
-In wondering why the intermediate level is privileged, they note the arbitrariness of the fact that perceptual hierarchies have three levels.
-Could they not have two?
-Or a hundred?
-Do the 50 or so areas that contribute to visual processing really divide neatly into three levels?
-I think these puzzles depend on a particular understanding of what the word “intermediate” amounts to.
-One might get caught up in the fact that the intermediate level is the second stage in a sequence.
-Call this the “serial understanding of the intermediate level.” Alternatively, one might think of the intermediate level semantically.
-On this reading, the intermediate level is one that is not abstract and categorical, but not piecemeal or disunifi ed.
-Th ese notions are all in need of some refi nement, but, as a fi rst approximation, the idea is that intermediate- level representations are neither too specifi c nor too general.}\cite{prinz2007intermediate}
-			\end{WritingMaterials}
-
+        % ---------------------------------------------------------------------------- %
+        %                             First-order theories                             %
+        % ---------------------------------------------------------------------------- %
 		\subsection{First-order theories}
@@
 
-			\begin{WritingMaterials}
-				@ \rewrite{
-					The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
-Thus the crucial difference between the first-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity.
-Therefore, in the group of first-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the first-order representations, as well as scientists who hold that visual awareness depends on activity in content-specific regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26].
-Most first-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g.
-subcortical) sensory pathways.
-Thus this view suggests that conscious and unconscious processing will have different functional consequences.
-Whereas some first-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most first-order theorists take a difference in perceptual task performance (e.g.
-‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33].
-In other words, they typically associate task performance with awareness..} \cite{lau2011empirical}
-
-				@ Among those are first-order theories, on which a mental state is conscious if being in that state results in one's being conscious of something;
-
-				@  According to first-order views, phenomenal consciousness consists in analog or fine-grained contents that are available to the first-order processes that guide thought and action.
-So a phenomenally-conscious percept of red, for example, consists in a state with the analog content red which is tokened in such a way as to feed into thoughts about red, or into actions that are in one way or another guided by redness.
-
-				@ However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents.
-\todo{Need more here, espectially more counterintuitive predictions}
-
-			\end{WritingMaterials}
-
+        % ---------------------------------------------------------------------------- %
+        %                 Higher Order Thought theory of consciousness                 %
+        % ---------------------------------------------------------------------------- %
 		\subsection{Higher Order Thought theory of consciousness}
@@
 For example, mental planning needs a precise forward model to infer the environmental dynamics.
-
-			\begin{WritingMaterials}
-			@ Good reference: \myQuote{Higher- Order Th eories of Consciousness; PETER CARRUTHERS (The Blackwell Companion to Consciousness (Blackwell, 2007))}
-
-		    @ In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.
-
-		    @ Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.
-
-		    @ It is true that the neural system does create  meta-representation to represent xxx.\needref{Maybe come studies about confidence represenatation}
-
-		    @ The higher-order representation may resemble coarse-grained variables.
-
-		    @ This may cause misidentify the entity which correlates conscious experience.
-
-		    @ ----------------------------------------------------------------------------
-
-			@ Information closure directly is critical for other systems to construct forward models.
-
-			@ Therefore, most of the high level cognition can utilise the state of informational closure.
-
-			@ For example, mental planning needs a precise forward model to infer the environmental dynamics.
-
-			@ \idea{This is way HOT always involve consciousness }
-
-			@ \cite{rosenthal2005consciousness}
-
-            @ ============================================================================
-
-			@ \rewrite{
-				According to this view, humans not only have first-order non-conceptual and/or analog perceptions of states of their environments and bodies, they also have second-order non-conceptual and/or analog perceptions of their first-order states of perception.
-And the most popular version of higher-order perception theory holds, in addition, that humans (and perhaps other animals) not only have sense-organs that scan the environment/body to produce fine-grained representations that can then serve to ground thoughts and action-planning, but they also have inner senses, charged with scanning the outputs of the first-order senses (i.e.
-perceptual experiences) to produce equally fine-grained, but higher-order, representations of those outputs (i.e.
-to produce higher-order experiences).
-A version of this view was first proposed by the British Empiricist philosopher John Locke (1690).
-In our own time it has been defended especially by Armstrong (1968, 1984) and by Lycan (1996).} \url{https://plato.stanford.edu/entries/consciousness-higher/#SelRepHigOrdThe}
-
-			@ \rewrite{
-				neutral about whether conscious awareness adds significant utility or immediate impact on behavior and task performance [1,27].
-This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on first-order rather than higher-order representations.
-Because conscious awareness can differ even if all first-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
-				\ideaCallout{
-					My theory would have similar prediction.
-Because conscious contents are coarse-grained results from low-level information.
-It is possible that more than two low-level neural states all coarse-grained to a high-level state.
-}
-
-			@ \rewrite{
-					Metacognition: cognition that is about another cognitive process as opposed to about objects in the world.
-In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efficacy of a perceptual process.
-The capacity of sensory metacognition is sometimes empirically assessed by the correspondence between subjective report and task performance: how closely are they associated with each other on a trial-by-trial basis}\cite{lau2011empirical}
-
-			\end{WritingMaterials}
 
@@
 
-		\begin{WritingMaterials}
-
-			@ Broadcasting: When new sensory information from a modality is involved in NTIC, the information can be preserved in the following dynamic of NTIC.
-The neural system can extract the information for specific task goals.
-This is equivalent to the function of broadcasting.
-
-			@ the presence of contexts as stable coalitions shaping access to the workspace.
-
-			@ e ‘all-or-none’ behaviour, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and amplified non-linearly into a full-blown state of high-level activity.
-This global ‘ignition’ has been proposed as a marker of conscious perception [70].
-Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear amplification of activation which invades a distributed set of parietal, prefrontal and cingulate areas
-
-			@ Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing?
-Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness.
-A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly defined brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
-Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be fiexibly deployed.
-
-			@ C1: Global availability of relevant information The need for integration and coordination \cite{Dehaene2017}
-
-			@ Evidence for integration and broadcasting
-
-			@ Stability as a feature of consciousness \rewrite{“ meta-stability ” seems to be necessary for the nervous system to integrate information from a variety of modules and then broadcast it back to them, achieving flexible cross-module routing.}
-
-			@ \rewrite{integration of computational resources in a large-scale coordination and for the exchange of information among processors}
-
-			@ \rewrite{Grounded on the distinction between conscious and unconscious processes, Bernard Baars’ global workspace theory is one of the most influential cognitive theories of consciousness.
-This theory relies on the metaphor of a theater.
-In this theater, unconscious specialized processors (equivalent to modules) are assumed to be the actors and the audience.
-While the audience represents the set of passive processors, actors represents active processors playing on the stage of the theater (i.e., the workspace).
-These actors are engaged in a competition for being seen by the audience: by broadcasting their information they actually compete for more broadcasting.
-Active processors with the highest coherent activity can form local coalitions that strengthen them in this competition process.
-The strongest coalition in this competition dominates the workspace, in a winner-take-all fashion, and corresponds to the content of consciousness.
-The workspace is equated by Baars to working-memory, in which only the most active content becomes conscious.
-Additionally, the dominant coalition benefits from global broadcasting, which allows it to recruit new processors from the audience in order to form a global coalition.
-Here, consciousness allows for the integration of computational resources in a large-scale coordination and for the exchange of information among processors that would otherwise remain separated.
-In this theory, each processor can operate in the conscious mode if it benefits from global broadcasting through the workspace, or it can operate in the unconscious mode when disconnected from the workspace.
-An important feature of the global workspace theory is the presence of contexts as stable coalitions shaping access to qeqthe workspace.
-Contexts are constituted of unconscious processors reflecting, in a hierarchical manner, our expectations, our beliefs, our goals, and ultimately our self.
-In particular, attention is implemented as a goal context in this theory.
-It is described as a mechanism that controls access to the workspace, acting as a filter and biasing the competition process toward a particular set of actors.
-At any given moment, the dominant coalition is under the spotlight of attention, and its informational content becomes the content of conscious experience.
-A crucial aspect of Baars’ theory is that it avoids the problem of the homunculus by reducing it to an audience of multiple unconscious processors.
-Here, there is no need for a hypothetical single conscious observer in the system, and thus there is no issue of infinite regression with a homunculus inside another homunculus.
-Instead, consciousness is considered to reflect the global broadcasting of information to an audience of unconscious processors.
-As the audience is unconscious, unsupervised, and receptive rather than attending to the information, it does not constitute an internal homunculus.}
-
-		\end{WritingMaterials}
-
         % ---------------------------------------------------------------------------- %
@@
 
-	    Our theory in general rejects this proposal based on the fundamental assumptions of SMC.As we mentioned in \ref{sec:Conscious versus Unconscious Processing}, a process directly maps the sensory state space to the action space should not be able to achieve NTIC.
+	    Our theory in general rejects this proposal based on the fundamental assumptions of SMC.As we mentioned in \ref{sec:Conscious versus Unconscious Processing}, a process directly maps the sensory state space to the action space should not be able to form NTIC.
 Because learning of contingencies between sensory input and action output doesn't guarantee to form any NTIC process, our theory predicts that sensorimotor contingency is neither a necessary nor a sufficient condition for conscious experience.
@@
 	    Nevertheless, our theory does appreciate the notion that interactions between agents and environment is crucial to shape specific types of conscious experience.
-This is because, for an agent to form a NTIC process with action output, the process needs to encode how agents' actions influence state transitions in the environment.
+This is because, for an agent to form an NTIC process with action output, the process needs to encode how agents' actions influence state transitions in the environment.
 Therefore, information of interaction should be encoded in the NTIC process and also determines the state of NTIC which associates a particular conscious content.
@@
 \todo{Need a better ending}
-
-		\begin{WritingMaterials}
-
-			%% Intro about this theory
-			@ O’Regan and Noë
-
-			@ \rewrite{According to Noë, perceptual presence is explained by a “ sensorimotor theory ” on which perception depends on a practical mastery of sensorimotor dependencies or “ sensorimotor contingencies ” (SMCs) (O ’ Regan \& Noë, 2001).
-The theory inherits from Gibsonian notions of “ affordances ” (Gibson, 1979) and from enactive cognitive science (Thompson \& Varela, 2001) which stress the importance of brain-body-world interactions in cognitive processes.
-On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations.
-A strong point of this theory is that it suggests why there are differences in qualitative character between modalities, the reason being that different modalities instantiate different SMCs (O ’ Regan \& Noë, 2001).
-}
-
-			@ In their seminal article O’Regan and Noë (2001) introduce sensorimotor contingencies (SMCs) as the basis of a sensorimotor account of conscious perception.
-
-			@ In short, different types of SMCs give rise to different qualities of sensory experience
-
-			@  Second, vision, audition, touch, etc., correspond to domains of knowledge of the respective SMCs that are exercised by an agent as part of its habitual behavior.This ‘‘mastery of SMCs’’ is what lets an agent perceive its environment and adapt its behavior accordingly
-
-			@ And third, sensory awareness arises when SMCs are integrated with planning, reasoning, and generation of behavior
-
-			@ The theory is a radical departure from the classical view that the brain constructs an internal representation of the outside world on which higher cognitive processes such as memorizing, reasoning, and planning operat
-
-			@ perception depends on a practical mastery of sensorimotor dependencies or “sensorimotor contingencies” (SMCs)
-
-			@ s the importance of brain-body-world interactions in cognitive processes.
-On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations.
-
-			@ ways of acting or as something we do, rather than an internal phenomenal experience or an internal representation of the world (O’Regan \& Noë, 2001)
-
-			@ \rewrite{I advance this truly astonishing hypothesis: To understand consciousness in humans and animals, we must look not inward, into the recesses of our insides; rather, we need to look to the ways in which each of us, as a whole animal, carries on the processes of living in and with and in response to the world around us .
-.
-.
-You are not your brain .
-.
-.
-Meaningful thought arises only for the whole animal dynamically engaged with its environment .
-.
-.
-And indeed the same is true for the quality of our conscious episodes .
-.
-.
-The taste of licorice is not something that happens in our brains.} (Noë, 2009, pp.
-7–8)
-
-			@ Because consciousness resides in our behavioural interactions with the world rather than in our brain, the theory postulates that consciousness does not derive from brain activity at all.
-Consequently, there is no need to explain how brain activity causes or constitutes consciousness, because it does not.
-
-			@ O ’ Regan, J.K. and Noë, A. (2001) A sensorimotor account of vision and visual consciousness. Behav. Brain Sci. 24, 939 – 973
-
-			@ SMC theory argues that consciousness arises from the execution of SMCs, resulting in brain – environmental interactions.
-
-			@ The second variant of SMC theory postulates that ‘ it is not movement as such, but the consequences of potential movement that play a role ’ (in perceptual experience) ([5], p.
-1015; see also [9,10,19,20]).
-This ‘ non-acute ’ or dispositional variant marks a signi fi cant shift in position because it de-emphasizes actual movement.
-\cite{pennartz2017consciousness}
-
-			@ It stipulates that for us to be conscious of something in the environment (or of our way of interacting with the environment)
-
-		\end{WritingMaterials}
 
@@
 However, the states of the internal variables are fully determined by the external input, implying that this algorithm is not informationally closed.
-We suggests that if a predictive process is not a NTIC process, predictions from this process will not be able to show in conscious contents (i.e., fail to meet the 1\lowercase{st} condition in section \ref{sec:Conscious versus Unconscious Processing}).
-In contrast, predictive information in the NTIC process is conscious and makes the process achieve information closure.
+We suggests that if a predictive process is not an NTIC process, predictions from this process will not be able to show in conscious contents (i.e., fail to meet the 1\lowercase{st} condition in section \ref{sec:Conscious versus Unconscious Processing}).
+In contrast, predictive information in the NTIC process is conscious and makes the process form information closure.
 
@@
 
-        \begin{WritingMaterials}
-    		@ We first hypothesize that predictive processing stays unconscious is because it is not able to achieve NTIC.
-
-    			@@ \idea{Example from PID controller?}
-
-    		@ Second, according to our theory, it is obvious that the computation of predictive processing is unconscious and only the result is conscious.
-Because the computational details is not at the coarse-grained level which achieves NTIC.
-
-    			@@ So far, many neuronal models and coding schema have been proposed to explain how to implement Bayesian inference and prediction at the neuronal level.
-
-    			@@ However?
-
-    		@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.
-
-    		%% About the unconscious Bayesian processing
-    		@ \cite{lamme2015predictive}
-    			@@ To my knowledge, this is the first time this has been so explicitly laid out—writers on predictive coding thus far have always stayed a little vague on where exactly consciousness sits in the Bayesian framework.
-
-    			@@ Yet the two points seem contradictory. In the Bayesian predictive coding framework, consciousness is the result of the unconscious inferential processes.
-
-    			@@ However, these authors have so far been very reticent about how exactly consciousness fits into the PC framework.
-For now, there is an emerging idea that understands consciousness as the final result of unconsciousness processing.
-According to Hohwy (2013), perceptual consciousness fits in the PC theory as the ‘upshot’ or ‘conclusion’ of unconscious perceptual inferences.
-Melloni (2014) also expects that inferential processes are conducted behind the curtain of consciousness and what we experience are the ‘outcomes’ or ‘results’ of an unconsciou inferential process.
-Lamme (2015) agrees with the idea that consciousness is based on the relation or more precisely conjunction of current inputs and priors, which together produce posterior beliefs.
-Karl Friston agrees to a certain extent with this interpretation of consciousness.
-According to Hobson and Friston (2016), consciousness is not a phenomenon but a process, a process of optimizing beliefs through inference (consciousness, dreams, and inference; the Cartesian theater revisited; a response to our theater critics).
-
-    		@ Link PP and c
-    			@@ \cite{hobson2016response}
-    			@@ \cite{Melloni2015}
-
-    		%% ----------------------------------------------------------------------------
-    		@ \cite{SethPP2014}
-
-    		@ When uncertainty is high, we should expect an increase in the ability of ever higher-level prior beliefs to determine conscious experience. I
-
-    		@ determine conscious experience.
-
-    		@ PP combines and builds upon previous ideas about the role of “unconscious inference” in perception (Helmholtz, 1925; Barlow, 1961; Gregory, 1970), the process of “analysis by synthesis” in psychology (Neisser, 1967), the “predictive coding” approach in neuroscience (Srinivasan et al., 1982; Rao and Ballard, 1999; Huang and Rao, 2011) and “generative models” and related probabilistic computational principles (MacKay, 1956; Mumford, 1992; Dayan et al., 1995; Hinton, 2007a,b; Tenenbaum et al., 2011).
-
-    		@ \rewrite{The brain is constantly confronted with a wealth of sensory information that must be processed efficiently to facilitate appropriate reactions.
-One way of optimizing this processing effort is to predict incoming sensory information based on previous experience so that expected information is processed efficiently and resources can be allocated to novel or surprising information.
-Theoretical and computational studies led to the formulation of the predictive coding framework (Friston 2005, Hawkins and Blakeslee 2004, Mumford 1992, Rao and Ballard 1999).
-Predictive coding states that the brain continually generates models of the world based on context and information from memory to predict sensory input.
-In terms of brain processing, a predictive model is created in higher cortical areas and communicated through feedback connections to lower sensory areas.
-In contrast, feedforward connections process and project an error signal, i.e.
-the mismatch between the predicted information and the actual sensory input (Rao \& Ballard, 1999).
-The predictive model is constantly updated according to this error signal.
-}
-
-    		@ \rewrite{Predictive inference and perception The concept of PC overturns classical notions of perception as a largely ‘bottom-up’ process of evidence accumulation or feature detection, proposing instead that perceptual content is specified by top-down predictive signals that emerge from hierarchically organized generative models of the causes of sensory signals.
-According to PC, the brain is continuously attempting to minimize the discrepancy or ‘prediction error’ between its inputs and its emerging models of the causes of these inputs via neural computations approximating Bayesian inference (Figure 1 and Box 1).
-Importantly, prediction errors can be minimized either by updating generative models (perceptual inference and learning; changing the model to fit the world) or by performing actions to bring about sensory states in line with predictions (active inference; changing the world to fit the model).}
-
-    		@ \rewrite{In terms of brain function, Hermann von Helmholtz’s 19th Century notion of perception as unconscious inference has found new momentum in modern formulations of ‘predictive processing’, the Bayesian brain, and the ‘free energy principle’ (Clark, 2013; Friston, 2010; Hohwy, 2013).
-On these formulations, which can all be subsumed under the general term ‘prediction error minimization’ (PEM, (Hohwy, 2013)) perceptual content is the result of probabilistic inference on the hidden causes of sensory signals.
-}
-
-    		@ \rewrite{Generative models encoded by brain structure and dynamics make predictions about sensory inputs, based on prior expectations.
-Action (e.g., body movements) and perception conspire to reduce sensory prediction errors, giving rise to perceptual content and}
-
-    		@ \rewrite{More informally, what we perceive is the brain’s ‘best guess’ of what’s out there (or ‘in here’, for perceptions of body and self).}
-
-    		@ \rewrite{“ predictive processing ” (PP) 1 or the “ Bayesian brain ” this holds that perceptual content is determined by hierarchically organized generative (i.e., predictive) models (HGMs) of the external causes of sensory signals, induced by a process approximating Bayesian inference (Friston, 2009).}
-
-    		@ Therefore, it's reasonably assume that if evolution wants to build predictive mechanisms, the mechanisms should be settled on the information at the \ac{cged} level.
-
-    		@ More specifically, a forward model, which received state and action as input and compute transition and then output next states, should be build on the representation that forms the \acl{ic}.
-
-    		@ Therefore, the state of predictive model can be conscious while it is linked to \acl{ic} representation.
-
-    		@ Note that, a system showing some predictive power is not sufficient to be conscious.
-
-    		@ For example, the proportional–integral–derivative controller (PID) controller shows predictive behaviours due to its derivative which computes and predict error value in the future.
-Derivative action predicts system behaviour and thus improves settling time and stability of the system.
-
-    		@ However, the state of the whole PID system still be determined by the inputs, i.e. the states of the controlled process, thus cannot complete \acl{ic}.
-
-    		.
-It can compute position, velocity, and acceleration of objects, and output control signals (action).
-However, the state of the PID controller is not information-closed.
-The state still fully determined by the input signals.
-Therefore, it fails to reach \ac{ic}.
-Hence, according to our theory, the PID system is not conscious.
-
-    		@ Similarly, the neural system also has many circuits that show predictive power but do not have \ac{ic}.
-    		@ considers the brain as a predictive machine
-    		@ According to predictive processing account, conscious contents are the inference results (posterior from Bayesian inference framework) of predictive mechanism.
-
-    		@ However, we can see that not all predictive mechanisms in the neural system can be consciously aware of.
-
-    		@ So what's the critical difference between them in terms of consciousness?
-
-    		@ We argue that when predictive mechanisms utilise the information in the informational closure, the predictive result is conscious.
-
-    		@ Because the forward model build on the informational closure representation can be seen as part of the closure. \critical{IS THIS TRUE? NEED DISCUSSION}
-
-    		@ we can consider two scenarios
-
-    			@@ Predictive information is encoded in neuron populations but there is high entropy of conditional probability which means it's not closure.
-Therefore, the conscious level could be very low even though the it still has some degree of predictability.
-
-    			@@ Another scenario is a forward model but its state fully depends on external sensory input. This system is not informational closed and therefore is not conscious.
-
-    			@@ Based on this point of view, predictive power for a system does not guarantee consciousness.
-
-    			@@ For example, in active inference \needref{active inference}, action is guided by prediction error so the state of the system is non-coloured
-	\end{WritingMaterials}
-
         % ---------------------------------------------------------------------------- %
@@
         % ---------------------------------------------------------------------------- %
-
 		\subsection{Integrated information theory}
@@
 In the current stage of our theory development, we have not proposed such sophisticated description of the mappting between informational structure and the qualia space.
-However, in line with this notion, we argue that the state space of a NTIC process determines the subjective experience possessed by the process.
+However, in line with this notion, we argue that the state space of an NTIC process determines the subjective experience possessed by the process.
 
@@
 
-		% -------------------------------- Difference -------------------------------- %
-		% Different prediction
 		Even though both theories are based on informational properties of a process, predictions of the two theories can be very different.
@@
 The causal power can emerge at macroscopic levels of a system.
-This claim is consistent with our prediction in which processes at macroscopic levels can achieve more deterministic and predictive state transitions.
+This claim is consistent with our prediction in which processes at macroscopic levels can form more deterministic and predictive state transitions.
 We expect further mathematical and empirical analysis can reveal the relationship between \ac{OurTheory} and Hoel's analyses about the causal power at different scales in a system.
-
-		\begin{WritingMaterials}
-
-			@ One common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness. \needref{cite David Chalmers}
-
-			@ Our theory is different from IIT which proposes that consciousness is information integration in a system.
-
-			@ For level of consciousness, IIT predicts a system with higher level of integration produces a higher level of consciousness.
-In our theory, the level of consciousness corresponds to the level of NTIC, which suggests that level of consciousness is determined by self-predictive information and the information about the environment encoded in the process.
-
-			@ In terms of conscious content, IIT suggests that the causal structure of a system determines the quality of conscious contents.
-In the current version of our theory, how the state of NTIC process maps to conscious content has not been sophisticatedly specified.
-More work is needed to understand the relationship between the state of NTIC process and conscious contents.
-
-		    @ --------------------------------------------------------------------
-			@ \toWrite{Information integration without awareness}\cite{Mudrik_Faivre_Koch}
-			@ \rewrite{consciousness is necessary for high-level but not low-level semantic integration}\cite{Mudrik_Faivre_Koch} we would argue an inverse relationship:"High-level information processing is necessary for consciousness." This is because higher-level information processing is more likely to create an informational closure representation.
-
-			@ Similarly, it is not \rewrite{consciousness is necessary for multisensory integration}.
-It should be multisensory integration is more likely to create an informational closure representation.
-Because in most situations, multisensory signals are generated from hidden causes which may have deterministic dynamic and relation with each other.
-Therefore, to infer the hidden causes and represent the deterministic relations can form informational closure representation which is conscious.
-
-		    @ Our theory is closely related to causal emergence described by Hoel et al.
-(2013) which was examined by a following work using integrated information theory (Hoel et al.
-2016).
-More research on the precise mathematical relationship between causal emergence and our theory is needed
-
-			@ \cite{hoel2016can}
-			@ causal emergence
-			@ \cite{hoel2013quantifying} examined causal power at different coarse-grained scale and show that causal power can be stronger at macro rather than micro levels.
-
-			@ To answer the question about what is the best scale to compute Phi, \cite{hoel2016can} examined causal power at different coarse-grained scale.
-
-			@ Further examination of the Hoel's theory and our theory is needed to elucidate the relationship between our theory and causal emergence.
-
-			@ Both theory
-
-			\end{WritingMaterials}
 
@@
 % ============================================================================ %
-    \section{Limitation and Future work}
+    \section{Limitation and Future work}\label{sec:Limitation and Future work}
         % Can't solve the hard problem
@@
 Two NTIC creatures (Alice "$A$" and Bob "$B$") living in a simple environment($E$) which has only two states $E_1$ and $E_2$.
-In this simple case, Alice and Bob should have only two states ($A_1, A_2$ and $B_1, B_2$) when they achieve the maximal level of NTIC (i.e.
+In this simple case, Alice and Bob should have only two states ($A_1, A_2$ and $B_1, B_2$) when they form the maximal level of NTIC (i.e.
 1 bit).
@@
 
-        % Finding potential coarse-graining functions
+        % boundary problem
+        In this paper, we claim that macroscopic level which forms NTIC from the system's environment is conscious. Anf
+
+        % Finding potential coarse-graining functions / coarse-grained computational units
         \needhelp{I think I need Martin's help here, I don't know how much we should say about this in this paper. Or just leave this to the future studies}
-        A major empirical difficulty of our theory is to find appropriate aggregation functions which map microscopic variables to macroscopic variables forming a NTIC process.
+        A major empirical difficulty of our theory is to find appropriate aggregation functions which map microscopic variables to macroscopic variables forming an NTIC process.
 In this paper, we do not speculate any form of aggregation functions.
@@
 
-        \begin{WritingMaterials}
-            % finding a suitable CG function
-			@ \rewrite{
-				not all causal relationships (or relationships of nomological dependency) among micro-events aggregate up to causal relationships among coarse-grained macro-events that are constituted by those micro-events.
-Instead, whether one gets causation at the macroscopic level will depend (among other things) on the particular coarse-graining that is chosen.} \cite{price2007causation}
-
-			@ \rewrite{
-				It may seem surprising, even counterintuitive, that causal and statistical dependence relationships involving fine grained microscopic variables do not automatically show up in causal and dependence relationships among the macroscopic variables that are realized by the fine grained variables.} \cite{price2007causation}
-
-			@ \cite{jonas2017could} well demonstrated that it is difficult to understand higher-level information processing by the current neuroscience methods.
-
-			@ Physiological location of NTIC
-
-			@ Practical measure of NTIC.
-
-		\end{WritingMaterials}
-
 % ============================================================================ %
@@
 	We introduce a new computational theory of consciousness based on two core assertions.
-First, consciousness occurs when a process achieves NTIC.
-Second, in the neural system, coarse-graining is necessary to construct a NTIC process at macroscopic scales.
-Therefore, consciousness only appears at a certain macroscopic level which achieve a high degree of NTIC.
+First, consciousness occurs when a process forms NTIC.
+Second, in the neural system, coarse-graining is necessary to construct an NTIC process at macroscopic scales.
+Therefore, consciousness only appears at a certain macroscopic level which forms a high degree of NTIC.
 
@@
 
-\newpage
-\begin{backup}
-\part*{Backup}
-\addcontentsline{toc}{part}{Backup}
-\setcounter{section}{0}
-	\section*{Biological evidence of informational closure in neural system}
-		\begin{ants}
-			% ============================================================================ %
-			%                             sederberg2018learning                            %
-			% ============================================================================ %
-
-			@ So far, not so much research on non-trivial informational closure in biological neural systems.
-
-			@ However, \rewording{XXX}
-
-			% Internal self-predictive mechanism
-			@ Recent biological evidence suggests that low-level neurons encodes predictive information about external  and
-
-			@ \toWrite{
-				need to say this is exactly the non-trivial informational closure, and refer to equation XXX}
-
-			@ \cite{sederberg2018learning}
-			@ \rewrite{
-				in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }
-
-			@ \rewrite{
-				We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}
-
-			@ \rewrite{
-				We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }
-
-			@ \rewrite{
-				Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal.
-This suggests that bottom-up prediction may play an important role in sensory processing}
-
-			@ \rewrite{
-				Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}
-
-			@ \rewrite{
-				Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}
-
-			@ They also showed generalization of internal predictability across stimulus. This suggests .... what?
-
-			@ \rewrite{
-				The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}
-
-			@ \cite{Palmer2015}
-			@ \rewrite{
-				Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}
-
-			@ \rewrite{
-				It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig.
-3, but the brain has no direct access to visual stimuli except that provided by the retina.
-Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs?
-More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + delta t in the future?
-The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +delta t j w t Þ } \url{http://tinyurl.com/y9zmhlln}
-
-			@ \rewrite{
-				larger groups of cells carry predictive information for hundreds of milliseconds, }
-
-		\end{ants}
-
-	\section*{Relation to empirical findings in neuroscience and studies of consciousness}
-
-		\subsection{Unconscious Processing}
-		\begin{ants}
-			@ According the theory, there are two factor that renders neural processes unconscious.
-
-			@ First, processes are reflexive. This causes non-closured
-
-			@ Second, the abstraction level of the information is below the non-trivial informational closure scale.
-		\end{ants}
-
-		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
-		\subsubsection{Reflection}
-		\begin{ants}
-			@ Reflexive systems is not informational closured.
-			@ Base	d on our theory,
-			@ x -> s -> a
-			@@ the system state is determined by environmental state, then it is not conscious.
-			@ Therefore, in general, a simple policy network is not conscious.
-		\end{ants}
-
-		\subsubsection{Blindsight}
-		\begin{ants}
-			@ This also blindsight.
-			@ Blindsight patients and still make above chance judgement without conscious awareness of visual targets.
-			@ The stimulus-reaction policy network still intact, but it cannot form informational closure and therefore, patients has no conscious awareness of visual  targets
-			@ Patient B.F. reactions are stimulus driven.
-		\end{ants}
-
-		\subsubsection{procedure memory}
-
-		\subsubsection{cerebellum}
-		\begin{ants}
-			@ cerebellum feed-forward connections, maybe just a policy network.\needref{cerebellum}
-		\end{ants}
-
-		\subsection{Under the level of informational closure}
-		\subsubsection{statistical inference}
-		\begin{ants}
-			@ The computation of Bayesian brain is unconscious.
-		\end{ants}
-
-		\subsubsection{subliminal perception}
-		\begin{ants}
-			@ Above chance performance can be performed through non-closure pathway (reflexive behaviours)
-
-			@ Due to coarse-graining, mapping between changes of microstate
-		\end{ants}
-		\subsubsection{Libet Experiments}
-
-		\subsection{Deterministic vs probabilistic}
-		\cite{dehaene2017consciousness}
-		\cite{vul2008temporal, moreno2011bayesian, asplund2014attentional, vul2009attention}
-
-	\section*{About Phenomenology (conscious processing)}
-\subsection{Perceptual overflow}
-\subsection{Volition and freewill}
-\begin{ants}
-	@ Volition is a result of coarse-graining
-
-	@ Lebel's experiment can be well explained by the experiment.
-\end{ants}
-
-\subsection{Planning}
-\subsection{Imagination}
-\subsection{Dream vs non-dream sleep}
-\subsection{Binocular rivalry}
-\subsection{Hallucinations}
-\subsection{Synaesthesia}
-
-	\section*{Theory predictions (Counter-intuitive prediction)}
-
-\subsection{informational closure}
-\begin{ants}
-	@ We predict that through coarse-graining, conscious agents create
-\end{ants}
-
-\subsection{Prediction on split-brain (vs IIT)}
-* IIT suggests that cutting, two subparts may both still have MIP, therefore, have two conscious mind.
-
-* However, our theory suggests that if the cut largely destroy the \ac{ic}, then both part may not be conscious.
-
-\end{backup}
-
 \end{document}

### 2019-08-29 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 \newacro{ncg}{neural coarse-graining}
-\newacro{OurTheory}[NCGTC]{The Neural Coarse-graining Theory of Consciousness}
+\newacro{OurTheory}[ICTC]{The Information Closure Theory of Consciousness}
 
@@
 We argue that the content of consciousness is determined by neural variables that obey informational closure and that other brain processes remain unconscious.
-Out theory provides a quantitative distinction between conscious and unconscious processing.
+Out theory based on concise assumptions and propose quantitative definitions using information theorem for both conscious content and conscious level.
 
@@
 
-		\toWrite{maybe need a transition sentence here}
-
 		%% scale
@@
 On the other hand, experience is more detailed than just a binary process, suggesting that the state space of conscious experience is much larger than what a single coarse-grained variable can represent.
+Here, we refer to this fact as \textbf{the scale problem of consciousness} (Fig.\ref{fig:scaleproblem}).
 
@@
 
-		In the following, we first introduce non-trivial informational closure and its importance to information processing for human scale agents \ref{sec:Non-trivial informational closure}.
-We next argue that through coarse-graining the neural system can form a high degree of non-trivial informational closure at a specific coarse-grained level\ref{sec:Neural coarse-graining}.
-We also illustrate how \ac{OurTheory} \ref{sec:OurTheory} can parsimoniously explain empirical findings from previous consciousness studies \ref{sec:Conscious versus Unconscious Processing} and reconcile several current major theories of consciousness\ref{sec:Comparison with other theories}.
-Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from this theory to the current consciousness science \ref{sec:Limitation and Future work}.
+		In the following, we first introduce non-trivial informational closure and its importance to information processing for human scale agents (sec.\ref{sec:Non-trivial informational closure}).
+We next argue that through coarse-graining the neural system can form a high degree of non-trivial informational closure at a specific coarse-grained level (sec.\ref{sec:Neural coarse-graining}).
+We also illustrate how \ac{OurTheory} can \ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (sec.\ref{sec:Comparison with other theories}).
+Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from this theory to the current consciousness science (sec.\ref{sec:Limitation and Future work}).
 
@@
 		    \centering
+		    \label{fig:scaleproblem}
 			\includegraphics[width=\textwidth]{WritingMaterials/Fig_ScaleProblemOfConsciousness/ScaleProblemOfConsciousness.pdf}
@@
 				\begin{figure}
-					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv.pdf}
+					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndUniv.pdf}
 					\caption{Figure adapted from \cite{BERTSCHINGER.2006}}
-					\label{fig:SystemAndEnv}
+					\label{fig:SystemAndUniverse}
 				\end{figure}
@@
 This gives biological agents a great functional and evolutionary advantage.
-Practically, \cite{guttenberg2016neural} proposed that NTIC can be formed by maximising the predictive power about the environment and the self-predictive information of the system concurrently.
+
+			% Practically, \cite{guttenberg2016neural} proposed that NTIC can be formed by maximising the predictive power about the environment and the self-predictive information of the system concurrently.
 
@@
 		%% stochasticity at microscopic levels
-		To create NTIC with a highly stochastic process is challenging.
+		Despite the evolutionary advantage of forming NTIC processes in a system, however, to create NTIC with a highly stochastic process is challenging.
 NTIC requires the predictability of the system state and is therefore impeded by noise in the system.
-Information processing at the microscopic levels (the cellular levels) in the neural system suffers from multiple environmental noise sources throughout, including sensory, cellular, electrical, and synaptic noises.
+Information processing at the microscopic levels (the cellular levels) in neural systems suffer from multiple environmental noise source es throughout, including sensory, cellular, electrical, and synaptic noises.
 For example, neurons have large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
@@
         %% Our argument
-		However, we argue that, neural systems can form NTIC at certain macroscopic levels by coarse-graining microscopic neural states.
-Although the microscopic levels in the neural system are stochastic and cannot form NTIC processes, coarse-grained variables can still form stable and robust representations in the system.
-Coarse-graining refers to many-to-one functions that map microscopic states to macroscopic states.
+		However, we argue that, neural systems can form NTIC at certain macroscopic levels through coarse-graining microscopic neural states.
+Coarse-graining refers to many-to-one functions which aggregate microscopic states to a macroscopic state.
 In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}.
-This is a common neural coding scheme that we see in a large number of previous neurophysiological studies.
+Neural systems, therefore, can form more stable and deterministic state transitions and be more capable to form NTIC processes at certain coarse-grained macroscopic levels.
+
+		Coarse-graining is considered as a common coding strategy in the neural system against ubiquitous stochasticity at microscopic levels.
+
+		Although the microscopic levels in the neural system are stochastic and may incapable of forming NTIC processes, the macroscopic processes in the system can still be  stable and robust.
+This is a common neural coding scheme that we see in a large number of neurophysiological studies.
 For example, individual neural spikes in a transient time span are stochastic, but they can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}.
@@
 		The practical implementation mentioned above suggests that  NTIC can be formed by coarse-graining sensory inputs in artificial neural networks.
-\citep{guttenberg2016neural} proposed a "neural coarse-graining (NCG)" architecture (fig.\ref{fig:NCG}) which aims to capture the emergent large-scale dynamics in the environment.
+\citep{guttenberg2016neural} proposed a "neural coarse-graining (NCG)" architecture which aims to capture the emergent large-scale dynamics in the environment.
 The NCG network learns to coarse-grain input signals and extract latent variables which are both predictive and predictable in the input signal and therefore form NTIC.
@@
 
-        In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory} \todo{We really need a good name}.
-        % \begin{enumerate}
-        %     \item We argue that the existence of an NTIC process within a system is sufficient for information processing to be conscious.
-        %     \item  A system that forms NTIC must necessarily satisfy coarse-graining
-        % \end{enumerate}
+        In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory}.
 
@@
 
-        In what follows, we will first establish two assumption on which this Theory depends. Then, we will develop the propositions in detail.
+        In what follows, we will first establish three assumptions on which this Theory depends. Then, we will develop the propositions in detail.
 
@@
 
-        This assumption is in agreement with the "axiom", \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
+        This assumption is also in agreement with the "axiom", \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
 2]{oizumi2014phenomenology}.
 
-        We further assume that all information requires physical substrates. 
+        Second, we further assume that all information requires physical substrates. 
         From these two assumptions, it follows that the amount of (self-)information possessed by a conscious percept must be equal to the (self-)information of a particular event or entity in the physical reality.
@@
         In this theory, we consider information is the common language between conscious experience and the physical reality.
-This means that consciousness is fundamentally associated with a specific kind of information, i.e., the information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}).
+This means that consciousness is fundamentally associated with information, i.e., the information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}).
 
@@
 
-        Our main proposition is that the coarse-grainings that physically represent consciousnesses are those that are NTIC with respect to the universe state.
+        Finally, our main proposition is that the coarse-grainings that physically represent consciousnesses are those that are NTIC with respect to the universe state.
 More formally this means that every NTIC process $Y_t$ at time $t$ corresponds to a conscious process $C_t=\{C_t^{Content},C_t^{Level}\}$ such that the content $C_{t}^{Content}$ of $C_t$ is just $Y_t$:
@@
         % ---------------------------------------------------------------------------- %
-	    \subsection{Level of Consciousness is equal to the degree of NTIC of a proces}
+	    \subsection{Level of Consciousness is equal to the degree of NTIC of a process}
 
-	    Our theory implies that conscious levels are determined by two quantities (Equation \ref{eq:nticObjective}).
+	    Our theory implies that conscious levels are determined by two quantities (Eq. \ref{eq:nticObjective}).
 
@@
         % ---------------------------------------------------------------------------- %
-		\subsection{Conscious Contents Corresponding to Coarse-grained States}\needfig{maybe I need a figure here}
+		\subsection{Conscious Contents Corresponding to States of a NTIC proces}\needfig{maybe I need a figure here}
         As we mentioned above, human conscious contents always consist of rich,  high dimensional, and integrated information.
@@
     \section{Limitation and Future work}\label{sec:Limitation and Future work}  
+        In this article, we propose the central proposition of our theory.
+We focused on convey the major concepts and mathematical formulation of the theory.
+In this section, we will discuss potential issues and challenges in the current version of \ac{OurTheory}.
+
+        % multi NTIC problem
+        Our theory is not complete yet. 
+        To identify an NTIC individuals and their boundaries, we can adopt the algorithm for computing individuality developed by \cite{krakauer2014information}.
+This algorithm defines an individual starting from a small set of variables and repeatedly computes individuality after adding more variables into the system.
+If the measure of individuality increase, the algorithm considers the new variables as the part of the system, and vise verse.
+However, this algorithm does not consider coarse-grained processes in a system (see "Caveats and challenges"\cite[p.
+13]{krakauer2014information}.
+
+        In the following articles, we will discuss the relationship between synergy and NTIC process
+
         % Can't solve the hard problem

### 2019-09-01 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 		%% stochasticity at microscopic levels
-		Despite the evolutionary advantage of forming NTIC processes in a system, however, to create NTIC with a highly stochastic process is challenging.
+		Despite the evolutionary advantage of having NTIC processes in a system, however, to create NTIC with a highly stochastic process is challenging.
 NTIC requires the predictability of the system state and is therefore impeded by noise in the system.
-Information processing at the microscopic levels (the cellular levels) in neural systems suffer from multiple environmental noise source es throughout, including sensory, cellular, electrical, and synaptic noises.
+Information processing at the microscopic levels (the cellular levels) in neural systems suffer from multiple environmental noise sources throughout, including sensory, cellular, electrical, and synaptic noises.
 For example, neurons have large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
@@
 In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}.
-Neural systems, therefore, can form more stable and deterministic state transitions and be more capable to form NTIC processes at certain coarse-grained macroscopic levels.
+Neural systems, therefore, can form more stable and deterministic state transitions and be more capable of forming NTIC processes at certain coarse-grained macroscopic levels.
 
-		Coarse-graining is considered as a common coding strategy in the neural system against ubiquitous stochasticity at microscopic levels.
+		Indeed, empirical evidence shows that coarse-graining is a common coding strategy in the neural system against ubiquitous stochasticity at microscopic levels.
 
-		Although the microscopic levels in the neural system are stochastic and may incapable of forming NTIC processes, the macroscopic processes in the system can still be  stable and robust.
+% 		Although the microscopic levels in the neural system are stochastic and may incapable of forming NTIC processes, the macroscopic processes in the system can still be  stable and robust.
 This is a common neural coding scheme that we see in a large number of neurophysiological studies.
-For example, individual neural spikes in a transient time span are stochastic, but they can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}.
+
+		For example, albeit the temporal intervals between two consecutive action potentials from individual neurons are stochastic, the firing rate, a temporal coarse-grained variable, represent more meaningful
+
+		they can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}.
 Neurons encode stimulus intensity by increasing or decreasing firing rate.

### 2019-09-02 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 \newacro{ncg}{neural coarse-graining}
-\newacro{OurTheory}[ICTC]{The Information Closure Theory of Consciousness}
+\newacro{OurTheory}[ICT]{The Information Closure Theory of Consciousness}
 
@@
 In addition, some parts of the neural system contribute very little to conscious experience (the cerebellum for example \citep{lemon2010life}), also suggesting that conscious contents do not have one-to-one mapping to the entire state of the neural system.
-On the other hand, experience is more detailed than just a binary process, suggesting that the state space of conscious experience is much larger than what a single coarse-grained variable can represent.
-Here, we refer to this fact as \textbf{the scale problem of consciousness} (Fig.\ref{fig:scaleproblem}).
+On the other hand, human conscious experience is more detailed than just a simple (e.g.
+binary) process can represent, suggesting that the state space of conscious experience is much larger than what a single overly coarse-grained binary variable can represent.
+These facts suggest that conscious processes are scale dependent.
+We refer to this notion as \textbf{the scale problem of consciousness} (Fig.\ref{fig:scaleproblem}).
 
@@
 We argue that every process with a high degree of not-trivial information closure (NTIC) has consciousness.
-This means that the state of such a process corresponds one-to-one to conscious content.
-\footnote{In the following NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}.
+This means that the state of such a process corresponds one-to-one to conscious content.\footnote{In the following NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}.
 We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC.
@@
 
-		In the following, we first introduce non-trivial informational closure and its importance to information processing for human scale agents (sec.\ref{sec:Non-trivial informational closure}).
-We next argue that through coarse-graining the neural system can form a high degree of non-trivial informational closure at a specific coarse-grained level (sec.\ref{sec:Neural coarse-graining}).
-We also illustrate how \ac{OurTheory} can \ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (sec.\ref{sec:Comparison with other theories}).
-Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from this theory to the current consciousness science (sec.\ref{sec:Limitation and Future work}).
+		In the following, we first introduce non-trivial informational closure and its importance to information processing for human scale agents (Sec.\ref{sec:Non-trivial informational closure}).
+We next argue that through coarse-graining the neural system can form a high degree of NTIC at a specific coarse-grained level (Sec.\ref{sec:Neural coarse-graining}).
+In the Sec.\ref{sec:OurTheory}, we propose our theory: \acf{OurTheory}.
+We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies (Sec.\ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (Sec.\ref{sec:Comparison with other theories}).
+Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from this theory to the current consciousness science (Sec.\ref{sec:Limitation and Future work}).
 
@@
 			\caption{The scale problem of consciousness: Human conscious experience does not reflect information processed at every scale.
-Only information at a certain scale in the neural system is conscious.}
+Only information at a certain coarse-grained scale in the neural system is conscious.}
 	   	\end{figure}
@@
 				\begin{figure}
-					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndUniv.pdf}
-					\caption{Figure adapted from \cite{BERTSCHINGER.2006}}
-					\label{fig:SystemAndUniverse}
+					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv_2.0.pdf}
+					\caption{} % Figure adapted from \cite{BERTSCHINGER.2006}
+					\label{fig:SystemAndEnv}
 				\end{figure}
@@
 
+		% New 
+		The coding scheme through cg provides a system which contains high stochasticity at microscope levels can encode stable information at the macroscopic level.
+Therefore, allow the system to form ntic processes at macroscopic levels.
+We argue that through cg the neural systems form ntic processes and encode env dynamic.
+
 		% neural coarse-graining by Nic
@@
 	\section{A neural coarse graining theory of consciousness}\label{sec:OurTheory}
+
+		\begin{figure}[H]
+		    \centering
+		    \label{fig:fullgraph}
+			\includegraphics[width=\textwidth]{WritingMaterials/Fig_FullGraph/FullGraph.pdf}
+			\caption{The information flow amounts the universe $X$, the system $Y$, the environment of the system $E$, and the coarse-grained process of the system $Y$.
+The solid line with a filled arrow from $X_t$ to $X_{t+1}$ represents the microscopic dynamic of the universe.
+The solid lines with a empty arrow represent directions of coarse-graining.
+The dashed lines represents virtual dependencies between  two macroscopic variables.
+The red $\hat{Y}_t$, $\hat{Y}_{t+1}$, and the red dashed line in between represents a macroscopic process which forms informational closure at a certain coarse-grained level.}
+	   	\end{figure}
 

### 2019-09-07 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 % \excludeversion{backup}
+
+\usepackage{chngcntr}
+\counterwithout{figure}{section}
 
@@
 \newacro{ncg}{neural coarse-graining}
-\newacro{OurTheory}[ICT]{The Information Closure Theory of Consciousness}
+\newacro{OurTheory}[ICT]{Information Closure Theory of Consciousness}
 
@@
 These facts suggest that conscious processes are scale dependent.
-We refer to this notion as \textbf{the scale problem of consciousness} (Fig.\ref{fig:scaleproblem}).
+We refer to this notion as \textbf{the scale problem of consciousness} (Fig.~\ref{fig:scaleproblem}).
 
@@
 We argue that every process with a high degree of not-trivial information closure (NTIC) has consciousness.
-This means that the state of such a process corresponds one-to-one to conscious content.\footnote{In the following NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}.
+This means that the state of such a process corresponds one-to-one to conscious content.\footnote{In the following IC stands for "informational closure" or "informationally closed" and NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}.
 We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC.
@@
 		    \centering
-		    \label{fig:scaleproblem}
 			\includegraphics[width=\textwidth]{WritingMaterials/Fig_ScaleProblemOfConsciousness/ScaleProblemOfConsciousness.pdf}
@@
 Only information at a certain coarse-grained scale in the neural system is conscious.}
+			\label{fig:scaleproblem}
 	   	\end{figure}
@@
 The concept of closure is closely related to system identification in systems theory.
-One can distinguish a system from its environment by computing the closedness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}.
+One can distinguish a system from its environment by computing the closeness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}.
 The closure can be further quantified by information theory.
@@
 			\noindent
-			Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network in Fig.\ref{fig:SystemAndEnv}.
-Then, information flow $J_{t}$ from the environment $E$ to a system $Y$ at time $t$ can be defined as the conditional mutual information $I$ between the current environment state $E_{t}$  and the future system state $Y_{t+1}$ given the current system state $Y_{t}$
+			Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network in Fig.~\ref{fig:SystemAndEnv}.
+Then, information flow $J_{t}$ from the environment $E$ to a system $S$ at time $t$ can be defined as the conditional mutual information $I$ between the current environment state $E_{t}$  and the future system state $Y_{t+1}$ given the current system state $Y_{t}$
 
@@
 				\begin{figure}
-					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv_2.0.pdf}
-					\caption{} % Figure adapted from \cite{BERTSCHINGER.2006}
+					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv_2.pdf}
+					\caption{The dependencies between a system and its environment.} % Figure adapted from \cite{BERTSCHINGER.2006}
 					\label{fig:SystemAndEnv}
@@
 				J_{t}(E \rightarrow Y )=0
+				\label{eq:informationflow2}
 				\end{equation}
@@
 In the non-trivial case, even though a system contains (or encodes) information about the environmental dynamics, the system can still be informationally closed.
-In such cases, the mutual information between the current states of the environment and the future state of the system is larger than zero\footnote{Here we assume that that the environment contains more information than the system, i.e.
+In such cases, the mutual information between the current states of the environment and the future state of the system is larger than zero.
+%\footnote{Here we assume that that the environment contains more information than the system, i.e.
 $H(E|S)>0$ and $E\neq S$}.
@@
     				& \text{minimising} & { } & I(Y_{t+1};Y_{t}|E_{t}) & { }
+    				\end{aligned}
+				\end{equation}
+
+			One can also maximise NTIC by 
+				\begin{equation}
+    				\label{eq:nticObjective2}
+    				\begin{aligned}
+    				& \text{maximising} & { } & I(Y_{t+1};E_{t}) & { } & \text{and} \\
+    				& \text{minimising} & { } & I(Y_{t+1};E_{t}|Y_{t}) & { }
     				\end{aligned}
@@
 Recent studies have shown relevant properties in the visual system of salamanders.
-Two studies \citep{Palmer2015, sederberg2018learning} examined salamander retina and found that the a large group of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states (see Fig.\ref{fig:sederberg2018learning}), therefore, in line with the characteristic of NTIC.
+Two studies \citep{Palmer2015, sederberg2018learning} examined salamander retina and found that the a large group of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states (see Fig.~\ref{fig:sederberg2018learning}), therefore, in line with the characteristic of NTIC.
 Therefore, the self-predictive information of the neural populations can guide prediction about external stimuli without reference to stimulus parameters explicitly.
@@
 % ============================================================================ %
-	\section{Coarse-graining In The Neural System} \label{sec:Neural coarse-graining}
+	\section{Coarse-graining in The Neural System} \label{sec:Neural coarse-graining}
 
@@
 
-		Indeed, empirical evidence shows that coarse-graining is a common coding strategy in the neural system against ubiquitous stochasticity at microscopic levels.
-
-% 		Although the microscopic levels in the neural system are stochastic and may incapable of forming NTIC processes, the macroscopic processes in the system can still be  stable and robust.
-This is a common neural coding scheme that we see in a large number of neurophysiological studies.
-
-		For example, albeit the temporal intervals between two consecutive action potentials from individual neurons are stochastic, the firing rate, a temporal coarse-grained variable, represent more meaningful
-
-		they can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}.
-Neurons encode stimulus intensity by increasing or decreasing firing rate.
-\citep{kandel2000principles}.
+		Indeed, empirical evidence has been showing that coarse-graining is a common coding strategy against ubiquitous stochasticity at microscopic levels of the the neural system.
+For instance, the inter-spike intervals of individual neurons are stochastic.
+This implies that states of individual neurons are incapable of encoding and representing stable information.
+However, the spiking rate, i.e.
+the average spike counts in a given time interval, shows astonishing stability and robustness against noise causing the variation of inter-spike intervals.
+Using this temporal coarse-graining strategy, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}, individual neurons can encode stimulus intensity by increasing or decreasing firing rate \citep{kandel2000principles}.
 \citep{stein2005neuronal}.
-In contrast, rate codes are relatively stable and are highly robust against noise caused by the variation of inter-spike intervals.
-The robustness is direct consequence of the many to one map used.
+The robustness of the rate coding is direct consequence of the many to one map used.
 
 		% population code
-		Another example of coarse-graining in neural systems is population coding.
-In this coding scheme, information (e.g.
-orientation of a bar) is represented by activation patterns of a population of neurons.
-Multiple activation patterns could represent the same information content.
-The subspaces of the joint state space of these neurons are the macroscopic coarse-grained variables.
-Therefore, the information is encoded in coarse-grained variables whose values are jointly determined by neural activation patterns within a neural population \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
-In such cases, encoded information cannot be read out by the stochastic activities of a single neuron.
-Instead, coarse-grained variables (such as population averaging or population vector, i.e.
-weighted sum of the preferred directions of a population of neurons) are able to represent information more stably.
-Encoding information at coarse-grained levels allow the neural system to ignore certain causal interactions relevant to fine-grained level of description \citep{Woodward2007-WOOCWA}.
-
-		% New 
-		The coding scheme through cg provides a system which contains high stochasticity at microscope levels can encode stable information at the macroscopic level.
-Therefore, allow the system to form ntic processes at macroscopic levels.
-We argue that through cg the neural systems form ntic processes and encode env dynamic.
-
-		% neural coarse-graining by Nic
-		The practical implementation mentioned above suggests that  NTIC can be formed by coarse-graining sensory inputs in artificial neural networks.
+		Population coding is another example of encoding information through coarse-graining in neural systems.
+In this coding scheme, information is encoded by activation patterns of a set of neurons (a neuron population).
+To reduce the influence noise on scholastic state transitions of individual neurons, many states for a neuron population map to the same information content.
+Therefore, stable representation can be formed through coarse-graining a high dimensional state space of a neuron population to a low dimensional state space of encoded contents \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
+Therefore, individual neuron states (the microscopic level) are not informative about the encoded contents at the population level (the macroscopic level).
+Instead, coarse-grained variables are better entities to encode information and allow the neural system to ignore noisy causal interaction at the fine-grained level of description \citep{Woodward2007-WOOCWA}.
+
+        The two examples show that coding schemes through coarse-graining can provides a stochastic system, e.g.
+the neural system, more stable and deterministic macroscopic processes to encode and process information reliably.
+We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic levels.
+Based on this argument, we proposes our theory of consciousness in the next section.
+
+% 		% neural coarse-graining by Nic
+% 		The practical implementation mentioned above suggests that  NTIC can be formed by coarse-graining sensory inputs in artificial neural networks.
 \citep{guttenberg2016neural} proposed a "neural coarse-graining (NCG)" architecture which aims to capture the emergent large-scale dynamics in the environment.
 The NCG network learns to coarse-grain input signals and extract latent variables which are both predictive and predictable in the input signal and therefore form NTIC.
-
-		%% not monotonic
-		It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
-We saw above that not coarse-graining enough and therefore considering processes that are too microscopic leads to low values of NTIC.
-We also saw that coarse-graining further can increase the values of NTIC.
-However, if the macroscopic variable is overly coarse-grained the system states can result in low degrees of NTIC.
-For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus looses the self and environmental predictive power.
-
-        %% Link to consciousness
-        % \ideaCallout{Discuss this part}
-        % At the physical scale which human beings live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
-This suggests that information in the environment is nearly closed at the right spatio-temporal scale.
-Therefore, this gives agents living at this physical scale great advantages if the agents form an NTIC process internally.
-Therefore, coarse-graining becomes necessary to map microscopic sensory and neuronal states into macroscopic NTIC process.
 
@@
 
-		\begin{figure}[H]
-		    \centering
-		    \label{fig:fullgraph}
-			\includegraphics[width=\textwidth]{WritingMaterials/Fig_FullGraph/FullGraph.pdf}
-			\caption{The information flow amounts the universe $X$, the system $Y$, the environment of the system $E$, and the coarse-grained process of the system $Y$.
-The solid line with a filled arrow from $X_t$ to $X_{t+1}$ represents the microscopic dynamic of the universe.
-The solid lines with a empty arrow represent directions of coarse-graining.
-The dashed lines represents virtual dependencies between  two macroscopic variables.
-The red $\hat{Y}_t$, $\hat{Y}_{t+1}$, and the red dashed line in between represents a macroscopic process which forms informational closure at a certain coarse-grained level.}
-	   	\end{figure}
-
         In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory}.
+We also discuss the implications of \ac{OurTheory} in Sec.~\ref{sec:cl}, \ref{sec:cc}, and \ref{sec:reconcile}.
 
@@
 
-        In what follows, we will first establish three assumptions on which this Theory depends. Then, we will develop the propositions in detail.
+        In what follows, we will first establish three assumptions on which this theory depends. Then, we will develop the propositions in detail.
 
@@
 
-        This assumption is also in agreement with the "axiom", \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
-2]{oizumi2014phenomenology}.
+        This assumption is also in agreement with one of the "axiom", \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.2]{oizumi2014phenomenology}.
 
@@
         In this theory, we consider information is the common language between conscious experience and the physical reality.
-This means that consciousness is fundamentally associated with information, i.e., the information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}).
+This means that consciousness is fundamentally associated with information \citep{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}).
 
         The third assumption is that no consciousness can contain information of the entire universe.
-Together with assumption one and two, this means that the physical representations of the contents of any consciousness must be a coarse-graining of the universe states.
-
-        Finally, our main proposition is that the coarse-grainings that physically represent consciousnesses are those that are NTIC with respect to the universe state.
+This means that there exists a informational boundary for every consciousness, i.e.
+informationally closed to the the universe.
+This is in line with our conscious experience that information provided by every conscious percept is limited.
+
+        Together with the first three assumptions, this means that the physical representations of the contents of any consciousness must be a coarse-graining of the universe states and also informationally closed to the universe.
+
+        Note that a coarse-grained process $Y$ can be a coarse-graining of another coarse-grained process $S$ of the universe $X$ (see Fig.~\ref{fig:fullgraph}).
+Here, we consider $S$ is a dynamic system and $Y$ is a coarse-grained process of the system $S$.
+Therefore, the environment $E$ of $S$ is also a coarse-graining of the universe.
+Importantly, in such case, if a macroscopic process $Y$ is informationally closed to the universe $X$, this implies $Y$ is also informationally closed to the microscopic level of the system $S$ and the environment $E$.
+
+		\begin{equation}
+			\label{eq:ICchain}
+			\begin{aligned}
+		    & I(Y_{t+1};X_t|Y_{t})=0 & \implies & I(Y_{t+1};S_t|Y_{t})=0 \\
+		    & {} & \implies & I(Y_{t+1};E_t|Y_{t})=0
+			\end{aligned}
+		\end{equation}
+
+        This results in a crucial implication that informational closure can occur between levels in a system.
+The macroscopic level $Y$ can be informationally closed to the microscopic level $S$ within a system \citep{PFANTE.2014}.
+
+		\begin{figure}[H]
+		    \centering
+			\includegraphics[width=\textwidth]{WritingMaterials/Fig_FullGraph/FullGraph.pdf}
+			\caption{The information flow amounts the universe $X$, the system $S$, the environment of the system $E$, and the coarse-grained process of the system $S$.
+The solid line with a filled arrow from $X_t$ to $X_{t+1}$ represents the microscopic dynamic of the universe.
+The solid lines with a empty arrow represent directions of coarse-graining.
+The dashed lines represents virtual dependencies between  two macroscopic variables.
+The red $Y_t$, $Y_{t+1}$, and the red dashed line in between represents a macroscopic process which forms informational closure at a certain coarse-grained level.}
+			\label{fig:fullgraph}
+	   	\end{figure}
+
+        A concrete example in the context of neuroscience is that $X$, $S$, $Y$, and $E$ represent the microscopic level of the universe, a cellular level process in the neural system, a macroscopic process of the neural system coarse-grained from the cellular level process $S$, and the environment which the cellular level process $S$ interacts with which may includes other processes in the neural system, the sensors for perception and interoception, and external physical worlds, respectively.
+
+        Our fourth assumption is that information provided by every conscious content is not trivial.
+More precisely, there exists a certain degree of mutual information between conscious processes and the environments which it interacts with.
+As mentioned in Sec.\ref{sec:Non-trivial informational closure} regardless one process is informationally closed to another one, to form mutual information between the two processes, i.e.
+NTIC, is still possible.
+Therefore, a macroscopic process $Y$ can be NTIC to the system's environment $E$ and concurrently be informationally closed to its microscopic process $S$.
+In other words, the macroscopic process can encode environmental information (by forming NTIC) and, however, be ignorant to its microscopic processes (IC).
+This is in line with our conscious experience that information that every conscious percept provides represent rich and structured environmental states without involving much information at microscopic activities.
+
+        Finally, together with the four assumptions above, our main proposition is that the coarse-graining that physically represent consciousnesses are those that are informationally closed with respect to the universe states and concurrently be NTIC with respect to its environment.
 More formally this means that every NTIC process $Y_t$ at time $t$ corresponds to a conscious process $C_t=\{C_t^{Content},C_t^{Level}\}$ such that the content $C_{t}^{Content}$ of $C_t$ is just $Y_t$:
@@
 		\end{equation}
-		\newline
-
 		We discuss the implications of these propositions in the following.
@@
         % ---------------------------------------------------------------------------- %
-	    \subsection{Level of Consciousness is equal to the degree of NTIC of a process}
-
-	    Our theory implies that conscious levels are determined by two quantities (Eq. \ref{eq:nticObjective}).
-
-	    First, to form high level of NTIC, one needs high self-predictive information $I(Y_{t+1};Y_{t})$ between the current internal state and the future internal state. 
-	    Consider two hypothetical systems composed of binary nodes.
-One has only three nodes and the other has 1 million nodes.
-Then the maximum possible self-predictive information for such systems are 3 bits and 1 million bits.
-So complex systems can potentially reach higher levels of consciousness.
-	    This outcome is naturally consistent with a common intuition in which levels of consciousness usually is associated with the level of complexity of a system.
-
-	    Second, one can also minimise the conditional mutual information  $I(Y_{t+1};Y_{t}|E_{t})$.
-This suggests that conscious level increases with the level of information about the environment dynamics that the NTIC process encodes.
-Therefore, an agent that forms an NTIC process lives in and adapts to a more complex environment has a higher conscious level than an agent that interacts with an environment with simpler dynamics.
-This also implies that agents who can explore, adapt their model, and react to diverse environments should have higher levels of consciousness.
-
-	    Note that the non-monotonic relationship between levels of NTIC and the scale of coarse-graining suggests that there exists a scale of coarse-graining with the maximal level of NTIC.
-The self-predictive information is the key to form a high level of consciousness.
-If a system dynamics is highly stochastic and unpredictable, the level of consciousness should be low.
-As a result, information processed at neuronal scales which is heavily noisy and highly stochastic cannot form a high level of consciousness.
-Similarly, after coarse-graining, macro-variables loose predictive fine-grain information, the predictability become low and also the channel capacity between the current state and future state becomes very small, NTIC would be low as well.
-Consequently, human consciousness should be maximised at a certain coarse-grained level in the neural system.
-
-	    Note that, the environment of an NTIC process in the neural system includes not only the\todo{rerite this}
-
+	    \subsection{Level of Consciousness is equal to the degree of NTIC of a process}\label{sec:cl}
+
+        According to Eq.~\ref{eq:nticObjective}, \ac{OurTheory} implies that conscious levels are determined by two quantities.
+
+        First, to form high level of NTIC, one can increase the mutual information $I(Y_{t+1};Y_{t})$ between the current internal state $Y_t$ and the future internal state $Y_{t+1}$.
+In other words, conscious levels are associated with the degree of self-predictive information.
+This mutual information term can be further decomposed to two information entropy quantities:
+
+        \begin{equation}
+        \label{eq:SelfEntropy}
+        I(Y_{t+1};Y_{t}) = H(Y_{t+1}) - H(Y_{t+1}|Y_t)
+        \end{equation}
+
+        This implies that a high NTIC process should have a rich dynamic and concurrently maintain self-productiveness overtime.
+Another implication is that a complex systems can potentially reach higher levels of consciousness due to a larger information capacity to achieve higher mutual information.
+This outcome is consistent with a common intuition that conscious levels are associated with the degrees of complexity of systems.
+
+	    Second, one can minimise the conditional mutual information $I(Y_{t+1};Y_{t}|E_{t})$ to increase the level of NTIC.
+This quantity suggests that conscious level increases with the level of information about the environment state $E_t$ that the NTIC process encodes in its own state $Y_t$.
+An important implication is that a NTIC possessed by an agent which interacts with and adapts to a complex environment should have a higher level of NTIC than one possessed by another agent which lives and adapts to a simple environment.
+In other words, the environmental complexity is associated with conscious levels of NTIC processes.
+
+	    %% not monotonic
+		It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+We saw above that not coarse-graining enough and therefore considering processes that are too microscopic leads to low values of NTIC.
+However, if the macroscopic variable is overly coarse-grained the system states can result in low degrees of NTIC.
+For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus looses the self and environmental predictive power.
+\ac{OurTheory}, therefore, argues that only processes at a certain level of coarse-graining in the neural system can reach high level of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
+As a result, there exists a certain level of coarse-graining which has a maximal conscious level within the neural system.
+
+		\begin{figure}[H]				
+    		\includegraphics[width=\textwidth]{WritingMaterials/Fig_temp/FoxitReader_2019-01-31_19-03-59.png}
+    		\caption{A n1on-monotonic relationship between Level of coarse-graining and level of consciousness.}
+    		\label{fig:LevelOfConsciousness}
+		\end{figure}
+
+        \ideaBox{About Human Scale}
         Finally, which coarse-grained level can form high NTIC? 
@@
         At the physical scale which human being interact with, the environmental dynamics is nearly deterministic following the laws of classical physics.
-It gives agents living at this physical scale great advantages if the agents can build NTIC process internally.
+It gives agents interact at this physical scale great advantages if the agents can build NTIC process internally.
 Therefore, to coarse-grain microscopic states is necessary
 
-		\begin{figure}[H]				
-    		\includegraphics[width=\textwidth]{WritingMaterials/Fig_temp/FoxitReader_2019-01-31_19-03-59.png}
-    		\label{fig:LevelOfConsciousness}
-    		\caption{Level of coarse-graining and level of consciousness.
-The degree of NTIC is not a monotonic function of coarse-graining levels, suggesting that high conscious level may exist at a certain coarse-grained level }
-		\end{figure}
-
-        % ---------------------------------------------------------------------------- %
-        %                Contents Corresponding to Coarse-grained States               %
-        % ---------------------------------------------------------------------------- %
-		\subsection{Conscious Contents Corresponding to States of a NTIC proces}\needfig{maybe I need a figure here}
-        As we mentioned above, human conscious contents always consist of rich,  high dimensional, and integrated information.
-The state space of the correspondent physical system must have the same information capacity as the information content of consciousness.
-We claim that conscious contents correspond to the state of the NTIC process.
-
-        This claim implies that the complexity of conscious contents is identical to the amount of information contained in the NTIC process.
-Therefore, a crucial predict from our theory is that the larger state space of the NTIC process has the richer conscious experience the process can have (e.g., an NTIC process involving a large amount of coarse variables).
-Crucially, even experience of full darkness contains rich information because it rules out other enormous potential alternative states of conscious contents.
-Equivalently, in the physical system, to know the state of the NTIC process when there is no sensory input (darkness) also requires the same amount of information from the system.
-
-        For example, a small creature lives in a simple environment with very limited environment dynamics.
-It may form a simple NTIC process.
-However, in this situation, the self-predictive information is very low and the state space of the NTIC process is small.
-Therefore, the richness of the conscious experience this agent has will be very limited.
-
-        Importantly, because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale, our theory supports multiple realisation thesis \needref{multiple realisation} which suggests same conscious experiences can be mapped to different physical implementations.
+        %% Link to consciousness
+        At the physical scale which human beings live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
+This suggests that information in the environment is nearly closed at the right spatio-temporal scale.
+Therefore, this gives agents living at this physical scale great advantages if the agents form an NTIC process internally.
+Therefore, coarse-graining becomes necessary to map microscopic sensory and neuronal states into macroscopic NTIC process.
+
+		\subsection{Conscious Contents Corresponding to States of a NTIC process}\label{sec:cc}
+	    % richness 
+		\ac{OurTheory} proposes that conscious contents correspond to states of NTIC processes (Eq.~\ref{eq:cContent}).
+This implies that the size of the state space of a NTIC process is associated with the richness of conscious contents that the process can potentially have.
+Therefore, a complex NTIC process with a high dimensional state space can have richer conscious experience than a simple NTIC process can have.
+This outcome is consistent with a the intuition that the richness of conscious contents is associated with the complexity of a system.
+
+		% CC doesn't include all microscopic states
+		As mentioned above, informational closure can happen between scales of coarse-graining within a single system.
+Thus, a macroscopic NTIC process can be ignorant to its microscopic states.
+\ac{OurTheory} argues that human conscious contents do not reflect cellular level activity because the conscious process which corresponds to a macroscopic NTIC process is informationally closed to the cellular level in the human neural system.
+Further more, since NTIC processes are informationally closed, each of them can be considered as a reality.
+In the extreme case, when the information flow from the its microscopic processes and environment is completely zero (Eq.~\ref{eq:informationflow2}), the future states of the process is only determined by its past states.
+
+		Importantly, NTIC processes encodes environmental information in its state.
+This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.
+This implication fit well with mental simulation theory of consciousness, predictive processing perspective of consciousness, and information generation theory of consciousness \needref{need three}.
+Note that \ac{OurTheory} doesn't assume that generative models are necessary.
+The implication a natural consequence based on our proposition.
+
+        Finally, due to a coarse-graining is a many to one map from microscopic to macroscopic scales, our theory implies multiple realisation thesis of consciousness\needref{multiple realisation} which suggests different physical implementation can map to the same conscious experience.
 
@@
         % ---------------------------------------------------------------------------- %
-	    \subsection{Reconciling the levels and contents of consciousness}
+	    \subsection{Reconciling the levels and contents of consciousness}\label{sec:reconcile}
 	    Segregation of conscious levels and conscious contents raises a debate \citep{bayne2016there, Fazekas2016}.
-Our framework reconciles conscious level and conscious content.
-When the information encapsulated in the NTIC process is large and reaches a high NTIC,the system has high level of consciousness.
-Simultaneously, this provides a rich state space which is equivalent to encoding rich predictive environmental dynamic in the system.
-From this perspective, levels and contents of consciousness are just two different properties of NTIC processes.
-An important prediction from our theory is that in which the conscious level is determined by the size of the state space of the NTIC process rather the transient state of a system.
-For example, when we experience monotonous environment (a dark room), this does not degrade the conscious level.
-
-	    Our framework also explains why in normal physiological states the level and the content are positively correlated \citep{laureys2005neural}\needfig{}.
-To form high NTIC, a system also needs to have high dimensionality and a large state space which guarantees rich and high dimensional information in conscious contents.
-Therefore, this framework well integrates the two key but debated concepts in consciousness research.
-
-        % ---------------------------------------------------------------------------- %
-        %                 sensory hierarchy and neural coarse-graining                 %
-        % ---------------------------------------------------------------------------- %
-		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}
-
-        It is important to note that the coarse-graining direction is not necessary aligned with \critical{Just saying anatomical is not enough.
-Need better expression} anatomical sensory hierarchy in the neural system.
-Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.
-Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.
-In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system.
-We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.
-
-		\begin{figure}[H]
-
-			\includegraphicsTodo[width=\textwidth]{WritingMaterials/Fig_SeperationOfCGandCortHierachy/SeperationOfCGandCortHierachy.pdf}
-			\label{fig:hierarchy}
-		\end{figure}
+In \ac{OurTheory} conscious levels and conscious contents are just two different properties of NTIC processes, and, therefore, naturally reconciles the two aspects of consciousness.
+To form high NTIC, a NTIC process needs to have a large and potentially high state space which guarantees rich and high dimensional information in conscious contents.
+Therefore, this framework well integrates the two key but debated concepts in consciousness research
+
+	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that the the size of the state space and information entropy $H(Y)$ of a NTIC process are associated with both conscious levels and conscious contents.
+To reach high NTIC, a process needs to have a large state space and high information entropy which guarantee rich conscious contents and also the capacity of predictive information of the system (Eq.~\ref{eq:nticObjective}).
+	    \ac{OurTheory} therefore explains why in normal physiological states conscious levels and conscious contents are positively correlated \citep{laureys2005neural}.
+This implication is also in line with the intuition in which consciousness is often associated with complex systems.
 
@@
         % ---------------------------------------------------------------------------- %
-        \subsection{Dynamical Boundary}
-        Our theory predicts that the boundary of a conscious system is dynamical.
+        % \subsection{Dynamical Boundary}
+        % Our theory predicts that the boundary of a conscious system is dynamical.
 The boundary is determined by the NTIC process.
@@
 Note that, due to synergistic information, even recruiting some new variables may largely increase the level of NTIC.
-        This may explain why consciousness is tightly associated with binding and integration of information in human perception and cognition.
+        % This may explain why consciousness is tightly associated with binding and integration of information in human perception and cognition.
 Another crucial implication is that the same neural substrates may not be always involved in conscious processing rather it depends on whether it creates high NTIC with other members in the neural system.
@@
 	\section{Conscious versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
-	    In this section, we show how our theory can make predictions about whether a process is conscious or unconscious.
-While our theory is built upon a minimal set of assumptions, it possesses predictive power about the relationship between information processing in the neural system and conscious experience.
-
-		Our theory argues that, to make information conscious, the following necessay and sufficient conditions need to be satisfied.
-		\ideaCallout{Need discussion}
-		\begin{enumerate}
-		    \item Sufficient condition: Information is encoded in NTIC process. 
-		    \item Necessary condition: The system is capable of constructing NTIC processes at coarse-grained levels. 
-		\end{enumerate}
-
-        We especially highlight the second condition because it is critically related to many empirical research results even though it is only a necessary condition.
+	    In this section, we show how our theory can make predictions about what processes are conscious and what are unconscious.
+
+        % While our theory is built upon a minimal set of assumptions, it possesses predictive power about the relationship between information processing in the neural system and conscious experience.
+
+% 		Our theory argues that, to make information conscious, the following necessary and sufficient conditions need to be satisfied.
+
+%         We especially highlight the second condition because it is critically related to many empirical research results even though it is only a necessary condition.
 As we will describe below, this theory can well explain a variety of previous empirical findings in consciousness science and further make predictions for future research.
@@
         \subsection{Unconscious Processing}
+        \ac{OurTheory} proposes that NTIC is sufficient for a process to be conscious. Here, we highlights three scenarios that
+
+        First, a process is not informational closed leads to low NTIC (Eq.~\ref{eq:nticObjective2}, and, therefore, low conscious levels or no consciousness.
+In this case, the current states of the process are largely determined by its environment.
+
+        We highlight two scenarios that a process is functional, however, but unconscious.
 
@@
 However, in this circumstance, the future state of the process is largely determined by the environmental states.
-That is, the process is not informational closed (${J_{t}(E \rightarrow Y )} \not\approx 0$, Fig.\ref{fig:reflexive}).
+That is, the process is not informationally closed (${J_{t}(E \rightarrow Y )} \not\approx 0$, Fig.~\ref{fig:reflexive}).
 
@@
 
-        For example, Fig. \ref{fig:TemperatureExample} illustrates the relationship 
+        For example, Fig.~ \ref{fig:TemperatureExample} illustrates the relationship 
         At the left panel, two cups contain water with different volumes $V_t$ and temperatures $T_t$.
@@
         % ---------------------------------------------------------------------------- %
+
+            % ---------------------------------------------------------------------------- %
+            %                 sensory hierarchy and neural coarse-graining                 %
+            % ---------------------------------------------------------------------------- %
+    		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}
+
+            It is important to note that the coarse-graining direction is not necessary aligned with \critical{Just saying anatomical is not enough.
+Need better expression} anatomical sensory hierarchy in the neural system.
+Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.
+Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.
+In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system.
+We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.
+
+    		\begin{figure}[H]
+
+    			\includegraphicsTodo[width=\textwidth]{WritingMaterials/Fig_SeperationOfCGandCortHierachy/SeperationOfCGandCortHierachy.pdf}
+    			\label{fig:hierarchy}
+    		\end{figure}
+
 		\subsection{Theories about multilevel views on consciousness and cognition}
@@
 However, we do not assume any rivalry mechanism.
-Instead, we argue that, if  information carried by the coarse-grained variables can increase the predictability of the process and form high NTIC,  it naturally form a informational closed boundary and
+Instead, we argue that, if  information carried by the coarse-grained variables can increase the predictability of the process and form high NTIC,  it naturally form a informationally closed boundary and
 

### 2019-09-11 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 
-        The two examples show that coding schemes through coarse-graining can provides a stochastic system, e.g.
-the neural system, more stable and deterministic macroscopic processes to encode and process information reliably.
+        The two examples show that coding schemes through coarse-graining could provides a stochastic system, e.g.
+the neural system, to form more stable and deterministic macroscopic processes to encode and process information reliably.
 We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic levels.
@@
         \subsection{Unconscious Processing}
-        \ac{OurTheory} proposes that NTIC is sufficient for a process to be conscious. Here, we highlights three scenarios that
-
-        First, a process is not informational closed leads to low NTIC (Eq.~\ref{eq:nticObjective2}, and, therefore, low conscious levels or no consciousness.
-In this case, the current states of the process are largely determined by its environment.
-
-        We highlight two scenarios that a process is functional, however, but unconscious.
-
-        \subsubsection*{Fail to meet the 1\lowercase{st} condition}
-            If a process fails to fulfil either of the two conditions, information remains unconscious.
-We first consider the scenario that a process fails to satisfy the first condition, i.e.
-the process fails to form high degree of NTIC.
-In the neural system many processes fall into this category.
-
-        	Considering the objectives of achieving NTIC (Eq.
-\ref{eq:nticObjective}), if a process is unable to maximise the mutual information between its past and future states ($I(Y_{t+1};Y_{t})$), it results in low NTIC.
-The failure to maximise the mutual information implies the past states of the process itself has little influence on its future states.
-In the meantime, if environmental information is able to flow into the process, the process can still produces functional outputs based on the current state of the environment accordingly.
-However, in this circumstance, the future state of the process is largely determined by the environmental states.
-That is, the process is not informationally closed (${J_{t}(E \rightarrow Y )} \not\approx 0$, Fig.~\ref{fig:reflexive}).
-
-            % or minimise $I(Y_{t+1};Y_{t}|E_{t})$
-
-            % If the future states of the system have strong mutual information with the current environmental states ($I(Y_{t+1};E_{t})$) but have weak mutual information with the current system states ($I(Y_{t+1};Y_{t})$), the informational closeness will be small.
+            \ac{OurTheory} proposes that NTIC is sufficient for a process to be conscious.
+Based on the definition of NTIC, we highlights two scenarios which lead low NTIC so that a process is unconscious.
+We additionally highlight the level of coarse-graining.
+            \ideaCallout{Need rewording}
+
+            % ============================================================================ %
+            %                                 Fail to be IC                                %
+            % ============================================================================ %
+            \subsubsection*{Fail to Form Informational Closure}
+                A process is not informationally closed leads to low levels of NTIC (Eq.~\ref{eq:nticObjective2}) and results in low or no consciousness.
+In this case, the current states of a process are largely depends on its environment states (see Fig.~\ref{fig:reflexive}) but little influenced by its past states.
+Reflexive behaviours \citep{casali2013theoretically} can be considered a classical example in this scenario.
+\ac{OurTheory} naturally explains why reflexive behaviours always do not involve voluntary conscious controls and operate unconsciously.
 
@@
         			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
-    			\caption{Reflexive Behaviours}
+        			\caption{
+        			    Reflexive behaviours happen between a process $Y$ and its environment $E$ which $Y$ interact with.
+The red nodes and arrows represent the major information flow in reflexive reactions.
+The internal state of the process $Y_t$ is largely dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$.
+Therefore, the process $Y$ is not informational closed.
+In consequence, $Y$ is unable to form high NTIC and, therefore, to have high conscious levels.
+        			    }
         			\label{fig:reflexive}
@@
 
-            In the neural system, this type of processes, for perception, shows the property that the perceptual processing mainly passively responds to the sensory inputs.
+        		The same principle can be applied to blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedure memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes.
+Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements without having any conscious perception about visual stimuli.
+We argue that action outputs of blindsight can be directly guided by sensory inputs through stimulus-response maps.
+The neural circuits are not informationally closed and, therefore, unconscious.
+Similarly, for procedure memory, the state transitions of action controls largely depends on the concurrent environmental states.
+This prevents the internal processes of procedure memory from informational closure and being conscious.
+
+                % In the neural system, this type of processes, for perception, shows the property that the perceptual processing mainly passively responds to the sensory inputs.
 For actions, this type of processes only produces "reflective-like" behaviours.
@@
 
-            The same principle can be applied to blindsight and procedure memory \needref{blindsight} which are often considered as unconscious processing.
+                % The same principle can be applied to blindsight and procedure memory \needref{blindsight} which are often considered as unconscious processing.
 Blindsight patients are able to track objects, avoid obstacles, and make above chance-level judgements without having any conscious perception about visual stimuli.
@@
 
-             This type of processing is similar to the model-free policy-based agents in the reinforcement learning framework.
+        %          This type of processing is similar to the model-free policy-based agents in the reinforcement learning framework.
 The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
-    		\begin{equation}
-    			\label{eq:PolicyBasedAgent}
-    			\begin{aligned}
-    			    \pi(A | S)=\operatorname{Pr}\left(A_{t}=a | S_{t}=s\right)
-    			\end{aligned}
-    		\end{equation}
-
-    		Our theory can explain why the patients with visual apperceptive agnosia (e.g., the famous case D.F.\cite{james2003ventral}) can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.
-The online visual information can be used to perform functional actions without forming an NTIC process.
-Our theory also explains why unconscious processes in this category often fail when a long delay periods is introduced in the tasks.
+        % 		\begin{equation}
+        % 			\label{eq:PolicyBasedAgent}
+        % 			\begin{aligned}
+        % 			    \pi(A | S)=\operatorname{Pr}\left(A_{t}=a | S_{t}=s\right)
+        % 			\end{aligned}
+        % 		\end{equation}
+
+                \ac{OurTheory} explains why the patients with visual apperceptive agnosia \citep{james2003ventral} can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.
+The online information from the visual inputs can be used to perform  functional actions without complete conscious perception of the visual targets.
+
+                % Our theory also explains why unconscious processes in this category often fail when a long delay periods is introduced in the tasks.
 Without self-predictive information in NTIC, the policies of motor outputs largely depends on the present environmental and sensory states implying that this type of processes often can only work online.
@@
 
-    		Finally, an interesting implication from our theory is that a pure feedforward neural network cannot be conscious because it is unable to maintain any form of memory so that there is no influence from the system past states to its future state.
-In contrast, with recurrent loops, a neural network is able to create information channels from its past to its future states and becomes capable of achieving NTIC.
-This result coincides with some theories of consciousness which emphasize the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
-    		% if more references are needed, check Eklund_2012_RECURRENT PROCESSING AND THE CONSCIOUSNESS.pdf
-    		However, we derive this conclusion from a more fundamental informational-related hypothesis indicating the more generalised principle behind it.
-
-        % ---------------------------------------------------------------------------- %
-        %                                Fail to meet 2                                %
-        % ---------------------------------------------------------------------------- %
-        \subsubsection*{Fail to meet the 2\lowercase{ed} condition}
+        		\ideaCallout{Mayeb can put in theory part}
+        		An implication from \ac{OurTheory} is that a pure feedforward network is incapable to be conscious due to a lack of any form of memory.
+Without memory, the network current states are entirely driven by network current inputs without any influence from its past states and, therefore, is incapable to be informationally closed.
+In contrast, a network with recurrent loops could keep information about its states.
+This forms an information channel between the past and the future states of the network and, thus, makes the network becomes capable of being informationally closed.
+This result coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
+
+        % 		However, we derive this conclusion from a more fundamental informational-related hypothesis indicating the more generalised principle behind it.
+
+            \subsubsection*{Encoded Information is Trivial}
+                Encoded information in a process is trivial, i.e.
+no mutual information between the system states and its environment states $I(Y_{t+1};E_{t})$ (Eq.~\ref{eq:nticObjective2}), could also lead low NTIC.
+This process is considered to be unconscious due to the low level of NTIC.
+This implies an isolated process which is simply informationally closed to its environment is not enough to be conscious.
+
+                This implies that \ac{OurTheory} provides a natural solution to the boundary problem of consciousness \citep{Raymont2006-RAYUOC}.
+Consider a NTIC process $Y$ and an isolated informationally closed process $\hat{Y}$ with trivial information.
+Adding $\hat{Y}$ to $Y$ can still keep informational closure, but, however, does not increase non-trivial information.
+
+    			\begin{equation}
+    			    \begin{aligned}
+                        I(Y,\hat{Y};E) & = H(Y,\hat{Y}) - H(Y,\hat{Y}|E) \\
+                                       & = H(Y) + H(\hat{Y}|Y) - (H(Y|E)+H(\hat{Y}|Y,E)) \\
+                                       & = H(Y) + H(\hat{Y}) - (H(Y|E)+H(\hat{Y})) \\
+                                       & = H(Y) - H(Y|E)\\
+                                       & = I(Y;E)				
+    				\end{aligned}
+    			\end{equation}
+
+                This indicates that isolated processes with trivial information do not contribute consciousness and should be outside the information boundary of the conscious processing.
+This result also implies that consciousness does not emerge from aggregating informationally closed processes with trivial information.
+
+            % \ideaCallout{Should I say this?}
+%             This implies that \ac{OurTheory} provides a natural solution to the boundary problem of consciousness \citep{Raymont2006-RAYUOC}.
+Consider a set of independent processes $Y=\{Y^1,...,Y^n\}$ with deterministic state transitions in a small universe.
+Each variable not only is informationally closed to other variables, they also share no mutual information.
+
+% 			\begin{equation}
+% 				\thickspace Y^i \bot Y^j, \quad \forall {i\neq j}
+% 			\end{equation}
+
+%             Now we randomly pick two variables and make group two variables s
+
+%             , therefore, unconscious. Next, we can select a two of the variables and compute NTIC between this subset and other variables.
+
+            \subsubsection*{Unsuitable Measurement scales }
+                \ac{OurTheory} proposes that human conscious process rests on a certain scale which forms NTIC.
+This implies the spatial and temporal scales of the physiological measurements are critical in the experiments aiming to finding neural correlates of consciousness (NCC).
+
+                % \subsubsection*{Fail t  o meet the 2\lowercase{ed} condition}
                 As mention above, information is level-dependent and can be virtually independent (closed) across different coarse-graining scales.
@@
 % ============================================================================ %
-	\section{Comparison with other theories}\label{sec:Comparison with other theories}
-	In this section, we compare our theory with other popular modern theories of consciousness.
+	\section{Comparison with other Relevant Theories of Consciousness}\label{sec:Comparison with other theories}
+	In this section, we \ac{OurTheory} with other relevant modern theories of consciousness.
 
@@
         % ---------------------------------------------------------------------------- %
+        \subsection{Multilevel views on consciousness and cognition}
+    		\ac{OurTheory} proposes that a conscious (NTIC) process only rest at a certain coarse-grained scale in the neural system.
+This suggests that the scales of coarse-graining is critical for searching for conscious processes.
+In previous research, a few multilevel views on consciousness have been (explicitly or implicitly) proposed.
+So far, to our knowledge, Pennartz's neurorepresentational theory (Neurorepresentationalism, \cite{pennartz2018consciousness,pennartz2015brain}) is the closest proposal in line with our multilevel view on consciousness.
+Similar to Neurorepresentationalism, the concept of levels \ac{OurTheory} is also relevant to Marr's level of analysis \citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}.
+    		However, \ac{OurTheory} suggests that coarse-graining is necessary only when the microscopic processes are stochastic (e.g.
+the neural system).
+An NTIC process can be formed in a noise-free deterministic system without coarse-graining.
+According to \ac{OurTheory}, this NTIC process is sufficient to be conscious.
+    		Another fundamental difference between \ac{OurTheory} and Neurorepresentationalism is that Neurorepresentationalism takes functionalist perspective and suggests consciousness should serve high-level world-modelling and makes a best guess about the interaction between the body and the environment.
+    		%Neurorepresentationalism also suggests conscious experience is associated with integrated representation for multimodal and situational information.
+    		However, \ac{OurTheory} is grounded by non-functional informational assumptions. Therefore, \ac{OurTheory} provides a more fundamental explanation for the scale problem of consciousness.
+
+    		Another proposal based on multilevel views is the Intermediate Level Theory of Consciousness \citep[ILT]{prinz2007intermediate, jackendoff1987consciousness}.
+ILT proposes that conscious experience is only associated with representations at intermediate levels of the sensory processing hierarchy (e.g., the 2.5D representation in terms of visual processing) rather than lower (e.g.
+pixel) or higher (e.g.
+abstract ) levels of the hierarchy.
+    		Here, we want to make a clear clarification that the "level" in \ac{OurTheory} refers to the levels of coarse-graining instead of the "level" for anatomy or information processing.
+It is important to note that the coarse-graining direction is not necessary aligned with the levels of anatomy or the information processing hierarchy in the neural system .
+Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example
+
+    		specific levels of representations in the hierarchy of sensory processing.
+ILT claims that consciousness only associates with the representation at intermediate levels (e.g., the 2.5D representation in terms of visual processing) rather than the ones at lower-level or higher-level.
+
+    		One fundamental difference between ILT and our theory is the definitions of the level.
+In our theory, level is within the context of coarse-graining.
+However, ILT focuses more on the levels in terms of anatomical direction (see fig \ref{fig:hierarchy}).
+As mentioned previously, we emphasise that we doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies.
+This leads to an important difference that the level of coarse-graining exists virtually.
+However, the level of cortical representation should be referred to neural substrates.
+Finally, different from ILT which suggests that some neural substrates responsible for the 2.5D computation are conscious, we predict that once information carried by coarse-grained variables is involved in the NTIC process, brain areas, not exclusively within 2.5D representation, should  co-vary with conscious contents.
 
@@
 Need better expression} anatomical sensory hierarchy in the neural system.
-Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.
+Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example
+
+        the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.
 Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.
@@
 
-		\subsection{Theories about multilevel views on consciousness and cognition}
-		Previously, similar to our theory, several multilevel views on consciousness and cognition have been proposed. We shortly discuss two theories relevant to our current proposal.
                 \subsubsection*{Level of Organisation \cite{wimsatt1994ontology}}
@@
 
-			\subsubsection*{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
-			    Our theory shares some close concepts with Pennartz's Neurorepresentationalism \citep{pennartz2018consciousness,pennartz2015brain}.
-Similar to Neurorepresentationalism, our framework is also close to Marr's original distinction between the levels of analysis \citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}.
-However, a fundamental difference between the two theories is that Neurorepresentationalism takes more functionalist point of view and suggests NCC should serve high-level world-modeling and makes a best guess about the interaction between the body and the environment.
-Neurorepresentationalism also suggests conscious experience is associated with integrated representation for multimodal and situational information.
-Out theory suggests that the association between the functions mentioned in Neurorepresentationalism is rooted in the more fundamental relationship between information and consciousness in which NTIC plays an important role.
+        % ---------------------------------------------------------------------------- %
+        %                                      IIT                                     %
+        % ---------------------------------------------------------------------------- %
+		\subsection{Integrated information theory}
+    		Integrated information theory (IIT) states that system's consciousness is determined by its causal properties.
+Consciousness is integrated information.
+As a computational theory of consciousness, the degree of discrimination and integration can be expressed in mathematical terms $\Phi$.
+Different from most of other scientific theory of consciousness, IIT asserts that the fundamental physical property associated with consciousness is causality.
+
+    		% -------------------------------- Similarity -------------------------------- %
+    		IIT and our theory shares common principles in many aspects.
+First common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness \needref{cite David Chalmers}.
+Therefore, both theories are capable of extrapolation and infer the states of consciousness in other systems beyond the human neural system.
+
+    		Second, both theories consider informational structure as the fundamental entities associated with the quality of conscious contents.
+IIT proposes that a "complex" which is defined as elements that generates a local maximum of integrated information as the core entity which determines the state space of subjective feeling (qualia space).
+In the current stage of our theory development, we have not proposed such sophisticated description of the mappting between informational structure and the qualia space.
+However, in line with this notion, we argue that the state space of an NTIC process determines the subjective experience possessed by the process.
+
+    		\ideaBox{Maybe synergy is the common part of the two theories }
+
+    		Even though both theories are based on informational properties of a process, predictions of the two theories can be very different.
+Taking the split brain cases as the example, when splitting a system into two parts, IIT suggests that each part can form a new complex.
+Therefore, splitting creates two new conscious entities.
+However, according to our theory, splitting a system may totally destroy the informational structure that created NTIC.
+This may lead to very small degree of NTIC in both hemispheres, thereby entirely destroying consciousness of this system.
+Notwithstanding, more simulation work is needed to thoroughly clarify how the two theories make same and different predictions in different contexts.
+Fortunately, due to the computational nature of the two theories, precise differences of predictions can be made from relatively simple toy model in the future work.
+
+    		% Hoel's theory\cite{hoel2016can}}
+    		Alongside with the main theoretical development of IIT, \cite{hoel2016can,hoel2013quantifying} discussed the scale-dependent causal structures using IIT as a measure of causal power at different scales.
+The result shows a qualitative similarity to our theory.
+The causal power can emerge at macroscopic levels of a system.
+This claim is consistent with our prediction in which processes at macroscopic levels can form more deterministic and predictive state transitions.
+We expect further mathematical and empirical analysis can reveal the relationship between \ac{OurTheory} and Hoel's analyses about the causal power at different scales in a system.
+
+            % =============== Internal simulation and self-modelling theory ============== %
+    		\subsection{Internal simulation and self-modelling theory}
+    		\idea{I will skip this section unless you think this is necessary.}
+
+        % ---------------------------------------------------------------------------- %
+        %                            Predictive Processing                             %
+        % ---------------------------------------------------------------------------- %
+		\subsection{Predictive Processing}
+    		Predictive processing is a powerful framework (PP) which integrates several influential ideas in the history of neuroscience including "perception as unconscious inference" from Helmholtz \citet{helmholtz1866concerning}, "analysis by synthesis", “predictive coding”, and "Bayesian brain hypothesis".
+This emerging theoretical framework of perception and brain function suggests that the neural system constantly generates predictions about incoming sensory signals and updates predictions based on prediction error between predictions and real sensory signals.
+According to PP, the neural system constantly performs unconscious statistical inference about hidden causes in the external environment.
+The perceptual contents are the "best guess" about the environment states including these hidden causes \citep{clark_2013, Hohwy2013}.
+Because it is well integrated with Bayesian brain hypothesis, the PP has been used to interpret conscious perception in many perceptual domain.
+\cite{Hohwy2013} \cite{SethPP2014}.
+
+    		%% The gaps between pp and consciousness
+    		PP is a powerful explanatory framework for diverse brain functions.
+However, to serve as a theory of consciousness, PP is still incomplete due to two theoretical gaps.
+First, there are enormous predictive mechanisms in the neural systems.
+It is  obvious that that not all the predictive information from these mechanisms is able to be part of conscious contents.
+Therefore, PP needs to explain the difference between conscious and unconscious predictive mechanisms.
+Second, if we closely look at a conscious predictive system, the only part can be consciously aware of is the result.
+Other details of the computation remain unconscious.
+PP also needs to explain how unconscious inferences is able to give rise to conscious results.
+In short, the two explanatory gaps prevent PP from been a complete theory of consciousness.
+
+    		Here, from more fundamental principles, we  argue that our theory is able to well fill the two gaps simply by considering the two conditions mentioned in section \ref{sec:Conscious versus Unconscious Processing}.
+
+    		First, predictive processes do not necessitate NTIC.
+A neural mechanisms is able to generate prediction does not guarantee it is an NTIC process.
+For example, an algorithm can take the current states of a target entity as the inputs and compute future states of the target.
+In this case, this algorithm can compute predictive information.
+However, the states of the internal variables are fully determined by the external input, implying that this algorithm is not informationally closed.
+We suggests that if a predictive process is not an NTIC process, predictions from this process will not be able to show in conscious contents (i.e., fail to meet the 1\lowercase{st} condition in section \ref{sec:Conscious versus Unconscious Processing}).
+In contrast, predictive information in the NTIC process is conscious and makes the process form information closure.
+
+    		Second, as mentioned in section \ref{sec:Conscious versus Unconscious Processing}, if a process is not at the coarse-grained level achieving NTIC, this process will not be conscious (Fail to meet the 2\lowercase{ed} condition).
+We have provided an example in section \ref{sec:Conscious versus Unconscious Processing} in which computation can be implemented at microscopic levels.
+However, if the coarse-grained result of the computation is included in the macroscopic NTIC process, only the result rather than the process itself can be consciously aware of.
+Therefore, we predict that the statistical inferences under PP are implemented in microscopic levels.
+The NTIC process is ignorant to the detail information of their computations.
+
+            Altogether, our theory provides more fundamental principles and explanations about the relationship between predictive mechanisms and consciousness.
+Moreover, the fundamental principles allow us to make more precise predictions about which types of PP should or should not be conscious.
+Therefore, our theory has stronger falsifiability and predictability beyond PP on consciousness research.
+
+        % ---------------------------------------------------------------------------- %
+        %                           Sensorimotor contingency                           %
+        % ---------------------------------------------------------------------------- %
+		\subsection{Sensorimotor contingency}
+    		Sensorimotor contingency (SMC) theory of consciousness is proposed to account for conscious perception.
+It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}.
+The theory radically rejects the view that conscious content is associated with information encoded in internal representations in the neural system.
+Rather, the quality of conscious perception depends on agents' mastery of SMCs.
+SMC emphasises that the interaction between a system (the neural system) and its environment is crucial to form any specific form of conscious experience.
+
+    	    Our theory in general rejects this proposal based on the fundamental assumptions of SMC.As we mentioned in \ref{sec:Conscious versus Unconscious Processing}, a process directly maps the sensory state space to the action space should not be able to form NTIC.
+Because learning of contingencies between sensory input and action output doesn't guarantee to form any NTIC process, our theory predicts that sensorimotor contingency is neither a necessary nor a sufficient condition for conscious experience.
+In fact, with extensive practice on a sensorimotor task with a fixed contingency, the task usually can be gradually performed unconsciously \needref{}.
+We believe that the neural system has established a process to directly map sensory evidence to action selection, and therefore, decrease the level of NTIC which against the basic assumption of SMC.
+
+    	    Nevertheless, our theory does appreciate the notion that interactions between agents and environment is crucial to shape specific types of conscious experience.
+This is because, for an agent to form an NTIC process with action output, the process needs to encode how agents' actions influence state transitions in the environment.
+Therefore, information of interaction should be encoded in the NTIC process and also determines the state of NTIC which associates a particular conscious content.
+
+            Finally, a new version of SMC theory, Predictive Processing of SensoriMotor Contingencies (PPSMC), proposed by \cite{seth2014predictive, seth2015presence} makes some promising progress.
+PPSMC combines SMC and the predictive processing (see the next section) framework together and emphasises the importance of action counterfactual (i.e.
+the alternative and potential actions that an agent can perform) to conscious experience.
+We believe that the critical advance from SMC to PPSMC is to acknowledge the generative models for computing counterfactuals.
+The existence of generative models is the prerequisite equipped by the agents.
+So far, what PPSMC claims is deviating from simple $S\rightarrow{}R$ mappings and links the predictive information to consciousness.
+We argue that if predictive information for the computation of counterfactual is involved in the NTIC process, PPSMC will be compatable to our theory and may have strong explanatory power on some special conscious experience.
+\todo{Need a better ending}
 
@@
         % ---------------------------------------------------------------------------- %
-		\subsection{First-order theories}
-            The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}.
+% 		\subsection{First-order theories}
+            % The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}.
 The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
-            First-order theories suggests that phenomenal consciousness is associated with fine-grained contents for the first-order processes.
+            % First-order theories suggests that phenomenal consciousness is associated with fine-grained contents for the first-order processes.
 Different from the first-order theories, our theory suggests that, whether the early sensory activities show in the conscious content, it depends on information encoded in the early sensory areas is recruited in the NTIC process at the macroscopic level or not.
@@
         % ---------------------------------------------------------------------------- %
-		\subsection{Higher Order Thought theory of consciousness}
-		    \ideaBox{Okay, I don't know how to deal with HOT now. I don't understand it at all}
-		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations which represent agents as being in particular internal states \citep{lau2011empirical}.
+% 		\subsection{Higher Order Thought theory of consciousness}
+% 		    \ideaBox{Okay, I don't know how to deal with HOT now. I don't understand it at all}
+% 		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations which represent agents as being in particular internal states \citep{lau2011empirical}.
 First-order processing needs to be observed or represented by a higher-order observer to become conscious.
 
-		    Meta-cognition is also associated with many conscious cognitive function.
+% 		    Meta-cognition is also associated with many conscious cognitive function.
 However, we propose a new perspective and indicate that HOT may be a misunderstanding \critical{Very bad writing.
@@
 
-		    This may be the result of neural coarse-graining. Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it.
-
-		    Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.
+% 		    This may be the result of neural coarse-graining. Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it.
+
+% 		    Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.
 It is true that the neural system does create  meta-representation to represent xxx\needref{Maybe come studies about confidence represenatation}.
@@
 
-		    Moreover, the predictive information in NTIC is critical for other systems to build forward models for a wild range of tasks.
+% 		    Moreover, the predictive information in NTIC is critical for other systems to build forward models for a wild range of tasks.
 Therefore, most of the high level cognition can utilise the state of informational closure.
@@
 
-        % ---------------------------------------------------------------------------- %
-        %                           Sensorimotor contingency                           %
-        % ---------------------------------------------------------------------------- %
-		\subsection{Sensorimotor contingency}
-		Sensorimotor contingency (SMC) theory of consciousness is proposed to account for conscious perception.
-It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}.
-The theory radically rejects the view that conscious content is associated with information encoded in internal representations in the neural system.
-Rather, the quality of conscious perception depends on agents' mastery of SMCs.
-SMC emphasises that the interaction between a system (the neural system) and its environment is crucial to form any specific form of conscious experience.
-
-	    Our theory in general rejects this proposal based on the fundamental assumptions of SMC.As we mentioned in \ref{sec:Conscious versus Unconscious Processing}, a process directly maps the sensory state space to the action space should not be able to form NTIC.
-Because learning of contingencies between sensory input and action output doesn't guarantee to form any NTIC process, our theory predicts that sensorimotor contingency is neither a necessary nor a sufficient condition for conscious experience.
-In fact, with extensive practice on a sensorimotor task with a fixed contingency, the task usually can be gradually performed unconsciously \needref{}.
-We believe that the neural system has established a process to directly map sensory evidence to action selection, and therefore, decrease the level of NTIC which against the basic assumption of SMC.
-
-	    Nevertheless, our theory does appreciate the notion that interactions between agents and environment is crucial to shape specific types of conscious experience.
-This is because, for an agent to form an NTIC process with action output, the process needs to encode how agents' actions influence state transitions in the environment.
-Therefore, information of interaction should be encoded in the NTIC process and also determines the state of NTIC which associates a particular conscious content.
-
-        Finally, a new version of SMC theory, Predictive Processing of SensoriMotor Contingencies (PPSMC), proposed by \cite{seth2014predictive, seth2015presence} makes some promising progress.
-PPSMC combines SMC and the predictive processing (see the next section) framework together and emphasises the importance of action counterfactual (i.e.
-the alternative and potential actions that an agent can perform) to conscious experience.
-We believe that the critical advance from SMC to PPSMC is to acknowledge the generative models for computing counterfactuals.
-The existence of generative models is the prerequisite equipped by the agents.
-So far, what PPSMC claims is deviating from simple $S\rightarrow{}R$ mappings and links the predictive information to consciousness.
-We argue that if predictive information for the computation of counterfactual is involved in the NTIC process, PPSMC will be compatable to our theory and may have strong explanatory power on some special conscious experience.
-\todo{Need a better ending}
-
-        % ---------------------------------------------------------------------------- %
-        %                            Predictive Processing                             %
-        % ---------------------------------------------------------------------------- %
-		\subsection{Predictive Processing}
-    		Predictive processing is a powerful framework (PP) which integrates several influential ideas in the history of neuroscience including "perception as unconscious inference" from Helmholtz \citet{helmholtz1866concerning}, "analysis by synthesis", “predictive coding”, and "Bayesian brain hypothesis".
-This emerging theoretical framework of perception and brain function suggests that the neural system constantly generates predictions about incoming sensory signals and updates predictions based on prediction error between predictions and real sensory signals.
-According to PP, the neural system constantly performs unconscious statistical inference about hidden causes in the external environment.
-The perceptual contents are the "best guess" about the environment states including these hidden causes \citep{clark_2013, Hohwy2013}.
-Because it is well integrated with Bayesian brain hypothesis, the PP has been used to interpret conscious perception in many perceptual domain.
-\cite{Hohwy2013} \cite{SethPP2014}.
-
-    		%% The gaps between pp and consciousness
-    		PP is a powerful explanatory framework for diverse brain functions.
-However, to serve as a theory of consciousness, PP is still incomplete due to two theoretical gaps.
-First, there are enormous predictive mechanisms in the neural systems.
-It is  obvious that that not all the predictive information from these mechanisms is able to be part of conscious contents.
-Therefore, PP needs to explain the difference between conscious and unconscious predictive mechanisms.
-Second, if we closely look at a conscious predictive system, the only part can be consciously aware of is the result.
-Other details of the computation remain unconscious.
-PP also needs to explain how unconscious inferences is able to give rise to conscious results.
-In short, the two explanatory gaps prevent PP from been a complete theory of consciousness.
-
-    		Here, from more fundamental principles, we  argue that our theory is able to well fill the two gaps simply by considering the two conditions mentioned in section \ref{sec:Conscious versus Unconscious Processing}.
-
-    		First, predictive processes do not necessitate NTIC.
-A neural mechanisms is able to generate prediction does not guarantee it is an NTIC process.
-For example, an algorithm can take the current states of a target entity as the inputs and compute future states of the target.
-In this case, this algorithm can compute predictive information.
-However, the states of the internal variables are fully determined by the external input, implying that this algorithm is not informationally closed.
-We suggests that if a predictive process is not an NTIC process, predictions from this process will not be able to show in conscious contents (i.e., fail to meet the 1\lowercase{st} condition in section \ref{sec:Conscious versus Unconscious Processing}).
-In contrast, predictive information in the NTIC process is conscious and makes the process form information closure.
-
-    		Second, as mentioned in section \ref{sec:Conscious versus Unconscious Processing}, if a process is not at the coarse-grained level achieving NTIC, this process will not be conscious (Fail to meet the 2\lowercase{ed} condition).
-We have provided an example in section \ref{sec:Conscious versus Unconscious Processing} in which computation can be implemented at microscopic levels.
-However, if the coarse-grained result of the computation is included in the macroscopic NTIC process, only the result rather than the process itself can be consciously aware of.
-Therefore, we predict that the statistical inferences under PP are implemented in microscopic levels.
-The NTIC process is ignorant to the detail information of their computations.
-
-            Altogether, our theory provides more fundamental principles and explanations about the relationship between predictive mechanisms and consciousness.
-Moreover, the fundamental principles allow us to make more precise predictions about which types of PP should or should not be conscious.
-Therefore, our theory has stronger falsifiability and predictability beyond PP on consciousness research.
-
-        % ---------------------------------------------------------------------------- %
-        %                                      IIT                                     %
-        % ---------------------------------------------------------------------------- %
-		\subsection{Integrated information theory}
-		Integrated information theory (IIT) states that system's consciousness is determined by its causal properties.
-Consciousness is integrated information.
-As a computational theory of consciousness, the degree of discrimination and integration can be expressed in mathematical terms $\Phi$.
-Different from most of other scientific theory of consciousness, IIT asserts that the fundamental physical property associated with consciousness is causality.
-
-		% -------------------------------- Similarity -------------------------------- %
-		IIT and our theory shares common principles in many aspects.
-First common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness \needref{cite David Chalmers}.
-Therefore, both theories are capable of extrapolation and infer the states of consciousness in other systems beyond the human neural system.
-
-		Second, both theories consider informational structure as the fundamental entities associated with the quality of conscious contents.
-IIT proposes that a "complex" which is defined as elements that generates a local maximum of integrated information as the core entity which determines the state space of subjective feeling (qualia space).
-In the current stage of our theory development, we have not proposed such sophisticated description of the mappting between informational structure and the qualia space.
-However, in line with this notion, we argue that the state space of an NTIC process determines the subjective experience possessed by the process.
-
-		\ideaBox{Maybe synergy is the common part of the two theories }
-
-		Even though both theories are based on informational properties of a process, predictions of the two theories can be very different.
-Taking the split brain cases as the example, when splitting a system into two parts, IIT suggests that each part can form a new complex.
-Therefore, splitting creates two new conscious entities.
-However, according to our theory, splitting a system may totally destroy the informational structure that created NTIC.
-This may lead to very small degree of NTIC in both hemispheres, thereby entirely destroying consciousness of this system.
-Notwithstanding, more simulation work is needed to thoroughly clarify how the two theories make same and different predictions in different contexts.
-Fortunately, due to the computational nature of the two theories, precise differences of predictions can be made from relatively simple toy model in the future work.
-
-		% Hoel's theory\cite{hoel2016can}}
-		Alongside with the main theoretical development of IIT, \cite{hoel2016can,hoel2013quantifying} discussed the scale-dependent causal structures using IIT as a measure of causal power at different scales.
-The result shows a qualitative similarity to our theory.
-The causal power can emerge at macroscopic levels of a system.
-This claim is consistent with our prediction in which processes at macroscopic levels can form more deterministic and predictive state transitions.
-We expect further mathematical and empirical analysis can reveal the relationship between \ac{OurTheory} and Hoel's analyses about the causal power at different scales in a system.
-
-        % =============== Internal simulation and self-modelling theory ============== %
-		\subsection{Internal simulation and self-modelling theory}
-		\idea{I will skip this section unless you think this is necessary.}
-
 % ============================================================================ %
@@
 
-        % multi NTIC problem
+        % Identity problem
         Our theory is not complete yet. 

### 2019-09-20 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 	\begin{abstract}
-		Neural systems process information through different levels of organisation in a hierarchical manner.
-Information at lower levels is finer-grained and can be coarse-grained for higher level computation.
-However, one is aware of information processed only at specific levels.
-Theorists have addressed this issue.
-For example, the intermediate level theory of consciousness suggests that the intermediate level seems to be privileged with respect to consciousness.
-It is true that we do not experience information processed by individual neurons which is always highly stochastic noisy.
-In addition, we have no conscious experience from interpersonal activities despite massive interactions among individuals.
-Instead, neurophysiological evidence has been showing that conscious experience tends to co-vary with information encoded in coarse-grained neural states such as neural population codes.
-We argue that the content of consciousness is determined by neural variables that obey informational closure and that other brain processes remain unconscious.
-Out theory based on concise assumptions and propose quantitative definitions using information theorem for both conscious content and conscious level.
+		Information processing in neural systems can be described and analysed at multiple spatiotemporal scales.
+Generally, information at lower levels is more fine-grained and can be coarse-grained in higher levels.
+However, information processed only at specific levels seems to be available for conscious awareness.
+We do not have direct experience of information available at the level of individual neurons, which is noisy and highly stochastic.
+Neither do we have experience of more macro-level interactions such as interpersonal communications.
+Neurophysiological evidence suggests that conscious experiences co-vary with information encoded in coarse-grained neural states such as the firing pattern of a population of neurons.
+In this article, we assume that conscious experience is confined due to informational closure from conscious processing to other coarse-grained levels.
+From this and three additional assumptions, we propose a new computational theory of consciousness: \ac{OurTheory}.
+\ac{OurTheory} proposes new quantitative definitions of both conscious content and conscious level.
+With the parsimonious assumptions and simple propositions, \ac{OurTheory} provides explanations and predictions of phenomena associated with consciousness.
+The implications of \ac{OurTheory} naturally reconciles issues in many existing theories of consciousness and provides explanations for many of our intuitions about consciousness.
+Most importantly, \ac{OurTheory} indicates that information is the common language bridging consciousness and physical reality.
 
@@
 
-% ============================================================================ %
-    \newpage
-    \section*{Not decided terminology}
-        \begin{ants}
-            @ information * in the NTIC process
-            @ Full and short name of this theory
-            @ core "?" (entity) for conscious content 
-            @ our theory? framework? proposal? 
-            @ system? process?
-            @ variable? node? element? member?
-            @ TODO:
-                @@ Change coarse-graining function to "aggregation function"
-            @ Decided
-                @@ "form" NTIC
-            @ Replacement
-                @ correlate -> ?
-                @ information processing -> ?
-                @ achieve -> form
-        \end{ants}
-
-% ============================================================================ %
-    \newpage
-    \section*{Discussion points}
-        \begin{ants}
-            @ I can understand that an NTIC process must be coarse-graining of the "full process" (Environment + NTIC or we say {E, Y}).
-But I am still thinking is this the same as my original idea that variables forming the NTIC process are coarse-grained from microscopic variables?
-This is very critical to how we present this paper.
-
-        \end{ants}
+%         \end{ants}
 
@@
 binary) process can represent, suggesting that the state space of conscious experience is much larger than what a single overly coarse-grained binary variable can represent.
-These facts suggest that conscious processes are scale dependent.
+These facts suggest that conscious processes occur at a particular scale.
+We currently lack a theory to identify the scale which conscious processes correspond to.
 We refer to this notion as \textbf{the scale problem of consciousness} (Fig.~\ref{fig:scaleproblem}).
@@
 		In this article, we propose a new information-based theory of consciousness, called \ac{OurTheory}.
-We argue that every process with a high degree of not-trivial information closure (NTIC) has consciousness.
+We argue that every process with a high degree of non-trivial information closure (NTIC) has consciousness.
 This means that the state of such a process corresponds one-to-one to conscious content.\footnote{In the following IC stands for "informational closure" or "informationally closed" and NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}.
@@
 
-		In the following, we first introduce non-trivial informational closure and its importance to information processing for human scale agents (Sec.\ref{sec:Non-trivial informational closure}).
+		In the following, we first introduce non-trivial informational closure and argue for its importance to information processing for human scale agents (Sec.\ref{sec:Non-trivial informational closure}).
 We next argue that through coarse-graining the neural system can form a high degree of NTIC at a specific coarse-grained level (Sec.\ref{sec:Neural coarse-graining}).
@@
 We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies (Sec.\ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (Sec.\ref{sec:Comparison with other theories}).
-Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from this theory to the current consciousness science (Sec.\ref{sec:Limitation and Future work}).
+Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from \ac{OurTheory} to the current consciousness science (Sec.\ref{sec:Limitation and Future work}).
 
@@
 				\end{figure}
-				\todo{Modify this figure}
 
@@
 			This implies the system contains in itself all the information about its own future and the self-predictive information is gained from the information about the environment.
-Therefore, to form NTIC, the system can internalise and synchronise the dynamics of the environment, i.e.
+Therefore, to form NTIC, the system can internalise and synchronise with the dynamics of the environment, i.e.
 modelling the environment.
@@
 		%% stochasticity at microscopic levels
-		Despite the evolutionary advantage of having NTIC processes in a system, however, to create NTIC with a highly stochastic process is challenging.
+		Despite evolutionary advantage of having NTIC processes in a system, however, the formation of NTIC witha  highly stochastic process is challenging.
 NTIC requires the predictability of the system state and is therefore impeded by noise in the system.
-Information processing at the microscopic levels (the cellular levels) in neural systems suffer from multiple environmental noise sources throughout, including sensory, cellular, electrical, and synaptic noises.
-For example, neurons have large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
-
-        % 		Furthermore, environmental information is always only partially observable to individual sensors and neurons which only receive little amount of information from the environment.
-Therefore, information about the environment state at the cellular level is difficult to represent at the cellular level.
-It is implausible to construct NTIC processes at microscopic levels.
+Information processing at the microscopic levels (the cellular levels) in neural systems suffer from multiple environmental noise sources such as sensor, cellular, electrical, and synaptic noises.
+For example, neurons exhibit large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
 
         %% Our argument
-		However, we argue that, neural systems can form NTIC at certain macroscopic levels through coarse-graining microscopic neural states.
+		However, we argue that, neural systems can form NTIC at certain macroscopic levels through coarse-graining of microscopic neural states.
 Coarse-graining refers to many-to-one functions which aggregate microscopic states to a macroscopic state.
-In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}.
+In other words, a number of different micro-states correspond to the same value of the macro-variable \citep{price2007causation}.
 Neural systems, therefore, can form more stable and deterministic state transitions and be more capable of forming NTIC processes at certain coarse-grained macroscopic levels.
 
-		Indeed, empirical evidence has been showing that coarse-graining is a common coding strategy against ubiquitous stochasticity at microscopic levels of the the neural system.
+		Indeed, empirical evidence suggests that coarse-graining is a common coding strategy to establish robustness against noise at microscopic levels of the the neural system.
 For instance, the inter-spike intervals of individual neurons are stochastic.
-This implies that states of individual neurons are incapable of encoding and representing stable information.
-However, the spiking rate, i.e.
-the average spike counts in a given time interval, shows astonishing stability and robustness against noise causing the variation of inter-spike intervals.
-Using this temporal coarse-graining strategy, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}, individual neurons can encode stimulus intensity by increasing or decreasing firing rate \citep{kandel2000principles}.
+This implies that the state of individual neurons cannot be used for encoding and representing stable information.
+However, the firing rate, i.e.
+the average spike counts over a given time interval, is more stable and robust against noise such as the variability in inter-spike intervals.
+Using this temporal coarse-graining strategy, known as the rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}, neurons can encode stimulus intensity by increasing or decreasing the firing rate \citep{kandel2000principles}.
 \citep{stein2005neuronal}.
-The robustness of the rate coding is direct consequence of the many to one map used.
+The robustness of the rate coding is a direct consequence of the many to one mapping (i.e., coarse-graining).
 
@@
 In this coding scheme, information is encoded by activation patterns of a set of neurons (a neuron population).
-To reduce the influence noise on scholastic state transitions of individual neurons, many states for a neuron population map to the same information content.
-Therefore, stable representation can be formed through coarse-graining a high dimensional state space of a neuron population to a low dimensional state space of encoded contents \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
+In the population coding scheme, many states for a neuron population map to the same information content, thereby reducing the influence of noise in individual neurons.
+That is, stable representations can be formed through coarse-graining a high dimensional state space of a neuron population to a low dimensional state space of encoded contents \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
 Therefore, individual neuron states (the microscopic level) are not informative about the encoded contents at the population level (the macroscopic level).
-Instead, coarse-grained variables are better entities to encode information and allow the neural system to ignore noisy causal interaction at the fine-grained level of description \citep{Woodward2007-WOOCWA}.
-
-        The two examples show that coding schemes through coarse-graining could provides a stochastic system, e.g.
-the neural system, to form more stable and deterministic macroscopic processes to encode and process information reliably.
+Instead, coarse-grained variables are better substrates for stably encoding information and allow the neural system to ignore noisy interactions at the fine-grained level \citep{Woodward2007-WOOCWA}.
+
+        These two examples show that the known coding schemes can be viewed as coarse-graining, and provide stochastic neural systems with the ability to form more stable and deterministic macroscopic processes for encoding and processing information reliably.
 We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic levels.
-Based on this argument, we proposes our theory of consciousness in the next section.
+Based on the merit of coarse-graining in neural systems, We propose a theory of consciousness in the next section.
 
@@
 % ============================================================================ %
-% Boundary problem 1: Add another NTIC process
-% 1. Ignore it / maybe next paper
-% 2. Acknowledge the problem but we don't have solution now
-% 3. Write down our comment
-
-% Micro/Macro and Environment point of views
-%   Whether a process can be a part of the environment
-% ============================================================================ %
-
-% ============================================================================ %
 %               A neural coarse graining theory of consciousness               %
 % ============================================================================ %
-	\section{A neural coarse graining theory of consciousness}\label{sec:OurTheory}
+	\section{\acf{OurTheory}}\label{sec:OurTheory}
 
         In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory}.
-We also discuss the implications of \ac{OurTheory} in Sec.~\ref{sec:cl}, \ref{sec:cc}, and \ref{sec:reconcile}.
-
-        We argue that the existence of an NTIC process within a system is sufficient for information processing to be conscious.
-
-        In what follows, we will first establish three assumptions on which this theory depends. Then, we will develop the propositions in detail.
+In \ac{OurTheory}, we claim that being NTIC is sufficient for a process to be conscious.
+The implications of \ac{OurTheory} will be discussed in Sec.~\ref{sec:cl}, \ref{sec:cc}, and \ref{sec:reconcile}.
+In what follows, we will first establish four assumptions on which \ac{OurTheory} depends, and then develop the specific propositions of \ac{OurTheory} in detail.
 
@@
 
+            \needhelp{@Martin, if you think it's better to have a proof for this and if you don't mind, you can help me to write the proof here or create an appendix section and put it there.
+If you have no time, I can also do this.}
 		\begin{equation}
@@
 
-            First, to form high level of NTIC, one can increase the mutual information $I(Y_{t+1};Y_{t})$ between the current internal state $Y_t$ and the future internal state $Y_{t+1}$.
+            First, to form a high level of NTIC, one can increase the mutual information $I(Y_{t+1};Y_{t})$ between the current internal state $Y_t$ and the future internal state $Y_{t+1}$.
 In other words, conscious levels are associated with the degree of self-predictive information.
@@
 
-            This implies that a high NTIC process should have a rich dynamic and concurrently maintain self-productiveness overtime.
-Another implication is that a complex systems can potentially reach higher levels of consciousness due to a larger information capacity to achieve higher mutual information.
-This outcome is consistent with a common intuition that conscious levels are associated with the degrees of complexity of systems.
+            This implies that a highly NTIC process must have rich dynamics with self-predictability over time.
+Another implication is that complex systems can potentially attain a higher level of consciousness due to the larger information capacity needed to attain high mutual information.
+This outcome is consistent with the common intuition that conscious levels are associated with the degree of complexity of the system.
 
     	    Second, one can minimise the conditional mutual information $I(Y_{t+1};Y_{t}|E_{t})$ to increase the level of NTIC.
-This quantity suggests that conscious level increases with the level of information about the environment state $E_t$ that the NTIC process encodes in its own state $Y_t$.
-An important implication is that a NTIC possessed by an agent which interacts with and adapts to a complex environment should have a higher level of NTIC than one possessed by another agent which lives and adapts to a simple environment.
-In other words, the environmental complexity is associated with conscious levels of NTIC processes.
+This quantity suggests that conscious level increases with the amount of information about the environment state $E_t$ that the NTIC process encodes in its own state $Y_t$.
+An important implication is that agents interacting with a complex environment have the chance to build a higher level of NTIC within their systems than those living in a simple environment.
+In other words, the level of consciousness is constrained by environmental complexity.
 
@@
     		It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
-We saw above that not coarse-graining enough and therefore considering processes that are too microscopic leads to low values of NTIC.
-However, if the macroscopic variable is overly coarse-grained the system states can result in low degrees of NTIC.
-For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus looses the self and environmental predictive power.
-\ac{OurTheory}, therefore, argues that only processes at a certain level of coarse-graining in the neural system can reach high level of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
-As a result, there exists a certain level of coarse-graining which has a maximal conscious level within the neural system.
+We saw above that not sufficiently coarse-grained variables have low values of NTIC.
+On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC.
+For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.
+Therefor, only processes at a certain level of coarse-graining in the neural system can form a high degree of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
+\ac{OurTheory} indicates that consciousness occurs at the intermediate level of coarse-graining where the maximal NTIC is formed within the neural system.
 
@@
 
-            \ideaBox{About Human Scale}
-            Finally, which coarse-grained level can form high NTIC? 
-            agent-scale operation
-            At the physical scale which human being interact with, the environmental dynamics is nearly deterministic following the laws of classical physics.
+            % Finally, which coarse-grained level can form high NTIC? 
+            % agent-scale operation
+            % At the physical scale which human being interact with, the environmental dynamics is nearly deterministic following the laws of classical physics.
 It gives agents interact at this physical scale great advantages if the agents can build NTIC process internally.
@@
 
-            %% Link to consciousness
-            At the physical scale which human beings live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
+            % %% Link to consciousness
+            % At the physical scale which human beings live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
 This suggests that information in the environment is nearly closed at the right spatio-temporal scale.
@@
     	    % richness 
-    		\ac{OurTheory} proposes that conscious contents correspond to states of NTIC processes (Eq.~\ref{eq:cContent}).
-This implies that the size of the state space of a NTIC process is associated with the richness of conscious contents that the process can potentially have.
+    		\ac{OurTheory} proposes that conscious contents correspond to the states of NTIC processes (Eq.~\ref{eq:cContent}).
+This implies that the size of the state space of an NTIC process is associated with the richness of conscious contents that the process can potentially have.
 Therefore, a complex NTIC process with a high dimensional state space can have richer conscious experience than a simple NTIC process can have.
-This outcome is consistent with a the intuition that the richness of conscious contents is associated with the complexity of a system.
+This outcome is consistent with the intuition that the richness of conscious contents is associated with the complexity of a system.
 
@@
 This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.
-This implication fit well with mental simulation theory of consciousness, predictive processing perspective of consciousness, and information generation theory of consciousness \needref{need three}.
-Note that \ac{OurTheory} doesn't assume that generative models are necessary.
+This implication fit well with some other theories of consciousness (for example, world simulation metaphor ~\citep{revonsuo2006inner}).
+Note that \ac{OurTheory} doesn't assume that generative models are necessary for consciousness.
 The implication a natural consequence based on our proposition.
 
-            Finally, due to a coarse-graining is a many to one map from microscopic to macroscopic scales, our theory implies multiple realisation thesis of consciousness\needref{multiple realisation} which suggests different physical implementation can map to the same conscious experience.
+            Finally, a coarse-graining is a many to one map from microscopic to macroscopic states and \ac{OurTheory} proposes that conscious contents $C_{t}^{Content}$ is the state of the NTIC process $Y_t$.
+Therefore, \ac{OurTheory} implies multiple realisation thesis of consciousness \citep{putnam1967psychological,bechtel1999multiple} which suggests that different physical implementations could map to the same conscious experience.
 
@@
 	    \subsection{Reconciling the levels and contents of consciousness}\label{sec:reconcile}
-    	    Segregation of conscious levels and conscious contents raises a debate \citep{bayne2016there, Fazekas2016}.
-In \ac{OurTheory} conscious levels and conscious contents are just two different properties of NTIC processes, and, therefore, naturally reconciles the two aspects of consciousness.
-To form high NTIC, a NTIC process needs to have a large and potentially high state space which guarantees rich and high dimensional information in conscious contents.
-Therefore, this framework well integrates the two key but debated concepts in consciousness research
-
-    	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that the the size of the state space and information entropy $H(Y)$ of a NTIC process are associated with both conscious levels and conscious contents.
-To reach high NTIC, a process needs to have a large state space and high information entropy which guarantee rich conscious contents and also the capacity of predictive information of the system (Eq.~\ref{eq:nticObjective}).
+    	    While it is useful to distinguish the notion of the  levels and contents of consciousness, whether they can be clearly dissociated has been a matter of debate \citep{bayne2016there, Fazekas2016}.
+In \ac{OurTheory}, conscious levels and conscious contents are just two different properties of NTIC processes, and, therefore, naturally reconciles the two aspects of consciousness.
+In an NTIC process with a large state space, conscious contents consist of rich and high dimensional information.
+Therefore, this framework integrates the levels and the contents of consciousness in a coherent fashion by providing explicit formal definitions of the two notions.
+
+    	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the entropy $H(Y)$ of an NTIC process, and therefore the size of the state space.
+To form a high degree of NTIC for rich conscious contents, the process needs to have a large state space and also the capacity of predictive information   (Eq.~\ref{eq:nticObjective}).
     	    \ac{OurTheory} therefore explains why in normal physiological states conscious levels and conscious contents are positively correlated \citep{laureys2005neural}.
@@
 	\section{Conscious versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
-	    In this section, we show how our theory can make predictions about what processes are conscious and what are unconscious.
+	    In this section, we show how \ac{OurTheory} can make predictions about what processes are conscious and what are unconscious.
+\ac{OurTheory} is constructed using information theory.
+Therefore, \ac{OurTheory} can provide predictions based on the mathematical definitions.
+In the end of this section, we discuss a critical implication of \ac{OurTheory} for neuroscience research on consciousness.
 
@@
         \subsection{Unconscious Processing}
-            \ac{OurTheory} proposes that NTIC is sufficient for a process to be conscious.
-Based on the definition of NTIC, we highlights two scenarios which lead low NTIC so that a process is unconscious.
-We additionally highlight the level of coarse-graining.
-            \ideaCallout{Need rewording}
-
-            % ============================================================================ %
-            %                                 Fail to be IC                                %
-            % ============================================================================ %
-            \subsubsection*{Fail to Form Informational Closure}
-                A process is not informationally closed leads to low levels of NTIC (Eq.~\ref{eq:nticObjective2}) and results in low or no consciousness.
-In this case, the current states of a process are largely depends on its environment states (see Fig.~\ref{fig:reflexive}) but little influenced by its past states.
-Reflexive behaviours \citep{casali2013theoretically} can be considered a classical example in this scenario.
-\ac{OurTheory} naturally explains why reflexive behaviours always do not involve voluntary conscious controls and operate unconsciously.
+            In this section, we highlight two scenarios in which the degree of NTIC is rendered low for a process, and thereby making the process unconscious.
+
+            \subsubsection*{Informational is not Closed}\label{sec:reflexive}
+                If a process is not informationally closed, the degree of NTIC is low (Eq.~\ref{eq:nticObjective2}) resulting in low or no consciousness.
+In such cases, the current state of a process depends primarily on the environment state (see Fig.~\ref{fig:reflexive}), but receives little influence from its past state.
+Reflexive behaviours \citep{casali2013theoretically} can be considered an example of this scenario.
+In \ac{OurTheory}, if we can view reflexive behaviours as situations in which the internal state $Y_t$, which triggers reflexive action, is determined by the environment state $E_{t-1}$ overruling the influences from its own past $Y_{t-1}$.
+Such interpretation of reflexive behaviour from the viewpoint of \ac{OurTheory} naturally explains why reflexes do not involve conscious experience of external stimuli.
 
@@
         			\caption{
-        			    Reflexive behaviours happen between a process $Y$ and its environment $E$ which $Y$ interact with.
-The red nodes and arrows represent the major information flow in reflexive reactions.
-The internal state of the process $Y_t$ is largely dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$.
+        			    A diagram depicting the information flow in reflexive behaviours (shown by the red nodes and arrows) happening through the interaction between a process $Y$ and its environment $E$.
+In such situations, the internal state $Y_t$ is mostly dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$.
 Therefore, the process $Y$ is not informational closed.
-In consequence, $Y$ is unable to form high NTIC and, therefore, to have high conscious levels.
+As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain unconscious.
         			    }
@@
 
-        		The same principle can be applied to blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedure memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes.
+        		The same principle can be applied to interpret blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedural memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes.
 Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements without having any conscious perception about visual stimuli.
@@
 The neural circuits are not informationally closed and, therefore, unconscious.
-Similarly, for procedure memory, the state transitions of action controls largely depends on the concurrent environmental states.
+Similarly, for procedural memory, the state transitions of action controls largely depends on the concurrent environmental states.
 This prevents the internal processes of procedure memory from informational closure and being conscious.
-
-                % In the neural system, this type of processes, for perception, shows the property that the perceptual processing mainly passively responds to the sensory inputs.
-For actions, this type of processes only produces "reflective-like" behaviours.
-Reflexive behaviours are commonly considered as automatic and non-conscious behavioural controls \citep{casali2013theoretically}\needref{More referene}.
-We argue that information carried by this type of processes is unconscious due to its failure of achieving high NTIC, i.e., the first condition.
-
-                % The same principle can be applied to blindsight and procedure memory \needref{blindsight} which are often considered as unconscious processing.
-Blindsight patients are able to track objects, avoid obstacles, and make above chance-level judgements without having any conscious perception about visual stimuli.
-We believe that these behaviours can be guided by direct stimulus-response mappings ($S\rightarrow{}R$).
-However, the direct $S\rightarrow{}R$ mappings also lead to non-NTIC neural processes  and, therefore, are unconscious.
-Similarly, in the case of procedure memory, processes always rely on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}.
-The information flow from the environment to the system is crucial to guide the state transition of procedural memory.
-Therefore, information processing of procedural memory also fails to form high NTIC and remain unconscious.
-
-        %          This type of processing is similar to the model-free policy-based agents in the reinforcement learning framework.
-The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
-        % 		\begin{equation}
-        % 			\label{eq:PolicyBasedAgent}
-        % 			\begin{aligned}
-        % 			    \pi(A | S)=\operatorname{Pr}\left(A_{t}=a | S_{t}=s\right)
-        % 			\end{aligned}
-        % 		\end{equation}
-
-                \ac{OurTheory} explains why the patients with visual apperceptive agnosia \citep{james2003ventral} can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.
-The online information from the visual inputs can be used to perform  functional actions without complete conscious perception of the visual targets.
-
-                % Our theory also explains why unconscious processes in this category often fail when a long delay periods is introduced in the tasks.
-Without self-predictive information in NTIC, the policies of motor outputs largely depends on the present environmental and sensory states implying that this type of processes often can only work online.
-With a long, sensory information is unable to guide the delayed motor outputs and leads to failure consequences.
+\ac{OurTheory} also offer an interpretation as to why patients with visual apperceptive agnosia \citep{james2003ventral} can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.
 
         		\ideaCallout{Mayeb can put in theory part}
-        		An implication from \ac{OurTheory} is that a pure feedforward network is incapable to be conscious due to a lack of any form of memory.
-Without memory, the network current states are entirely driven by network current inputs without any influence from its past states and, therefore, is incapable to be informationally closed.
-In contrast, a network with recurrent loops could keep information about its states.
-This forms an information channel between the past and the future states of the network and, thus, makes the network becomes capable of being informationally closed.
+        		As we have seen in the examples above, a crucial implication of \ac{OurTheory} is that a pure feedforward network cannot produce consciousness because NTIC requires a form of memory $I(Y_{t+1};Y_{t})$.
+Without memory, a network's current state is entirely driven by the input the network receives from the environment without any influence from its own past states.
+Therefore, such a network is incapable of forming an NTIC.
+In contrast, a network with recurrent loops can maintain information about its own past states.
+This forms an information channel between the past and the future states of the network and, thus, makes the network capable of being informationally closed.
 This result coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
@@
 
-            \subsubsection*{Encoded Information is Trivial}
-                Encoded information in a process is trivial, i.e.
-no mutual information between the system states and its environment states $I(Y_{t+1};E_{t})$ (Eq.~\ref{eq:nticObjective2}), could also lead low NTIC.
-This process is considered to be unconscious due to the low level of NTIC.
-This implies an isolated process which is simply informationally closed to its environment is not enough to be conscious.
-
-                This implies that \ac{OurTheory} provides a natural solution to the boundary problem of consciousness \citep{Raymont2006-RAYUOC}.
-Consider a NTIC process $Y$ and an isolated informationally closed process $\hat{Y}$ with trivial information.
-Adding $\hat{Y}$ to $Y$ can still keep informational closure, but, however, does not increase non-trivial information.
+            \subsubsection*{Information is Trivial}
+                According to \ac{OurTheory}, when encoded information in a process is trivial, i.e.
+no mutual information between the process states and its environment states $I(Y_{t+1};E_{t})$ (Eq.~\ref{eq:nticObjective2}), this could lead low NTIC.
+In such case, this process is considered to be unconscious due to the low level of NTIC.
+This implies an isolated process which is simply informationally closed is insufficient to be conscious.
+                This mathematical property of \ac{OurTheory} provides a natural and intuitive (but only partial, see the current challenge in  Sec.~\ref{sec:Limitation and Future work}) solution to the boundary and the individuality problem of consciousness
+                    \footnote{The boundary problem of consciousness refers to identifying physical boundaries of conscious processes and the individuality problem of consciousness refers to identifying individual consciousnesses in the universe.}
+                \citep{Raymont2006-RAYUOC}.
+Consider a NTIC process $Y$ and an isolated informationally closed process $\hat{Y}$ with only trivial information.
+Adding $\hat{Y}$ to $Y$ can still keep informational closure, but, however, does not increase non-trivial information, i.e.
+doesn't affect consciousness.
 
@@
 
-                This indicates that isolated processes with trivial information do not contribute consciousness and should be outside the information boundary of the conscious processing.
-This result also implies that consciousness does not emerge from aggregating informationally closed processes with trivial information.
-
-            % \ideaCallout{Should I say this?}
-%             This implies that \ac{OurTheory} provides a natural solution to the boundary problem of consciousness \citep{Raymont2006-RAYUOC}.
-Consider a set of independent processes $Y=\{Y^1,...,Y^n\}$ with deterministic state transitions in a small universe.
-Each variable not only is informationally closed to other variables, they also share no mutual information.
-
-% 			\begin{equation}
-% 				\thickspace Y^i \bot Y^j, \quad \forall {i\neq j}
-% 			\end{equation}
-
-%             Now we randomly pick two variables and make group two variables s
-
-%             , therefore, unconscious. Next, we can select a two of the variables and compute NTIC between this subset and other variables.
-
-            \subsubsection*{Unsuitable Measurement scales }
-                \ac{OurTheory} proposes that human conscious process rests on a certain scale which forms NTIC.
-This implies the spatial and temporal scales of the physiological measurements are critical in the experiments aiming to finding neural correlates of consciousness (NCC).
-
-                % \subsubsection*{Fail t  o meet the 2\lowercase{ed} condition}
-                As mention above, information is level-dependent and can be virtually independent (closed) across different coarse-graining scales.
+                This implies that isolated processes with trivial information do not contribute consciousness and should be considered being outside the information boundary of the conscious processing (for more details of the boundary detection procedure, see \cite{krakauer2014information}).
+                This property also implies that consciousnesses do not emerge from just aggregating informationally closed (isolated) processes which contain trivial information.\footnote{However, we do not exclude the possibility that triviality of encoded information is just a proxy of other quantities which more directly associate with consciousness.
+We point out that this is a limitation of the current version of \ac{OurTheory} in Sec.~\ref{sec:Limitation and Future work}.}
+
+        % ---------------------------------------------------------------------------- %
+        %                             Conscious Processing                             %
+        % ---------------------------------------------------------------------------- %
+		\subsection{Conscious Processing}\label{sec:conscious processing}
+		    According to \ac{OurTheory}, NTIC is sufficient for a process to be conscious.
+We claim that any process, system, or cognitive function which involves any NTIC process should be accompanied by conscious experience.
+
+		    Previous consciousness research has identified a number of diverse cognitive processes often accompanied by conscious experience.
+\ac{OurTheory} provides an integrated account for why these processes involve conscious experience.
+NTIC processes encode environmental information into its own states and dynamics.
+Therefore, An NTIC process can be seen as an internal simulation engine for the agent-environmental interactions \citep{BERTSCHINGER.2006}.
+Information from NTIC processes is essential for several cognitive processes.
+
+		  %  NTIC is a powerful property in the context of evolution.
+NTIC processes encode environmental information into its own states and dynamics.
+Hence, an NTIC process can be seen as a simulation engine of the environment \citep{BERTSCHINGER.2006}.
+Therefore, NTIC processes can provides valuable information for survival as a basis of several cognitive functions.
+
+		    One of the most valuable information is the predictions about the environmental states.
+Cognitive functions requiring agent-scale environmental predictions are likely to recruit NTIC processes and therefore accompanied by conscious experience, for example planning and achieving long term goals.
+
+            Second, as a simulation engine, with a given initial state, an NTIC process can self-evolve and simulate the environmental transitions.
+Cognitive functions involving simulations are expected to involve NTIC processes.
+Consequently, mental simulation, imagination, computing alternative realities, and generating counterfactuals often come with conscious experience.
+
+    	    Third, as an informationally closed system, an NTIC process can still provide environmental information without new sensory inputs.
+This is crucial for many types of off-line processing.
+Therefore, in contrast to reflex-like behaviours mentioned above (Sec.~\ref{sec:reflexive}), behaviours requiring off-line computations \citep{milner1999paradoxical, himmelbach2005dorsal,revol2003pointing} often involve conscious experience.
+
+    	    Finally, for agents adapting to complex environments (e.g., human being), any state of the NTIC process can be seen as an integration of high dimensional information.
+To accurately encode information about the complex environmental states and transitions, the NTIC process requires knowledge about the complex causal dependencies involved in the environment.
+Therefore, cognitive functions requiring large scale integration are likely to involve NTIC processes and accompanied by conscious experience.
+% Furthermore, the high dimensional integrated information is also critical for an agent to learn new behaviours to achieve flexibility and the strategic behavioural controls and decision-making.
+
+    	    Note that many of the claims above are compatible with several theories of consciousness which highlight the connection between consciousness and internal simulation, predictive mechanism, or generative models inside a system (e.g.
+world simulation metaphor ~\citep{revonsuo2006inner}, predictive processing and Bayesian brain~\citep{clark_2013,Hohwy2013,SethPP2014}, generative model and information generation~\citep{kanai_chang_yu_de_abril_biehl_guttenberg_2019}).
+Instead of relating functional or mechanistic aspects of a system to consciousness, \ac{OurTheory} captures common informational properties underlying those cognitive functions associated with consciousness.
+As such, \ac{OurTheory} does not assume any functionalist perspective of consciousness, which associate specific functions to consciousness.
+That is to say, since \ac{OurTheory} associates information  with consciousness, functional features accompanied by consciousness are collateral consequences of neural systems utilising NTIC processes for adaptive functions.
+
+    	    In sum, we argue that cognitive functions involving the NTIC process are inevitably accompanied by consciousness.
+Having an NTIC process is potentially an effective approach to increase fitness in the evolution.
+It is likely that biological creatures evolve NTIC processes at some point in the evolution.
+Due to the fundamental relation between information and consciousness, biological creatures also evolve different degrees of consciousness depending on the physical scales and the complexity of the environments they adapt to.
+
+    	    \ac{OurTheory} starting with non-functional assumptions and propositions, however, leads to profound implications about the functional aspects of consciousness.
+\ac{OurTheory} further demonstrates remarkable explanatory power for various findings of conscious and unconscious processing with concise propositions.
+
+    % \subsection{Inconsistency between Conscious States and Measured Physiological States}
+    %     \ac{OurTheory} claims that the human conscious (NTIC) process rests on a certain coarse-grained level in the human neural system.
+This implies the spatial and temporal scales of the physiological measurements are critical for finding neural correlates of consciousness (NCC).
+Choosing unsuitable measuring scales may lead to confusing results and inappropriate interpretations.
+Here we elaborate this issue with two classic examples.
+
+    %     % probabilistic inference
+    %     \subsubsection*{The First Example: Probabilistic Inference}
+    %     Strong evidence suggests that the neural system is capable to encode probability distribution and perform probabilistic inference in a near optimal way \citep{knill2004bayesian, pouget2013probabilistic}.
+However, an intriguing fact is that our conscious contents are almost ignorant of all details of the computations.
+Instead, we are always only conscious of "a sample" of the posterior distributions \citep{dehaene2017consciousness, vul2009attention, asplund2014attentional, vul2008temporal, moreno2011bayesian}.
+In short, one needs to explain why information about the probability distributions are unconscious and only a realisation of the posterior distribution becomes conscious.
+    %     \ac{OurTheory} provides an answer to this question.
+We argue that all the computation of the statistical inference is carried out at microscopic levels of the neural system.
+The macroscopic NTIC process only encodes sufficient statistics of the microscopic processes and has no way to access the full microscopic states due to informational closure to the microscopic processes.
+    %     In this case, microscopic (cellular level) measurements may not have good correspondence with conscious contents.
+Instead, summary statistics are macroscopic variables corresponding with conscious contents.
+
+    %     \subsubsection*{The Second Example: Libet Experiments: The measurement is overly coarse-grained }
+    %         The same scenario can be applied to the results from Libet's volition experimental paradigm \citep{Libet1983TimeOC, Libet1985Dec}.
+
+    %         Experiments using similar procedures usually show that the recorded neural activities start earlier than subjects' feeling of their own intention to act in the self-determined experimental settings.
+
+    %         hWe argue that free actions are initiated at the microscopic levels, for example, the random fluctuation in the neural system \citep{schurger_accumulator_2012}.
+However, the conscious experience of volition is information at the macroscopic level with NTIC.
+Due to the information closure, there is no way for the NTIC process to observe the information of the microscopic states, i.e.
+the initiation of actions.
+
+    %     % \subsubsection*{Fail t  o meet the 2\lowercase{ed} condition}
+    %     As mention above, information is level-dependent and can be virtually independent (closed) across different coarse-graining scales.
 If processes at some levels of a system are able to form high NTIC and become conscious, information at other levels still remains unconscious.
@@
 
-                We argue that many mysterious results in previous research of consciousness are originated from inappropriate biological and behavioural measurement scale.
-In the following, we list some examples.
-
-                Unconscious processing in this category of
-
-                @ Evidence suggests that the neural system is able to encode probability distribution and perform probabilistic inference in a near optimal way\needref{bayesian brain}.
+    %     @ Evidence suggests that the neural system is able to encode probability distribution and perform probabilistic inference in a near optimal way\needref{bayesian brain}.
 However, an intriguing fact is that we are nearly ignorant of all the probabilistic computation of the inference processes but are only aware of "a sample" of the posterior distributions of the inferences \citep{dehaene2017consciousness, vul2009attention, asplund2014attentional, vul2008temporal, moreno2011bayesian}.
@@
 
-                For example, Fig.~ \ref{fig:TemperatureExample} illustrates the relationship 
-                At the left panel, two cups contain water with different volumes $V_t$ and temperatures $T_t$.
+    %     For example, Fig.~ \ref{fig:TemperatureExample} illustrates the relationship 
+    %     At the left panel, two cups contain water with different volumes $V_t$ and temperatures $T_t$.
 Even though we know volumes and temperatures are coarse-grained macroscopic variables, the states of mixed water ($V_{t+1}$, $T_{t+1}$) can still be predicted without knowing any information from the microscopic levels (the molecular level),i.e., the information closure at the macroscopic level.
@@
 
-        		\begin{figure}[H]
-        			\includegraphics[width=1.3\textwidth]{WritingMaterials/Fig_Temperature_Example/ExampleOfCG.pdf}
-        			\centering
-        			\caption{An Example of ...}
-        			\label{fig:TemperatureExample}
-        		\end{figure}
-
-                The same scenario can be applied to the results from Libet's volition experimental paradigm \citep{Libet1983TimeOC, Libet1985Dec}.
+    % 	\begin{figure}[H]
+    % 		\includegraphics[width=1.3\textwidth]{WritingMaterials/Fig_Temperature_Example/ExampleOfCG.pdf}
+    % 		\centering
+    % 		\caption{An Example of ...}
+    % 		\label{fig:TemperatureExample}
+    % 	\end{figure}
+
+    %     The same scenario can be applied to the results from Libet's volition experimental paradigm \citep{Libet1983TimeOC, Libet1985Dec}.
 Experiments using similar procedures usually show that the recorded neural activities start earlier than subjects' feeling of their own intention to act in the self-determined experimental settings.
@@
 
-                \idea{Not sure if I want to address this point}  Note that, some evidence suggests single-cell-level correlation of conscious experience, the Jennifer Aniston cell for example \citep{Quiroga2005Jun, Quiroga2012Jul}.
+    %     \idea{Not sure if I want to address this point}  Note that, some evidence suggests single-cell-level correlation of conscious experience, the Jennifer Aniston cell for example \citep{Quiroga2005Jun, Quiroga2012Jul}.
 This may seem to counter our argument that single-cell level information is incapable to be conscious.
@@
 
-        % ---------------------------------------------------------------------------- %
-        %                             Conscious Processing                             %
-        % ---------------------------------------------------------------------------- %
-		\subsection{Conscious Processing}
-		When the both conditions are fulfilled, our theory suggests that the states of an NTIC process correspond to particular conscious contents and the information incorporated in the NTIC process is conscious.
-Due to the predictive nature about the environment dynamics of NTIC processes, to form high NTIC and to construct functions within the process have a huge evolutionary advantage.
-It is important to emphasise that our theory does not suggest any functionalism of consciousness.
-Rather, we argue that information fundamentally associates with consciousness.
-Nevertheless, consciousness research still suggests a strong functional relation between consciousness and some specific types of cognition and behaviours \citep{Seth2009Encyclopediaofconsciousness}.
-We believe that this relation comes from several special properties of NTIC and these properties support the foundations of many cognitive functions in the neural system.
-
-		First, an NTIC process encodes predictive information about environmental dynamics.
-This is crucial for constructing forward models for predicting future states of the environment.
-Therefore, cognitive functions which require agent-scale prediction are likely to be accompanied by conscious experience.
-This properties is required by planning and also achieving long term goals.\needref{}
-
-		Second, an NTIC process can be considered as a close form simulation machine.
-With a given initial state, the process can self-evolve and follow a certain trajectory in the state space.
-This trajectory can be seem as a simulation about the environmental transition.
-Therefore, an NTIC process can serve cognitive functions as a perfect simulation engine \citep{BERTSCHINGER.2006}.
-Accordingly, mental simulation, imagination, computing alternative realities, and generating counterfactual outcomes can be implemented with an NTIC process.
-\needref{}
-
-	    Third, an important properties of NTIC processes is its high stability.
-The state transitions and trajectory are highly predictable.
-In such case, NTIC processes are more suitable for integrating information across larger time scales (above millisecond).
-Therefore, tasks which require to integrate information across time above the millisecond scale are often associated with conscious experience.
-
-	    Fourth, an NTIC process as a closed system can still provide predictive information without new information flowing into the process. This is crucial for many types of off-line processing.
-
-	    Fifth, any state of an NTIC process can be seem as a integration of multiple sources of information.
-For the human scale activities, to know certain transition about the environment, the NTIC process must include a high dimensional information from multiple modalities and have the knowledge about how the high dimensional data interact to each other.
-Without the knowledge and information, a process may not be capable of produce a stable state transitions which mimic the environmental dynamics.
-Thus, cognitive functions requiring this large scale integration are likely to be conscious.
-Furthermore, the high dimensional integrated information is also critical for an agent to learn new behaviours to achieve flexibility and the strategic behavioural controls and decision-making.
-
-	    In sum, we argue that having an NTIC process is critical for survival in the evolution.
-It is likely that biological creatures acquired NTIC process at some stages in the evolution.
-And due to the fundamental relationship between information and consciousness, these biological agents also acquired different degrees of consciousness depending on the physical scales and the complexity of the environments they live in.
-Our theory well explains why some processes and functions in the neural system are conscious and some are not with only two parsimonious conditions.
-
-% ============================================================================ %
-%                        Comparison with other theories                        %
-% ============================================================================ %
+    % % ============================================================================ %
+    % %                        Comparison with other theories                        %
+    % % ============================================================================ %
     \section{Comparison with other Relevant Theories of Consciousness}\label{sec:Comparison with other theories}
-	In this section, we \ac{OurTheory} with other relevant modern theories of consciousness.
+    In this section, we compare \ac{OurTheory} with other relevant theories of consciousness.
 
@@
         % ---------------------------------------------------------------------------- %
-        \subsection{Multilevel views on consciousness and cognition}
-    		\ac{OurTheory} proposes that a conscious (NTIC) process only rest at a certain coarse-grained scale in the neural system.
-This suggests that the scales of coarse-graining is critical for searching for conscious processes.
-In previous research, a few multilevel views on consciousness have been (explicitly or implicitly) proposed.
-So far, to our knowledge, Pennartz's neurorepresentational theory (Neurorepresentationalism, \cite{pennartz2018consciousness,pennartz2015brain}) is the closest proposal in line with our multilevel view on consciousness.
-Similar to Neurorepresentationalism, the concept of levels \ac{OurTheory} is also relevant to Marr's level of analysis \citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}.
+        \subsection{Multilevel views on consciousness and cognition}\label{sec:MultiLevelView}
+    		\ac{OurTheory} proposes that conscious processes can occur at any level of coarse-graining which forms NTIC within a system.
+This suggests that the scale of coarse-graining is critical for searching and identifying the information corresponding to consciousness.
+A few versions of multilevel views on consciousness have previously been (explicitly or implicitly) proposed.
+To our knowledge, Pennartz's neurorepresentational theory (also called Neurorepresentationalism,~\citep{pennartz2018consciousness,pennartz2015brain}) is the proposal closest to the multilevel view of \ac{OurTheory}.
+Similar to Neurorepresentationalism, the concept of levels in \ac{OurTheory} is also relevant to Marr's level of analysis~\citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}.
     		However, \ac{OurTheory} suggests that coarse-graining is necessary only when the microscopic processes are stochastic (e.g.
@@
 
-    		Another proposal based on multilevel views is the Intermediate Level Theory of Consciousness \citep[ILT]{prinz2007intermediate, jackendoff1987consciousness}.
-ILT proposes that conscious experience is only associated with representations at intermediate levels of the sensory processing hierarchy (e.g., the 2.5D representation in terms of visual processing) rather than lower (e.g.
-pixel) or higher (e.g.
-abstract ) levels of the hierarchy.
-    		Here, we want to make a clear clarification that the "level" in \ac{OurTheory} refers to the levels of coarse-graining instead of the "level" for anatomy or information processing.
-It is important to note that the coarse-graining direction is not necessary aligned with the levels of anatomy or the information processing hierarchy in the neural system .
-Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example
-
-    		specific levels of representations in the hierarchy of sensory processing.
-ILT claims that consciousness only associates with the representation at intermediate levels (e.g., the 2.5D representation in terms of visual processing) rather than the ones at lower-level or higher-level.
-
-    		One fundamental difference between ILT and our theory is the definitions of the level.
-In our theory, level is within the context of coarse-graining.
-However, ILT focuses more on the levels in terms of anatomical direction (see fig \ref{fig:hierarchy}).
-As mentioned previously, we emphasise that we doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies.
-This leads to an important difference that the level of coarse-graining exists virtually.
-However, the level of cortical representation should be referred to neural substrates.
-Finally, different from ILT which suggests that some neural substrates responsible for the 2.5D computation are conscious, we predict that once information carried by coarse-grained variables is involved in the NTIC process, brain areas, not exclusively within 2.5D representation, should  co-vary with conscious contents.
-
-        % ---------------------------------------------------------------------------- %
-        %                 sensory hierarchy and neural coarse-graining                 %
-        % ---------------------------------------------------------------------------- %
-		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}
-
-        It is important to note that the coarse-graining direction is not necessary aligned with \critical{Just saying anatomical is not enough.
-Need better expression} anatomical sensory hierarchy in the neural system.
-Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example
-
-        the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.
-Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.
-In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system.
-We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.
+    		Another well-known proposal based on multilevel views is the Intermediate Level Theory of Consciousness \citep[ILT]{prinz2007intermediate, jackendoff1987consciousness}.
+ILT proposes that conscious experience is only associated with neural representations at intermediate \textbf{levels of the sensory processing hierarchy} (e.g., the 2.5D representation of visual processing) rather than lower (e.g., pixel) or higher (e.g., abstract) levels of the sensory hierarchy.
+
+    		Here, we want to make clear that the "level" in \ac{OurTheory} refers to the \textbf{levels of coarse-graining} instead of the "level" for the cortical anatomy or sensory processing.
+It is important to note that the coarse-graining direction is an orthogonal dimension irrespective of the level of anatomy or the level of information processing hierarchy in the neural system (see Fig.~\ref{fig:hierarchy}).
+Because ILT focuses on the levels of the sensory processing hierarchy and \ac{OurTheory} focus on informational closure among the levels of coarse-graining, the two theories are fundamentally different.
 
     		\begin{figure}[H]
-
-			\includegraphicsTodo[width=\textwidth]{WritingMaterials/Fig_SeperationOfCGandCortHierachy/SeperationOfCGandCortHierachy.pdf}
+    			\includegraphics[width=\textwidth]{WritingMaterials/Fig_SeperationOfCGandCortHierachy/SeperationOfCGandCortHierachy.pdf}
+				\caption{The distinction between the level of coarse-graining and the level of the cortical hierarchy.
+$X$ and $Y$ represent the microscopic and macroscopic coarse-grained  variables, respectively.
+$X^0$ represents the microscopic states at the upstream of the cortical hierarchy.
+The red empty arrows represents the directions of coarse-graining and the blue arrows represent the directions of the physical dependencies in the cortical hierarchy from the upstream to the downstream.
+(Some variables and dependencies are omitted for clarity.)}
 				\label{fig:hierarchy}
@@
 
-                \subsubsection*{Level of Organisation \cite{wimsatt1994ontology}}
-                    As mentioned previously, the level of coarse-graining is different from the anatomical level.
-                    Pennartz focuses more on multimodal representation as the most important factor (See the discussion in \cite{pennartz2015brain}).
-Our proposal is inline with Pennartz's Neurorepresentational  theory (Neurorepresentationalism) \cite{pennartz2018consciousness,pennartz2015brain}.
-However, it’s crucial to note that our theory claims only the level of coarse-graining achieving NTIC matters to consciousness rather than the anatomical level of sensory hierarchy.
-
-    			\subsubsection*{Intermediate Level Theory} \label{IntermediateLevelTheory}
-                    One important theory tries to connect consciousness to multilevel views is the Intermediate Level Theory (ILT, \cite{jackendoff1987consciousness, prinz2007intermediate}).
-ILT proposes that conscious experience only correlates specific levels of representations in the hierarchy of sensory processing.
-ILT claims that consciousness only associates with the representation at intermediate levels (e.g., the 2.5D representation in terms of visual processing) rather than the ones at lower-level or higher-level.
-                    One fundamental difference between ILT and our theory is the definitions of the level.
-In our theory, level is within the context of coarse-graining.
-However, ILT focuses more on the levels in terms of anatomical direction (see fig \ref{fig:hierarchy}).
-As mentioned previously, we emphasise that we doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies.
-This leads to an important difference that the level of coarse-graining exists virtually.
-However, the level of cortical representation should be referred to neural substrates.
-Finally, different from ILT which suggests that some neural substrates responsible for the 2.5D computation are conscious, we predict that once information carried by coarse-grained variables is involved in the NTIC process, brain areas, not exclusively within 2.5D representation, should  co-vary with conscious contents.
-
         % ---------------------------------------------------------------------------- %
@@
 		\subsection{Integrated information theory}
-    		Integrated information theory (IIT) states that system's consciousness is determined by its causal properties.
+            Integrated information theory (IIT) states that consciousness is integrated information and system's consciousness is determined by its causal properties \citep{tononi2016integrated}.
+\ac{OurTheory} is in line with IIT in that informational properties are thought to underlie consciousness.
+In this section, we will discuss \ac{OurTheory} in the light of IIT.
+
+            \textbf{The concept of "information"}: In IIT, information refers to "integrated information":\\ \say{Information that is specified by a system that is irreducible to that specified by its parts.}~\citep{tononi2016integrated} In \ac{OurTheory}, information refers to "self-information", i.e.
+information about the states of conscious experience and the physical states of a process.
+Therefore, IIT focuses more on the relationships between consciousness and causal interactions among elements within a system, whereas \ac{OurTheory} focuses more on the informational relationships between conscious experience and being in a certain state of a process.
+
+		    \textbf{The "Exclusion" axiom in IIT}: In IIT, the Exclusion axiom claims that of all overlapping sets of elements, only one set with maximal integrated information can be conscious.
+The exclusion axiom should be applied over elements, space, time, and scales \citep{oizumi2014phenomenology, hoel2016can}.
+Different from IIT, \ac{OurTheory} allows multiple consciousnesses coexist across different levels of coarse-graining within a system if they are informationally closed from each other.
+The two distinctive predictions decisively pinpoint the core concepts of the two theories.
+
+		    %For example, a human brain may be a part of a conscious process at human society level. However, due to the informational closure, we should have no information about it in our consciousness.
+
+		    \textbf{Prediction after system damaged}: \ac{OurTheory} and IIT lead to different predictions when a system suffers from a damage.
+For example, considering a densely connected networks whose dynamics forms an NTIC process.
+If we cut the network in half, IIT would predict that this results in two consciousnesses because elements in both networks still maintain high degrees of interactions.
+In contrast, \ac{OurTheory} would predict that this operation could completely destroy NTIC rendering both parts unconscious.
+
+		    In the current paper, we did not include the notion of integrated information within \ac{OurTheory}.
+However, one of the current weaknesses of \ac{OurTheory} is that it lacks the ability to individuate NTIC processes as distinct entities because a macro-process composed of two independent NTIC processes is also an NTIC.
+This is a severe limitation of our current theory.
+The notion of integration is a possible remedy for this issue and we hope to address this more explicitly in future work using the concept of synergy.
+
+            % ============================================================================ %
+            %                                    Backup                                    %
+            % ============================================================================ %
+
+% 		    % ================================ Difference ================================ 
+% 		    \begin{ants}
+%     		    @@ However, \ac{OurTheory} considers that when a process is informationally closed to the universe, the process can be reckoned as a reality.
+
+%     		    One difference is that IIT does not consider environmental information
+%     		    @ IIT considered causality is the key foundation of consciousness
+%     		    @ \ac{OurTheory} focus more on informational closure as the key properties to form a reality. 
+% .
+
+%     		    @ Conscious contents in \ac{OurTheory} are 
+%     		    @@  a subset of elements can contribute a specific aspect of experience only if its cause-effect repertoire within the system is irreducible by the minimum partition of the mechanism (‘small phi’ or φ)
+
+%     		    @@ \ac{OurTheory} considered whether a part contribute conscious content whether it's within the range of informational closure
+
+%     		    @ Exclusion 
+%     		    @@ Boundary problem by exclusion
+%     		    @@ In \ac{OurTheory}, boundaries of a conscious process is defined by its information boundary, i.e. informational closure.
+%     		    @@ ic between level
+%     		    @ conscious level
+%     		    @@  Φ max
+% 		    \end{ants}
+
+% 		    % ----------------------------------------------------------------------------
+%     		Integrated information theory (IIT) states that system's consciousness is determined by its causal properties.
 Consciousness is integrated information.
@@
 
-    		% -------------------------------- Similarity -------------------------------- %
-    		IIT and our theory shares common principles in many aspects.
+%     		% -------------------------------- Similarity -------------------------------- %
+%     		IIT and our theory shares common principles in many aspects.
 First common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness \needref{cite David Chalmers}.
@@
 
-    		Second, both theories consider informational structure as the fundamental entities associated with the quality of conscious contents.
+%     		Second, both theories consider informational structure as the fundamental entities associated with the quality of conscious contents.
 IIT proposes that a "complex" which is defined as elements that generates a local maximum of integrated information as the core entity which determines the state space of subjective feeling (qualia space).
@@
 
-    		\ideaBox{Maybe synergy is the common part of the two theories }
-
-    		Even though both theories are based on informational properties of a process, predictions of the two theories can be very different.
+%     		\ideaBox{Maybe synergy is the common part of the two theories }
+
+%     		Even though both theories are based on informational properties of a process, predictions of the two theories can be very different.
 Taking the split brain cases as the example, when splitting a system into two parts, IIT suggests that each part can form a new complex.
@@
 
-    		% Hoel's theory\cite{hoel2016can}}
-    		Alongside with the main theoretical development of IIT, \cite{hoel2016can,hoel2013quantifying} discussed the scale-dependent causal structures using IIT as a measure of causal power at different scales.
+%     		% Hoel's theory\cite{hoel2016can}}
+%     		Alongside with the main theoretical development of IIT, \cite{hoel2016can,hoel2013quantifying} discussed the scale-dependent causal structures using IIT as a measure of causal power at different scales.
 The result shows a qualitative similarity to our theory.
@@
 
-            % =============== Internal simulation and self-modelling theory ============== %
-    		\subsection{Internal simulation and self-modelling theory}
-    		\idea{I will skip this section unless you think this is necessary.}
-
         % ---------------------------------------------------------------------------- %
@@
 		\subsection{Predictive Processing}
-    		Predictive processing is a powerful framework (PP) which integrates several influential ideas in the history of neuroscience including "perception as unconscious inference" from Helmholtz \citet{helmholtz1866concerning}, "analysis by synthesis", “predictive coding”, and "Bayesian brain hypothesis".
-This emerging theoretical framework of perception and brain function suggests that the neural system constantly generates predictions about incoming sensory signals and updates predictions based on prediction error between predictions and real sensory signals.
-According to PP, the neural system constantly performs unconscious statistical inference about hidden causes in the external environment.
+    		Predictive processing (PP) is a powerful framework which integrates several ideas from neuroscience.
+This emerging theoretical framework posits that neural systems constantly generate predictions about incoming sensory signals and updates predictions based on prediction errors between predictions and sensory signals.
+According to PP, neural systems constantly perform unconscious statistical inference about hidden causes in the external environment.
 The perceptual contents are the "best guess" about the environment states including these hidden causes \citep{clark_2013, Hohwy2013}.
-Because it is well integrated with Bayesian brain hypothesis, the PP has been used to interpret conscious perception in many perceptual domain.
-\cite{Hohwy2013} \cite{SethPP2014}.
+PP is well integrated with Bayesian brain hypothesis and has been used to interpret conscious perception in many domains \citep{Hohwy2013, SethPP2014}.
 
@@
     		PP is a powerful explanatory framework for diverse brain functions.
-However, to serve as a theory of consciousness, PP is still incomplete due to two theoretical gaps.
-First, there are enormous predictive mechanisms in the neural systems.
-It is  obvious that that not all the predictive information from these mechanisms is able to be part of conscious contents.
-Therefore, PP needs to explain the difference between conscious and unconscious predictive mechanisms.
-Second, if we closely look at a conscious predictive system, the only part can be consciously aware of is the result.
-Other details of the computation remain unconscious.
+However, to serve as a theory of consciousness, PP is still incomplete due to two explanatory gaps.
+First, it has been known that the neural system is equipped multiple predictive mechanisms.
+Apparently, not all the predictive mechanisms are involved in conscious processes (e.g.
+mismatch negativity, \cite{naatanen2007mismatch}).
+PP needs to explain the difference between conscious and unconscious predictive mechanisms.
+
+    		Second, PP can be considered as a sophisticated computation for perceptual inference.
+It takes von Helmholtz's conception of perception as unconscious inference.
+Thus, only the most probable outcome computed by the inference processes can be conscious while other details of the computation remain unconscious.
 PP also needs to explain how unconscious inferences is able to give rise to conscious results.
-In short, the two explanatory gaps prevent PP from been a complete theory of consciousness.
-
-    		Here, from more fundamental principles, we  argue that our theory is able to well fill the two gaps simply by considering the two conditions mentioned in section \ref{sec:Conscious versus Unconscious Processing}.
-
-    		First, predictive processes do not necessitate NTIC.
+In short, while PP is often discussed in the context of consciousness, these explanatory gaps prevent PP from being a theory of consciousness.
+
+    		% compatible things
+    		\ac{OurTheory} is well compatible with PP.
+Crucially, \ac{OurTheory} further provides natural and fundamental explanations to fills the two explanatory gaps which PP encounters.
+According to the definition of NTIC, a process with high NTIC can be regarded as a powerful predictive machine which has accurate self-predictive information ($I(Y_{t+1};Y_{t})$, E.q.~\ref{eq:NTIC}) and concurrently incorporates environmental information into its dynamic ($I(Y_{t+1};Y_{t}|E_{t})$, E.q.~\ref{eq:NTIC}).
+This predictive nature of NTIC processes is in agreement with the core notion of PP in which the conscious contents are always the predicted (inferred) outcome of our predictive mechanisms.
+Second, due to the informational closure to the environment, the encoded information about its environment in an NTIC process can be seemed as "the best guess" about the external environment in the context of Bayesian inference.
+
+    		% fill the gaps
+    		So, eventually, why are some predictive information conscious and some are not?
+\ac{OurTheory} predicts that only the predictions generated from mechanisms involving the NTIC process are conscious.
+Note that predictive processes are not necessary to involve NTIC processes.
+A predictive process can make prediction about the future state of its environment based on the current sensory inputs.
+In this case, the the process is not informationally closed and could not be conscious.
+
+            According to \ac{OurTheory}, we further propose that we can only be aware of the predictions from predictive processes due to informational closure to computational details of microscopic predictive processes.
+The macroscopic NTIC process only acquires the coarse-grained summary statistics of the microscopic processes.
+In other words, we predict that the computation of the statistical inferences of PP is implemented at microscopic (cellular) levels in the neural system.
+
+    		% finally
+    		Finally, we consider PP as an potential empirical implementation of NTIC processes.
+To maintain accurate information about the environment encoded in an NTIC process, one can open an information channel between the process and the environment for minimal information flow to correct the divergence between them.
+This proposal is compatible with PP which suggests that PP systems updates (corrects) the current estimations by computing prediction errors between predicted and real sensory inputs.
+
+    		% ============================================================================
+    		----------------------------------------------------------------------------\\
+
+    % 		Furthermore, only the mutual information between environments and NTIC processes matters. The "true" external reality may not be known.
+
+    % 		self-predictive nature of a NTIC process
+
+    % 		Here, from more fundamental principles, we  argue that our theory is able to well fill the two gaps simply by considering the two conditions mentioned in section \ref{sec:Conscious versus Unconscious Processing}.
+
+    % 		First, predictive processes do not necessitate NTIC.
 A neural mechanisms is able to generate prediction does not guarantee it is an NTIC process.
@@
 
-    		Second, as mentioned in section \ref{sec:Conscious versus Unconscious Processing}, if a process is not at the coarse-grained level achieving NTIC, this process will not be conscious (Fail to meet the 2\lowercase{ed} condition).
+    % 		Second, as mentioned in section \ref{sec:Conscious versus Unconscious Processing}, if a process is not at the coarse-grained level achieving NTIC, this process will not be conscious (Fail to meet the 2\lowercase{ed} condition).
 We have provided an example in section \ref{sec:Conscious versus Unconscious Processing} in which computation can be implemented at microscopic levels.
@@
 
-            Altogether, our theory provides more fundamental principles and explanations about the relationship between predictive mechanisms and consciousness.
+    %         Altogether, our theory provides more fundamental principles and explanations about the relationship between predictive mechanisms and consciousness.
 Moreover, the fundamental principles allow us to make more precise predictions about which types of PP should or should not be conscious.
@@
 		\subsection{Sensorimotor contingency}
-    		Sensorimotor contingency (SMC) theory of consciousness is proposed to account for conscious perception.
-It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}.
-The theory radically rejects the view that conscious content is associated with information encoded in internal representations in the neural system.
-Rather, the quality of conscious perception depends on agents' mastery of SMCs.
-SMC emphasises that the interaction between a system (the neural system) and its environment is crucial to form any specific form of conscious experience.
-
-    	    Our theory in general rejects this proposal based on the fundamental assumptions of SMC.As we mentioned in \ref{sec:Conscious versus Unconscious Processing}, a process directly maps the sensory state space to the action space should not be able to form NTIC.
-Because learning of contingencies between sensory input and action output doesn't guarantee to form any NTIC process, our theory predicts that sensorimotor contingency is neither a necessary nor a sufficient condition for conscious experience.
-In fact, with extensive practice on a sensorimotor task with a fixed contingency, the task usually can be gradually performed unconsciously \needref{}.
-We believe that the neural system has established a process to directly map sensory evidence to action selection, and therefore, decrease the level of NTIC which against the basic assumption of SMC.
-
-    	    Nevertheless, our theory does appreciate the notion that interactions between agents and environment is crucial to shape specific types of conscious experience.
-This is because, for an agent to form an NTIC process with action output, the process needs to encode how agents' actions influence state transitions in the environment.
-Therefore, information of interaction should be encoded in the NTIC process and also determines the state of NTIC which associates a particular conscious content.
-
-            Finally, a new version of SMC theory, Predictive Processing of SensoriMotor Contingencies (PPSMC), proposed by \cite{seth2014predictive, seth2015presence} makes some promising progress.
-PPSMC combines SMC and the predictive processing (see the next section) framework together and emphasises the importance of action counterfactual (i.e.
-the alternative and potential actions that an agent can perform) to conscious experience.
-We believe that the critical advance from SMC to PPSMC is to acknowledge the generative models for computing counterfactuals.
-The existence of generative models is the prerequisite equipped by the agents.
-So far, what PPSMC claims is deviating from simple $S\rightarrow{}R$ mappings and links the predictive information to consciousness.
-We argue that if predictive information for the computation of counterfactual is involved in the NTIC process, PPSMC will be compatable to our theory and may have strong explanatory power on some special conscious experience.
-\todo{Need a better ending}
+    		Sensorimotor contingency (SMC) theory of consciousness proposes that different types of SMCs give rise to different characteristics of conscious experience \citep{o2001sensorimotor}.
+The theory radically rejects the view that conscious content is associated with internal representations of a system.
+Rather, the quality of conscious experience depends on agents' mastery of SMCs.
+SMC emphasises that the interaction between a system and its environment determines conscious experience.
+
+    	    \ac{OurTheory} is not compatible with SMC due to the fundamental differences of assumptions of the two theories.
+As mentioned in Sec.~\ref{sec:Conscious versus Unconscious Processing}, a process directly maps the sensory states to the action states is insufficient to be NTIC.
+Therefore, learning contingencies between sensory inputs and action outputs does not imply NTIC.
+Hence, \ac{OurTheory} predicts that having sensorimotor contingencies is neither a necessary nor a sufficient condition for consciousness.
+In fact, empirically, with extensive training on a sensorimotor task with a fixed contingency, the task can be gradually performed unconsciously.
+This indicates that strong SMCs do not contribute conscious contents.
+In contrast, \ac{OurTheory} suggests that, with extensive training, the neural system establishes a neural mapping from sensory inputs to action outputs.
+This decrease the level of informational closure and, as a result, decrease the conscious level of this process.
+This outcome strongly supports \ac{OurTheory} than SMC.
+
+    	    Nevertheless, \ac{OurTheory} does appreciate the notion that interactions between a process and its environment is crucial to shape conscious experience.
+As mentioned above, to form NTIC, a process needs to encode environmental transitions into its own dynamic.
+Therefore, information of agent-environment interaction should also be encoded in the NTIC process, and therefore, shape conscious contents in a specific way.
+
+    	    Different from the classical SMC, a new version of SMC, Predictive Processing of SensoriMotor Contingencies (PPSMC), proposed by \cite{seth2014predictive, seth2015presence} PPSMC combines SMC and the predictive processing framework together.
+PPSMC emphasises the important role of generative models in computing counterfactual, inferring hidden causes of sensory signals, and linking fictive sensory signals to possible actions.
+We argue that if the generative model involving the NTIC process for the computation of counterfactual, PPSMC will be compatible to our theory and may have strong explanatory power on some special conscious experience.
 
@@
 		\subsection{Global workspace theory}
-		\needhelp{I think I need some help here.
+		Global workspace theory (GWT; \cite{baars1988cognitive, baars1997theatre, baars2002conscious}) or Global Neuronal Workspace theory (GNWT; \cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental}) states that the neural system consists of several specialised modules and a central global workspace (GW) which integrates and broadcasts information gathered from those specialised modules.
+Only the information in the global workspace reaches conscious awareness, and information outside of it remains unconscious.
+These modules compete with each other to gain the access to the GW and the information from the winner triggers an all-or-none "ignition" in the GW.
+Information in the GW is broadcasted to other modules.
+Conscious contents then are associates with the information that gains access to the internal global workspace \cite{Dehaene2017}.
+
+        While GWT emphasise the importance of global information sharing as a basis of consciousness, the precise meaning of information broadcasting has been somewhat unclear if one tries to describe it more formally in the language of information theory.
+\ac{OurTheory} offers one possible way to consider the meaning of broadcasting in GWT.
+Specifically, one could interpret the global workspace as the network of nodes where information is shared at the scale of NTIC where communication is performed through macro-variables that are linked via mutual predictability.
+That is, global workspace should be also NTIC.
+While this link remains speculative at this point, this interpretation encourages empirical studies into the relationship between the contents of consciousness and macrostate neural activities that are mutually predictive of each other.
+
+		=================================== Old  ===================================
+
+	    There are nearly no have no commonality between GWT and \ac{OurTheory}.
+In GWT, only information can be accessed by GW is conscious.
+However, it's always difficult to identify the GW because there is no clear computational definition for it.
+In \ac{OurTheory}, any process forming NTIC is conscious.
+Therefore, to determine whether a process is conscious is a decidable problem for \ac{OurTheory} but not for GWT.
+
+	    GWT claims that a module is not accessed by the GW is unconscious.
+
+		Currently, we don't have strong theoretical implications to relate \ac{OurTheory} to GWT. However, based on \ac{OurTheory},  reasoning
+
+		First, according to \ac{OurTheory}, consciousnesses occurs together with NTIC processes.
+Due to processes in the GW are accompanied by conscious experience, we suggest that the GW should occur at the scale where NTIC is formed.
+Second, notion of assess to GWS could be the state changes of the NTIC process at this coarse-grained level.
+Third, the all-or-none non-linear ignition may suggest the functions of coarse-graining are nonlinear.
+Finally, because NTIC encodes complex information about environmental states and dynamics,any state of the NTIC process can be seen as an integration of high dimensional information.
+
+		P-consciousness vs A=consciousness
+
+		Due to processes in the GW are accompanied by conscious experience, we can only postulate that the GW should occur at the scale where NTIC is formed. It is also likely that the
+
+		GWT proposes a number of core properties, e.g., stability, broadcasting, and non-linear ignition.
+
+		In \ac{OurTheory}, self-predictive information $I(Y_{t+1};Y_{t})$ is one of the quantity that contributes NTIC (Eq.~\ref{eq:nticObjective}).
+This property grantees the stability of a NTIC process.
+This outcome coincides with one of the GWT's claim that conscious contents often show stronger stability which may be necessary for the neural system to integrate information from a variety of modules.
+Although stability is claimed by both theories, the underliing reasons are different.
+GWT suggests that the neural mechanism to achieve stability is top-down amplifications from the GW to individual modules which gain the access to the GW.
+In contrast, \ac{OurTheory} suggests that stability is a natural consequence of NTIC without additional assumptions.
+
+		We will address this comparison in our following modelling paper.
+		Currently, we do not have concrete prediction about how an NTIC process reacts to rapid changes in the environment.
+		More modeling work is needed
+
+		However, regarding broadcasting and non-linear ignition
+
+		conjectures to bridge the two theories.
+
+		GW itself could be the NTIC process
+
+		similar or dissimilar
+
+		We suggests that the GW should occur at the scale where NTIC is formed. 
+		We further hypothesise that the GW recruits the NTIC process to achieve its functional goal and, therefore, is accompany by conscious experience.
+
+		Self-predictive information $I(Y_{t+1};Y_{t})$ is one of the quantity that contributes  NTIC (Eq.~\ref{eq:nticObjective}).
+This property grantees the stability of a NTIC process.
+This outcome coincides with one of the GWT's claim that conscious contents often show stronger stability which may be necessary for the neural system to integrate information from a variety of modules.Although stability is claimed by both theories, the proposed reasons are different.
+GWT suggests that the neural mechanism to achieve stability is top-down amplifications from the GW to individual modules which gain the access to the GW.
+In contrast, \ac{OurTheory} suggests that stability is a natural consequence of NTIC withour additional assumptions.
+
+		The notion of assess to GWS could be the access at the coarse grained level.
+
+		We suggest that when a coarse-grained variable becomes a part of the NTIC process. This makes information about the states of the variable occur in the conscious contents.
+
+% 		\needhelp{I think I need some help here.
 I am not sure what should I write here.
@@
 Without any modelling work on NTIC, it's difficult to say whether we will replicate those profiles of consciousness mentioned in GWT.}
-		\ideaBox{Need ending and better difference }
-		Global workspace theory (GWT; \cite{baars1988cognitive, baars1997theatre, baars2002conscious}) or Global Neuronal Workspace theory (GNWT; \cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental}) states that the neural system consists of several specialised modules and a central global workspace (GW) which integrates and broadcasts information amount these modules.
+% 		\ideaBox{Need ending and better difference }
+% 		Global workspace theory (GWT; \cite{baars1988cognitive, baars1997theatre, baars2002conscious}) or Global Neuronal Workspace theory (GNWT; \cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental}) states that the neural system consists of several specialised modules and a central global workspace (GW) which integrates and broadcasts information amount these modules.
 Only the information accessed by the global workspace can be consciously aware of.
@@
 
-		In many aspects, our theory can well accommodate GWT.
+% 		In many aspects, our theory can well accommodate GWT.
 NTIC processes shares several properties with the GW.
@@
 
-		% === Stability ===
-		Stability: GWT indicates that the conscious contents often show stronger stability which may be necessary for the neural system to integrate information from a variety of modules.
+% 		% === Stability ===
+% 		Stability: GWT indicates that the conscious contents often show stronger stability which may be necessary for the neural system to integrate information from a variety of modules.
 Suggested by GWT, this is caused by top-down amplification from the GW to individual modules which gain the access to the GW \needref{}.
@@
 
-		% === Broadcasting ===
-		\idea{A bit not sure about this part}Broadcasting: Because individual modules use different coding schemes, the neural system requires a mechanism for passing information between modules.
+% 		% === Broadcasting ===
+% 		\idea{A bit not sure about this part}Broadcasting: Because individual modules use different coding schemes, the neural system requires a mechanism for passing information between modules.
 GWT suggests that the GW is responsible for connecting the information source, translating the code, and finally making the information globally accessible.
@@
 
-        % === Non-linear ignition ===
-        Non-linear ignition: Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates \needhelp{Is this statement correct?}.
+%         % === Non-linear ignition ===
+%         Non-linear ignition: Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates \needhelp{Is this statement correct?}.
 Therefore, a continuous state transition at microscopic levels may lead to a discrete and non-linear state transition at macroscopic levels.
@@
 
-        \idea{Long distance connectivity?}
-        \rewrite{(1) sudden, all-or-none ignition of prefronto-parietal networks; (2) concomitant all-or-none ampliﬁcation of sensory activation; (3) a late global P3b wave in event-related potentials; (4) late ampliﬁcation of broad-band power in the gamma range; (5) enhanced longdistance phase synchronization, particularly in the beta range; and (6) enhanced causal relations between distant areas, including a signiﬁcant top-down component.
+%         \idea{Long distance connectivity?}
+%         \rewrite{(1) sudden, all-or-none ignition of prefronto-parietal networks; (2) concomitant all-or-none ampliﬁcation of sensory activation; (3) a late global P3b wave in event-related potentials; (4) late ampliﬁcation of broad-band power in the gamma range; (5) enhanced longdistance phase synchronization, particularly in the beta range; and (6) enhanced causal relations between distant areas, including a signiﬁcant top-down component.
 }
-        Future modeling work is needed
-
-		% -------------------------------- Difference -------------------------------- %
-		\todo{Finish this part}
-		However, there are still fundamental differences between the two theories. 
-		In GWT, modules rival with each other to gain access to the GW.
+%         Future modeling work is needed
+
+% 		% -------------------------------- Difference -------------------------------- %
+% 		\todo{Finish this part}
+% 		However, there are still fundamental differences between the two theories. 
+% 		In GWT, modules rival with each other to gain access to the GW.
 Our theory suggests that the one enters conscious contents is the one which can create the higher NTIC with other coarse-grained information.
@@
 
-		Up to now, GWT does not indicate in what conditions a process can be considered as a GW.
+% 		Up to now, GWT does not indicate in what conditions a process can be considered as a GW.
 This results in an intractable situation of finding the GW, especially when empirical data show distributed information encoded in many brain areas\citep{siegel2015cortical}.
 
-		Another difference between our theory and GWT is that our theory does not suggest a neuronal core anatomical area for consciousness.
+% 		Another difference between our theory and GWT is that our theory does not suggest a neuronal core anatomical area for consciousness.
 \todo{Link to Section 4}.
@@
 
-		In sum, our theory is compatible with previous physiological evidence supporting GWT.
+% 		In sum, our theory is compatible with previous physiological evidence supporting GWT.
 
@@
     \section{Limitation and Future work}\label{sec:Limitation and Future work}  
-        In this article, we propose the central proposition of our theory.
-We focused on convey the major concepts and mathematical formulation of the theory.
-In this section, we will discuss potential issues and challenges in the current version of \ac{OurTheory}.
+        In this article, we propose the first version of \ac{OurTheory} and introduce the central concepts, assumptions, and propositions.
+However, as a brand new theory of consciousness, \ac{OurTheory} is still far from completion.
+In the following, we discuss the current limitations and challenges of \ac{OurTheory} and point out the potential future research directions.
+
+        % =============================== Theoretical  ===============================
+
+        % Can't solve the hard problem
+        It's important to clarify that \ac{OurTheory} does not intend to completely solve the hard problems of consciousness \citep{chalmers1995facing}.
+Knowing the state of a conscious process does not allow us to answer "What is it like to be in this state of this process" \citep{nagel1974like}.
+Instead, \ac{OurTheory} focuses more on bridging consciousness and the physical world using information as a common language in between.
+%Therefore, \ac{OurTheory} cannot solve the inverted spectrum argument \citep{Shoemaker1982-SHOTIS, Block1990-BLOIE, Locke1979-LOCTCE-2} unless we can gain one more bit of information to distinguish whether the two processes are same or different.
+
+        %This means \ac{OurTheory} cannot solve the inverted spectrum argument \citep{Shoemaker1982-SHOTIS, Block1990-BLOIE, Locke1979-LOCTCE-2}.
 
         % Identity problem
-        Our theory is not complete yet. 
-        To identify an NTIC individuals and their boundaries, we can adopt the algorithm for computing individuality developed by \cite{krakauer2014information}.
-This algorithm defines an individual starting from a small set of variables and repeatedly computes individuality after adding more variables into the system.
-If the measure of individuality increase, the algorithm considers the new variables as the part of the system, and vise verse.
-However, this algorithm does not consider coarse-grained processes in a system (see "Caveats and challenges"\cite[p.
-13]{krakauer2014information}.
-
-        In the following articles, we will discuss the relationship between synergy and NTIC process
-
-        % Can't solve the hard problem
-        It's important to clarify that our theory does not intend to solve the hard problem of consciousness\citep{chalmers1995facing}.
-Our theory claims that different states of an NTIC process should map to different conscious contents.
-However, knowing the state of a conscious process does not allow us to answer "What is it like to be this system"\citep{nagel1974like}.
-We can consider a simplified version of the inverted spectrum argument \citep{Shoemaker1982-SHOTIS, Block1990-BLOIE, Locke1979-LOCTCE-2}.
-Two NTIC creatures (Alice "$A$" and Bob "$B$") living in a simple environment($E$) which has only two states $E_1$ and $E_2$.
-In this simple case, Alice and Bob should have only two states ($A_1, A_2$ and $B_1, B_2$) when they form the maximal level of NTIC (i.e.
-1 bit).
-Our theory can only claim that Alice has different conscious experience $\hat{A}_1$ and $\hat{A}_2$ at state $A_1$ and $A_2$, respectively (same as for $\hat{B}_1$ and $\hat{B}_2$ map to $B_1$ and $B_2$).
-However, there is no way to know whether $\hat{A}_1$ is the same as $\hat{B}_1$ or $\hat{B}_2$.
-
-        Instead, we believe that this is an ill-posed problem.
-Assuming that one day we know $\hat{A}_1$ is or is not the same as $\hat{b}_1$, this implies that we acquire at least 1 additional bit of information to make this judgement which does not exist within this simple system.
-Therefore, our theory is unable to answer the subjective quality that a conscious system feel like.
-
-        % boundary problem
-        In this paper, we claim that macroscopic level which forms NTIC from the system's environment is conscious. Anf
-
-        % Finding potential coarse-graining functions / coarse-grained computational units
-        \needhelp{I think I need Martin's help here, I don't know how much we should say about this in this paper. Or just leave this to the future studies}
-        A major empirical difficulty of our theory is to find appropriate aggregation functions which map microscopic variables to macroscopic variables forming an NTIC process.
-In this paper, we do not speculate any form of aggregation functions.
-It seems very difficult to find an appropriate one among infinite candidates\citep{price2007causation}.
-Nevertheless, relevant research has been exploring the mathematical relationship between aggregation functions and macroscopic processes \citep{PFANTE.2014}.
-\cite{Gamez2016} has also
-        systematically describe relevant issues in terms of finding data correlates of consciousness amount different levels of abstraction.
-These analyses are helpful to pin down the mathematical properties of the aggregation functions.
-
-        Another potential approach is to examine "readout" mechanisms in the neural system.
-To perform action outputs, information encoded in the NTIC process needs to be decoded by certain readout mechanisms.
-To investigate how the neural system decodes coarse-grained information may advance more understanding of the aggregation function.\ideaCallout{REALLY???}
-
-        Finally, with artificial neural networks as a universal function approximator, we can learn what aggregation functions the neural networks can learn when we set NTIC as the objective of training.
-
-        Since NTIC is a relatively new concept in neuroscience.
-Less empirical studies have examined this or relevant properties in the neural system so far.
-The lack of empirical data is a bottleneck of our current theory development.
-More empirical research targeting NTIC in the neural system is needed in the future.
+        The current version of \ac{OurTheory} cannot entirely solve the problem of individuality in some extreme circumstances.
+In common cases, one can identify individual consciousnesses by computing the levels of NTIC of a process.
+This approach can also be applied to finding the boundaries of individual consciousnesses (for details of the boundary detection procedure, see \cite{krakauer2014information}).
+However, in some spacial circumstances, individuality of consciousness has more than one outcome.
+For instance,
+            \needhelp{@Martin, if you think it's better to have a proof for this and if you don't mind, you can help me to write the proof here or create an appendix section and put it there.
+If you have no time, I can also do this.}
+        we can define a new process $Y$ and also its environment $E$ by recruiting two independent NTIC processes $Y^1~\&~Y^2$ and their environments $E^1~\&~E^2$, respectively.
+So that $Y = \{Y^1,Y^2\}$ and $E=\{E^1,E^2\}$.
+In such case, the new process $Y$ will also be NTIC to $E$.
+Therefore, the current version of \ac{OurTheory} cannot determine whether there are two smaller consciousnesses or one bigger consciousness (or 3 coexisting consciousnesses ).
+The problem of individuality is a significant theoretical weakness of the current version of \ac{OurTheory}.
+An intuitive solution is to recruit an "integration" quantity in our propositions.
+In our next theoretical article, we will discuss informational synergy and redundancy in the context of NTIC and consciousness.
+
+        % About the environment
+        The current version of \ac{OurTheory} assume that consciousness is only contributed by  non-trivial rather than trivial information encoded in a process.
+In other words, how much information about environmental states and dynamics encoded in a process is a key quantity for consciousness.
+However, we do not exclude the possibility that environmental information may be just a proxy of other informational quantities.
+So far, we can only claim NTIC is sufficient for consciousness.
+We are not able to draw further speculations.
+More theoretical work is needed.
+This issue will also be discuss in our next theoretical paper.
+
+        % ================================= Empirical ================================ 
+        % finding the coarse-graining function 
+        Empirically, a major challenge to \ac{OurTheory} is to find proper coarse-graining functions which map microscopic processes to macroscopic NTIC processes.
+This will become an imperative issue of find neurological supporting evidence for \ac{OurTheory}.
+To find proper coarse-graining functions among infinite candidates \citep{price2007causation} seem to be very challenging.
+Nevertheless, there are still theoretical and technical progresses recently that may contribute to  solving this issue.
+For example, the concept of \textit{causal emergence} proposed by Hoel \citep{Hoel19790, Hoel2018} has been further developed recently.
+Causal emergence is highly relevant to informational closure at coarse-grained levels.
+In their new study by \cite{klein2019uncertainty}, they started to compare how different coarse-graining functions influence causal emergence at macroscopic levels.
+\cite{PFANTE.2014, PFANTE.2014b} provides thorough mathematical analyses on level identification including informational closure.
+In neuroscience, the understanding of neural population codes also achieves a tremendous progress due to the advancement of recording technique and data science \citep{Kohn2016, panzeri2015neural}.
+\cite{Gamez2016} has also systematically describe relevant issues in terms of finding data correlates of consciousness amount different levels of abstraction.
+We believe that interdisciplinary research is required to narrow down the scope of searching the coarse-graining functions and conscious processes at the coarse-grained level in the neural system and beyond.
+
+        Finally another empirical challenge to \ac{OurTheory} is the lack of empirical supporting evidence.
+This is understandable because the concept of NTIC is relatively new in the history of information science, not to mention in neuroscience.
+Very few experiments and data collections are designed for examining NTIC properties in the neural system.
+To our knowledge, only two studies \citep{Palmer2015, sederberg2018learning} coincidentally examine similar properties in salamander retina.
+They found that the a large group of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states.
+The results, in line with the characteristic of NTIC.
+We expect that there will be more empirical studies examining the NTIC property in the neural system.
 
@@
     \section{Conclusion}
-	We introduce a new computational theory of consciousness based on two core assertions.
-First, consciousness occurs when a process forms NTIC.
-Second, in the neural system, coarse-graining is necessary to construct an NTIC process at macroscopic scales.
-Therefore, consciousness only appears at a certain macroscopic level which forms a high degree of NTIC.
-
-	Our theory is based on parsimonious assumptions.
-Nevertheless, it is able to, first, explain a large number of empirical findings in consciousness research and, second, reconcile several other theories of consciousness by the fundamental principles among them.
-
-	Our theory asserts that consciousness is informational-based phenomenon.
+	\todo{@Ryota, sorry that I didn't notify you I will rewrite the conclusion entirely. This is the new version. Please have a look.}
+    % short re-introduction 
+    In this paper, we introduced \textbf{\acf{OurTheory}}, a new informational theory of consciousness.
+Based on four assumptions, \ac{OurTheory} proposes that a process which forms \textbf{non-trivial informational closure (NTIC)} is sufficient to be conscious and through coarse-graining the neural system forms a NTIC process, i.e., a conscious process, at a certain macroscopic level.
+\ac{OurTheory} considers that information is a common language to bridge the gap between conscious experience and the physical reality.
+Using information theory, \ac{OurTheory} proposes computational definitions for both conscious level and conscious content.
+This makes \ac{OurTheory} be able to generalise to any system beyond the human brains.
+
+    % For neuroscience
+    \ac{OurTheory} provides explanation for various findings from research of conscious and unconscious processing.
+The implications of \ac{OurTheory} point out that the levels of coarse-graining play a critical role in searching for neural substrates of consciousness.
+Improper measurements, e.g., too fine or too coarse in terms of the scale of measurements, of neurophysiological signals may lead to misleading results and interpretations.
+
+    % For scientific theory of consciousness
+    \ac{OurTheory} reconciles several theories of consciousness.
+\ac{OurTheory} indicates that they conditionally coincide with \ac{OurTheory}'s implications and predictions but, however, not the fundamental and sufficient conditions for consciousness.
+For example, theories includes the theories emphasising recurrent circuits \citep{lamme2006towards, edelman1992bright}, the theories highlighting the internal simulation,  predictive mechanism, and generative models ~\citep{revonsuo2006inner, clark_2013,Hohwy2013,SethPP2014, kanai_chang_yu_de_abril_biehl_guttenberg_2019, seth2014predictive, seth2015presence}, and theories related to multilevel view of consciousness~\citep{pennartz2018consciousness,pennartz2015brain,prinz2007intermediate, jackendoff1987consciousness}.
+Notably, \ac{OurTheory} is proposed based on non-functional assumptions and propositions.
+Notwithstanding, its implications for the functional aspects of a system well fit the proposals from functionalist theories mentioned above.
+
+	% For philosophy of mind
+	Regarding philosophy of mind, \ac{OurTheory} connects several distinct arguments together.
+\ac{OurTheory} can be seen as an identity theory because it assumes a fundamental relation between consciousness and information.
+Second, the implications of \ac{OurTheory} tightly link consciousness to several cognitive functions in the context of evolution.
+This explains why people might intuitively have a functionalist point of view of consciousness.
+\ac{OurTheory} emphasises that informational closure between levels of coarse-graining is critical to form NTIC processes in some stochastic systems.
+In this case, especially for the neural system, forming conscious processes at the macroscopic levels coincide with the perspective of emergentism.
+Finally, forming NTIC (conscious) processes through many-to-one maps, i.e., coarse-graining, implies multiple realizability of consciousness.
+As a result, \ac{OurTheory} provides a integrated view for these arguments and is further capable of indicating how and why they are conditionally true.
+
+	% Final 
+	So far, the current version of \ac{OurTheory} is still far from completion.
+Further theoretical and empirical research is indispensably required for \ac{OurTheory} to improve and solve several issues in the current version.
+Nevertheless, \ac{OurTheory} offers explanation and prediction for consciousness science.
+We hope that \ac{OurTheory} provides a new way of thinking and understanding neural substrates of consciousness.
+
+%     ================================ Old version ===============================
+% 	In this paper, We introduced a new computational theory of consciousness based on two assertions.
+First, consciousness occurs when a process forms an NTIC.
+Second, in the neural system, construction of an NTIC process requires coarse graining.
+From these assumptions, it follows that consciousness only appears at a certain macroscopic level which forms a high degree of NTIC.
+	Our  theory offers an explanation for a large number of empirical findings in consciousness research and reconciles with several other theories of consciousness.
+
+% 	Our theory asserts that consciousness is an informational phenomenon.
 We further emphasise that the scale-dependent nature of information processing is critical to conscious experience.
@@
 
-	The computational nature of the theory makes it feasible to extrapolate and apply to other non-human systems.
+% 	The computational nature of the theory makes it feasible to extrapolate and apply to other non-human systems.
 Note that, even though our theory does not start from a functionalist point of view, it comes out with explanatory power on the functional aspect of consciousness and points out the evolutionary drive of having conscious processing.
 
-	Finally, we quote the famous epistemological questions: "If a tree falls in a forest and no one is around to hear it, does it make a sound?".
+% 	Finally, we quote the famous epistemological questions: "If a tree falls in a forest and no one is around to hear it, does it make a sound?".
 Now, we can ask a new version of this question: "If an action potential rises outside an informationally closed process, does it make any conscious percept to this process?" We answer: "if the process is conscious, the event occurring outside the realm of the informational closure should never become part of the conscious contents."
@@
 	\section*{Funding}
-
+        \needhelp{@Ryota, could you help me with this part?}
 	\section*{Acknowledgements}

### 2019-09-23 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC.
-(for the level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
+(for a discussion of the distinction between level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
 
@@
 			\includegraphics[width=\textwidth]{WritingMaterials/Fig_ScaleProblemOfConsciousness/ScaleProblemOfConsciousness.pdf}
-			\caption{The scale problem of consciousness: Human conscious experience does not reflect information processed at every scale.
-Only information at a certain coarse-grained scale in the neural system is conscious.}
+			\caption{The scale problem of consciousness: Human conscious experience does not reflect information from every scale.
+Only information at a certain coarse-grained scale in the neural system is reflected in consciousness.}
 			\label{fig:scaleproblem}
@@
 The concept of closure is closely related to system identification in systems theory.
-One can distinguish a system from its environment by computing the closeness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}.
+One can distinguish a system from its environment by computing the closedness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}.
 The closure can be further quantified by information theory.
@@
 			\noindent
-			This implies the system contains in itself all the information about its own future and the self-predictive information is gained from the information about the environment.
+			This implies the system contains in itself all the information about its own future and the self-predictive information contains the information about the environment.
 Therefore, to form NTIC, the system can internalise and synchronise with the dynamics of the environment, i.e.
-modelling the environment.
+model the environment.
 Furthermore, having high degrees of NTIC entails having high predictive power about the environment.
@@
 
-			% Practically, \cite{guttenberg2016neural} proposed that NTIC can be formed by maximising the predictive power about the environment and the self-predictive information of the system concurrently.
-
-			% Biological evidence of informational closure in the neural system
-            % 			Despite the significant advantage for biological systems to form NTIC, to our knowledge, there are only a few studies directly examining NTIC in biological systems.
-Recent studies have shown relevant properties in the visual system of salamanders.
-Two studies \citep{Palmer2015, sederberg2018learning} examined salamander retina and found that the a large group of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states (see Fig.~\ref{fig:sederberg2018learning}), therefore, in line with the characteristic of NTIC.
-Therefore, the self-predictive information of the neural populations can guide prediction about external stimuli without reference to stimulus parameters explicitly.
-Moreover, the internal predictability can be generalised to different stimulus classes suggesting the tendency to internalise the information of environmental dynamics in the neural populations.
-\toWrite{Add Some ending sentences}
-
-            % 			\begin{figure}[H]
-            % 				\includegraphics[width=\textwidth]{WritingMaterials/Fig_Sederberg/Fig_Sederberg.pdf}
-            % 				\caption{Figure adapted from \cite{sederberg2018learning}}
-            % 				\label{fig:sederberg2018learning}
-            % 			\end{figure}
-
 % ============================================================================ %
@@
 % ============================================================================ %
-	\section{Coarse-graining in The Neural System} \label{sec:Neural coarse-graining}
+	\section{Coarse-graining in the Neural System} \label{sec:Neural coarse-graining}
 
 		%% stochasticity at microscopic levels
-		Despite evolutionary advantage of having NTIC processes in a system, however, the formation of NTIC witha  highly stochastic process is challenging.
+		The formation of NTIC with a  highly stochastic process is challenging.
 NTIC requires the predictability of the system state and is therefore impeded by noise in the system.
@@
         %% Our argument
-		However, we argue that, neural systems can form NTIC at certain macroscopic levels through coarse-graining of microscopic neural states.
+		However, it is possible that neural systems form NTIC at certain macroscopic levels through coarse-graining of microscopic neural states.
+
 		Coarse-graining refers to many-to-one functions which aggregate microscopic states to a macroscopic state.
 In other words, a number of different micro-states correspond to the same value of the macro-variable \citep{price2007causation}.
-Neural systems, therefore, can form more stable and deterministic state transitions and be more capable of forming NTIC processes at certain coarse-grained macroscopic levels.
-
-		Indeed, empirical evidence suggests that coarse-graining is a common coding strategy to establish robustness against noise at microscopic levels of the the neural system.
-For instance, the inter-spike intervals of individual neurons are stochastic.
-This implies that the state of individual neurons cannot be used for encoding and representing stable information.
+Coarse-grainings, can therefore form more stable and deterministic state transitions and more often form NTIC processes.
+
+		For neural systems this means that a microscopically noisy neural system may still give rise to an NTIC process
+		on a more macroscopic scale.
+
+		In neural systems such coarse-grainings have been observed to represent external stimuli in empirical studies.
+
+		=== so, to here, it's fine ===
+		Because coarse-graining is an effective way to create stable variables, a stochastic system (e.g., neural systems) can represent information stably by encoding information using coarse-grained macroscopic variables.
+
+		============================================================================
+
+		Indeed, empirical evidence suggests that coarse-graining is a common coding strategy to establish robustness against noise at microscopic levels of the neural system.
+For instance, the inter-spike intervals of an individual neuron are stochastic.
+This implies that the state of an individual neuron does not represent stable information.
 However, the firing rate, i.e.
 the average spike counts over a given time interval, is more stable and robust against noise such as the variability in inter-spike intervals.
-Using this temporal coarse-graining strategy, known as the rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}, neurons can encode stimulus intensity by increasing or decreasing the firing rate \citep{kandel2000principles}.
+Using this temporal coarse-graining strategy, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}, neurons can encode stimulus intensity by increasing or decreasing the firing rate \citep{kandel2000principles}.
 \citep{stein2005neuronal}.
@@
 In this coding scheme, information is encoded by activation patterns of a set of neurons (a neuron population).
-In the population coding scheme, many states for a neuron population map to the same information content, thereby reducing the influence of noise in individual neurons.
-That is, stable representations can be formed through coarse-graining a high dimensional state space of a neuron population to a low dimensional state space of encoded contents \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
-Therefore, individual neuron states (the microscopic level) are not informative about the encoded contents at the population level (the macroscopic level).
+In the population coding scheme, many states for a neuron population map to the same state of encoded information, thereby reducing the influence of noise in individual neurons.
+That is, stable representations can be formed through coarse-graining the high dimensional state space of a neuron population to a lower dimensional macroscopic state space \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
+Therefore, individual neuron states (the microscopic level) are not informative enough about the full encoded contents at the population level (the macroscopic level).
 Instead, coarse-grained variables are better substrates for stably encoding information and allow the neural system to ignore noisy interactions at the fine-grained level \citep{Woodward2007-WOOCWA}.
@@
 
-        The first assumption is that every human conscious precept is informative.
+        The first assumption is that every human conscious percept is informative.
 Here, "informative" refers to the resolution of uncertainty.
@@
 This is in line with the impression that our conscious experience consist of multi-dimensional information and usually involves information from multiple modalities.
-Therefore, every human conscious precept resolves some amount of uncertainty and provides information.
-
-        This assumption is also in agreement with one of the "axiom", \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.2]{oizumi2014phenomenology}.
+Therefore, every human conscious percept resolves some amount of uncertainty and provides information.
+
+        This assumption is also in agreement with the "axiom" of \textit{information} in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.2]{oizumi2014phenomenology}.
 
@@
 
-        The third assumption is that no consciousness can contain information of the entire universe.
+        === How about if I change this ===
+        The third assumption is that no consciousness can contain complete information about the universe.
 This means that there exists a informational boundary for every consciousness, i.e.
@@
 
+        === to this ===
+        The third assumption is that there exists a informational boundary for every consciousness.
+The informational boundary here means that no consciousness can contain information of the entire universe and every consciousness is informationally closed to the the universe.
+This is in line with our conscious experience that information provided by every conscious percept is limited.
+
         Together with the first three assumptions, this means that the physical representations of the contents of any consciousness must be a coarse-graining of the universe states and also informationally closed to the universe.
@@
         Note that a coarse-grained process $Y$ can be a coarse-graining of another coarse-grained process $S$ of the universe $X$ (see Fig.~\ref{fig:fullgraph}).
-Here, we consider $S$ is a dynamic system and $Y$ is a coarse-grained process of the system $S$.
-Therefore, the environment $E$ of $S$ is also a coarse-graining of the universe.
-Importantly, in such case, if a macroscopic process $Y$ is informationally closed to the universe $X$, this implies $Y$ is also informationally closed to the microscopic level of the system $S$ and the environment $E$.
+Here, we consider $S$ as a coarse-graining of $X$ and call it the system.
+Then $Y$ is a coarse-graining of the system $S$.
+We can then also define another coarse-graining of $X$ called the environment $E$ of $S$.
+This is the coarse-graining that contains the information about $X$ that is not contained in $S$.
+Importantly, in this case, if a macroscopic process $Y$ is informationally closed to the universe $X$, this implies $Y$ is also informationally closed to both the system $S$ and the environment $E$.
 
@@
         This results in a crucial implication that informational closure can occur between levels in a system.
-The macroscopic level $Y$ can be informationally closed to the microscopic level $S$ within a system \citep{PFANTE.2014}.
+The macroscopic level $Y$ can be informationally closed to its microscopic level $S$ within a system \citep{PFANTE.2014}.
 
@@
 
-        A concrete example in the context of neuroscience is that $X$, $S$, $Y$, and $E$ represent the microscopic level of the universe, a cellular level process in the neural system, a macroscopic process of the neural system coarse-grained from the cellular level process $S$, and the environment which the cellular level process $S$ interacts with which may includes other processes in the neural system, the sensors for perception and interoception, and external physical worlds, respectively.
+        A concrete example in the context of neuroscience is that $X$ represents the microscopic level of the universe, $S$ a cellular level process in the neural system, $Y$ a more macroscopic process of the neural system coarse-grained from the cellular level process $S$, and $E$ the environment which the cellular level process $S$ interacts with.
+The environment $E$ may includes other processes in the neural system, the sensors for perception and interoception, and external physical worlds, respectively.
 
@@
 More precisely, there exists a certain degree of mutual information between conscious processes and the environments which it interacts with.
-As mentioned in Sec.\ref{sec:Non-trivial informational closure} regardless one process is informationally closed to another one, to form mutual information between the two processes, i.e.
-NTIC, is still possible.
-Therefore, a macroscopic process $Y$ can be NTIC to the system's environment $E$ and concurrently be informationally closed to its microscopic process $S$.
+As mentioned in Sec.\ref{sec:Non-trivial informational closure} a process can be informationally closed to another one and still have mutual information with it, i.e.
+be NTIC.
+Therefore, a macroscopic process $Y$ can be NTIC to the system's environment $E$ and at the same time be informationally closed to its microscopic process $S$.
 In other words, the macroscopic process can encode environmental information (by forming NTIC) and, however, be ignorant to its microscopic processes (IC).
@@
 
-		    %For example, a human brain may be a part of a conscious process at human society level. However, due to the informational closure, we should have no information about it in our consciousness.
-
 		    \textbf{Prediction after system damaged}: \ac{OurTheory} and IIT lead to different predictions when a system suffers from a damage.
@@
 
-		=================================== Old  ===================================
-
-	    There are nearly no have no commonality between GWT and \ac{OurTheory}.
+% 		=================================== Old  ===================================
+
+% 	    There are nearly no have no commonality between GWT and \ac{OurTheory}.
 In GWT, only information can be accessed by GW is conscious.
@@
 
-	    GWT claims that a module is not accessed by the GW is unconscious.
-
-		Currently, we don't have strong theoretical implications to relate \ac{OurTheory} to GWT. However, based on \ac{OurTheory},  reasoning
-
-		First, according to \ac{OurTheory}, consciousnesses occurs together with NTIC processes.
+% 	    GWT claims that a module is not accessed by the GW is unconscious.
+
+% 		Currently, we don't have strong theoretical implications to relate \ac{OurTheory} to GWT. However, based on \ac{OurTheory},  reasoning
+
+% 		First, according to \ac{OurTheory}, consciousnesses occurs together with NTIC processes.
 Due to processes in the GW are accompanied by conscious experience, we suggest that the GW should occur at the scale where NTIC is formed.
@@
 
-		P-consciousness vs A=consciousness
-
-		Due to processes in the GW are accompanied by conscious experience, we can only postulate that the GW should occur at the scale where NTIC is formed. It is also likely that the
-
-		GWT proposes a number of core properties, e.g., stability, broadcasting, and non-linear ignition.
-
-		In \ac{OurTheory}, self-predictive information $I(Y_{t+1};Y_{t})$ is one of the quantity that contributes NTIC (Eq.~\ref{eq:nticObjective}).
+% 		P-consciousness vs A=consciousness
+
+% 		Due to processes in the GW are accompanied by conscious experience, we can only postulate that the GW should occur at the scale where NTIC is formed. It is also likely that the
+
+% 		GWT proposes a number of core properties, e.g., stability, broadcasting, and non-linear ignition.
+
+% 		In \ac{OurTheory}, self-predictive information $I(Y_{t+1};Y_{t})$ is one of the quantity that contributes NTIC (Eq.~\ref{eq:nticObjective}).
 This property grantees the stability of a NTIC process.
@@
 
-		We will address this comparison in our following modelling paper.
-		Currently, we do not have concrete prediction about how an NTIC process reacts to rapid changes in the environment.
-		More modeling work is needed
-
-		However, regarding broadcasting and non-linear ignition
-
-		conjectures to bridge the two theories.
-
-		GW itself could be the NTIC process
-
-		similar or dissimilar
-
-		We suggests that the GW should occur at the scale where NTIC is formed. 
-		We further hypothesise that the GW recruits the NTIC process to achieve its functional goal and, therefore, is accompany by conscious experience.
-
-		Self-predictive information $I(Y_{t+1};Y_{t})$ is one of the quantity that contributes  NTIC (Eq.~\ref{eq:nticObjective}).
+% 		We will address this comparison in our following modelling paper.
+% 		Currently, we do not have concrete prediction about how an NTIC process reacts to rapid changes in the environment.
+% 		More modeling work is needed
+
+% 		However, regarding broadcasting and non-linear ignition
+
+% 		conjectures to bridge the two theories.
+
+% 		GW itself could be the NTIC process
+
+% 		similar or dissimilar
+
+% 		We suggests that the GW should occur at the scale where NTIC is formed. 
+% 		We further hypothesise that the GW recruits the NTIC process to achieve its functional goal and, therefore, is accompany by conscious experience.
+
+% 		Self-predictive information $I(Y_{t+1};Y_{t})$ is one of the quantity that contributes  NTIC (Eq.~\ref{eq:nticObjective}).
 This property grantees the stability of a NTIC process.
@@
 
-		The notion of assess to GWS could be the access at the coarse grained level.
-
-		We suggest that when a coarse-grained variable becomes a part of the NTIC process. This makes information about the states of the variable occur in the conscious contents.
+% 		The notion of assess to GWS could be the access at the coarse grained level.
+
+% 		We suggest that when a coarse-grained variable becomes a part of the NTIC process. This makes information about the states of the variable occur in the conscious contents.
+
+		% ================================= Super old ================================ %
 
@@
     \section{Conclusion}
-	\todo{@Ryota, sorry that I didn't notify you I will rewrite the conclusion entirely. This is the new version. Please have a look.}
     % short re-introduction 

### 2019-09-24 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 % ============================================================================ %
-\author[]{Acer Y.C. Chang\thanks{acercyc@araya.org}}
+\author[]{Acer Y.C. Chang\thanks{Corresponding author, acercyc@araya.org}}
 \author[]{Martin Biehl\thanks{martin@araya.org}}
@@
 		However, it is possible that neural systems form NTIC at certain macroscopic levels through coarse-graining of microscopic neural states.
-
 Coarse-graining refers to many-to-one functions which aggregate microscopic states to a macroscopic state.
@@
 Coarse-grainings, can therefore form more stable and deterministic state transitions and more often form NTIC processes.
-
-		For neural systems this means that a microscopically noisy neural system may still give rise to an NTIC process
-		on a more macroscopic scale.
-
-		In neural systems such coarse-grainings have been observed to represent external stimuli in empirical studies.
-
-		=== so, to here, it's fine ===
-		Because coarse-graining is an effective way to create stable variables, a stochastic system (e.g., neural systems) can represent information stably by encoding information using coarse-grained macroscopic variables.
-
-		============================================================================
+For neural systems this means that a microscopically noisy neural system may still give rise to an NTIC process on a more macroscopic scale.
 
@@
 In this coding scheme, information is encoded by activation patterns of a set of neurons (a neuron population).
-In the population coding scheme, many states for a neuron population map to the same state of encoded information, thereby reducing the influence of noise in individual neurons.
+In the population coding scheme, many states for a neuron population map to the same state of macroscopic variables which encode particular informational contents, thereby reducing the influence of noise in individual neurons.
 That is, stable representations can be formed through coarse-graining the high dimensional state space of a neuron population to a lower dimensional macroscopic state space \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
@@
 Based on the merit of coarse-graining in neural systems, We propose a theory of consciousness in the next section.
-
-% 		% neural coarse-graining by Nic
-% 		The practical implementation mentioned above suggests that  NTIC can be formed by coarse-graining sensory inputs in artificial neural networks.
-\citep{guttenberg2016neural} proposed a "neural coarse-graining (NCG)" architecture which aims to capture the emergent large-scale dynamics in the environment.
-The NCG network learns to coarse-grain input signals and extract latent variables which are both predictive and predictable in the input signal and therefore form NTIC.
 
@@
 
-        The first assumption is that every human conscious percept is informative.
-Here, "informative" refers to the resolution of uncertainty.
+        % ---------------------------------------------------------------------------- %
+        %                             Ryota's common backup                            %
+        % ---------------------------------------------------------------------------- %
+            % kanair: I suggest that we cut all of this.
+            % Sep 15, 2019 12:52 AM
+
+            % The 3 assumptions - Information - Necessity of Physical substrate - Boundary The main proposal is not necessarily derived from these assumptions.
+If anything, our theory is entirely on the boundary issue, namely, consciousness occurs at a particular scale.
+            % Sep 15, 2019 12:53 AM
+
+            % I understand that for a theory to be complete, we want to specify the assumptions here, but I felt these are distracting, because their relevance to the current theory is somewhat weak.
+            % Sep 15, 2019 12:55 AM
+
+            % Instead of delving into these assumptions, we should describe the main claims of the theory directly.
+        % ---------------------------------------------------------------------------- %
+
+        The first assumption is that consciousness is information.
+Every human conscious percept is informative.
+Here, "information" refers to the resolution of uncertainty.
 Being in a certain conscious state rules out a number of other possible conscious states.
@@
         Second, we further assume that all information requires physical substrates. 
-        From these two assumptions, it follows that the amount of (self-)information possessed by a conscious percept must be equal to the (self-)information of a particular event or entity in the physical reality.
+        From these two assumptions, it follows that for every conscious percept there exists a corresponding physical event whose self-information is is equal to the self-information of the percept.
+        % the amount of (self-)information possessed by a conscious percept must be equal to the (self-)information of a particular event or entity in the physical reality.
 
@@
 Therefore, a macroscopic process $Y$ can be NTIC to the system's environment $E$ and at the same time be informationally closed to its microscopic process $S$.
-In other words, the macroscopic process can encode environmental information (by forming NTIC) and, however, be ignorant to its microscopic processes (IC).
+In other words, the macroscopic process can encode environmental information (by forming NTIC), however, be ignorant to part of the information of its microscopic processes.
 This is in line with our conscious experience that information that every conscious percept provides represent rich and structured environmental states without involving much information at microscopic activities.
@@
             First, to form a high level of NTIC, one can increase the mutual information $I(Y_{t+1};Y_{t})$ between the current internal state $Y_t$ and the future internal state $Y_{t+1}$.
-In other words, conscious levels are associated with the degree of self-predictive information.
+In other words, conscious levels are associated with the degree of self-predictive information \citep{bialek2001predictability}.
 This mutual information term can be further decomposed to two information entropy quantities:
@@
 This quantity suggests that conscious level increases with the amount of information about the environment state $E_t$ that the NTIC process encodes in its own state $Y_t$.
+In other words, $Y_t$ should not contain more information about $Y_{t+1}$ than $E_t$.
 An important implication is that agents interacting with a complex environment have the chance to build a higher level of NTIC within their systems than those living in a simple environment.
@@
 
+		    \textbf{The concept of "integration"}: In IIT, integrated information is one of the core concept of defining conscious individuals.
 In the current paper, we did not include the notion of integrated information within \ac{OurTheory}.
-However, one of the current weaknesses of \ac{OurTheory} is that it lacks the ability to individuate NTIC processes as distinct entities because a macro-process composed of two independent NTIC processes is also an NTIC.
-This is a severe limitation of our current theory.
-The notion of integration is a possible remedy for this issue and we hope to address this more explicitly in future work using the concept of synergy.
+This, however, results in one of the current weaknesses of \ac{OurTheory} that it lacks the ability to individuate NTIC processes in some extreme cases (i.e., the problem of individuality).
+We discussed this weaknesses in Sec.~\ref{sec:Limitation and Future work}.
 
@@
 While this link remains speculative at this point, this interpretation encourages empirical studies into the relationship between the contents of consciousness and macrostate neural activities that are mutually predictive of each other.
-
-% 		=================================== Old  ===================================
-
-% 	    There are nearly no have no commonality between GWT and \ac{OurTheory}.
-In GWT, only information can be accessed by GW is conscious.
-However, it's always difficult to identify the GW because there is no clear computational definition for it.
-In \ac{OurTheory}, any process forming NTIC is conscious.
-Therefore, to determine whether a process is conscious is a decidable problem for \ac{OurTheory} but not for GWT.
-
-% 	    GWT claims that a module is not accessed by the GW is unconscious.
-
-% 		Currently, we don't have strong theoretical implications to relate \ac{OurTheory} to GWT. However, based on \ac{OurTheory},  reasoning
-
-% 		First, according to \ac{OurTheory}, consciousnesses occurs together with NTIC processes.
-Due to processes in the GW are accompanied by conscious experience, we suggest that the GW should occur at the scale where NTIC is formed.
-Second, notion of assess to GWS could be the state changes of the NTIC process at this coarse-grained level.
-Third, the all-or-none non-linear ignition may suggest the functions of coarse-graining are nonlinear.
-Finally, because NTIC encodes complex information about environmental states and dynamics,any state of the NTIC process can be seen as an integration of high dimensional information.
-
-% 		P-consciousness vs A=consciousness
-
-% 		Due to processes in the GW are accompanied by conscious experience, we can only postulate that the GW should occur at the scale where NTIC is formed. It is also likely that the
-
-% 		GWT proposes a number of core properties, e.g., stability, broadcasting, and non-linear ignition.
-
-% 		In \ac{OurTheory}, self-predictive information $I(Y_{t+1};Y_{t})$ is one of the quantity that contributes NTIC (Eq.~\ref{eq:nticObjective}).
-This property grantees the stability of a NTIC process.
-This outcome coincides with one of the GWT's claim that conscious contents often show stronger stability which may be necessary for the neural system to integrate information from a variety of modules.
-Although stability is claimed by both theories, the underliing reasons are different.
-GWT suggests that the neural mechanism to achieve stability is top-down amplifications from the GW to individual modules which gain the access to the GW.
-In contrast, \ac{OurTheory} suggests that stability is a natural consequence of NTIC without additional assumptions.
-
-% 		We will address this comparison in our following modelling paper.
-% 		Currently, we do not have concrete prediction about how an NTIC process reacts to rapid changes in the environment.
-% 		More modeling work is needed
-
-% 		However, regarding broadcasting and non-linear ignition
-
-% 		conjectures to bridge the two theories.
-
-% 		GW itself could be the NTIC process
-
-% 		similar or dissimilar
-
-% 		We suggests that the GW should occur at the scale where NTIC is formed. 
-% 		We further hypothesise that the GW recruits the NTIC process to achieve its functional goal and, therefore, is accompany by conscious experience.
-
-% 		Self-predictive information $I(Y_{t+1};Y_{t})$ is one of the quantity that contributes  NTIC (Eq.~\ref{eq:nticObjective}).
-This property grantees the stability of a NTIC process.
-This outcome coincides with one of the GWT's claim that conscious contents often show stronger stability which may be necessary for the neural system to integrate information from a variety of modules.Although stability is claimed by both theories, the proposed reasons are different.
-GWT suggests that the neural mechanism to achieve stability is top-down amplifications from the GW to individual modules which gain the access to the GW.
-In contrast, \ac{OurTheory} suggests that stability is a natural consequence of NTIC withour additional assumptions.
-
-% 		The notion of assess to GWS could be the access at the coarse grained level.
-
-% 		We suggest that when a coarse-grained variable becomes a part of the NTIC process. This makes information about the states of the variable occur in the conscious contents.
-
-		% ================================= Super old ================================ %
-
-% 		\needhelp{I think I need some help here.
-I am not sure what should I write here.
-Or  what position I should take.
-To some extent, GWT is a very qualitative theory.
-It kind of just summarises everything.
-Without any modelling work on NTIC, it's difficult to say whether we will replicate those profiles of consciousness mentioned in GWT.}
-% 		\ideaBox{Need ending and better difference }
-% 		Global workspace theory (GWT; \cite{baars1988cognitive, baars1997theatre, baars2002conscious}) or Global Neuronal Workspace theory (GNWT; \cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental}) states that the neural system consists of several specialised modules and a central global workspace (GW) which integrates and broadcasts information amount these modules.
-Only the information accessed by the global workspace can be consciously aware of.
-These modules competes with each other to gain the access to the GW and the information from the winner can trigger an all-or-none "ignition" in the GW.
-Information in the GW is able to be broadcasted to other modules.
-Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}.
-
-% 		In many aspects, our theory can well accommodate GWT.
-NTIC processes shares several properties with the GW.
-Here we discuss three core properties, stability, broadcasting, and non-linear ignition, emphasised by the GWT.
-
-% 		% === Stability ===
-% 		Stability: GWT indicates that the conscious contents often show stronger stability which may be necessary for the neural system to integrate information from a variety of modules.
-Suggested by GWT, this is caused by top-down amplification from the GW to individual modules which gain the access to the GW \needref{}.
-In contrast, without assuming any additional mechanism, our theory argues that stability is a natural quality of NTIC due to its strong self-predictive characteristic.
-Our theory can even further quantify the stability of conscious contents by computing the mutual information between the current and the future states of a conscious process.
-
-% 		% === Broadcasting ===
-% 		\idea{A bit not sure about this part}Broadcasting: Because individual modules use different coding schemes, the neural system requires a mechanism for passing information between modules.
-GWT suggests that the GW is responsible for connecting the information source, translating the code, and finally making the information globally accessible.
-We argue that, because the NTIC process encodes high dimensional information about the environmental dynamics, it can be considered as an integrated informational entity \todo{Need rewording}.
-These with the coarse-graining variables involved in the NTIC process together.
-Other modules outside the NTIC process can decode and extract needed information for the current goal of the task.
-
-%         % === Non-linear ignition ===
-%         Non-linear ignition: Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates \needhelp{Is this statement correct?}.
-Therefore, a continuous state transition at microscopic levels may lead to a discrete and non-linear state transition at macroscopic levels.
-Based on our theory, when new information enters conscious contents, the NTIC process must undergo a corresponding state transition.
-This transition can trigger a significant change of the brain states and resembles non-linear ignition of brain activities
-
-%         \idea{Long distance connectivity?}
-%         \rewrite{(1) sudden, all-or-none ignition of prefronto-parietal networks; (2) concomitant all-or-none ampliﬁcation of sensory activation; (3) a late global P3b wave in event-related potentials; (4) late ampliﬁcation of broad-band power in the gamma range; (5) enhanced longdistance phase synchronization, particularly in the beta range; and (6) enhanced causal relations between distant areas, including a signiﬁcant top-down component.
-}
-%         Future modeling work is needed
-
-% 		% -------------------------------- Difference -------------------------------- %
-% 		\todo{Finish this part}
-% 		However, there are still fundamental differences between the two theories. 
-% 		In GWT, modules rival with each other to gain access to the GW.
-Our theory suggests that the one enters conscious contents is the one which can create the higher NTIC with other coarse-grained information.
-This difference leads very different predictions and implications.
-For GWT, to find the biological implementation of the rivalry mechanism (attention, for example) is critical.
-However, we do not assume any rivalry mechanism.
-Instead, we argue that, if  information carried by the coarse-grained variables can increase the predictability of the process and form high NTIC,  it naturally form a informationally closed boundary and
-
-% 		Up to now, GWT does not indicate in what conditions a process can be considered as a GW.
-This results in an intractable situation of finding the GW, especially when empirical data show distributed information encoded in many brain areas\citep{siegel2015cortical}.
-
-% 		Another difference between our theory and GWT is that our theory does not suggest a neuronal core anatomical area for consciousness.
-\todo{Link to Section 4}.
-Coarse-grained information in NTIC is more crucial for consciousness rather than neural substrates supporting the global workspace.
-
-% 		In sum, our theory is compatible with previous physiological evidence supporting GWT.
 
@@
 The problem of individuality is a significant theoretical weakness of the current version of \ac{OurTheory}.
-An intuitive solution is to recruit an "integration" quantity in our propositions.
-In our next theoretical article, we will discuss informational synergy and redundancy in the context of NTIC and consciousness.
+The notion of integration is a possible remedy for this issue and we will address this issue more explicitly in future work using the concept of synergy.
 

### 2019-09-26 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 % \excludeversion{backup}
+
+\usepackage{amsthm}
+
+% \theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem*{hypothesis}{Hypothesis}
+
+\newcommand{\cp}{C-process} 
+\newcommand{\cps}{C-processes}
 
@@
 \newacro{OurTheory}[ICT]{Information Closure Theory of Consciousness}
+\newacro{cp}{C-process}
 
@@
 \title{Information Closure Theory of Consciousness}
+\date{}
 
@@
 Neurophysiological evidence suggests that conscious experiences co-vary with information encoded in coarse-grained neural states such as the firing pattern of a population of neurons.
-In this article, we assume that conscious experience is confined due to informational closure from conscious processing to other coarse-grained levels.
-From this and three additional assumptions, we propose a new computational theory of consciousness: \ac{OurTheory}.
+In this article, we introduce a new informational theory of consciousness: \acf{OurTheory}.
+We hypothesise that conscious processes are processes which form \ac{ntic} with respect to the environment at certain coarse-grained levels.
+This hypothesis implies that conscious experience is confined due to informational closure from conscious processing to other coarse-grained levels.
 \ac{OurTheory} proposes new quantitative definitions of both conscious content and conscious level.
-With the parsimonious assumptions and simple propositions, \ac{OurTheory} provides explanations and predictions of phenomena associated with consciousness.
+With the parsimonious definitions and a hypothesise, \ac{OurTheory} provides explanations and predictions of various phenomena associated with consciousness.
 The implications of \ac{OurTheory} naturally reconciles issues in many existing theories of consciousness and provides explanations for many of our intuitions about consciousness.
-Most importantly, \ac{OurTheory} indicates that information is the common language bridging consciousness and physical reality.
+Most importantly, \ac{OurTheory} demonstrates that information can be the common language between consciousness and physical reality.
 
@@
 	\section*{Keywords:}
-	Keywords: consciousness, informational closure, neural coarse-graining, level of analysis
+	Keywords: consciousness, informational closure, non-trivial informational closure, coarse-graining, level of analysis,
 
@@
 		In this article, we propose a new information-based theory of consciousness, called \ac{OurTheory}.
-We argue that every process with a high degree of non-trivial information closure (NTIC) has consciousness.
+We argue that every process with a positive non-trivial information closure (NTIC) has consciousness.
 This means that the state of such a process corresponds one-to-one to conscious content.\footnote{In the following IC stands for "informational closure" or "informationally closed" and NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}.
@@
 			And, non-trivial informational closure can be defined as
-				\begin{equation}
+				\begin{align}
 				\label{eq:NTIC}
-    				\left.\begin{array}
-    				{rl}{NTIC} & {:=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t})}
-    				\end{array} \right.
-				\end{equation}
+    				% \left.\begin{array}
+    				NTIC_t(E\rightarrow Y) :&=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t})\\
+    				&=I(Y_{t+1};E_{t})-I(Y_{t+1};E_{t}|Y_{t})
+    				% \end{array} \right.
+				\end{align}
+
+% 			\noindent
+%             The definition can also be re-arranged as 
+% 				\begin{equation}
+% 				\label{eq:NTIC2}
+%     				\left.\begin{array}
+%     				{rl}{\qquad} & {\ =I(Y_{t+1};E_{t})-I(Y_{t+1};E_{t}|Y_{t})}
+%     				\end{array} \right.
+% 				\end{equation}
 
 			\noindent
-            The definition can also be re-arranged as 
-				\begin{equation}
-				\label{eq:NTIC2}
-    				\left.\begin{array}
-    				{rl}{\qquad} & {\ =I(Y_{t+1};E_{t})-I(Y_{t+1};E_{t}|Y_{t})}
-    				\end{array} \right.
-				\end{equation}
-
-			\noindent
-			Hence, maximising NTIC amounts to
+			Hence, maximising $NTIC_t(E\rightarrow Y)$ amounts to
 				\begin{equation}
@@
 
-			One can also maximise NTIC by 
+			One can also maximise $NTIC_t(E\rightarrow Y)$ by 
 				\begin{equation}
@@
 We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic levels.
-Based on the merit of coarse-graining in neural systems, We propose a theory of consciousness in the next section.
+Based on the merit of coarse-graining in neural systems, We propose a new theory of consciousness in the next section.
 
@@
         In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory}.
-In \ac{OurTheory}, we claim that being NTIC is sufficient for a process to be conscious.
-The implications of \ac{OurTheory} will be discussed in Sec.~\ref{sec:cl}, \ref{sec:cc}, and \ref{sec:reconcile}.
-In what follows, we will first establish four assumptions on which \ac{OurTheory} depends, and then develop the specific propositions of \ac{OurTheory} in detail.
-
-        % ---------------------------------------------------------------------------- %
-        %                             Ryota's common backup                            %
-        % ---------------------------------------------------------------------------- %
-            % kanair: I suggest that we cut all of this.
-            % Sep 15, 2019 12:52 AM
-
-            % The 3 assumptions - Information - Necessity of Physical substrate - Boundary The main proposal is not necessarily derived from these assumptions.
-If anything, our theory is entirely on the boundary issue, namely, consciousness occurs at a particular scale.
-            % Sep 15, 2019 12:53 AM
-
-            % I understand that for a theory to be complete, we want to specify the assumptions here, but I felt these are distracting, because their relevance to the current theory is somewhat weak.
-            % Sep 15, 2019 12:55 AM
-
-            % Instead of delving into these assumptions, we should describe the main claims of the theory directly.
-        % ---------------------------------------------------------------------------- %
-
-        The first assumption is that consciousness is information.
-Every human conscious percept is informative.
-Here, "information" refers to the resolution of uncertainty.
-Being in a certain conscious state rules out a number of other possible conscious states.
-This is in line with the impression that our conscious experience consist of multi-dimensional information and usually involves information from multiple modalities.
-Therefore, every human conscious percept resolves some amount of uncertainty and provides information.
-
-        This assumption is also in agreement with the "axiom" of \textit{information} in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.2]{oizumi2014phenomenology}.
-
-        Second, we further assume that all information requires physical substrates. 
-        From these two assumptions, it follows that for every conscious percept there exists a corresponding physical event whose self-information is is equal to the self-information of the percept.
-        % the amount of (self-)information possessed by a conscious percept must be equal to the (self-)information of a particular event or entity in the physical reality.
-
-        In this theory, we consider information is the common language between conscious experience and the physical reality.
-This means that consciousness is fundamentally associated with information \citep{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}).
-
-        === How about if I change this ===
-        The third assumption is that no consciousness can contain complete information about the universe.
-This means that there exists a informational boundary for every consciousness, i.e.
-informationally closed to the the universe.
-This is in line with our conscious experience that information provided by every conscious percept is limited.
-
-        === to this ===
-        The third assumption is that there exists a informational boundary for every consciousness.
-The informational boundary here means that no consciousness can contain information of the entire universe and every consciousness is informationally closed to the the universe.
-This is in line with our conscious experience that information provided by every conscious percept is limited.
-
-        Together with the first three assumptions, this means that the physical representations of the contents of any consciousness must be a coarse-graining of the universe states and also informationally closed to the universe.
-
-        Note that a coarse-grained process $Y$ can be a coarse-graining of another coarse-grained process $S$ of the universe $X$ (see Fig.~\ref{fig:fullgraph}).
-Here, we consider $S$ as a coarse-graining of $X$ and call it the system.
-Then $Y$ is a coarse-graining of the system $S$.
-We can then also define another coarse-graining of $X$ called the environment $E$ of $S$.
-This is the coarse-graining that contains the information about $X$ that is not contained in $S$.
-Importantly, in this case, if a macroscopic process $Y$ is informationally closed to the universe $X$, this implies $Y$ is also informationally closed to both the system $S$ and the environment $E$.
-
-            \needhelp{@Martin, if you think it's better to have a proof for this and if you don't mind, you can help me to write the proof here or create an appendix section and put it there.
-If you have no time, I can also do this.}
-		\begin{equation}
-			\label{eq:ICchain}
-			\begin{aligned}
-		    & I(Y_{t+1};X_t|Y_{t})=0 & \implies & I(Y_{t+1};S_t|Y_{t})=0 \\
-		    & {} & \implies & I(Y_{t+1};E_t|Y_{t})=0
-			\end{aligned}
-		\end{equation}
-
-        This results in a crucial implication that informational closure can occur between levels in a system.
-The macroscopic level $Y$ can be informationally closed to its microscopic level $S$ within a system \citep{PFANTE.2014}.
+The main hypothesis is that conscious processes are captured by what we call \textit{C-processes}.
+We first define C-processes, then state our hypothesis and discuss its implications.
 
@@
 
+	   	% ------------------------------- definition 1 ------------------------------- %
+	   	In order to define C-processes we need to define coarse-grainings first.
+Every coarse-graining is characterized by a function that maps the microscopic process to the coarse-grained macroscopic process.
+More formally:
+
+	   	\begin{definition}
+	   	Given a stochastic process $X$ with state space $\mathcal{X}$ a \emph{coarse-graining of $X$} is a stochastic process $Y$ with state space $\mathcal{Y}$ such that there exists a function\footnote{Functions in the mathematical sense used here are always either one-to-one or many-to-one.} $f_Y:\mathcal{X}\rightarrow \mathcal{Y}$ with $Y_t=f_Y(X_t)$.
+	   	\end{definition}
+	   	A more general definition of coarse-grainings that maps temporally extended sequences of the microscopic process to macroscopic states are possible but for his first exposure of our theory the simpler definition above is sufficient.
+
+	   	% ------------------------------- definition 2 ------------------------------- %
+        \begin{definition}
+        Given a stochastic process $X$ called the universe process, a \emph{C-process} is a coarse-graining $Y$ of $X$ such that the following two conditions are satisfied (see Fig.~\ref{fig:fullgraph}):
+        \begin{enumerate}
+        \item $Y$ is informationally closed to $X$
+        \item there exists a pair $(S,E)$ of coarse-grainings of $X$ such that 
+        \begin{itemize}
+            \item $Y$ is a coarse-graining of $S$,
+            \item the state space $\mathcal{X}$ of $X$ is equal to the Cartesian product of the state spaces $\mathcal{S}$ and $\mathcal{E}$ of processes $S$ and $E$ respectively, formally $\mathcal{X}=\mathcal{S}\times\mathcal{E}$, and
+            \item $Y$ is NTIC to $E$, formally:
+        \begin{align}
+            NTIC_t(E\rightarrow Y) >0
+        \end{align}
+        \end{itemize} 
+        \end{enumerate}
+       \end{definition}
+
+         \begin{definition}
+        Given a stochastic process $X$ called the universe process, a \emph{C-process} is a coarse-graining $Y$ of $X$ such that the following two conditions are satisfied (see Fig.~\ref{fig:fullgraph}):
+        \begin{enumerate}
+        \item $Y$ is informationally closed to $X$
+        \item there exists a coarse-graining $E$ of $X$ such that
+        \begin{itemize}
+            \item the state space $\mathcal{X}$ of $X$ is equal to the Cartesian product of the state spaces $\mathcal{Y}$ and $\mathcal{E}$ of processes $Y$ and $E$ respectively, formally $\mathcal{X}=\mathcal{Y}\times\mathcal{E}$, and
+            \item $Y$ is NTIC to $E$, formally:
+        \begin{align}
+            NTIC_t(E\rightarrow Y) >0
+        \end{align}
+        \end{itemize} 
+        \end{enumerate}
+       \end{definition}
+
+        With the two definitions we can state the main hypothesis of \ac{OurTheory}:
+
+        \begin{hypothesis}
+        A process $Y$ is conscious if and only if it is a C-process of some process $X$.
+Also the content of consciousness $C_t^{Content}$ at time $t$ is the state $Y_t$ of the C-process at time $t$ and the level of consciousness $C_t^{Level}$ is the degree of NTIC of the C-process to the environment i.e.
+$NTIC_t(E\rightarrow Y)$:
+        \begin{align}
+            C_t^{Content} &= Y_t \label{eq:cContent}\\
+            C_t^{Level} &= NTIC_t(E\rightarrow Y) \label{eq:cLevel}
+        \end{align}
+        \end{hypothesis}
+
+        %  In \ac{OurTheory}, we claim that being NTIC is sufficient for a process to be conscious.
+The implications of \ac{OurTheory} will be discussed in Sec.~\ref{sec:cl}, \ref{sec:cc}, and \ref{sec:reconcile}.
+In what follows, we will first establish four assumptions on which \ac{OurTheory} depends, and then develop the specific propositions of \ac{OurTheory} in detail.
+
+        % ---------------------------------------------------------------------------- %
+        %                             Ryota's common backup                            %
+        % ---------------------------------------------------------------------------- %
+            % kanair: I suggest that we cut all of this.
+            % Sep 15, 2019 12:52 AM
+
+            % The 3 assumptions - Information - Necessity of Physical substrate - Boundary The main proposal is not necessarily derived from these assumptions.
+If anything, our theory is entirely on the boundary issue, namely, consciousness occurs at a particular scale.
+            % Sep 15, 2019 12:53 AM
+
+            % I understand that for a theory to be complete, we want to specify the assumptions here, but I felt these are distracting, because their relevance to the current theory is somewhat weak.
+            % Sep 15, 2019 12:55 AM
+
+            % Instead of delving into these assumptions, we should describe the main claims of the theory directly.
+        % ---------------------------------------------------------------------------- %
+
         A concrete example in the context of neuroscience is that $X$ represents the microscopic level of the universe, $S$ a cellular level process in the neural system, $Y$ a more macroscopic process of the neural system coarse-grained from the cellular level process $S$, and $E$ the environment which the cellular level process $S$ interacts with.
-The environment $E$ may includes other processes in the neural system, the sensors for perception and interoception, and external physical worlds, respectively.
-
-        Our fourth assumption is that information provided by every conscious content is not trivial.
+The environment $E$ may include other processes in the neural system, the sensors for perception and interoception, and external physical worlds.\\
+
+        Based on the hypothesis, \ac{OurTheory} leads to four core implications: 
+        \begin{description}
+            \item[Implication 1.] Consciousness is information.
+Being in a certain conscious state rules out other possible conscious states $y'_t\neq y_t$.
+This is in line with the impression that our conscious experience consist of multi-dimensional information and usually involves information from multiple modalities.
+Therefore, every conscious percept resolves some amount of uncertainty and provides information.
+\\
+            This implication is also in agreement with the "axiom" of \textit{information} in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.2]{oizumi2014phenomenology}.
+
+            \item[Implication 2.] Consciousness requires physical substrates.
+Every conscious percept $y_t$ corresponds to a physical event.
+This means that the self-information of the conscious percept is also the self-information of the corresponding physical event.
+
+            %In \ac{OurTheory}, we consider information is the common language between conscious experience and the physical reality.
+This means that consciousness is fundamentally associated with information \citep{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}).
+
+            \item[Implication 3.] Conscious processes are self-determining. 
+            % There are no coarse-grainings that contain information about the future of the conscious process that is not already contained in the conscious process itself. 
+            No coarse-graining knows anything about the conscious process' future that the conscious process does not know itself.
+This is a direct implication of the requirement that $Y$ is informationally closed with respect to $X$.
+This is in line with our daily life conscious experience often shows stability and continuity and is ignorant of the stochasticity of the cellular levels.
+
+            % \item[Implication 4.] Conscious processes can be ignorant to part of the information of more microscopic processes and must be ignorant to part of the information about the universe process.
+This is due to $Y$ being a coarse-graining of the universe process $X$ and NTIC to the environment $E$.
+The environment must contain information (have multiple possible states) for NTIC to be positive.
+At a given time $t$ this information in $E_t$ must then be missing from $Y_t$
+            % and possible intermediate coarse-grainings between $X$ and $Y$.
+
+            % \item[Implication 5.] Even though conscious processes are ignorant of are informationally closed with respect to all other coarse-grainings of the universe.
+This is a direct consequence of $Y$ being informationally closed with respect to $X$.
+            % Informational closure can occur between levels in a system.
+The macroscopic level $Y$ can be informationally closed with respect to its microscopic level $S$ within a system \citep{PFANTE.2014}.
+
+            % This implication is in line with our conscious experience that information provided by every conscious percept is limited.
+            % This means that the physical representations of the contents of any consciousness must be a coarse-graining of the universe states and also informationally closed to the universe. \\
+    %         Note that a coarse-grained process $Y$ can be a coarse-graining of another coarse-grained process $S$ of the universe $X$ (see Fig.~\ref{fig:fullgraph}).
+Here, we consider $S$ as a coarse-graining of $X$ and call it the system.
+Then $Y$ is a coarse-graining of the system $S$.
+We can then also define another coarse-graining of $X$ called the environment $E$ of $S$.
+This is the coarse-graining that contains the information about $X$ that is not contained in $S$.
+Importantly, in this case, if a macroscopic process $Y$ is informationally closed to the universe $X$, this implies $Y$ is also informationally closed to both the system $S$ and the environment $E$.
+\\
+    %         Together with the first three implications, this means that the physical representations of the contents of any consciousness must be a coarse-graining of the universe states and also informationally closed to the universe.
+
+    % 		\begin{equation}
+    % 			\label{eq:ICchain}
+    % 			\begin{aligned}
+    % 		    & I(Y_{t+1};X_t|Y_{t})=0 & \implies & I(Y_{t+1};S_t|Y_{t})=0 \\
+    % 		    & {} & \implies & I(Y_{t+1};E_t|Y_{t})=0
+    % 			\end{aligned}
+    % 		\end{equation}
+
+            \item[Implication 5.] The environment of a conscious process shares information with the future of the conscious process.
+This is due to the non-triviality of the informational closure of $Y$ to $E$.
+            At the same time all of this information is known to the conscious processes themselves since they are informationally closed with respect to their environments. 
+            % This is a direct consequence of the requirement that $Y$ is NTIC to $E$.
+
+            % Information provided by every conscious content is not trivial.
 More precisely, there exists a certain degree of mutual information between conscious processes and the environments which it interacts with.
@@
 Therefore, a macroscopic process $Y$ can be NTIC to the system's environment $E$ and at the same time be informationally closed to its microscopic process $S$.
-In other words, the macroscopic process can encode environmental information (by forming NTIC), however, be ignorant to part of the information of its microscopic processes.
-This is in line with our conscious experience that information that every conscious percept provides represent rich and structured environmental states without involving much information at microscopic activities.
-
-        Finally, together with the four assumptions above, our main proposition is that the coarse-graining that physically represent consciousnesses are those that are informationally closed with respect to the universe states and concurrently be NTIC with respect to its environment.
-More formally this means that every NTIC process $Y_t$ at time $t$ corresponds to a conscious process $C_t=\{C_t^{Content},C_t^{Level}\}$ such that the content $C_{t}^{Content}$ of $C_t$ is just $Y_t$:
-		\begin{equation}\label{eq:cContent}
-			C_{t}^{Content} = Y_{t}.
-		\end{equation}
-
-		\noindent
-        We further propose that the level of consciousness $C_{t}^{Level}$ can be measured by the degree of $NTIC_{t}$ of $Y_t$:
-		\begin{equation}\label{eq:cLevel}
-			C_{t}^{Level} = NTIC_{t}.
-		\end{equation}
-		We discuss the implications of these propositions in the following.
+
+            \item[Implication 6.]
+            Conscious processes can encode environmental information (by forming NTIC), however, be ignorant to part of the information of more microscopic processes.
+This is in line with our conscious experience that information that every conscious percept provides represent rich and structured environmental states without involving all the information about microscopic activities.
+        \end{description}
 
@@
 	    \subsection{Level of Consciousness is equal to the degree of NTIC of a process}\label{sec:cl}
-
             According to Eq.~\ref{eq:nticObjective}, \ac{OurTheory} implies that conscious levels are determined by two quantities.
@@
         \subsection{Unconscious Processing}
-            In this section, we highlight two scenarios in which the degree of NTIC is rendered low for a process, and thereby making the process unconscious.
+            In this section, we highlight two scenarios in which the degree of NTIC is rendered low for a process, and thereby making the process less conscious.
 
@@
 
-    	    \ac{OurTheory} starting with non-functional assumptions and propositions, however, leads to profound implications about the functional aspects of consciousness.
+    	    \ac{OurTheory} starts with a non-functional hypothesis, however, it accounts for the association between  functional and consciousness.
 \ac{OurTheory} further demonstrates remarkable explanatory power for various findings of conscious and unconscious processing with concise propositions.
@@
 We argue that if the generative model involving the NTIC process for the computation of counterfactual, PPSMC will be compatible to our theory and may have strong explanatory power on some special conscious experience.
-
-        % ---------------------------------------------------------------------------- %
-        %                             First-order theories                             %
-        % ---------------------------------------------------------------------------- %
-% 		\subsection{First-order theories}
-            % The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}.
-The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
-            % First-order theories suggests that phenomenal consciousness is associated with fine-grained contents for the first-order processes.
-Different from the first-order theories, our theory suggests that, whether the early sensory activities show in the conscious content, it depends on information encoded in the early sensory areas is recruited in the NTIC process at the macroscopic level or not.
-As we mentioned in \ref{sec:Unconscious Processing}, if the sensory activities are only passively triggered by the environmental states, they are not able to form hign NTIC and remain unconscious.
-We predict that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities can contribute conscious content.
-
-        % ---------------------------------------------------------------------------- %
-        %                 Higher Order Thought theory of consciousness                 %
-        % ---------------------------------------------------------------------------- %
-% 		\subsection{Higher Order Thought theory of consciousness}
-% 		    \ideaBox{Okay, I don't know how to deal with HOT now. I don't understand it at all}
-% 		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations which represent agents as being in particular internal states \citep{lau2011empirical}.
-First-order processing needs to be observed or represented by a higher-order observer to become conscious.
-
-% 		    Meta-cognition is also associated with many conscious cognitive function.
-However, we propose a new perspective and indicate that HOT may be a misunderstanding \critical{Very bad writing.
-I need to rewrite this part}.
-
-% 		    This may be the result of neural coarse-graining. Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it.
-
-% 		    Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.
-It is true that the neural system does create  meta-representation to represent xxx\needref{Maybe come studies about confidence represenatation}.
-The higher-order representation may resemble coarse-grained variables.
-This may cause misidentify the entity which correlates conscious experience.
-
-% 		    Moreover, the predictive information in NTIC is critical for other systems to build forward models for a wild range of tasks.
-Therefore, most of the high level cognition can utilise the state of informational closure.
-For example, mental planning needs a precise forward model to infer the environmental dynamics.
 
@@
         Empirically, a major challenge to \ac{OurTheory} is to find proper coarse-graining functions which map microscopic processes to macroscopic NTIC processes.
-This will become an imperative issue of find neurological supporting evidence for \ac{OurTheory}.
+This will become an imperative issue of finding neurological supporting evidence for \ac{OurTheory}.
 To find proper coarse-graining functions among infinite candidates \citep{price2007causation} seem to be very challenging.
@@
 In neuroscience, the understanding of neural population codes also achieves a tremendous progress due to the advancement of recording technique and data science \citep{Kohn2016, panzeri2015neural}.
-\cite{Gamez2016} has also systematically describe relevant issues in terms of finding data correlates of consciousness amount different levels of abstraction.
+\cite{Gamez2016} has also systematically described relevant issues in terms of finding data correlates of consciousness amount different levels of abstraction.
 We believe that interdisciplinary research is required to narrow down the scope of searching the coarse-graining functions and conscious processes at the coarse-grained level in the neural system and beyond.
@@
 Finally, forming NTIC (conscious) processes through many-to-one maps, i.e., coarse-graining, implies multiple realizability of consciousness.
-As a result, \ac{OurTheory} provides a integrated view for these arguments and is further capable of indicating how and why they are conditionally true.
+As a result, \ac{OurTheory} provides an integrated view for these arguments and is further capable of indicating how and why they are conditionally true.
 
@@
 
-%     ================================ Old version ===============================
-% 	In this paper, We introduced a new computational theory of consciousness based on two assertions.
-First, consciousness occurs when a process forms an NTIC.
-Second, in the neural system, construction of an NTIC process requires coarse graining.
-From these assumptions, it follows that consciousness only appears at a certain macroscopic level which forms a high degree of NTIC.
-	Our  theory offers an explanation for a large number of empirical findings in consciousness research and reconciles with several other theories of consciousness.
-
-% 	Our theory asserts that consciousness is an informational phenomenon.
-We further emphasise that the scale-dependent nature of information processing is critical to conscious experience.
-We believe that many discrepancies in previous studies of neural correlates of consciousness resulted from measurements at inappropriate scales.
-Except where and when, future studies should also focus on "what scale" of the neural system the data are acquired at.
-
-% 	The computational nature of the theory makes it feasible to extrapolate and apply to other non-human systems.
-Note that, even though our theory does not start from a functionalist point of view, it comes out with explanatory power on the functional aspect of consciousness and points out the evolutionary drive of having conscious processing.
-
-% 	Finally, we quote the famous epistemological questions: "If a tree falls in a forest and no one is around to hear it, does it make a sound?".
-Now, we can ask a new version of this question: "If an action potential rises outside an informationally closed process, does it make any conscious percept to this process?" We answer: "if the process is conscious, the event occurring outside the realm of the informational closure should never become part of the conscious contents."
-
 	% ============================================================================ %
@@
 	% ============================================================================ %
-
-	\section*{Funding}
-        \needhelp{@Ryota, could you help me with this part?}
 	\section*{Acknowledgements}
-
-	\section*{Supplemental Data}
+	A.C., Y.Y, and R.K. are funded by Japan Science and Technology Agency (JST) CREST project. R.K. and M.B. are supported by Templeton World Charity Foundation.
+	   % Thank David Schwartzman for letting me concertrate several months for this work.
 

### 2019-09-26 Paper_neural_coarse_graining_of_consciousness.tex
Clean

@@
 
-\newcommand{\cp}{C-process} 
-\newcommand{\cps}{C-processes}
-
 \usepackage{chngcntr}
@@
 \newacro{OurTheory}[ICT]{Information Closure Theory of Consciousness}
-\newacro{cp}{C-process}
 
@@
 
-%         \end{ants}
-
 % ============================================================================ %
@@
 Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials along axons.
-However, you have no idea that you are one of the neurons in Alice's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup.
+However, you have no idea that you are one of the neurons in Alice's supplementary motor area and involved in many motor control processes for Alice's actions, for example, grabbing a cup.
 You are ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.
@@
 We next argue that through coarse-graining the neural system can form a high degree of NTIC at a specific coarse-grained level (Sec.\ref{sec:Neural coarse-graining}).
-In the Sec.\ref{sec:OurTheory}, we propose our theory: \acf{OurTheory}.
+In the Sec.\ref{sec:OurTheory}, we propose a new theory of consciousness: \acf{OurTheory}.
 We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies (Sec.\ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (Sec.\ref{sec:Comparison with other theories}).
@@
 One can distinguish a system from its environment by computing the closedness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}.
-The closure can be further quantified by information theory.
+The closedness can be further quantified by information theory.
 
 		% Definition of informational closure
-			\noindent
 			Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network in Fig.~\ref{fig:SystemAndEnv}.
@@
     				{rl}{J_{t}(E \rightarrow Y )} & {:= I(Y_{t+1};E_{t}|Y_{t})} \\
-    				%{ } & { \ = H(Y_{t+1}|Y_{t})-H(Y_{t+1}|Y_{t},E_{t})} \\
-    				%{ } & { \ = H(E_{t}|Y_{t})-H(Y_{t}|Y_{t},Y_{t+1})} \\
-    				%{ } & { \ = H(E_{t}|Y_{t})-H(E_{t}|Y_{t},Y_{t+1})}\\
     				{ } & { \ = I(Y_{t+1};E_{t}) - (I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}))}
@@
 In such cases, the mutual information between the current states of the environment and the future state of the system is larger than zero.
-%\footnote{Here we assume that that the environment contains more information than the system, i.e.
-$H(E|S)>0$ and $E\neq S$}.
 
@@
 
-% 			\noindent
-%             The definition can also be re-arranged as 
-% 				\begin{equation}
-% 				\label{eq:NTIC2}
-%     				\left.\begin{array}
-%     				{rl}{\qquad} & {\ =I(Y_{t+1};E_{t})-I(Y_{t+1};E_{t}|Y_{t})}
-%     				\end{array} \right.
-% 				\end{equation}
-
 			\noindent
@@
 
+			\noindent
 			One can also maximise $NTIC_t(E\rightarrow Y)$ by 
@@
 			This implies the system contains in itself all the information about its own future and the self-predictive information contains the information about the environment.
-Therefore, to form NTIC, the system can internalise and synchronise with the dynamics of the environment, i.e.
-model the environment.
+Therefore, to form NTIC, the system can internalise and synchronise with the dynamics of the environment, e.g., model the environment.
 Furthermore, having high degrees of NTIC entails having high predictive power about the environment.
@@
 NTIC requires the predictability of the system state and is therefore impeded by noise in the system.
-Information processing at the microscopic levels (the cellular levels) in neural systems suffer from multiple environmental noise sources such as sensor, cellular, electrical, and synaptic noises.
+Information processing at the microscopic levels (the cellular levels) in neural systems suffers from multiple environmental noise sources such as sensor, cellular, electrical, and synaptic noises.
 For example, neurons exhibit large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
@@
 		However, it is possible that neural systems form NTIC at certain macroscopic levels through coarse-graining of microscopic neural states.
-Coarse-graining refers to many-to-one functions which aggregate microscopic states to a macroscopic state.
+Coarse-graining refers to many-to-one or one-to-one maps which aggregate microscopic states to a macroscopic state.
 In other words, a number of different micro-states correspond to the same value of the macro-variable \citep{price2007causation}.
@@
 That is, stable representations can be formed through coarse-graining the high dimensional state space of a neuron population to a lower dimensional macroscopic state space \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
-Therefore, individual neuron states (the microscopic level) are not informative enough about the full encoded contents at the population level (the macroscopic level).
+Therefore, individual neuron states (the microscopic level) are not informative enough about the complete encoded contents at the population level (the macroscopic level).
 Instead, coarse-grained variables are better substrates for stably encoding information and allow the neural system to ignore noisy interactions at the fine-grained level \citep{Woodward2007-WOOCWA}.
@@
 			\includegraphics[width=\textwidth]{WritingMaterials/Fig_FullGraph/FullGraph.pdf}
-			\caption{The information flow amounts the universe $X$, the system $S$, the environment of the system $E$, and the coarse-grained process of the system $S$.
+			\caption{The information flow amounts the universe $X$, the system $S$, the environment of the system $E$, and the coarse-grained process $Y$ of the system $S$.
 The solid line with a filled arrow from $X_t$ to $X_{t+1}$ represents the microscopic dynamic of the universe.
@@
 	   	In order to define C-processes we need to define coarse-grainings first.
-Every coarse-graining is characterized by a function that maps the microscopic process to the coarse-grained macroscopic process.
+Every coarse-graining is characterised by a function that maps the microscopic process to the coarse-grained macroscopic process.
 More formally:
@@
 	   	\begin{definition}
-	   	Given a stochastic process $X$ with state space $\mathcal{X}$ a \emph{coarse-graining of $X$} is a stochastic process $Y$ with state space $\mathcal{Y}$ such that there exists a function\footnote{Functions in the mathematical sense used here are always either one-to-one or many-to-one.} $f_Y:\mathcal{X}\rightarrow \mathcal{Y}$ with $Y_t=f_Y(X_t)$.
+	   	Given a stochastic process $X$ with state space $\mathcal{X}$, a \emph{coarse-graining of $X$} is a stochastic process $Y$ with state space $\mathcal{Y}$ such that there exists a function\footnote{Functions in the mathematical sense used here are always either one-to-one or many-to-one.} $f_Y:\mathcal{X}\rightarrow \mathcal{Y}$ with $Y_t=f_Y(X_t)$.
 	   	\end{definition}
@@
 
-         \begin{definition}
-        Given a stochastic process $X$ called the universe process, a \emph{C-process} is a coarse-graining $Y$ of $X$ such that the following two conditions are satisfied (see Fig.~\ref{fig:fullgraph}):
-        \begin{enumerate}
-        \item $Y$ is informationally closed to $X$
-        \item there exists a coarse-graining $E$ of $X$ such that
-        \begin{itemize}
-            \item the state space $\mathcal{X}$ of $X$ is equal to the Cartesian product of the state spaces $\mathcal{Y}$ and $\mathcal{E}$ of processes $Y$ and $E$ respectively, formally $\mathcal{X}=\mathcal{Y}\times\mathcal{E}$, and
-            \item $Y$ is NTIC to $E$, formally:
-        \begin{align}
-            NTIC_t(E\rightarrow Y) >0
-        \end{align}
-        \end{itemize} 
-        \end{enumerate}
-       \end{definition}
-
         With the two definitions we can state the main hypothesis of \ac{OurTheory}:
@@
         A process $Y$ is conscious if and only if it is a C-process of some process $X$.
-Also the content of consciousness $C_t^{Content}$ at time $t$ is the state $Y_t$ of the C-process at time $t$ and the level of consciousness $C_t^{Level}$ is the degree of NTIC of the C-process to the environment i.e.
+Also the content of consciousness $C_t^{Content}$ at time $t$ is the state $y_t$ of the C-process at time $t$ and the level of consciousness $C_t^{Level}$ is the degree of NTIC of the C-process to the environment i.e.
 $NTIC_t(E\rightarrow Y)$:
         \begin{align}
-            C_t^{Content} &= Y_t \label{eq:cContent}\\
+            C_t^{Content} &= y_t \label{eq:cContent}\\
             C_t^{Level} &= NTIC_t(E\rightarrow Y) \label{eq:cLevel}
@@
 
-        %  In \ac{OurTheory}, we claim that being NTIC is sufficient for a process to be conscious.
-The implications of \ac{OurTheory} will be discussed in Sec.~\ref{sec:cl}, \ref{sec:cc}, and \ref{sec:reconcile}.
-In what follows, we will first establish four assumptions on which \ac{OurTheory} depends, and then develop the specific propositions of \ac{OurTheory} in detail.
-
-        % ---------------------------------------------------------------------------- %
-        %                             Ryota's common backup                            %
-        % ---------------------------------------------------------------------------- %
-            % kanair: I suggest that we cut all of this.
-            % Sep 15, 2019 12:52 AM
-
-            % The 3 assumptions - Information - Necessity of Physical substrate - Boundary The main proposal is not necessarily derived from these assumptions.
-If anything, our theory is entirely on the boundary issue, namely, consciousness occurs at a particular scale.
-            % Sep 15, 2019 12:53 AM
-
-            % I understand that for a theory to be complete, we want to specify the assumptions here, but I felt these are distracting, because their relevance to the current theory is somewhat weak.
-            % Sep 15, 2019 12:55 AM
-
-            % Instead of delving into these assumptions, we should describe the main claims of the theory directly.
-        % ---------------------------------------------------------------------------- %
-
         A concrete example in the context of neuroscience is that $X$ represents the microscopic level of the universe, $S$ a cellular level process in the neural system, $Y$ a more macroscopic process of the neural system coarse-grained from the cellular level process $S$, and $E$ the environment which the cellular level process $S$ interacts with.
@@
 
-        Based on the hypothesis, \ac{OurTheory} leads to four core implications: 
+        Based on the hypothesis, \ac{OurTheory} leads to five core implications: 
         \begin{description}
-            \item[Implication 1.] Consciousness is information.
-Being in a certain conscious state rules out other possible conscious states $y'_t\neq y_t$.
-This is in line with the impression that our conscious experience consist of multi-dimensional information and usually involves information from multiple modalities.
+            \item[Implication 1.] 
+            Consciousness is information.
+Here, "informative" refers to the resolution of uncertainty.
+Being in a certain conscious state rules out other possible conscious states.
 Therefore, every conscious percept resolves some amount of uncertainty and provides information.
@@
 
-            \item[Implication 2.] Consciousness requires physical substrates.
-Every conscious percept $y_t$ corresponds to a physical event.
-This means that the self-information of the conscious percept is also the self-information of the corresponding physical event.
+            \item[Implication 2.] 
+            Consciousness is associated with physical substrates and the self-information of the conscious percept is equal to the self-information of the corresponding physical event.
+This is a direct implication from our hypothesis that every conscious percept $C_t^{Content}$ corresponds to a physical event $y_t$.
 
@@
 
-            \item[Implication 3.] Conscious processes are self-determining. 
-            % There are no coarse-grainings that contain information about the future of the conscious process that is not already contained in the conscious process itself. 
-            No coarse-graining knows anything about the conscious process' future that the conscious process does not know itself.
+            \item[Implication 3.] 
+            Conscious processes are self-determining.
 This is a direct implication of the requirement that $Y$ is informationally closed with respect to $X$.
-This is in line with our daily life conscious experience often shows stability and continuity and is ignorant of the stochasticity of the cellular levels.
+To be informationally closed with respect to $X$, no coarse-graining knows anything about the conscious process' future that the conscious process does not know itself.
+This self-determining characteristics is also in line with our daily life conscious experience which often shows stability and continuity and is ignorant of the stochasticity (e.g., noise) of the cellular levels.
 
-            % \item[Implication 4.] Conscious processes can be ignorant to part of the information of more microscopic processes and must be ignorant to part of the information about the universe process.
-This is due to $Y$ being a coarse-graining of the universe process $X$ and NTIC to the environment $E$.
-The environment must contain information (have multiple possible states) for NTIC to be positive.
-At a given time $t$ this information in $E_t$ must then be missing from $Y_t$
-            % and possible intermediate coarse-grainings between $X$ and $Y$.
-
-            % \item[Implication 5.] Even though conscious processes are ignorant of are informationally closed with respect to all other coarse-grainings of the universe.
-This is a direct consequence of $Y$ being informationally closed with respect to $X$.
-            % Informational closure can occur between levels in a system.
-The macroscopic level $Y$ can be informationally closed with respect to its microscopic level $S$ within a system \citep{PFANTE.2014}.
-
-            % This implication is in line with our conscious experience that information provided by every conscious percept is limited.
-            % This means that the physical representations of the contents of any consciousness must be a coarse-graining of the universe states and also informationally closed to the universe. \\
-    %         Note that a coarse-grained process $Y$ can be a coarse-graining of another coarse-grained process $S$ of the universe $X$ (see Fig.~\ref{fig:fullgraph}).
-Here, we consider $S$ as a coarse-graining of $X$ and call it the system.
-Then $Y$ is a coarse-graining of the system $S$.
-We can then also define another coarse-graining of $X$ called the environment $E$ of $S$.
-This is the coarse-graining that contains the information about $X$ that is not contained in $S$.
-Importantly, in this case, if a macroscopic process $Y$ is informationally closed to the universe $X$, this implies $Y$ is also informationally closed to both the system $S$ and the environment $E$.
-\\
-    %         Together with the first three implications, this means that the physical representations of the contents of any consciousness must be a coarse-graining of the universe states and also informationally closed to the universe.
-
-    % 		\begin{equation}
-    % 			\label{eq:ICchain}
-    % 			\begin{aligned}
-    % 		    & I(Y_{t+1};X_t|Y_{t})=0 & \implies & I(Y_{t+1};S_t|Y_{t})=0 \\
-    % 		    & {} & \implies & I(Y_{t+1};E_t|Y_{t})=0
-    % 			\end{aligned}
-    % 		\end{equation}
-
-            \item[Implication 5.] The environment of a conscious process shares information with the future of the conscious process.
+            \item[Implication 4.] 
+            Conscious processes encode the environmental influence on itself.
 This is due to the non-triviality of the informational closure of $Y$ to $E$.
 At the same time all of this information is known to the conscious processes themselves since they are informationally closed with respect to their environments.
-            % This is a direct consequence of the requirement that $Y$ is NTIC to $E$.
+This also suggests that conscious processes can model the environmental influence without knowing more information from the environment.
 
-            % Information provided by every conscious content is not trivial.
-More precisely, there exists a certain degree of mutual information between conscious processes and the environments which it interacts with.
-As mentioned in Sec.\ref{sec:Non-trivial informational closure} a process can be informationally closed to another one and still have mutual information with it, i.e.
-be NTIC.
-Therefore, a macroscopic process $Y$ can be NTIC to the system's environment $E$ and at the same time be informationally closed to its microscopic process $S$.
-
-            \item[Implication 6.]
-            Conscious processes can encode environmental information (by forming NTIC), however, be ignorant to part of the information of more microscopic processes.
+            \item[Implication 5.]
+            Conscious processes can encode environmental information (by forming NTIC), however, be ignorant to part of the information of more microscopic processes (from Implication 3 and 4).
 This is in line with our conscious experience that information that every conscious percept provides represent rich and structured environmental states without involving all the information about microscopic activities.
@@
             This implies that a highly NTIC process must have rich dynamics with self-predictability over time.
-Another implication is that complex systems can potentially attain a higher level of consciousness due to the larger information capacity needed to attain high mutual information.
-This outcome is consistent with the common intuition that conscious levels are associated with the degree of complexity of the system.
+Another implication is that complex systems can potentially attain higher levels of consciousness due to the larger information capacities needed to attain high mutual information.
+This outcome is consistent with the common intuition that conscious levels are often associated with the degree of complexity of a system.
 
@@
 An important implication is that agents interacting with a complex environment have the chance to build a higher level of NTIC within their systems than those living in a simple environment.
-In other words, the level of consciousness is constrained by environmental complexity.
+In other words, the level of consciousness is associated with environmental complexity.
 
@@
 Therefor, only processes at a certain level of coarse-graining in the neural system can form a high degree of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
-\ac{OurTheory} indicates that consciousness occurs at the intermediate level of coarse-graining where the maximal NTIC is formed within the neural system.
+\ac{OurTheory} indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
 
@@
         		\includegraphics[width=\textwidth]{WritingMaterials/Fig_temp/FoxitReader_2019-01-31_19-03-59.png}
-        		\caption{A n1on-monotonic relationship between Level of coarse-graining and level of consciousness.}
+        		\caption{A non-monotonic relationship between Level of coarse-graining and level of consciousness.}
         		\label{fig:LevelOfConsciousness}
     		\end{figure}
-
-            % Finally, which coarse-grained level can form high NTIC? 
-            % agent-scale operation
-            % At the physical scale which human being interact with, the environmental dynamics is nearly deterministic following the laws of classical physics.
-It gives agents interact at this physical scale great advantages if the agents can build NTIC process internally.
-Therefore, to coarse-grain microscopic states is necessary
-
-            % %% Link to consciousness
-            % At the physical scale which human beings live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
-This suggests that information in the environment is nearly closed at the right spatio-temporal scale.
-Therefore, this gives agents living at this physical scale great advantages if the agents form an NTIC process internally.
-Therefore, coarse-graining becomes necessary to map microscopic sensory and neuronal states into macroscopic NTIC process.
 
@@
 Further more, since NTIC processes are informationally closed, each of them can be considered as a reality.
-In the extreme case, when the information flow from the its microscopic processes and environment is completely zero (Eq.~\ref{eq:informationflow2}), the future states of the process is only determined by its past states.
+In the extreme case, when the information flow from its microscopic processes and environment to the informationally closed process is completely zero (Eq.~\ref{eq:informationflow2}), the future states of the process is only determined by its past states.
 
@@
 This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.
-This implication fit well with some other theories of consciousness (for example, world simulation metaphor ~\citep{revonsuo2006inner}).
+This implication fits well with some theories of consciousness (for example, world simulation metaphor ~\citep{revonsuo2006inner}).
 Note that \ac{OurTheory} doesn't assume that generative models are necessary for consciousness.
-The implication a natural consequence based on our proposition.
+The implication is a natural result of processes with NTIC.
 
-            Finally, a coarse-graining is a many to one map from microscopic to macroscopic states and \ac{OurTheory} proposes that conscious contents $C_{t}^{Content}$ is the state of the NTIC process $Y_t$.
+            Finally, a coarse-graining can be a many to one map from microscopic to macroscopic states and \ac{OurTheory} proposes that conscious contents $C^{Content}$ is the state of the NTIC process $Y$.
 Therefore, \ac{OurTheory} implies multiple realisation thesis of consciousness \citep{putnam1967psychological,bechtel1999multiple} which suggests that different physical implementations could map to the same conscious experience.
@@
 In \ac{OurTheory}, conscious levels and conscious contents are just two different properties of NTIC processes, and, therefore, naturally reconciles the two aspects of consciousness.
-In an NTIC process with a large state space, conscious contents consist of rich and high dimensional information.
+In an NTIC process with a large state space, conscious contents should also consist of rich and high dimensional information.
 Therefore, this framework integrates the levels and the contents of consciousness in a coherent fashion by providing explicit formal definitions of the two notions.
 
-    	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the entropy $H(Y)$ of an NTIC process, and therefore the size of the state space.
-To form a high degree of NTIC for rich conscious contents, the process needs to have a large state space and also the capacity of predictive information   (Eq.~\ref{eq:nticObjective}).
-    	    \ac{OurTheory} therefore explains why in normal physiological states conscious levels and conscious contents are positively correlated \citep{laureys2005neural}.
+    	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the state space of an NTIC process $Y$.
+A large state space of $Y$ contributes conscious levels through the mutual information $I(Y_{t+1};Y_{t})$ and also contributes richer conscious contents by providing more possbile states of conscious processes.
+    	    \ac{OurTheory} therefore explains why, in normal physiological states, conscious levels and conscious contents are often positively correlated \citep{laureys2005neural}.
 This implication is also in line with the intuition in which consciousness is often associated with complex systems.
@@
 	\section{Conscious versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
-	    In this section, we show how \ac{OurTheory} can make predictions about what processes are conscious and what are unconscious.
+	    In this section, we show how \ac{OurTheory} can explain and make predictions about what processes are conscious and what are unconscious.
 \ac{OurTheory} is constructed using information theory.
 Therefore, \ac{OurTheory} can provide predictions based on the mathematical definitions.
-In the end of this section, we discuss a critical implication of \ac{OurTheory} for neuroscience research on consciousness.
-
-        % While our theory is built upon a minimal set of assumptions, it possesses predictive power about the relationship between information processing in the neural system and conscious experience.
-
-        % 		Our theory argues that, to make information conscious, the following necessary and sufficient conditions need to be satisfied.
-
-        %         We especially highlight the second condition because it is critically related to many empirical research results even though it is only a necessary condition.
-As we will describe below, this theory can well explain a variety of previous empirical findings in consciousness science and further make predictions for future research.
-In this section, we discuss how the two informational-based conditions link to conscious experience.
 
@@
         \subsection{Unconscious Processing}
-            In this section, we highlight two scenarios in which the degree of NTIC is rendered low for a process, and thereby making the process less conscious.
+            Regarding unconscious processing, we highlight two scenarios in which the degree of NTIC is rendered low for a process, and thereby making the process less conscious.
 
@@
 Therefore, the process $Y$ is not informational closed.
-As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain unconscious.
+As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain lesss conscious or unconscious.
         			    }
@@
 
-        		\ideaCallout{Mayeb can put in theory part}
         		As we have seen in the examples above, a crucial implication of \ac{OurTheory} is that a pure feedforward network cannot produce consciousness because NTIC requires a form of memory $I(Y_{t+1};Y_{t})$.
@@
 This result coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
-
-                % However, we derive this conclusion from a more fundamental informational-related hypothesis indicating the more generalised principle behind it.
 
@@
                 This implies that isolated processes with trivial information do not contribute consciousness and should be considered being outside the information boundary of the conscious processing (for more details of the boundary detection procedure, see \cite{krakauer2014information}).
-                This property also implies that consciousnesses do not emerge from just aggregating informationally closed (isolated) processes which contain trivial information.\footnote{However, we do not exclude the possibility that triviality of encoded information is just a proxy of other quantities which more directly associate with consciousness.
+                This property also implies that consciousnesses do not emerge from just aggregating informationally closed (isolated) processes which contain trivial information.%\footnote{However, we do not exclude the possibility that triviality of encoded information is just a proxy of other quantities which more directly associate with consciousness.
 We point out that this is a limitation of the current version of \ac{OurTheory} in Sec.~\ref{sec:Limitation and Future work}.}
@@
 		\subsection{Conscious Processing}\label{sec:conscious processing}
-		    According to \ac{OurTheory}, NTIC is sufficient for a process to be conscious.
-We claim that any process, system, or cognitive function which involves any NTIC process should be accompanied by conscious experience.
+		    According to \ac{OurTheory}, we claim that any process, system, or cognitive function which involves any NTIC process should be accompanied by conscious experience.
 
 		    Previous consciousness research has identified a number of diverse cognitive processes often accompanied by conscious experience.
-\ac{OurTheory} provides an integrated account for why these processes involve conscious experience.
-NTIC processes encode environmental information into its own states and dynamics.
-Therefore, An NTIC process can be seen as an internal simulation engine for the agent-environmental interactions \citep{BERTSCHINGER.2006}.
-Information from NTIC processes is essential for several cognitive processes.
-
-		  %  NTIC is a powerful property in the context of evolution.
-NTIC processes encode environmental information into its own states and dynamics.
-Hence, an NTIC process can be seen as a simulation engine of the environment \citep{BERTSCHINGER.2006}.
-Therefore, NTIC processes can provides valuable information for survival as a basis of several cognitive functions.
+\ac{OurTheory} provides an integrated account for the reason why these processes involve conscious experience.
+As mentioned above, an NTIC process can be seen as an internal simulation engine for the agent-environmental interactions \citep{BERTSCHINGER.2006}.
+Therefore, information encoded in NTIC processes is essential for several cognitive processes.
 
@@
 This is crucial for many types of off-line processing.
-Therefore, in contrast to reflex-like behaviours mentioned above (Sec.~\ref{sec:reflexive}), behaviours requiring off-line computations \citep{milner1999paradoxical, himmelbach2005dorsal,revol2003pointing} often involve conscious experience.
+Therefore, in contrast to reflexive-like behaviours mentioned above (Sec.~\ref{sec:reflexive}), behaviours requiring off-line computations \citep{milner1999paradoxical, himmelbach2005dorsal,revol2003pointing} often involve conscious experience.
 
@@
     	    Note that many of the claims above are compatible with several theories of consciousness which highlight the connection between consciousness and internal simulation, predictive mechanism, or generative models inside a system (e.g.
-world simulation metaphor ~\citep{revonsuo2006inner}, predictive processing and Bayesian brain~\citep{clark_2013,Hohwy2013,SethPP2014}, generative model and information generation~\citep{kanai_chang_yu_de_abril_biehl_guttenberg_2019}).
+world simulation metaphor ~\citep{revonsuo2006inner}, predictive processing and Bayesian brain~\citep{clark_2013,Hohwy2013,seth2014predictive}, generative model and information generation~\citep{kanai_chang_yu_de_abril_biehl_guttenberg_2019}).
 Instead of relating functional or mechanistic aspects of a system to consciousness, \ac{OurTheory} captures common informational properties underlying those cognitive functions associated with consciousness.
@@
     	    \ac{OurTheory} starts with a non-functional hypothesis, however, it accounts for the association between  functional and consciousness.
-\ac{OurTheory} further demonstrates remarkable explanatory power for various findings of conscious and unconscious processing with concise propositions.
-
-    % \subsection{Inconsistency between Conscious States and Measured Physiological States}
-    %     \ac{OurTheory} claims that the human conscious (NTIC) process rests on a certain coarse-grained level in the human neural system.
-This implies the spatial and temporal scales of the physiological measurements are critical for finding neural correlates of consciousness (NCC).
-Choosing unsuitable measuring scales may lead to confusing results and inappropriate interpretations.
-Here we elaborate this issue with two classic examples.
-
-    %     % probabilistic inference
-    %     \subsubsection*{The First Example: Probabilistic Inference}
-    %     Strong evidence suggests that the neural system is capable to encode probability distribution and perform probabilistic inference in a near optimal way \citep{knill2004bayesian, pouget2013probabilistic}.
-However, an intriguing fact is that our conscious contents are almost ignorant of all details of the computations.
-Instead, we are always only conscious of "a sample" of the posterior distributions \citep{dehaene2017consciousness, vul2009attention, asplund2014attentional, vul2008temporal, moreno2011bayesian}.
-In short, one needs to explain why information about the probability distributions are unconscious and only a realisation of the posterior distribution becomes conscious.
-    %     \ac{OurTheory} provides an answer to this question.
-We argue that all the computation of the statistical inference is carried out at microscopic levels of the neural system.
-The macroscopic NTIC process only encodes sufficient statistics of the microscopic processes and has no way to access the full microscopic states due to informational closure to the microscopic processes.
-    %     In this case, microscopic (cellular level) measurements may not have good correspondence with conscious contents.
-Instead, summary statistics are macroscopic variables corresponding with conscious contents.
-
-    %     \subsubsection*{The Second Example: Libet Experiments: The measurement is overly coarse-grained }
-    %         The same scenario can be applied to the results from Libet's volition experimental paradigm \citep{Libet1983TimeOC, Libet1985Dec}.
-
-    %         Experiments using similar procedures usually show that the recorded neural activities start earlier than subjects' feeling of their own intention to act in the self-determined experimental settings.
-
-    %         hWe argue that free actions are initiated at the microscopic levels, for example, the random fluctuation in the neural system \citep{schurger_accumulator_2012}.
-However, the conscious experience of volition is information at the macroscopic level with NTIC.
-Due to the information closure, there is no way for the NTIC process to observe the information of the microscopic states, i.e.
-the initiation of actions.
-
-    %     % \subsubsection*{Fail t  o meet the 2\lowercase{ed} condition}
-    %     As mention above, information is level-dependent and can be virtually independent (closed) across different coarse-graining scales.
-If processes at some levels of a system are able to form high NTIC and become conscious, information at other levels still remains unconscious.
-The first implication of this argument is that processes at levels with high stochasticity are unable to form high NTIC and, therefore, unconscious.
-High stochasticity corrupts informational channel capacity and leads to low mutual information between past and future states of a process.
-In the neural system, the cellular level activities are highly noisy and are unable to reach high NTIC.
-Therefore, the information processed by the microscopic levels in the neural system are not conscious and we never can experience detail activities in the microscopic levels.
-
-    %     @ Evidence suggests that the neural system is able to encode probability distribution and perform probabilistic inference in a near optimal way\needref{bayesian brain}.
-However, an intriguing fact is that we are nearly ignorant of all the probabilistic computation of the inference processes but are only aware of "a sample" of the posterior distributions of the inferences \citep{dehaene2017consciousness, vul2009attention, asplund2014attentional, vul2008temporal, moreno2011bayesian}.
-The information of all alternative possible states is unable to enter conscious contents.
-In short, one needs to explain why the neural system can hold the joint probability distributions of inferred variables but, however, only a realisation of the inference outcome becomes conscious.
-Based on our theory, we argue that the computation of statistical inference is carried out at microscopic levels of the neural system and the NTIC process correlated with conscious contents only possesses the coarse-grained information of the computation.
-The mapping from the microscopic to macroscopic states naturally leads to a single and stable state at the macroscopic levels.
-
-    %     For example, Fig.~ \ref{fig:TemperatureExample} illustrates the relationship 
-    %     At the left panel, two cups contain water with different volumes $V_t$ and temperatures $T_t$.
-Even though we know volumes and temperatures are coarse-grained macroscopic variables, the states of mixed water ($V_{t+1}$, $T_{t+1}$) can still be predicted without knowing any information from the microscopic levels (the molecular level),i.e., the information closure at the macroscopic level.
-Similarly, taking Bayesian inference as an example, the microscopic neuron populations are able to represent probabilistic distributions about inferred target variables and the neural networks perform the statistical inference to obtain the posterior distributions.
-However, enormous microscopic neural states can be coarse-grained into the same state of summary statistics (e.g., the mean $\mu_{t}$  and standard deviation $\sigma_{t}$) at a macroscopic level.
-The state transition ($\mu_{t+1}$ and $\sigma_{t}$) is also predictable without any additional information from microscopic levels.
-Therefore, consciousness can only "observe" the coarse-grained states without the knowledge of how the statistical inference is implemented and performed at the microscopic levels.
-
-    % 	\begin{figure}[H]
-    % 		\includegraphics[width=1.3\textwidth]{WritingMaterials/Fig_Temperature_Example/ExampleOfCG.pdf}
-    % 		\centering
-    % 		\caption{An Example of ...}
-    % 		\label{fig:TemperatureExample}
-    % 	\end{figure}
-
-    %     The same scenario can be applied to the results from Libet's volition experimental paradigm \citep{Libet1983TimeOC, Libet1985Dec}.
-Experiments using similar procedures usually show that the recorded neural activities start earlier than subjects' feeling of their own intention to act in the self-determined experimental settings.
-We argue that free actions are initiated at the microscopic levels, for example, the random fluctuation in the neural system \citep{schurger_accumulator_2012}.
-However, the conscious experience of volition is information at the macroscopic level with NTIC.
-Due to the information closure, there is no way for the NTIC process to observe the information of the microscopic states, i.e.
-the initiation of actions.
-
-    %     \idea{Not sure if I want to address this point}  Note that, some evidence suggests single-cell-level correlation of conscious experience, the Jennifer Aniston cell for example \citep{Quiroga2005Jun, Quiroga2012Jul}.
-This may seem to counter our argument that single-cell level information is incapable to be conscious.
-However, first, the correlations are always not the direct microscopic state changes of the cells, e.g.
-the action potentials.
-Instead, the correlated variables are always coarse-grained.
-The neuronal firing rate, for example, is a temporal coarse-grained variable.
-Second, it has been well established that heterogeneous nonlinearity is critical for neural populations to encode rich and high dimensional information.
-\citep{Chelaru2008, Rigotti2010Oct, Shamir2004Jun}.
-It is common to detecting a single neuron whose activity profile well align with a subspace which represents a single object within the state space of a population code.\needhelp{Maybe need to rewording here} We believe that multi-scale data and analyses are needed to elucidate whether single neuron behaviours are sufficiently representative for any type of conscious experience.
+\ac{OurTheory} further demonstrates remarkable explanatory power for various findings of conscious and unconscious processing.
 
@@
     		%Neurorepresentationalism also suggests conscious experience is associated with integrated representation for multimodal and situational information.
-    		However, \ac{OurTheory} is grounded by non-functional informational assumptions. Therefore, \ac{OurTheory} provides a more fundamental explanation for the scale problem of consciousness.
+    		However, \ac{OurTheory} is grounded by non-functional informational hypothesis. Therefore, \ac{OurTheory} provides a more fundamental explanation for the scale problem of consciousness.
 
@@
 
-		    \textbf{Prediction after system damaged}: \ac{OurTheory} and IIT lead to different predictions when a system suffers from a damage.
-For example, considering a densely connected networks whose dynamics forms an NTIC process.
-If we cut the network in half, IIT would predict that this results in two consciousnesses because elements in both networks still maintain high degrees of interactions.
-In contrast, \ac{OurTheory} would predict that this operation could completely destroy NTIC rendering both parts unconscious.
-
 		    \textbf{The concept of "integration"}: In IIT, integrated information is one of the core concept of defining conscious individuals.
@@
 
-            % ============================================================================ %
-            %                                    Backup                                    %
-            % ============================================================================ %
-
-% 		    % ================================ Difference ================================ 
-% 		    \begin{ants}
-%     		    @@ However, \ac{OurTheory} considers that when a process is informationally closed to the universe, the process can be reckoned as a reality.
-
-%     		    One difference is that IIT does not consider environmental information
-%     		    @ IIT considered causality is the key foundation of consciousness
-%     		    @ \ac{OurTheory} focus more on informational closure as the key properties to form a reality. 
-% .
-
-%     		    @ Conscious contents in \ac{OurTheory} are 
-%     		    @@  a subset of elements can contribute a specific aspect of experience only if its cause-effect repertoire within the system is irreducible by the minimum partition of the mechanism (‘small phi’ or φ)
-
-%     		    @@ \ac{OurTheory} considered whether a part contribute conscious content whether it's within the range of informational closure
-
-%     		    @ Exclusion 
-%     		    @@ Boundary problem by exclusion
-%     		    @@ In \ac{OurTheory}, boundaries of a conscious process is defined by its information boundary, i.e. informational closure.
-%     		    @@ ic between level
-%     		    @ conscious level
-%     		    @@  Φ max
-% 		    \end{ants}
-
-% 		    % ----------------------------------------------------------------------------
-%     		Integrated information theory (IIT) states that system's consciousness is determined by its causal properties.
-Consciousness is integrated information.
-As a computational theory of consciousness, the degree of discrimination and integration can be expressed in mathematical terms $\Phi$.
-Different from most of other scientific theory of consciousness, IIT asserts that the fundamental physical property associated with consciousness is causality.
-
-%     		% -------------------------------- Similarity -------------------------------- %
-%     		IIT and our theory shares common principles in many aspects.
-First common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness \needref{cite David Chalmers}.
-Therefore, both theories are capable of extrapolation and infer the states of consciousness in other systems beyond the human neural system.
-
-%     		Second, both theories consider informational structure as the fundamental entities associated with the quality of conscious contents.
-IIT proposes that a "complex" which is defined as elements that generates a local maximum of integrated information as the core entity which determines the state space of subjective feeling (qualia space).
-In the current stage of our theory development, we have not proposed such sophisticated description of the mappting between informational structure and the qualia space.
-However, in line with this notion, we argue that the state space of an NTIC process determines the subjective experience possessed by the process.
-
-%     		\ideaBox{Maybe synergy is the common part of the two theories }
-
-%     		Even though both theories are based on informational properties of a process, predictions of the two theories can be very different.
-Taking the split brain cases as the example, when splitting a system into two parts, IIT suggests that each part can form a new complex.
-Therefore, splitting creates two new conscious entities.
-However, according to our theory, splitting a system may totally destroy the informational structure that created NTIC.
-This may lead to very small degree of NTIC in both hemispheres, thereby entirely destroying consciousness of this system.
-Notwithstanding, more simulation work is needed to thoroughly clarify how the two theories make same and different predictions in different contexts.
-Fortunately, due to the computational nature of the two theories, precise differences of predictions can be made from relatively simple toy model in the future work.
-
-%     		% Hoel's theory\cite{hoel2016can}}
-%     		Alongside with the main theoretical development of IIT, \cite{hoel2016can,hoel2013quantifying} discussed the scale-dependent causal structures using IIT as a measure of causal power at different scales.
-The result shows a qualitative similarity to our theory.
-The causal power can emerge at macroscopic levels of a system.
-This claim is consistent with our prediction in which processes at macroscopic levels can form more deterministic and predictive state transitions.
-We expect further mathematical and empirical analysis can reveal the relationship between \ac{OurTheory} and Hoel's analyses about the causal power at different scales in a system.
+		    \textbf{Prediction after system damaged}: \ac{OurTheory} and IIT lead to different predictions when a system suffers from a damage.
+For example, considering a densely connected networks whose dynamics forms an NTIC process.
+If we cut the network in half, IIT would predict that this results in two consciousnesses because elements in both networks still maintain high degrees of interactions.
+In contrast, \ac{OurTheory} would predict that this operation could completely destroy NTIC rendering both parts unconscious.
 
@@
 The perceptual contents are the "best guess" about the environment states including these hidden causes \citep{clark_2013, Hohwy2013}.
-PP is well integrated with Bayesian brain hypothesis and has been used to interpret conscious perception in many domains \citep{Hohwy2013, SethPP2014}.
+PP is well integrated with Bayesian brain hypothesis and has been used to interpret conscious perception in many domains \citep{Hohwy2013, seth2014predictive}.
 
@@
 
-    		% ============================================================================
-    		----------------------------------------------------------------------------\\
-
-    % 		Furthermore, only the mutual information between environments and NTIC processes matters. The "true" external reality may not be known.
-
-    % 		self-predictive nature of a NTIC process
-
-    % 		Here, from more fundamental principles, we  argue that our theory is able to well fill the two gaps simply by considering the two conditions mentioned in section \ref{sec:Conscious versus Unconscious Processing}.
-
-    % 		First, predictive processes do not necessitate NTIC.
-A neural mechanisms is able to generate prediction does not guarantee it is an NTIC process.
-For example, an algorithm can take the current states of a target entity as the inputs and compute future states of the target.
-In this case, this algorithm can compute predictive information.
-However, the states of the internal variables are fully determined by the external input, implying that this algorithm is not informationally closed.
-We suggests that if a predictive process is not an NTIC process, predictions from this process will not be able to show in conscious contents (i.e., fail to meet the 1\lowercase{st} condition in section \ref{sec:Conscious versus Unconscious Processing}).
-In contrast, predictive information in the NTIC process is conscious and makes the process form information closure.
-
-    % 		Second, as mentioned in section \ref{sec:Conscious versus Unconscious Processing}, if a process is not at the coarse-grained level achieving NTIC, this process will not be conscious (Fail to meet the 2\lowercase{ed} condition).
-We have provided an example in section \ref{sec:Conscious versus Unconscious Processing} in which computation can be implemented at microscopic levels.
-However, if the coarse-grained result of the computation is included in the macroscopic NTIC process, only the result rather than the process itself can be consciously aware of.
-Therefore, we predict that the statistical inferences under PP are implemented in microscopic levels.
-The NTIC process is ignorant to the detail information of their computations.
-
-    %         Altogether, our theory provides more fundamental principles and explanations about the relationship between predictive mechanisms and consciousness.
-Moreover, the fundamental principles allow us to make more precise predictions about which types of PP should or should not be conscious.
-Therefore, our theory has stronger falsifiability and predictability beyond PP on consciousness research.
-
         % ---------------------------------------------------------------------------- %
@@
 
-    	    \ac{OurTheory} is not compatible with SMC due to the fundamental differences of assumptions of the two theories.
+    	    \ac{OurTheory} is not compatible with SMC.
 As mentioned in Sec.~\ref{sec:Conscious versus Unconscious Processing}, a process directly maps the sensory states to the action states is insufficient to be NTIC.
@@
 
-    	    Different from the classical SMC, a new version of SMC, Predictive Processing of SensoriMotor Contingencies (PPSMC), proposed by \cite{seth2014predictive, seth2015presence} PPSMC combines SMC and the predictive processing framework together.
-PPSMC emphasises the important role of generative models in computing counterfactual, inferring hidden causes of sensory signals, and linking fictive sensory signals to possible actions.
-We argue that if the generative model involving the NTIC process for the computation of counterfactual, PPSMC will be compatible to our theory and may have strong explanatory power on some special conscious experience.
+    	    Different from the classical SMC, a new version of SMC, Predictive Processing of SensoriMotor Contingencies (PPSMC), proposed by \cite{seth2014predictive, seth2015presence} combines SMC and the predictive processing framework together.
+PPSMC emphasises the important role of generative models in computing counterfactuals, inferring hidden causes of sensory signals, and linking fictive sensory signals to possible actions.
+According to \ac{OurTheory}, if the generative model involving the NTIC process for the computation of counterfactuals, PPSMC will be compatible to our theory and may have strong explanatory power on some specific conscious experience.
 
@@
 
-        While GWT emphasise the importance of global information sharing as a basis of consciousness, the precise meaning of information broadcasting has been somewhat unclear if one tries to describe it more formally in the language of information theory.
+        While GWT emphasises the importance of global information sharing as a basis of consciousness, the precise meaning of information broadcasting has been somewhat unclear if one tries to describe it more formally in the language of information theory.
 \ac{OurTheory} offers one possible way to consider the meaning of broadcasting in GWT.
@@
     \section{Limitation and Future work}\label{sec:Limitation and Future work}  
-        In this article, we propose the first version of \ac{OurTheory} and introduce the central concepts, assumptions, and propositions.
-However, as a brand new theory of consciousness, \ac{OurTheory} is still far from completion.
+        As a brand new theory of consciousness, \ac{OurTheory} is still far from completion.
 In the following, we discuss the current limitations and challenges of \ac{OurTheory} and point out the potential future research directions.
@@
 Knowing the state of a conscious process does not allow us to answer "What is it like to be in this state of this process" \citep{nagel1974like}.
-Instead, \ac{OurTheory} focuses more on bridging consciousness and the physical world using information as a common language in between.
-%Therefore, \ac{OurTheory} cannot solve the inverted spectrum argument \citep{Shoemaker1982-SHOTIS, Block1990-BLOIE, Locke1979-LOCTCE-2} unless we can gain one more bit of information to distinguish whether the two processes are same or different.
-
-        %This means \ac{OurTheory} cannot solve the inverted spectrum argument \citep{Shoemaker1982-SHOTIS, Block1990-BLOIE, Locke1979-LOCTCE-2}.
+Instead, \ac{OurTheory} focuses more on bridging consciousness and the physical world using information theory as a common language in between.
 
@@
 This approach can also be applied to finding the boundaries of individual consciousnesses (for details of the boundary detection procedure, see \cite{krakauer2014information}).
-However, in some spacial circumstances, individuality of consciousness has more than one outcome.
-For instance,
-            \needhelp{@Martin, if you think it's better to have a proof for this and if you don't mind, you can help me to write the proof here or create an appendix section and put it there.
-If you have no time, I can also do this.}
-        we can define a new process $Y$ and also its environment $E$ by recruiting two independent NTIC processes $Y^1~\&~Y^2$ and their environments $E^1~\&~E^2$, respectively.
+However, in some specific circumstances, individuality of consciousness is not clear.
+For instance, we can define a new process $Y$ and also its environment $E$ by recruiting two independent NTIC processes $Y^1~\&~Y^2$ and their environments $E^1~\&~E^2$, respectively.
 So that $Y = \{Y^1,Y^2\}$ and $E=\{E^1,E^2\}$.
 In such case, the new process $Y$ will also be NTIC to $E$.
-Therefore, the current version of \ac{OurTheory} cannot determine whether there are two smaller consciousnesses or one bigger consciousness (or 3 coexisting consciousnesses ).
+Therefore, the current version of \ac{OurTheory} cannot determine whether there are two smaller consciousnesses or one bigger consciousness (or 3 coexisting consciousnesses).
 The problem of individuality is a significant theoretical weakness of the current version of \ac{OurTheory}.
-The notion of integration is a possible remedy for this issue and we will address this issue more explicitly in future work using the concept of synergy.
+The notion of integration is a possible remedy for this issue and we will address this issue more explicitly in our future work using the concept of synergy.
 
@@
 However, we do not exclude the possibility that environmental information may be just a proxy of other informational quantities.
-So far, we can only claim NTIC is sufficient for consciousness.
-We are not able to draw further speculations.
-More theoretical work is needed.
+More theoretical work is needed to elucidate the role of environments.
 This issue will also be discuss in our next theoretical paper.
@@
 For example, the concept of \textit{causal emergence} proposed by Hoel \citep{Hoel19790, Hoel2018} has been further developed recently.
-Causal emergence is highly relevant to informational closure at coarse-grained levels.
+Causal emergence is highly relevant to the relationship between informational closure and coarse-graining.
 In their new study by \cite{klein2019uncertainty}, they started to compare how different coarse-graining functions influence causal emergence at macroscopic levels.
@@
 \cite{Gamez2016} has also systematically described relevant issues in terms of finding data correlates of consciousness amount different levels of abstraction.
-We believe that interdisciplinary research is required to narrow down the scope of searching the coarse-graining functions and conscious processes at the coarse-grained level in the neural system and beyond.
+We believe that interdisciplinary research is required to narrow down the scope of searching the coarse-graining functions and conscious processes at the coarse-grained levels in the neural system and beyond.
 
@@
 This is understandable because the concept of NTIC is relatively new in the history of information science, not to mention in neuroscience.
-Very few experiments and data collections are designed for examining NTIC properties in the neural system.
-To our knowledge, only two studies \citep{Palmer2015, sederberg2018learning} coincidentally examine similar properties in salamander retina.
+Very few experiments and data collections are designed for examining NTIC properties in neural systems.
+To our knowledge, only two studies \citep{Palmer2015, sederberg2018learning} coincidentally examine relevant properties in salamander retina.
 They found that the a large group of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states.
-The results, in line with the characteristic of NTIC.
-We expect that there will be more empirical studies examining the NTIC property in the neural system.
+This result is in line with the characteristic of NTIC.
+We expect that there will be more empirical studies examining relevant neural properties of NTIC.
 
@@
     In this paper, we introduced \textbf{\acf{OurTheory}}, a new informational theory of consciousness.
-Based on four assumptions, \ac{OurTheory} proposes that a process which forms \textbf{non-trivial informational closure (NTIC)} is sufficient to be conscious and through coarse-graining the neural system forms a NTIC process, i.e., a conscious process, at a certain macroscopic level.
+\ac{OurTheory} proposes that a process which forms \textbf{non-trivial informational closure (NTIC)} is conscious and through coarse-graining the neural system can form NTIC processes, i.e., conscious processes, at a certain macroscopic level.
 \ac{OurTheory} considers that information is a common language to bridge the gap between conscious experience and the physical reality.
@@
 The implications of \ac{OurTheory} point out that the levels of coarse-graining play a critical role in searching for neural substrates of consciousness.
-Improper measurements, e.g., too fine or too coarse in terms of the scale of measurements, of neurophysiological signals may lead to misleading results and interpretations.
+Improper measurements, e.g., too fine or too coarse in terms of the scale of measurements, of neurophysiological signals may lead to misleading results and misinterpretations.
 
@@
 \ac{OurTheory} indicates that they conditionally coincide with \ac{OurTheory}'s implications and predictions but, however, not the fundamental and sufficient conditions for consciousness.
-For example, theories includes the theories emphasising recurrent circuits \citep{lamme2006towards, edelman1992bright}, the theories highlighting the internal simulation,  predictive mechanism, and generative models ~\citep{revonsuo2006inner, clark_2013,Hohwy2013,SethPP2014, kanai_chang_yu_de_abril_biehl_guttenberg_2019, seth2014predictive, seth2015presence}, and theories related to multilevel view of consciousness~\citep{pennartz2018consciousness,pennartz2015brain,prinz2007intermediate, jackendoff1987consciousness}.
-Notably, \ac{OurTheory} is proposed based on non-functional assumptions and propositions.
-Notwithstanding, its implications for the functional aspects of a system well fit the proposals from functionalist theories mentioned above.
+For example, theories includes the theories emphasising recurrent circuits \citep{lamme2006towards, edelman1992bright}, the theories highlighting the internal simulation,  predictive mechanism, and generative models ~\citep{revonsuo2006inner, clark_2013,Hohwy2013, kanai_chang_yu_de_abril_biehl_guttenberg_2019, seth2014predictive, seth2015presence}, and theories related to multilevel view of consciousness~\citep{pennartz2018consciousness,pennartz2015brain,prinz2007intermediate, jackendoff1987consciousness}.
+Notably, \ac{OurTheory} is proposed based on the non-functional hypothesis.
+Notwithstanding, its implications for the functional aspects of a system well fit several functionalist proposals.
 
@@
 As a result, \ac{OurTheory} provides an integrated view for these arguments and is further capable of indicating how and why they are conditionally true.
-
+W
 	% Final 
@@
 	\section*{Acknowledgements}
-	A.C., Y.Y, and R.K. are funded by Japan Science and Technology Agency (JST) CREST project. R.K. and M.B. are supported by Templeton World Charity Foundation.
+	A.C., Y.Y, and R.K.
+are funded by Japan Science and Technology Agency (JST) CREST project.
+Work by M.B.
+and R.K.
+on this publication was made possible through the support of a grant from Templeton World Charity Foundation, Inc.
+The opinions expressed in this publication are those of the authors and do not necessarily reflect the views of Templeton World Charity Foundation, Inc.
 	   % Thank David Schwartzman for letting me concertrate several months for this work.

### 2019-09-28 Paper_neural_coarse_graining_of_consciousness.tex
First submission
Updates from Overleaf

@@
 \begin{document}
-    \linenumbers
+    % \linenumbers
 	\maketitle
@@
     	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the state space of an NTIC process $Y$.
-A large state space of $Y$ contributes conscious levels through the mutual information $I(Y_{t+1};Y_{t})$ and also contributes richer conscious contents by providing more possbile states of conscious processes.
+A large state space of $Y$ contributes conscious levels through the mutual information $I(Y_{t+1};Y_{t})$ and also contributes richer conscious contents by providing more possible states of conscious processes.
     	    \ac{OurTheory} therefore explains why, in normal physiological states, conscious levels and conscious contents are often positively correlated \citep{laureys2005neural}.
@@
 Therefore, the process $Y$ is not informational closed.
-As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain lesss conscious or unconscious.
+As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain less conscious or unconscious.
         			    }
@@
 In this case, especially for the neural system, forming conscious processes at the macroscopic levels coincide with the perspective of emergentism.
-Finally, forming NTIC (conscious) processes through many-to-one maps, i.e., coarse-graining, implies multiple realizability of consciousness.
+Finally, forming NTIC (conscious) processes through many-to-one maps, i.e., coarse-graining, implies multiple realisability of consciousness.
 As a result, \ac{OurTheory} provides an integrated view for these arguments and is further capable of indicating how and why they are conditionally true.
-W
+
 	% Final 

### 2019-09-28 Paper_neural_coarse_graining_of_consciousness.tex
Replace dirty talk to cquotes

@@
 \\
-            This implication is also in agreement with the "axiom" of \textit{information} in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.2]{oizumi2014phenomenology}.
+            This implication is also in agreement with the "axiom" of \textit{information} in Integrated Information Theory (IIT 3.0) which claims that \textquote[{\citealp[P.~2]{oizumi2014phenomenology}}]{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...}
 
@@
 
-            \textbf{The concept of "information"}: In IIT, information refers to "integrated information":\\ \say{Information that is specified by a system that is irreducible to that specified by its parts.}~\citep{tononi2016integrated} In \ac{OurTheory}, information refers to "self-information", i.e.
+            \textbf{The concept of "information"}: In IIT, information refers to "integrated information":\\ \textquote[\citealt{tononi2016integrated}]{Information that is specified by a system that is irreducible to that specified by its parts.} In \ac{OurTheory}, information refers to "self-information", i.e.
 information about the states of conscious experience and the physical states of a process.

### 2019-10-15 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 \begin{document}
-    % \linenumbers
+    \linenumbers
 	\maketitle
@@
 	\section*{Keywords:}
-	Keywords: consciousness, informational closure, non-trivial informational closure, coarse-graining, level of analysis,
+	Keywords: theory of consciousness, non-trivial informational closure, NTIC, coarse-graining, level of analysis
 
@@
 		%% our argument
-		In this article, we propose a new information-based theory of consciousness, called \ac{OurTheory}.
+		In this article, we propose a new information-based theory of consciousness, called \acf{OurTheory}.
 We argue that every process with a positive non-trivial information closure (NTIC) has consciousness.
@@
 We next argue that through coarse-graining the neural system can form a high degree of NTIC at a specific coarse-grained level (Sec.\ref{sec:Neural coarse-graining}).
-In the Sec.\ref{sec:OurTheory}, we propose a new theory of consciousness: \acf{OurTheory}.
+In the Sec.\ref{sec:OurTheory}, we propose a new theory of consciousness (\ac{OurTheory}).
 We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies (Sec.\ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (Sec.\ref{sec:Comparison with other theories}).
@@
 % ============================================================================ %
-	\section{Non-trivial informational closure} \label{sec:Non-trivial informational closure}
+	\section{Non-trivial Informational Closure} \label{sec:Non-trivial informational closure}
 		The notion of non-trivial informational closure (NTIC) is introduced by \cite{BERTSCHINGER.2006}.
@@
 We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic levels.
-Based on the merit of coarse-graining in neural systems, We propose a new theory of consciousness in the next section.
+Based on the merit of coarse-graining in neural systems, we propose a new theory of consciousness in the next section.
 
@@
         % ---------------------------------------------------------------------------- %
-	    \subsection{Level of Consciousness is equal to the degree of NTIC of a process}\label{sec:cl}
+	    \subsection{Level of Consciousness is Equal to the Degree of NTIC of a Process}\label{sec:cl}
             According to Eq.~\ref{eq:nticObjective}, \ac{OurTheory} implies that conscious levels are determined by two quantities.
@@
     		\begin{figure}[H]				
-        		\includegraphics[width=\textwidth]{WritingMaterials/Fig_temp/FoxitReader_2019-01-31_19-03-59.png}
+        		\includegraphics[width=\textwidth]{WritingMaterials/Fig_nonMono/nonMono.pdf}
         		\caption{A non-monotonic relationship between Level of coarse-graining and level of consciousness.}
@@
 
-		\subsection{Conscious Contents Corresponding to States of a NTIC process}\label{sec:cc}
+		\subsection{Conscious Contents Corresponding to States of a NTIC Process}\label{sec:cc}
     	    % richness 
@@
         % ---------------------------------------------------------------------------- %
-	    \subsection{Reconciling the levels and contents of consciousness}\label{sec:reconcile}
+	    \subsection{Reconciling the Levels and Contents of Consciousness}\label{sec:reconcile}
     	    While it is useful to distinguish the notion of the levels and contents of consciousness, whether they can be clearly dissociated has been a matter of debate \citep{bayne2016there, Fazekas2016}.
@@
     % ============================================================================ %
-	\section{Conscious versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
+	\section{Conscious Versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
 	    In this section, we show how \ac{OurTheory} can explain and make predictions about what processes are conscious and what are unconscious.
@@
     % % ============================================================================ %
-    \section{Comparison with other Relevant Theories of Consciousness}\label{sec:Comparison with other theories}
+    \section{Comparison with Other Relevant Theories of Consciousness}\label{sec:Comparison with other theories}
     In this section, we compare \ac{OurTheory} with other relevant theories of consciousness.
@@
         % ---------------------------------------------------------------------------- %
-        \subsection{Multilevel views on consciousness and cognition}\label{sec:MultiLevelView}
+        \subsection{Multilevel Views on Consciousness and Cognition}\label{sec:MultiLevelView}
     		\ac{OurTheory} proposes that conscious processes can occur at any level of coarse-graining which forms NTIC within a system.
@@
         % ---------------------------------------------------------------------------- %
-		\subsection{Integrated information theory}
+		\subsection{Integrated Information Theory}
             Integrated information theory (IIT) states that consciousness is integrated information and system's consciousness is determined by its causal properties \citep{tononi2016integrated}.
@@
         % ---------------------------------------------------------------------------- %
-		\subsection{Sensorimotor contingency}
+		\subsection{Sensorimotor Contingency}
     		Sensorimotor contingency (SMC) theory of consciousness proposes that different types of SMCs give rise to different characteristics of conscious experience \citep{o2001sensorimotor}.
@@
 
-		\subsection{Global workspace theory}
+		\subsection{Global Workspace Theory}
 		Global workspace theory (GWT; \cite{baars1988cognitive, baars1997theatre, baars2002conscious}) or Global Neuronal Workspace theory (GNWT; \cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental}) states that the neural system consists of several specialised modules and a central global workspace (GW) which integrates and broadcasts information gathered from those specialised modules.
@@
 % ============================================================================ %
-    \section{Limitation and Future work}\label{sec:Limitation and Future work}  
+    \section{Limitation and Future Work}\label{sec:Limitation and Future work}  
         As a brand new theory of consciousness, \ac{OurTheory} is still far from completion.
@@
 % ============================================================================ %
-    \section{Conclusion}
+    \section{Conclusions}
     % short re-introduction 
@@
 
+    \section*{Author Contributions Statement}
+    \section*{Conflict of Interest Statement}
+
 	\bibliographystyle{authordate1}

### 2019-10-15 Paper_neural_coarse_graining_of_consciousness_Frontiers.tex
Updates from Overleaf

--- 2019-10-15 Paper_neural_coarse_graining_of_consciousness.tex
@@
 \usepackage{amsthm}
+
+% list of fig para
+\usepackage{tocloft}
+\newlength{\mylen}
+\renewcommand{\cftfigpresnum}{\figurename\enspace}
+\renewcommand{\cftfigaftersnum}{:}
+\settowidth{\mylen}{\cftfigpresnum\cftfigaftersnum}
+\addtolength{\cftfignumwidth}{\mylen}
 
@@
 	\section*{Acknowledgements}
+	\addcontentsline{toc}{section}{Acknowledgements}
 	A.C., Y.Y, and R.K.
@@
 The opinions expressed in this publication are those of the authors and do not necessarily reflect the views of Templeton World Charity Foundation, Inc.
-	   % Thank David Schwartzman for letting me concertrate several months for this work.
 
     \section*{Author Contributions Statement}
+    \addcontentsline{toc}{section}{Author Contributions Statement}
+    A.C.
+conceived and developed the theory.
+M.B.
+and A.C.
+contributed the mathematical formalisation of the theory.
+A.C., M.B, and R.K wrote the manuscript, based on a first draft by A.C.
+with extensive comments from Y.Y.
+All authors contributed to manuscript revision, read and approved the submitted version.
+
     \section*{Conflict of Interest Statement}
+    \addcontentsline{toc}{section}{Conflict of Interest Statement}
+    The authors declare no conflict of interest.
 
 	\bibliographystyle{authordate1}
+	\addcontentsline{toc}{section}{Reference}
 	\bibliography{ref}
 
+	\section*{Figure Legends}
+	\renewcommand{\listfigurename}{~}
+	\addcontentsline{toc}{section}{Figure Legends}
+    \listoffigures
+
 \end{document}

### 2019-10-15 Paper_neural_coarse_graining_of_consciousness_Frontiers.tex
Updates from Overleaf

@@
 \usepackage{import}
-\usepackage{WritingToolsByAcer}
+
+\ProvidesPackage{WritingToolsByAcer}
+
+%% Language and font encoding
+\usepackage[english]{babel}
+%\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+
+%% Sets page size and margins
+\usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
+% \usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
+
+%% Title style
+\usepackage{stringstrings}
+\usepackage[explicit]{titlesec}
+\usepackage{sectsty}
+
+%% ============================== Useful packages ============================= %
+\usepackage[dvipsnames,table,xcdraw]{xcolor}
+\usepackage[round, sort]{natbib}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{graphicx}
+\usepackage{svg}
+\usepackage[colorlinks=true, allcolors=blue]{hyperref}
+\usepackage{authblk}
+\usepackage{float}
+\usepackage{tikz}
+\usepackage{lineno}
+\usepackage{csquotes}
+
+% =================================== Macro ================================== %
+\usepackage[colorinlistoftodos]{todonotes}
+\usepackage[at]{easylist}
+\usepackage{tcolorbox}
+\tcbuselibrary{skins}
+\usepackage{comment}
+\usepackage[framemethod=tikz]{mdframed}
+\usetikzlibrary{shadows}
+\usepackage{soul}
+\usepackage{version}
+
+% Meaning of colours --------------------------------------------------------- %
+%	Red: Important and Critical
+%	Orange: Todo
+%	Blue: Topic and Guideline
+%	Purple: Murmur
+%	Green: Question, Call for help, Open for opinions and comments
+%	Brown: Need Wording
+% ---------------------------------------------------------------------------- %
+
+% Real content
+	% Outline items that can be integrated into main text
+		\newenvironment{ants}
+			{
+			 \begin{easylist}[itemize]
+		 	}
+			{
+			\end{easylist}
+			} %
+
+	% Writing Materials
+    \newenvironment{WritingMaterials} %
+    	{
+            \begin{tcolorbox}[enhanced,
+                title=-,
+                size=small,
+                colbacktitle=Aquamarine,
+                drop fuzzy shadow,
+                fontupper=\small,
+                boxrule=0.4pt,
+                colback=Aquamarine!10!white,
+                sharp corners]
+                Writing Materials
+            \end{tcolorbox}
+            \begin{easylist}[itemize]
+    	}
+    	{
+            \end{easylist}  
+            \begin{tcolorbox}[enhanced,
+                halign=flush right,
+                halign title=right,
+                size=small,
+                colbacktitle=Aquamarine,
+                drop fuzzy shadow,
+                fontupper=\small,
+                boxrule=0.4pt,
+                colback=Aquamarine,
+                colupper=White,
+                sharp corners]
+                Writing Materials -
+            \end{tcolorbox}        
+    	}
+
+    % \excludeversion{WritingMaterials}
+
+% Functional content
+	% Quotes: green
+		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}
+
+	% todo: orange
+		% text todo
+		\newcommand{\toWrite}[1]{\noindent
+			\textcolor{Orange}{\textbf{[[ #1 ]]}}}
+
+	% figure todo
+        \newcommand{\includegraphicsTodo}[2][]{%
+            \tcbox[enhanced,
+                center,
+            	adjusted title=\large To Be Modified ...,
+            	halign title=center,
+            	attach boxed title to top left={yshift=-3mm, xshift=1cm,yshifttext=-1mm}, boxed title style={drop fuzzy shadow},
+            	colbacktitle=RedOrange!70!black,
+            	coltitle=white,
+            	colframe=RedOrange!50!black,
+            	colback=white
+        	]{\includegraphics[#1]{#2}}}
+
+		% figure todo callout
+        \newcommand{\needfig}[1]{%
+			\ifthenelse{\equal{#1}{}}{%
+				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig}}}{%
+				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig: #1}}%
+			}%
+		}
+
+		% rewording
+		\newcommand{\rewording}[1]{\textcolor{RawSienna}{[[ REWORDING | #1 ]]}}
+
+		% Need reference
+		\newcommand{\needref}[1]{%
+			\ifthenelse{\equal{#1}{}}{%
+				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref}}}{%
+				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref: #1}}%
+			}%
+		}
+
+	% Highlight: Yellow or Red
+		% Highlight only
+		\newcommand{\highlight}[2][Yellow]{\sethlcolor{#1}\hl{#2}}
+
+		% Highlight and comment
+        \newcommand{\highlightAndComment}[3][Yellow]{\sethlcolor{#1}\hl{#2}\todo[color=#1, linecolor=Yellow]{#3}}
+
+		% Critical point
+		\newcommand{\critical}[1]{%
+			\todo[color=OrangeRed!80!white]{#1}
+		}
+
+	% idea: Purple
+		% text idea
+			\newcommand{\idea}[2][Plum]{\noindent
+				\textcolor{#1}{[[ #2 ]]}}
+
+		% box idea
+			\newcommand{\ideaBox}[1]{
+			    \vspace{2mm}
+				\begin{tcolorbox}[enhanced,%
+                    title=-,
+                    center,
+                    fontupper=\small,
+                    lifted shadow={1mm}{-2mm}{3mm}{0.1mm}{black!50!white},%
+                    boxrule=0.4pt,
+                    width=9cm,
+                    colback=Thistle!50!white,
+                    sharp corners]
+					#1
+				\end{tcolorbox}
+				\vspace{2mm}
+			}
+
+		% call-out idea
+			\newcommand{\ideaCallout}[1]{\todo[color=Thistle!50!white, size=\small]{#1}}
+
+	% communication: green
+		% call for help
+			\newcommand{\needhelp}[1]{\todo[color=SpringGreen]{[Need Help]: #1}}
+
+		% comment
+			% comment by authors
+			\newcommand{\addcomment}[3][\empty]{\todo[color=SkyBlue]{Comment [#2]:\newline#3}\colorbox{SkyBlue}{#1}}
+
+			% usage:
+			% \addcomment{auther}{comment text}
+			% or
+			% \addcomment[highlighted text]{auther}{comment text}
+			%
+			% e.g.
+			% It's a \addcomment[beautiful]{Acer}{need a reference} day
+
+    % backup: 
+    \newenvironment{backup}
+    {
+
+        \begin{tcolorbox}[enhanced,
+            title=-,
+            size=small,
+            colbacktitle=black!70!white,
+            colback=black!10!white,            
+            drop fuzzy shadow,
+            fontupper=\small,
+            boxrule=0.4pt,
+            sharp corners]
+            Backup
+        \end{tcolorbox}
+    }
+    {
+        \begin{tcolorbox}[enhanced,
+            halign=flush right,
+            halign title=right,
+            size=small,
+            colbacktitle=black!10!white,
+            colback=black!70!white,
+            drop fuzzy shadow,
+            fontupper=\small,
+            boxrule=0.4pt,
+            colupper=White,
+            sharp corners]
+            Backup -
+        \end{tcolorbox}    
+    }
+    % \excludeversion{backup}
+
+% review loop annotation
+    \usepackage[xcolor, outerbars]{changebar}
+    \cbcolor{red}
+
+    % start anchor: \rlstart
+    \newcommand{\rlstart}[1]{  %
+        \setlength\changebarwidth{#1pt*2}  %
+        \hspace*{-40pt}
+        \cbstart{\textcolor{red}{\newline\textbf{iteration #1}}\newline}}
+
+    % end anchor: \rlend
+    \newcommand{\rlend}{\cbend}
+
+% quote
+\newcommand{\myQuote}[1]{\textit{``#1''}}
+
+% Review ---------------------------------------------------------------------------- %
+\newenvironment{reply}  
+    {\color{Blue}\noindent\newline}
+    {\newline}
+
+% \revise
+%   {Page}{original text}{revised text}
+\newcommand{\revise}[2]{
+    \noindent
+    \newline
+    Original:\newline
+    \textit{"#1"}
+    \newline
+    \newline
+    Revised:\newline
+    \textit{"#2"}\newline}
 
@@
 	\maketitle
+
+	\section*{Word Count:}
+	Total Words :7115\\
+    Headers :27\\
+    Math Inline :112\\
+    Math Display :12\\
+
 	\tableofcontents

### 2020-02-19 ICT_Frontiers_rev202001.tex
Updates from Overleaf

--- 2019-10-15 Paper_neural_coarse_graining_of_consciousness_Frontiers.tex
@@
 The opinions expressed in this publication are those of the authors and do not necessarily reflect the views of Templeton World Charity Foundation, Inc.
+This manuscript has been released as a Pre-Print at arXiv \citep{chang2019information}.
 
@@
     \addcontentsline{toc}{section}{Conflict of Interest Statement}
-    The authors declare no conflict of interest.
+    All authors were was employed by the company Araya Inc.
+The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
 

### 2020-02-27 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

% \input{ICT_Frontiers_rev202001.tex}
\documentclass[utf8]{article}
% \usepackage{import}
% \usepackage{RevisionToolsByAcer}
% \ProvidesPackage{RevisionToolsByAcer}
% \documentclass[utf8]{article}
% \ProvidesPackage{RevisionToolsByAcer}

%% Language and font encoding
\usepackage[english]{babel}
\usepackage[T1]{fontenc}

\usepackage{xr}
\externaldocument{ICT_Frontiers_rev202001}

% Sets page size and margins
% \usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
% \usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
\usepackage{titlesec}
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[at]{easylist}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}
\usepackage[threshold=2, autopunct=true, autostyle=true]{csquotes}

% =============================== Header style =============================== %
\titlelabel{}

% ============================================================================ %
%                               Macros from Acer                               %
% ============================================================================ %
\newenvironment{ants}
	{
	 \begin{easylist}[itemize]
 	}
	{
	\end{easylist}
	}

% env question	
\newcounter{cQuestion}[section]
\newenvironment{question}
    {\refstepcounter{cQuestion}\color{Blue}\noindent\newline Q\thecQuestion:}
    {~\newline}

% env ans    
\newenvironment{ans}  
    {\color{Black}\noindent A:}
    {~\newline}

\newcommand{\QA}[2]{
    \begin{question}  
        #1
    \end{question}

    \begin{ans}  
        #2
    \end{ans}
}

% \revise
%   {Page}{original text}{revised text}
\newcommand{\revise}[3]{
    \noindent
    \newline
    \textbf{On page {#1}:}\newline
    \newline
    Original:\newline
    \textit{"#2"}
    \newline
    \newline
    Revised:\newline
    \textit{"#3"}\newline}
% =================================== Title ================================== %
\title{Response to Reviewers $Rev^1$}
\date{\today}
\author{}

% =================================== Begin ================================== % 
\begin{document}

    \maketitle
    \section*{Reply to Editor}
        \begin{question}
        In addition, I have a question. if we view molecules as coarse grains of elementary particles, would the phenomenon of molecular recognition have high NTIC and thus be conscious?
        \end{question}

        \begin{ans}
            Dear Prof. Hoffman,
            Thank you for this interesting question. 
            There is no question that molecular complexes are coarse-grained objects of molecules through molecular recognition. Based on our hypothesis, if the dynamics of a molecular complex form an NTIC process, our theory (ICT) claims that the molecular complex is conscious. 
            We speculate that it may be easy to find informationally closed molecular complexes (isolated complexes) but may not be easy to find ones with NTIC. Nevertheless, this is a legible empirical question, and we look forward to discovering any self-assembly NTIC process at the molecular scales.
        \end{ans}

    \section{Reply to Reviewer 1}
        \begin{question}
            Regarding the NTCI measure: \\\\
            a) Bertschinger et al. 2006 define informationally closed as $J_t(E -> Y) = 0$, but this is not a requirement for NTIC. Meaning, a positive NTIC measure does not entail that $J_t = 0$. $J_t = 0$ is only true if the NTIC is equal to $I(Y_{t+1}; E_t)$. In what sense does it correspond to non-trivial information closure then? (see also my concern \#2, maybe that is related) As defined in eq. 6 a video camera might have very high NTIC if it records a natural scene, even though it is in no way informationally closed from the environment.\\\\
            b) Is $NTIC_t$ state dependent or not? As capital letters are used I assume it is based on (conditional) mutual information measures across one time step but averaged over the possible states of the system at time t and t+1, so state distributions. But which distributions are used to compute $NTIC_t$? The stationary joint distribution of states at t and t+1? It cannot be just some observed measure, because then the level of consciousness would depend on how long the observation is. Moreover, if $NTIC_t$ is not state dependent, then the Reflex example on p. 10 is not intuitive. Because the system (brain) is the same and awake whether it behaves reflexively or not, so while the content may depend on the type of action, the $NTIC_t$ (level) would stay the same.              
        \end{question}

        \begin{ans}
            TBD
        \end{ans}

        \begin{question}
            Hypothesis and Implication 3: Why is it crucial that there is an underlying X with respect to which Y is a C-process? Does Y being informationally closed with respect to X imply that Y is also informationally closed with respect to E, i.e. $J_t(E-Y) = 0$? I don't think that could be true for the brain, or part of it really. My brain's next state, at whatever level, certainly depends to some degree on unpredictable sensory inputs from the environment. In the end, is $I(Y_{t+1}; E_t|Y_t) = 0$ required for consciousness or not? (see point 1a). In other points in the manuscript this does not seem required, e.g. p. 10 "If a process is not informationally closed, the degree of NTIC is low resulting in low or no consciousness".        
        \end{question}

        \begin{ans}
            Yes. Because X is the micro-level of the universe, any coarse-graining of X (including E and S) should have equal or less information of X. Since Y is informationally closed with respect to X meaning that $X_t$ does not have more information about $Y_{t+1}$ than $Y_t$, any coarse-graining of X should also have equal or less information than $Y_t$. Therefore, Y is informationally closed with respect to X implying that Y is also informationally closed with respect to E and all other coarse-grainings of X.\\
            $\Delta t$
        \end{ans}

        \begin{question}
            Exclusion or no exclusion? The authors state multiple times that "every process with a positive non-trivial information closure (NTCI) has consciousness." (p.3, and also p.12).
            a) Yet, Figure 4 is ambiguous in the sense that the maximum somehow seems important, while actually all levels should give rise to separate experiences. I don't see how ICT without something like exclusion (IIT style) would indicate that the maximum should correspond to human consciousness. It could just be any one out of many consciousnesses.
            b) p. 14: comparison to IIT: what does ICT say about different sets of variables at the same level. There might well be multiple ways to partition X into S and E, with many overlapping S's. Would those all be conscious? They would not be informationally closed from each other but they could all fulfill the requirements in the Hypothesis. It seems like finding the maximum within a level over the possible sets of elements/variables is a necessary step to identify boundaries (I think also Krakauer does that across sets of variables, but not 100\% sure)        
        \end{question}

        \begin{question}
            Feedback and memory: p. 11. If $NTIC > 0$ is sufficient and true information closure is not required, then feedfoward networks can be conscious according to ICT. Also, in that case, memory is not necessary, as the video camera would have $NTIC > 0$ as long as it records from a stable environment. In that case $I(Y_{t+1}, Y_t) > 0$ and $I(Y_{t+1}, Y_t|E_t)$ is small. This issue here is that having information about the next state does not imply that there is any causation, so if $Y_t$ is highly correlated with $E_t$ and $E_t$ causes $Y_{t+1}$ then NTIC is high. (Thus the IIT emphasis on causation).\\
            If somehow the fact that Y must be informationally closed wrt X does the heavy-lifting here that should be made more explicit (see above).
        \end{question}

        \begin{question}
            Does ICT imply that one is unconscious while dreaming? In that case $I(Y_{t+1}; Y_t|E)$ should almost be identical to $I(Y_{t+1};I_t)$ and thus lead to NTIC approx. 0.        
        \end{question}

        \begin{question}
            Minor:
            \begin{itemize}
                \item "contributions to the field" This section is just a copy paste from the abstract and thus not necessarily helpful. Not sure though what the purpose of this section is meant to be by Frontiers.

                \item Introduction: "We currently lack a theory... " IIT and the geometric theory of consciousness (Fekete et al.) have proposed solutions. So there are theories. The following paper should be of interest and should probably be cited:
                Fekete T, van Leeuwen C, Edelman S (2016) System, subsystem, hive: Boundary problems in computational theories of consciousness. Front Psychol 7:1041.

                \item $y_t$ corresponds to the content. I would argue that an activation state, without taking the system or relation between elements etc into account is meaningless and cannot capture/explain the structure of an experience. Though this issue can be dealt with at a later time.
            \end{itemize}
        \end{question}

    \section{Reply to Reviewer 2}
        \begin{question}
I had a few problems in reading the paper, which I think should be addressed (especially the first) before the paper is published. For detailed notes on these see below.

1. The coarse-graining idea seems undefined in critical ways, but the paper reads as though it is well-defined. So maybe the authors have compressed too much detail? In the formalism presented it is unclear what coarse-graining (or information closure to other grains) amounts to. With this lack of detail, it is then unclear to me why intermediate maxima in IC are a plausible result (why does IC not just decline with progressive coarse graining).

2. The idea of 'simulation'. This is a more minor point but I would appreciate if the authors could be clearer on this. It is arguable whether or not consciousness simulates anything (e.g. see Hoffman's interface theory); and some of the assertions the authors make re simulation seem unfounded anyways. But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)

3. There were several other assertions that stood out to me as strange or wrong, but could be a matter of explanation or ignorance on my part (the feedforward system, the cut-apart system). Either way some more explanation would be good.
        \end{question}

        \begin{question}
            The English is not perfect and needs some good proofreading, though it was understandable throughout.

            On line 182, defining C-processes as cases where ‘Y is informationally closed to X’. This is now information closure in the sense of coarse-graining, but no such thing has been defined yet? Is it supposed to be so trivial that it is not required to make it explicit? To this point, closure is defined entirely in terms of system with respect to environment.

            Basically, I am not sure whether closer between scales is a matter of same-time (e.g. $I(Y_{t+1};X_{t+1})$) or across-time interactions ($I(Y_{t+1};X_t)$). Or could it be both?

            On line 241: “.. not sufficiently coarse-grained variables have low values of NTIC”, this is phrased as though it is necessarily true (and also that “we saw above”, though I do not see above where this is justified), but is it?

            At the very finest grain, wouldn’t even all the most ‘stochastic’ dynamics of a system be accounted for by prior states of the system, or by the environment? Why wouldn’t we assume that NTIC *only decreases* as the system is coarse-grained (as number of elements/states is decreased), for similar reasons as it must be zero at a 1-element 1-state system as the authors note? This seems an important point to be very clear on…

            on line 263: “NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.“

            Why does encoding suggest simulation? An encoding *could* be a simulation, but it could well be nothing like a simulation, if we understand simulation to mean something like an imitation or reconstruction of some structure or dynamics. Two totally different environmental situations could potentially be encoded in exactly the same way (eg. as a string of 1s and 0s).

            The ‘simulation’ notion is brought up again in section 5.2 (line 344), citing Bertschinger et al, though I do not find the idea in that paper.. I think authors need to be clearer on what they mean by ‘simulation’ to make this point.

            line 306: “Blindsight patients… make above chancel-level visual judgments without having any conscious perception about visual stimuli” I am not sure this characterization of blindsight is correct, it may be a matter of the phrasing. It could be - or probably is - the case that ‘blindsight’ patients always have some conscious experience of what drives their correct responses, but that the “visual character” of these experiences is degraded or missing.
            (Overgaard, Experimental Brain Research 2011)
            for a specific example
            (Mazzi, Bagattini, Savazzi; Frontiers in Psychology, 2016)

            on Line 316: On the issue of a feedforward network, the current state of a feedforward network with more than one layer is certainly driven by its own past states! So, mutual information of a feedforward network over a time lag should not be zero, unless I am misunderstanding something here?
             At the same time, I can see a version of the authors’ argument here - for a unit in a feedforward network with depth (distance-from-input) of N, a time lag of N time steps would always account fully for the states of the element. Is this the idea?

            on line 441: under the 'Prediction after system damaged', it is suggested that ICT predicts cutting a system in half would render both halves unconscious. But this would only be the case if neither half contains its own C-processes, yes? Since ICT allows that many C-processes can exist at the same time, it would have to be some special case for this prediction to hold true. So it seems to me the prediction is actually similar to that of IIT.

            Line 540: the theory doesn’t really seem to intend to solve the hard problem(s) at all, much less “completely solve”.

            I was expecting the problem of dreaming to come up in the last section (maybe along with SMC for which it is a serious problem). When dreaming the information between environment and the system is virtually zero; is this a problem for ICT? Also, more specific phenomena like the eigengrau - if you take away all visual input, for long enough, I do not lose my visual experiences - rather they take on a special state. Does ITC need to accept the possibility that even *trivial* IC can be a conscious process?        
        \end{question}

\end{document}

### 2020-03-10 ICT_Frontiers_rev202001.tex
Move to local writing

@@
 
-\ProvidesPackage{WritingToolsByAcer}
+%\ProvidesPackage{WritingToolsByAcer}
 
@@
 \usepackage[explicit]{titlesec}
-\usepackage{sectsty}
+%\usepackage{sectsty}
 
@@
 These facts suggest that conscious processes occur at a particular scale.
-We currently lack a theory to identify the scale which conscious processes correspond to.
+\linelabel{line:lack-theory}We currently lack a theory to identify the scale which conscious processes correspond to.
 We refer to this notion as \textbf{the scale problem of consciousness} (Fig.~\ref{fig:scaleproblem}).
@@
 		% Definition of informational closure
-			Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network in Fig.~\ref{fig:SystemAndEnv}.
+			\linelabel{line:r1q1a}Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network in Fig.~\ref{fig:SystemAndEnv}.
 Then, information flow $J_{t}$ from the environment $E$ to a system $S$ at time $t$ can be defined as the conditional mutual information $I$ between the current environment state $E_{t}$  and the future system state $Y_{t+1}$ given the current system state $Y_{t}$
@@
 				\begin{align}
-				\label{eq:NTIC}
+%				\label{eq:NTIC}
     				% \left.\begin{array}
-    				NTIC_t(E\rightarrow Y) :&=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t})\\
+    				NTIC_t(E\rightarrow Y) :&=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}) 
+    				\label{eq:NTIC1}\\
     				&=I(Y_{t+1};E_{t})-I(Y_{t+1};E_{t}|Y_{t}) 
+    				\label{eq:NTIC2}
     				% \end{array} \right.
@@
 	   	\begin{definition}
-	   	Given a stochastic process $X$ with state space $\mathcal{X}$, a \emph{coarse-graining of $X$} is a stochastic process $Y$ with state space $\mathcal{Y}$ such that there exists a function\footnote{Functions in the mathematical sense used here are always either one-to-one or many-to-one.} $f_Y:\mathcal{X}\rightarrow \mathcal{Y}$ with $Y_t=f_Y(X_t)$.
+	   	\linelabel{line:r2q1-1} Given a stochastic process $X$ with state space $\mathcal{X}$, a \emph{coarse-graining of $X$} is a stochastic process $Y$ with state space $\mathcal{Y}$ such that there exists a function \footnote{Functions in the mathematical sense used here are always either one-to-one or many-to-one.} $f_Y:\mathcal{X}\rightarrow \mathcal{Y}$ with $Y_t=f_Y(X_t)$.
 	   	\end{definition}
@@
         A concrete example in the context of neuroscience is that $X$ represents the microscopic level of the universe, $S$ a cellular level process in the neural system, $Y$ a more macroscopic process of the neural system coarse-grained from the cellular level process $S$, and $E$ the environment which the cellular level process $S$ interacts with.
-The environment $E$ may include other processes in the neural system, the sensors for perception and interoception, and external physical worlds.\\
+\linelabel{line:neu-env} The environment $E$ may include other processes in the neural system, the sensors for perception and interoception, and external physical worlds.\\
 
@@
 
-    		Importantly, NTIC processes encodes environmental information in its state.
+    		Importantly, NTIC processes encode environmental information in its state.
 This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.
@@
         		The same principle can be applied to interpret blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedural memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes.
-Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements without having any conscious perception about visual stimuli.
+        		\linelabel{line:r2q6}Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements when their visual experiences is degraded or missing (however, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}).
 We argue that action outputs of blindsight can be directly guided by sensory inputs through stimulus-response maps.
@@
 
-		    \textbf{Prediction after system damaged}: \ac{OurTheory} and IIT lead to different predictions when a system suffers from a damage.
+		    \textbf{Prediction after system damaged}:\linelabel{line:r2-cutting} \ac{OurTheory} and IIT lead to different predictions when a system suffers from a damage.
 For example, considering a densely connected networks whose dynamics forms an NTIC process.
@@
 Crucially, \ac{OurTheory} further provides natural and fundamental explanations to fills the two explanatory gaps which PP encounters.
-According to the definition of NTIC, a process with high NTIC can be regarded as a powerful predictive machine which has accurate self-predictive information ($I(Y_{t+1};Y_{t})$, E.q.~\ref{eq:NTIC}) and concurrently incorporates environmental information into its dynamic ($I(Y_{t+1};Y_{t}|E_{t})$, E.q.~\ref{eq:NTIC}).
+According to the definition of NTIC, a process with high NTIC can be regarded as a powerful predictive machine which has accurate self-predictive information ($I(Y_{t+1};Y_{t})$, E.q.~\ref{eq:NTIC1}) and concurrently incorporates environmental information into its dynamic ($I(Y_{t+1};Y_{t}|E_{t})$, E.q.~\ref{eq:NTIC1}).
 This predictive nature of NTIC processes is in agreement with the core notion of PP in which the conscious contents are always the predicted (inferred) outcome of our predictive mechanisms.
@@
 This issue will also be discuss in our next theoretical paper.
+
+        \linelabel{line:dream}
 
@@
 
-        Finally another empirical challenge to \ac{OurTheory} is the lack of empirical supporting evidence.
+        \linelabel{line:r1-state-dep}
+
+        Finally another empirical challenge to \ac{OurTheory} is the  of empirical supporting evidence.
 This is understandable because the concept of NTIC is relatively new in the history of information science, not to mention in neuroscience.

### 2020-03-10 ICT_Frontiers_rev202001_reply.tex
Move to local writing

@@
 \documentclass[utf8]{article}
-% \usepackage{import}
 % \usepackage{RevisionToolsByAcer}
@@
 % \ProvidesPackage{RevisionToolsByAcer}
-
 %% Language and font encoding
 \usepackage[english]{babel}
+\usepackage[round, sort]{natbib}
 \usepackage[T1]{fontenc}
 
+% ============================ Sourcing main file ============================ %
 \usepackage{xr}
 \externaldocument{ICT_Frontiers_rev202001}
+\usepackage{lineno}
 
@@
 % \usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
-% \usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
+\usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
 \usepackage{titlesec}
@@
 \usepackage[threshold=2, autopunct=true, autostyle=true]{csquotes}
+\usepackage[colorinlistoftodos]{todonotes}
 
@@
 \newcommand{\revise}[3]{
+	\newline
+	\newline
     \noindent
-    \newline
-    \textbf{On page {#1}:}\newline
+    \textbf{line #1:}
     \newline
@@
     \textit{"#3"}\newline}
+
+% ================================ Annotation ================================ %
+\newcommand{\toWrite}[1]{\noindent
+	\textcolor{Orange}{\textbf{[[ #1 ]]}}}
+
 % =================================== Title ================================== %
@@
         \begin{ans}
-            Dear Prof. Hoffman,
-            Thank you for this interesting question. 
-            There is no question that molecular complexes are coarse-grained objects of molecules through molecular recognition.
-Based on our hypothesis, if the dynamics of a molecular complex form an NTIC process, our theory (ICT) claims that the molecular complex is conscious.
-            We speculate that it may be easy to find informationally closed molecular complexes (isolated complexes) but may not be easy to find ones with NTIC.
-Nevertheless, this is a legible empirical question, and we look forward to discovering any self-assembly NTIC process at the molecular scales.
+            Hi Prof. Hoffman,
+            Thank you for your attention to our manuscript and your interesting question. \\
+            There is no question that molecular complexes are coarse-grainings of molecules via molecular recognition.
+Based on our hypothesis, if the dynamics of a molecular complex is an NTIC process, the information closure theory of consciousness (ICT) would claim that the molecular complex has a certain degree of consciousness.
+Therefore, to your question, it is theoretically plausible under the framework of ICT.
+We speculate that it may be easy to find informationally closed molecular complexes (isolated complexes) but may not be easy to find ones forming NTIC processes.
+Nevertheless, with well-defined mathematical definition, this is an empirical and testable question to ICT.
+We look forward to learning any self-assembly process forming NTIC at molecular scales in the near future.
         \end{ans}
@@
     	\begin{ans}
-            TBD
+    		\newline
+    		a) In one of the fomulations of NTIC, Equation 7, NTIC is the sum of  two terms: $I(Y_{t+1}; E_t)$ and $J_t(E -> Y)$. 
+    		It is true that having high NTIC $I(Y_{t+1}; E_t)$ needs to be high.
+However, based on the setting in both Bertschinger et al.
+2006 and our Section 2 (from Line \lineref{line:r1q1a}),  if $Y_t$ does not have information $J_t(E -> Y)$
+
+    		In the video camera example that the reviewer proposed, we can consider two cases.
+If the sensory information extracted by the camera is only partially predictive to the (predictive information \citep{bialek2001predictability} is small).
+
+    		We then consider the other case which the environment E is deterministic and fully observable. If $H(E_{t+1|E_t}=0$ 
+    		It is true that simply copy the entire environment state to $Y$ will yield 
+    		$I(Y_{t+1}; E_t)>0$ and $J_t(E -> Y)=0$.
+
+    		$I(Y_{t+1}; E_t)$ will be large. However, 
+    		\\
+    		\toWrite{Don't know how much to write there}
+
+    		b) Thank the reviewer for this outstanding question. 
+    		Actually, we are currently working on state-dependent formulations of ICT. 
+    		In this first version of ICT, we did not use state-dependent formulations. 
+    		However, we do think a state-dependent measurement is important to describe the conscious experience. 
+    		We have been working on a state-dependent version of NTIC using point-wise informational measurements. 
+    		We have been planning to propose state-dependent ICT in our next version. 
+    		We have added a short paragraph about this issue at Line \lineref{line:r1-state-dep}.
+    		\toWrite{add a short para}
+
     	\end{ans}
@@
 Therefore, Y is informationally closed with respect to X implying that Y is also informationally closed with respect to E and all other coarse-grainings of X.\\
-            $\Delta t$
+            $\Delta t$ regards to the temporal coarse-graining and, therefore, determines the temporal scale that form higher NTIC. It's true that the 
+            \toWrite{Something here}\\
+			In our current version, NTIC was proposed because we attribute both closureness $-I(Y_{t+1}; E_t|Y_t)$ and non-triviality $I(Y_{t+1}; E_t) = 0$. 
+			$I(Y_{t+1}; E_t|Y_t) = 0$ is not necessary. 
+			\toWrite{Really difficult to say this part}
+
         \end{ans}
@@
         \end{question}
+
+    	\begin{ans}
+    		\toWrite{Maybe this needs to be written together with previous reply.}
+    	\end{ans}
 
@@
 
+    	\begin{ans}
+    		\toWrite{Add something here}
+    		We have added a paragraph at Line \lineref{line:dream}
+    	\end{ans}
+
         \begin{question}
             Minor:
-            \begin{itemize}
+            \begin{enumerate}
                 \item "contributions to the field" This section is just a copy paste from the abstract and thus not necessarily helpful.
@@
 Though this issue can be dealt with at a later time.
-            \end{itemize}
+            \end{enumerate}
         \end{question}
+
+    	\begin{ans}
+    		\begin{enumerate}
+    			\item It's true that we were also confused about it during submission. 
+    			We have modified this as follows: \\
+    			\toWrite{"contributions to the field"}
+
+    			\item Thank the reviewer for this suggestion. We have modified our manuscript and cited  the reference at Line \lineref{line:lack-theory}. \toWrite{Change main text}
+
+    			\item We fully agree with the reviewer's comment. 
+    			In fact, in our theory, we do not partition states of processes into activation and relation.
+For example, both activation and structure states of a neural network should be considered.
+After all, they can be parameterised as the parameters of processes.
+The only difference is the temporal scales of parameter changes.
+States of activation may have more rapid dynamics than states of relation.
+In ICT, this difference is crucially related to the temporal coarse-graining which we did not address in this article but can be easily generalised in future versions of ICT.
+
+    			\toWrite{To write something in the main text?}
+
+    		\end{enumerate}
+
+    	\end{ans}
 
@@
 
-1.
-The coarse-graining idea seems undefined in critical ways, but the paper reads as though it is well-defined.
+			\begin{enumerate}
+				\item The coarse-graining idea seems undefined in critical ways, but the paper reads as though it is well-defined.
 So maybe the authors have compressed too much detail?
@@
 
-2.
-The idea of 'simulation'.
+				\item The idea of 'simulation'.
 This is a more minor point but I would appreciate if the authors could be clearer on this.
@@
 see Hoffman's interface theory); and some of the assertions the authors make re simulation seem unfounded anyways.
-But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)
+But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)\todo{I don't understand this question well}
 
-3.
-There were several other assertions that stood out to me as strange or wrong, but could be a matter of explanation or ignorance on my part (the feedforward system, the cut-apart system).
+				\item There were several other assertions that stood out to me as strange or wrong, but could be a matter of explanation or ignorance on my part (the feedforward system, the cut-apart system).
 Either way some more explanation would be good.
+			\end{enumerate}
         \end{question}
+
+    	\begin{ans}
+    		\begin{enumerate}
+    			\item In this article, the definition of coarse-graining is our "Definition 1" (line: \lineref{line:r2q1-1}) which is simply a function mapping a stochastic process $X$ with state space $\mathcal{X}$ to a stochastic process $Y$ with state space $\mathcal{Y}$.
+    			We do not specify any specific types of coarse-graining.
+    			\toWrite{Instead, our hypothesis states that any process which coarse-graining which}
+
+    			We emphasise the non-monotonic relation between the scales of coarse-graining and the degrees of NTIC.
+However, we do not exclude the possibility that there exist multiple NTIC picks across scales of coarse-graining of a process.
+    			This implies that we do not exclude the possibility that there exist multiple high conscious processes at different scales. 
+    			(However, due to IC, conscious processes are not able to know the existence of each other. 
+					\todo{Discuss this}
+
+    			\item \toWrite{TBD}
+    			\item \toWrite{After replying the first reviewer}
+    		\end{enumerate}
+
+    	\end{ans}
 
@@
 			The English is not perfect and needs some good proofreading, though it was understandable throughout.
+        \end{question}
 
+    	\begin{ans}
+    		\todo{What should we deal with this?}
+    	\end{ans}
+
+    	\begin{question}
 			On line 182, defining C-processes as cases where ‘Y is informationally closed to X’.
@@
 			Basically, I am not sure whether closer between scales is a matter of same-time (e.g. $I(Y_{t+1};X_{t+1})$) or across-time interactions ($I(Y_{t+1};X_t)$). Or could it be both?    		
+    	\end{question}
 
+    	\begin{ans}
+			Here, we followed a common setup of coarse-graining (e.g.
+\toWrite{cite here}), which does not take time $Y_t=f_Y(X_t)$ (in Definition 1).
+In this setup, coarse-graining is unidirectional ad does not involve interaction between scales.
+This means that coarser scales supervene on finer scales, and there exists no top-down causation.
+\\
+			In our hypothesis, Y is IC with respect to the microstate of the universe, X.
+This is critical in the hypothesis because Y is IC with respect to X, implying that Y is also IC with respect to its intermediate level S and its environment E in Fig.
+\ref{fig:fullgraph}.\todo{need any change in the main text?}
+    	\end{ans}
+
+    	\begin{question}            
     		On line 241: “..
@@
 This seems an important point to be very clear on…
+    	\end{question}
 
+    	\begin{ans}
+    		\toWrite{The reviewer is right?}
+    		Thank the reviewer for this critical comment.
+It is true that NTIC a monotonic function of scales of coarse-graining.
+NTIC can increase or decrease when the grains are coarser.
+We are currently still working on the relationship between scales and NTIC.
+    		We will systematically address NTIC and functions of coarse-graining in our following studies. 
+    		Further more, in our current analysis, it seems that this is also related to informational synergy and redundancy. We aim for presenting the core concept of ICT in this article.
+    		The reviewer's critical question is on our list of future work. 
+    		\toWrite{Need to change the text a lot!!}
+    	\end{ans}
+
+    	\begin{question}
     		on line 263: “NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.“
@@
 I think authors need to be clearer on what they mean by ‘simulation’ to make this point.
+    	\end{question}
 
+    	\begin{ans}
+    		Thank the reviewer for this mindful comment. 
+    		Our description indeed is not clear enough. The environmental information here about not only states but also state transitions. 
+    		This is because high NTIC implies high mutual information between a process and its environment $I(Y_{t+1};E_t)$ (Eq.
+\ref{eq:nticObjective2}).
+Therefore, the dynamics of the process $Y$ needs to covary with the dynamics of its environment $E$.
+Here, we consider 'simulation' is a more precise expression than 'encoding'.
+    		The notion of simulation is the same as the 'Modeling' case on Page 4 in Bertschinger et al. , 2006: \\
+    		\textit{"B2)~Modeling: The system reaches synchronization and internalizes the correlations observed in the environment by building up own structures."}
+    		\\ \toWrite{add something in the main text}
+    	\end{ans}
+
+   	\begin{question}
 			line 306: “Blindsight patients… make above chancel-level visual judgments without having any conscious perception about visual stimuli” I am not sure this characterization of blindsight is correct, it may be a matter of the phrasing.
@@
 			(Mazzi, Bagattini, Savazzi; Frontiers in Psychology, 2016)
+    	\end{question}
 
+   		\begin{ans}
+   			Thank the reviewer for the clarification. 
+   			Yes, we specifically address the visual character of their experience.
+   			We have changed our sentence as follows:
+   			\revise{\lineref{line:r2q6}}
+   			{
+   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements without having any conscious perception about visual stimuli.
+   			}
+   			{
+   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements when their visual experiences is degraded or missing (however, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}).
+   			}
+   		\end{ans}
+
+    	\begin{question}
             on Line 316: On the issue of a feedforward network, the current state of a feedforward network with more than one layer is certainly driven by its own past states!
 So, mutual information of a feedforward network over a time lag should not be zero, unless I am misunderstanding something here?
-             At the same time, I can see a version of the authors’ argument here - for a unit in a feedforward network with depth (distance-from-input) of N, a time lag of N time steps would always account fully for the states of the element.
+			At the same time, I can see a version of the authors' argument here - for a unit in a feedforward network with depth (distance-from-input) of N, a time lag of N time steps would always account fully for the states of the element.
 Is this the idea?
+    	\end{question}
 
+ 		\begin{ans}
+ 			Thank the reviewer for this valuable comment. 
+ 			Indeed, 
+ 			\\
+ 			\toWrite{This is really a good question.}
+ 			\todo{Indeed, if information is just copied to the process, it will still be NTIC. Feedforward is just a way to copy the information}
+ 		\end{ans}
+
+    	\begin{question}
     		on line 441: under the 'Prediction after system damaged', it is suggested that ICT predicts cutting a system in half would render both halves unconscious.
@@
 So it seems to me the prediction is actually similar to that of IIT.
+    	\end{question}
 
+    	\begin{ans}
+    		Thank the reviewer for this considerate comment.
+The reviewer is correct.
+This prediction is under an assumption which we did not explicitly specify in our last version.
+We assume that we have one conscious (NTIC) process involving information in both brain hemispheres.
+Namely, the process is informationally closed only when we consider the information in both hemispheres.
+We agree that if both hemispheres have their own NTIC proceess ICT should predict no change of conscious experience before and after cutting.
+Cutting should not make any difference because they are informationally closed with respect to each other.
+We also agree that this prediction is relatively premature.
+However, we also acknowledge the strength of all computational theories of consciousness.
+The reviewer's question is empirical to us under formal mathematical formulations of ICT and IIT.
+Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.
+
+    		\toWrite{The original paragraph has been changed as follows: lline \lineref{line:r2-cutting}:}
+    	\end{ans}
+
+        \begin{question}                                                                   
             Line 540: the theory doesn’t really seem to intend to solve the hard problem(s) at all, much less “completely solve”.            
-
             I was expecting the problem of dreaming to come up in the last section (maybe along with SMC for which it is a serious problem).
@@
 
+    	\begin{ans}
+    		ICT is our first attempt to approach the hard problem of consciousness.
+We hope that ICT and our following works can establish an informational perspective on conscious experience.
+Instead of solving the hard problem of consciousness, we more look forward to mathematically determining whether the hard problem can be solved or not by information theory.
+However, because the relevant discussion is clearly outside the scope of this article, we prefer not to discuss the hard problem here.
+n
+
+    		It is important to note that we reckon only part of the neural system is involved in the NTIC process(es).
+This is due to the fact that some parts of the neural system are evidently not informationally closed.
+They only passively react to sensory inputs or other parts of the neural system.
+    		To the NTIC process(es), the rest of the neural system is considered as the environment. This notion is shortly indicated at line \lineref{line:neu-env}.
+    		We speculate that, during dreaming, the neural system can still form the NTIC process(es) with respect to other parts of the neural system which we know they maintain high activities.
+The same idea can be also applied to phenomena like Eigengrau.
+However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our last version of the manuscript.
+However, thank the reviewer for bringing up this question.
+We believe that it is still worth to mention issues about dreaming.
+We have added a short paragraph as follows:
+
+    		\toWrite{add something in the main text at Line \lineref{line:dream}}
+
+    		Finally, we believe that this is also a clear empirical question that can be tested in future studies. 
+    	\end{ans}
+
+	\bibliography{ref}
 \end{document}

### 2020-03-12 ICT_Frontiers_rev202001.tex
ignore desktop.ini

@@
 	   	\end{definition}
-	   	A more general definition of coarse-grainings that maps temporally extended sequences of the microscopic process to macroscopic states are possible but for his first exposure of our theory the simpler definition above is sufficient.
+	   	A more general definition of coarse-grainings that maps temporally extended sequences of the microscopic process to macroscopic states are possible but for this first exposure of our theory the simpler definition above is sufficient.
 
@@
         % Identity problem
-        The current version of \ac{OurTheory} cannot entirely solve the problem of individuality in some extreme circumstances.
+        \linelabel{line:individuality}The current version of \ac{OurTheory} cannot entirely solve the problem of individuality in some extreme circumstances.
 In common cases, one can identify individual consciousnesses by computing the levels of NTIC of a process.
@@
 
-        \linelabel{line:r1-state-dep}
+        \linelabel{line:r1-state-dep}In this article, we do not use a state-dependent formulation of NTIC in the current version of ICT.
+However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.
+Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed in the next version of ICT.
 

### 2020-03-12 ICT_Frontiers_rev202001_reply.tex
ignore desktop.ini

@@
 % ============================================================================ %
-\newenvironment{ants}
-	{
-	 \begin{easylist}[itemize]
- 	}
-	{
-	\end{easylist}
-	}
 
-% env question	
+% --------------------------------- Question --------------------------------- %	
 \newcounter{cQuestion}[section]
@@
 
-% env ans    
+% ------------------------------------ Ans ----------------------------------- %
 \newenvironment{ans}  
@@
 
-% \revise
-%   {Page}{original text}{revised text}
+% ---------------------------------- Revise ---------------------------------- %
+% \Revise{Page}{original text}{revised text}
 \newcommand{\revise}[3]{
@@
     \textit{"#3"}\newline}
+
+% ---------------------------------- Add New --------------------------------- %
+% \addnew{line number}{text}
+\newcommand{\addnew}[2]{\blockcquote{}{Line #1:~\newline\textit{"#2"}}
+}
 
@@
     		\newline
-    		a) In one of the fomulations of NTIC, Equation 7, NTIC is the sum of  two terms: $I(Y_{t+1}; E_t)$ and $J_t(E -> Y)$. 
-    		It is true that having high NTIC $I(Y_{t+1}; E_t)$ needs to be high.
+    		a) Considering Eq.\ref{eq:NTIC2}, it is true that the transfer entropy term $J_t(E -> Y)=0$ is not required for $NTIC>0$.
+It is possible to have a high degree of NTIC when $J_t(E -> Y) > 0$, i.e.
+the process is not completely closed.
+\\
     		However, based on the setting in both Bertschinger et al.
-2006 and our Section 2 (from Line \lineref{line:r1q1a}),  if $Y_t$ does not have information $J_t(E -> Y)$
+2006 and our Section 2 (at Line \lineref{line:r1q1a}), $Y_{t+1}$ is determined by both $Y_t$ and $E_t$.
+Simply increasing $I(Y_{t+1}; E_t)$ without closedness (e.g, copy the information in sensory signals to the process such as the case in the video camera example), the transfer entropy term $J_t(E -> Y)$ should increase at the same rate and cancel out the increment of $I(Y_{t+1}; E_t)$ resulting low NTIC.
+Namely, keeping high closedness, i.e.
+minimising $J_t(E -> Y)$, is crucial to increase NTIC even though $J_t(E -> Y) > 0$.\\
+    		In our current version of ICT, we consider the level of consciousness corresponds to the degree of NTIC of a process.
+Therefore, a conscious process does not have to be completely closed.
+However, a high degree of closedness is crucial to have a high level of consciousness.\\
 
-    		In the video camera example that the reviewer proposed, we can consider two cases.
-If the sensory information extracted by the camera is only partially predictive to the (predictive information \citep{bialek2001predictability} is small).
+    		\noindent
+    		b) Thank the reviewer for this outstanding question.
+We entirely agree that state-dependent measurements are essential to describe the dynamics of conscious experience.
+In fact, we now are working on state-dependent formulations for the next version of the ICT.
+In contrast to the current version, this work involves point-wise informational measures and certainly require more space and discussion.
+Therefore, we prefer to address the state-dependent version of ICT in future studies and keep the first version of our theory simple.\\
+    		We appreciated that the reviewer pointed this out. We have added a short paragraph about this issue.
 
-    		We then consider the other case which the environment E is deterministic and fully observable. If $H(E_{t+1|E_t}=0$ 
-    		It is true that simply copy the entire environment state to $Y$ will yield 
-    		$I(Y_{t+1}; E_t)>0$ and $J_t(E -> Y)=0$.
-
-    		$I(Y_{t+1}; E_t)$ will be large. However, 
-    		\\
-    		\toWrite{Don't know how much to write there}
-
-    		b) Thank the reviewer for this outstanding question. 
-    		Actually, we are currently working on state-dependent formulations of ICT. 
-    		In this first version of ICT, we did not use state-dependent formulations. 
-    		However, we do think a state-dependent measurement is important to describe the conscious experience. 
-    		We have been working on a state-dependent version of NTIC using point-wise informational measurements. 
-    		We have been planning to propose state-dependent ICT in our next version. 
-    		We have added a short paragraph about this issue at Line \lineref{line:r1-state-dep}.
-    		\toWrite{add a short para}
+	    	\addnew{\lineref{line:r1-state-dep}}{
+	    		In this article, we do not use a state-dependent formulation of NTIC in the current version of ICT.
+However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.
+Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed in the next version of ICT.}
 
@@
         \begin{ans}        	
-            Yes.
-Because X is the micro-level of the universe, any coarse-graining of X (including E and S) should have equal or less information of X.
-Since Y is informationally closed with respect to X meaning that $X_t$ does not have more information about $Y_{t+1}$ than $Y_t$, any coarse-graining of X should also have equal or less information than $Y_t$.
-Therefore, Y is informationally closed with respect to X implying that Y is also informationally closed with respect to E and all other coarse-grainings of X.\\
-            $\Delta t$ regards to the temporal coarse-graining and, therefore, determines the temporal scale that form higher NTIC. It's true that the 
-            \toWrite{Something here}\\
-			In our current version, NTIC was proposed because we attribute both closureness $-I(Y_{t+1}; E_t|Y_t)$ and non-triviality $I(Y_{t+1}; E_t) = 0$. 
-			$I(Y_{t+1}; E_t|Y_t) = 0$ is not necessary. 
-			\toWrite{Really difficult to say this part}
-
+            Because X is the micro-level of the universe, any coarse-graining of X (including E and S) should have equal or less information about Y than X, i.e.
+$I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and  $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$.
+Therefoe, Y is informationally closed with respect to X implying that Y is also informationally closed with respect to S, E, and all other coarse-grainings of X.
+As explained in Question 1a, it is not required for NTIC processes to be completely closed.
+Therefore, the closedness of Y with respect to X $I(Y_{t+1}; X_t|Y_t)$ serves as the lower bound of the closedness of Y to any other processes.
+            For this first exposure of our theory, we did not discuss NTIC in the context of the temporal coarse-graining.
+It is true that we certainly encounter some degree on unpredictable sensory inputs from the environment from time to time.
+Therefore, NTIC should be higher for finer temporal scales than for coarser temporal scales.
+We also speculate that the temporal coarse-graining is related to the speed of "stream of consciousness" and will address this issue in our future studies.
         \end{ans}
@@
     	\begin{ans}
-    		\toWrite{Maybe this needs to be written together with previous reply.}
+
     	\end{ans}
@@
     			\item \toWrite{TBD}
-    			\item \toWrite{After replying the first reviewer}
+%    			\item \toWrite{After replying the first reviewer}
     		\end{enumerate}
@@
  			Thank the reviewer for this valuable comment. 
+ 			\begin{figure}[H]
+ 				\centering
+ 				\includegraphics[width=\textwidth]{WritingMaterials/Fig_ScaleProblemOfConsciousness/ScaleProblemOfConsciousness.pdf}
+ 				\caption{The scale problem of consciousness: Human conscious experience does not reflect information from every scale.
+Only information at a certain coarse-grained scale in the neural system is reflected in consciousness.}
+ 				\label{fig:scaleproblem}
+ 			\end{figure}
+
  			Indeed, 

### 2020-03-17 ICT_Frontiers_rev202001.tex
start sharing

@@
 These facts suggest that conscious processes occur at a particular scale.
-\linelabel{line:lack-theory}We currently lack a theory to identify the scale which conscious processes correspond to.
+\linelabel{line:lack-theory}We currently have only few theories (e.g., Integrated Information Theory \citep{hoel2016can} and Geometric Theory of Consciousness \citep{fekete2011towards,fekete2012lack}) to identify the scale which conscious processes correspond to ( also see discussion in \cite{fekete2016system}).
 We refer to this notion as \textbf{the scale problem of consciousness} (Fig.~\ref{fig:scaleproblem}).
@@
 
+        \linelabel{line:IC2CG}Note that we applied the same definition of information closure (Eq.\ref{eq:InformationFlow}) to processes at different coarse-grained levels \citep{{PFANTE.2014}}.\\
+
         With the two definitions we can state the main hypothesis of \ac{OurTheory}:
@@
     	    %% not monotonic
-    		It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+    		\linelabel{line:non-monotonic}It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
 We saw above that not sufficiently coarse-grained variables have low values of NTIC.
@@
 
-    		Importantly, NTIC processes encode environmental information in its state.
-This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.
-This implication fits well with some theories of consciousness (for example, world simulation metaphor ~\citep{revonsuo2006inner}).
+    		\linelabel{line:encode}Importantly, NTIC processes internalise the environmental dynamics in its states \citep[also see P.~4][]{BERTSCHINGER.2006}.
+This suggests that a NTIC process can be considered as a process that models the environmental dynamics.This implication fits well with some theories of consciousness (for example, world simulation metaphor ~\citep{revonsuo2006inner}).
 Note that \ac{OurTheory} doesn't assume that generative models are necessary for consciousness.
@@
         		\begin{figure}[H]
-        			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
+        			\incluphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
         			\caption{
@@
         		The same principle can be applied to interpret blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedural memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes.
-        		\linelabel{line:r2q6}Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements when their visual experiences is degraded or missing (however, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}).
+        		\linelabel{line:r2q6}Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience (however, in some cases, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}).
 We argue that action outputs of blindsight can be directly guided by sensory inputs through stimulus-response maps.
@@
 The exclusion axiom should be applied over elements, space, time, and scales \citep{oizumi2014phenomenology, hoel2016can}.
-Different from IIT, \ac{OurTheory} allows multiple consciousnesses coexist across different levels of coarse-graining within a system if they are informationally closed from each other.
+\linelabel{line:multi-consciousness}Different from IIT, \ac{OurTheory} allows multiple consciousnesses coexist across different levels of coarse-graining within a system if they are informationally closed from each other.
 The two distinctive predictions decisively pinpoint the core concepts of the two theories.
@@
 
-        \linelabel{line:dream}
+        \linelabel{line:dream}Explaining conscious experience during dreaming is always a challenge to all the theories of consciousness.
+ICT currently does not have a certain answer to dreaming.
+However, we want to emphasise that not all the processes in the neural system are NTIC.
+This is trivial since some processes are evidently not informationally closed.
+They mainly passively react to sensory inputs or other processes in the neural system.
+To the conscious (NTIC) process, the rest of the neural system is part of the environment, and undoubtedly retains some degree of activity during sleep and dreaming.
+We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
+the other parts of the neural system.
+However, at the current stage, this is mere speculation.
+Searching for the NTIC process(es) during dreaming is a crucial step to extend the scope of ICT in future research.
 

### 2020-03-17 ICT_Frontiers_rev202001_reply.tex
start sharing

@@
     \noindent
-    \textbf{line #1:}
+    \textbf{Line #1:}
     \newline
@@
 % \addnew{line number}{text}
-\newcommand{\addnew}[2]{\blockcquote{}{Line #1:~\newline\textit{"#2"}}
+\newcommand{\addnew}[2]{\blockcquote{}{\textbf{Line #1:}~\newline\textit{"#2"}}
 }
@@
     	\begin{ans}
+			We do not impose the exclusion criterion in ICT.
+Instead, the concept of informational closure already involved the notion of individuality and was used to identify the system-environment distinction \citep{BERTSCHINGER.2006} and level identification \citep{PFANTE.2014} in system theory (however not complete, please see our discussion at Line \lineref{line:individuality}).
+In \cite{BERTSCHINGER.2006},
 
+			It is true that if we assume a process $Y$ is NITC with respect to $E$.
+Every subset of $Y$ can have different degrees of NTIC with respect to $E$ as well.
+However, it is important to note that the subsets are not "other consciousnesses".
+Rather, they are subspaces of this conscious process $Y$.
+
+			\toWrite{I this this is still bad}
+
+%			\textit{If we sample a subset of elements, if its closedness is lower than 
+%			Consider a simplified case, a process $Y$ is NITC with respect to $E$. 
+%			For Any subset of 
+%			A partition of $Y$ is a set $P_y$ which divides $Y$ into two subsets $P_y=\{Y_1, Y_2\}$. }    		    		    		
     	\end{ans}
@@
     	\begin{ans}
-    		\toWrite{Add something here}
-    		We have added a paragraph at Line \lineref{line:dream}
+	    	We want to emphasise that not all the processes in the neural system are NTIC processes.
+This is evident since some processes in the neural system are not informationally closed.
+They only passively react to sensory inputs or other processes of the neural system.
+
+	    	To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment.
+This notion is shortly indicated at line \lineref{line:neu-env} in our original manuscript.
+There is no doubt that these processes are still active during sleep and dreaming.
+We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e.
+other parts of the neural system.
+However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our manuscript.
+However, we thank the reviewer for bringing up this important question.
+We believe that this is still worth mentioning.
+We have added a short paragraph as follows:
+
+			\addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to all the theories of consciousness.
+ICT currently does not have a certain answer to dreaming.
+However, we want to emphasise that not all the processes in the neural system are NTIC.
+This is trivial since some processes are evidently not informationally closed.
+They mainly passively react to sensory inputs or other processes in the neural system.
+To the conscious (NTIC) process, the rest of the neural system is part of the environment, and undoubtedly retains some degree of activity during sleep and dreaming.
+We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
+the other parts of the neural system.
+However, at the current stage, this is mere speculation.
+Searching for the NTIC process(es) during dreaming is a crucial step to extend the scope of ICT in future research.}
+
+	    	Finally, we believe that this is also an
+	    	empirical question that can and should be tested in future studies.
     	\end{ans}
@@
 
-    			\item Thank the reviewer for this suggestion. We have modified our manuscript and cited  the reference at Line \lineref{line:lack-theory}. \toWrite{Change main text}
+    			\item Thank the reviewer for the reminder. We have modified our manuscript and cited the relevant references. 
+    			\revise{\lineref{line:lack-theory}}
+    			{We currently lack a theory to identify the scale which conscious processes correspond to.}
+    			{We currently have only few theories (e.g., Integrated Information Theory \citep{hoel2016can} and Geometric Theory of consciousness \citep{fekete2011towards,fekete2012lack}) to identify the scale which conscious processes correspond to (please also see the discussion in \cite{fekete2016system}).}
 
-    			\item We fully agree with the reviewer's comment. 
-    			In fact, in our theory, we do not partition states of processes into activation and relation.
-For example, both activation and structure states of a neural network should be considered.
-After all, they can be parameterised as the parameters of processes.
-The only difference is the temporal scales of parameter changes.
+    			\item We agree with the reviewer's comment. 
+    			In fact, in ICT, we do not differentiate states of processes between activation and relation.
+Take neural networks as an example, activation and structure states of a neural network should be both considered.
+After all, they are all just parameters of the process of the neural network.
+The only difference between the two groups of the parameters is the temporal scales of the parameter changes.
 States of activation may have more rapid dynamics than states of relation.
-In ICT, this difference is crucially related to the temporal coarse-graining which we did not address in this article but can be easily generalised in future versions of ICT.
+In ICT, this is crucially related to the coarse-graining at the temporal domain which we did not address in this article but can be easily generalised in the future versions of ICT.
 
-    			\toWrite{To write something in the main text?}
+    			\todo{Do we need to write something in the main text?}
 
@@
     		\begin{enumerate}
-    			\item In this article, the definition of coarse-graining is our "Definition 1" (line: \lineref{line:r2q1-1}) which is simply a function mapping a stochastic process $X$ with state space $\mathcal{X}$ to a stochastic process $Y$ with state space $\mathcal{Y}$.
-    			We do not specify any specific types of coarse-graining.
-    			\toWrite{Instead, our hypothesis states that any process which coarse-graining which}
+    			\item In this article, the definition of coarse-graining is our "Definition 1" (line: \lineref{line:r2q1-1}).
+Coarse-graining is simply a function which maps a stochastic process $X$ with state space $\mathcal{X}$ to a stochastic process $Y$ with state space $\mathcal{Y}$.
+As we explained in Footnote 2, functions in the mathematical sense used here are always either one-to-one or many-to-one.
+We do not constrain ICT to be applied to any specific classes of coarse-graining.
+    			Thank the reviewer for proposing the question about the relationship between NTIC and scale of coarse-graining.
+We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining.
+Some coarse-grainings lead to higher NTICs for macroscopic than microscopic processes.
+However, we are just starting the research on this relationship, and have not yet had a systematic understanding of it.
+This work may involve the technique of partial information decomposition and related research fields.
+    			We agree that our original claim about existing a intermediate maxima in NTIC was too strong.
+
+    			We hope to address this question in future research.
 
@@
     			(However, due to IC, conscious processes are not able to know the existence of each other. 
-					\todo{Discuss this}
-
+    			\revise{\lineref{line:non-monotonic}}
+    			{
+    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+We saw above that not sufficiently coarse-grained variables have low values of NTIC.
+On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC.
+For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.
+Therefore, only processes at a certain level of coarse-graining in the neural system can form a high degree of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
+ICT indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
+    			}
+    			{
+    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+Insufficiently coarse-grained variables could lead to lower values of NTICs at micro than macroscopic processes.
+On the other hand, overly coarse-grained macroscopic variables also result in low values of NTIC.
+For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.
+Therefore, processes at certain levels of coarse-graining may have higher values of NTIC than other levels (Fig.~\ref{fig:LevelOfConsciousness}).
+ICT suggests that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
+    			}										
     			\item \toWrite{TBD}
@@
     	\begin{ans}
-			Here, we followed a common setup of coarse-graining (e.g.
-\toWrite{cite here}), which does not take time $Y_t=f_Y(X_t)$ (in Definition 1).
+			We followed a common setting of coarse-graining (e.g.
+\cite{PFANTE.2014}) which does not and should not take time $Y_t=f_Y(X_t)$ (in Definition 1).
+Coarse-graining is merely a function which maps microstates of a system to macrostates, and the microstates and the macrostates are simply different level of descriptions of a system.
+			Following this setting, the definition of information closure (flow) $J_{t}(X \rightarrow Y )$ can also be applied in the sense of coarse-graining.
+
+			We understand that this may lead to confusion for our readers. We have added the following sentence to make this point explicit.     		
+			\addnew{\lineref{line:IC2CG}}{Note that we applied the same definition of information closure (Eq.\ref{eq:InformationFlow}) to processes at different coarse-grained levels \citep{{PFANTE.2014}}.}
+%			Here, we followed a common setup of coarse-graining (e.g.
+\cite{PFANTE.2014}) which does not take time $Y_t=f_Y(X_t)$ (in Definition 1).
 In this setup, coarse-graining is unidirectional ad does not involve interaction between scales.
@@
 \\
-			In our hypothesis, Y is IC with respect to the microstate of the universe, X.
+%			In our hypothesis, Y is IC with respect to the microstate of the universe, X.
 This is critical in the hypothesis because Y is IC with respect to X, implying that Y is also IC with respect to its intermediate level S and its environment E in Fig.
@@
     		Thank the reviewer for this mindful comment. 
-    		Our description indeed is not clear enough. The environmental information here about not only states but also state transitions. 
-    		This is because high NTIC implies high mutual information between a process and its environment $I(Y_{t+1};E_t)$ (Eq.
-\ref{eq:nticObjective2}).
-Therefore, the dynamics of the process $Y$ needs to covary with the dynamics of its environment $E$.
-Here, we consider 'simulation' is a more precise expression than 'encoding'.
-    		The notion of simulation is the same as the 'Modeling' case on Page 4 in Bertschinger et al. , 2006: \\
+    		Our wording indeed is not clear. The notion of simulation is the same as the 'Modeling' case on Page 4 in \cite{BERTSCHINGER.2006}: 
+    		\begin{quote}
 		    	\textit{"B2)~Modeling: The system reaches synchronization and internalizes the correlations observed in the environment by building up own structures."}    	
-    		\\ \toWrite{add something in the main text}
+    		\end{quote}
+
+    		To avoid the confusion We have revised the following sentence, changed "simulation" to "modeling", and added the reference.
+    		\revise{\lineref{line:encode}}
+    		{
+    			Importantly, NTIC processes encode environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics. }
+    		{
+    			Importantly, NTIC processes internalise the environmental dynamics in its states \citep[also see P.~4][]{BERTSCHINGER.2006}.
+This suggests that a NTIC process can be considered as a process that models the environmental dynamics.
+    		}
     	\end{ans}
@@
    			Thank the reviewer for the clarification. 
-   			Yes, we specifically address the visual character of their experience.
-   			We have changed our sentence as follows:
+   			Yes, we specifically wanted to address the visual character of their experience. We agree that some patients still preserve some forms of conscious experience. 
+   			We have changed our sentence and cited the relevant references as follows:
    			\revise{\lineref{line:r2q6}}
@@
    			{
-   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements when their visual experiences is degraded or missing (however, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}).
+   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience (however, in some cases, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}).
    			}
@@
  		\begin{ans}
- 			Thank the reviewer for this valuable comment. 
+			Thank the reviewer for proposing this interesting and valuable comment. \\
+			We can consider a simple case in which a feedforward neural network $Y$ consists of three layers, $Y^0$, $Y^1$, and $Y^2$. 
+			$Y^0$ receives sensory input from the environment $E$.
+Each layer $Y^i_t$ passes information to the next layer $Y^{i+1}_{t+1}$ with a constant time cost $\Delta t$ as showed in the following figure.
+
  			\begin{figure}[H]
  				\centering
- 				\includegraphics[width=\textwidth]{WritingMaterials/Fig_ScaleProblemOfConsciousness/ScaleProblemOfConsciousness.pdf}
- 				\caption{The scale problem of consciousness: Human conscious experience does not reflect information from every scale.
-Only information at a certain coarse-grained scale in the neural system is reflected in consciousness.}
- 				\label{fig:scaleproblem}
+ 				\includegraphics[width=\textwidth]{WritingMaterials/Fig_rev1_feedforward/Fig_rev1_feedforward} 				
+ 				\label{fig:rev1_feedforward}
  			\end{figure}
 
- 			Indeed, 
- 			\\
- 			\toWrite{This is really a good question.}
- 			\todo{Indeed, if information is just copied to the process, it will still be NTIC. Feedforward is just a way to copy the information}
+			Because $Y^0_t$ determines $Y^1_{t+1}$ and $Y^1_t$ determines $Y^2_{t+1}$, it is true that the mutual information $I(Y_t; Y_{t+1}) \geq 0$.
+However, $E_t$ only influences $Y^0_{t+1}$ at time $t+1$.
+Therefore
+			\begin{equation*}
+				\begin{aligned}
+					& I(Y_t; Y_{t+1}|E_t) = I(Y_t; Y_{t+1}) & \text{and} \\
+					& NTIC_t(E\rightarrow Y)=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}) =0  { }
+				\end{aligned}
+			\end{equation*}
+
+			Therefore, a feedforward network passively driven by input signals should have zero NTIC even though when time step (temporal coarse-graining) is small. 
+			\todo{I don't think I answer this question well. Do we need to add anything in the main text?}
+
  		\end{ans}
@@
 However, because the relevant discussion is clearly outside the scope of this article, we prefer not to discuss the hard problem here.
-n
 
-    		It is important to note that we reckon only part of the neural system is involved in the NTIC process(es).
-This is due to the fact that some parts of the neural system are evidently not informationally closed.
-They only passively react to sensory inputs or other parts of the neural system.
-    		To the NTIC process(es), the rest of the neural system is considered as the environment. This notion is shortly indicated at line \lineref{line:neu-env}.
-    		We speculate that, during dreaming, the neural system can still form the NTIC process(es) with respect to other parts of the neural system which we know they maintain high activities.
+			We want to emphasise that not all the processes in the neural system are NTIC processes.
+This is evident since some processes in the neural system are not informationally closed.
+They only passively react to sensory inputs or other processes of the neural system.
+
+    		To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment.
+This notion is shortly indicated at line \lineref{line:neu-env} in the original manuscript.
+There is no doubt that these processes are still active during sleep and dreaming.
+We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e.
+other parts of the neural system.
 The same idea can be also applied to phenomena like Eigengrau.
 However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our last version of the manuscript.
-However, thank the reviewer for bringing up this question.
-We believe that it is still worth to mention issues about dreaming.
+However, we thank the reviewer for bringing up this important question.
+We believe that this is still worth mentioning.
 We have added a short paragraph as follows:
 
-    		\toWrite{add something in the main text at Line \lineref{line:dream}}
+    		\addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to all the theories of consciousness.
+ICT currently does not have a certain answer to dreaming.
+However, we want to emphasise that not all the processes in the neural system are NTIC.
+This is trivial since some processes are evidently not informationally closed.
+They mainly passively react to sensory inputs or other processes in the neural system.
+To the conscious (NTIC) process, the rest of the neural system is part of the environment, and undoubtedly retains some degree of activity during sleep and dreaming.
+We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
+the other parts of the neural system.
+However, at the current stage, this is mere speculation.
+Searching for the NTIC process(es) during dreaming is a crucial step to extend the scope of ICT in future research.}
 
-    		Finally, we believe that this is also a clear empirical question that can be tested in future studies. 
+    		Finally, we believe that this is also an
+    		empirical question that can and should be tested in future studies. 
     	\end{ans}

### 2020-03-17 ICT_Frontiers_rev202001_reply.tex
update

@@
 see Hoffman's interface theory); and some of the assertions the authors make re simulation seem unfounded anyways.
-But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)\todo{I don't understand this question well}
+But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)
 

### 2020-03-17 ICT_Frontiers_rev202001_reply.tex
update

@@
     	\begin{ans}
-    		\begin{enumerate}
-    			\item In this article, the definition of coarse-graining is our "Definition 1" (line: \lineref{line:r2q1-1}).
+    		Thank the reviewer for the critical comments. We have replied these comments in details in the following Q\&A. 
+%    		\begin{enumerate}
+%    			\item In this article, the definition of coarse-graining is our "Definition 1" (line: \lineref{line:r2q1-1}).
 Coarse-graining is simply a function which maps a stochastic process $X$ with state space $\mathcal{X}$ to a stochastic process $Y$ with state space $\mathcal{Y}$.
@@
 We do not constrain ICT to be applied to any specific classes of coarse-graining.
-    			Thank the reviewer for proposing the question about the relationship between NTIC and scale of coarse-graining.
+%    			Thank the reviewer for proposing the question about the relationship between NTIC and scale of coarse-graining.
 We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining.
@@
 This work may involve the technique of partial information decomposition and related research fields.
-    			We agree that our original claim about existing a intermediate maxima in NTIC was too strong.
-
-    			We hope to address this question in future research.
-
-    			We emphasise the non-monotonic relation between the scales of coarse-graining and the degrees of NTIC.
+%    			We agree that our original claim about existing a intermediate maxima in NTIC was too strong. 
+%    			
+%    			
+%    			We hope to address this question in future research. 
+%    			
+%    			
+%    			
+%    			We emphasise the non-monotonic relation between the scales of coarse-graining and the degrees of NTIC.
 However, we do not exclude the possibility that there exist multiple NTIC picks across scales of coarse-graining of a process.
-    			This implies that we do not exclude the possibility that there exist multiple high conscious processes at different scales. 
-    			(However, due to IC, conscious processes are not able to know the existence of each other. 
-    			\revise{\lineref{line:non-monotonic}}
-    			{
-    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+%    			This implies that we do not exclude the possibility that there exist multiple high conscious processes at different scales. 
+%    			(However, due to IC, conscious processes are not able to know the existence of each other. 
+%    			\revise{\lineref{line:non-monotonic}}
+%    			{
+%    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
 We saw above that not sufficiently coarse-grained variables have low values of NTIC.
@@
 ICT indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
-    			}
-    			{
-    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+%    			}
+%    			{
+%    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
 Insufficiently coarse-grained variables could lead to lower values of NTICs at micro than macroscopic processes.
@@
 ICT suggests that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
-    			}										
-    			\item \toWrite{TBD}
-%    			\item \toWrite{After replying the first reviewer}
-    		\end{enumerate}
+%    			}										
+%    			\item 
+%    			\item
+%    		\end{enumerate}
 
@@
     	\begin{ans}
-			We followed a common setting of coarse-graining (e.g.
+			We followed the common setting of coarse-graining (e.g.
 \cite{PFANTE.2014}) which does not and should not take time $Y_t=f_Y(X_t)$ (in Definition 1).

### 2020-03-18 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
 2006 and our Section 2 (at Line \lineref{line:r1q1a}), $Y_{t+1}$ is determined by both $Y_t$ and $E_t$.
-Simply increasing $I(Y_{t+1}; E_t)$ without closedness (e.g, copy the information in sensory signals to the process such as the case in the video camera example), the transfer entropy term $J_t(E -> Y)$ should increase at the same rate and cancel out the increment of $I(Y_{t+1}; E_t)$ resulting low NTIC.
+Simply increasing $I(Y_{t+1}; E_t)$ without closedness (e.g, copy the information in sensory signals to the process such as the case in the video camera example), the transfer entropy term $J_t(E -> Y)$ should increase at the same rate and cancel out the increment of $I(Y_{t+1}; E_t)$ resulting in low NTIC.
 Namely, keeping high closedness, i.e.
@@
     		\noindent
-    		b) Thank the reviewer for this outstanding question.
+    		b) We thank the reviewer for this question.
 We entirely agree that state-dependent measurements are essential to describe the dynamics of conscious experience.
@@
 	    	\addnew{\lineref{line:r1-state-dep}}{
-	    		In this article, we do not use a state-dependent formulation of NTIC in the current version of ICT.
+	    		In this article, we do not use a state-dependent formulation of NTIC.
 However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.
@@
         \begin{ans}        	
-            Because X is the micro-level of the universe, any coarse-graining of X (including E and S) should have equal or less information about Y than X, i.e.
+            Because X is the micro-level of the universe, the information transfer from any coarse-graining (including E and S) of X  to Y must be lower than that from X to Y, i.e.
 $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$.
-Therefoe, Y is informationally closed with respect to X implying that Y is also informationally closed with respect to S, E, and all other coarse-grainings of X.
-As explained in Question 1a, it is not required for NTIC processes to be completely closed.
-Therefore, the closedness of Y with respect to X $I(Y_{t+1}; X_t|Y_t)$ serves as the lower bound of the closedness of Y to any other processes.
-            For this first exposure of our theory, we did not discuss NTIC in the context of the temporal coarse-graining.
-It is true that we certainly encounter some degree on unpredictable sensory inputs from the environment from time to time.
-Therefore, NTIC should be higher for finer temporal scales than for coarser temporal scales.
-We also speculate that the temporal coarse-graining is related to the speed of "stream of consciousness" and will address this issue in our future studies.
+Therefore, it is crucial to have an underlying X with respect to Y because Y is informationally closed with respect to X implies that Y is also informationally closed with respect to S, E, and all other coarse-grainings of X.
+However, as explained in Question 1a, it is not required for NTIC processes to be completely closed.
+The information transfer from X to Y $I(Y_{t+1}; X_t|Y_t)$ (if non-zero) serves as the upper bound of the information transfer from any other process to Y.
+So unpredictable sensory inputs will contribute to a positive information transfer.
+For high NTIC systems however this transfer must be less than the mutual information between the sensory inputs and the next system state.
         \end{ans}
@@
 			We do not impose the exclusion criterion in ICT.
-Instead, the concept of informational closure already involved the notion of individuality and was used to identify the system-environment distinction \citep{BERTSCHINGER.2006} and level identification \citep{PFANTE.2014} in system theory (however not complete, please see our discussion at Line \lineref{line:individuality}).
-In \cite{BERTSCHINGER.2006},
+That human consciousness constitutes a maximum is a conjecture at the moment.
+Humans are of course very good at predicting their future experiences and (apart from multiple humans together) we are not aware of systems that are better.
+This is the only reason why we think human consciousness constitutes a maximum.
+We accept that there can be many other overlapping conscious systems.
+Concerning multiple possible partitions, \citet{krakauer2014information} propose an algorithm to add and remove variables in order to find a maximum.
+This could be used to find a maximum and something like a boundary of the maximum.
+Maxima are of course interesting but we don't see why they should exclude anything.
+Instead, the concept of informational closure already involves the notion of individuality and was used to identify the system-environment distinction \citep{BERTSCHINGER.2006} and level identification \citep{PFANTE.2014} in systems theory (however not completely, please see our discussion at Line \lineref{line:individuality}).
 
@@
         \end{question}
+
+        \begin{ans}
+            \toWrite{Thinking to combine the answer to this question with other answers. But not sure yet. Need to think about it. We can skip this one for now.}
+        \end{ans}
 
@@
 
-    			\item Thank the reviewer for the reminder. We have modified our manuscript and cited the relevant references. 
+    			\item We thank the reviewer for the reminder. We have modified our manuscript and cited the relevant references. 
     			\revise{\lineref{line:lack-theory}}
@@
 States of activation may have more rapid dynamics than states of relation.
-In ICT, this is crucially related to the coarse-graining at the temporal domain which we did not address in this article but can be easily generalised in the future versions of ICT.
+In ICT, this is crucially related to the coarse-graining at the temporal domain which we did not address in this article but can be generalised in the future versions of ICT.
 
@@
     	\begin{ans}
-    		Thank the reviewer for the critical comments. We have replied these comments in details in the following Q\&A. 
+    		We thank the reviewer for the critical comments. We have replied these comments in details in the following Q\&A. 
 %    		\begin{enumerate}
@@
 We do not constrain ICT to be applied to any specific classes of coarse-graining.
-%    			Thank the reviewer for proposing the question about the relationship between NTIC and scale of coarse-graining.
+%    			We thank the reviewer for proposing the question about the relationship between NTIC and scale of coarse-graining.
 We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining.
@@
     	\begin{question}
-			On line 182, defining C-processes as cases where ‘Y is informationally closed to X’.
+			On line 182, defining C-processes as cases where 'Y is informationally closed to X'.
 This is now information closure in the sense of coarse-graining, but no such thing has been defined yet?
@@
     	\begin{question}            
-    		On line 241: “..
-not sufficiently coarse-grained variables have low values of NTIC”, this is phrased as though it is necessarily true (and also that “we saw above”, though I do not see above where this is justified), but is it?
+    		On line 241: '..
+not sufficiently coarse-grained variables have low values of NTIC', this is phrased as though it is necessarily true (and also that 'we saw above', though I do not see above where this is justified), but is it?
 
-    		At the very finest grain, wouldn’t even all the most ‘stochastic’ dynamics of a system be accounted for by prior states of the system, or by the environment?
-Why wouldn’t we assume that NTIC *only decreases* as the system is coarse-grained (as number of elements/states is decreased), for similar reasons as it must be zero at a 1-element 1-state system as the authors note?
-This seems an important point to be very clear on…
+    		At the very finest grain, wouldn't even all the most 'stochastic' dynamics of a system be accounted for by prior states of the system, or by the environment?
+Why wouldn't we assume that NTIC *only decreases* as the system is coarse-grained (as number of elements/states is decreased), for similar reasons as it must be zero at a 1-element 1-state system as the authors note?
+This seems an important point to be very clear on\dots
     	\end{question}
@@
     	\begin{ans}
-    		\toWrite{The reviewer is right?}
-    		Thank the reviewer for this critical comment.
+    		\todo{I think I made a big mistake in the manuscript.
+When I wrote this part I only considered IC as a function of scales of coarse-graining.
+But I just realised NTIC is totally a different story that I didn't think about thoroughly.
+I may need to re-write this paragraph}
+
+    		We thank the reviewer for proposing the question about the relationship between NTIC and scale of coarse-graining.
+We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining.
+Some coarse-grainings lead to higher NTICs for macroscopic than microscopic processes.
+However, we are just starting the research on this relationship, and have not yet had a systematic understanding of it.
+This work may involve the technique of partial information decomposition and related research fields.
+    		We agree that our original claim about existing a intermediate maxima in NTIC was too strong and have revised the paragraph as follows: 
+            % We emphasise the non-monotonic relation between the scales of coarse-graining and the degrees of NTIC.
+However, we do not exclude the possibility that there exist multiple NTIC picks across scales of coarse-graining of a process.
+This implies that we do not exclude the possibility that there exist multiple high conscious processes at different scales.
+(However, due to IC, conscious processes are not able to know the existence of each other.
+			\revise{\lineref{line:non-monotonic}}
+			{
+				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+We saw above that not sufficiently coarse-grained variables have low values of NTIC.
+On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC.
+For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.
+Therefore, only processes at a certain level of coarse-graining in the neural system can form a high degree of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
+ICT indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
+			}
+			{
+				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+Insufficiently coarse-grained variables could lead to lower values of NTICs at micro than macroscopic processes.
+On the other hand, overly coarse-grained macroscopic variables also result in low values of NTIC.
+For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.
+Therefore, processes at certain levels of coarse-graining may have higher values of NTIC than other levels (Fig.~\ref{fig:LevelOfConsciousness}).
+ICT suggests that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
+			}	    		
+            % 		We thank the reviewer for this critical comment.
 It is true that NTIC a monotonic function of scales of coarse-graining.
@@
 We will systematically address NTIC and functions of coarse-graining in our following studies.
-    		Further more, in our current analysis, it seems that this is also related to informational synergy and redundancy. We aim for presenting the core concept of ICT in this article.
+Further more, in our current analysis, it seems that this is also related to informational synergy and redundancy.
+We aim for presenting the core concept of ICT in this article.
 The reviewer's critical question is on our list of future work.
-    		\toWrite{Need to change the text a lot!!}
     	\end{ans}
@@
     	\begin{question}
-    		on line 263: “NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.“
+    		on line 263: 'NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.'
 
@@
 
-    		The ‘simulation’ notion is brought up again in section 5.2 (line 344), citing Bertschinger et al, though I do not find the idea in that paper..
-I think authors need to be clearer on what they mean by ‘simulation’ to make this point.
+    		The 'simulation' notion is brought up again in section 5.2 (line 344), citing Bertschinger et al, though I do not find the idea in that paper..
+I think authors need to be clearer on what they mean by 'simulation' to make this point.
     	\end{question}
@@
     	\begin{ans}
-    		Thank the reviewer for this mindful comment. 
+    		We thank the reviewer for this mindful comment. 
     		Our wording indeed is not clear. The notion of simulation is the same as the 'Modeling' case on Page 4 in \cite{BERTSCHINGER.2006}: 
@@
    	\begin{question}
-			line 306: “Blindsight patients… make above chancel-level visual judgments without having any conscious perception about visual stimuli” I am not sure this characterization of blindsight is correct, it may be a matter of the phrasing.
-It could be - or probably is - the case that ‘blindsight’ patients always have some conscious experience of what drives their correct responses, but that the “visual character” of these experiences is degraded or missing.
+			line 306: 'Blindsight patients\dots make above chancel-level visual judgments without having any conscious perception about visual stimuli' I am not sure this characterization of blindsight is correct, it may be a matter of the phrasing.
+It could be - or probably is - the case that 'blindsight' patients always have some conscious experience of what drives their correct responses, but that the 'visual character' of these experiences is degraded or missing.
 			(Overgaard, Experimental Brain Research 2011)
@@
    		\begin{ans}
-   			Thank the reviewer for the clarification. 
+   			We thank the reviewer for the clarification. 
    			Yes, we specifically wanted to address the visual character of their experience. We agree that some patients still preserve some forms of conscious experience. 
@@
  		\begin{ans}
-			Thank the reviewer for proposing this interesting and valuable comment. \\
+			We thank the reviewer for this interesting and valuable comment. \\
 			We can consider a simple case in which a feedforward neural network $Y$ consists of three layers, $Y^0$, $Y^1$, and $Y^2$. 
@@
     	\begin{ans}
-    		Thank the reviewer for this considerate comment.
+    		We thank the reviewer for this considerate comment.
 The reviewer is correct.
@@
         \begin{question}                                                                   
-            Line 540: the theory doesn’t really seem to intend to solve the hard problem(s) at all, much less “completely solve”.            
+            Line 540: the theory doesn't really seem to intend to solve the hard problem(s) at all, much less 'completely solve'.            
             I was expecting the problem of dreaming to come up in the last section (maybe along with SMC for which it is a serious problem).
@@
 Instead of solving the hard problem of consciousness, we more look forward to mathematically determining whether the hard problem can be solved or not by information theory.
-However, because the relevant discussion is clearly outside the scope of this article, we prefer not to discuss the hard problem here.
+However, because the relevant discussion is outside the scope of this article, we prefer not to discuss the hard problem here.
 
@@
 However, we want to emphasise that not all the processes in the neural system are NTIC.
-This is trivial since some processes are evidently not informationally closed.
+This is evident since some processes are not informationally closed.
 They mainly passively react to sensory inputs or other processes in the neural system.

### 2020-03-25 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
             Thank you for your attention to our manuscript and your interesting question. \\
+            If we understand correctly, molecular recognition refers to specific types of interactions among molecules to form molecular complexes.
 There is no question that molecular complexes are coarse-grainings of molecules via molecular recognition.
@@
             Hypothesis and Implication 3: Why is it crucial that there is an underlying X with respect to which Y is a C-process?     
+        \end{question}
+
+        \begin{ans}        	
+            It is crucial to have an underlying X with respect to Y because this assumption can solve the scale problem of consciousness.
+It ensures that the information transfer from all coarse-grainings of X to Y vanishes.
+Therefore, human conscious experiences do not involve information from other scales of coarse-graining.
+
+            Because X is the micro-level of the universe, the information transfer from any coarse-graining (including E and S) of X  to Y must be lower than that from X to Y, i.e.
+$I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$.
+
+            So that Y is informationally closed with respect to X implies that Y is also informationally closed with respect to S, E, and all other coarse-grainings of X.             
+        \end{ans}
+
+        \begin{question}
             Does Y being informationally closed with respect to X imply that Y is also informationally closed with respect to E, i.e.
@@
         \begin{ans}
-            Because X is the micro-level of the universe, the information transfer from any coarse-graining (including E and S) of X  to Y must be lower than that from X to Y, i.e.
-$I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$.
-Therefore, it is crucial to have an underlying X with respect to Y because Y is informationally closed with respect to X implies that Y is also informationally closed with respect to S, E, and all other coarse-grainings of X.
-However, as explained in Question 1a, it is not required for NTIC processes to be completely closed.
+            Yes. Y being informationally closed with respect to X implies that Y is also informationally closed with respect to E, i.e. $J_t(E-Y) = 0$.
+            As explained in Question 1a, it is not required for NTIC processes to be completely closed.
 The information transfer from X to Y $I(Y_{t+1}; X_t|Y_t)$ (if non-zero) serves as the upper bound of the information transfer from any other process to Y.
@@
         \begin{question}
+            \todo{*****}
             Feedback and memory: p.
@@
             \toWrite{Thinking to combine the answer to this question with other answers. But not sure yet. Need to think about it. We can skip this one for now.}
+
         \end{ans}
@@
 
+			\todo{Add the definition to the conttext of coarse-graining}
+
 			We understand that this may lead to confusion for our readers. We have added the following sentence to make this point explicit.     		
@@
     	\begin{question}            
+    	\todo{*****}
     		On line 241: '..
@@
     	\begin{question}
+    	\todo{Camera thing...}
             on Line 316: On the issue of a feedforward network, the current state of a feedforward network with more than one layer is certainly driven by its own past states!

### 2020-03-30 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
 Therefore, a conscious process does not have to be completely closed.
-However, a high degree of closedness is crucial to have a high level of consciousness.\\
+However, a high degree of closedness is crucial to have a high level of consciousness.
+(Regarding to the video camera example, please see more discussion in our reply to your Q6.) \\
 
@@
 Therefore, human conscious experiences do not involve information from other scales of coarse-graining.
-
             Because X is the micro-level of the universe, the information transfer from any coarse-graining (including E and S) of X  to Y must be lower than that from X to Y, i.e.
 $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$.
-
 So that Y is informationally closed with respect to X implies that Y is also informationally closed with respect to S, E, and all other coarse-grainings of X.
@@
         \begin{ans}
-            Yes. Y being informationally closed with respect to X implies that Y is also informationally closed with respect to E, i.e. $J_t(E-Y) = 0$.
+            Yes. Y being informationally closed with respect to X implies that Y is also informationally closed with respect to E, i.e. $J_t(E-Y) = 0$ (Please see our reply to Q2).\\
             As explained in Question 1a, it is not required for NTIC processes to be completely closed.
@@
     	\begin{ans}
-			We do not impose the exclusion criterion in ICT.
-That human consciousness constitutes a maximum is a conjecture at the moment.
+            We thank the reviewer for this critical question. We do not impose the exclusion criterion in ICT. This is a critical difference between IIT and ICT. \\
+            % The exclusion criterion is based on the assumption that individual entities (e,g, consciousnesses) should share no subset with any other entities.
+Namely, within the boundary of an individual, we should not find any subset also belonging to other individuals.
+\\
+            A key feature of ICT is that, instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of system-environment separation and a boundary of a system \citep{BERTSCHINGER.2006}.
+For example, \citet{krakauer2014information} proposed an algorithm to add and remove variables in order to find the boundary.
+\\
+            It is true that every subset of a system can be computed and can have a positive value of NTIC.
+However, following the notion of informational closure, if a subset is not informationally closed, the subset is considered as a part of the system.
+            ICT applies the same notion to consciousness.
+A subprocess (partition) of a conscious (NTIC) process can have a positive value of NTIC, and therefore, is conscious.
+However, the subprocess is not "another conscious process".
+Instead, it is considered as a subspace of the consciousness.
+Namely, the information contributed from the subprocess corresponds to a part of the whole conscious experience.
+\\
+            This is also why ICT allowed the existence of multiple consciousnesses across the scale of coarse-graining.
+Because conscious processes are informationally closed from each other across the scale of coarse-graining, they are not able to know the existence of other consciousnesses within the same system (information flow from other processes is zero).
+This is in line with using informational closure in level identification \citep{PFANTE.2014} .
+\\
+            Therefore, ICT without exclusion criterion can parsimoniously explain the individuality of consciousness within and across the scale of coarse-graining.
+            \todo{Maybe add something in the manuscript}
+% 			We do not impose the exclusion criterion in ICT. Instead, the concept of informational closure already involves the notion of identifying the boundary of a system.
+
+% 			 system-environment distinction \citep{BERTSCHINGER.2006} and level identification \citep{PFANTE.2014}
+
+% 			That human consciousness constitutes a maximum is a conjecture at the moment.
 Humans are of course very good at predicting their future experiences and (apart from multiple humans together) we are not aware of systems that are better.
@@
 
-			It is true that if we assume a process $Y$ is NITC with respect to $E$.
+% 			It is true that if we assume a process $Y$ is NITC with respect to $E$.
 Every subset of $Y$ can have different degrees of NTIC with respect to $E$ as well.
@@
 
-			\toWrite{I this this is still bad}
+% 			\toWrite{I this this is still bad}
 

### 2020-04-02 ICT_Frontiers_rev202001.tex
Updates from Overleaf
Update from local

@@
 	\maketitle
-
-	\section*{Word Count:}
-	Total Words :7115\\
-    Headers :27\\
-    Math Inline :112\\
-    Math Display :12\\
-
 	\tableofcontents
@@
 
-        \linelabel{line:IC2CG}Note that we applied the same definition of information closure (Eq.\ref{eq:InformationFlow}) to processes at different coarse-grained levels \citep{{PFANTE.2014}}.\\
-
-        With the two definitions we can state the main hypothesis of \ac{OurTheory}:
+        \linelabel{line:IC2CG}
+        With the two definitions we can state the main hypothesis of \ac{OurTheory}
+        \footnote{Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) and informational closure (Eq.~\ref{eq:informationflow2}) to the system-environment dependency (e.g.
+$J_{t}(E \rightarrow Y )=0$) and the micro-macro level dependency (e.g.
+$J_{t}(X \rightarrow Y )=0$), even though the Bayesian graphs are different between the two scenarios.
+This follows the common settings in previous studies (e.g.
+\cite{BERTSCHINGER.2006, PFANTE.2014}).}:
 
@@
         		\begin{figure}[H]
-        			\incluphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
+        			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
         			\caption{
@@
 
-        \linelabel{line:r1-state-dep}In this article, we do not use a state-dependent formulation of NTIC in the current version of ICT.
+        \linelabel{line:r1-state-dep}In this article, we do not use a state-dependent formulation of NTIC.
 However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.

### 2020-04-02 ICT_Frontiers_rev202001_reply.tex
Update from local

@@
         \begin{question}
-            \todo{*****}
             Feedback and memory: p.
@@
         \begin{ans}
-            \toWrite{Thinking to combine the answer to this question with other answers. But not sure yet. Need to think about it. We can skip this one for now.}
+		    @ The reviewer is correct about the example of the video camera under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.
+
+		    @ In such case, simply copying the environmental states to another process (assuming that the sensor of the video camera can capture the whole state of the environment) can lead to positive NTIC.
+
+		    @ This is, in fact, the "Passive adaptation" case mentioned in \cite[p.~4]{BERTSCHINGER.2006},	
+		    \begin{quote}
+			      	\textit{"B1)~Passive adaptation: The system is driven by the environment and adapts passively to all changes in the environment.
+In the case of an environment, that appears deterministic to the system, $H(\hat{e}_{n+1} |\hat{e}_n)=0$, this can be achieved by simply copying the observation of the environment into the system, $S_{n+1} = \hat{e}_n$."}
+		    \end{quote}
+
+	    @ The reviewer is correct about the video camera example under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.
+
+	    @ In such case, simply copying environmental states to a process can lead to positive NTIC.
+
+	    @ In fact, this is one way to achieve NTIC discribed in \cite[p.~4]{BERTSCHINGER.2006},    
+	    \begin{quote}
+	    	\textit{"B1)~Passive adaptation: The system is driven by the environment and adapts passively to all changes in the environment.
+In the case of an environment, that appears deterministic to the system, $H(\hat{e}_{n+1} |\hat{e}_n)=0$, this can be achieved by simply copying the observation of the environment into the system, $S_{n+1} = \hat{e}_n$."}
+	    \end{quote}
+
+	    @ We can also consider this is a special case of modelling the environment when a system has enough sensory and memory capacities, and, therefore, can virtually model the environment by simply copying the environmental states into the system.
+
+	    @ Because this question point to the core concept of ICT, we would like to clarify and emphasise two critical points here.
+
+	    @ a) Informational closure and causation: The definition of information closure \citep{BERTSCHINGER.2006} does not involve causation.
+As described in \cite{BERTSCHINGER.2006}, NTIC can be achieved via "modelling" or "passive adaptation".
+In the "modelling" case, the future state of a process ($Y_{t+1}$) can be caused by $Y_t$, which contain predictive information about how the environment influences the system.
+In the "passive adaptation" case,  the future state of a process ($Y_{t+1}$) is caused by copying environmental information which involves environmental dynamics.
+
+	    The latter case may be conceptually counterintuitive because the internal state of the system (e,g, the video camera) is entirely driven by external input.
+However, it is crucial to know that both cases lead the information flow $J(E\rightarrow Y)$ to (virtually) zero.
+This means that if $Y_t$ contains information about how the environment $E_t$ causes $Y_{t+1}$,
+
+	    However, this is the most critical consequence of solving the scale problem of consciousness in ICT.
+In physical reality, there only exists microscopic processes at the finest microscopic level.
+Any causal dependency at coarse-graining levels should be virtual.
+For example, when Y is informationally closed to X, even though $Y_t$
+
+	    @ b) As described in our manuscript, to form a higher level of NTIC, the informational richness of the environment, i.e.
+$H(E)$ also has to be higher since $H(E_t)$ and $H(Y_{t+1})$ both are the lower bound of $I(Y_{t+1}; H(E_t))$.
+Practically, we believe that with limited sensory and memory capacities, it is difficult to give rise to high NTIC via copying sensory signals to a system.
 
@@
     	\begin{ans}
-			We followed the common setting of coarse-graining (e.g.
+    		We thank the reviewer for this question. We agree that this point is not clear in our original manuscript.
+
+    		Even though the Bayesian graphs for the system-environment dependency are different from the one for the micro-macro level dependency, we apply the same definitions of information flow ($J_{t}(X \rightarrow Y )$) and informational closure ($J_{t}(X \rightarrow Y )=0$) to both graphs.
+
+    		This is a critical assumption in ICT because applying the same definition of informational closure in both scenarios can solve the scale problem of consciousness (informational closure from one level to other levels) and construct our hypothesis about NTIC and consciousness (informational closure from a process to its environment) in an integrated framework.
+
+    		In terms of the Bayesian graphs for the micro-macro level dependency and the definition of informational closure between scales, we followed the conventional setting (e.g.
+\cite{PFANTE.2014}).
+It is important to note that coarse-graining does not and should not take time $Y_t=f_Y(X_t)$ (also see our Definition 1).
+Coarse-graining is merely a function which maps microstates of a system to macrostates, and the microstates and the macrostates are only different level of descriptions of the same system.
+
+    		We agree that we did not indicate this assumption explicitly and may lead to some confusion for our readers. We have added a footnote to make this point explicit.
+
+    		\addnew{\lineref{line:IC2CG}}{
+    			Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) and informational closure (Eq.~\ref{eq:informationflow2}) to the system-environment dependency (e.g.
+$J_{t}(E \rightarrow Y )=0$) and the micro-macro level dependency (e.g.
+$J_{t}(X \rightarrow Y )=0$), even though the Bayesian graphs are different between the two scenarios.
+This follows the common settings in previous studies (e.g.
+\cite{BERTSCHINGER.2006, PFANTE.2014}).
+    		}
+
+%			We followed the common setting of coarse-graining (e.g.
 \cite{PFANTE.2014}) which does not and should not take time $Y_t=f_Y(X_t)$ (in Definition 1).
 Coarse-graining is merely a function which maps microstates of a system to macrostates, and the microstates and the macrostates are simply different level of descriptions of a system.
-			Following this setting, the definition of information closure (flow) $J_{t}(X \rightarrow Y )$ can also be applied in the sense of coarse-graining.
-
-			\todo{Add the definition to the conttext of coarse-graining}
-
-			We understand that this may lead to confusion for our readers. We have added the following sentence to make this point explicit.     		
-			\addnew{\lineref{line:IC2CG}}{Note that we applied the same definition of information closure (Eq.\ref{eq:InformationFlow}) to processes at different coarse-grained levels \citep{{PFANTE.2014}}.}
+%			Following this setting, the definition of information closure (flow) $J_{t}(X \rightarrow Y )$ can also be applied in the sense of coarse-graining. 
+%			
+%			\todo{Add the definition to the conttext of coarse-graining}
+%						
+%			We understand that this may lead to confusion for our readers. We have added the following sentence to make this point explicit.     		
+%			\addnew{\lineref{line:IC2CG}}{Note that we applied the same definition of information closure (Eq.\ref{eq:InformationFlow}) to processes at different coarse-grained levels \citep{{PFANTE.2014}}.}
 %			Here, we followed a common setup of coarse-graining (e.g.

### 2020-04-02 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

--- 2020-03-30 ICT_Frontiers_rev202001_reply.tex
@@
     			\item We agree with the reviewer's comment. 
-    			In fact, in ICT, we do not differentiate states of processes between activation and relation.
-Take neural networks as an example, activation and structure states of a neural network should be both considered.
-After all, they are all just parameters of the process of the neural network.
-The only difference between the two groups of the parameters is the temporal scales of the parameter changes.
+                In fact, we do not differentiate states of processes between activation and relation.
+Take neural network as an example; the relations between elements are determined by the topology of a network (structure) and  its hyperparameters (e.g.
+activation functions).
+We agree that activation and relation of a neural network should be both considered.
+After all, they are all merely the parameters for the process of the neural network.
+The only difference between the two groups of the parameters is the temporal scales of changes.
 States of activation may have more rapid dynamics than states of relation.
-In ICT, this is crucially related to the coarse-graining at the temporal domain which we did not address in this article but can be generalised in the future versions of ICT.
+In ICT, the two sets of parameters do not have any qualitative differences.
 
@@
     	\begin{ans}
-    		\todo{What should we deal with this?}
+    		We have invited a native English speaker for proofreading. Please inform us if it is still not clear and readable. 
     	\end{ans}

### 2020-04-02 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
     	\begin{ans}
-    		We have invited a native English speaker for proofreading. Please inform us if it is still not clear and readable. 
+    		We have invited a native English speaker for proofreading. Please inform us if it is still not clear or unreadable. 
     	\end{ans}
@@
     	\begin{ans}
-    		We thank the reviewer for this question. We agree that this point is not clear in our original manuscript.
-
+    		We thank the reviewer for this question.
+We agree that this point is not clear in our original manuscript.
 Even though the Bayesian graphs for the system-environment dependency are different from the one for the micro-macro level dependency, we apply the same definitions of information flow ($J_{t}(X \rightarrow Y )$) and informational closure ($J_{t}(X \rightarrow Y )=0$) to both graphs.
 
-    		This is a critical assumption in ICT because applying the same definition of informational closure in both scenarios can solve the scale problem of consciousness (informational closure from one level to other levels) and construct our hypothesis about NTIC and consciousness (informational closure from a process to its environment) in an integrated framework.
+    		This is a critical assumption in ICT because applying the same definition of informational closure in both scenarios can solve the scale problem of consciousness (informational closure from one level to other levels) and construct our hypothesis about the relation between NTIC and consciousness (informational closed from a process to its environment) in an integrated framework.
 

### 2020-04-03 ICT_Frontiers_rev202001_reply.tex
update from local

@@
         \begin{ans}
+        	\todo{Everything I want to say is here. Just hard to make these pieces into a whole. Feel frustrated. }
 		    @ The reviewer is correct about the example of the video camera under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.
@@
     	\begin{question}            
-    	\todo{*****}
+    	\todo{I am rewriting this part, please wait}
     		On line 241: '..
@@
     	\begin{question}
-    	\todo{Camera thing...}
+    	\todo{Camera thing..., we need to rewrite this reply as well}
             on Line 316: On the issue of a feedforward network, the current state of a feedforward network with more than one layer is certainly driven by its own past states!

### 2020-04-03 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
         \begin{ans}
+            \todo{camera}
         	\todo{Everything I want to say is here. Just hard to make these pieces into a whole. Feel frustrated. }
+
 		    @ The reviewer is correct about the example of the video camera under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.
@@
 	    @ b) As described in our manuscript, to form a higher level of NTIC, the informational richness of the environment, i.e.
-$H(E)$ also has to be higher since $H(E_t)$ and $H(Y_{t+1})$ both are the lower bound of $I(Y_{t+1}; H(E_t))$.
+$H(E)$ also has to be higher since $H(E_t)$ and $H(Y_{t+1})$ both are the upper bound of $I(Y_{t+1}; H(E_t))$.
 Practically, we believe that with limited sensory and memory capacities, it is difficult to give rise to high NTIC via copying sensory signals to a system.
@@
     	\begin{question}
+
     	\todo{Camera thing..., we need to rewrite this reply as well}

### 2020-04-03 ICT_Frontiers_rev202001.tex
Local update

@@
 
-            \subsubsection*{Informational is not Closed}\label{sec:reflexive}
+            \subsubsection*{Processes are not Informationally Closed}\label{sec:reflexive}
+           		If the environment is info closed we could copy it to get closure.
+In realistic situations we are not sure whether the environment is informationally closed but even if we assume it is we can confidently assert that we don't observe it completely and that the part we do observe (our sensory values) are not themselves closed.
+For example, the images on our retina are insufficient to predict their successors without imagining the outside world behind them.
+This imagining however requires internal processing like recurrent connections.
+
                 If a process is not informationally closed, the degree of NTIC is low (Eq.~\ref{eq:nticObjective2}) resulting in low or no consciousness.

### 2020-04-03 ICT_Frontiers_rev202001.tex
Updates from Overleaf

--- 2020-04-02 ICT_Frontiers_rev202001.tex
@@
     	    %% not monotonic
-    		\linelabel{line:non-monotonic}It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
-We saw above that not sufficiently coarse-grained variables have low values of NTIC.
+    		\linelabel{line:non-monotonic}It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining\footnote{We have known that NTIC is not a non-monotonic function of the scale of coarse-graining.
+However, we currently have limited understanding about this relationship.
+Future work is needed and may involve relevant informational techniques (e.g.,partial information decomposition).}.
+At the finest scale, when we consider the dynamics of the whole universe as a process, the universe should be an informationally closed.
+However, there exists no environment to the universe and, therefore, NTIC of the universe is zero (trivially closed).
 On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC.
-For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.
-Therefor, only processes at a certain level of coarse-graining in the neural system can form a high degree of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
+For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any informational capacity and thus cannot have  mutual information between adjacent time steps.
+Therefor, processes at certain levels of coarse-graining in the neural system can form high degrees of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
 \ac{OurTheory} indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
@@
 
-            \subsubsection*{Informational is not Closed}\label{sec:reflexive}
-                If a process is not informationally closed, the degree of NTIC is low (Eq.~\ref{eq:nticObjective2}) resulting in low or no consciousness.
-In such cases, the current state of a process depends primarily on the environment state (see Fig.~\ref{fig:reflexive}), but receives little influence from its past state.
+            \subsubsection*{Processes that are not Informationally Closed}\label{sec:reflexive}
+            ICT leads to some surprisingly simple conscious processes.
+Consider the case already noted by \citet{BERTSCHINGER.2006} where the environment process is deterministic (or close to it) and the system just copies the environment process.
+Then the system achieves a high value of NTIC with respect to the environment.
+ICT states that such processes are conscious.
+
+            (We assume Transfer entropy from environment to system is equal to transfer entropy from sensor to system by definition).
+
+            However, in more realistic cases the system cannot copy the environment state because it observes only part of it. 
+            % and/or because it is itself not large enough to contain a copy of the environment.
+
+            Let us assume that the system only observes a part of the (still environment state.
+            \footnote{In theory this part of the environment state may still evolve deterministically over time in which case the system need only copy this part to achieve NTIC and consciousness.
+This seems to be a rare case as well and we assume the observed part of the environment is not close to deterministic in the following.}
+            In this case it is well known that the observed part of the environment need not even be a Markov process even if the environment itself is deterministic.
+So the mutual information between subsequent observations may be much lower than the mutual information between subsequent environment states.
+
+            Furthermore, in this case the transfer entropy from environment to the system becomes equal to the transfer entropy from the observed part of the environment to the system.
+
+            Finally, note that the transfer entropy that can be achieved by copying the environment state or the observed part of the environment state is bounded from above by the mutual information between the subsequent environment states or observations.
+Copying the environment state corresponds to setting $S_{t+1}=E_t$ such that the transfer entropy is
+            \begin{align}
+             I(S_{t+1}:E_t|S_t)=I(E_t:E_t|E_{t-1})=H(E_t|E_{t-1}).
+            \end{align}
+            We can represent the part of the environment that we observe by the value of a function applied to the environment state so that
+
+            % In such situations ITC predicts that higher levels of consciousness are achieved if the system can anticipate the next observed values which requires a higher internal self-determination than that of the copies of the observations.
+
+            % Another way to put this is the higher the difference in predictability of the sensor values and the entrie environment state the more potential is there to increase the level of consciousness for the system by modelling the underlying hidden Markov process i.e.\ environment.
+
+            % Also assume that the part that the system observes is not itself deterministic or close to it but that the underlying environment is.
+
+            % A system with a high NTIC in such situations must 
+            % Then the system can decrease the transfer entropy from the environment to itself by anticipating the next observation.
+This is due to the fact that the transfer entropy from the environment to the system is equal to the transfer entropy from the observations to the system.
+
+            % does not have access to the entire environment state and instead observes only part of it.
+This part is rarely close to deterministic even if the entire environment is deterministic.
+In order to achieve informational closure with respect to the entire environment the system has to achieve closure exactly with respect to its sensor values.
+
+            % we could copy it to get closure.
+In realistic situations we are not sure whether the environment is informationally closed but even if we assume it is we can confidently assert that we don't observe it completely and that the part we do observe (our sensory values) are not themselves closed.
+For example, the images on our retina are insufficient to predict their successors without imagining the outside world behind them.
+This imagining however requires internal processing like recurrent connections.
+
+                The higher the transfer entropy from environment to the system the lower NTIC (Eq.~\ref{eq:nticObjective2}) and therefore, according to ICT, the lower the level of consciousness.
+Under the assumptions above,
+
+                high transfer entropies occur when the current state of a process depends primarily on the environment state (see Fig.~\ref{fig:reflexive}), but receives little influence from its past state.
 Reflexive behaviours \citep{casali2013theoretically} can be considered an example of this scenario.
@@
 
-            \subsubsection*{Information is Trivial}
+            \subsubsection*{Processes are Trivial closed}
                 According to \ac{OurTheory}, when encoded information in a process is trivial, i.e.

### 2020-04-03 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
     	\begin{ans}
-    		\todo{I think I made a big mistake in the manuscript.
-When I wrote this part I only considered IC as a function of scales of coarse-graining.
-But I just realised NTIC is totally a different story that I didn't think about thoroughly.
-I may need to re-write this paragraph}
+    	We thank the reviewer for asking this question. We did not write this part clearly.
 
-    		We thank the reviewer for proposing the question about the relationship between NTIC and scale of coarse-graining.
-We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining.
-Some coarse-grainings lead to higher NTICs for macroscopic than microscopic processes.
-However, we are just starting the research on this relationship, and have not yet had a systematic understanding of it.
-This work may involve the technique of partial information decomposition and related research fields.
+    	It is true that at the finest scale, when we consider the whole universe as a system, the universe should be an informationally closed and deterministic process.
+However, there exists no environment to the universe and, therefore, NTIC of the universe is zero (trivially closed).We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining.
+However, we currently have very limited understanding of this relationship.
+Future work is needed and may involve the techniques of partial information decomposition and related research fields.
+
 		We agree that our original claim about existing a intermediate maxima in NTIC was too strong and have revised the paragraph as follows:
-            % We emphasise the non-monotonic relation between the scales of coarse-graining and the degrees of NTIC.
-However, we do not exclude the possibility that there exist multiple NTIC picks across scales of coarse-graining of a process.
-This implies that we do not exclude the possibility that there exist multiple high conscious processes at different scales.
-(However, due to IC, conscious processes are not able to know the existence of each other.
+
 		\revise{\lineref{line:non-monotonic}}
@@
 		{
-				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
-Insufficiently coarse-grained variables could lead to lower values of NTICs at micro than macroscopic processes.
+			It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining\footnote{We have known that NTIC is not a non-monotonic function of the scale of coarse-graining.
+However, we currently have limited understanding about this relationship.
+Future work is needed and may involve relevant informational techniques (e.g.,partial information decomposition).}.
+At the finest scale, when we consider the dynamics of the whole universe as a process, the universe should be an informationally closed.
+However, there exists no environment to the universe and, therefore, NTIC of the universe is zero (trivially closed).
 On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC.
-For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.
-Therefore, processes at certain levels of coarse-graining may have higher values of NTIC than other levels (Fig.~\ref{fig:LevelOfConsciousness}).
-ICT suggests that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
+For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any informational capacity and thus cannot have  mutual information between adjacent time steps.
+Therefor, processes at certain levels of coarse-graining in the neural system can form high degrees of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
+\ac{OurTheory} indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
 		}	    		

### 2020-04-04 ICT_Frontiers_rev202001.tex
Updates from Overleaf

@@
 
-            Finally, note that the transfer entropy that can be achieved by copying the environment state or the observed part of the environment state is bounded from above by the mutual information between the subsequent environment states or observations.
+            Finally, note that the transfer entropy that can be achieved by copying the environment state or the observed part of the environment state equal to the mutual information between the subsequent environment states or observations.
 Copying the environment state corresponds to setting $S_{t+1}=E_t$ such that the transfer entropy is
@@
             \end{align}
-            We can represent the part of the environment that we observe by the value of a function applied to the environment state so that
+            We can represent the part of the environment that we observe by the value of a function applied to the environment state so that in this case we get
+            \begin{align}
+             I(S_{t+1}:f(E_t)|S_t)=I(f(E_t):f(E_t)|f(E_{t-1}))=H(f(E_t)|f(E_{t-1}).
+            \end{align}
+            Now additionally apply a feedforward network with layer $i$ represented by function $g_i$ then we get
+            \begin{align}
+             I(S_{t+1}: f(E_t)|S_t)=I(g\circ f(E_t):f(E_t)|f(E_{t-1}))=H(f(E_t)|f(E_{t-1}).
+            \end{align}
 

### 2020-04-04 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
             Thank you for your attention to our manuscript and your interesting question. \\
-            If we understand correctly, molecular recognition refers to specific types of interactions among molecules to form molecular complexes.
+            If we understand correctly, molecular recognition refers to specific types of interactions among molecules that form molecular complexes.
 There is no question that molecular complexes are coarse-grainings of molecules via molecular recognition.
 Based on our hypothesis, if the dynamics of a molecular complex is an NTIC process, the information closure theory of consciousness (ICT) would claim that the molecular complex has a certain degree of consciousness.
-Therefore, to your question, it is theoretically plausible under the framework of ICT.
+            % Therefore, to your question, it is theoretically plausible under the framework of ICT.
 We speculate that it may be easy to find informationally closed molecular complexes (isolated complexes) but may not be easy to find ones forming NTIC processes.
-Nevertheless, with well-defined mathematical definition, this is an empirical and testable question to ICT.
+This is an empirical and testable question under the ICT.
 We look forward to learning any self-assembly process forming NTIC at molecular scales in the near future.

### 2020-04-04 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
     		\newline
-    		a) Considering Eq.\ref{eq:NTIC2}, it is true that the transfer entropy term $J_t(E -> Y)=0$ is not required for $NTIC>0$.
+    		a) Considering Eq.\ref{eq:NTIC2}, it is true that the transfer entropy term $J_t(E -> Y)$ does not have to be zero for $NTIC>0$.
 It is possible to have a high degree of NTIC when $J_t(E -> Y) > 0$, i.e.
 the process is not completely closed.
+We consider NTIC here as just the quantity defined in Eq.\ref{eq:NTIC2}.
 \\
-    		However, based on the setting in both Bertschinger et al.
+            % 		However, based on the setting in both Bertschinger et al.
 2006 and our Section 2 (at Line \lineref{line:r1q1a}), $Y_{t+1}$ is determined by both $Y_t$ and $E_t$.
@@
 minimising $J_t(E -> Y)$, is crucial to increase NTIC even though $J_t(E -> Y) > 0$.\\
-    		In our current version of ICT, we consider the level of consciousness corresponds to the degree of NTIC of a process.
+            % 		In our current version of ICT, we consider the level of consciousness corresponds to the degree of NTIC of a process. 
             Therefore, a conscious process does not have to be completely closed. 
-However, a high degree of closedness is crucial to have a high level of consciousness.
-(Regarding to the video camera example, please see more discussion in our reply to your Q6.) \\
+            However, processes that manage to reduce the transfer entropy from the environment without reducing their mutual information with the environment achieve 
+            % higher degreed of closedness is crucial to have a
+            higher levels of consciousness. 
+            Regarding the video camera example, please see more discussion in our reply to your Q6. \\
 
     		\noindent
-    		b) We thank the reviewer for this question.
-We entirely agree that state-dependent measurements are essential to describe the dynamics of conscious experience.
-In fact, we now are working on state-dependent formulations for the next version of the ICT.
-In contrast to the current version, this work involves point-wise informational measures and certainly require more space and discussion.
+    		b) It is true that NTIC is not state-dependent.
+We agree that state-dependent measurements are essential to describe the dynamics of conscious experience.
+We are  working on state-dependent formulations for the next version of the ICT.
+In contrast to the current version, this work involves point-wise informational measures and requires more space and discussion.
 Therefore, we prefer to address the state-dependent version of ICT in future studies and keep the first version of our theory simple.\\
@@
 However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.
-Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed in the next version of ICT.}
+Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed for the next version of ICT.}
 
@@
         \begin{question}
-            Hypothesis and Implication 3: Why is it crucial that there is an underlying X with respect to which Y is a C-process?     
+            Hypothesis and Implication 3: Why is it crucial that there is an underlying $X$ with respect to which $Y$ is a C-process?     
         \end{question}
@@
         \begin{ans}        	
-            It is crucial to have an underlying X with respect to Y because this assumption can solve the scale problem of consciousness.
-It ensures that the information transfer from all coarse-grainings of X to Y vanishes.
+            It is crucial to have an underlying $X$ with respect to $Y$ because this assumption can solve the scale problem of consciousness.
+It ensures that the information transfer from all coarse-grainings of $X$ to $Y$ vanishes.
 Therefore, human conscious experiences do not involve information from other scales of coarse-graining.
-            Because X is the micro-level of the universe, the information transfer from any coarse-graining (including E and S) of X  to Y must be lower than that from X to Y, i.e.
+            Because $X$ is the micro-level of the universe, the information transfer from any coarse-graining (including E and S) of $X$  to $Y$ must be lower than that from $X$ to Y, i.e.
 $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$.
-So that Y is informationally closed with respect to X implies that Y is also informationally closed with respect to S, E, and all other coarse-grainings of X.
+So that $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to S, E, and all other coarse-grainings of X.
         \end{ans}
@@
         \begin{question}
-            Does Y being informationally closed with respect to X imply that Y is also informationally closed with respect to E, i.e.
+            Does $Y$ being informationally closed with respect to $X$ imply that $Y$ is also informationally closed with respect to E, i.e.
 $J_t(E-Y) = 0$?
@@
         \begin{ans}
-            Yes. Y being informationally closed with respect to X implies that Y is also informationally closed with respect to E, i.e. $J_t(E-Y) = 0$ (Please see our reply to Q2).\\
+            Yes. $Y$ being informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to E, i.e. $J_t(E-Y) = 0$ (Please see our reply to Q2).\\
             As explained in Question 1a, it is not required for NTIC processes to be completely closed.
-The information transfer from X to Y $I(Y_{t+1}; X_t|Y_t)$ (if non-zero) serves as the upper bound of the information transfer from any other process to Y.
+The information transfer from $X$ to $Y$ $I(Y_{t+1}; X_t|Y_t)$ (if non-zero) serves as the upper bound of the information transfer from any other process to Y.
 So unpredictable sensory inputs will contribute to a positive information transfer.
@@
 14: comparison to IIT: what does ICT say about different sets of variables at the same level.
-There might well be multiple ways to partition X into S and E, with many overlapping S's.
+There might well be multiple ways to partition $X$ into S and E, with many overlapping S's.
 Would those all be conscious?
@@
 (Thus the IIT emphasis on causation).\\
-            If somehow the fact that Y must be informationally closed wrt X does the heavy-lifting here that should be made more explicit (see above).
+            If somehow the fact that $Y$ must be informationally closed wrt $X$ does the heavy-lifting here that should be made more explicit (see above).
         \end{question}
@@
 Any causal dependency at coarse-graining levels should be virtual.
-For example, when Y is informationally closed to X, even though $Y_t$
+For example, when $Y$ is informationally closed to X, even though $Y_t$
 
@@
 We agree that this point is not clear in our original manuscript.
-Even though the Bayesian graphs for the system-environment dependency are different from the one for the micro-macro level dependency, we apply the same definitions of information flow ($J_{t}(X \rightarrow Y )$) and informational closure ($J_{t}(X \rightarrow Y )=0$) to both graphs.
+Even though the Bayesian graphs for the system-environment dependency are different from the one for the micro-macro level dependency, we apply the same definitions of information flow ($J_{t}(X \rightarrow $Y$ )$) and informational closure ($J_{t}(X \rightarrow $Y$ )=0$) to both graphs.
 
@@
     			Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) and informational closure (Eq.~\ref{eq:informationflow2}) to the system-environment dependency (e.g.
-$J_{t}(E \rightarrow Y )=0$) and the micro-macro level dependency (e.g.
-$J_{t}(X \rightarrow Y )=0$), even though the Bayesian graphs are different between the two scenarios.
+$J_{t}(E \rightarrow $Y$ )=0$) and the micro-macro level dependency (e.g.
+$J_{t}(X \rightarrow $Y$ )=0$), even though the Bayesian graphs are different between the two scenarios.
 This follows the common settings in previous studies (e.g.
@@
 Coarse-graining is merely a function which maps microstates of a system to macrostates, and the microstates and the macrostates are simply different level of descriptions of a system.
-%			Following this setting, the definition of information closure (flow) $J_{t}(X \rightarrow Y )$ can also be applied in the sense of coarse-graining. 
+%			Following this setting, the definition of information closure (flow) $J_{t}(X \rightarrow $Y$ )$ can also be applied in the sense of coarse-graining. 
 %			
@@
 \\
-%			In our hypothesis, Y is IC with respect to the microstate of the universe, X.
-This is critical in the hypothesis because Y is IC with respect to X, implying that Y is also IC with respect to its intermediate level S and its environment E in Fig.
+%			In our hypothesis, $Y$ is IC with respect to the microstate of the universe, X.
+This is critical in the hypothesis because $Y$ is IC with respect to X, implying that $Y$ is also IC with respect to its intermediate level S and its environment E in Fig.
 \ref{fig:fullgraph}.\todo{need any change in the main text?}

### 2020-04-06 ICT_Frontiers_rev202001.tex
Updates from Overleaf

--- 2020-04-03 ICT_Frontiers_rev202001.tex
@@
                 center,
-            	adjusted title=\large To Be Modified ...,
+            	adjusted title=\large To Be Modified \dots,
             	halign title=center,
@@
 \\
-            This implication is also in agreement with the "axiom" of \textit{information} in Integrated Information Theory (IIT 3.0) which claims that \textquote[{\citealp[P.~2]{oizumi2014phenomenology}}]{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...}
+            This implication is also in agreement with the "axiom" of \textit{information} in Integrated Information Theory (IIT 3.0) which claims that \textquote[{\citealp[P.~2]{oizumi2014phenomenology}}]{\dots an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences\dots}
 
@@
 	\section{Conscious Versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
-	    In this section, we show how \ac{OurTheory} can explain and make predictions about what processes are conscious and what are unconscious.
+	    In this section, we show how \ac{OurTheory} can explain and make predictions about what processes are more conscious than others.
 \ac{OurTheory} is constructed using information theory.
@@
         \subsection{Unconscious Processing}
-            Regarding unconscious processing, we highlight two scenarios in which the degree of NTIC is rendered low for a process, and thereby making the process less conscious.
+            Regarding unconscious processing, we highlight two scenarios which decrease the degree of NTIC of a process, thereby making the process less conscious.
 
             \subsubsection*{Processes that are not Informationally Closed}\label{sec:reflexive}
-            ICT leads to some surprisingly simple conscious processes.
+            \linelable{line:notIC}
+            % \paragraph{@ Acer's version}
+            % Based on Eq.~\ref{eq:nticObjective2}), to maximise NTIC, a process can minimise the information flow from the environment to the process $J_{t}(E \rightarrow Y ) := I(Y_{t+1};E_{t}|Y_{t})$ (Eq.~\ref{eq:InformationFlow}).
+For agents such as human being, who always face informationally rich environments, the environment is usually partially observable with limited sensory capacities.
+This leads to the sensor values are not deterministic (or close to it).
+In such cases, if the state of a internal process is mainly driven by sensory inputs, the information flow from the environment to the process is considered to be large and the process is not informationally closed.
+
+            % First, to maximise NTIC, a process can minimise the information flow from the environment to the process $J_{t}(E \rightarrow Y ) := I(Y_{t+1};E_{t}|Y_{t})$ (Eq.~\ref{eq:InformationFlow}).
+Here, we illustrate two distinctive scenarios which shade light of the relationship between informational closure and consciousness.
+
+            % \paragraph{@ Martin's version}
+            The first scenario is that of a system partially observing the environment in such a way that the current observation is insufficient to predict the next.
+In this situation we can show that a system passively processing the observations (including copying them) achieves lower values of NTIC and therefore lower levels of consciousness than a system that is able to accurately predict the observations.
+
+            %Is there a (generative) epsilon machine that achieves higher NTIC than copying?
+If yes, under what conditions (e.g.
+reversibility of the underlying environment process?) on the sensor process does it exist?
+            %Is Bertschinger's system better than copying? 
+            \ac{OurTheory} leads to some surprisingly simple conscious processes.
 Consider the case already noted by \citet{BERTSCHINGER.2006} where the environment process is deterministic (or close to it) and the system just copies the environment process.
-Then the system achieves a high value of NTIC with respect to the environment.
+Then the system can achieve positive values of NTIC with respect to the environment.
 ICT states that such processes are conscious.
 
-            (We assume Transfer entropy from environment to system is equal to transfer entropy from sensor to system by definition).
-
-            However, in more realistic cases the system cannot copy the environment state because it observes only part of it. 
+            % (We assume Transfer entropy from environment to system is equal to transfer entropy from sensor to system by definition).
+
+            However, in more realistic cases the system cannot copy the entire environment state because it observes only part of it. 
             % and/or because it is itself not large enough to contain a copy of the environment.
 
-            Let us assume that the system only observes a part of the (still environment state.
-            \footnote{In theory this part of the environment state may still evolve deterministically over time in which case the system need only copy this part to achieve NTIC and consciousness.
-This seems to be a rare case as well and we assume the observed part of the environment is not close to deterministic in the following.}
-            In this case it is well known that the observed part of the environment need not even be a Markov process even if the environment itself is deterministic.
-So the mutual information between subsequent observations may be much lower than the mutual information between subsequent environment states.
-
-            Furthermore, in this case the transfer entropy from environment to the system becomes equal to the transfer entropy from the observed part of the environment to the system.
-
-            Finally, note that the transfer entropy that can be achieved by copying the environment state or the observed part of the environment state is bounded from above by the mutual information between the subsequent environment states or observations.
-Copying the environment state corresponds to setting $S_{t+1}=E_t$ such that the transfer entropy is
-            \begin{align}
-             I(S_{t+1}:E_t|S_t)=I(E_t:E_t|E_{t-1})=H(E_t|E_{t-1}).
-            \end{align}
-            We can represent the part of the environment that we observe by the value of a function applied to the environment state so that
+            We show in Appendix \ref{sec:appendix} that whenever the environment has itself more predictable dynamics than the observations there is potential for a predictive process to achieve higher NTIC than a copying system or any system that only processes its last observations without taking into account other internal memory.
+Similar to \citet{BERTSCHINGER.2006} we will refer to systems of the latter type as \textit{passive}.
+We will call all other systems that achieve positive NTIC \textit{predictive}.
+Note that the predictive process might need to be more complex than the system that only copies its observations.
+
+            We tentatively assume below that for a feed-forward network which can be seen as implementing a function from an extended history of past observations to the system state there also always exist systems that achieve higher NTIC.
+This remains to be verified.
+
+            % Notes: 
+            % -put complicated stuff into appendix
+            % -make clear notion of passive system vs predictive system.
+            % This shows that for 
+            % \begin{align}
+            %  I(S_{t+1}; f(E_t)|S_t)=I(g\circ f(E_t);f(E_t)|f(E_{t-1}))=H(f(E_t)|f(E_{t-1}).
+            % \end{align}
 
@@
 
-                The higher the transfer entropy from environment to the system the lower NTIC (Eq.~\ref{eq:nticObjective2}) and therefore, according to ICT, the lower the level of consciousness.
+           	% \textit{=== End of the modification === }\\
+
+                % The higher the transfer entropy from environment to the system the lower NTIC (Eq.~\ref{eq:nticObjective2}) and therefore, according to ICT, the lower the level of consciousness.
 Under the assumptions above,
 
-                high transfer entropies occur when the current state of a process depends primarily on the environment state (see Fig.~\ref{fig:reflexive}), but receives little influence from its past state.
-Reflexive behaviours \citep{casali2013theoretically} can be considered an example of this scenario.
+                % high transfer entropies occur when the current state of a process depends primarily on the environment state (see Fig.~\ref{fig:reflexive}), but receives little influence from its past state.
+
+                Let us now look at some examples of this scenario.
+
+               The first are reflexive behaviours \citep{casali2013theoretically}. 
+            %   can be considered an example of this scenario. 
                In \ac{OurTheory}, if we can view reflexive behaviours as situations in which the internal state $Y_t$, which triggers reflexive action, is determined by the environment state $E_{t-1}$ overruling the influences from its own past $Y_{t-1}$.
-Such interpretation of reflexive behaviour from the viewpoint of \ac{OurTheory} naturally explains why reflexes do not involve conscious experience of external stimuli.
+Such interpretation of reflexive behaviour from the viewpoint of \ac{OurTheory} naturally explains why we are less conscious of external stimuli causing reflexes than of others.
 
@@
         		The same principle can be applied to interpret blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedural memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes.
-        		\linelabel{line:r2q6}Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience (however, in some cases, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}).
+        		\linelabel{line:r2q6}Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.
+However, in some cases, they may still preserve some forms of conscious experience (see \cite{overgaard2011visual, mazzi2016blind}).
 We argue that action outputs of blindsight can be directly guided by sensory inputs through stimulus-response maps.
-The neural circuits are not informationally closed and, therefore, unconscious.
-Similarly, for procedural memory, the state transitions of action controls largely depends on the concurrent environmental states.
-This prevents the internal processes of procedure memory from informational closure and being conscious.
-\ac{OurTheory} also offer an interpretation as to why patients with visual apperceptive agnosia \citep{james2003ventral} can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.
-
-        		As we have seen in the examples above, a crucial implication of \ac{OurTheory} is that a pure feedforward network cannot produce consciousness because NTIC requires a form of memory $I(Y_{t+1};Y_{t})$.
+The corresponding neural circuits are passive and therefore do not achieve the same level of informational closure as processes/behaviours involving prediction.
+According to \ac{OurTheory} we are therefore less conscious of them.
+
+        		Similarly, for procedural memory, the transitions of the part of the neural system determining the action sequences largely depend on the  environmental states.
+Procedural memory may therefore be considered a passive process.
+\ac{OurTheory} then predicts that we are less conscious of procedural memory than of more predictive processes.
+
+        		\ac{OurTheory} also offers an interpretation as to why patients with visual apperceptive agnosia \citep{james2003ventral} can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.
+
+                % \paragraph{@ Acer's revision}
+                % However, with a caveat, informational closure can also be achieve by just copying the environment process in some certain cases.
+Consider the case already noted by \citet{BERTSCHINGER.2006} where the environment process is deterministic (or close to it) and full observe.
+the system just copies the environment process.
+Then the system achieves a high value of NTIC with respect to the environment.
+ICT states that such processes are conscious.
+
+                % \paragraph{@ Orignal}
+                Networks with recurrent loops employ information stored in their own past states that is not necessarily a function of a single time-step observation. 
+        		If it indeed turns out to be true that for every pure feed-forward network there are non-feed-forward systems achieving higher NTIC then ICT predicts that the latter  systems achieve higher levels of consciousness.
+
+        % 		than the because NTIC requires a form of memory $I(Y_{t+1};Y_{t})$.
 Without memory, a network's current state is entirely driven by the input the network receives from the environment without any influence from its own past states.
 Therefore, such a network is incapable of forming an NTIC.
-In contrast, a network with recurrent loops can maintain information about its own past states.
-This forms an information channel between the past and the future states of the network and, thus, makes the network capable of being informationally closed.
-This result coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
+In contrast,
+
+        		This would coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
 
@@
 However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.
-Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed in the next version of ICT.
+Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed for the next version of ICT.
 
@@
 The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
-
+\section{Appendix*}
+\label{sec:appendix}
+            Let us assume that the system only observes a part of the environment state.
+            % \footnote{In theory this part of the environment state may still evolve deterministically over time in which case the system need only copy this part to achieve NTIC and consciousness.
+This seems to be a rare case as well and we assume the observed part of the environment is not close to deterministic in the following.}
+            % In this case it is well known that the observed part of the environment need not even be a Markov process even if the environment itself is deterministic.
+So the mutual information between subsequent observations may be much lower than the mutual information between subsequent environment states.
+
+            % Furthermore, in this case the transfer entropy from environment to the system becomes equal to the transfer entropy from the observed part of the environment to the system.
+
+            % Finally, note that the transfer entropy that can be achieved by copying the environment state or the observed part of the environment state equal to the mutual information between the subsequent environment states or observations.
+Copying the environment state corresponds to setting $S_{t+1}=E_t$ such that the transfer entropy is
+            % \begin{align}
+            %  I(S_{t+1}:E_t|S_t)=I(E_t:E_t|E_{t-1})=H(E_t|E_{t-1}).
+            % \end{align}
+            We can represent the part of the environment that we observe by the value of a function $f$ applied to the environment state. In this case we get for the transfer entropy
+            \begin{align}
+             I(S_{t+1}:E_t|S_t)=I(S_{t+1}:f(E_t)|S_t).
+            \end{align}
+            If the system only copies the observation we then get for the transfer entropy
+            \begin{align}
+             I(S_{t+1}:f(E_t)|S_t)=I(f(E_t):f(E_t)|f(E_{t-1}))=H(f(E_t)|f(E_{t-1})
+            \end{align}
+            and for the mutual information
+            \begin{align}
+             I(S_{t+1};E_t)=I(f(E_{t+1};E_t)=H(f(E_t))
+            \end{align}
+            such that 
+            \begin{align}
+                NTIC=I(f(E_t);f(E_{t-1})).
+            \end{align}
+            This shows that whenever there is mutual information between subsequent observations a process that only copies the observations has positive NTIC.
+Note that any additional (internal) processing of the observation without reference to an additional internal state using a function $g$ can only reduce this mutual information:
+            \begin{align}
+               I(f(E_t);g(f(E_{t-1})))\leq I(f(E_t);f(E_{t-1})).
+            \end{align}
+            However, for each such system there are systems that achieve higher NTIC.
+Take for example a "mirrored" and synchronized environment.
+In this case we have $S_t:=E_t$ such that the transfer entropy vanishes
+            \begin{align}
+             I(S_{t+1}:f(E_t)|S_t)=I(E_{t+1}:f(E_t)|E_t)=0
+            \end{align}
+            and the mutual information is equal to the mutual information between current and next environment state:
+            \begin{align}
+                I(S_{t+1};E_t)=I(E_{t+1};E_t)\geq I(f(E_{t+1});f(E_t)).
+            \end{align}
+             This shows that whenever the environment has itself more predictable dynamics than the observations there is potential for a predictive process to achieve higher NTIC than a copying system or any system that only processes its last observations without taking into account other internal memory.
+
+----------------------
+            For a feedforward network with each layer computing just the identity:
+            \begin{align}                NTIC&=I(f(E_t),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n}))\\
+            &=H(f(E_t),\dots,f(E_{t-n+1})) - H(f(E_t)|f(E_{t-1}),\dots,f(E_{t-n})).
+            \end{align}
+            For the mirror environment, if we use the history dependent NTIC \citep{BERTSCHINGER.2006} we get:
+            \begin{align}
+                NTIC^{s,m}=I(E_{t+1};E_t,\dots,E_{t-n+1})
+            \end{align}
+            To see that this is always larger or equal to the feedforward network note that the feedforward NTIC can be rewrittten:
+            \begin{align}                NTIC^{ff}&=I(f(E_t),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n}))\\
+            &=I(f(E_t);f(E_{t-1}),\dots,f(E_{t-n}))+
+            I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
+            &=I(f(E_t);f(E_{t-1}),\dots,f(E_{t-n}))+
+            I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
+            &=I(f(E_t);g(E_{t-1},\dots,E_{t-n}))+
+            I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
+            &=I(E_t;E_{t-1},\dots,E_{t-n}) \underbrace{-B+
+            I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))}_{\leq 0}\\
+            &\leq I(E_t;E_{t-1},\dots,E_{t-n}).
+            % &\leq NTIC^{s,m}+
+            % I(C;C,f(E_{t-n})|f(E_t))\\
+            % &=NTIC^{s,m}+
+            % I(C;C|f(E_t))\\
+            % &=NTIC^{s,m}+
+            % H(C|f(E_t))\\
+            % &=\underbrace{I(f(E_t);f(E_{t-1}),\dots,f(E_{t-n}))}_{\text{stationarity:}\leq NTIC^{s,m}}+
+            % I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
+            % &\leq NTIC^{s,m}+
+            % I(C;C,f(E_{t-n})|f(E_t))\\
+            % &=NTIC^{s,m}+
+            % I(C;C|f(E_t))\\
+            % &=NTIC^{s,m}+
+            % H(C|f(E_t))\\
+            % ============================================================================ WEIRD
+            % &=I(f(E_t);C)+I(f(E_t),f(E_{t-n})|C)+
+            % H(C|f(E_t))\\
+            % &=H(C)-H(C|f(E_t))+I(f(E_t),f(E_{t-n})|C)+
+            % H(C|f(E_t))\\
+            % &=H(C)+I(f(E_t),f(E_{t-n})|C)\\
+            % &=H(C)+H(f(E_t)|C)-H(f(E_t)|f(E_{t-n}),C)\\
+            % &=I(f(E_t);C)-H(f(E_t)|f(E_{t-n}),C)\\
+            % &=I(A, C;C,B).
+            \end{align}
+
+            \begin{align}
+                I(X;Y)&=_? I(f(X),X:g(Y),Y)\\
+                &=I(X:g(Y),Y)+I(f(X):g(Y),Y|X)\\
+                &=I(X:g(Y),Y)\\
+                &=I(X:Y)+I(X:g(Y)|Y)\\
+                &=I(X:Y)
+            \end{align}
+
+            \begin{align}
+                I(X;Y)&= I(f(X),X:g(Y),Y)\\
+                &=I(f(X):g(Y),Y)+I(X:g(Y),Y|f(X))\\
+                &=I(f(X):g(Y))+I(f(X):Y|g(Y))+ I(X:Y|f(X))+I(X:g(Y)|Y,f(X)).
+            \end{align}
+
+            \begin{align}
+                I(f(X):g(Y))=I(X;Y)-I(f(X):Y|g(Y))- I(X:Y|f(X))-I(X:g(Y)|Y,f(X))
+            \end{align}
+
+----------------------
 	\bibliographystyle{authordate1}

### 2020-04-06 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
             a) Bertschinger et al.
-2006 define informationally closed as $J_t(E -> Y) = 0$, but this is not a requirement for NTIC.
+2006 define informationally closed as $J_t(E\rightarrow Y) = 0$, but this is not a requirement for NTIC.
 Meaning, a positive NTIC measure does not entail that $J_t = 0$.
@@
     		\newline
-    		a) Considering Eq.\ref{eq:NTIC2}, it is true that the transfer entropy term $J_t(E -> Y)$ does not have to be zero for $NTIC>0$.
-It is possible to have a high degree of NTIC when $J_t(E -> Y) > 0$, i.e.
+    		a) Considering Eq.\ref{eq:NTIC2}, it is true that the transfer entropy term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$.
+It is possible to have a high degree of NTIC when $J_t(E\rightarrow Y) > 0$, i.e.
 the process is not completely closed.
@@
         \begin{ans}        	
-            It is crucial to have an underlying $X$ with respect to $Y$ because this assumption can solve the scale problem of consciousness.
-It ensures that the information transfer from all coarse-grainings of $X$ to $Y$ vanishes.
+            The C-processes are constructed to answer questions about the scale problem of consciousness. Their definition therefore states their relation to the microscopic scale $X$. 
+            At the same time it would be possible to remove $X$ from the definition and instead require that $Y$ is informationally closed with respect to all other processes.
+In some cases such a definition would be more general than the present one for example when there is no final microscale and instead there is an infinite number of more and more microscopic scales.
+However, we find the use of an explicit microscale $X$ easier to understand and sufficient to communicate the idea.
+Note that closure with respect to $X$ (if it exists) implies closure with respect to every coarse-graining of $X$.
+            % For this We use the underlying $X$ with respect to $Y$ in order to illustrate the scale problem of consciousness. 
+            % It ensures that the information transfer from all coarse-grainings of $X$ to $Y$ vanishes.
 Therefore, human conscious experiences do not involve information from other scales of coarse-graining.
-            Because $X$ is the micro-level of the universe, the information transfer from any coarse-graining (including E and S) of $X$  to $Y$ must be lower than that from $X$ to Y, i.e.
+            % 
+            To see this note that the information transfer from any coarse-graining (including $E$ and $S$) of $X$ to $Y$ must be lower than that from $X$ to $Y$, i.e.
 $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$.
-So that $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to S, E, and all other coarse-grainings of X.
+So that $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to $S, E$, and all other coarse-grainings of $X$.
         \end{ans}
@@
             Does $Y$ being informationally closed with respect to $X$ imply that $Y$ is also informationally closed with respect to E, i.e.
-$J_t(E-Y) = 0$?
+$J_t(E\rightarrow Y)= 0$?
 I don't think that could be true for the brain, or part of it really.
@@
         \begin{ans}
-            Yes. $Y$ being informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to E, i.e. $J_t(E-Y) = 0$ (Please see our reply to Q2).\\
+            Yes.
+As mentioned in our answer to Q2 $Y$ being informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to E, i.e.
+$J_t(E\rightarrow Y) = 0$.
             As explained in Question 1a, it is not required for NTIC processes to be completely closed.
@@
 So unpredictable sensory inputs will contribute to a positive information transfer.
-For high NTIC systems however this transfer must be less than the mutual information between the sensory inputs and the next system state.
+            As mentioned before higher NTIC values are achieved when this information transfer can be reduced without reducing the mutual information between the sensory inputs and the next system state.
         \end{ans}
@@
     	\begin{ans}
-            We thank the reviewer for this critical question. We do not impose the exclusion criterion in ICT. This is a critical difference between IIT and ICT. \\
+            We can see how Figure 4 was ambiguous with respect to this question. We do not impose the exclusion criterion in ICT and have changed Figure 4 to remove the impression that it does. 
+            % This is a difference between IIT and ICT. \\
             % The exclusion criterion is based on the assumption that individual entities (e,g, consciousnesses) should share no subset with any other entities.
@@
             A key feature of ICT is that, instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of system-environment separation and a boundary of a system \citep{BERTSCHINGER.2006}.
-For example, \citet{krakauer2014information} proposed an algorithm to add and remove variables in order to find the boundary.
+For example, \citet{krakauer2014information,krakauer2020information} proposed an algorithm to add and remove variables in order to find the boundary.
 \\
-            It is true that every subset of a system can be computed and can have a positive value of NTIC.
-However, following the notion of informational closure, if a subset is not informationally closed, the subset is considered as a part of the system.
-            ICT applies the same notion to consciousness.
+            It is true that NTIC can be computed for every subset of a system and can also have a positive value of NTIC for multiple of those.
+All such subsets are thus conscious.
+However, while conscious, they are not necessarily the entire or whole consciousness.
+They may be part of a more extended consciousness.
+In order to find whole or entire consciousnesses we can use the algorithm in \citet{krakauer2014information, krakauer2020information}.
+This algorithm adds variables to or removes variables from the system if this results in a reduction of transfer entropy from the corresponding environment.
+This means that whole consciousnesses are maximally closed subsets of variables.
+We currently do not know if such maxima also are maxima of NTIC.
+We also currently do not know whether multiple such whole consciousnesses can overlap or not and will accept either case within ICT.
+In this way either exclusion emerges from our definitions or not.
+
+            % if a subset is not informationally closed the subset is considered as a part of the system.
+            % ICT applies the same notion to consciousness.
 A subprocess (partition) of a conscious (NTIC) process can have a positive value of NTIC, and therefore, is conscious.
@@
 \\
-            This is also why ICT allowed the existence of multiple consciousnesses across the scale of coarse-graining.
+            This is also why ICT allowed the existence of multiple consciousnesses across the scales of coarse-graining.
 Because conscious processes are informationally closed from each other across the scale of coarse-graining, they are not able to know the existence of other consciousnesses within the same system (information flow from other processes is zero).
@@
 \\
-            Therefore, ICT without exclusion criterion can parsimoniously explain the individuality of consciousness within and across the scale of coarse-graining.
+            % Therefore, ICT without exclusion criterion can parsimoniously explain the individuality of consciousness within and across the scale of coarse-graining.
             \todo{Maybe add something in the manuscript}
@@
         \begin{ans}
-            \todo{camera}
-        	\todo{Everything I want to say is here. Just hard to make these pieces into a whole. Feel frustrated. }
+        	The reviewer is right.
+Feed-forward networks can be conscious under ICT.
+Similarly, a video camera can achieve positive levels of NTIC and, therefore, be conscious.
+We have worked extensively on Section 5 to make this clear (see from Line:~\lineref{line:notIC}).
+        	There we have weakened multiple claims involving a clear conscious to unconscious distinction to claims about differences between levels of consciousness. 
+        	Concerning the camera example we can show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image and the next there are systems that achieve higher NTIC.
+        	For the case of the feedforward network we speculate that a similar situation remains true and that there are always systems that achieve higher levels of consciousness than those consisting only of feedforward networks.
 
-		    @ The reviewer is correct about the example of the video camera under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.
+    %     	Please note that
 
-		    @ In such case, simply copying the environmental states to another process (assuming that the sensor of the video camera can capture the whole state of the environment) can lead to positive NTIC.
+		  %  @ The reviewer is correct about the example of the video camera under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.
 
-		    @ This is, in fact, the "Passive adaptation" case mentioned in \cite[p.~4]{BERTSCHINGER.2006},	
-		    \begin{quote}
-			      	\textit{"B1)~Passive adaptation: The system is driven by the environment and adapts passively to all changes in the environment.
+		  %  @ In such case, simply copying the environmental states to another process (assuming that the sensor of the video camera can capture the whole state of the environment) can lead to positive NTIC.
+
+		  %  @ This is, in fact, the "Passive adaptation" case mentioned in \cite[p.~4]{BERTSCHINGER.2006},	
+		  %  \begin{quote}
+			 %     	\textit{"B1)~Passive adaptation: The system is driven by the environment and adapts passively to all changes in the environment.
 In the case of an environment, that appears deterministic to the system, $H(\hat{e}_{n+1} |\hat{e}_n)=0$, this can be achieved by simply copying the observation of the environment into the system, $S_{n+1} = \hat{e}_n$."}
-		    \end{quote}
+		  %  \end{quote}
 
-	    @ The reviewer is correct about the video camera example under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.
+	   % @ The reviewer is correct about the video camera example under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.
 
-	    @ In such case, simply copying environmental states to a process can lead to positive NTIC.
+	   % @ In such case, simply copying environmental states to a process can lead to positive NTIC.
 
-	    @ In fact, this is one way to achieve NTIC discribed in \cite[p.~4]{BERTSCHINGER.2006},    
-	    \begin{quote}
-	    	\textit{"B1)~Passive adaptation: The system is driven by the environment and adapts passively to all changes in the environment.
+	   % @ In fact, this is one way to achieve NTIC discribed in \cite[p.~4]{BERTSCHINGER.2006},    
+	   % \begin{quote}
+	   % 	\textit{"B1)~Passive adaptation: The system is driven by the environment and adapts passively to all changes in the environment.
 In the case of an environment, that appears deterministic to the system, $H(\hat{e}_{n+1} |\hat{e}_n)=0$, this can be achieved by simply copying the observation of the environment into the system, $S_{n+1} = \hat{e}_n$."}
-	    \end{quote}
+	   % \end{quote}
 
-	    @ We can also consider this is a special case of modelling the environment when a system has enough sensory and memory capacities, and, therefore, can virtually model the environment by simply copying the environmental states into the system.
+	   % @ We can also consider this is a special case of modelling the environment when a system has enough sensory and memory capacities, and, therefore, can virtually model the environment by simply copying the environmental states into the system.
 
-	    @ Because this question point to the core concept of ICT, we would like to clarify and emphasise two critical points here.
+	   % @ Because this question point to the core concept of ICT, we would like to clarify and emphasise two critical points here.
 
-	    @ a) Informational closure and causation: The definition of information closure \citep{BERTSCHINGER.2006} does not involve causation.
+	   % @ a) Informational closure and causation: The definition of information closure \citep{BERTSCHINGER.2006} does not involve causation.
 As described in \cite{BERTSCHINGER.2006}, NTIC can be achieved via "modelling" or "passive adaptation".
@@
 
-	    The latter case may be conceptually counterintuitive because the internal state of the system (e,g, the video camera) is entirely driven by external input.
+	   % The latter case may be conceptually counterintuitive because the internal state of the system (e,g, the video camera) is entirely driven by external input.
 However, it is crucial to know that both cases lead the information flow $J(E\rightarrow Y)$ to (virtually) zero.
@@
 
-	    However, this is the most critical consequence of solving the scale problem of consciousness in ICT.
+	   % However, this is the most critical consequence of solving the scale problem of consciousness in ICT.
 In physical reality, there only exists microscopic processes at the finest microscopic level.
@@
 
-	    @ b) As described in our manuscript, to form a higher level of NTIC, the informational richness of the environment, i.e.
+	   % @ b) As described in our manuscript, to form a higher level of NTIC, the informational richness of the environment, i.e.
 $H(E)$ also has to be higher since $H(E_t)$ and $H(Y_{t+1})$ both are the upper bound of $I(Y_{t+1}; H(E_t))$.
@@
 However, we want to emphasise that not all the processes in the neural system are NTIC.
-This is trivial since some processes are evidently not informationally closed.
+Some processes in the neural system are not informationally closed.
 They mainly passively react to sensory inputs or other processes in the neural system.
@@
 %			In our hypothesis, $Y$ is IC with respect to the microstate of the universe, X.
-This is critical in the hypothesis because $Y$ is IC with respect to X, implying that $Y$ is also IC with respect to its intermediate level S and its environment E in Fig.
+This is critical in the hypothesis because $Y$ is IC with respect to X, implying that $Y$ is also IC with respect to its intermediate level S and its environment $E$ in Fig.
 \ref{fig:fullgraph}.\todo{need any change in the main text?}
@@
 Therefor, processes at certain levels of coarse-graining in the neural system can form high degrees of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
-\ac{OurTheory} indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
+ICT indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
 		}
-            % 		We thank the reviewer for this critical comment.
-It is true that NTIC a monotonic function of scales of coarse-graining.
-NTIC can increase or decrease when the grains are coarser.
-We are currently still working on the relationship between scales and NTIC.
-We will systematically address NTIC and functions of coarse-graining in our following studies.
-Further more, in our current analysis, it seems that this is also related to informational synergy and redundancy.
-We aim for presenting the core concept of ICT in this article.
-The reviewer's critical question is on our list of future work.
     	\end{ans}

### 2020-04-07 ICT_Frontiers_rev202001.tex
Updates from Overleaf

@@
 
+\newcommand{\X}{\mathcal{X}}
+\renewcommand{\S}{\mathcal{S}}
+\newcommand{\E}{\mathcal{E}}
+\DeclareMathOperator*{\argmax}{arg\,max}
 % ============================================================================ %
@@
 Generally, information at lower levels is more fine-grained and can be coarse-grained in higher levels.
-However, information processed only at specific levels seems to be available for conscious awareness.
-We do not have direct experience of information available at the level of individual neurons, which is noisy and highly stochastic.
-Neither do we have experience of more macro-level interactions such as interpersonal communications.
+However, information processed only at specific scales of coarse-graining seems to be available for conscious awareness.
+We do not have direct experience of information available at the scale of individual neurons, which is noisy and highly stochastic.
+Neither do we have experience of more macro-scale interactions such as interpersonal communications.
 Neurophysiological evidence suggests that conscious experiences co-vary with information encoded in coarse-grained neural states such as the firing pattern of a population of neurons.
 In this article, we introduce a new informational theory of consciousness: \acf{OurTheory}.
-We hypothesise that conscious processes are processes which form \ac{ntic} with respect to the environment at certain coarse-grained levels.
-This hypothesis implies that conscious experience is confined due to informational closure from conscious processing to other coarse-grained levels.
+We hypothesise that conscious processes are processes which form \ac{ntic} with respect to the environment at certain coarse-grained scales.
+This hypothesis implies that conscious experience is confined due to informational closure from conscious processing to other coarse-grained scales.
 \ac{OurTheory} proposes new quantitative definitions of both conscious content and conscious level.
@@
 		It seems to be true that we are not consciously accessing information processed at every scale in the neural system.
-There are both more microscopic and more macroscopic levels than the level corresponding to the conscious contents.
+There are both more microscopic and more macroscopic scales than the scale corresponding to the conscious contents.
 On the one hand, dynamics of individual neurons are stochastic \citep{Goldwyn2011, White2000}.
@@
 		In the following, we first introduce non-trivial informational closure and argue for its importance to information processing for human scale agents (Sec.\ref{sec:Non-trivial informational closure}).
-We next argue that through coarse-graining the neural system can form a high degree of NTIC at a specific coarse-grained level (Sec.\ref{sec:Neural coarse-graining}).
+We next argue that through coarse-graining the neural system can form a high degree of NTIC at a specific coarse-grained scale (Sec.\ref{sec:Neural coarse-graining}).
 In the Sec.\ref{sec:OurTheory}, we propose a new theory of consciousness (\ac{OurTheory}).
@@
 NTIC requires the predictability of the system state and is therefore impeded by noise in the system.
-Information processing at the microscopic levels (the cellular levels) in neural systems suffers from multiple environmental noise sources such as sensor, cellular, electrical, and synaptic noises.
-For example, neurons exhibit large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
+Information processing at the microscopic scales (the cellular scale) in neural systems suffers from multiple environmental noise sources such as sensor, cellular, electrical, and synaptic noises.
+For example, neurons exhibit large trial-to-trial variability at the cellular scale, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
 
         %% Our argument
-		However, it is possible that neural systems form NTIC at certain macroscopic levels through coarse-graining of microscopic neural states.
+		However, it is possible that neural systems form NTIC at certain macroscopic scales through coarse-graining of microscopic neural states.
 Coarse-graining refers to many-to-one or one-to-one maps which aggregate microscopic states to a macroscopic state.
@@
 
-		Indeed, empirical evidence suggests that coarse-graining is a common coding strategy to establish robustness against noise at microscopic levels of the neural system.
+		Indeed, empirical evidence suggests that coarse-graining is a common coding strategy to establish robustness against noise at microscopic scales of the neural system.
 For instance, the inter-spike intervals of an individual neuron are stochastic.
@@
 That is, stable representations can be formed through coarse-graining the high dimensional state space of a neuron population to a lower dimensional macroscopic state space \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
-Therefore, individual neuron states (the microscopic level) are not informative enough about the complete encoded contents at the population level (the macroscopic level).
-Instead, coarse-grained variables are better substrates for stably encoding information and allow the neural system to ignore noisy interactions at the fine-grained level \citep{Woodward2007-WOOCWA}.
+Therefore, individual neuron states (the microscopic scale) are not informative enough about the complete encoded contents at the population scale (the macroscopic scale).
+Instead, coarse-grained variables are better substrates for stably encoding information and allow the neural system to ignore noisy interactions at the fine-grained scale \citep{Woodward2007-WOOCWA}.
 
         These two examples show that the known coding schemes can be viewed as coarse-graining, and provide stochastic neural systems with the ability to form more stable and deterministic macroscopic processes for encoding and processing information reliably.
-We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic levels.
+We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic scales.
 Based on the merit of coarse-graining in neural systems, we propose a new theory of consciousness in the next section.
@@
 The dashed lines represents virtual dependencies between  two macroscopic variables.
-The red $Y_t$, $Y_{t+1}$, and the red dashed line in between represents a macroscopic process which forms informational closure at a certain coarse-grained level.}
+The red $Y_t$, $Y_{t+1}$, and the red dashed line in between represents a macroscopic process which forms informational closure at a certain coarse-grained scale.}
 			\label{fig:fullgraph}
@@
 
+    %     \begin{definition}
+    %     Given a stochastic process $X$ called the universe process, a \emph{C-process} is a coarse-graining $Y$ of $X$ such that the following two conditions are satisfied (see Fig.~\ref{fig:fullgraph}):
+    %     \begin{enumerate}
+    %     \item $Y$ is informationally closed to $X$
+    %     \item there exists a pair $(S,E)$ of coarse-grainings of $X$ called the \textit{system} $S$ and its \textit{environment} $E$  such that 
+    %     \begin{itemize}
+    %         \item $Y$ is a coarse-graining of $S$,
+    %         \item the state space $\mathcal{X}$ of $X$ is equal to the Cartesian product of the state spaces $\mathcal{S}$ and $\mathcal{E}$ of processes $S$ and $E$ respectively, formally $\mathcal{X}=\mathcal{S}\times\mathcal{E}$, and
+    %         \item $E$ is the environment process of $S$ with respect to which $Y$ is maximally NTIC:
+    %         \begin{align}
+    %         f_E:=\argmax_{\{\E||\E|\leq |\X|\},g:\X \rightarrow \E} NTIC(g(X)\rightarrow Y) \end{align}
+    %     %     $Y$ is NTIC to $E$, formally:
+    %     % \begin{align}
+    %     %     NTIC_t(E\rightarrow Y) >0
+    %     % \end{align}
+    %     \end{itemize} 
+    %     \end{enumerate}
+    %   \end{definition}
+
         \linelabel{line:IC2CG}
+		Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) 
+		\begin{align}
+		    J_{t}(E \rightarrow Y )=I(Y_{t+1};E_t|Y_t)
+		\end{align}
+		to the system-environment dependency
+         and the micro-macro scale dependency
+         \begin{align}
+		    J_{t}(X \rightarrow Y )=I(Y_{t+1};X_t|Y_t)
+		\end{align}  
+         even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).
+
         With the two definitions we can state the main hypothesis of \ac{OurTheory}
-        \footnote{Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) and informational closure (Eq.~\ref{eq:informationflow2}) to the system-environment dependency (e.g.
-$J_{t}(E \rightarrow Y )=0$) and the micro-macro level dependency (e.g.
-$J_{t}(X \rightarrow Y )=0$), even though the Bayesian graphs are different between the two scenarios.
-This follows the common settings in previous studies (e.g.
-\cite{BERTSCHINGER.2006, PFANTE.2014}).}:
-
         \begin{hypothesis}
@@
 
-        A concrete example in the context of neuroscience is that $X$ represents the microscopic level of the universe, $S$ a cellular level process in the neural system, $Y$ a more macroscopic process of the neural system coarse-grained from the cellular level process $S$, and $E$ the environment which the cellular level process $S$ interacts with.
+\begin{hypothesis}
+        For any coarse-graining $Y$ of a stochastic process $X$, a refinement $S$ of $Y$ and the environment $E$ of $S$.  
+        The \emph{content $C_t^{Content}(Y)$ of the consciousness of $Y$ at time $t$} is the state $y_t$ of $Y$ at time $t$ and \emph{the level $C_t^{Level}(Y)$ of the consciousness of $Y$} is the degree of NTIC of the C-process to the environment minus the information flow from the microscopic process $X$ to $Y$:
+        \begin{align}
+            C_t^{Content} &= y_t \label{eq:cContent}\\
+            C_t^{Level} &= NTIC_t(E\rightarrow Y)-J_t(X \rightarrow Y) \label{eq:cLevel}
+        \end{align}
+        \end{hypothesis}
+
+        A concrete example in the context of neuroscience is that $X$ represents the microscopic scale of the universe, $S$ a cellular scale process in the neural system, $Y$ a more macroscopic process of the neural system coarse-grained from the cellular scale process $S$, and $E$ the environment which the cellular level process $S$ interacts with.
 \linelabel{line:neu-env} The environment $E$ may include other processes in the neural system, the sensors for perception and interoception, and external physical worlds.\\
@@
 To be informationally closed with respect to $X$, no coarse-graining knows anything about the conscious process' future that the conscious process does not know itself.
-This self-determining characteristics is also in line with our daily life conscious experience which often shows stability and continuity and is ignorant of the stochasticity (e.g., noise) of the cellular levels.
+This self-determining characteristics is also in line with our daily life conscious experience which often shows stability and continuity and is ignorant of the stochasticity (e.g., noise) of the cellular scales.
 
@@
     	    %% not monotonic
-    		\linelabel{line:non-monotonic}It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining\footnote{We have known that NTIC is not a non-monotonic function of the scale of coarse-graining.
+    		\linelabel{line:non-monotonic}It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining
+    % 		\footnote{We have known that NTIC is not a non-monotonic function of the scale of coarse-graining.
 However, we currently have limited understanding about this relationship.
 Future work is needed and may involve relevant informational techniques (e.g.,partial information decomposition).}.
-At the finest scale, when we consider the dynamics of the whole universe as a process, the universe should be an informationally closed.
-However, there exists no environment to the universe and, therefore, NTIC of the universe is zero (trivially closed).
-On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC.
-For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any informational capacity and thus cannot have  mutual information between adjacent time steps.
-Therefor, processes at certain levels of coarse-graining in the neural system can form high degrees of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
-\ac{OurTheory} indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
+    		At the finest scale we consider the whole universe $X$ as the process $Y$. then, since $Y$ is a coarse graining of $S$ we have $Y=S=X$.  
+    % 		the universe should be informationally closed. 
+    		In this case the environment $E$ corresponding to the universe seen as a system is the constant coarse-graining\footnote{Recall that, for a system with state space $\S$ the environment state space $\E$ must be such that $\X=\S \times \E$.
+I $\S =\X$ then we need $\E$ with $\X \times \E=\X$ such that $\E$ must be a singleton set.
+All coarse-grainings mapping $\X$ to a singleton set are constant over $\X$.} and therefore the mutual information $I(E_t;Y_{t+1})=0$ and the transfer entropy $I(Y_{t+1};E_t|Y_t)$ are zero.
+Then NTIC of the universe with respect to its environment is zero and $X$ can never be a C-process.
+    % 		For simplicity let us assume that we choose $Y=S$ in the following as well. This lets
+
+    		If we now increase the scale of $Y$, this allows $S$ to also reduce in scale and therefore $E$ can become more and more fine-grained.
+This means that the mutual information $I(E_t;Y_{t+1})$ between $E$ and $Y$ can at least potentially become positive.
+Up to the point where $E$ accounts for half of the bits of $X$ and $S$ for the other half (and we have $Y=S$) the maximally possible mutual information $I(E_t;Y_{t+1})$ increases.
+Even further refining $E$ then again leads to a reduction of the maximally possible $I(E_t;Y_{t+1})$.
+
+            % ==================================== %
+            %    WHY DO WE NEED the FUCKING $Y$    %
+            % ==================================== %
+            % 2020/04/07 01:57
+    		% Why does Definition 2 have a fucking $Y$?
+It seems the whole thing could be defined wihtout referring to the underlying $S$ and directly use $Y$'s own environment (together with which it corresponds to $X$).
+We would always have a refinement of $Y$ that could be called $S$ to gether with its environment.
+But this is alwyas the case so it doesn't restrict the definition of $Y$ at all.
+(Especially if we can just choose $S=Y$).
+The only thing that makes the current definition of $Y$ more general is that it may be that $Y$ is only closed with respect to a coarsening of its own environment and not to its own environment itself.
+This is a waekening of the restriction compared to requiring that $Y$ be NTIC with respect to its own environment and IC with respect to $X$.
+Actually no, since $Y$ is IC with respect $X$ it is IC with respect to everything including to any coarsening of its own environment.
+Since the mutual information between $Y$ and its environment is greater or equal to the mutual information between $Y$ and a coarsening of its environment $Y$ must also be NTIC with respect to its own environment.
+    		% ==================================== %
+
+    		On the other extreme, when $E=X$ the system state space must be the singleton set and NTIC from $E$ to $Y$ must again be zero.
+Therefore, processes at certain scales of coarse-graining in the neural system can form high degrees of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
+\ac{OurTheory} indicates that human consciousness occurs at the scale of coarse-graining where higher NTIC is formed within the neural system.
 
     		\begin{figure}[H]				
-        		\includegraphics[width=\textwidth]{WritingMaterials/Fig_nonMono/nonMono.pdf}
-        		\caption{A non-monotonic relationship between Level of coarse-graining and level of consciousness.}
+        		\includegraphics[width=\textwidth]{Submission/Frontiers/nonMono.pdf}
+        		\caption{A non-monotonic relationship between scale of coarse-graining and level of consciousness.}
         		\label{fig:LevelOfConsciousness}
@@
 Thus, a macroscopic NTIC process can be ignorant to its microscopic states.
-\ac{OurTheory} argues that human conscious contents do not reflect cellular level activity because the conscious process which corresponds to a macroscopic NTIC process is informationally closed to the cellular level in the human neural system.
+\ac{OurTheory} argues that human conscious contents do not reflect cellular scale activity because the conscious process which corresponds to a macroscopic NTIC process is informationally closed to the cellular scale in the human neural system.
 Further more, since NTIC processes are informationally closed, each of them can be considered as a reality.
@@
 Here, we illustrate two distinctive scenarios which shade light of the relationship between informational closure and consciousness.
-
             % \paragraph{@ Martin's version}
@@
         \subsection{Multilevel Views on Consciousness and Cognition}\label{sec:MultiLevelView}
-    		\ac{OurTheory} proposes that conscious processes can occur at any level of coarse-graining which forms NTIC within a system.
+    		\ac{OurTheory} proposes that conscious processes can occur at any scale of coarse-graining which forms NTIC within a system.
 This suggests that the scale of coarse-graining is critical for searching and identifying the information corresponding to consciousness.
@@
 
-    		Here, we want to make clear that the "level" in \ac{OurTheory} refers to the \textbf{levels of coarse-graining} instead of the "level" for the cortical anatomy or sensory processing.
+    		Here, we want to make clear that the "level" in \ac{OurTheory} refers to the \textbf{scales of coarse-graining} instead of the "level" for the cortical anatomy or sensory processing.
 It is important to note that the coarse-graining direction is an orthogonal dimension irrespective of the level of anatomy or the level of information processing hierarchy in the neural system (see Fig.~\ref{fig:hierarchy}).
@@
 The exclusion axiom should be applied over elements, space, time, and scales \citep{oizumi2014phenomenology, hoel2016can}.
-\linelabel{line:multi-consciousness}Different from IIT, \ac{OurTheory} allows multiple consciousnesses coexist across different levels of coarse-graining within a system if they are informationally closed from each other.
+\linelabel{line:multi-consciousness}Different from IIT, \ac{OurTheory} allows multiple consciousnesses coexist across different scales of coarse-graining within a system if they are informationally closed from each other.
 The two distinctive predictions decisively pinpoint the core concepts of the two theories.
@@
 The macroscopic NTIC process only acquires the coarse-grained summary statistics of the microscopic processes.
-In other words, we predict that the computation of the statistical inferences of PP is implemented at microscopic (cellular) levels in the neural system.
+In other words, we predict that the computation of the statistical inferences of PP is implemented at microscopic (cellular) scales in the neural system.
 
@@
 Causal emergence is highly relevant to the relationship between informational closure and coarse-graining.
-In their new study by \cite{klein2019uncertainty}, they started to compare how different coarse-graining functions influence causal emergence at macroscopic levels.
+In their new study by \cite{klein2019uncertainty}, they started to compare how different coarse-graining functions influence causal emergence at macroscopic scales.
 \cite{PFANTE.2014, PFANTE.2014b} provides thorough mathematical analyses on level identification including informational closure.
@@
 \cite{Gamez2016} has also systematically described relevant issues in terms of finding data correlates of consciousness amount different levels of abstraction.
-We believe that interdisciplinary research is required to narrow down the scope of searching the coarse-graining functions and conscious processes at the coarse-grained levels in the neural system and beyond.
+We believe that interdisciplinary research is required to narrow down the scope of searching the coarse-graining functions and conscious processes at the coarse-grained scales in the neural system and beyond.
 
@@
     In this paper, we introduced \textbf{\acf{OurTheory}}, a new informational theory of consciousness.
-\ac{OurTheory} proposes that a process which forms \textbf{non-trivial informational closure (NTIC)} is conscious and through coarse-graining the neural system can form NTIC processes, i.e., conscious processes, at a certain macroscopic level.
+\ac{OurTheory} proposes that a process which forms \textbf{non-trivial informational closure (NTIC)} is conscious and through coarse-graining the neural system can form NTIC processes, i.e., conscious processes, at a certain macroscopic scales.
 \ac{OurTheory} considers that information is a common language to bridge the gap between conscious experience and the physical reality.
@@
     \ac{OurTheory} provides explanation for various findings from research of conscious and unconscious processing.
-The implications of \ac{OurTheory} point out that the levels of coarse-graining play a critical role in searching for neural substrates of consciousness.
+The implications of \ac{OurTheory} point out that the scales of coarse-graining play a critical role in searching for neural substrates of consciousness.
 Improper measurements, e.g., too fine or too coarse in terms of the scale of measurements, of neurophysiological signals may lead to misleading results and misinterpretations.
@@
 This explains why people might intuitively have a functionalist point of view of consciousness.
-\ac{OurTheory} emphasises that informational closure between levels of coarse-graining is critical to form NTIC processes in some stochastic systems.
-In this case, especially for the neural system, forming conscious processes at the macroscopic levels coincide with the perspective of emergentism.
+\ac{OurTheory} emphasises that informational closure between scales of coarse-graining is critical to form NTIC processes in some stochastic systems.
+In this case, especially for the neural system, forming conscious processes at the macroscopic scales coincide with the perspective of emergentism.
 Finally, forming NTIC (conscious) processes through many-to-one maps, i.e., coarse-graining, implies multiple realisability of consciousness.

### 2020-04-07 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
     		\newline
-    		a) Considering Eq.\ref{eq:NTIC2}, it is true that the transfer entropy term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$.
+    		a) It is true it is true that the information flow term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$.
+However, in Definition 2, a C-process is informationally closed to the microscopic universe process $X$.
+This implies C-process is also informationally closed to any other coarse-grainings of X including E (see also our reply to Q2.
+Therefore, only completely closed NTIC processes are consider as C-processes.
+    		Regarding the video camera example, please see more discussion in our reply to your Q6. \\
+
+    		% Backup 2020/04/07 14:23
+    		% ====================================
+            % 		a) Considering Eq.\ref{eq:NTIC2}, it is true that the transfer entropy term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$.
 It is possible to have a high degree of NTIC when $J_t(E\rightarrow Y) > 0$, i.e.
@@
 \\
-            % 		However, based on the setting in both Bertschinger et al.
-2006 and our Section 2 (at Line \lineref{line:r1q1a}), $Y_{t+1}$ is determined by both $Y_t$ and $E_t$.
-Simply increasing $I(Y_{t+1}; E_t)$ without closedness (e.g, copy the information in sensory signals to the process such as the case in the video camera example), the transfer entropy term $J_t(E -> Y)$ should increase at the same rate and cancel out the increment of $I(Y_{t+1}; E_t)$ resulting in low NTIC.
-Namely, keeping high closedness, i.e.
-minimising $J_t(E -> Y)$, is crucial to increase NTIC even though $J_t(E -> Y) > 0$.\\
-            % 		In our current version of ICT, we consider the level of consciousness corresponds to the degree of NTIC of a process. 
-            Therefore, a conscious process does not have to be completely closed. 
-            However, processes that manage to reduce the transfer entropy from the environment without reducing their mutual information with the environment achieve 
-            % higher degreed of closedness is crucial to have a
-            higher levels of consciousness. 
-            Regarding the video camera example, please see more discussion in our reply to your Q6. \\
+
+            %         Therefore, a conscious process does not have to be completely closed. 
+            %         However, processes that manage to reduce the transfer entropy from the environment without reducing their mutual information with the environment achieve higher levels of consciousness.
+            %         Regarding the video camera example, please see more discussion in our reply to your Q6. \\
+            % ====================================
 
@@
     	\begin{ans}
-    		We thank the reviewer for this question.
     		We agree that this point is not clear in our original manuscript.
@@
 
-    		This is a critical assumption in ICT because applying the same definition of informational closure in both scenarios can solve the scale problem of consciousness (informational closure from one level to other levels) and construct our hypothesis about the relation between NTIC and consciousness (informational closed from a process to its environment) in an integrated framework.
+    % 		This is a critical assumption in ICT because applying the same definition of informational closure in both scenarios can solve the scale problem of consciousness (informational closure from one level to other levels) and construct our hypothesis about the relation between NTIC and consciousness (informational closed from a process to its environment) in an integrated framework.
 
-    		In terms of the Bayesian graphs for the micro-macro level dependency and the definition of informational closure between scales, we followed the conventional setting (e.g.
+    % 		In terms of the Bayesian graphs for the micro-macro level dependency and the definition of informational closure between scales, we followed the conventional setting (e.g.
 \cite{PFANTE.2014}).
@@
 
-    		We agree that we did not indicate this assumption explicitly and may lead to some confusion for our readers. We have added a footnote to make this point explicit.
+    % 		We agree that we did not indicate this assumption explicitly and may lead to some confusion for our readers. 
+    		We have added a paragraph to make this point explicit.
 
     		\addnew{\lineref{line:IC2CG}}{
-    			Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) and informational closure (Eq.~\ref{eq:informationflow2}) to the system-environment dependency (e.g.
-$J_{t}(E \rightarrow $Y$ )=0$) and the micro-macro level dependency (e.g.
-$J_{t}(X \rightarrow $Y$ )=0$), even though the Bayesian graphs are different between the two scenarios.
-This follows the common settings in previous studies (e.g.
-\cite{BERTSCHINGER.2006, PFANTE.2014}).
+    			Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) 
+    			\begin{align}
+    			    J_{t}(E \rightarrow Y )=I(Y_{t+1};E_t|Y_t)
+    			\end{align}
+    			to the system-environment dependency
+                 and the micro-macro level dependency
+                 \begin{align}
+    			    J_{t}(X \rightarrow Y )=I(Y_{t+1};X_t|Y_t)
+    			\end{align}  
+                 even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).
     		}
@@
     	\begin{question}            
-    	\todo{I am rewriting this part, please wait}
     		On line 241: '..
@@
     	\begin{ans}
-    	We thank the reviewer for asking this question. We did not write this part clearly.
-
-    	It is true that at the finest scale, when we consider the whole universe as a system, the universe should be an informationally closed and deterministic process.
-However, there exists no environment to the universe and, therefore, NTIC of the universe is zero (trivially closed).We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining.
+    % 	It is true that at the finest scale, when we consider the whole universe as a system, the universe should be an informationally closed and deterministic process.
+However, there exists no environment to the universe and, therefore, NTIC of the universe is zero (trivially closed).
+    	We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining.
 However, we currently have very limited understanding of this relationship.
@@
 		{
-			It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining\footnote{We have known that NTIC is not a non-monotonic function of the scale of coarse-graining.
+			It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining\footnote{We know that NTIC is not a non-monotonic function of the scale of coarse-graining.
 However, we currently have limited understanding about this relationship.

### 2020-04-08 ICT_Frontiers_rev202001.tex
Updates from Overleaf

@@
 
-        \linelabel{line:IC2CG}
-		Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) 
+        \noindent Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) \linelabel{line:IC2CG}
         \begin{align}
@@
         \end{align}  
-         even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).
+        even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).\\
 
@@
         A process $Y$ is conscious if and only if it is a C-process of some process $X$.
-Also the content of consciousness $C_t^{Content}$ at time $t$ is the state $y_t$ of the C-process at time $t$ and the level of consciousness $C_t^{Level}$ is the degree of NTIC of the C-process to the environment i.e.
+Also the content of consciousness $C_t^{Content}$ at time $t$ is the state $y_t$ of the C-process at time $t$ and the level of consciousness $C_t^{Level}$ is the degree of NTIC of the process to the environment i.e.
 $NTIC_t(E\rightarrow Y)$:
@@
         \begin{hypothesis}
-        For any coarse-graining $Y$ of a stochastic process $X$, a refinement $S$ of $Y$ and the environment $E$ of $S$.  
-        The \emph{content $C_t^{Content}(Y)$ of the consciousness of $Y$ at time $t$} is the state $y_t$ of $Y$ at time $t$ and \emph{the level $C_t^{Level}(Y)$ of the consciousness of $Y$} is the degree of NTIC of the C-process to the environment minus the information flow from the microscopic process $X$ to $Y$:
+        A process $Y$ is conscious if and only if it is a C-process of some process $X$.
+Also the content of consciousness $C_t^{Content}$ at time $t$ is the state $y_t$ of the C-process at time $t$ and the level of consciousness $C_t^{Level}$ is the degree of NTIC of the process to the environment i.e.
+$NTIC_t(E\rightarrow Y)$:
         \begin{align}
             C_t^{Content} &= y_t \label{eq:cContent}\\
-            C_t^{Level} &= NTIC_t(E\rightarrow Y)-J_t(X \rightarrow Y) \label{eq:cLevel}
+            C_t^{Level} &= NTIC_t(E\rightarrow Y) \label{eq:cLevel}
         \end{align}
         \end{hypothesis}
+
+        % \begin{hypothesis}
+        %         For any coarse-graining $Y$ of a stochastic process $X$, a refinement $S$ of $Y$ and the environment $E$ of $S$.  
+        %         The \emph{content $C_t^{Content}(Y)$ of the consciousness of $Y$ at time $t$} is the state $y_t$ of $Y$ at time $t$ and \emph{the level $C_t^{Level}(Y)$ of the consciousness of $Y$} is the degree of NTIC of the C-process to the environment minus the information flow from the microscopic process $X$ to $Y$:
+        %         \begin{align}
+        %             C_t^{Content} &= y_t \label{eq:cContent}\\
+        %             C_t^{Level} &= NTIC_t(E\rightarrow Y)-J_t(X \rightarrow Y) \label{eq:cLevel}
+        %         \end{align}
+        %         \end{hypothesis}
 
@@
             \subsubsection*{Processes that are not Informationally Closed}\label{sec:reflexive}
-            \linelable{line:notIC}
+             \linelabel{line:notIC}The first scenario is that of a system partially observing the environment in such a way that the current observation is insufficient to predict the next.
+In this situation we can show that a system passively processing the observations (including copying them) achieves lower values of NTIC and therefore lower levels of consciousness than a system that is able to accurately predict the observations.
             % \paragraph{@ Acer's version}
@@
 In such cases, if the state of a internal process is mainly driven by sensory inputs, the information flow from the environment to the process is considered to be large and the process is not informationally closed.
-
             % First, to maximise NTIC, a process can minimise the information flow from the environment to the process $J_{t}(E \rightarrow Y ) := I(Y_{t+1};E_{t}|Y_{t})$ (Eq.~\ref{eq:InformationFlow}).
@@
             % \paragraph{@ Martin's version}
-            The first scenario is that of a system partially observing the environment in such a way that the current observation is insufficient to predict the next.
-In this situation we can show that a system passively processing the observations (including copying them) achieves lower values of NTIC and therefore lower levels of consciousness than a system that is able to accurately predict the observations.
-
             %Is there a (generative) epsilon machine that achieves higher NTIC than copying?

### 2020-04-08 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
 However, in Definition 2, a C-process is informationally closed to the microscopic universe process $X$.
-This implies C-process is also informationally closed to any other coarse-grainings of X including E (see also our reply to Q2.
+This implies C-process is also informationally closed to any other coarse-grainings of X including E (see also our reply to Q2).
 Therefore, only completely closed NTIC processes are consider as C-processes.
@@
 Note that closure with respect to $X$ (if it exists) implies closure with respect to every coarse-graining of $X$.
-            % For this We use the underlying $X$ with respect to $Y$ in order to illustrate the scale problem of consciousness. 
-            % It ensures that the information transfer from all coarse-grainings of $X$ to $Y$ vanishes.
-Therefore, human conscious experiences do not involve information from other scales of coarse-graining.
-            % 
             To see this note that the information transfer from any coarse-graining (including $E$ and $S$) of $X$ to $Y$ must be lower than that from $X$ to $Y$, i.e.
@@
 
+        process:$X$
+        p(x'|x):=\delta_{f(x)}(x')-\delta_{\X\backslash f(x)}(|\X|-1)*n
+        p(x'|x,n)=
+        then H(X'|X)=H(\Epsilon)
+
+        find g:\X \rightarrow \Y
+
+        such that H(g(X')|g(X))=0
+        but still H(g(X'))>0
         \begin{question}
@@
             We can see how Figure 4 was ambiguous with respect to this question. We do not impose the exclusion criterion in ICT and have changed Figure 4 to remove the impression that it does. 
-            % This is a difference between IIT and ICT. \\
-            % The exclusion criterion is based on the assumption that individual entities (e,g, consciousnesses) should share no subset with any other entities.
-Namely, within the boundary of an individual, we should not find any subset also belonging to other individuals.
-\\
             A key feature of ICT is that, instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of system-environment separation and a boundary of a system \citep{BERTSCHINGER.2006}.
@@
             It is true that NTIC can be computed for every subset of a system and can also have a positive value of NTIC for multiple of those.
-All such subsets are thus conscious.
-However, while conscious, they are not necessarily the entire or whole consciousness.
-They may be part of a more extended consciousness.
+However, according to our definition, if these processes are not informationally closed to their environments (including the complement subset in the system), ICT claims that they are not C-processes, and thus not conscious.
+.
 In order to find whole or entire consciousnesses we can use the algorithm in \citet{krakauer2014information, krakauer2020information}.
 This algorithm adds variables to or removes variables from the system if this results in a reduction of transfer entropy from the corresponding environment.
-This means that whole consciousnesses are maximally closed subsets of variables.
-We currently do not know if such maxima also are maxima of NTIC.
-We also currently do not know whether multiple such whole consciousnesses can overlap or not and will accept either case within ICT.
-In this way either exclusion emerges from our definitions or not.
+This means that consciousnesses are informationally closed subsets of variables.
 
-            % if a subset is not informationally closed the subset is considered as a part of the system.
-            % ICT applies the same notion to consciousness.
-A subprocess (partition) of a conscious (NTIC) process can have a positive value of NTIC, and therefore, is conscious.
-However, the subprocess is not "another conscious process".
-Instead, it is considered as a subspace of the consciousness.
-Namely, the information contributed from the subprocess corresponds to a part of the whole conscious experience.
-\\
             This is also why ICT allowed the existence of multiple consciousnesses across the scales of coarse-graining.
 Because conscious processes are informationally closed from each other across the scale of coarse-graining, they are not able to know the existence of other consciousnesses within the same system (information flow from other processes is zero).
-This is in line with using informational closure in level identification \citep{PFANTE.2014} .
-\\
-            % Therefore, ICT without exclusion criterion can parsimoniously explain the individuality of consciousness within and across the scale of coarse-graining.
-            \todo{Maybe add something in the manuscript}
-% 			We do not impose the exclusion criterion in ICT. Instead, the concept of informational closure already involves the notion of identifying the boundary of a system.
-
-% 			 system-environment distinction \citep{BERTSCHINGER.2006} and level identification \citep{PFANTE.2014}
-
-% 			That human consciousness constitutes a maximum is a conjecture at the moment.
-Humans are of course very good at predicting their future experiences and (apart from multiple humans together) we are not aware of systems that are better.
-This is the only reason why we think human consciousness constitutes a maximum.
-We accept that there can be many other overlapping conscious systems.
-Concerning multiple possible partitions, \citet{krakauer2014information} propose an algorithm to add and remove variables in order to find a maximum.
-This could be used to find a maximum and something like a boundary of the maximum.
-Maxima are of course interesting but we don't see why they should exclude anything.
-Instead, the concept of informational closure already involves the notion of individuality and was used to identify the system-environment distinction \citep{BERTSCHINGER.2006} and level identification \citep{PFANTE.2014} in systems theory (however not completely, please see our discussion at Line \lineref{line:individuality}).
-
-% 			It is true that if we assume a process $Y$ is NITC with respect to $E$.
-Every subset of $Y$ can have different degrees of NTIC with respect to $E$ as well.
-However, it is important to note that the subsets are not "other consciousnesses".
-Rather, they are subspaces of this conscious process $Y$.
-
-% 			\toWrite{I this this is still bad}
-
-%			\textit{If we sample a subset of elements, if its closedness is lower than 
-%			Consider a simplified case, a process $Y$ is NITC with respect to $E$. 
-%			For Any subset of 
-%			A partition of $Y$ is a set $P_y$ which divides $Y$ into two subsets $P_y=\{Y_1, Y_2\}$. }    		    		    		
+This is in line with using informational closure in level identification \citep{PFANTE.2014}.
     	\end{ans}
@@
 Feed-forward networks can be conscious under ICT.
+We thank the reviewer to correct this point.
 Similarly, a video camera can achieve positive levels of NTIC and, therefore, be conscious.
@@
 		  %  @ This is, in fact, the "Passive adaptation" case mentioned in \cite[p.~4]{BERTSCHINGER.2006},	
-		  %  \begin{quote}
-			 %     	\textit{"B1)~Passive adaptation: The system is driven by the environment and adapts passively to all changes in the environment.
-In the case of an environment, that appears deterministic to the system, $H(\hat{e}_{n+1} |\hat{e}_n)=0$, this can be achieved by simply copying the observation of the environment into the system, $S_{n+1} = \hat{e}_n$."}
-		  %  \end{quote}
-
-	   % @ The reviewer is correct about the video camera example under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.
-
-	   % @ In such case, simply copying environmental states to a process can lead to positive NTIC.
-
-	   % @ In fact, this is one way to achieve NTIC discribed in \cite[p.~4]{BERTSCHINGER.2006},    
 		  %  \begin{quote}
@@
     	\begin{ans}
-	    	We want to emphasise that not all the processes in the neural system are NTIC processes.
-This is evident since some processes in the neural system are not informationally closed.
-They only passively react to sensory inputs or other processes of the neural system.
-
+	    	We want to emphasise that not all the processes in the neural system are NTIC processes, since some processes in the neural system are not informationally closed.
 	    	To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment.
@@
 
-	    	Finally, we believe that this is also an
-	    	empirical question that can and should be tested in future studies.
+	    	Finally, we believe that this is also an empirical question that can and should be tested in future studies.
     	\end{ans}

### 2020-04-08 ICT_Frontiers_rev202001.tex
Changed Figure 2

@@
 				\begin{figure}
-					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv_2.pdf}
-					\caption{The dependencies between a system and its environment.} % Figure adapted from \cite{BERTSCHINGER.2006}
+					\includegraphics[width=\textwidth]{Submission/Frontiers/SystemAndEnv_3.pdf}
+					\caption{The dependencies between a system  $Y$ and its environment $E$ through the channels $\hat{y_t}$ and $\hat{e_t}$.} % Figure adapted from \cite{BERTSCHINGER.2006}
 					\label{fig:SystemAndEnv}

### 2020-04-10 ICT_Frontiers_rev202001.tex
Local update
Updates from Overleaf

@@
 
+			\subsection{Informational Closure and Causality}
+			A surprising result of the definition of information flow $Jt(E\rightarrow Y)$ (Eq. \ref{eq:InformationFlow}) is that it does not involve causal dependency between $E$ and $Y$.
+			Consider the case already noted by \citet{BERTSCHINGER.2006} where the sensory process $\hat{e_t}$ is deterministic (or close to it) and the system just copies the sensory states.
+Then the system can potentially achieve positive values of NTIC and informational closure with respect to the environment.
+			This scenario is called "passive adaptation" \citet{BERTSCHINGER.2006}.
+Counterintuitively, in such case, the future state is totally determined by the environment however, the information flow $Jt(E\rightarrow Y)$ is (or nearly) zero.
+
+			@ However, in more realistic cases, the environment is often partial obseriable. The system cannot copy the entire environment state because it observes only part of it.
+
+            We show in Appendix \ref{sec:appendix} that whenever the environment has itself more predictable dynamics than the observations there is potential for a predictive process to achieve higher NTIC than a copying system or any system that only processes its last observations without taking into account other internal memory.
+In this case is called "modelling" in \cite{BERTSCHINGER.2006}
+
+            In such case, the system can potentially achieve higher NTIC than simply copy the sensory value.
+
+            We can see both senatios are critical in ICT.
+
+            % Similar to \citet{BERTSCHINGER.2006} we will refer to systems of the latter type as \textit{passive}.
+We will call all other systems that achieve positive NTIC \textit{predictive}.
+Note that the predictive process might need to be more complex than the system that only copies its observations.
+
 % ============================================================================ %
@@
 
+    % ==================================== %
+    % martin.biehl: 
+    % doesn't work because the information closrue with respect to $X$ implies full closrure with respect to every 
+    % other process. This means all conscious processes are fully closed. This contradicts what we say below.
+    % Apr 7, 2020 3:23 AM
+    % ==================================== %
     %     \begin{definition}
@@
     %   \end{definition}
+    % ====================================%
 
@@
         With the two definitions we can state the main hypothesis of \ac{OurTheory}
-        \begin{hypothesis}
-        A process $Y$ is conscious if and only if it is a C-process of some process $X$.
-Also the content of consciousness $C_t^{Content}$ at time $t$ is the state $y_t$ of the C-process at time $t$ and the level of consciousness $C_t^{Level}$ is the degree of NTIC of the process to the environment i.e.
-$NTIC_t(E\rightarrow Y)$:
-        \begin{align}
-            C_t^{Content} &= y_t \label{eq:cContent}\\
-            C_t^{Level} &= NTIC_t(E\rightarrow Y) \label{eq:cLevel}
-        \end{align}
-        \end{hypothesis}
-
         \begin{hypothesis}
@@
     	    %% not monotonic
-    		\linelabel{line:non-monotonic}It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining
-    % 		\footnote{We have known that NTIC is not a non-monotonic function of the scale of coarse-graining.
-However, we currently have limited understanding about this relationship.
-Future work is needed and may involve relevant informational techniques (e.g.,partial information decomposition).}.
-    		At the finest scale we consider the whole universe $X$ as the process $Y$. then, since $Y$ is a coarse graining of $S$ we have $Y=S=X$.  
-    % 		the universe should be informationally closed. 
+    		\linelabel{line:non-monotonic}It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+At the finest scale we consider the whole universe $X$ as the process $Y$.
+then, since $Y$ is a coarse graining of $S$ we have $Y=S=X$.
 In this case the environment $E$ corresponding to the universe seen as a system is the constant coarse-graining\footnote{Recall that, for a system with state space $\S$ the environment state space $\E$ must be such that $\X=\S \times \E$.
@@
 Then NTIC of the universe with respect to its environment is zero and $X$ can never be a C-process.
-    % 		For simplicity let us assume that we choose $Y=S$ in the following as well. This lets
 
@@
 Even further refining $E$ then again leads to a reduction of the maximally possible $I(E_t;Y_{t+1})$.
-
             % ==================================== %
@@
 This implication is also in line with the intuition in which consciousness is often associated with complex systems.
-
-            % ---------------------------------------------------------------------------- %
-            %                              Dynamical Boundary                              %
-            % ---------------------------------------------------------------------------- %
-            % \subsection{Dynamical Boundary}
-            % Our theory predicts that the boundary of a conscious system is dynamical.
-The boundary is determined by the NTIC process.
-This implies that when the structure of interaction between variables changes the physical boundaries supporting consciousness should also change.
-If some coarse-grained variables encode environmental information, they may become necessary components to form high NTIC.
-In such case, these coarse-grained variables are "recruited" inside the boundary of conscious processes.
-Note that, due to synergistic information, even recruiting some new variables may largely increase the level of NTIC.
-            % This may explain why consciousness is tightly associated with binding and integration of information in human perception and cognition.
-Another crucial implication is that the same neural substrates may not be always involved in conscious processing rather it depends on whether it creates high NTIC with other members in the neural system.
-\needfig{Maybe I need a figure here as well}
 

### 2020-04-15 ICT_Frontiers_rev202001.tex
Updates from Overleaf

@@
+% Three major changes
+% 1. 2.1
+% 2. 4.1  non-monotonic 
+% 3. 5.1 Processes that are not Informationally Closed
+% 4. appendix
+
+% todo
+% ------------------------------------
+% unpredictable sensory 
+% As mentioned above, informational closure can happen between scales of coarse-graining within a single system.....
+
 \documentclass[utf8]{article}
@@
 			This implies the system contains in itself all the information about its own future and the self-predictive information contains the information about the environment.
-Therefore, to form NTIC, the system can internalise and synchronise with the dynamics of the environment, e.g., model the environment.
-Furthermore, having high degrees of NTIC entails having high predictive power about the environment.
-This gives biological agents a great functional and evolutionary advantage.
-
-			\subsection{Informational Closure and Causality}
-			A surprising result of the definition of information flow $Jt(E\rightarrow Y)$ (Eq. \ref{eq:InformationFlow}) is that it does not involve causal dependency between $E$ and $Y$.
-			Consider the case already noted by \citet{BERTSCHINGER.2006} where the sensory process $\hat{e_t}$ is deterministic (or close to it) and the system just copies the sensory states.
-Then the system can potentially achieve positive values of NTIC and informational closure with respect to the environment.
-			This scenario is called "passive adaptation" \citet{BERTSCHINGER.2006}.
-Counterintuitively, in such case, the future state is totally determined by the environment however, the information flow $Jt(E\rightarrow Y)$ is (or nearly) zero.
-
-			@ However, in more realistic cases, the environment is often partial obseriable. The system cannot copy the entire environment state because it observes only part of it.
-
-            We show in Appendix \ref{sec:appendix} that whenever the environment has itself more predictable dynamics than the observations there is potential for a predictive process to achieve higher NTIC than a copying system or any system that only processes its last observations without taking into account other internal memory.
-In this case is called "modelling" in \cite{BERTSCHINGER.2006}
-
-            In such case, the system can potentially achieve higher NTIC than simply copy the sensory value.
-
-            We can see both senatios are critical in ICT.
-
-            % Similar to \citet{BERTSCHINGER.2006} we will refer to systems of the latter type as \textit{passive}.
-We will call all other systems that achieve positive NTIC \textit{predictive}.
-Note that the predictive process might need to be more complex than the system that only copies its observations.
+
+			\subsection{Informational Closure Does not Imply Causality}\label{sec:causality}
+                A surprising (but well known; see ???) result from the definition of information flow $J_t(E\rightarrow Y)$ (Eq.
+\ref{eq:InformationFlow}) is that information flow does not indicate causal dependency from $E_t$ to $Y_{t+1}$ and from $Y_t$ to $Y_{t+1}$.
+Here we consider two scenarios, called "modelling" and "passive adaptation", which were already noted by \citet{BERTSCHINGER.2006}.
+In both scenarios, a process can form positive NTIC ($NTIC(E\rightarrow Y)> 0$) and informational closure ($J(E\rightarrow Y)=0$), however, via different causal dependencies.
+
+                In the scenario of \textit{modelling}, to achieve positive NTIC and informational closure, a system can internalise and synchronise with the dynamics of the environment, e.g., model the environment.
+In this case, the future internal state $Y_{t+1}$ of the system is driven by the current internal state $Y_t$ and the system still retains mutual information with the environment.
+Having high degrees of NTIC then entails having high predictive power about the environment.
+This gives biological agents functional and evolutionary advantages.
+
+                In the scenario of \textit{passive adaptation}, counterintuitively, the future system states ($Y_{t+1}$) are  entirely driven by the current environment states ($E_t$) but can also have positive NTIC and informational closure.
+This happens under the condition that the sensory process $\hat{e}_t$ is deterministic and the system simply copies the sensory values.
+The system is then a copy of another informationally closed process ($\hat{e}_t$) and is therefore closed itself.
+At the same time it has mutual information with the process that it is copying.
+
+                However, in most of the realistic cases, the environment is partially observable to the system and, thus, the sensory process is usually not deterministic.
+Therefore, it is difficult for the system to be informationally closed and have higher NTIC.
+                More importantly, we argue in Appendix \ref{sec:appendix} that whenever the environment has itself more predictable dynamics than the observations, there is potential for a process to achieve higher NTIC by modelling the environment than by copying the observations.
+
+                We will see that both scenarios are relevant to ICT in the following sections.
 
@@
 NTIC requires the predictability of the system state and is therefore impeded by noise in the system.
-Information processing at the microscopic scales (the cellular scale) in neural systems suffers from multiple environmental noise sources such as sensor, cellular, electrical, and synaptic noises.
+Information processing at the microscopic scale (the cellular scale) in neural systems suffers from multiple environmental noise sources such as sensor, cellular, electrical, and synaptic noises.
 For example, neurons exhibit large trial-to-trial variability at the cellular scale, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
@@
         \end{align}  
-        even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).\\
+        even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).\\\\
 
@@
 
+        % ====================================
+        % Refinement construction approach
+        % ====================================
         % \begin{hypothesis}
@@
         %         \end{hypothesis}
+        % ====================================
 
@@
 
-            %In \ac{OurTheory}, we consider information is the common language between conscious experience and the physical reality.
-This means that consciousness is fundamentally associated with information \citep{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}).
-
             \item[Implication 3.] 
@@
     	    Second, one can minimise the conditional mutual information $I(Y_{t+1};Y_{t}|E_{t})$ to increase the level of NTIC.
-This quantity suggests that conscious level increases with the amount of information about the environment state $E_t$ that the NTIC process encodes in its own state $Y_t$.
+If the mutual information term $I(Y_{t+1};Y_t)$ is supposed to stay large, this quantity suggests that conscious level increases with the amount of information about the environment state $E_t$ that the NTIC process encodes in its own state $Y_t$ and $Y_{t+1}$.
 In other words, $Y_t$ should not contain more information about $Y_{t+1}$ than $E_t$.
@@
 In this case the environment $E$ corresponding to the universe seen as a system is the constant coarse-graining\footnote{Recall that, for a system with state space $\S$ the environment state space $\E$ must be such that $\X=\S \times \E$.
-I $\S =\X$ then we need $\E$ with $\X \times \E=\X$ such that $\E$ must be a singleton set.
-All coarse-grainings mapping $\X$ to a singleton set are constant over $\X$.} and therefore the mutual information $I(E_t;Y_{t+1})=0$ and the transfer entropy $I(Y_{t+1};E_t|Y_t)$ are zero.
+If $\S =\X$ then we need $\E$ with $\X \times \E=\X$ such that $\E$ must be a singleton set.
+All coarse-grainings mapping $\X$ to a singleton set are constant over $\X$.} and therefore the mutual information $I(E_t;Y_{t+1})$ and the transfer entropy $I(Y_{t+1};E_t|Y_t)$ are zero.
 Then NTIC of the universe with respect to its environment is zero and $X$ can never be a C-process.
@@
 This means that the mutual information $I(E_t;Y_{t+1})$ between $E$ and $Y$ can at least potentially become positive.
-Up to the point where $E$ accounts for half of the bits of $X$ and $S$ for the other half (and we have $Y=S$) the maximally possible mutual information $I(E_t;Y_{t+1})$ increases.
-Even further refining $E$ then again leads to a reduction of the maximally possible $I(E_t;Y_{t+1})$.
+Up to the point where $E$ accounts for half of the bits of $X$ and $S$ for the other half the upper bound of the mutual information $I(E_t;Y_{t+1})$ achieved when $Y=S$ increases.
+Even further refining $E$ then again leads to a reduction of the upper bound of $I(E_t;Y_{t+1})$.
             % ==================================== %
@@
     		On the other extreme, when $E=X$ the system state space must be the singleton set and NTIC from $E$ to $Y$ must again be zero.
-Therefore, processes at certain scales of coarse-graining in the neural system can form high degrees of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
+Therefore, processes at intermediate scales of coarse-graining can form higher degrees of NTIC than at the most microscopic or macroscopic scales (Fig.~\ref{fig:LevelOfConsciousness}).
 \ac{OurTheory} indicates that human consciousness occurs at the scale of coarse-graining where higher NTIC is formed within the neural system.
@@
     	    While it is useful to distinguish the notion of the levels and contents of consciousness, whether they can be clearly dissociated has been a matter of debate \citep{bayne2016there, Fazekas2016}.
-In \ac{OurTheory}, conscious levels and conscious contents are just two different properties of NTIC processes, and, therefore, naturally reconciles the two aspects of consciousness.
+In \ac{OurTheory}, conscious levels and conscious contents are just two different properties of NTIC processes, and it therefore naturally reconciles the two aspects of consciousness.
 In an NTIC process with a large state space, conscious contents should also consist of rich and high dimensional information.
@@
         \subsection{Unconscious Processing}
-            Regarding unconscious processing, we highlight two scenarios which decrease the degree of NTIC of a process, thereby making the process less conscious.
+            In this section we highlight two scenarios in which ICT predicts that processes remain unconscious. 
+            % e or  decrease the degree of NTIC of a process, thereby making the process less conscious or unconscious.
 
             \subsubsection*{Processes that are not Informationally Closed}\label{sec:reflexive}
-             \linelabel{line:notIC}The first scenario is that of a system partially observing the environment in such a way that the current observation is insufficient to predict the next.
+                % ------------------------------------
+                % This section should follow:
+                % 1. Processes that are not informationally closed is unconscious
+                % 2. Some informationally not closed processes are passively driven by the environment (some examples)
+                % 3. This may give readers the impression that processes passively driven by the environment are all not informationally closed
+                % 4. This is a wrong impression because in a specific circumstance which the sensory processes are deterministic, passive adaptation can be informational closed.
+                % 5.
+However, 4 is difficult to get because in realistic cases, the environment is often partially observable and this leads to sensory processes being non-deterministic.
+Therefore, ICT predict that in most of the realistic cases, passive adaptation (e.g., feed-forward network, video camera) is unconscious.
+                % ------------------------------------
+                \linelabel{line:notIC} 
+                % To maximise NTIC, one can minimise the information flow $J_{t}(E \rightarrow Y )$ from the environment $E$ to the process $Y$ (Eq.~\ref{eq:InformationFlow},\ref{eq:nticObjective2}).
+When the information flow is zero, the process is informationally closed with respect to the environment.
+                The first scenario is built upon the assumption that sensor values are non-deterministic and the process dynamics are passively driven by the environmental inputs.
+Such processes cannot be informationally closed and are therefore unconscious.
+
+                % When the sensor processes are not deterministic, if processes dynamics is passively driven by the environmental inputs the process is not informationally closed and, thus, unconscious.
+
+                Reflexive behaviours \citep{casali2013theoretically} can be considered as an example of this scenario.
+In \ac{OurTheory}, if we can view reflexive behaviours as situations in which the internal state $Y_t$, which triggers reflexive action, is determined by the environment state $E_{t-1}$, overruling the influences from its own past $Y_{t-1}$.
+Such interpretation of reflexive behaviour from the viewpoint of \ac{OurTheory} naturally explains why reflexes involve less or no conscious experience of external stimuli.
+
+        		\begin{figure}[H]
+        			\includegraphics[width=0.8\textwidth]{Submission/Frontiers/Reflexive.pdf}
+        			\caption{
+        			    A diagram depicting the information flow in reflexive behaviours (shown by the red nodes and arrows) happening through the interaction between a process $Y$ and its environment $E$.
+In such situations, the internal state $Y_t$ is mostly dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$.
+Therefore, the process $Y$ is not informational closed.
+As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain less conscious or unconscious (see Fig.~\ref{fig:reflexive}).
+        			    }
+        			\label{fig:reflexive}
+        		\end{figure}
+
+                The same principle can be applied to interpret blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedural memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes.
+        		\linelabel{line:r2q6}Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.
+However, in some cases, they may still preserve some forms of conscious experience (see \cite{overgaard2011visual, mazzi2016blind}).
+We argue that blindsight-guided actions are a result of
+        		% action outputs of blindsight can be directly guided by sensory inputs through 
+        		stimulus-response mapping.
+The corresponding neural circuits are driven passively and therefore are not informationally closed.
+According to \ac{OurTheory} we therefore have no conscious experience of the visual stimuli.
+
+        		Similarly, for procedural memory, the state transitions of corresponding neural circuits determining the action sequences largely depend on  sensory inputs.
+This prevents the neural processes of procedural memory from informational closure and being conscious.
+        		\ac{OurTheory} also offers an interpretation as to why patients with visual apperceptive agnosia \citep{james2003ventral} can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.
+
+                Note that, not all processes that are driven by the environment (passive adaptation) are unconscious.
+When the sensor processes are deterministic, a system can still have positive NTIC and achieve informational closure via passive adaptation.
+Therefore, some passive system (for example pure feedforward networks) can potentially produce consciousness.
+
+                For agents such as human beings, the environment is often informationally rich but only partially observable in such a way that the current sensory inputs are insufficient to predict the next and to form deterministic sensor processes.
+In this circumstance, the system cannot become informationally closed by passive adaptation (e.g., simply copying the sensory values to the system).
+ICT predicts that, in most of the realistic cases, processes with passive adaptation are unconscious.
+On the other hand, networks with recurrent loops employ information stored in their own past states have the potential to achieve higher NTIC by modelling the environment.
+If it turns out to be true that for every pure feed-forward network there are non-feed-forward systems achieving higher NTIC then ICT predicts that the latter systems achieve higher levels of consciousness.
+This implication would coincide with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
+
+                % ==== end ===
+
+                % Finally, with a caveat, when the sensory dynamics is deterministic, a system can still have positive NTIC and achieve informational closure by simply copying the sensory values to its internal state (i.e.
+passive adaptation, see Sec.~\ref{sec:causality}).
+ICT will predict that, in this specific scenario, the systems can have some levels of consciousness.
+Although this specific scenario is uncommon in realistic circumstance an important implication is that pure feedforward networks can potentially produce consciousness.
+The level of consciousness for these networks is bounded by the sensory channel capacity and depth of the network.
+On the other hand, networks with recurrent loops employ information stored in their own past states have the potential to achieve higher NTIC by modelling the environment.
+If it turns out to be true that for every pure feed-forward network there are non-feed-forward systems achieving higher NTIC then ICT predicts that the latter systems achieve higher levels of consciousness.
+
+                % Namely, if the future state of a process depends primarily on the sensor value but receives little influence from its past state.
+
+            %  The first scenario is that of a system partially observing the environment in such a way that the current observation is insufficient to predict the next.
 In this situation we can show that a system passively processing the observations (including copying them) achieves lower values of NTIC and therefore lower levels of consciousness than a system that is able to accurately predict the observations.
+
             % \paragraph{@ Acer's version}
@@
             %Is Bertschinger's system better than copying?
-            \ac{OurTheory} leads to some surprisingly simple conscious processes.
+
+            % ------------------------------------
+            % \ac{OurTheory} leads to some surprisingly simple conscious processes.
 Consider the case already noted by \citet{BERTSCHINGER.2006} where the environment process is deterministic (or close to it) and the system just copies the environment process.
@@
 ICT states that such processes are conscious.
+            % ------------------------------------
 
@@
 
-            However, in more realistic cases the system cannot copy the entire environment state because it observes only part of it. 
+            % However, in more realistic cases the system cannot copy the entire environment state because it observes only part of it. 
             % and/or because it is itself not large enough to contain a copy of the environment.
 
-            We show in Appendix \ref{sec:appendix} that whenever the environment has itself more predictable dynamics than the observations there is potential for a predictive process to achieve higher NTIC than a copying system or any system that only processes its last observations without taking into account other internal memory.
+            % We show in Appendix \ref{sec:appendix} that whenever the environment has itself more predictable dynamics than the observations there is potential for a predictive process to achieve higher NTIC than a copying system or any system that only processes its last observations without taking into account other internal memory.
 Similar to \citet{BERTSCHINGER.2006} we will refer to systems of the latter type as \textit{passive}.
@@
 
-            We tentatively assume below that for a feed-forward network which can be seen as implementing a function from an extended history of past observations to the system state there also always exist systems that achieve higher NTIC.
+            % We tentatively assume below that for a feed-forward network which can be seen as implementing a function from an extended history of past observations to the system state there also always exist systems that achieve higher NTIC.
 This remains to be verified.
@@
 
-                Let us now look at some examples of this scenario.
-
-               The first are reflexive behaviours \citep{casali2013theoretically}. 
-            %   can be considered an example of this scenario. 
-               In \ac{OurTheory}, if we can view reflexive behaviours as situations in which the internal state $Y_t$, which triggers reflexive action, is determined by the environment state $E_{t-1}$ overruling the influences from its own past $Y_{t-1}$.
+            %     Let us now look at some examples of this scenario.
+
+            %   The first are reflexive behaviours \citep{casali2013theoretically}. 
+            % %   can be considered an example of this scenario. 
+            %   In \ac{OurTheory}, if we can view reflexive behaviours as situations in which the internal state $Y_t$, which triggers reflexive action, is determined by the environment state $E_{t-1}$ overruling the influences from its own past $Y_{t-1}$.
 Such interpretation of reflexive behaviour from the viewpoint of \ac{OurTheory} naturally explains why we are less conscious of external stimuli causing reflexes than of others.
@@
              	% reflexive behaviour
-        		\begin{figure}[H]
-        			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
-        			\caption{
-        			    A diagram depicting the information flow in reflexive behaviours (shown by the red nodes and arrows) happening through the interaction between a process $Y$ and its environment $E$.
-In such situations, the internal state $Y_t$ is mostly dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$.
-Therefore, the process $Y$ is not informational closed.
-As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain less conscious or unconscious.
-        			    }
-        			\label{fig:reflexive}
-        		\end{figure}
-
-        		The same principle can be applied to interpret blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedural memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes.
-        		\linelabel{line:r2q6}Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.
-However, in some cases, they may still preserve some forms of conscious experience (see \cite{overgaard2011visual, mazzi2016blind}).
-We argue that action outputs of blindsight can be directly guided by sensory inputs through stimulus-response maps.
-The corresponding neural circuits are passive and therefore do not achieve the same level of informational closure as processes/behaviours involving prediction.
-According to \ac{OurTheory} we are therefore less conscious of them.
-
-        		Similarly, for procedural memory, the transitions of the part of the neural system determining the action sequences largely depend on the  environmental states.
-Procedural memory may therefore be considered a passive process.
-\ac{OurTheory} then predicts that we are less conscious of procedural memory than of more predictive processes.
-
-        		\ac{OurTheory} also offers an interpretation as to why patients with visual apperceptive agnosia \citep{james2003ventral} can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.
-
-                % \paragraph{@ Acer's revision}
-                % However, with a caveat, informational closure can also be achieve by just copying the environment process in some certain cases.
+
+        %         their conscious levels are bounded by their sensory channel capacity.
+
+        %         % \paragraph{@ Acer's revision}
+        %         % However, with a caveat, informational closure can also be achieve by just copying the environment process in some certain cases.
 Consider the case already noted by \citet{BERTSCHINGER.2006} where the environment process is deterministic (or close to it) and full observe.
@@
 
-                % \paragraph{@ Orignal}
-                Networks with recurrent loops employ information stored in their own past states that is not necessarily a function of a single time-step observation. 
-        		If it indeed turns out to be true that for every pure feed-forward network there are non-feed-forward systems achieving higher NTIC then ICT predicts that the latter  systems achieve higher levels of consciousness.
-
+        %         % \paragraph{@ Orignal}
+
+        % 		A crucial implication of ICT is that a pure feedforward network in the most of
+
+        % 		cannot produce consciousness because NTIC requires a form of memory I(Y t+1 ; Y t ) .
+Without memory, a network’s current state is entirely driven by the input the network receives from the environment without any inﬂuence from its own past states.
+Therefore, such a network is incapable of forming an NTIC.
+In contrast, a network with recurrent loops can maintain information about its own past states.
+This forms an information channel between the past and the future states of the network and, thus, makes the network capable of being informationally closed.
+This result coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness (Edelman, 1992; Lamme, 2006; Tononi & Koch, 2008).
         % 		than the because NTIC requires a form of memory $I(Y_{t+1};Y_{t})$.
@@
 
-        		This would coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
-
-            \subsubsection*{Processes are Trivial closed}
-                According to \ac{OurTheory}, when encoded information in a process is trivial, i.e.
-no mutual information between the process states and its environment states $I(Y_{t+1};E_{t})$ (Eq.~\ref{eq:nticObjective2}), this could lead low NTIC.
-In such case, this process is considered to be unconscious due to the low level of NTIC.
-This implies an isolated process which is simply informationally closed is insufficient to be conscious.
+            \subsubsection*{Processes are Trivially Closed}
+                The second scenario is that when encoded information in a process is trivial, i.e.
+no mutual information between the process states and its environment states $I(Y_{t+1};E_{t})$ (Eq.~\ref{eq:nticObjective2}), this leads to non-positive NTIC.
+In such cases, the process is considered to be unconscious.
+This implies that an isolated process which is informationally closed is insufficient to be conscious.
                 This mathematical property of \ac{OurTheory} provides a natural and intuitive (but only partial, see the current challenge in  Sec.~\ref{sec:Limitation and Future work}) solution to the boundary and the individuality problem of consciousness
@@
 Consider a NTIC process $Y$ and an isolated informationally closed process $\hat{Y}$ with only trivial information.
-Adding $\hat{Y}$ to $Y$ can still keep informational closure, but, however, does not increase non-trivial information, i.e.
-doesn't affect consciousness.
+Adding $\hat{Y}$ to $Y$ can still maintain informational closure but does not increase non-trivial information, i.e.,  consciousness is unaffected.
 
@@
 If we cut the network in half, IIT would predict that this results in two consciousnesses because elements in both networks still maintain high degrees of interactions.
-In contrast, \ac{OurTheory} would predict that this operation could completely destroy NTIC rendering both parts unconscious.
+In contrast, \ac{OurTheory} would predict that this operation may completely destroy informational closure of the network and rendering both parts unconscious.
 
@@
             \begin{align}
-             I(S_{t+1}:f(E_t)|S_t)=I(f(E_t):f(E_t)|f(E_{t-1}))=H(f(E_t)|f(E_{t-1})
+             I(S_{t+1}:f(E_t)|S_t)=I(f(E_t):f(E_t)|f(E_{t-1}))=H(f(E_t)|f(E_{t-1}))
             \end{align}
@@
             \begin{align}
-             I(S_{t+1};E_t)=I(f(E_{t+1};E_t)=H(f(E_t))
+             I(S_{t+1};E_t)=I(f(E_{t+1});E_t)=H(f(E_t))
             \end{align}
@@
             \begin{align}
-                NTIC=I(f(E_t);f(E_{t-1})).
+                NTIC_t(E\rightarrow S)=I(f(E_t);f(E_{t-1})).
             \end{align}
@@
             \end{align}
-            However, for each such system there are systems that achieve higher NTIC.
-Take for example a "mirrored" and synchronized environment.
-In this case we have $S_t:=E_t$ such that the transfer entropy vanishes
+            However, ignoring restrictions due to a possibly fixed choice of the universe process $X$ we find that for each such system there are other systems that achieve higher NTIC.
+For example define the system to be the "mirrored" and synchronized environment by setting $S_t:=E_t$.
+Then the transfer entropy vanishes
             \begin{align}
-             I(S_{t+1}:f(E_t)|S_t)=I(E_{t+1}:f(E_t)|E_t)=0
+             I(S_{t+1}:E_t|S_t)=I(E_{t+1}:E_t|E_t)=0
             \end{align}
@@
             \begin{align}
-                I(S_{t+1};E_t)=I(E_{t+1};E_t)\geq I(f(E_{t+1});f(E_t)).
+                I(S_{t+1};E_t)=I(E_{t+1};E_t).
             \end{align}
-             This shows that whenever the environment has itself more predictable dynamics than the observations there is potential for a predictive process to achieve higher NTIC than a copying system or any system that only processes its last observations without taking into account other internal memory.
-
-----------------------
-            For a feedforward network with each layer computing just the identity:
-            \begin{align}                NTIC&=I(f(E_t),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n}))\\
-            &=H(f(E_t),\dots,f(E_{t-n+1})) - H(f(E_t)|f(E_{t-1}),\dots,f(E_{t-n})).
+             In the case where the environment has itself higher predictive mutual information than the observations it produces i.e.\ when
+             \begin{align}                I(E_{t+1};E_t)\geq I(f(E_{t+1});f(E_t))
             \end{align}
-            For the mirror environment, if we use the history dependent NTIC \citep{BERTSCHINGER.2006} we get:
-            \begin{align}
-                NTIC^{s,m}=I(E_{t+1};E_t,\dots,E_{t-n+1})
-            \end{align}
-            To see that this is always larger or equal to the feedforward network note that the feedforward NTIC can be rewrittten:
-            \begin{align}                NTIC^{ff}&=I(f(E_t),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n}))\\
-            &=I(f(E_t);f(E_{t-1}),\dots,f(E_{t-n}))+
-            I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
-            &=I(f(E_t);f(E_{t-1}),\dots,f(E_{t-n}))+
-            I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
-            &=I(f(E_t);g(E_{t-1},\dots,E_{t-n}))+
-            I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
-            &=I(E_t;E_{t-1},\dots,E_{t-n}) \underbrace{-B+
-            I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))}_{\leq 0}\\
-            &\leq I(E_t;E_{t-1},\dots,E_{t-n}).
-            % &\leq NTIC^{s,m}+
-            % I(C;C,f(E_{t-n})|f(E_t))\\
-            % &=NTIC^{s,m}+
-            % I(C;C|f(E_t))\\
-            % &=NTIC^{s,m}+
-            % H(C|f(E_t))\\
-            % &=\underbrace{I(f(E_t);f(E_{t-1}),\dots,f(E_{t-n}))}_{\text{stationarity:}\leq NTIC^{s,m}}+
+            there is then potential for a predictive process to achieve higher NTIC than a copying system or any system that only processes its last observations without taking into account other internal memory (i.e.\ those systems also applying $g$ to their observations).
+Note that this also holds true in the case where the observations are themselves closed.
+If there is a more complex environment behind them, the mirrored and synchoronized system has higher NTIC with respect to that environment than the system copying the observations.
+
+% ----------------------
+%             For a feedforward network with each layer computing just the identity:
+%             \begin{align}                NTIC&=I(f(E_t),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n}))\\
+%             &=H(f(E_t),\dots,f(E_{t-n+1})) - H(f(E_t)|f(E_{t-1}),\dots,f(E_{t-n})).
+%             \end{align}
+%             For the mirror environment, if we use the history dependent NTIC \citep{BERTSCHINGER.2006} we get:
+%             \begin{align}
+%                 NTIC^{s,m}=I(E_{t+1};E_t,\dots,E_{t-n+1})
+%             \end{align}
+%             To see that this is always larger or equal to the feedforward network note that the feedforward NTIC can be rewrittten:
+%             \begin{align}                NTIC^{ff}&=I(f(E_t),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n}))\\
+%             &=I(f(E_t);f(E_{t-1}),\dots,f(E_{t-n}))+
 %             I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
-            % &\leq NTIC^{s,m}+
-            % I(C;C,f(E_{t-n})|f(E_t))\\
-            % &=NTIC^{s,m}+
-            % I(C;C|f(E_t))\\
-            % &=NTIC^{s,m}+
-            % H(C|f(E_t))\\
-            % ============================================================================ WEIRD
-            % &=I(f(E_t);C)+I(f(E_t),f(E_{t-n})|C)+
-            % H(C|f(E_t))\\
-            % &=H(C)-H(C|f(E_t))+I(f(E_t),f(E_{t-n})|C)+
-            % H(C|f(E_t))\\
-            % &=H(C)+I(f(E_t),f(E_{t-n})|C)\\
-            % &=H(C)+H(f(E_t)|C)-H(f(E_t)|f(E_{t-n}),C)\\
-            % &=I(f(E_t);C)-H(f(E_t)|f(E_{t-n}),C)\\
-            % &=I(A, C;C,B).
-            \end{align}
-
-            \begin{align}
-                I(X;Y)&=_? I(f(X),X:g(Y),Y)\\
-                &=I(X:g(Y),Y)+I(f(X):g(Y),Y|X)\\
-                &=I(X:g(Y),Y)\\
-                &=I(X:Y)+I(X:g(Y)|Y)\\
-                &=I(X:Y)
-            \end{align}
-
-            \begin{align}
-                I(X;Y)&= I(f(X),X:g(Y),Y)\\
-                &=I(f(X):g(Y),Y)+I(X:g(Y),Y|f(X))\\
-                &=I(f(X):g(Y))+I(f(X):Y|g(Y))+ I(X:Y|f(X))+I(X:g(Y)|Y,f(X)).
-            \end{align}
-
-            \begin{align}
-                I(f(X):g(Y))=I(X;Y)-I(f(X):Y|g(Y))- I(X:Y|f(X))-I(X:g(Y)|Y,f(X))
-            \end{align}
-
-----------------------
+%             &=I(f(E_t);f(E_{t-1}),\dots,f(E_{t-n}))+
+%             I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
+%             &=I(f(E_t);g(E_{t-1},\dots,E_{t-n}))+
+%             I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
+%             &=I(E_t;E_{t-1},\dots,E_{t-n}) \underbrace{-B+
+%             I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))}_{\leq 0}\\
+%             &\leq I(E_t;E_{t-1},\dots,E_{t-n}).
+%             % &\leq NTIC^{s,m}+
+%             % I(C;C,f(E_{t-n})|f(E_t))\\
+%             % &=NTIC^{s,m}+
+%             % I(C;C|f(E_t))\\
+%             % &=NTIC^{s,m}+
+%             % H(C|f(E_t))\\
+%             % &=\underbrace{I(f(E_t);f(E_{t-1}),\dots,f(E_{t-n}))}_{\text{stationarity:}\leq NTIC^{s,m}}+
+%             % I(f(E_{t-1}),\dots,f(E_{t-n+1});f(E_{t-1}),\dots,f(E_{t-n})|f(E_t))\\
+%             % &\leq NTIC^{s,m}+
+%             % I(C;C,f(E_{t-n})|f(E_t))\\            t
+%             % &=NTIC^{s,m}+
+%             % I(C;C|f(E_t))\\
+%             % &=NTIC^{s,m}+
+%             % H(C|f(E_t))\\
+%             % ============================================================================ WEIRD
+%             % &=I(f(E_t);C)+I(f(E_t),f(E_{t-n})|C)+
+%             % H(C|f(E_t))\\
+%             % &=H(C)-H(C|f(E_t))+I(f(E_t),f(E_{t-n})|C)+
+%             % H(C|f(E_t))\\
+%             % &=H(C)+I(f(E_t),f(E_{t-n})|C)\\
+%             % &=H(C)+H(f(E_t)|C)-H(f(E_t)|f(E_{t-n}),C)\\
+%             % &=I(f(E_t);C)-H(f(E_t)|f(E_{t-n}),C)\\
+%             % &=I(A, C;C,B).
+%             \end{align}
+
+%             \begin{align}
+%                 I(X;Y)&=_? I(f(X),X:g(Y),Y)\\
+%                 &=I(X:g(Y),Y)+I(f(X):g(Y),Y|X)\\
+%                 &=I(X:g(Y),Y)\\
+%                 &=I(X:Y)+I(X:g(Y)|Y)\\
+%                 &=I(X:Y)
+%             \end{align}
+
+%             \begin{align}
+%                 I(X;Y)&= I(f(X),X:g(Y),Y)\\
+%                 &=I(f(X):g(Y),Y)+I(X:g(Y),Y|f(X))\\
+%                 &=I(f(X):g(Y))+I(f(X):Y|g(Y))+ I(X:Y|f(X))+I(X:g(Y)|Y,f(X)).
+%             \end{align}
+
+%             \begin{align}
+%                 I(f(X):g(Y))=I(X;Y)-I(f(X):Y|g(Y))- I(X:Y|f(X))-I(X:g(Y)|Y,f(X))
+%             \end{align}
+
+% ----------------------
 	\bibliographystyle{authordate1}

### 2020-04-15 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
 This implies C-process is also informationally closed to any other coarse-grainings of X including E (see also our reply to Q2).
-Therefore, only completely closed NTIC processes are consider as C-processes.
+Currently, we only consider closed NTIC processes are C-processes.
     		Regarding the video camera example, please see more discussion in our reply to your Q6. \\
@@
 Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed for the next version of ICT.}
-
     	\end{ans}
@@
 $J_t(E\rightarrow Y) = 0$.
-            As explained in Question 1a, it is not required for NTIC processes to be completely closed.
+            As explained in Question 1a, we currently only consider informationally closed processes as C-processes.
+The reviewer is also correct that our internal states depends to some degree on unpredictable sensory inputs from the environment.
+This results in some interesting predictions.
+For example, the unpredicted sensory inputs may temporally break informational closure and ICT predicts that conscious agents may lose consciousness for a short time when they receive prediction errors.
+Unfortunately, referring to your Q1b, the current version of ICT does not include state-dependent IC and NTIC.
+Therefore, the current formulation of ICT cannot well describe the dynamics of conscious experience under unpredictable states.
+We expect that our next version of ICT can better answer your question.
+
+            % it is not required for NTIC processes to be completely closed.
 The information transfer from $X$ to $Y$ $I(Y_{t+1}; X_t|Y_t)$ (if non-zero) serves as the upper bound of the information transfer from any other process to Y.
 So unpredictable sensory inputs will contribute to a positive information transfer.
-            As mentioned before higher NTIC values are achieved when this information transfer can be reduced without reducing the mutual information between the sensory inputs and the next system state.
+            % As mentioned before higher NTIC values are achieved when this information transfer can be reduced without reducing the mutual information between the sensory inputs and the next system state.
         \end{ans}
 
-        process:$X$
-        p(x'|x):=\delta_{f(x)}(x')-\delta_{\X\backslash f(x)}(|\X|-1)*n
-        p(x'|x,n)=
-        then H(X'|X)=H(\Epsilon)
-
-        find g:\X \rightarrow \Y
-
-        such that H(g(X')|g(X))=0
-        but still H(g(X'))>0
         \begin{question}
@@
 
-            This is also why ICT allowed the existence of multiple consciousnesses across the scales of coarse-graining.
+            This is also why ICT allows the existence of multiple consciousnesses across the scales of coarse-graining (which IIT does not).
 Because conscious processes are informationally closed from each other across the scale of coarse-graining, they are not able to know the existence of other consciousnesses within the same system (information flow from other processes is zero).
@@
         	The reviewer is right.
-Feed-forward networks can be conscious under ICT.
+We have reconsidered case of the feed-forward networks and the video camera example (which can be considered as a single layer feed-forward networks).
+According to ICT, feed-forward networks can be conscious under under some specific constrains.
 We thank the reviewer to correct this point.
 Similarly, a video camera can achieve positive levels of NTIC and, therefore, be conscious.
-We have worked extensively on Section 5 to make this clear (see from Line:~\lineref{line:notIC}).
-        	There we have weakened multiple claims involving a clear conscious to unconscious distinction to claims about differences between levels of consciousness. 
-        	Concerning the camera example we can show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image and the next there are systems that achieve higher NTIC.
+We have worked extensively on Section \ref{sec:causality} and Section 5 to make this clear (for Section 5, please see from Line:~\lineref{line:notIC}).
+        	There we have weakened multiple claims in the original version of the manuscript.
+        	Concerning the camera example we also show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image (sensor values) and the next there are systems that achieve higher NTIC.
         	For the case of the feedforward network we speculate that a similar situation remains true and that there are always systems that achieve higher levels of consciousness than those consisting only of feedforward networks.
+        	In summary, we mainly revised our manuscript as follows:
+        	\begin{itemize}
+        	    \item Add sensory channels in Fig.~2
+        	    \item Add Section \ref{sec:causality} to illustrate two NTIC scenarios about causality. 
+        	    \item Extensively modify the paragraph about feed-forward networks and memory in Section 5
+        	    \item Add a session in the Appendix to prove that NTIC achieved by modelling the environment can potentially achieve higher NTIC then the one by copying sensory values (e.g., the video camera).
+        	\end{itemize}
 
@@
     	\begin{ans}
-    		We agree that this point is not clear in our original manuscript.
+    		We agree that this point is not clear.
 Even though the Bayesian graphs for the system-environment dependency are different from the one for the micro-macro level dependency, we apply the same definitions of information flow ($J_{t}(X \rightarrow $Y$ )$) and informational closure ($J_{t}(X \rightarrow $Y$ )=0$) to both graphs.
@@
     		}	
-
-%			We followed the common setting of coarse-graining (e.g.
-\cite{PFANTE.2014}) which does not and should not take time $Y_t=f_Y(X_t)$ (in Definition 1).
-Coarse-graining is merely a function which maps microstates of a system to macrostates, and the microstates and the macrostates are simply different level of descriptions of a system.
-%			Following this setting, the definition of information closure (flow) $J_{t}(X \rightarrow $Y$ )$ can also be applied in the sense of coarse-graining. 
-%			
-%			\todo{Add the definition to the conttext of coarse-graining}
-%						
-%			We understand that this may lead to confusion for our readers. We have added the following sentence to make this point explicit.     		
-%			\addnew{\lineref{line:IC2CG}}{Note that we applied the same definition of information closure (Eq.\ref{eq:InformationFlow}) to processes at different coarse-grained levels \citep{{PFANTE.2014}}.}
-%			Here, we followed a common setup of coarse-graining (e.g.
-\cite{PFANTE.2014}) which does not take time $Y_t=f_Y(X_t)$ (in Definition 1).
-In this setup, coarse-graining is unidirectional ad does not involve interaction between scales.
-This means that coarser scales supervene on finer scales, and there exists no top-down causation.
-\\
-%			In our hypothesis, $Y$ is IC with respect to the microstate of the universe, X.
-This is critical in the hypothesis because $Y$ is IC with respect to X, implying that $Y$ is also IC with respect to its intermediate level S and its environment $E$ in Fig.
-\ref{fig:fullgraph}.\todo{need any change in the main text?}
     	\end{ans}
@@
     	\begin{ans}
-    % 	It is true that at the finest scale, when we consider the whole universe as a system, the universe should be an informationally closed and deterministic process.
-However, there exists no environment to the universe and, therefore, NTIC of the universe is zero (trivially closed).
-    	We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining.
-However, we currently have very limited understanding of this relationship.
-Future work is needed and may involve the techniques of partial information decomposition and related research fields.
-
-		We agree that our original claim about existing a intermediate maxima in NTIC was too strong and have revised the paragraph as follows:
+    	We have added a whole new paragraph to explain this session. We also agree that our claim about existing a intermediate maxima in NTIC was too strong and have revised the paragraph as follows:
 
@@
     	\begin{ans}
-    		We thank the reviewer for this mindful comment. 
     		Our wording indeed is not clear. The notion of simulation is the same as the 'Modeling' case on Page 4 in \cite{BERTSCHINGER.2006}: 
@@
     	\end{ans}
+    	We also added a new section (Section \ref{sec:causality}) to describe the scenario of modelling.
 
@@
    		\begin{ans}
-   			We thank the reviewer for the clarification. 
    			Yes, we specifically wanted to address the visual character of their experience. We agree that some patients still preserve some forms of conscious experience. 
@@
     	\begin{question}
-
-    	\todo{Camera thing..., we need to rewrite this reply as well}
             on Line 316: On the issue of a feedforward network, the current state of a feedforward network with more than one layer is certainly driven by its own past states!
@@
  		\begin{ans}
-			We thank the reviewer for this interesting and valuable comment. \\
+ 		    The reviewer is correct. Based on the 
+            Because another reviewer also proposed relevent questions and based on some reconsideration, 
 			We can consider a simple case in which a feedforward neural network $Y$ consists of three layers, $Y^0$, $Y^1$, and $Y^2$. 
@@
     	\begin{ans}
-    		We thank the reviewer for this considerate comment.
     		The reviewer is correct.
@@
 We also agree that this prediction is relatively premature.
-However, we also acknowledge the strength of all computational theories of consciousness.
-The reviewer's question is empirical to us under formal mathematical formulations of ICT and IIT.
 Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.

### 2020-04-16 ICT_Frontiers_rev202001.tex
Updates from Overleaf

@@
 
-		In the following, we first introduce non-trivial informational closure and argue for its importance to information processing for human scale agents (Sec.\ref{sec:Non-trivial informational closure}).
-We next argue that through coarse-graining the neural system can form a high degree of NTIC at a specific coarse-grained scale (Sec.\ref{sec:Neural coarse-graining}).
-In the Sec.\ref{sec:OurTheory}, we propose a new theory of consciousness (\ac{OurTheory}).
-We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies (Sec.\ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (Sec.\ref{sec:Comparison with other theories}).
+		In the following, we first introduce non-trivial informational closure and argue for its importance to information processing for human scale agents (Sec.~\ref{sec:Non-trivial informational closure}).
+We next argue that through coarse-graining the neural system can form informational closure and a high degree of NTIC at a specific scale of coarse-graining  (Sec.~\ref{sec:Neural coarse-graining}).
+In the Sec.~\ref{sec:OurTheory}, we propose a new theory of consciousness (\ac{OurTheory}).
+We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies (Sec.~\ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (Sec.\ref{sec:Comparison with other theories}).
 Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from \ac{OurTheory} to the current consciousness science (Sec.\ref{sec:Limitation and Future work}).
@@
 			\subsection{Informational Closure Does not Imply Causality}\label{sec:causality}
-                A surprising (but well known; see ???) result from the definition of information flow $J_t(E\rightarrow Y)$ (Eq.
+                A surprising (but well known) result from the definition of information flow $J_t(E\rightarrow Y)$ (Eq.
 \ref{eq:InformationFlow}) is that information flow does not indicate causal dependency from $E_t$ to $Y_{t+1}$ and from $Y_t$ to $Y_{t+1}$.
@@
 Therefore, processes at intermediate scales of coarse-graining can form higher degrees of NTIC than at the most microscopic or macroscopic scales (Fig.~\ref{fig:LevelOfConsciousness}).
-\ac{OurTheory} indicates that human consciousness occurs at the scale of coarse-graining where higher NTIC is formed within the neural system.
+\ac{OurTheory} suggests that human consciousness occurs at a scale of coarse-graining where high NTIC is formed within the neural system.
+\linelabel{line:non-monotonic_end}
 
@@
     		% CC doesn't include all microscopic states
-    		As mentioned above, informational closure can happen between scales of coarse-graining within a single system.
+    		Informational closure can happen between scales of coarse-graining within a single system.
 Thus, a macroscopic NTIC process can be ignorant to its microscopic states.
@@
 When the information flow is zero, the process is informationally closed with respect to the environment.
-                The first scenario is built upon the assumption that sensor values are non-deterministic and the process dynamics are passively driven by the environmental inputs.
+                The first scenario is built upon the assumption that sensor processes are non-deterministic \footnote{Non-deterministic sensor processes here means $H(\hat{e}_{t+1}|\hat{e}_t)>0$.} and the process dynamics are passively driven by the environmental inputs.
 Such processes cannot be informationally closed and are therefore unconscious.
@@
 When the sensor processes are deterministic, a system can still have positive NTIC and achieve informational closure via passive adaptation.
-Therefore, some passive system (for example pure feedforward networks) can potentially produce consciousness.
+\linelabel{line:feedforward}Therefore, some passive system (for example pure feedforward networks) can potentially produce consciousness.\footnote{Since a $n$-layer feedforward network is a system with $n$-step memory it is technically appropriate to use the $n$-step memory definition of NTIC, i.e.
+$NTIC^m_t(E\rightarrow Y):=I(Y_{t+1}:E_t,...,E_{t-n+1})-I(Y_{t+1}:E_t,...,E_{t-n+1}|Y_t)$ \citep{BERTSCHINGER.2006}, for such systems.
+In this case the notion of non-deterministic input processes should be generalised to input processes with $H(\hat{e}_t|\hat_{e}_{t-1},...,\hat{e}_{t-n})>0$.}
 
@@
 
-            \subsubsection*{Processes are Trivially Closed}
+            \subsubsection*{Processes that are Trivially Closed}
                 The second scenario is that when encoded information in a process is trivial, i.e.
@@
 This implies that an isolated process which is informationally closed is insufficient to be conscious.
-                This mathematical property of \ac{OurTheory} provides a natural and intuitive (but only partial, see the current challenge in  Sec.~\ref{sec:Limitation and Future work}) solution to the boundary and the individuality problem of consciousness
-                    \footnote{The boundary problem of consciousness refers to identifying physical boundaries of conscious processes and the individuality problem of consciousness refers to identifying individual consciousnesses in the universe.}
+                This mathematical property of \ac{OurTheory} 
+                is relevant for 
+                % provides a natural and intuitive (but only partial, see the current challenge in  Sec.~\ref{sec:Limitation and Future work}) solution to 
+                dealing with 
+                the boundary and the individuality problems of consciousness\footnote{The boundary problem of consciousness refers to identifying physical boundaries of conscious processes and the individuality problem of consciousness refers to identifying individual consciousnesses in the universe.}
                 \citep{Raymont2006-RAYUOC}.
@@
 
-                This implies that isolated processes with trivial information do not contribute consciousness and should be considered being outside the information boundary of the conscious processing (for more details of the boundary detection procedure, see \cite{krakauer2014information}).
-                This property also implies that consciousnesses do not emerge from just aggregating informationally closed (isolated) processes which contain trivial information.%\footnote{However, we do not exclude the possibility that triviality of encoded information is just a proxy of other quantities which more directly associate with consciousness.
+                This implies that isolated processes with trivial information do not contribute consciousness and should be considered being outside the information boundary of the conscious processing.
+                % (for more details of the boundary detection procedure, see \cite{krakauer2014information}). 
+                This property also implies that consciousnesses do not emerge from just aggregating informationally closed (isolated) processes which contain trivial information.
+                In the future we hope to adapt the procedures for boundary detection proposed in \citet{krakauer2014information,krakauer2020information} to ICT.
+
+                %\footnote{However, we do not exclude the possibility that triviality of encoded information is just a proxy of other quantities which more directly associate with consciousness.
 We point out that this is a limitation of the current version of \ac{OurTheory} in Sec.~\ref{sec:Limitation and Future work}.}
@@
         % Identity problem
-        \linelabel{line:individuality}The current version of \ac{OurTheory} cannot entirely solve the problem of individuality in some extreme circumstances.
-In common cases, one can identify individual consciousnesses by computing the levels of NTIC of a process.
-This approach can also be applied to finding the boundaries of individual consciousnesses (for details of the boundary detection procedure, see \cite{krakauer2014information}).
+        \linelabel{line:individuality}The current version of \ac{OurTheory} cannot entirely solve the problem of individuality.
+The main issue with identifying individual consciousnesses using \ac{OurTheory} is that at the moment the environment is not uniquely defined.
+Once we have identified processes that are informationally closed with respect to $X$ we still have to find the environment process $E$ with respect to which we compute NTIC.
+However, there are usually multiple system processes $S$ of which a given $Y$ is a coarse-graining in which case there are also multiple environment processes $E$ with respect to which we could compute NTIC.
+
+        % Assuming that we have nonetheless identified two conscious processes 
+        % In common cases, one can identify individual consciousnesses by finding informationally closed processes and computing the levels of NTIC of a process.
+This approach can also be applied to finding the boundaries of individual consciousnesses (for details of the boundary detection procedure, see \cite{krakauer2014information, krakauer2020information}).
 However, in some specific circumstances, individuality of consciousness is not clear.
-For instance, we can define a new process $Y$ and also its environment $E$ by recruiting two independent NTIC processes $Y^1~\&~Y^2$ and their environments $E^1~\&~E^2$, respectively.
-So that $Y = \{Y^1,Y^2\}$ and $E=\{E^1,E^2\}$.
+        A more general problem of NTIC based individuality is that
+        we can define a new process $Y$ and also its environment $E$ by recruiting two independent NTIC processes $Y^1~\&~Y^2$ and their environments $E^1~\&~E^2$, respectively.
+So that $Y = (Y^1,Y^2)$ and $E=(E^1,E^2)$.
 In such case, the new process $Y$ will also be NTIC to $E$.

### 2020-04-16 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
 This results in some interesting predictions.
-For example, the unpredicted sensory inputs may temporally break informational closure and ICT predicts that conscious agents may lose consciousness for a short time when they receive prediction errors.
+For example, the unpredicted sensory inputs may temporally break informational closure and ICT predicts that conscious agents may then lose consciousness for a short time.
 Unfortunately, referring to your Q1b, the current version of ICT does not include state-dependent IC and NTIC.
@@
             We can see how Figure 4 was ambiguous with respect to this question. We do not impose the exclusion criterion in ICT and have changed Figure 4 to remove the impression that it does. 
-            A key feature of ICT is that, instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of system-environment separation and a boundary of a system \citep{BERTSCHINGER.2006}.
+            % A key feature of ICT is that, instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of system-environment separation and a boundary of a system \citep{BERTSCHINGER.2006}.
 For example, \citet{krakauer2014information,krakauer2020information} proposed an algorithm to add and remove variables in order to find the boundary.
 \\
-            It is true that NTIC can be computed for every subset of a system and can also have a positive value of NTIC for multiple of those.
-However, according to our definition, if these processes are not informationally closed to their environments (including the complement subset in the system), ICT claims that they are not C-processes, and thus not conscious.
-.
+            % It is true that NTIC can be computed for every subset of a system and can also have a positive value of NTIC for multiple of those. 
+            It is true that every subset of a system can be a C-process and there can be multiple of those in a system.
+            % However, according to our definition, if these processes are not informationally closed to their environments (including the complement subset in the system), they are not C-processes, and thus ICT claims that they are not conscious.
+            % .
 In order to find whole or entire consciousnesses we can use the algorithm in \citet{krakauer2014information, krakauer2020information}.
@@
         	The reviewer is right.
-We have reconsidered case of the feed-forward networks and the video camera example (which can be considered as a single layer feed-forward networks).
-According to ICT, feed-forward networks can be conscious under under some specific constrains.
+We have reconsidered case of the feed-forward networks and the video camera example (which can be considered as a single layer feed-forward network).
+According to ICT, feed-forward networks can be conscious under for deterministic sensor processes.
 We thank the reviewer to correct this point.
-Similarly, a video camera can achieve positive levels of NTIC and, therefore, be conscious.
+In this case also a video camera can achieve positive levels of NTIC and, therefore, be conscious.
 We have worked extensively on Section \ref{sec:causality} and Section 5 to make this clear (for Section 5, please see from Line:~\lineref{line:notIC}).
-        	There we have weakened multiple claims in the original version of the manuscript.
-        	Concerning the camera example we also show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image (sensor values) and the next there are systems that achieve higher NTIC.
-        	For the case of the feedforward network we speculate that a similar situation remains true and that there are always systems that achieve higher levels of consciousness than those consisting only of feedforward networks.
+        % 	There we have weakened multiple claims in the original version of the manuscript.
+        % 	Concerning the camera example we also show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image (sensor values) and the next there are systems that achieve higher NTIC.
+        % 	For the case of the feedforward network we speculate that a similar situation remains true and that there are always systems that achieve higher levels of consciousness than those consisting only of feedforward networks.
         	In summary, we mainly revised our manuscript as follows:
         	\begin{itemize}
+        	    \item Add Section \ref{sec:causality} to illustrate two NTIC scenarios about causality. 
         	    \item Add sensory channels in Fig.~2
-        	    \item Add Section \ref{sec:causality} to illustrate two NTIC scenarios about causality. 
-        	    \item Extensively modify the paragraph about feed-forward networks and memory in Section 5
+        	    \item Extensively modify the paragraphs about feed-forward networks and memory in Section 5
         	    \item Add a session in the Appendix to prove that NTIC achieved by modelling the environment can potentially achieve higher NTIC then the one by copying sensory values (e.g., the video camera).
@@
     			We have modified this as follows: \\
-    			\toWrite{"contributions to the field"}
+    			"We propose a new theory of consciousness and discuss some preliminary implications."
 
@@
 In ICT, the two sets of parameters do not have any qualitative differences.
-
-    			\todo{Do we need to write something in the main text?}
 
@@
 
-			Basically, I am not sure whether closer between scales is a matter of same-time (e.g. $I(Y_{t+1};X_{t+1})$) or across-time interactions ($I(Y_{t+1};X_t)$). Or could it be both?    		
+			Basically, I am not sure whether closure between scales is a matter of same-time (e.g. $I(Y_{t+1};X_{t+1})$) or across-time interactions ($I(Y_{t+1};X_t)$). Or could it be both?    		
     	\end{question}
@@
     	\begin{ans}
-    	We have added a whole new paragraph to explain this session. We also agree that our claim about existing a intermediate maxima in NTIC was too strong and have revised the paragraph as follows:
+    	To make this point more clear, we have added a new paragraph and made a significant revision of this section from Line \lineref{line:non-monotonic} to Line  \lineref{line:non-monotonic_end}.
 
-		\revise{\lineref{line:non-monotonic}}
-		{
-			It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
+% 		\revise{\lineref{line:non-monotonic}}
+% 		{
+% 			It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
 We saw above that not sufficiently coarse-grained variables have low values of NTIC.
@@
 ICT indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
-		}
-		{
-			It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining\footnote{We know that NTIC is not a non-monotonic function of the scale of coarse-graining.
-However, we currently have limited understanding about this relationship.
-Future work is needed and may involve relevant informational techniques (e.g.,partial information decomposition).}.
-At the finest scale, when we consider the dynamics of the whole universe as a process, the universe should be an informationally closed.
-However, there exists no environment to the universe and, therefore, NTIC of the universe is zero (trivially closed).
-On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC.
-For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any informational capacity and thus cannot have  mutual information between adjacent time steps.
-Therefor, processes at certain levels of coarse-graining in the neural system can form high degrees of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
-ICT indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
-		}
+% 		}
+% 		{
+% 		
+% 		}
     	\end{ans}
@@
     	\begin{ans}
-    		Our wording indeed is not clear. The notion of simulation is the same as the 'Modeling' case on Page 4 in \cite{BERTSCHINGER.2006}: 
+    		The notion of simulation is the same as the 'Modeling' case on Page 4 in \cite{BERTSCHINGER.2006}: 
     		\begin{quote}
@@
 
-    		To avoid the confusion We have revised the following sentence, changed "simulation" to "modeling", and added the reference.
+    	    In this revision, we added a new subsection \ref{sec:causality} to describe the scenario of modelling.
+    		Also, to avoid the confusion We have revised the following sentence, changed "simulation" to "modeling", and added the reference.
     		\revise{\lineref{line:encode}}
@@
     	\end{ans}
-    	We also added a new section (Section \ref{sec:causality}) to describe the scenario of modelling.
 
@@
    			{
-   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience (however, in some cases, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}).
+   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.
+However, in some cases, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}.
    			}
@@
  		\begin{ans}
- 		    The reviewer is correct. Based on the 
-            Because another reviewer also proposed relevent questions and based on some reconsideration, 
-			We can consider a simple case in which a feedforward neural network $Y$ consists of three layers, $Y^0$, $Y^1$, and $Y^2$. 
-			$Y^0$ receives sensory input from the environment $E$.
-Each layer $Y^i_t$ passes information to the next layer $Y^{i+1}_{t+1}$ with a constant time cost $\Delta t$ as showed in the following figure.
-
- 			\begin{figure}[H]
- 				\centering
- 				\includegraphics[width=\textwidth]{WritingMaterials/Fig_rev1_feedforward/Fig_rev1_feedforward} 				
- 				\label{fig:rev1_feedforward}
- 			\end{figure}
-
-			Because $Y^0_t$ determines $Y^1_{t+1}$ and $Y^1_t$ determines $Y^2_{t+1}$, it is true that the mutual information $I(Y_t; Y_{t+1}) \geq 0$.
-However, $E_t$ only influences $Y^0_{t+1}$ at time $t+1$.
-Therefore
-			\begin{equation*}
-				\begin{aligned}
-					& I(Y_t; Y_{t+1}|E_t) = I(Y_t; Y_{t+1}) & \text{and} \\
-					& NTIC_t(E\rightarrow Y)=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}) =0  { }
-				\end{aligned}
-			\end{equation*}
-
-			Therefore, a feedforward network passively driven by input signals should have zero NTIC even though when time step (temporal coarse-graining) is small. 
-			\todo{I don't think I answer this question well. Do we need to add anything in the main text?}
+ 		    The reviewer is correct.
+As we have now made clear in the case of a deterministic observation process a feedforward network (or a copying process) can be informationally closed and also maintain mutual information such that it is conscious according to ICT.
+We call such process passive adaptation processes and introduce this in the new section \ref{sec:causality}.
+We mention the possibility of conscious feedforward networks now in section \ref{sec:reflexive} and add a footnote specific for n-layer feedforward networks at Line \lineref{line:feedforward}.
+Note that most observation processes in the real world are not deterministic so that most passive adaptation processes aren't conscious.
 
@@
     	\begin{ans}
-    		ICT is our first attempt to approach the hard problem of consciousness.
-We hope that ICT and our following works can establish an informational perspective on conscious experience.
-Instead of solving the hard problem of consciousness, we more look forward to mathematically determining whether the hard problem can be solved or not by information theory.
-However, because the relevant discussion is outside the scope of this article, we prefer not to discuss the hard problem here.
-
+    		We appreciate the reviewer to bring up the hard problem of consciousness and dreaming. 
+    % 		This is a very good question and dreaming really poses a challenge for ICT.
+At the moment we can only speculate about possible solutions.
+One possiblity to may be that during dreaming the environment extends further into the neural system and NTIC is achieved with respect to other parts of the brain e.g.
+the visual cortex.
+    % 		Another solution may come from using the memory extended version of NTIC. Dreams probably do maintain mutual information with the history of expereiences of a person.
 			We want to emphasise that not all the processes in the neural system are NTIC processes.

### 2020-04-16 ICT_Frontiers_rev202001.tex
Updates from Overleaf

@@
 \usepackage[round, sort]{natbib}
+\usepackage{nameref}
 \usepackage{amsmath}
@@
 		% Definition of informational closure
-			\linelabel{line:r1q1a}Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network in Fig.~\ref{fig:SystemAndEnv}.
+			\linelabel{line:r1q1a}Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network with the sensor channel $\hat{e}_{t}$ and the action $\hat{y}_{t}$ channel in Fig.~\ref{fig:SystemAndEnv}.
 Then, information flow $J_{t}$ from the environment $E$ to a system $S$ at time $t$ can be defined as the conditional mutual information $I$ between the current environment state $E_{t}$  and the future system state $Y_{t+1}$ given the current system state $Y_{t}$
@@
 			\subsection{Informational Closure Does not Imply Causality}\label{sec:causality}
-                A surprising (but well known) result from the definition of information flow $J_t(E\rightarrow Y)$ (Eq.
-\ref{eq:InformationFlow}) is that information flow does not indicate causal dependency from $E_t$ to $Y_{t+1}$ and from $Y_t$ to $Y_{t+1}$.
-Here we consider two scenarios, called "modelling" and "passive adaptation", which were already noted by \citet{BERTSCHINGER.2006}.
+                A surprising result from the definition of information flow $J_t(E\rightarrow Y)$ (Eq.~\ref{eq:InformationFlow}) is that information flow does not indicate causal dependency from $E_t$ to $Y_{t+1}$ and from $Y_t$ to $Y_{t+1}$.
+Here we consider two scenarios, called \textit{modelling} and \textit{passive adaptation}, which were already noted by \citet{BERTSCHINGER.2006}.
 In both scenarios, a process can form positive NTIC ($NTIC(E\rightarrow Y)> 0$) and informational closure ($J(E\rightarrow Y)=0$), however, via different causal dependencies.
@@
 Therefore, it is difficult for the system to be informationally closed and have higher NTIC.
-                More importantly, we argue in Appendix \ref{sec:appendix} that whenever the environment has itself more predictable dynamics than the observations, there is potential for a process to achieve higher NTIC by modelling the environment than by copying the observations.
+                More importantly, we argue in Appendix that whenever the environment has itself more predictable dynamics than the observations, there is potential for a process to achieve higher NTIC by modelling the environment than by copying the observations.
 
@@
         \end{align}
-        even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).\\\\
+        Even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).\\
 
@@
 
-        % ====================================
-        % Refinement construction approach
-        % ====================================
-        % \begin{hypothesis}
-        %         For any coarse-graining $Y$ of a stochastic process $X$, a refinement $S$ of $Y$ and the environment $E$ of $S$.  
-        %         The \emph{content $C_t^{Content}(Y)$ of the consciousness of $Y$ at time $t$} is the state $y_t$ of $Y$ at time $t$ and \emph{the level $C_t^{Level}(Y)$ of the consciousness of $Y$} is the degree of NTIC of the C-process to the environment minus the information flow from the microscopic process $X$ to $Y$:
-        %         \begin{align}
-        %             C_t^{Content} &= y_t \label{eq:cContent}\\
-        %             C_t^{Level} &= NTIC_t(E\rightarrow Y)-J_t(X \rightarrow Y) \label{eq:cLevel}
-        %         \end{align}
-        %         \end{hypothesis}
-        % ====================================
-
         A concrete example in the context of neuroscience is that $X$ represents the microscopic scale of the universe, $S$ a cellular scale process in the neural system, $Y$ a more macroscopic process of the neural system coarse-grained from the cellular scale process $S$, and $E$ the environment which the cellular level process $S$ interacts with.
-\linelabel{line:neu-env} The environment $E$ may include other processes in the neural system, the sensors for perception and interoception, and external physical worlds.\\
+\linelabel{line:neu-env} The environment $E$ may include other processes in the neural system, the sensors for perception and interoception, and external physical worlds.
 
@@
             \item[Implication 5.]
-            Conscious processes can encode environmental information (by forming NTIC), however, be ignorant to part of the information of more microscopic processes (from Implication 3 and 4).
+            Conscious processes can model environmental information (by forming NTIC), however, be ignorant to part of the information of more microscopic processes (from Implication 3 and 4).
 This is in line with our conscious experience that information that every conscious percept provides represent rich and structured environmental states without involving all the information about microscopic activities.
@@
 Further more, since NTIC processes are informationally closed, each of them can be considered as a reality.
-In the extreme case, when the information flow from its microscopic processes and environment to the informationally closed process is completely zero (Eq.~\ref{eq:informationflow2}), the future states of the process is only determined by its past states.
-
-    		\linelabel{line:encode}Importantly, NTIC processes internalise the environmental dynamics in its states \citep[also see P.~4][]{BERTSCHINGER.2006}.
-This suggests that a NTIC process can be considered as a process that models the environmental dynamics.This implication fits well with some theories of consciousness (for example, world simulation metaphor ~\citep{revonsuo2006inner}).
-Note that \ac{OurTheory} doesn't assume that generative models are necessary for consciousness.
+When the information flow from its microscopic processes and environment to the informationally closed process is completely zero (Eq.~\ref{eq:informationflow2}), the future states of the process can entirely be determined by its past states.
+
+    		\linelabel{line:encode}Importantly, in most of the realistic cases, NTIC processes internalise the environmental dynamics in its states (see Sec.
+\ref{sec:causality} and also \cite{BERTSCHINGER.2006}).
+This suggests that a NTIC process can be considered as a process that models the environmental dynamics.
+This implication fits well with several theories of consciousness (for example, world simulation metaphor ~\citep{revonsuo2006inner}).
+Note that \ac{OurTheory} does not assume that generative models are necessary for consciousness.
 The implication is a natural result of processes with NTIC.
@@
     	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the state space of an NTIC process $Y$.
-A large state space of $Y$ contributes conscious levels through the mutual information $I(Y_{t+1};Y_{t})$ and also contributes richer conscious contents by providing more possible states of conscious processes.
+A larger state space of $Y$ contributes conscious levels through the mutual information $I(Y_{t+1};Y_{t})$ and also contributes richer conscious contents by providing more possible states of conscious processes.
     	    \ac{OurTheory} therefore explains why, in normal physiological states, conscious levels and conscious contents are often positively correlated \citep{laureys2005neural}.
@@
                 The first scenario is built upon the assumption that sensor processes are non-deterministic \footnote{Non-deterministic sensor processes here means $H(\hat{e}_{t+1}|\hat{e}_t)>0$.} and the process dynamics are passively driven by the environmental inputs.
-Such processes cannot be informationally closed and are therefore unconscious.
-
-                % When the sensor processes are not deterministic, if processes dynamics is passively driven by the environmental inputs the process is not informationally closed and, thus, unconscious.
+Such processes cannot be informationally closed and are, therefore, unconscious.
 
                 Reflexive behaviours \citep{casali2013theoretically} can be considered as an example of this scenario.
-In \ac{OurTheory}, if we can view reflexive behaviours as situations in which the internal state $Y_t$, which triggers reflexive action, is determined by the environment state $E_{t-1}$, overruling the influences from its own past $Y_{t-1}$.
+In \ac{OurTheory}, if we can view reflexive behaviours as situations in which (Fig.~\ref{fig:reflexive}) the internal state $Y_t$, which triggers reflexive action $\hat{y}_t$, is determined by the environment state $E_{t-1}$, overruling the influences from its own past $Y_{t-1}$.
 Such interpretation of reflexive behaviour from the viewpoint of \ac{OurTheory} naturally explains why reflexes involve less or no conscious experience of external stimuli.
@@
         			    A diagram depicting the information flow in reflexive behaviours (shown by the red nodes and arrows) happening through the interaction between a process $Y$ and its environment $E$.
-In such situations, the internal state $Y_t$ is mostly dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$.
-Therefore, the process $Y$ is not informational closed.
-As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain less conscious or unconscious (see Fig.~\ref{fig:reflexive}).
-        			    }
+When the sensor process $\hat{e}_t$ is  non-deterministic and the internal state $Y_t$ is mostly dependent on the sensor state $\hat{e}_t$ driven by the environment $E_{t-1}$ but less on its past state $Y_{t-1}$.
+As a consequence, $Y$ is unable to form informational closure and, therefore, remain unconscious.}
         			\label{fig:reflexive}
@@
                 The same principle can be applied to interpret blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedural memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes.
-        		\linelabel{line:r2q6}Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.
-However, in some cases, they may still preserve some forms of conscious experience (see \cite{overgaard2011visual, mazzi2016blind}).
+        		\linelabel{line:r2q6}Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.(However, in some cases, they may still preserve some forms of conscious experience; See \cite{overgaard2011visual, mazzi2016blind}).
 We argue that blindsight-guided actions are a result of
-        		% action outputs of blindsight can be directly guided by sensory inputs through 
         		stimulus-response mapping.
 The corresponding neural circuits are driven passively and therefore are not informationally closed.
-According to \ac{OurTheory} we therefore have no conscious experience of the visual stimuli.
+According to \ac{OurTheory} we therefore have no conscious visual experience of visual the  stimuli.
 
@@
                 Note that, not all processes that are driven by the environment (passive adaptation) are unconscious.
-When the sensor processes are deterministic, a system can still have positive NTIC and achieve informational closure via passive adaptation.
-\linelabel{line:feedforward}Therefore, some passive system (for example pure feedforward networks) can potentially produce consciousness.\footnote{Since a $n$-layer feedforward network is a system with $n$-step memory it is technically appropriate to use the $n$-step memory definition of NTIC, i.e.
-$NTIC^m_t(E\rightarrow Y):=I(Y_{t+1}:E_t,...,E_{t-n+1})-I(Y_{t+1}:E_t,...,E_{t-n+1}|Y_t)$ \citep{BERTSCHINGER.2006}, for such systems.
-In this case the notion of non-deterministic input processes should be generalised to input processes with $H(\hat{e}_t|\hat_{e}_{t-1},...,\hat{e}_{t-n})>0$.}
+As mentioned in Sec.~\ref{sec:causality}, when the sensor processes are deterministic, a system can still have positive NTIC and achieve informational closure via passive adaptation.
+\linelabel{line:feedforward}Therefore, some passive system (for example pure feedforward networks) can potentially be conscious.\footnote{Since a $n$-layer feedforward network is a system with $n$-step memory it is technically appropriate to use the $n$-step memory definition of NTIC, i.e.~$NTIC^m_t(E\rightarrow Y):=I(Y_{t+1}:E_t,\dots,E_{t-n+1})-I(Y_{t+1}:E_t,\dots,E_{t-n+1}|Y_t)$ \citep{BERTSCHINGER.2006}, for such systems.
+In this case the notion of non-deterministic input processes should be generalised to input processes with $H(\hat{e}_t|\hat{e}_{t-1},\dots,\hat{e}_{t-n})>0$.}
 
@@
 This implication would coincide with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
-
-                % ==== end ===
-
                 % Finally, with a caveat, when the sensory dynamics is deterministic, a system can still have positive NTIC and achieve informational closure by simply copying the sensory values to its internal state (i.e.
@@
 In contrast,
-
             \subsubsection*{Processes that are Trivially Closed}
@@
 
-                This implies that isolated processes with trivial information do not contribute consciousness and should be considered being outside the information boundary of the conscious processing.
+                This implies that isolated processes with trivial information do not contribute consciousness and should be considered being outside the informational boundary of the conscious processing.
                 % (for more details of the boundary detection procedure, see \cite{krakauer2014information}). 
@@
 \ac{OurTheory} provides an integrated account for the reason why these processes involve conscious experience.
-As mentioned above, an NTIC process can be seen as an internal simulation engine for the agent-environmental interactions \citep{BERTSCHINGER.2006}.
+As mentioned above, an NTIC process can be seen as an internal modelling engine for the agent-environmental interactions \citep{BERTSCHINGER.2006}.
 Therefore, information encoded in NTIC processes is essential for several cognitive processes.
@@
 
-            Second, as a simulation engine, with a given initial state, an NTIC process can self-evolve and simulate the environmental transitions.
+            Second, as a modelling engine, with a given initial state, an NTIC process can self-evolve and simulate the environmental transitions.
 Cognitive functions involving simulations are expected to involve NTIC processes.
@@
 To accurately encode information about the complex environmental states and transitions, the NTIC process requires knowledge about the complex causal dependencies involved in the environment.
-Therefore, cognitive functions requiring large scale integration are likely to involve NTIC processes and accompanied by conscious experience.
+Therefore, cognitive functions requiring larger scale integration are likely to involve NTIC processes and accompanied by conscious experience.
 % Furthermore, the high dimensional integrated information is also critical for an agent to learn new behaviours to achieve flexibility and the strategic behavioural controls and decision-making.
@@
 To our knowledge, Pennartz's neurorepresentational theory (also called Neurorepresentationalism,~\citep{pennartz2018consciousness,pennartz2015brain}) is the proposal closest to the multilevel view of \ac{OurTheory}.
-Similar to Neurorepresentationalism, the concept of levels in \ac{OurTheory} is also relevant to Marr's level of analysis~\citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}.
-    		However, \ac{OurTheory} suggests that coarse-graining is necessary only when the microscopic processes are stochastic (e.g.
+Similar to Neurorepresentationalism, the concept of levels in \ac{OurTheory} is relevant to Marr's level of analysis~\citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}.
+    		However, \ac{OurTheory} suggests that coarse-graining is necessary only when the microscopic processes are not NTIC (e.g.
 the neural system).
@@
     		%Neurorepresentationalism also suggests conscious experience is associated with integrated representation for multimodal and situational information.
-    		However, \ac{OurTheory} is grounded by non-functional informational hypothesis. Therefore, \ac{OurTheory} provides a more fundamental explanation for the scale problem of consciousness.
+    		However, \ac{OurTheory} is grounded by non-functional informational hypothesis.
+Therefore, \ac{OurTheory} provides a non-functional and fundamental explanation for the scale problem of consciousness.
 
@@
 
-    		Here, we want to make clear that the "level" in \ac{OurTheory} refers to the \textbf{scales of coarse-graining} instead of the "level" for the cortical anatomy or sensory processing.
+    		Here, we want to make clear that the "level" in \ac{OurTheory} refers to the \textbf{scale of coarse-graining} instead of the "level" for the cortical anatomy or sensory processing.
 It is important to note that the coarse-graining direction is an orthogonal dimension irrespective of the level of anatomy or the level of information processing hierarchy in the neural system (see Fig.~\ref{fig:hierarchy}).
@@
 In the current paper, we did not include the notion of integrated information within \ac{OurTheory}.
-This, however, results in one of the current weaknesses of \ac{OurTheory} that it lacks the ability to individuate NTIC processes in some extreme cases (i.e., the problem of individuality).
+This, however, results in one of the current weaknesses of \ac{OurTheory} that it lacks the ability to individuate NTIC processes in some cases (i.e., the problem of individuality).
 We discussed this weaknesses in Sec.~\ref{sec:Limitation and Future work}.
@@
 Note that predictive processes are not necessary to involve NTIC processes.
-A predictive process can make prediction about the future state of its environment based on the current sensory inputs.
-In this case, the the process is not informationally closed and could not be conscious.
+A predictive process can make prediction about the future state of its environment solely based on the current sensor states when the current sensor states and future sensor states have positive mutual information.
+However, this is not sufficient for a process to be informationally closed and, therefore, be conscious.
 
@@
 This decrease the level of informational closure and, as a result, decrease the conscious level of this process.
-This outcome strongly supports \ac{OurTheory} than SMC.
+This outcome more supports \ac{OurTheory} than SMC.
 
@@
         % Can't solve the hard problem
-        It's important to clarify that \ac{OurTheory} does not intend to completely solve the hard problems of consciousness \citep{chalmers1995facing}.
+        It's important to clarify that \ac{OurTheory} does not intend to  solve the hard problems of consciousness \citep{chalmers1995facing}.
 Knowing the state of a conscious process does not allow us to answer "What is it like to be in this state of this process" \citep{nagel1974like}.
@@
 More theoretical work is needed to elucidate the role of environments.
-This issue will also be discuss in our next theoretical paper.
-
-        \linelabel{line:dream}Explaining conscious experience during dreaming is always a challenge to all the theories of consciousness.
+This issue will also be discuss in our future theoretical paper.
+
+        \linelabel{line:r1-state-dep}In this article, we do not use a state-dependent formulation of NTIC.
+However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.
+Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed for the next version of ICT.
+
+        \linelabel{line:dream}Explaining conscious experience during dreaming is always a challenge to theories of consciousness.
 ICT currently does not have a certain answer to dreaming.
-However, we want to emphasise that not all the processes in the neural system are NTIC.
-This is trivial since some processes are evidently not informationally closed.
+However, we want to emphasise that not all the processes in the neural system are NTIC since some processes are not informationally closed.
 They mainly passively react to sensory inputs or other processes in the neural system.
-To the conscious (NTIC) process, the rest of the neural system is part of the environment, and undoubtedly retains some degree of activity during sleep and dreaming.
+To the conscious (NTIC) process, the rest of the neural system and the body are parts of the environment, and they retains some degree of activity during sleep and dreaming.
 We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
@@
 However, at the current stage, this is mere speculation.
-Searching for the NTIC process(es) during dreaming is a crucial step to extend the scope of ICT in future research.
+Searching for the NTIC process(es) during dreaming is a important step to extend the scope of ICT in future research.
 
@@
 \cite{Gamez2016} has also systematically described relevant issues in terms of finding data correlates of consciousness amount different levels of abstraction.
-We believe that interdisciplinary research is required to narrow down the scope of searching the coarse-graining functions and conscious processes at the coarse-grained scales in the neural system and beyond.
-
-        \linelabel{line:r1-state-dep}In this article, we do not use a state-dependent formulation of NTIC.
-However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.
-Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed for the next version of ICT.
+We believe that interdisciplinary research is required to narrow down the scope of searching the coarse-graining functions and conscious processes at macro-scales in the neural system and beyond.
 
@@
 The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
-\section{Appendix*}
+\section*{Appendix}
 \label{sec:appendix}

### 2020-04-16 ICT_Frontiers_rev202001.tex
Updates from Overleaf

@@
 
-        \noindent Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) \linelabel{line:IC2CG}
+        \noindent Note that, \linelabel{line:IC2CG}here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow})
         \begin{align}
@@
 
-		    \textbf{Prediction after system damaged}:\linelabel{line:r2-cutting} \ac{OurTheory} and IIT lead to different predictions when a system suffers from a damage.
+		    \textbf{Prediction after system damaged}: \ac{OurTheory} and IIT lead to different predictions when a system suffers from a damage.
 For example, considering a densely connected networks whose dynamics forms an NTIC process.
@@
 In contrast, \ac{OurTheory} would predict that this operation may completely destroy informational closure of the network and rendering both parts unconscious.
+\linelabel{line:r2-cutting}Nevertheless, this prediction is relatively premature.
+Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.
 
@@
 They mainly passively react to sensory inputs or other processes in the neural system.
-To the conscious (NTIC) process, the rest of the neural system and the body are parts of the environment, and they retains some degree of activity during sleep and dreaming.
+To the conscious (NTIC) process, the rest of the neural system and the body should be also considered as part of the environment.
+They retains some degree of activities during sleep and dreaming.
 We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.

### 2020-04-16 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

@@
 Based on our hypothesis, if the dynamics of a molecular complex is an NTIC process, the information closure theory of consciousness (ICT) would claim that the molecular complex has a certain degree of consciousness.
-            % Therefore, to your question, it is theoretically plausible under the framework of ICT.
-We speculate that it may be easy to find informationally closed molecular complexes (isolated complexes) but may not be easy to find ones forming NTIC processes.
-This is an empirical and testable question under the ICT.
-We look forward to learning any self-assembly process forming NTIC at molecular scales in the near future.
         \end{ans}
@@
             We can see how Figure 4 was ambiguous with respect to this question. We do not impose the exclusion criterion in ICT and have changed Figure 4 to remove the impression that it does.
-            % A key feature of ICT is that, instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of system-environment separation and a boundary of a system \citep{BERTSCHINGER.2006}.
-For example, \citet{krakauer2014information,krakauer2020information} proposed an algorithm to add and remove variables in order to find the boundary.
-\\
-            % It is true that NTIC can be computed for every subset of a system and can also have a positive value of NTIC for multiple of those. 
-            It is true that every subset of a system can be a C-process and there can be multiple of those in a system.
-            % However, according to our definition, if these processes are not informationally closed to their environments (including the complement subset in the system), they are not C-processes, and thus ICT claims that they are not conscious.
-            % .
-In order to find whole or entire consciousnesses we can use the algorithm in \citet{krakauer2014information, krakauer2020information}.
-This algorithm adds variables to or removes variables from the system if this results in a reduction of transfer entropy from the corresponding environment.
-This means that consciousnesses are informationally closed subsets of variables.
+
+            Instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of individuality and defining the boundary of a system.
+\citep{BERTSCHINGER.2006}.
+This allows ICT to solve the individuality problem of consciousness in some cases (but not all, please see the paragraph in Limitation from Line~\lineref{line:individuality}) without imposing an exclusion criterion.
+Therefore, it is true that Krakauer's boundary detection procedure can potentially helpful and be adapted for ICT in the future.
 
@@
 This is in line with using informational closure in level identification \citep{PFANTE.2014}.
+
+            We understand that not solving individuality completely is one major weakness of the current version of ICT (and all IC and NTIC based theories).
+More work on this issue is needed in our following research.
+
     	\end{ans}
@@
 	    	To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment.
-This notion is shortly indicated at line \lineref{line:neu-env} in our original manuscript.
-There is no doubt that these processes are still active during sleep and dreaming.
+This notion is shortly indicated at line \lineref{line:neu-env} in our first version of the manuscript.
+These processes are still active during sleep and dreaming.
 We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e.
@@
 However, we thank the reviewer for bringing up this important question.
+This is also an empirical question that can and should be tested in future studies.
 We believe that this is still worth mentioning.
@@
 
-			\addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to all the theories of consciousness.
+			\addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to theories of consciousness.
 ICT currently does not have a certain answer to dreaming.
-However, we want to emphasise that not all the processes in the neural system are NTIC.
-Some processes in the neural system are not informationally closed.
+However, we want to emphasise that not all the processes in the neural system are NTIC since some processes are not informationally closed.
 They mainly passively react to sensory inputs or other processes in the neural system.
-To the conscious (NTIC) process, the rest of the neural system is part of the environment, and undoubtedly retains some degree of activity during sleep and dreaming.
+To the conscious (NTIC) process, the rest of the neural system and the body should be also considered as part of the environment.
+They retains some degree of activities during sleep and dreaming.
 We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
@@
 However, at the current stage, this is mere speculation.
-Searching for the NTIC process(es) during dreaming is a crucial step to extend the scope of ICT in future research.}
-
-	    	Finally, we believe that this is also an empirical question that can and should be tested in future studies.
+Searching for the NTIC process(es) during dreaming is a important step to extend the scope of ICT in future research.}
     	\end{ans}
@@
     			We have modified this as follows: \\
-    			"We propose a new theory of consciousness and discuss some preliminary implications."
+    			\textit{"We propose a new theory of consciousness and discuss some preliminary implications."}
 
@@
     			\revise{\lineref{line:lack-theory}}
-    			{We currently lack a theory to identify the scale which conscious processes correspond to.}
-    			{We currently have only few theories (e.g., Integrated Information Theory \citep{hoel2016can} and Geometric Theory of consciousness \citep{fekete2011towards,fekete2012lack}) to identify the scale which conscious processes correspond to (please also see the discussion in \cite{fekete2016system}).}
+    			{
+    			We currently lack a theory to identify the scale which conscious processes correspond to.
+    			}
+    			{
+    			We currently have only few theories (e.g., Integrated Information Theory \citep{hoel2016can} and Geometric Theory of consciousness \citep{fekete2011towards,fekete2012lack}) to identify the scale which conscious processes correspond to (also see the discussion in \cite{fekete2016system}).
+    			}
 
@@
     		We thank the reviewer for the critical comments. We have replied these comments in details in the following Q\&A. 
-%    		\begin{enumerate}
-%    			\item In this article, the definition of coarse-graining is our "Definition 1" (line: \lineref{line:r2q1-1}).
-Coarse-graining is simply a function which maps a stochastic process $X$ with state space $\mathcal{X}$ to a stochastic process $Y$ with state space $\mathcal{Y}$.
-As we explained in Footnote 2, functions in the mathematical sense used here are always either one-to-one or many-to-one.
-We do not constrain ICT to be applied to any specific classes of coarse-graining.
-%    			We thank the reviewer for proposing the question about the relationship between NTIC and scale of coarse-graining.
-We currently know that NTIC is not a non-monotonic function of the scale of coarse-graining.
-Some coarse-grainings lead to higher NTICs for macroscopic than microscopic processes.
-However, we are just starting the research on this relationship, and have not yet had a systematic understanding of it.
-This work may involve the technique of partial information decomposition and related research fields.
-%    			We agree that our original claim about existing a intermediate maxima in NTIC was too strong. 
-%    			
-%    			
-%    			We hope to address this question in future research. 
-%    			
-%    			
-%    			
-%    			We emphasise the non-monotonic relation between the scales of coarse-graining and the degrees of NTIC.
-However, we do not exclude the possibility that there exist multiple NTIC picks across scales of coarse-graining of a process.
-%    			This implies that we do not exclude the possibility that there exist multiple high conscious processes at different scales. 
-%    			(However, due to IC, conscious processes are not able to know the existence of each other. 
-%    			\revise{\lineref{line:non-monotonic}}
-%    			{
-%    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
-We saw above that not sufficiently coarse-grained variables have low values of NTIC.
-On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC.
-For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.
-Therefore, only processes at a certain level of coarse-graining in the neural system can form a high degree of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
-ICT indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
-%    			}
-%    			{
-%    				It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
-Insufficiently coarse-grained variables could lead to lower values of NTICs at micro than macroscopic processes.
-On the other hand, overly coarse-grained macroscopic variables also result in low values of NTIC.
-For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.
-Therefore, processes at certain levels of coarse-graining may have higher values of NTIC than other levels (Fig.~\ref{fig:LevelOfConsciousness}).
-ICT suggests that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
-%    			}										
-%    			\item 
-%    			\item
-%    		\end{enumerate}
-
     	\end{ans}
@@
     			\end{align}
-    			to the system-environment dependency
-                 and the micro-macro level dependency
+    			to the system-environment dependency and the micro-macro level dependency
                  \begin{align}
@@
     	\begin{ans}
-    	To make this point more clear, we have added a new paragraph and made a significant revision of this section from Line \lineref{line:non-monotonic} to Line  \lineref{line:non-monotonic_end}.
-
-% 		\revise{\lineref{line:non-monotonic}}
-% 		{
-% 			It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
-We saw above that not sufficiently coarse-grained variables have low values of NTIC.
-On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC.
-For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.
-Therefore, only processes at a certain level of coarse-graining in the neural system can form a high degree of NTIC (Fig.~\ref{fig:LevelOfConsciousness}).
-ICT indicates that human consciousness occurs at the level of coarse-graining where higher NTIC is formed within the neural system.
-% 		}
-% 		{
-% 		
-% 		}
+        	We understand that this section in the last version is very unclear.
+Therefore, to make this point clear, we have added a new paragraph and made a significant revision of this section.
+In short, we more formally describe how NTIC may change non-monotonically from the finest microscale to the coarsest macroscale.
+Please see our revised manuscript from Line \lineref{line:non-monotonic} to Line \lineref{line:non-monotonic_end}.
     	\end{ans}
@@
 
-    	    In this revision, we added a new subsection \ref{sec:causality} to describe the scenario of modelling.
-    		Also, to avoid the confusion We have revised the following sentence, changed "simulation" to "modeling", and added the reference.
-    		\revise{\lineref{line:encode}}
-    		{
-    			Importantly, NTIC processes encode environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics. }
-    		{
-    			Importantly, NTIC processes internalise the environmental dynamics in its states \citep[also see P.~4][]{BERTSCHINGER.2006}.
-This suggests that a NTIC process can be considered as a process that models the environmental dynamics.
-    		}
+    	    To avoid any confusion to our reader, in this revision, we added a new subsection \ref{sec:causality} to describe the scenario of modelling.
+    		Also, we replaced "simulation" and "encoding" with "modelling" in many places in this revision. We hope that this change can make our point more clear. 
     	\end{ans}
@@
    				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.
-However, in some cases, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}.
+(However, in some cases, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}.)
    			}
@@
 Note that most observation processes in the real world are not deterministic so that most passive adaptation processes aren't conscious.
-
  		\end{ans}
@@
     	\begin{ans}
-    		The reviewer is correct.
-This prediction is under an assumption which we did not explicitly specify in our last version.
         	We assume that we have one conscious (NTIC) process involving information in both brain hemispheres.
 Namely, the process is informationally closed only when we consider the information in both hemispheres.
-We agree that if both hemispheres have their own NTIC proceess ICT should predict no change of conscious experience before and after cutting.
+We agree that if both hemispheres have their own NTIC process ICT should predict no change of conscious experience before and after cutting.
 Cutting should not make any difference because they are informationally closed with respect to each other.
@@
 Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.
+We also weakened our statement by added the following sentence:
 
-    		\toWrite{The original paragraph has been changed as follows: lline \lineref{line:r2-cutting}:}
+        	\addnew{\lineref{line:r2-cutting}}{Nevertheless, this prediction is relatively premature.
+Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.
+}
+
     	\end{ans}
@@
     		We appreciate the reviewer to bring up the hard problem of consciousness and dreaming.
-    % 		This is a very good question and dreaming really poses a challenge for ICT.
+This is a very good question and dreaming really poses a challenge for ICT.
 At the moment we can only speculate about possible solutions.
-One possiblity to may be that during dreaming the environment extends further into the neural system and NTIC is achieved with respect to other parts of the brain e.g.
-the visual cortex.
-    % 		Another solution may come from using the memory extended version of NTIC. Dreams probably do maintain mutual information with the history of expereiences of a person.
-			We want to emphasise that not all the processes in the neural system are NTIC processes.
-This is evident since some processes in the neural system are not informationally closed.
-They only passively react to sensory inputs or other processes of the neural system.
-
-    		To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment.
+One point We want to emphasise is that not all the processes in the neural system are NTIC processes.
+To the conscious (NTIC) process, the rest of the neural system should be considered as part of the environment.
 This notion is shortly indicated at line \lineref{line:neu-env} in the original manuscript.
-There is no doubt that these processes are still active during sleep and dreaming.
 We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e.
@@
 
-    		\addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to all the theories of consciousness.
+            \addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to theories of consciousness.
 ICT currently does not have a certain answer to dreaming.
-However, we want to emphasise that not all the processes in the neural system are NTIC.
-This is evident since some processes are not informationally closed.
+However, we want to emphasise that not all the processes in the neural system are NTIC since some processes are not informationally closed.
 They mainly passively react to sensory inputs or other processes in the neural system.
-To the conscious (NTIC) process, the rest of the neural system is part of the environment, and undoubtedly retains some degree of activity during sleep and dreaming.
+To the conscious (NTIC) process, the rest of the neural system and the body should be also considered as part of the environment.
+They retains some degree of activities during sleep and dreaming.
 We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
@@
 However, at the current stage, this is mere speculation.
-Searching for the NTIC process(es) during dreaming is a crucial step to extend the scope of ICT in future research.}
+Searching for the NTIC process(es) during dreaming is a important step to extend the scope of ICT in future research.}
 
-    		Finally, we believe that this is also an
+    		Finally, we believe that this is a good
     		empirical question that can and should be tested in future studies. 

### 2020-05-15 ICT_Frontiers_rev202001.tex

@@
 		Information processing in neural systems can be described and analysed at multiple spatiotemporal scales.
-Generally, information at lower levels is more fine-grained and can be coarse-grained in higher levels.
-However, information processed only at specific scales of coarse-graining seems to be available for conscious awareness.
+Generally, information at lower levels is more fine-grained but can be coarse-grained at higher levels.
+However, only information processed at specific scales of coarse-graining appears to be available for conscious awareness.
 We do not have direct experience of information available at the scale of individual neurons, which is noisy and highly stochastic.
-Neither do we have experience of more macro-scale interactions such as interpersonal communications.
+Neither do we have experience of more macro-scale interactions, such as interpersonal communications.
 Neurophysiological evidence suggests that conscious experiences co-vary with information encoded in coarse-grained neural states such as the firing pattern of a population of neurons.
@@
 With the parsimonious definitions and a hypothesise, \ac{OurTheory} provides explanations and predictions of various phenomena associated with consciousness.
-The implications of \ac{OurTheory} naturally reconciles issues in many existing theories of consciousness and provides explanations for many of our intuitions about consciousness.
+The implications of \ac{OurTheory} naturally reconcile issues in many existing theories of consciousness and provides explanations for many of our intuitions about consciousness.
 Most importantly, \ac{OurTheory} demonstrates that information can be the common language between consciousness and physical reality.
@@
 		%% Story about a cell
-		Imagine you are a neuron in Alice's brain.
+		Imagine you are a neuron in Alice’s brain.
 Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials along axons.
-However, you have no idea that you are one of the neurons in Alice's supplementary motor area and involved in many motor control processes for Alice's actions, for example, grabbing a cup.
-You are ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.
-		A similar story also happens to Alice's conscious mind.
+However, you have no idea that you are one of the neurons in Alice’s supplementary motor area and are involved in many motor control processes for Alice’s actions, such as grabbing a cup.
+You are ignorant of intentions, goals, and motor plans that Alice has at any moment, even though you are part of the physiological substrate responsible for all these actions.
+A similar story also happens in Alice’s conscious mind.
 To grab a cup, for example, Alice is conscious of her intention and visuosensory experience of this action.
 However, her conscious experience does not reflect the dynamic of your membrane potential or the action potentials you send to other neurons every second.
-That is, not all information you have is available to Alice's conscious mind.
+That is, not all the information you have is available to Alice’s conscious mind.
 
@@
 
-		It seems to be true that we are not consciously accessing information processed at every scale in the neural system.
+		It appears to be true that we do not consciously access information processed at every scale in the neural system.
 There are both more microscopic and more macroscopic scales than the scale corresponding to the conscious contents.
-On the one hand, dynamics of individual neurons are stochastic \citep{Goldwyn2011, White2000}.
+On the one hand, the dynamics of individual neurons are stochastic \citep{Goldwyn2011, White2000}.
 However, what we are aware of in our conscious mind shows astonishing stability and robustness against the ubiquitous noise in the neural system \citep{mathis1995computational}.
@@
 These facts suggest that conscious processes occur at a particular scale.
-\linelabel{line:lack-theory}We currently have only few theories (e.g., Integrated Information Theory \citep{hoel2016can} and Geometric Theory of Consciousness \citep{fekete2011towards,fekete2012lack}) to identify the scale which conscious processes correspond to ( also see discussion in \cite{fekete2016system}).
+\linelabel{line:lack-theory}We currently have possess only a few theories (e.g., Integrated Information Theory \citep{hoel2016can} and Geometric Theory of Consciousness \citep{fekete2011towards,fekete2012lack}) to identify the scale to which conscious processes correspond (also see discussion in \cite{fekete2016system}).
 We refer to this notion as \textbf{the scale problem of consciousness} (Fig.~\ref{fig:scaleproblem}).
@@
 		%% our argument
-		In this article, we propose a new information-based theory of consciousness, called \acf{OurTheory}.
+		In this article, we propose a new information-based theory of consciousness, called the  \acf{OurTheory}.
 We argue that every process with a positive non-trivial information closure (NTIC) has consciousness.
@@
 We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC.
-(for a discussion of the distinction between level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
+(For a discussion of the distinction between level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
 
@@
 We next argue that through coarse-graining the neural system can form informational closure and a high degree of NTIC at a specific scale of coarse-graining  (Sec.~\ref{sec:Neural coarse-graining}).
-In the Sec.~\ref{sec:OurTheory}, we propose a new theory of consciousness (\ac{OurTheory}).
+In Sec.~\ref{sec:OurTheory}, we propose a new theory of consciousness (\ac{OurTheory}).
 We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies (Sec.~\ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (Sec.\ref{sec:Comparison with other theories}).
-Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from \ac{OurTheory} to the current consciousness science (Sec.\ref{sec:Limitation and Future work}).
+Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications of \ac{OurTheory} on the current consciousness science (Sec.\ref{sec:Limitation and Future work}).
 
@@
 	\section{Non-trivial Informational Closure} \label{sec:Non-trivial informational closure}
-		The notion of non-trivial informational closure (NTIC) is introduced by \cite{BERTSCHINGER.2006}.
+		The notion of non-trivial informational closure (NTIC) was introduced by \cite{BERTSCHINGER.2006}.
 The concept of closure is closely related to system identification in systems theory.
 One can distinguish a system from its environment by computing the closedness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}.
-The closedness can be further quantified by information theory.
+Closedness itself can be further quantified by information theory.
 
 		% Definition of informational closure
-			\linelabel{line:r1q1a}Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system's process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network with the sensor channel $\hat{e}_{t}$ and the action $\hat{y}_{t}$ channel in Fig.~\ref{fig:SystemAndEnv}.
-Then, information flow $J_{t}$ from the environment $E$ to a system $S$ at time $t$ can be defined as the conditional mutual information $I$ between the current environment state $E_{t}$  and the future system state $Y_{t+1}$ given the current system state $Y_{t}$
+			\linelabel{line:r1q1a}Consider two processes, the environment process $(E_t)_{t \in \mathbb{N}}$ and the system process $(Y_t)_{t \in \mathbb{N}}$ and let their interaction be described by the Bayesian network with the sensor channel $\hat{e}_{t}$ and the action $\hat{y}_{t}$ channel in Fig.~\ref{fig:SystemAndEnv}.
+Information flow $J_{t}$ from the environment $E$ to a system $S$ at time $t$ can then be defined as the conditional mutual information $I$ between the current environment state $E_{t}$  and the future system state $Y_{t+1}$ given the current system state $Y_{t}$
 
@@
 					\includegraphics[width=\textwidth]{Submission/Frontiers/SystemAndEnv_3.pdf}
-					\caption{The dependencies between a system  $Y$ and its environment $E$ through the channels $\hat{y_t}$ and $\hat{e_t}$.} % Figure adapted from \cite{BERTSCHINGER.2006}
+					\caption{Dependencies between a system  $Y$ and its environment $E$ through the channels $\hat{y_t}$ and $\hat{e_t}$.} % Figure adapted from \cite{BERTSCHINGER.2006}
 					\label{fig:SystemAndEnv}
@@
 			\noindent
-			\cite{BERTSCHINGER.2006} defines that a system is informationally closed when information flow from the environment to the system is zero.
+			\cite{BERTSCHINGER.2006} defines a system as informationally closed when information flow from the environment to the system is zero.
 
@@
 			\noindent
-			This implies the system contains in itself all the information about its own future and the self-predictive information contains the information about the environment.
+			This implies that the system contains within itself all the information about its own future and the self-predictive information contains the information about the environment.
 
 			\subsection{Informational Closure Does not Imply Causality}\label{sec:causality}
-                A surprising result from the definition of information flow $J_t(E\rightarrow Y)$ (Eq.~\ref{eq:InformationFlow}) is that information flow does not indicate causal dependency from $E_t$ to $Y_{t+1}$ and from $Y_t$ to $Y_{t+1}$.
-Here we consider two scenarios, called \textit{modelling} and \textit{passive adaptation}, which were already noted by \citet{BERTSCHINGER.2006}.
-In both scenarios, a process can form positive NTIC ($NTIC(E\rightarrow Y)> 0$) and informational closure ($J(E\rightarrow Y)=0$), however, via different causal dependencies.
+                A surprising result from the definition of information flow $J_t(E\rightarrow Y)$ (Eq.~\ref{eq:InformationFlow}) is that information flow does not indicate causal dependency from $E_t$ to $Y_{t+1}$ or from $Y_t$ to $Y_{t+1}$.
+Here we consider two scenarios, called \textit{modelling} and \textit{passive adaptation}, which previously noted by \citet{BERTSCHINGER.2006}.
+In both scenarios, a process can form positive NTIC ($NTIC(E\rightarrow Y)> 0$) and informational closure ($J(E\rightarrow Y)=0$), albeit via different causal dependencies.
 
@@
 
-                In the scenario of \textit{passive adaptation}, counterintuitively, the future system states ($Y_{t+1}$) are  entirely driven by the current environment states ($E_t$) but can also have positive NTIC and informational closure.
+                In the \textit{passive adaptation} scenario, counterintuitively, the future system states ($Y_{t+1}$) are  entirely driven by the current environment states ($E_t$) but can also have positive NTIC and informational closure.
 This happens under the condition that the sensory process $\hat{e}_t$ is deterministic and the system simply copies the sensory values.
@@
 
-                However, in most of the realistic cases, the environment is partially observable to the system and, thus, the sensory process is usually not deterministic.
-Therefore, it is difficult for the system to be informationally closed and have higher NTIC.
-                More importantly, we argue in Appendix that whenever the environment has itself more predictable dynamics than the observations, there is potential for a process to achieve higher NTIC by modelling the environment than by copying the observations.
+                In most of the realistic cases, however, the environment is partially observable to the system, and thus the sensory process is usually not deterministic.
+Accordingly, it is difficult for the system to be informationally closed and have higher NTIC.
+                More importantly, we argue in the Appendix that whenever the environment has itself more predictable dynamics than the observations, there is the potential exists for a process to achieve higher NTIC by modelling the environment rather than by copying the observations.
 
@@
 NTIC requires the predictability of the system state and is therefore impeded by noise in the system.
-Information processing at the microscopic scale (the cellular scale) in neural systems suffers from multiple environmental noise sources such as sensor, cellular, electrical, and synaptic noises.
+Information processing at the microscopic scale (cellular scale) in neural systems suffers from multiple environmental noise sources such as sensor, cellular, electrical, and synaptic noises.
 For example, neurons exhibit large trial-to-trial variability at the cellular scale, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
@@
         %% Our argument
-		However, it is possible that neural systems form NTIC at certain macroscopic scales through coarse-graining of microscopic neural states.
+		Nevertheless, it is possible that neural systems form NTIC at certain macroscopic scales through coarse-graining of microscopic neural states.
 Coarse-graining refers to many-to-one or one-to-one maps which aggregate microscopic states to a macroscopic state.
 In other words, a number of different micro-states correspond to the same value of the macro-variable \citep{price2007causation}.
-Coarse-grainings, can therefore form more stable and deterministic state transitions and more often form NTIC processes.
+Coarse-grainings can therefore form more stable and deterministic state transitions and more often form NTIC processes.
 For neural systems this means that a microscopically noisy neural system may still give rise to an NTIC process on a more macroscopic scale.
 
-		Indeed, empirical evidence suggests that coarse-graining is a common coding strategy to establish robustness against noise at microscopic scales of the neural system.
+		Indeed, empirical evidence suggests that coarse-graining is a common coding strategy of the neural system by which it establishes robustness against noise at microscopic scales.
 For instance, the inter-spike intervals of an individual neuron are stochastic.
@@
 the average spike counts over a given time interval, is more stable and robust against noise such as the variability in inter-spike intervals.
-Using this temporal coarse-graining strategy, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}, neurons can encode stimulus intensity by increasing or decreasing the firing rate \citep{kandel2000principles}.
+Using this temporal coarse-graining strategy, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}, neurons can encode stimulus intensity by increasing or decreasing their firing rate \citep{kandel2000principles}.
 \citep{stein2005neuronal}.
-The robustness of the rate coding is a direct consequence of the many to one mapping (i.e., coarse-graining).
+The robustness of rate coding is a direct consequence of the many-to-one mapping (i.e., coarse-graining).
 
@@
 		Population coding is another example of encoding information through coarse-graining in neural systems.
-In this coding scheme, information is encoded by activation patterns of a set of neurons (a neuron population).
-In the population coding scheme, many states for a neuron population map to the same state of macroscopic variables which encode particular informational contents, thereby reducing the influence of noise in individual neurons.
+In this coding scheme, information is encoded by the activation patterns of a set of neurons (a neuron population).
+In the population coding scheme, many states of a neuron population map to the same state of macroscopic variables which encode particular informational contents, thereby reducing the influence of noise in individual neurons.
 That is, stable representations can be formed through coarse-graining the high dimensional state space of a neuron population to a lower dimensional macroscopic state space \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
-Therefore, individual neuron states (the microscopic scale) are not informative enough about the complete encoded contents at the population scale (the macroscopic scale).
+Therefore, individual neuron states (microscopic scale) are not sufficiently informative about the complete encoded contents at the population scale (macroscopic scale).
 Instead, coarse-grained variables are better substrates for stably encoding information and allow the neural system to ignore noisy interactions at the fine-grained scale \citep{Woodward2007-WOOCWA}.
@@
         These two examples show that the known coding schemes can be viewed as coarse-graining, and provide stochastic neural systems with the ability to form more stable and deterministic macroscopic processes for encoding and processing information reliably.
-We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic scales.
+We argue that coarse-graining allows neural systems to form NTIC processes at macroscopic scales.
 Based on the merit of coarse-graining in neural systems, we propose a new theory of consciousness in the next section.
@@
 % ============================================================================ %
-	\section{\acf{OurTheory}}\label{sec:OurTheory}
-
-        In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory}.
+	\section{\acl{OurTheory}}\label{sec:OurTheory}
+
+        In this section, we propose a new theoretical framework of consciousness: the \acf{OurTheory}.
 The main hypothesis is that conscious processes are captured by what we call \textit{C-processes}.
@@
 	   	% ------------------------------- definition 1 ------------------------------- %
-	   	In order to define C-processes we need to define coarse-grainings first.
+	   	To define C-processes we first need to define coarse-grainings.
 Every coarse-graining is characterised by a function that maps the microscopic process to the coarse-grained macroscopic process.
@@
 	   	\end{definition}
-	   	A more general definition of coarse-grainings that maps temporally extended sequences of the microscopic process to macroscopic states are possible but for this first exposure of our theory the simpler definition above is sufficient.
+	   	A more general definition of coarse-grainings that maps temporally extended sequences of the microscopic process to macroscopic states are possible, but for this first exposure of our theory the simpler definition above is sufficient.
 
@@
         \end{align}
-        Even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).\\
+        even though the Bayesian graphs differ in the two scenarios. Both these settings have been previously used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}.\\
 
@@
 To be informationally closed with respect to $X$, no coarse-graining knows anything about the conscious process' future that the conscious process does not know itself.
-This self-determining characteristics is also in line with our daily life conscious experience which often shows stability and continuity and is ignorant of the stochasticity (e.g., noise) of the cellular scales.
+This self-determining characteristics is also consistent with our daily life conscious experience which often shows stability and continuity and is ignorant of the stochasticity (e.g., noise) of the cellular scales.
 
@@
             \item[Implication 5.]
-            Conscious processes can model environmental information (by forming NTIC), however, be ignorant to part of the information of more microscopic processes (from Implication 3 and 4).
-This is in line with our conscious experience that information that every conscious percept provides represent rich and structured environmental states without involving all the information about microscopic activities.
+            Conscious processes can model environmental information (by forming NTIC) but be ignorant to part of the information of more microscopic processes (from Implication 3 and 4).
+This is consistent with our conscious experience, namely that the information that every conscious percept provides represents rich and structured environmental states without involving all the information about microscopic activities.
         \end{description}
@@
             This implies that a highly NTIC process must have rich dynamics with self-predictability over time.
-Another implication is that complex systems can potentially attain higher levels of consciousness due to the larger information capacities needed to attain high mutual information.
+Another implication is that complex systems can potentially attain higher levels of consciousness due to the greater information capacities needed to attain high mutual information.
 This outcome is consistent with the common intuition that conscious levels are often associated with the degree of complexity of a system.
@@
 At the finest scale we consider the whole universe $X$ as the process $Y$.
-then, since $Y$ is a coarse graining of $S$ we have $Y=S=X$.
+Then, since $Y$ is a coarse-graining of $S$ we have $Y=S=X$.
 In this case the environment $E$ corresponding to the universe seen as a system is the constant coarse-graining\footnote{Recall that, for a system with state space $\S$ the environment state space $\E$ must be such that $\X=\S \times \E$.
@@
 All coarse-grainings mapping $\X$ to a singleton set are constant over $\X$.} and therefore the mutual information $I(E_t;Y_{t+1})$ and the transfer entropy $I(Y_{t+1};E_t|Y_t)$ are zero.
-Then NTIC of the universe with respect to its environment is zero and $X$ can never be a C-process.
+The NTIC of the universe with respect to its environment is then zero, and $X$ can never be a C-process.
 
@@
 Up to the point where $E$ accounts for half of the bits of $X$ and $S$ for the other half the upper bound of the mutual information $I(E_t;Y_{t+1})$ achieved when $Y=S$ increases.
-Even further refining $E$ then again leads to a reduction of the upper bound of $I(E_t;Y_{t+1})$.
+Refining $E$ even further again leads to a reduction of the upper bound of $I(E_t;Y_{t+1})$.
             % ==================================== %
@@
 
-    		On the other extreme, when $E=X$ the system state space must be the singleton set and NTIC from $E$ to $Y$ must again be zero.
-Therefore, processes at intermediate scales of coarse-graining can form higher degrees of NTIC than at the most microscopic or macroscopic scales (Fig.~\ref{fig:LevelOfConsciousness}).
+    		At the other extreme, when $E=X$ the system state space must be the singleton set and NTIC from $E$ to $Y$ must again be zero.
+Therefore, processes at intermediate scales of coarse-graining can form higher degrees of NTIC than those at the most microscopic or macroscopic scales (Fig.~\ref{fig:LevelOfConsciousness}).
 \ac{OurTheory} suggests that human consciousness occurs at a scale of coarse-graining where high NTIC is formed within the neural system.
@@
         		\includegraphics[width=\textwidth]{Submission/Frontiers/nonMono.pdf}
-        		\caption{A non-monotonic relationship between scale of coarse-graining and level of consciousness.}
+        		\caption{A non-monotonic relationship between the scale of coarse-graining and level of consciousness.}
         		\label{fig:LevelOfConsciousness}
@@
 
-		\subsection{Conscious Contents Corresponding to States of a NTIC Process}\label{sec:cc}
+		\subsection{Conscious Contents Corresponding to States of an NTIC Process}\label{sec:cc}
     	    % richness 
     		\ac{OurTheory} proposes that conscious contents correspond to the states of NTIC processes (Eq.~\ref{eq:cContent}).
-This implies that the size of the state space of an NTIC process is associated with the richness of conscious contents that the process can potentially have.
-Therefore, a complex NTIC process with a high dimensional state space can have richer conscious experience than a simple NTIC process can have.
+This implies that the size of the state space of an NTIC process is associated with the richness of the conscious contents that the process can potentially have.
+Accordingly, a complex NTIC process with a high dimensional state space can have richer conscious experience than a simple NTIC process.
 This outcome is consistent with the intuition that the richness of conscious contents is associated with the complexity of a system.
@@
     		Informational closure can happen between scales of coarse-graining within a single system.
-Thus, a macroscopic NTIC process can be ignorant to its microscopic states.
+Thus, a macroscopic NTIC process can be ignorant of its microscopic states.
 \ac{OurTheory} argues that human conscious contents do not reflect cellular scale activity because the conscious process which corresponds to a macroscopic NTIC process is informationally closed to the cellular scale in the human neural system.
 Further more, since NTIC processes are informationally closed, each of them can be considered as a reality.
-When the information flow from its microscopic processes and environment to the informationally closed process is completely zero (Eq.~\ref{eq:informationflow2}), the future states of the process can entirely be determined by its past states.
-
-    		\linelabel{line:encode}Importantly, in most of the realistic cases, NTIC processes internalise the environmental dynamics in its states (see Sec.
+When the information flow from its microscopic processes (and from the environment) to it is zero (Eq.~\ref{eq:informationflow2}), the future states of the process can be entirely self-determined by its past states.
+
+    		\linelabel{line:encode}Importantly, in most realistic cases, NTIC processes internalise the environmental dynamics in its states (see Sec.
 \ref{sec:causality} and also \cite{BERTSCHINGER.2006}).
-This suggests that a NTIC process can be considered as a process that models the environmental dynamics.
+This suggests that an NTIC process can be considered as a process that models the environmental dynamics.
 This implication fits well with several theories of consciousness (for example, world simulation metaphor ~\citep{revonsuo2006inner}).
@@
 
-            Finally, a coarse-graining can be a many to one map from microscopic to macroscopic states and \ac{OurTheory} proposes that conscious contents $C^{Content}$ is the state of the NTIC process $Y$.
-Therefore, \ac{OurTheory} implies multiple realisation thesis of consciousness \citep{putnam1967psychological,bechtel1999multiple} which suggests that different physical implementations could map to the same conscious experience.
+            Finally, a coarse-graining can be a many-to-one map from microscopic to macroscopic states and \ac{OurTheory} proposes that conscious contents $C^{Content}$ is the state of the NTIC process $Y$.
+\ac{OurTheory} therefore implies the multiple realisation thesis of consciousness \citep{putnam1967psychological,bechtel1999multiple}, which suggests that different physical implementations could map to the same conscious experience.
 
@@
 	    \subsection{Reconciling the Levels and Contents of Consciousness}\label{sec:reconcile}
-    	    While it is useful to distinguish the notion of the levels and contents of consciousness, whether they can be clearly dissociated has been a matter of debate \citep{bayne2016there, Fazekas2016}.
-In \ac{OurTheory}, conscious levels and conscious contents are just two different properties of NTIC processes, and it therefore naturally reconciles the two aspects of consciousness.
+    	    While it is useful to distinguish the levels and contents of consciousness at the notion level, whether they can be clearly dissociated has been a matter of debate \citep{bayne2016there, Fazekas2016}.
+In \ac{OurTheory}, conscious levels and conscious contents are simply two different properties of NTIC processes, and the two aspects of consciousness are therefore naturally reconciled.
 In an NTIC process with a large state space, conscious contents should also consist of rich and high dimensional information.
-Therefore, this framework integrates the levels and the contents of consciousness in a coherent fashion by providing explicit formal definitions of the two notions.
+This framework therefore integrates the levels and the contents of consciousness in a coherent fashion by providing explicit formal definitions of the two notions.
 
     	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the state space of an NTIC process $Y$.
-A larger state space of $Y$ contributes conscious levels through the mutual information $I(Y_{t+1};Y_{t})$ and also contributes richer conscious contents by providing more possible states of conscious processes.
+A larger state space of $Y$ contributes conscious levels through the mutual information $I(Y_{t+1};Y_{t})$ and also contributes richer conscious contents by providing a greater number of possible states of conscious processes.
     	    \ac{OurTheory} therefore explains why, in normal physiological states, conscious levels and conscious contents are often positively correlated \citep{laureys2005neural}.
-This implication is also in line with the intuition in which consciousness is often associated with complex systems.
+This implication is also consistent with the intuition that consciousness is often associated with complex systems.
 
@@
 	\section{Conscious Versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
-	    In this section, we show how \ac{OurTheory} can explain and make predictions about what processes are more conscious than others.
-\ac{OurTheory} is constructed using information theory.
-Therefore, \ac{OurTheory} can provide predictions based on the mathematical definitions.
+	    In this section, we show how \ac{OurTheory} can explain and make predictions about which processes are more conscious than others.
+\ac{OurTheory} is constructed using information theory and can provide predictions based on mathematical definitions.
 
@@
 When the information flow is zero, the process is informationally closed with respect to the environment.
-                The first scenario is built upon the assumption that sensor processes are non-deterministic \footnote{Non-deterministic sensor processes here means $H(\hat{e}_{t+1}|\hat{e}_t)>0$.} and the process dynamics are passively driven by the environmental inputs.
+                The first scenario is built upon the assumption that sensor processes are non-deterministic \footnote{Non-deterministic sensor processes here means $H(\hat{e}_{t+1}|\hat{e}_t)>0$.} and that process dynamics are passively driven by  environmental inputs.
 Such processes cannot be informationally closed and are, therefore, unconscious.
 
-                Reflexive behaviours \citep{casali2013theoretically} can be considered as an example of this scenario.
-In \ac{OurTheory}, if we can view reflexive behaviours as situations in which (Fig.~\ref{fig:reflexive}) the internal state $Y_t$, which triggers reflexive action $\hat{y}_t$, is determined by the environment state $E_{t-1}$, overruling the influences from its own past $Y_{t-1}$.
+                Reflexive behaviours \citep{casali2013theoretically} can be considered an example of this scenario.
+In \ac{OurTheory}, we can view reflexive behaviours as situations in which (Fig.~\ref{fig:reflexive}) the internal state $Y_t$, which triggers reflexive action $\hat{y}_t$, is determined by the environment state $E_{t-1}$, overruling the influences from its own past $Y_{t-1}$.
 Such interpretation of reflexive behaviour from the viewpoint of \ac{OurTheory} naturally explains why reflexes involve less or no conscious experience of external stimuli.
@@
         			\caption{
-        			    A diagram depicting the information flow in reflexive behaviours (shown by the red nodes and arrows) happening through the interaction between a process $Y$ and its environment $E$.
-When the sensor process $\hat{e}_t$ is  non-deterministic and the internal state $Y_t$ is mostly dependent on the sensor state $\hat{e}_t$ driven by the environment $E_{t-1}$ but less on its past state $Y_{t-1}$.
-As a consequence, $Y$ is unable to form informational closure and, therefore, remain unconscious.}
+        			    Schema depicting the information flow in reflexive behaviours (shown by the red nodes and arrows) happening through the interaction between a process $Y$ and its environment $E$.
+When the sensor process $\hat{e}_t$ is  non-deterministic and the internal state $Y_t$ is mostly dependent on the sensor state $\hat{e}_t$ driven by the environment $E_{t-1}$ but less on its past state $Y_{t-1}$, as a consequence, $Y$ is unable to form informational closure and, therefore, remain unconscious.}
         			\label{fig:reflexive}
@@
 
-                The same principle can be applied to interpret blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedural memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes.
+                The same principle can be applied to interpret blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedural memory \citep{doyon2009contributions, ashby2010cortical} which are often considered unconscious processes.
         		\linelabel{line:r2q6}Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.(However, in some cases, they may still preserve some forms of conscious experience; See \cite{overgaard2011visual, mazzi2016blind}).
@@
 The corresponding neural circuits are driven passively and therefore are not informationally closed.
-According to \ac{OurTheory} we therefore have no conscious visual experience of visual the  stimuli.
+According to \ac{OurTheory} we therefore have no conscious visual experience of visual stimuli.
 
@@
 As mentioned in Sec.~\ref{sec:causality}, when the sensor processes are deterministic, a system can still have positive NTIC and achieve informational closure via passive adaptation.
-\linelabel{line:feedforward}Therefore, some passive system (for example pure feedforward networks) can potentially be conscious.\footnote{Since a $n$-layer feedforward network is a system with $n$-step memory it is technically appropriate to use the $n$-step memory definition of NTIC, i.e.~$NTIC^m_t(E\rightarrow Y):=I(Y_{t+1}:E_t,\dots,E_{t-n+1})-I(Y_{t+1}:E_t,\dots,E_{t-n+1}|Y_t)$ \citep{BERTSCHINGER.2006}, for such systems.
+\linelabel{line:feedforward}Therefore, some passive system (for example pure feedforward networks) can potentially be conscious.\footnote{Since an $n$-layer feedforward network is a system with $n$-step memory it is technically appropriate to use the $n$-step memory definition of NTIC, i.e.~$NTIC^m_t(E\rightarrow Y):=I(Y_{t+1}:E_t,\dots,E_{t-n+1})-I(Y_{t+1}:E_t,\dots,E_{t-n+1}|Y_t)$ \citep{BERTSCHINGER.2006}, for such systems.
 In this case the notion of non-deterministic input processes should be generalised to input processes with $H(\hat{e}_t|\hat{e}_{t-1},\dots,\hat{e}_{t-n})>0$.}
 
-                For agents such as human beings, the environment is often informationally rich but only partially observable in such a way that the current sensory inputs are insufficient to predict the next and to form deterministic sensor processes.
-In this circumstance, the system cannot become informationally closed by passive adaptation (e.g., simply copying the sensory values to the system).
-ICT predicts that, in most of the realistic cases, processes with passive adaptation are unconscious.
-On the other hand, networks with recurrent loops employ information stored in their own past states have the potential to achieve higher NTIC by modelling the environment.
-If it turns out to be true that for every pure feed-forward network there are non-feed-forward systems achieving higher NTIC then ICT predicts that the latter systems achieve higher levels of consciousness.
-This implication would coincide with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
+                For agents such as human beings, the environment is often informationally rich but only partially observable in such a way that the current sensory inputs are insufficient to predict the next inputs and to form deterministic sensor processes.
+In this situation, the system cannot become informationally closed by passive adaptation (e.g., simply copying the sensory values to the system).
+ICT predicts that, in most realistic cases, processes with passive adaptation are unconscious.
+On the other hand, networks with recurrent loops employing information stored in their own past states have the potential to achieve higher NTIC by modelling the environment.
+If it turns out to be true that for every pure feed-forward network there are non-feed-forward systems achieving higher NTIC, then ICT predicts that the latter systems achieve higher levels of consciousness.
+This implication coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
                 % Finally, with a caveat, when the sensory dynamics is deterministic, a system can still have positive NTIC and achieve informational closure by simply copying the sensory values to its internal state (i.e.
@@
                 The second scenario is that when encoded information in a process is trivial, i.e.
-no mutual information between the process states and its environment states $I(Y_{t+1};E_{t})$ (Eq.~\ref{eq:nticObjective2}), this leads to non-positive NTIC.
+there is no mutual information between the process states and the environment states $I(Y_{t+1};E_{t})$ (Eq.~\ref{eq:nticObjective2}), this leads to non-positive NTIC.
 In such cases, the process is considered to be unconscious.
@@
                 dealing with 
-                the boundary and the individuality problems of consciousness\footnote{The boundary problem of consciousness refers to identifying physical boundaries of conscious processes and the individuality problem of consciousness refers to identifying individual consciousnesses in the universe.}
+                the boundary and individuality problems of consciousness\footnote{The boundary problem of consciousness refers to identifying physical boundaries of conscious processes and the individuality problem of consciousness refers to identifying individual consciousnesses in the universe.}
                 \citep{Raymont2006-RAYUOC}.
-Consider a NTIC process $Y$ and an isolated informationally closed process $\hat{Y}$ with only trivial information.
+Consider an NTIC process $Y$ and an isolated informationally closed process $\hat{Y}$ with only trivial information.
 Adding $\hat{Y}$ to $Y$ can still maintain informational closure but does not increase non-trivial information, i.e.,  consciousness is unaffected.
@@
 
-                This implies that isolated processes with trivial information do not contribute consciousness and should be considered being outside the informational boundary of the conscious processing.
+                This implies that isolated processes with trivial information do not contribute consciousness and should be considered as being outside the informational boundary of the conscious processing.
                 % (for more details of the boundary detection procedure, see \cite{krakauer2014information}). 
-                This property also implies that consciousnesses do not emerge from just aggregating informationally closed (isolated) processes which contain trivial information.
+                This property also implies that consciousnesses do not emerge from simple aggregation of informationally closed (isolated) processes which contain trivial information.
                 In the future we hope to adapt the procedures for boundary detection proposed in \citet{krakauer2014information,krakauer2020information} to ICT.
@@
 		\subsection{Conscious Processing}\label{sec:conscious processing}
-		    According to \ac{OurTheory}, we claim that any process, system, or cognitive function which involves any NTIC process should be accompanied by conscious experience.
-
-		    Previous consciousness research has identified a number of diverse cognitive processes often accompanied by conscious experience.
-\ac{OurTheory} provides an integrated account for the reason why these processes involve conscious experience.
-As mentioned above, an NTIC process can be seen as an internal modelling engine for the agent-environmental interactions \citep{BERTSCHINGER.2006}.
+		    In accordance with \ac{OurTheory}, we claim that any process, system, or cognitive function which involves any NTIC process should be accompanied by conscious experience.
+
+		    Previous consciousness research has identified a number of diverse cognitive processes which are often accompanied by conscious experience.
+\ac{OurTheory} provides an integrated account of why these processes involve conscious experience.
+As mentioned above, an NTIC process can be seen as an internal modelling engine for agent-environmental interactions \citep{BERTSCHINGER.2006}.
 Therefore, information encoded in NTIC processes is essential for several cognitive processes.
 
-		    One of the most valuable information is the predictions about the environmental states.
-Cognitive functions requiring agent-scale environmental predictions are likely to recruit NTIC processes and therefore accompanied by conscious experience, for example planning and achieving long term goals.
-
-            Second, as a modelling engine, with a given initial state, an NTIC process can self-evolve and simulate the environmental transitions.
+		    Among the most valuable types of information are predictions about environmental states.
+Cognitive functions requiring agent-scale environmental predictions are likely to recruit NTIC processes, and to therefore be accompanied by conscious experience; examples include planning and achieving long term goals.
+
+            Second, as a modelling engine, an NTIC process with a given initial state can self-evolve and simulate the environmental transitions.
 Cognitive functions involving simulations are expected to involve NTIC processes.
@@
 This is crucial for many types of off-line processing.
-Therefore, in contrast to reflexive-like behaviours mentioned above (Sec.~\ref{sec:reflexive}), behaviours requiring off-line computations \citep{milner1999paradoxical, himmelbach2005dorsal,revol2003pointing} often involve conscious experience.
-
-    	    Finally, for agents adapting to complex environments (e.g., human being), any state of the NTIC process can be seen as an integration of high dimensional information.
-To accurately encode information about the complex environmental states and transitions, the NTIC process requires knowledge about the complex causal dependencies involved in the environment.
-Therefore, cognitive functions requiring larger scale integration are likely to involve NTIC processes and accompanied by conscious experience.
+Therefore, in contrast to reflexive-like behaviours, such as those mentioned above (Sec.~\ref{sec:reflexive}), behaviours requiring off-line computations \citep{milner1999paradoxical, himmelbach2005dorsal,revol2003pointing} often involve conscious experience.
+
+    	    Finally, for agents adapting to complex environments (e.g., human beings), any state of the NTIC process can be seen as an integration of high dimensional information.
+To accurately encode information about complex environmental states and transitions, the NTIC process requires knowledge about the complex causal dependencies involved in the environment.
+Cognitive functions requiring larger scale integration are therefore likely to involve NTIC processes and accompanied by conscious experience.
 % Furthermore, the high dimensional integrated information is also critical for an agent to learn new behaviours to achieve flexibility and the strategic behavioural controls and decision-making.
@@
 world simulation metaphor ~\citep{revonsuo2006inner}, predictive processing and Bayesian brain~\citep{clark_2013,Hohwy2013,seth2014predictive}, generative model and information generation~\citep{kanai_chang_yu_de_abril_biehl_guttenberg_2019}).
-Instead of relating functional or mechanistic aspects of a system to consciousness, \ac{OurTheory} captures common informational properties underlying those cognitive functions associated with consciousness.
-As such, \ac{OurTheory} does not assume any functionalist perspective of consciousness, which associate specific functions to consciousness.
-That is to say, since \ac{OurTheory} associates information  with consciousness, functional features accompanied by consciousness are collateral consequences of neural systems utilising NTIC processes for adaptive functions.
+Instead of relating functional or mechanistic aspects of a system to consciousness, \ac{OurTheory} captures common informational properties underlying those cognitive functions which are associated with consciousness.
+As such, \ac{OurTheory} does not assume any functionalist perspectives of consciousness, which associate specific functions to consciousness.
+That is to say, since \ac{OurTheory} associates information  with consciousness, functional features accompanied by consciousness are collateral consequences of neural systems which utilise NTIC processes for adaptive functions.
 
     	    In sum, we argue that cognitive functions involving the NTIC process are inevitably accompanied by consciousness.
-Having an NTIC process is potentially an effective approach to increase fitness in the evolution.
-It is likely that biological creatures evolve NTIC processes at some point in the evolution.
-Due to the fundamental relation between information and consciousness, biological creatures also evolve different degrees of consciousness depending on the physical scales and the complexity of the environments they adapt to.
-
-    	    \ac{OurTheory} starts with a non-functional hypothesis, however, it accounts for the association between  functional and consciousness.
-\ac{OurTheory} further demonstrates remarkable explanatory power for various findings of conscious and unconscious processing.
+Having an NTIC process is potentially an effective approach to increasing fitness in the evolutionary process.
+It is likely that biological creatures evolve NTIC processes at some point during their evolution.
+Due to the fundamental relation between information and consciousness, biological creatures also evolve different degrees of consciousness depending on the physical scale and complexity of the environments they adapt to.
+
+    	    Although it starts with a non-functional hypothesis, \ac{OurTheory} accounts for the association between function and consciousness.
+Further, \ac{OurTheory}  demonstrates remarkable explanatory power for various findings concerning conscious and unconscious processing.
 
@@
     		\ac{OurTheory} proposes that conscious processes can occur at any scale of coarse-graining which forms NTIC within a system.
-This suggests that the scale of coarse-graining is critical for searching and identifying the information corresponding to consciousness.
-A few versions of multilevel views on consciousness have previously been (explicitly or implicitly) proposed.
-To our knowledge, Pennartz's neurorepresentational theory (also called Neurorepresentationalism,~\citep{pennartz2018consciousness,pennartz2015brain}) is the proposal closest to the multilevel view of \ac{OurTheory}.
+This suggests that the scale of coarse-graining is critical for in searching for and identifying the information corresponding to consciousness.
+A few number of versions of multilevel views on consciousness have previously been (explicitly or implicitly) proposed.
+To our knowledge, Pennartz’s neurorepresentational theory (also called Neurorepresentationalism,~\citep{pennartz2018consciousness,pennartz2015brain}) is closest to the multilevel view of \ac{OurTheory}.
 Similar to Neurorepresentationalism, the concept of levels in \ac{OurTheory} is relevant to Marr's level of analysis~\citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}.
@@
 An NTIC process can be formed in a noise-free deterministic system without coarse-graining.
-According to \ac{OurTheory}, this NTIC process is sufficient to be conscious.
-    		Another fundamental difference between \ac{OurTheory} and Neurorepresentationalism is that Neurorepresentationalism takes functionalist perspective and suggests consciousness should serve high-level world-modelling and makes a best guess about the interaction between the body and the environment.
+According to \ac{OurTheory}, this NTIC process is sufficient for consciousness.
+    		Another fundamental difference between \ac{OurTheory} and Neurorepresentationalism is that Neurorepresentationalism takes a functionalist perspective and suggests that consciousness should serve high-level world-modelling and make a best guess about the interaction between the body and the environment.
     		%Neurorepresentationalism also suggests conscious experience is associated with integrated representation for multimodal and situational information.
-    		However, \ac{OurTheory} is grounded by non-functional informational hypothesis.
+    		In contrast, however, \ac{OurTheory} is grounded by a non-functional informational hypothesis.
 Therefore, \ac{OurTheory} provides a non-functional and fundamental explanation for the scale problem of consciousness.
@@
     		Another well-known proposal based on multilevel views is the Intermediate Level Theory of Consciousness \citep[ILT]{prinz2007intermediate, jackendoff1987consciousness}.
-ILT proposes that conscious experience is only associated with neural representations at intermediate \textbf{levels of the sensory processing hierarchy} (e.g., the 2.5D representation of visual processing) rather than lower (e.g., pixel) or higher (e.g., abstract) levels of the sensory hierarchy.
-
-    		Here, we want to make clear that the "level" in \ac{OurTheory} refers to the \textbf{scale of coarse-graining} instead of the "level" for the cortical anatomy or sensory processing.
-It is important to note that the coarse-graining direction is an orthogonal dimension irrespective of the level of anatomy or the level of information processing hierarchy in the neural system (see Fig.~\ref{fig:hierarchy}).
-Because ILT focuses on the levels of the sensory processing hierarchy and \ac{OurTheory} focus on informational closure among the levels of coarse-graining, the two theories are fundamentally different.
+ILT proposes that conscious experience is only associated with neural representations at intermediate \textbf{levels of the sensory processing hierarchy} (e.g., the 2.5D representation of visual processing), and not with lower (e.g., pixel) or higher (e.g., abstract) levels of the sensory hierarchy.
+
+    		Here, we want to make clear that "level" in \ac{OurTheory} refers to the \textbf{scale of coarse-graining}, rather than "level" in cortical anatomy or sensory processing.
+It is important to note that the coarse-graining direction is an orthogonal dimension irrespective of the level of anatomy or of information processing hierarchy in the neural system (see Fig.~\ref{fig:hierarchy}).
+Because ILT focuses the levels of the sensory processing hierarchy and \ac{OurTheory} focus on informational closure among the levels of coarse-graining, the two theories are fundamentally different.
 
@@
     			\includegraphics[width=\textwidth]{WritingMaterials/Fig_SeperationOfCGandCortHierachy/SeperationOfCGandCortHierachy.pdf}
-				\caption{The distinction between the level of coarse-graining and the level of the cortical hierarchy.
+				\caption{Distinction between the level of coarse-graining and the level of cortical hierarchy.
 $X$ and $Y$ represent the microscopic and macroscopic coarse-grained  variables, respectively.
-$X^0$ represents the microscopic states at the upstream of the cortical hierarchy.
-The red empty arrows represents the directions of coarse-graining and the blue arrows represent the directions of the physical dependencies in the cortical hierarchy from the upstream to the downstream.
+$X^0$ represents microscopic states upstream of the cortical hierarchy.
+The red empty arrows represents the directions of coarse-graining and the blue arrows represent the directions of the physical dependencies in the cortical hierarchy from upstream to downstream.
 (Some variables and dependencies are omitted for clarity.)}
@@
 		\subsection{Integrated Information Theory}
-            Integrated information theory (IIT) states that consciousness is integrated information and system's consciousness is determined by its causal properties \citep{tononi2016integrated}.
-\ac{OurTheory} is in line with IIT in that informational properties are thought to underlie consciousness.
+            Integrated information theory (IIT) states that consciousness is integrated information and that a system’s consciousness is determined by its causal properties \citep{tononi2016integrated}.
+\ac{OurTheory} is consistent with IIT in that informational properties are thought to underlie consciousness.
 In this section, we will discuss \ac{OurTheory} in the light of IIT.
 
-            \textbf{The concept of "information"}: In IIT, information refers to "integrated information":\\ \textquote[\citealt{tononi2016integrated}]{Information that is specified by a system that is irreducible to that specified by its parts.} In \ac{OurTheory}, information refers to "self-information", i.e.
+            \textbf{The concept of "information"}: In IIT, information refers to "integrated information", namely \textquote[\citealt{tononi2016integrated}]{Information that is specified by a system that is irreducible to that specified by its parts.} In \ac{OurTheory}, information refers to "self-information", i.e.
 information about the states of conscious experience and the physical states of a process.
@@
 
-		    \textbf{The "Exclusion" axiom in IIT}: In IIT, the Exclusion axiom claims that of all overlapping sets of elements, only one set with maximal integrated information can be conscious.
+		    \textbf{The "Exclusion" axiom in IIT}: In IIT, the Exclusion axiom claims that among all overlapping sets of elements, only one set, having maximal integrated information, can be conscious.
 The exclusion axiom should be applied over elements, space, time, and scales \citep{oizumi2014phenomenology, hoel2016can}.
-\linelabel{line:multi-consciousness}Different from IIT, \ac{OurTheory} allows multiple consciousnesses coexist across different scales of coarse-graining within a system if they are informationally closed from each other.
+\linelabel{line:multi-consciousness} Differing from IIT, ICT allows multiple consciousnesses to coexist across different scales of coarse-graining within a system if they are informationally closed from to each other.
 The two distinctive predictions decisively pinpoint the core concepts of the two theories.
 
-		    \textbf{The concept of "integration"}: In IIT, integrated information is one of the core concept of defining conscious individuals.
-In the current paper, we did not include the notion of integrated information within \ac{OurTheory}.
-This, however, results in one of the current weaknesses of \ac{OurTheory} that it lacks the ability to individuate NTIC processes in some cases (i.e., the problem of individuality).
-We discussed this weaknesses in Sec.~\ref{sec:Limitation and Future work}.
-
-		    \textbf{Prediction after system damaged}: \ac{OurTheory} and IIT lead to different predictions when a system suffers from a damage.
-For example, considering a densely connected networks whose dynamics forms an NTIC process.
-If we cut the network in half, IIT would predict that this results in two consciousnesses because elements in both networks still maintain high degrees of interactions.
-In contrast, \ac{OurTheory} would predict that this operation may completely destroy informational closure of the network and rendering both parts unconscious.
+		    \textbf{The concept of "integration"}: In IIT, integrated information is a core concept in defining conscious individuals.
+In the present paper, we do not include the notion of integrated information within ICT.
+However, this represents one of the current weaknesses of ICT, namely that it in some cases it lacks the ability to individuate NTIC processes (i.e., the problem of individuality).
+We discuss this weaknesses in Sec.~\ref{sec:Limitation and Future work}.
+
+		    \textbf{Prediction after system damage}: Prediction after system damage: ICT and IIT lead to different predictions when a system suffers from damage.
+Consider for example a densely connected network whose dynamics forms an NTIC process.
+If we cut the network in half, IIT predicts that this would result in two consciousnesses because elements in both networks still maintain high degrees of interaction.
+In contrast, ICT would predict that this operation might completely destroy informational closure of the network, and thereby render both parts unconscious.
 \linelabel{line:r2-cutting}Nevertheless, this prediction is relatively premature.
-Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.
+In the future, rigorous modelling studies will allow systematic comparisons between model predictions.
 
@@
     		Predictive processing (PP) is a powerful framework which integrates several ideas from neuroscience.
-This emerging theoretical framework posits that neural systems constantly generate predictions about incoming sensory signals and updates predictions based on prediction errors between predictions and sensory signals.
+This emerging theoretical framework posits that neural systems constantly generate predictions about incoming sensory signals and update predictions based on prediction errors between predictions and sensory signals.
 According to PP, neural systems constantly perform unconscious statistical inference about hidden causes in the external environment.
-The perceptual contents are the "best guess" about the environment states including these hidden causes \citep{clark_2013, Hohwy2013}.
+The perceptual contents are the "best guess" about those environment states which include these hidden causes \citep{clark_2013, Hohwy2013}.
 PP is well integrated with Bayesian brain hypothesis and has been used to interpret conscious perception in many domains \citep{Hohwy2013, seth2014predictive}.
@@
 However, to serve as a theory of consciousness, PP is still incomplete due to two explanatory gaps.
-First, it has been known that the neural system is equipped multiple predictive mechanisms.
-Apparently, not all the predictive mechanisms are involved in conscious processes (e.g.
+First, the neural system is equipped with multiple predictive mechanisms, but it appears that not all of these predictive mechanisms are involved in conscious processes (e.g.
 mismatch negativity, \cite{naatanen2007mismatch}).
@@
 It takes von Helmholtz's conception of perception as unconscious inference.
-Thus, only the most probable outcome computed by the inference processes can be conscious while other details of the computation remain unconscious.
-PP also needs to explain how unconscious inferences is able to give rise to conscious results.
+Thus, only the most probable outcome computed by the inference processes can be conscious, while other details of the computation remain unconscious.
+PP also needs to explain how unconscious inferences are able to give rise to conscious results.
 In short, while PP is often discussed in the context of consciousness, these explanatory gaps prevent PP from being a theory of consciousness.
@@
     		% compatible things
-    		\ac{OurTheory} is well compatible with PP.
-Crucially, \ac{OurTheory} further provides natural and fundamental explanations to fills the two explanatory gaps which PP encounters.
+    		ICT is well compatible with PP.
+Crucially, ICT further provides natural and fundamental explanations to fill the two explanatory gaps which hamper PP.
 According to the definition of NTIC, a process with high NTIC can be regarded as a powerful predictive machine which has accurate self-predictive information ($I(Y_{t+1};Y_{t})$, E.q.~\ref{eq:NTIC1}) and concurrently incorporates environmental information into its dynamic ($I(Y_{t+1};Y_{t}|E_{t})$, E.q.~\ref{eq:NTIC1}).
 This predictive nature of NTIC processes is in agreement with the core notion of PP in which the conscious contents are always the predicted (inferred) outcome of our predictive mechanisms.
-Second, due to the informational closure to the environment, the encoded information about its environment in an NTIC process can be seemed as "the best guess" about the external environment in the context of Bayesian inference.
+Second, due to the informational closure to the environment, the encoded information about its environment in an NTIC process can appear to be as "the best guess" about the external environment in the context of Bayesian inference.
 
     		% fill the gaps
-    		So, eventually, why are some predictive information conscious and some are not?
+    		Finally, therefore, why is some predictive information conscious and some are not?
 \ac{OurTheory} predicts that only the predictions generated from mechanisms involving the NTIC process are conscious.
-Note that predictive processes are not necessary to involve NTIC processes.
-A predictive process can make prediction about the future state of its environment solely based on the current sensor states when the current sensor states and future sensor states have positive mutual information.
+Note that it is not necessary for predictive processes to involve NTIC processes.
+A predictive process can make a prediction about the future state of its environment solely based on the current sensor states when the current sensor states and future sensor states have positive mutual information.
 However, this is not sufficient for a process to be informationally closed and, therefore, be conscious.
 
-            According to \ac{OurTheory}, we further propose that we can only be aware of the predictions from predictive processes due to informational closure to computational details of microscopic predictive processes.
-The macroscopic NTIC process only acquires the coarse-grained summary statistics of the microscopic processes.
+            Also in accordance with ICT, we further propose that we can only be aware of the predictions of predictive processes due to informational closure to computational details of microscopic predictive processes.
+Acquisition by the macroscopic NTIC process is limited to the coarse-grained summary statistics of the microscopic processes.
 In other words, we predict that the computation of the statistical inferences of PP is implemented at microscopic (cellular) scales in the neural system.
@@
     		% finally
-    		Finally, we consider PP as an potential empirical implementation of NTIC processes.
-To maintain accurate information about the environment encoded in an NTIC process, one can open an information channel between the process and the environment for minimal information flow to correct the divergence between them.
-This proposal is compatible with PP which suggests that PP systems updates (corrects) the current estimations by computing prediction errors between predicted and real sensory inputs.
+    		Finally, we consider that PP is a potential empirical implementation of NTIC processes.
+To maintain accurate information about the environment encoded in an NTIC process, one can open an information channel between the process and the environment to allow the minimal flow of information required to correct the divergence between them.
+This proposal is compatible with PP, which suggests that PP systems update (correct) the current estimations by computing prediction errors between predicted and real sensory inputs.
 
@@
 		\subsection{Sensorimotor Contingency}
-    		Sensorimotor contingency (SMC) theory of consciousness proposes that different types of SMCs give rise to different characteristics of conscious experience \citep{o2001sensorimotor}.
-The theory radically rejects the view that conscious content is associated with internal representations of a system.
-Rather, the quality of conscious experience depends on agents' mastery of SMCs.
-SMC emphasises that the interaction between a system and its environment determines conscious experience.
-
-    	    \ac{OurTheory} is not compatible with SMC.
-As mentioned in Sec.~\ref{sec:Conscious versus Unconscious Processing}, a process directly maps the sensory states to the action states is insufficient to be NTIC.
-Therefore, learning contingencies between sensory inputs and action outputs does not imply NTIC.
-Hence, \ac{OurTheory} predicts that having sensorimotor contingencies is neither a necessary nor a sufficient condition for consciousness.
+			The sensorimotor contingency (SMC) theory of consciousness proposes that different types of SMCs give rise to different characteristics of conscious experience  \citep{o2001sensorimotor}.
+The theory radically rejects the view that conscious content is associated with the internal representations of a system.
+Rather, the quality of conscious experience depends on the agent’s mastery of SMCs.
+SMC emphasizes that the interaction between a system and its environment determines conscious experience.
+
+    		ICT is not compatible with SMC.
+As mentioned in Sec.~\ref{sec:Conscious versus Unconscious Processing}, a process which directly maps the sensory states to the action states is insufficient to be NTIC.
+Therefore, learning contingencies between sensory inputs and action outputs do not imply NTIC.
+Hence, ICT predicts that having sensorimotor contingencies is neither a necessary nor a sufficient condition for consciousness.
 In fact, empirically, with extensive training on a sensorimotor task with a fixed contingency, the task can be gradually performed unconsciously.
 This indicates that strong SMCs do not contribute conscious contents.
-In contrast, \ac{OurTheory} suggests that, with extensive training, the neural system establishes a neural mapping from sensory inputs to action outputs.
-This decrease the level of informational closure and, as a result, decrease the conscious level of this process.
-This outcome more supports \ac{OurTheory} than SMC.
-
-    	    Nevertheless, \ac{OurTheory} does appreciate the notion that interactions between a process and its environment is crucial to shape conscious experience.
+In contrast, ICT suggests that, with extensive training, the neural system establishes a neural mapping from sensory inputs to action outputs.
+This decreases the level of informational closure and, as a result, decrease the consciousness level of this process.
+This outcome better supports ICT than SMC.
+
+    		Nevertheless, ICT does appreciate the notion that interactions between a process and its environment are crucial to shaping conscious experience.
 As mentioned above, to form NTIC, a process needs to encode environmental transitions into its own dynamic.
-Therefore, information of agent-environment interaction should also be encoded in the NTIC process, and therefore, shape conscious contents in a specific way.
-
-    	    Different from the classical SMC, a new version of SMC, Predictive Processing of SensoriMotor Contingencies (PPSMC), proposed by \cite{seth2014predictive, seth2015presence} combines SMC and the predictive processing framework together.
+Therefore, information of agent-environment interaction should also be encoded in the NTIC process, and thereby shape conscious contents in a specific way.
+
+    	    Different to classical SMC, a new version of SMC proposed by \cite{seth2014predictive, seth2015presence}, namely Predictive Processing of SensoriMotor Contingencies (PPSMC), combines SMC and the predictive processing framework together.
 PPSMC emphasises the important role of generative models in computing counterfactuals, inferring hidden causes of sensory signals, and linking fictive sensory signals to possible actions.
-According to \ac{OurTheory}, if the generative model involving the NTIC process for the computation of counterfactuals, PPSMC will be compatible to our theory and may have strong explanatory power on some specific conscious experience.
+According to ICT, if the generative model involves the NTIC process in the computation of counterfactuals, PPSMC will be compatible with our theory and may have strong explanatory power for some specific conscious experience.
 
@@
 		\subsection{Global Workspace Theory}
-		Global workspace theory (GWT; \cite{baars1988cognitive, baars1997theatre, baars2002conscious}) or Global Neuronal Workspace theory (GNWT; \cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental}) states that the neural system consists of several specialised modules and a central global workspace (GW) which integrates and broadcasts information gathered from those specialised modules.
-Only the information in the global workspace reaches conscious awareness, and information outside of it remains unconscious.
-These modules compete with each other to gain the access to the GW and the information from the winner triggers an all-or-none "ignition" in the GW.
-Information in the GW is broadcasted to other modules.
-Conscious contents then are associates with the information that gains access to the internal global workspace \cite{Dehaene2017}.
-
-        While GWT emphasises the importance of global information sharing as a basis of consciousness, the precise meaning of information broadcasting has been somewhat unclear if one tries to describe it more formally in the language of information theory.
-\ac{OurTheory} offers one possible way to consider the meaning of broadcasting in GWT.
-Specifically, one could interpret the global workspace as the network of nodes where information is shared at the scale of NTIC where communication is performed through macro-variables that are linked via mutual predictability.
-That is, global workspace should be also NTIC.
-While this link remains speculative at this point, this interpretation encourages empirical studies into the relationship between the contents of consciousness and macrostate neural activities that are mutually predictive of each other.
+		Global workspace theory (GWT; \cite{baars1988cognitive, baars1997theatre, baars2002conscious}) and Global Neuronal Workspace theory (GNWT; \cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental}) state that the neural system consists of several specialised modules, and a central global workspace (GW) which integrates and broadcasts information gathered from these specialised modules.
+Only the information in the global workspace reaches conscious awareness, while information outside of it remains unconscious.
+These modules compete with each other to gain access to the GW, and the information from the winner triggers an all-or-none "ignition" in the GW.
+Information in the GW is broadcast to other modules.
+Conscious contents are then associates with the information that gains access to the internal global workspace \citep{Dehaene2017}.
+
+        While GWT emphasises the importance of global information sharing as a basis of consciousness, the precise meaning of information broadcasting remains somewhat unclear if one tries to describe it more formally in the language of information theory.
+ICT offers one possible way to consider the meaning of broadcasting in GWT.
+Specifically, one could interpret the global workspace as the network of nodes wherein information is shared at the scale of NTIC and where communication is performed through macro-variables that are linked via mutual predictability.
+In other words, the global workspace should also be NTIC.
+While this link remains speculative, this interpretation encourages empirical studies into the relationship between the contents of consciousness and macrostate neural activities that are mutually predictive of each other.
 
@@
 % ============================================================================ %
-    \section{Limitation and Future Work}\label{sec:Limitation and Future work}  
-        As a brand new theory of consciousness, \ac{OurTheory} is still far from completion.
-In the following, we discuss the current limitations and challenges of \ac{OurTheory} and point out the potential future research directions.
+    \section{Limitations and Future Work}\label{sec:Limitation and Future work}  
+        As a completely new theory of consciousness, \ac{OurTheory} is still far from completion.
+In the following, we discuss the current limitations and challenges of \ac{OurTheory} and point out some potential future research directions.
 
@@
         % Can't solve the hard problem
-        It's important to clarify that \ac{OurTheory} does not intend to  solve the hard problems of consciousness \citep{chalmers1995facing}.
+        It is important to clarify that \ac{OurTheory} does not intend to  solve the hard problems of consciousness \citep{chalmers1995facing}.
 Knowing the state of a conscious process does not allow us to answer "What is it like to be in this state of this process" \citep{nagel1974like}.
-Instead, \ac{OurTheory} focuses more on bridging consciousness and the physical world using information theory as a common language in between.
+Instead, \ac{OurTheory} focuses more on bridging consciousness and the physical world using information theory as a common language between them.
 
@@
 However, in some specific circumstances, individuality of consciousness is not clear.
-        A more general problem of NTIC based individuality is that
+        A more general problem of NTIC-based individuality is that
         we can define a new process $Y$ and also its environment $E$ by recruiting two independent NTIC processes $Y^1~\&~Y^2$ and their environments $E^1~\&~E^2$, respectively.
-So that $Y = (Y^1,Y^2)$ and $E=(E^1,E^2)$.
-In such case, the new process $Y$ will also be NTIC to $E$.
-Therefore, the current version of \ac{OurTheory} cannot determine whether there are two smaller consciousnesses or one bigger consciousness (or 3 coexisting consciousnesses).
-The problem of individuality is a significant theoretical weakness of the current version of \ac{OurTheory}.
-The notion of integration is a possible remedy for this issue and we will address this issue more explicitly in our future work using the concept of synergy.
+Accordingly, $Y = (Y^1,Y^2)$ and $E=(E^1,E^2)$.
+In such a case, the new process $Y$ will also be NTIC to $E$.
+The current version of \ac{OurTheory} is therefore unable to determine whether there are two smaller consciousnesses or one bigger consciousness (or for that matter 3 coexisting consciousnesses).
+The problem of individuality is a significant theoretical weakness of the current version of ICT.
+The notion of integration is a possible remedy for this issue, and we will address it explicitly in our future work using the concept of synergy.
 
         % About the environment
-        The current version of \ac{OurTheory} assume that consciousness is only contributed by non-trivial rather than trivial information encoded in a process.
-In other words, how much information about environmental states and dynamics encoded in a process is a key quantity for consciousness.
-However, we do not exclude the possibility that environmental information may be just a proxy of other informational quantities.
+        The current version of ICT assumes that consciousness receives contribution from only non-trivial information, rather than trivial information encoded in a process.
+In other words, the amount of information about environmental states and dynamics encoded in a process is a key quantity for consciousness.
+However, we do not exclude the possibility that environmental information may simply be a proxy for other informational quantities.
 More theoretical work is needed to elucidate the role of environments.
@@
         \linelabel{line:r1-state-dep}In this article, we do not use a state-dependent formulation of NTIC.
-However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.
-Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed for the next version of ICT.
+However, we believe that state-dependent NTIC is essential to describing the dynamics of conscious experience.
+The next version of ICT therefore requires further research using point-wise informational measures to construct state-dependent NTIC.
 
         \linelabel{line:dream}Explaining conscious experience during dreaming is always a challenge to theories of consciousness.
-ICT currently does not have a certain answer to dreaming.
-However, we want to emphasise that not all the processes in the neural system are NTIC since some processes are not informationally closed.
+ICT currently does not have a specific answer to dreaming.
+However, we wish to emphasize that not all processes in the neural system are NTIC since some processes are not informationally closed.
 They mainly passively react to sensory inputs or other processes in the neural system.
-To the conscious (NTIC) process, the rest of the neural system and the body should be also considered as part of the environment.
-They retains some degree of activities during sleep and dreaming.
+To the conscious (NTIC) process, the rest of the neural system and the body should also be considered as part of the environment.
+They retain some degree of activity during sleep and dreaming.
 We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
 the other parts of the neural system.
-However, at the current stage, this is mere speculation.
-Searching for the NTIC process(es) during dreaming is a important step to extend the scope of ICT in future research.
+At present, however, this remains mere speculation.
+Identification of the NTIC process(es) during dreaming is an important milestone in extending the scope of ICT.
 
@@
         % finding the coarse-graining function 
-        Empirically, a major challenge to \ac{OurTheory} is to find proper coarse-graining functions which map microscopic processes to macroscopic NTIC processes.
-This will become an imperative issue of finding neurological supporting evidence for \ac{OurTheory}.
-To find proper coarse-graining functions among infinite candidates \citep{price2007causation} seem to be very challenging.
-Nevertheless, there are still theoretical and technical progresses recently that may contribute to  solving this issue.
+        Empirically, a major challenge to \ac{OurTheory} is to find appropriate coarse-graining functions which map microscopic processes to macroscopic NTIC processes.
+This issue will become imperative in the search for neurological evidence supporting \ac{OurTheory}.
+Identifying such coarse-graining functions among infinite candidates \citep{price2007causation} appears to be very challenging.
+Nevertheless, recent theoretical and technical progress may contribute to  solving this issue.
 For example, the concept of \textit{causal emergence} proposed by Hoel \citep{Hoel19790, Hoel2018} has been further developed recently.
 Causal emergence is highly relevant to the relationship between informational closure and coarse-graining.
-In their new study by \cite{klein2019uncertainty}, they started to compare how different coarse-graining functions influence causal emergence at macroscopic scales.
-\cite{PFANTE.2014, PFANTE.2014b} provides thorough mathematical analyses on level identification including informational closure.
-In neuroscience, the understanding of neural population codes also achieves a tremendous progress due to the advancement of recording technique and data science \citep{Kohn2016, panzeri2015neural}.
-\cite{Gamez2016} has also systematically described relevant issues in terms of finding data correlates of consciousness amount different levels of abstraction.
-We believe that interdisciplinary research is required to narrow down the scope of searching the coarse-graining functions and conscious processes at macro-scales in the neural system and beyond.
-
-        Finally another empirical challenge to \ac{OurTheory} is the  of empirical supporting evidence.
+In their new study, \cite{klein2019uncertainty}, start to compare how different coarse-graining functions influence causal emergence at macroscopic scales.
+\cite{PFANTE.2014, PFANTE.2014b} provide a thorough mathematical analysis of level identification, including informational closure.
+In neuroscience, an understanding of neural population codes has also made a tremendous progress due to advance in recording technique and data science \citep{Kohn2016, panzeri2015neural}.
+\cite{Gamez2016} has also systematically described relevant issues in finding data correlates of consciousness among different levels of abstraction.
+We believe that interdisciplinary research is required to narrow down the scope of search for coarse-graining functions and conscious processes at macro-scales in the neural system and beyond.
+
+        Finally, another empirical challenge to ICT is that of empirical supporting evidence.
 This is understandable because the concept of NTIC is relatively new in the history of information science, not to mention in neuroscience.
-Very few experiments and data collections are designed for examining NTIC properties in neural systems.
-To our knowledge, only two studies \citep{Palmer2015, sederberg2018learning} coincidentally examine relevant properties in salamander retina.
-They found that the a large group of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states.
-This result is in line with the characteristic of NTIC.
+Very few experiments and data collections examining NTIC properties in neural systems have yet appeared.
+To our knowledge, only two studies \citep{Palmer2015, sederberg2018learning} coincidentally examined relevant properties in salamander retina; these found that a large group of neural populations of retinal ganglion cells encoded predictive information about external stimuli and also had high self-predictive information about their own future states.
+This result is consistent with the characteristic of NTIC.
 We expect that there will be more empirical studies examining relevant neural properties of NTIC.
@@
     % short re-introduction 
-    In this paper, we introduced \textbf{\acf{OurTheory}}, a new informational theory of consciousness.
-\ac{OurTheory} proposes that a process which forms \textbf{non-trivial informational closure (NTIC)} is conscious and through coarse-graining the neural system can form NTIC processes, i.e., conscious processes, at a certain macroscopic scales.
-\ac{OurTheory} considers that information is a common language to bridge the gap between conscious experience and the physical reality.
+    In this paper, we introduce the \textbf{\acf{OurTheory}}, a new informational theory of consciousness.
+\ac{OurTheory} proposes that a process which forms \textbf{non-trivial informational closure (NTIC)} is conscious and through coarse-graining the neural system can form NTIC processes, i.e., conscious processes, at certain macroscopic scales.
+\ac{OurTheory} considers that information is a common language to bridge the gap between conscious experience and physical reality.
 Using information theory, \ac{OurTheory} proposes computational definitions for both conscious level and conscious content.
-This makes \ac{OurTheory} be able to generalise to any system beyond the human brains.
+This allows \ac{OurTheory} to be generalised to any system beyond the human brain.
 
     % For neuroscience    
-    \ac{OurTheory} provides explanation for various findings from research of conscious and unconscious processing.
-The implications of \ac{OurTheory} point out that the scales of coarse-graining play a critical role in searching for neural substrates of consciousness.
-Improper measurements, e.g., too fine or too coarse in terms of the scale of measurements, of neurophysiological signals may lead to misleading results and misinterpretations.
+    ICT provides an explanation for various findings from research into conscious and unconscious processing.
+The implications of ICT indicate that the scales of coarse-graining play a critical role in the search for neural substrates of consciousness.
+Improper measurement of neurophysiological signals, such as those which are excessively fine or coarse in scale, may lead to misleading results and misinterpretations.
 
@@
 \ac{OurTheory} indicates that they conditionally coincide with \ac{OurTheory}'s implications and predictions but, however, not the fundamental and sufficient conditions for consciousness.
-For example, theories includes the theories emphasising recurrent circuits \citep{lamme2006towards, edelman1992bright}, the theories highlighting the internal simulation,  predictive mechanism, and generative models ~\citep{revonsuo2006inner, clark_2013,Hohwy2013, kanai_chang_yu_de_abril_biehl_guttenberg_2019, seth2014predictive, seth2015presence}, and theories related to multilevel view of consciousness~\citep{pennartz2018consciousness,pennartz2015brain,prinz2007intermediate, jackendoff1987consciousness}.
-Notably, \ac{OurTheory} is proposed based on the non-functional hypothesis.
-Notwithstanding, its implications for the functional aspects of a system well fit several functionalist proposals.
+Example theories include those which emphasise recurrent circuits \citep{lamme2006towards, edelman1992bright}; highlight the internal simulation,  predictive mechanisms, and generative models ~\citep{revonsuo2006inner, clark_2013,Hohwy2013, kanai_chang_yu_de_abril_biehl_guttenberg_2019, seth2014predictive, seth2015presence}; and relate to multilevel view of consciousness~\citep{pennartz2018consciousness,pennartz2015brain,prinz2007intermediate, jackendoff1987consciousness}.
+Notably, while \ac{OurTheory} is proposed based on the non-functional hypothesis, its implications for the functional aspects of a system fit several functionalist proposals well.
 
@@
 	Regarding philosophy of mind, \ac{OurTheory} connects several distinct arguments together.
-\ac{OurTheory} can be seen as an identity theory because it assumes a fundamental relation between consciousness and information.
+First, \ac{OurTheory} can be seen as an identity theory because it assumes a fundamental relation between consciousness and information.
 Second, the implications of \ac{OurTheory} tightly link consciousness to several cognitive functions in the context of evolution.
@@
 \ac{OurTheory} emphasises that informational closure between scales of coarse-graining is critical to form NTIC processes in some stochastic systems.
-In this case, especially for the neural system, forming conscious processes at the macroscopic scales coincide with the perspective of emergentism.
+In this case, especially for the neural system, forming conscious processes at macroscopic scales coincides with the perspective of emergentism.
 Finally, forming NTIC (conscious) processes through many-to-one maps, i.e., coarse-graining, implies multiple realisability of consciousness.
@@
 	% Final 
-	So far, the current version of \ac{OurTheory} is still far from completion.
-Further theoretical and empirical research is indispensably required for \ac{OurTheory} to improve and solve several issues in the current version.
-Nevertheless, \ac{OurTheory} offers explanation and prediction for consciousness science.
-We hope that \ac{OurTheory} provides a new way of thinking and understanding neural substrates of consciousness.
+	The current version of ICT is still far from completion, and several outstanding issues mandate further theoretical and empirical research.
+Nevertheless, ICT offers an explanation and a prediction for consciousness science.
+We hope that ICT will provide a new way of thinking about and understanding of neural substrates of consciousness.
 
@@
 	A.C., Y.Y, and R.K.
-are funded by Japan Science and Technology Agency (JST) CREST project.
+are funded by the Japan Science and Technology Agency (JST) CREST project.
 Work by M.B.
@@
     \addcontentsline{toc}{section}{Conflict of Interest Statement}
-    All authors were was employed by the company Araya Inc.
+    All authors were employed by Araya Inc.
 The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
@@
             However, ignoring restrictions due to a possibly fixed choice of the universe process $X$ we find that for each such system there are other systems that achieve higher NTIC.
-For example define the system to be the "mirrored" and synchronized environment by setting $S_t:=E_t$.
-Then the transfer entropy vanishes
+For example, if we define the system to be the "mirrored" and synchronized environment by setting $S_t:=E_t$, then the transfer entropy vanishes
             \begin{align}
@@
             \end{align}
-            and the mutual information is equal to the mutual information between current and next environment state:
+            and the mutual information is equal to the mutual information between the current and next environment state:
             \begin{align}
@@
             \end{align}
-             In the case where the environment has itself higher predictive mutual information than the observations it produces i.e.\ when
+             In cases where the environment has itself higher predictive mutual information than the observations it produces - in other words, when
              \begin{align}                I(E_{t+1};E_t)\geq I(f(E_{t+1});f(E_t))
             \end{align}
-            there is then potential for a predictive process to achieve higher NTIC than a copying system or any system that only processes its last observations without taking into account other internal memory (i.e.\ those systems also applying $g$ to their observations).
-Note that this also holds true in the case where the observations are themselves closed.
-If there is a more complex environment behind them, the mirrored and synchoronized system has higher NTIC with respect to that environment than the system copying the observations.
+            there is then potential for a predictive process to achieve higher NTIC than a copying system or any system that only processes its last observations without taking account of other internal memory (i.e.\ those systems also applying $g$ to their observations).
+Note that this also holds true in cases where the observations are themselves closed.
+If there is a more complex environment behind them, the mirrored and synchronised system has higher NTIC with respect to that environment than the system copying the observations.
 

### 2020-05-15 ICT_Frontiers_rev202001_reply_rev1.tex

--- 2020-04-16 ICT_Frontiers_rev202001_reply.tex
@@
 % =================================== Title ================================== %
-\title{Response to Reviewers $Rev^1$}
+\title{Response to Reviewers (Revision 1)}
 \date{\today}
@@
     \maketitle
-    \section*{Reply to Editor}
-        \begin{question}
-        In addition, I have a question. if we view molecules as coarse grains of elementary particles, would the phenomenon of molecular recognition have high NTIC and thus be conscious?
-        \end{question}
-
-        \begin{ans}
-            Hi Prof. Hoffman,
-            Thank you for your attention to our manuscript and your interesting question. \\
-            If we understand correctly, molecular recognition refers to specific types of interactions among molecules that form molecular complexes.
-There is no question that molecular complexes are coarse-grainings of molecules via molecular recognition.
-Based on our hypothesis, if the dynamics of a molecular complex is an NTIC process, the information closure theory of consciousness (ICT) would claim that the molecular complex has a certain degree of consciousness.
-        \end{ans}
 
@@
     		\newline
-    		a) It is true it is true that the information flow term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$.
+    		a) It is correct that the information flow term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$.
 However, in Definition 2, a C-process is informationally closed to the microscopic universe process $X$.
-This implies C-process is also informationally closed to any other coarse-grainings of X including E (see also our reply to Q2).
-Currently, we only consider closed NTIC processes are C-processes.
+This implies that the C-process is also informationally closed to any other coarse-graining of X, including E (see also our reply to Q2).
+Currently, we only consider that closed NTIC processes are C-processes.
     		Regarding the video camera example, please see more discussion in our reply to your Q6. \\
@@
     		\noindent
-    		b) It is true that NTIC is not state-dependent.
-We agree that state-dependent measurements are essential to describe the dynamics of conscious experience.
+    		b) It is correct that NTIC is not state-dependent.
+We agree that state-dependent measurements are essential to describing the dynamics of conscious experience.
 We are working on state-dependent formulations for the next version of the ICT.
-In contrast to the current version, this work involves point-wise informational measures and requires more space and discussion.
-Therefore, we prefer to address the state-dependent version of ICT in future studies and keep the first version of our theory simple.\\
-    		We appreciated that the reviewer pointed this out. We have added a short paragraph about this issue.
+In contrast to the present version, this work involves point-wise informational measures and requires more space and discussion.
+We would therefore prefer to address the state-dependent version of ICT in future studies and keep the first version of our theory simple.
+
+    		Nevertheless, we appreciate that the reviewer’s raising of this issue, and have added a short paragraph about it:
 
@@
 	    		In this article, we do not use a state-dependent formulation of NTIC.
-However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.
-Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed for the next version of ICT.}
+However, we believe that state-dependent NTIC is essential to describing the dynamics of conscious experience.
+The next version of ICT therefore requires further research using point-wise informational measures to construct state-dependent NTIC.}
     	\end{ans}
@@
             At the same time it would be possible to remove $X$ from the definition and instead require that $Y$ is informationally closed with respect to all other processes.
-In some cases such a definition would be more general than the present one for example when there is no final microscale and instead there is an infinite number of more and more microscopic scales.
+In some cases such a definition would be more general than the present one for example when there is no final microscale but instead an infinite number of more and more microscopic scales.
 However, we find the use of an explicit microscale $X$ easier to understand and sufficient to communicate the idea.
 Note that closure with respect to $X$ (if it exists) implies closure with respect to every coarse-graining of $X$.
-            To see this note that the information transfer from any coarse-graining (including $E$ and $S$) of $X$ to $Y$ must be lower than that from $X$ to $Y$, i.e.
+            To grasp this, note that the information transfer from any coarse-graining (including $E$ and $S$) of $X$ to $Y$ must be lower than that from $X$ to $Y$, i.e.
 $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$.
-So that $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to $S, E$, and all other coarse-grainings of $X$.
+Accordingly, $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to $S, E$, and all other coarse-grainings of $X$.
         \end{ans}
@@
 This results in some interesting predictions.
-For example, the unpredicted sensory inputs may temporally break informational closure and ICT predicts that conscious agents may then lose consciousness for a short time.
+For example, unpredicted sensory inputs may temporally break informational closure and ICT predicts that conscious agents may then lose consciousness for a short time.
 Unfortunately, referring to your Q1b, the current version of ICT does not include state-dependent IC and NTIC.
 Therefore, the current formulation of ICT cannot well describe the dynamics of conscious experience under unpredictable states.
-We expect that our next version of ICT can better answer your question.
+We expect that our next version of ICT will be better able to answer your question.
 
@@
 \citep{BERTSCHINGER.2006}.
-This allows ICT to solve the individuality problem of consciousness in some cases (but not all, please see the paragraph in Limitation from Line~\lineref{line:individuality}) without imposing an exclusion criterion.
-Therefore, it is true that Krakauer's boundary detection procedure can potentially helpful and be adapted for ICT in the future.
+This allows ICT to solve the individuality problem of consciousness in some cases (but not all; please see the paragraph in Limitations from Line~\lineref{line:individuality}) without imposing an exclusion criterion.
+Therefore, it is true that Krakauer's boundary detection procedure is potentially helpful and can be adapted for ICT in the future.
 
@@
 
-            We understand that not solving individuality completely is one major weakness of the current version of ICT (and all IC and NTIC based theories).
-More work on this issue is needed in our following research.
+            We understand that not solving individuality completely is a major weakness of the current version of ICT (and in fact of all IC- and NTIC-based theories).
+More work on this issue is needed in our future research.
 
@@
         \begin{ans}
-        	The reviewer is right.
-We have reconsidered case of the feed-forward networks and the video camera example (which can be considered as a single layer feed-forward network).
-According to ICT, feed-forward networks can be conscious under for deterministic sensor processes.
-We thank the reviewer to correct this point.
-In this case also a video camera can achieve positive levels of NTIC and, therefore, be conscious.
-We have worked extensively on Section \ref{sec:causality} and Section 5 to make this clear (for Section 5, please see from Line:~\lineref{line:notIC}).
+        	The reviewer is correct.
+We have reconsidered the case of the feed-forward networks and the video camera example (which can be considered as a single-layer feed-forward network).
+According to ICT, feed-forward networks can be conscious for deterministic sensor processes.
+We thank the reviewer for correcting this point.
+In this case also, a video camera can achieve positive levels of NTIC and, therefore, be conscious.
+We have worked extensively on Sec.~\ref{sec:causality} and Sec.~\ref{sec:reflexive} to make this clear.
+In summary, we have mainly revised our manuscript as follows:
+
         % 	There we have weakened multiple claims in the original version of the manuscript.
@@
         	\begin{itemize}
-        	    \item Add Section \ref{sec:causality} to illustrate two NTIC scenarios about causality. 
-        	    \item Add sensory channels in Fig.~2
-        	    \item Extensively modify the paragraphs about feed-forward networks and memory in Section 5
-        	    \item Add a session in the Appendix to prove that NTIC achieved by modelling the environment can potentially achieve higher NTIC then the one by copying sensory values (e.g., the video camera).
+        	    \item Added Section \ref{sec:causality} to illustrate two NTIC scenarios about causality. 
+        	    \item Added sensory channels in Fig.~2
+        	    \item Extensively modified the paragraphs about feed-forward networks and memory in Section 5
+        	    \item Added a session in the Appendix to prove that NTIC achieved by modelling the environment can potentially achieve higher NTIC than the one which copies sensory values (e.g., the video camera).
         	\end{itemize}
@@
     	\begin{ans}
-	    	We want to emphasise that not all the processes in the neural system are NTIC processes, since some processes in the neural system are not informationally closed.
+	    	We want to emphasise that not all processes in the neural system are NTIC processes, since some processes in the neural system are not informationally closed.
 	    	To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment.
-This notion is shortly indicated at line \lineref{line:neu-env} in our first version of the manuscript.
+This notion is briefly indicated at line \lineref{line:neu-env} in our first version of the manuscript.
 These processes are still active during sleep and dreaming.
@@
 other parts of the neural system.
-However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our manuscript.
-However, we thank the reviewer for bringing up this important question.
+At present, however, this is mere speculation so we restrained ourself from making the statement in our manuscript.
+However, we refrained the reviewer for bringing up this important question.
 This is also an empirical question that can and should be tested in future studies.
@@
 
-			\addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to theories of consciousness.
-ICT currently does not have a certain answer to dreaming.
-However, we want to emphasise that not all the processes in the neural system are NTIC since some processes are not informationally closed.
+			\addnew{\lineref{line:dream}}{
+			Explaining conscious experience during dreaming is always a challenge to theories of consciousness.
+ICT currently does not have a specific answer to dreaming.
+However, we wish to emphasize that not all processes in the neural system are NTIC since some processes are not informationally closed.
 They mainly passively react to sensory inputs or other processes in the neural system.
-To the conscious (NTIC) process, the rest of the neural system and the body should be also considered as part of the environment.
-They retains some degree of activities during sleep and dreaming.
+To the conscious (NTIC) process, the rest of the neural system and the body should also be considered as part of the environment.
+They retain some degree of activity during sleep and dreaming.
 We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
 the other parts of the neural system.
-However, at the current stage, this is mere speculation.
-Searching for the NTIC process(es) during dreaming is a important step to extend the scope of ICT in future research.}
+At present, however, this remains mere speculation.
+Identification of the NTIC process(es) during dreaming is an important milestone in extending the scope of ICT.}
     	\end{ans}
@@
     		\begin{enumerate}
-    			\item It's true that we were also confused about it during submission. 
+    			\item In fact we were also confused about this during submission. 
     			We have modified this as follows: \\
@@
 
-    			\item We agree with the reviewer's comment. 
+    			\item We agree with the reviewer’s comment.
 In fact, we do not differentiate states of processes between activation and relation.
-Take neural network as an example; the relations between elements are determined by the topology of a network (structure) and its hyperparameters (e.g.
+To take neural networks as an example; : the relations between elements are is determined by the topology of a the network (structure) and its hyperparameters (e.g.
 activation functions).
-We agree that activation and relation of a neural network should be both considered.
-After all, they are all merely the parameters for the process of the neural network.
+We agree that the activation and relation of a neural network should be both be considered.
+After all, they are all of them merely the parameters for the process of the neural network.
 The only difference between the two groups of the parameters is the temporal scales of changes.
@@
 
-    \section{Reply to Reviewer 2}
-        \begin{question}
-			I had a few problems in reading the paper, which I think should be addressed (especially the first) before the paper is published. For detailed notes on these see below.
-
-			\begin{enumerate}
-				\item The coarse-graining idea seems undefined in critical ways, but the paper reads as though it is well-defined.
-So maybe the authors have compressed too much detail?
-In the formalism presented it is unclear what coarse-graining (or information closure to other grains) amounts to.
-With this lack of detail, it is then unclear to me why intermediate maxima in IC are a plausible result (why does IC not just decline with progressive coarse graining).
-
-				\item The idea of 'simulation'.
-This is a more minor point but I would appreciate if the authors could be clearer on this.
-It is arguable whether or not consciousness simulates anything (e.g.
-see Hoffman's interface theory); and some of the assertions the authors make re simulation seem unfounded anyways.
-But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)
-
-				\item There were several other assertions that stood out to me as strange or wrong, but could be a matter of explanation or ignorance on my part (the feedforward system, the cut-apart system).
-Either way some more explanation would be good.
-			\end{enumerate}
-        \end{question}
-
-    	\begin{ans}
-    		We thank the reviewer for the critical comments. We have replied these comments in details in the following Q\&A. 
-    	\end{ans}
-
-        \begin{question}
-			The English is not perfect and needs some good proofreading, though it was understandable throughout.
-        \end{question}
-
-    	\begin{ans}
-    		We have invited a native English speaker for proofreading. Please inform us if it is still not clear or unreadable. 
-    	\end{ans}
-
-    	\begin{question}
-			On line 182, defining C-processes as cases where 'Y is informationally closed to X'.
-This is now information closure in the sense of coarse-graining, but no such thing has been defined yet?
-Is it supposed to be so trivial that it is not required to make it explicit?
-To this point, closure is defined entirely in terms of system with respect to environment.
-
-			Basically, I am not sure whether closure between scales is a matter of same-time (e.g. $I(Y_{t+1};X_{t+1})$) or across-time interactions ($I(Y_{t+1};X_t)$). Or could it be both?    		
-    	\end{question}
-
-    	\begin{ans}
-    		We agree that this point is not clear.
-Even though the Bayesian graphs for the system-environment dependency are different from the one for the micro-macro level dependency, we apply the same definitions of information flow ($J_{t}(X \rightarrow $Y$ )$) and informational closure ($J_{t}(X \rightarrow $Y$ )=0$) to both graphs.
-
-    % 		This is a critical assumption in ICT because applying the same definition of informational closure in both scenarios can solve the scale problem of consciousness (informational closure from one level to other levels) and construct our hypothesis about the relation between NTIC and consciousness (informational closed from a process to its environment) in an integrated framework.
-
-    % 		In terms of the Bayesian graphs for the micro-macro level dependency and the definition of informational closure between scales, we followed the conventional setting (e.g.
-\cite{PFANTE.2014}).
-It is important to note that coarse-graining does not and should not take time $Y_t=f_Y(X_t)$ (also see our Definition 1).
-Coarse-graining is merely a function which maps microstates of a system to macrostates, and the microstates and the macrostates are only different level of descriptions of the same system.
-
-    % 		We agree that we did not indicate this assumption explicitly and may lead to some confusion for our readers. 
-    		We have added a paragraph to make this point explicit.
-
-    		\addnew{\lineref{line:IC2CG}}{
-    			Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) 
-    			\begin{align}
-    			    J_{t}(E \rightarrow Y )=I(Y_{t+1};E_t|Y_t)
-    			\end{align}
-    			to the system-environment dependency and the micro-macro level dependency
-                 \begin{align}
-    			    J_{t}(X \rightarrow Y )=I(Y_{t+1};X_t|Y_t)
-    			\end{align}  
-                 even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).
-    		}	
-    	\end{ans}
-
-    	\begin{question}            
-    		On line 241: '..
-not sufficiently coarse-grained variables have low values of NTIC', this is phrased as though it is necessarily true (and also that 'we saw above', though I do not see above where this is justified), but is it?
-
-    		At the very finest grain, wouldn't even all the most 'stochastic' dynamics of a system be accounted for by prior states of the system, or by the environment?
-Why wouldn't we assume that NTIC *only decreases* as the system is coarse-grained (as number of elements/states is decreased), for similar reasons as it must be zero at a 1-element 1-state system as the authors note?
-This seems an important point to be very clear on\dots
-    	\end{question}
-
-    	\begin{ans}
-        	We understand that this section in the last version is very unclear.
-Therefore, to make this point clear, we have added a new paragraph and made a significant revision of this section.
-In short, we more formally describe how NTIC may change non-monotonically from the finest microscale to the coarsest macroscale.
-Please see our revised manuscript from Line \lineref{line:non-monotonic} to Line \lineref{line:non-monotonic_end}.
-    	\end{ans}
-
-    	\begin{question}
-    		on line 263: 'NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.'
-
-    		Why does encoding suggest simulation?
-An encoding *could* be a simulation, but it could well be nothing like a simulation, if we understand simulation to mean something like an imitation or reconstruction of some structure or dynamics.
-Two totally different environmental situations could potentially be encoded in exactly the same way (eg.
-as a string of 1s and 0s).
-
-    		The 'simulation' notion is brought up again in section 5.2 (line 344), citing Bertschinger et al, though I do not find the idea in that paper..
-I think authors need to be clearer on what they mean by 'simulation' to make this point.
-    	\end{question}
-
-    	\begin{ans}
-    		The notion of simulation is the same as the 'Modeling' case on Page 4 in \cite{BERTSCHINGER.2006}: 
-    		\begin{quote}
-		    	\textit{"B2)~Modeling: The system reaches synchronization and internalizes the correlations observed in the environment by building up own structures."}
-    		\end{quote}
-
-    	    To avoid any confusion to our reader, in this revision, we added a new subsection \ref{sec:causality} to describe the scenario of modelling.
-    		Also, we replaced "simulation" and "encoding" with "modelling" in many places in this revision. We hope that this change can make our point more clear. 
-    	\end{ans}
-
-   	\begin{question}
-			line 306: 'Blindsight patients\dots make above chancel-level visual judgments without having any conscious perception about visual stimuli' I am not sure this characterization of blindsight is correct, it may be a matter of the phrasing.
-It could be - or probably is - the case that 'blindsight' patients always have some conscious experience of what drives their correct responses, but that the 'visual character' of these experiences is degraded or missing.
-			(Overgaard, Experimental Brain Research 2011)
-			for a specific example
-			(Mazzi, Bagattini, Savazzi; Frontiers in Psychology, 2016)
-    	\end{question}
-
-   		\begin{ans}
-   			Yes, we specifically wanted to address the visual character of their experience. We agree that some patients still preserve some forms of conscious experience. 
-   			We have changed our sentence and cited the relevant references as follows:
-   			\revise{\lineref{line:r2q6}}
-   			{
-   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements without having any conscious perception about visual stimuli.
-   			}
-   			{
-   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.
-(However, in some cases, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}.)
-   			}
-   		\end{ans}
-
-    	\begin{question}
-            on Line 316: On the issue of a feedforward network, the current state of a feedforward network with more than one layer is certainly driven by its own past states!
-So, mutual information of a feedforward network over a time lag should not be zero, unless I am misunderstanding something here?
-			At the same time, I can see a version of the authors' argument here - for a unit in a feedforward network with depth (distance-from-input) of N, a time lag of N time steps would always account fully for the states of the element.
-Is this the idea?
-    	\end{question}
-
- 		\begin{ans}
- 		    The reviewer is correct.
-As we have now made clear in the case of a deterministic observation process a feedforward network (or a copying process) can be informationally closed and also maintain mutual information such that it is conscious according to ICT.
-We call such process passive adaptation processes and introduce this in the new section \ref{sec:causality}.
-We mention the possibility of conscious feedforward networks now in section \ref{sec:reflexive} and add a footnote specific for n-layer feedforward networks at Line \lineref{line:feedforward}.
-Note that most observation processes in the real world are not deterministic so that most passive adaptation processes aren't conscious.
- 		\end{ans}
-
-    	\begin{question}
-    		on line 441: under the 'Prediction after system damaged', it is suggested that ICT predicts cutting a system in half would render both halves unconscious.
-But this would only be the case if neither half contains its own C-processes, yes?
-Since ICT allows that many C-processes can exist at the same time, it would have to be some special case for this prediction to hold true.
-So it seems to me the prediction is actually similar to that of IIT.
-    	\end{question}
-
-    	\begin{ans}
-        	We assume that we have one conscious (NTIC) process involving information in both brain hemispheres.
-Namely, the process is informationally closed only when we consider the information in both hemispheres.
-We agree that if both hemispheres have their own NTIC process ICT should predict no change of conscious experience before and after cutting.
-Cutting should not make any difference because they are informationally closed with respect to each other.
-We also agree that this prediction is relatively premature.
-Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.
-We also weakened our statement by added the following sentence:
-
-        	\addnew{\lineref{line:r2-cutting}}{Nevertheless, this prediction is relatively premature.
-Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.
-}
-
-    	\end{ans}
-
-        \begin{question}                              
-            Line 540: the theory doesn't really seem to intend to solve the hard problem(s) at all, much less 'completely solve'.            
-            I was expecting the problem of dreaming to come up in the last section (maybe along with SMC for which it is a serious problem).
-When dreaming the information between environment and the system is virtually zero; is this a problem for ICT?
-Also, more specific phenomena like the eigengrau - if you take away all visual input, for long enough, I do not lose my visual experiences - rather they take on a special state.
-Does ITC need to accept the possibility that even *trivial* IC can be a conscious process?
-        \end{question}
-
-    	\begin{ans}
-    		We appreciate the reviewer to bring up the hard problem of consciousness and dreaming.
-This is a very good question and dreaming really poses a challenge for ICT.
-At the moment we can only speculate about possible solutions.
-One point We want to emphasise is that not all the processes in the neural system are NTIC processes.
-To the conscious (NTIC) process, the rest of the neural system should be considered as part of the environment.
-This notion is shortly indicated at line \lineref{line:neu-env} in the original manuscript.
-We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e.
-other parts of the neural system.
-The same idea can be also applied to phenomena like Eigengrau.
-However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our last version of the manuscript.
-However, we thank the reviewer for bringing up this important question.
-We believe that this is still worth mentioning.
-We have added a short paragraph as follows:
-
-            \addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to theories of consciousness.
-ICT currently does not have a certain answer to dreaming.
-However, we want to emphasise that not all the processes in the neural system are NTIC since some processes are not informationally closed.
-They mainly passively react to sensory inputs or other processes in the neural system.
-To the conscious (NTIC) process, the rest of the neural system and the body should be also considered as part of the environment.
-They retains some degree of activities during sleep and dreaming.
-We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
-the other parts of the neural system.
-However, at the current stage, this is mere speculation.
-Searching for the NTIC process(es) during dreaming is a important step to extend the scope of ICT in future research.}
-
-    		Finally, we believe that this is a good
-    		empirical question that can and should be tested in future studies. 
-    	\end{ans}
-
-	\bibliography{ref}
 \end{document}

### 2020-05-15 ICT_Frontiers_rev202001_reply_rev2.tex

--- 2020-04-16 ICT_Frontiers_rev202001_reply.tex
@@
     \maketitle
-    \section*{Reply to Editor}
-        \begin{question}
-        In addition, I have a question. if we view molecules as coarse grains of elementary particles, would the phenomenon of molecular recognition have high NTIC and thus be conscious?
-        \end{question}
-
-        \begin{ans}
-            Hi Prof. Hoffman,
-            Thank you for your attention to our manuscript and your interesting question. \\
-            If we understand correctly, molecular recognition refers to specific types of interactions among molecules that form molecular complexes.
-There is no question that molecular complexes are coarse-grainings of molecules via molecular recognition.
-Based on our hypothesis, if the dynamics of a molecular complex is an NTIC process, the information closure theory of consciousness (ICT) would claim that the molecular complex has a certain degree of consciousness.
-        \end{ans}
-
-    \section{Reply to Reviewer 1}
-        \begin{question}
-            Regarding the NTCI measure: \\\\
-            a) Bertschinger et al.
-2006 define informationally closed as $J_t(E\rightarrow Y) = 0$, but this is not a requirement for NTIC.
-Meaning, a positive NTIC measure does not entail that $J_t = 0$.
-$J_t = 0$ is only true if the NTIC is equal to $I(Y_{t+1}; E_t)$.
-In what sense does it correspond to non-trivial information closure then?
-(see also my concern \#2, maybe that is related) As defined in eq.
-6 a video camera might have very high NTIC if it records a natural scene, even though it is in no way informationally closed from the environment.\\\\
-            b) Is $NTIC_t$ state dependent or not?
-As capital letters are used I assume it is based on (conditional) mutual information measures across one time step but averaged over the possible states of the system at time t and t+1, so state distributions.
-But which distributions are used to compute $NTIC_t$?
-The stationary joint distribution of states at t and t+1?
-It cannot be just some observed measure, because then the level of consciousness would depend on how long the observation is.
-Moreover, if $NTIC_t$ is not state dependent, then the Reflex example on p.
-10 is not intuitive.
-Because the system (brain) is the same and awake whether it behaves reflexively or not, so while the content may depend on the type of action, the $NTIC_t$ (level) would stay the same.
-        \end{question}
-
-    	\begin{ans}
-    		\newline
-    		a) It is true it is true that the information flow term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$.
-However, in Definition 2, a C-process is informationally closed to the microscopic universe process $X$.
-This implies C-process is also informationally closed to any other coarse-grainings of X including E (see also our reply to Q2).
-Currently, we only consider closed NTIC processes are C-processes.
-    		Regarding the video camera example, please see more discussion in our reply to your Q6. \\
-
-    		% Backup 2020/04/07 14:23
-    		% ====================================
-            % 		a) Considering Eq.\ref{eq:NTIC2}, it is true that the transfer entropy term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$.
-It is possible to have a high degree of NTIC when $J_t(E\rightarrow Y) > 0$, i.e.
-the process is not completely closed.
-We consider NTIC here as just the quantity defined in Eq.\ref{eq:NTIC2}.
-\\
-
-            %         Therefore, a conscious process does not have to be completely closed. 
-            %         However, processes that manage to reduce the transfer entropy from the environment without reducing their mutual information with the environment achieve higher levels of consciousness.
-            %         Regarding the video camera example, please see more discussion in our reply to your Q6. \\
-            % ====================================
-
-    		\noindent
-    		b) It is true that NTIC is not state-dependent.
-We agree that state-dependent measurements are essential to describe the dynamics of conscious experience.
-We are  working on state-dependent formulations for the next version of the ICT.
-In contrast to the current version, this work involves point-wise informational measures and requires more space and discussion.
-Therefore, we prefer to address the state-dependent version of ICT in future studies and keep the first version of our theory simple.\\
-    		We appreciated that the reviewer pointed this out. We have added a short paragraph about this issue.
-
-	    	\addnew{\lineref{line:r1-state-dep}}{
-	    		In this article, we do not use a state-dependent formulation of NTIC.
-However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience.
-Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed for the next version of ICT.}
-    	\end{ans}
-
-        \begin{question}
-            Hypothesis and Implication 3: Why is it crucial that there is an underlying $X$ with respect to which $Y$ is a C-process?     
-        \end{question}
-
-        \begin{ans}        	
-            The C-processes are constructed to answer questions about the scale problem of consciousness. Their definition therefore states their relation to the microscopic scale $X$. 
-            At the same time it would be possible to remove $X$ from the definition and instead require that $Y$ is informationally closed with respect to all other processes.
-In some cases such a definition would be more general than the present one for example when there is no final microscale and instead there is an infinite number of more and more microscopic scales.
-However, we find the use of an explicit microscale $X$ easier to understand and sufficient to communicate the idea.
-Note that closure with respect to $X$ (if it exists) implies closure with respect to every coarse-graining of $X$.
-            To see this note that the information transfer from any coarse-graining (including $E$ and $S$) of $X$ to $Y$ must be lower than that from $X$ to $Y$, i.e.
-$I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$.
-So that $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to $S, E$, and all other coarse-grainings of $X$.
-        \end{ans}
-
-        \begin{question}
-            Does $Y$ being informationally closed with respect to $X$ imply that $Y$ is also informationally closed with respect to E, i.e.
-$J_t(E\rightarrow Y)= 0$?
-I don't think that could be true for the brain, or part of it really.
-My brain's next state, at whatever level, certainly depends to some degree on unpredictable sensory inputs from the environment.
-In the end, is $I(Y_{t+1}; E_t|Y_t) = 0$ required for consciousness or not?
-(see point 1a).
-In other points in the manuscript this does not seem required, e.g.
-p.
-10 "If a process is not informationally closed, the degree of NTIC is low resulting in low or no consciousness".
-        \end{question}
-
-        \begin{ans}
-            Yes.
-As mentioned in our answer to Q2 $Y$ being informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to E, i.e.
-$J_t(E\rightarrow Y) = 0$.
-            As explained in Question 1a, we currently only consider informationally closed processes as C-processes.
-The reviewer is also correct that our internal states depends to some degree on unpredictable sensory inputs from the environment.
-This results in some interesting predictions.
-For example, the unpredicted sensory inputs may temporally break informational closure and ICT predicts that conscious agents may then lose consciousness for a short time.
-Unfortunately, referring to your Q1b, the current version of ICT does not include state-dependent IC and NTIC.
-Therefore, the current formulation of ICT cannot well describe the dynamics of conscious experience under unpredictable states.
-We expect that our next version of ICT can better answer your question.
-
-            % it is not required for NTIC processes to be completely closed.
-The information transfer from $X$ to $Y$ $I(Y_{t+1}; X_t|Y_t)$ (if non-zero) serves as the upper bound of the information transfer from any other process to Y.
-So unpredictable sensory inputs will contribute to a positive information transfer.
-            % As mentioned before higher NTIC values are achieved when this information transfer can be reduced without reducing the mutual information between the sensory inputs and the next system state.
-        \end{ans}
-
-        \begin{question}
-            Exclusion or no exclusion? The authors state multiple times that "every process with a positive non-trivial information closure (NTCI) has consciousness." (p.3, and also p.12).
-            a) Yet, Figure 4 is ambiguous in the sense that the maximum somehow seems important, while actually all levels should give rise to separate experiences.
-I don't see how ICT without something like exclusion (IIT style) would indicate that the maximum should correspond to human consciousness.
-It could just be any one out of many consciousnesses.
-            b) p.
-14: comparison to IIT: what does ICT say about different sets of variables at the same level.
-There might well be multiple ways to partition $X$ into S and E, with many overlapping S's.
-Would those all be conscious?
-They would not be informationally closed from each other but they could all fulfill the requirements in the Hypothesis.
-It seems like finding the maximum within a level over the possible sets of elements/variables is a necessary step to identify boundaries (I think also Krakauer does that across sets of variables, but not 100\% sure)
-        \end{question}
-
-    	\begin{ans}
-            We can see how Figure 4 was ambiguous with respect to this question. We do not impose the exclusion criterion in ICT and have changed Figure 4 to remove the impression that it does.
-
-            Instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of individuality and defining the boundary of a system.
-\citep{BERTSCHINGER.2006}.
-This allows ICT to solve the individuality problem of consciousness in some cases (but not all, please see the paragraph in Limitation from Line~\lineref{line:individuality}) without imposing an exclusion criterion.
-Therefore, it is true that Krakauer's boundary detection procedure can potentially helpful and be adapted for ICT in the future.
-
-            This is also why ICT allows the existence of multiple consciousnesses across the scales of coarse-graining (which IIT does not).
-Because conscious processes are informationally closed from each other across the scale of coarse-graining, they are not able to know the existence of other consciousnesses within the same system (information flow from other processes is zero).
-This is in line with using informational closure in level identification \citep{PFANTE.2014}.
-
-            We understand that not solving individuality completely is one major weakness of the current version of ICT (and all IC and NTIC based theories).
-More work on this issue is needed in our following research.
-
-    	\end{ans}
-
-        \begin{question}
-            Feedback and memory: p.
-11.
-If $NTIC > 0$ is sufficient and true information closure is not required, then feedfoward networks can be conscious according to ICT.
-Also, in that case, memory is not necessary, as the video camera would have $NTIC > 0$ as long as it records from a stable environment.
-In that case $I(Y_{t+1}, Y_t) > 0$ and $I(Y_{t+1}, Y_t|E_t)$ is small.
-This issue here is that having information about the next state does not imply that there is any causation, so if $Y_t$ is highly correlated with $E_t$ and $E_t$ causes $Y_{t+1}$ then NTIC is high.
-(Thus the IIT emphasis on causation).\\
-            If somehow the fact that $Y$ must be informationally closed wrt $X$ does the heavy-lifting here that should be made more explicit (see above).
-        \end{question}
-
-        \begin{ans}
-        	The reviewer is right.
-We have reconsidered case of the feed-forward networks and the video camera example (which can be considered as a single layer feed-forward network).
-According to ICT, feed-forward networks can be conscious under for deterministic sensor processes.
-We thank the reviewer to correct this point.
-In this case also a video camera can achieve positive levels of NTIC and, therefore, be conscious.
-We have worked extensively on Section \ref{sec:causality} and Section 5 to make this clear (for Section 5, please see from Line:~\lineref{line:notIC}).
-        % 	There we have weakened multiple claims in the original version of the manuscript.
-        % 	Concerning the camera example we also show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image (sensor values) and the next there are systems that achieve higher NTIC.
-        % 	For the case of the feedforward network we speculate that a similar situation remains true and that there are always systems that achieve higher levels of consciousness than those consisting only of feedforward networks.
-        	In summary, we mainly revised our manuscript as follows:
-        	\begin{itemize}
-        	    \item Add Section \ref{sec:causality} to illustrate two NTIC scenarios about causality. 
-        	    \item Add sensory channels in Fig.~2
-        	    \item Extensively modify the paragraphs about feed-forward networks and memory in Section 5
-        	    \item Add a session in the Appendix to prove that NTIC achieved by modelling the environment can potentially achieve higher NTIC then the one by copying sensory values (e.g., the video camera).
-        	\end{itemize}
-
-    %     	Please note that
-
-		  %  @ The reviewer is correct about the example of the video camera under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.
-
-		  %  @ In such case, simply copying the environmental states to another process (assuming that the sensor of the video camera can capture the whole state of the environment) can lead to positive NTIC.
-
-		  %  @ This is, in fact, the "Passive adaptation" case mentioned in \cite[p.~4]{BERTSCHINGER.2006},	
-		  %  \begin{quote}
-			 %     	\textit{"B1)~Passive adaptation: The system is driven by the environment and adapts passively to all changes in the environment.
-In the case of an environment, that appears deterministic to the system, $H(\hat{e}_{n+1} |\hat{e}_n)=0$, this can be achieved by simply copying the observation of the environment into the system, $S_{n+1} = \hat{e}_n$."}
-		  %  \end{quote}
-
-	   % @ We can also consider this is a special case of modelling the environment when a system has enough sensory and memory capacities, and, therefore, can virtually model the environment by simply copying the environmental states into the system.
-
-	   % @ Because this question point to the core concept of ICT, we would like to clarify and emphasise two critical points here.
-
-	   % @ a) Informational closure and causation: The definition of information closure \citep{BERTSCHINGER.2006} does not involve causation.
-As described in \cite{BERTSCHINGER.2006}, NTIC can be achieved via "modelling" or "passive adaptation".
-In the "modelling" case, the future state of a process ($Y_{t+1}$) can be caused by $Y_t$, which contain predictive information about how the environment influences the system.
-In the "passive adaptation" case,  the future state of a process ($Y_{t+1}$) is caused by copying environmental information which involves environmental dynamics.
-
-	   % The latter case may be conceptually counterintuitive because the internal state of the system (e,g, the video camera) is entirely driven by external input.
-However, it is crucial to know that both cases lead the information flow $J(E\rightarrow Y)$ to (virtually) zero.
-This means that if $Y_t$ contains information about how the environment $E_t$ causes $Y_{t+1}$,
-
-	   % However, this is the most critical consequence of solving the scale problem of consciousness in ICT.
-In physical reality, there only exists microscopic processes at the finest microscopic level.
-Any causal dependency at coarse-graining levels should be virtual.
-For example, when $Y$ is informationally closed to X, even though $Y_t$
-
-	   % @ b) As described in our manuscript, to form a higher level of NTIC, the informational richness of the environment, i.e.
-$H(E)$ also has to be higher since $H(E_t)$ and $H(Y_{t+1})$ both are the upper bound of $I(Y_{t+1}; H(E_t))$.
-Practically, we believe that with limited sensory and memory capacities, it is difficult to give rise to high NTIC via copying sensory signals to a system.
-
-        \end{ans}
-
-        \begin{question}
-            Does ICT imply that one is unconscious while dreaming? In that case $I(Y_{t+1}; Y_t|E)$ should almost be identical to $I(Y_{t+1};I_t)$ and thus lead to NTIC approx. 0.        
-        \end{question}
-
-    	\begin{ans}
-	    	We want to emphasise that not all the processes in the neural system are NTIC processes, since some processes in the neural system are not informationally closed.
-	    	To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment.
-This notion is shortly indicated at line \lineref{line:neu-env} in our first version of the manuscript.
-These processes are still active during sleep and dreaming.
-We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e.
-other parts of the neural system.
-However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our manuscript.
-However, we thank the reviewer for bringing up this important question.
-This is also an empirical question that can and should be tested in future studies.
-We believe that this is still worth mentioning.
-We have added a short paragraph as follows:
-
-			\addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to theories of consciousness.
-ICT currently does not have a certain answer to dreaming.
-However, we want to emphasise that not all the processes in the neural system are NTIC since some processes are not informationally closed.
-They mainly passively react to sensory inputs or other processes in the neural system.
-To the conscious (NTIC) process, the rest of the neural system and the body should be also considered as part of the environment.
-They retains some degree of activities during sleep and dreaming.
-We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
-the other parts of the neural system.
-However, at the current stage, this is mere speculation.
-Searching for the NTIC process(es) during dreaming is a important step to extend the scope of ICT in future research.}
-    	\end{ans}
-
-        \begin{question}
-            Minor:
-            \begin{enumerate}
-                \item "contributions to the field" This section is just a copy paste from the abstract and thus not necessarily helpful.
-Not sure though what the purpose of this section is meant to be by Frontiers.
-
-                \item Introduction: "We currently lack a theory...
-" IIT and the geometric theory of consciousness (Fekete et al.) have proposed solutions.
-So there are theories.
-The following paper should be of interest and should probably be cited:
-                Fekete T, van Leeuwen C, Edelman S (2016) System, subsystem, hive: Boundary problems in computational theories of consciousness. Front Psychol 7:1041.
-
-                \item $y_t$ corresponds to the content.
-I would argue that an activation state, without taking the system or relation between elements etc into account is meaningless and cannot capture/explain the structure of an experience.
-Though this issue can be dealt with at a later time.
-            \end{enumerate}
-        \end{question}
-
-    	\begin{ans}
-    		\begin{enumerate}
-    			\item It's true that we were also confused about it during submission. 
-    			We have modified this as follows: \\
-    			\textit{"We propose a new theory of consciousness and discuss some preliminary implications."}
-
-    			\item We thank the reviewer for the reminder. We have modified our manuscript and cited the relevant references. 
-    			\revise{\lineref{line:lack-theory}}
-    			{
-    			We currently lack a theory to identify the scale which conscious processes correspond to.
-    			}
-    			{
-    			We currently have only few theories (e.g., Integrated Information Theory \citep{hoel2016can} and Geometric Theory of consciousness \citep{fekete2011towards,fekete2012lack}) to identify the scale which conscious processes correspond to (also see the discussion in \cite{fekete2016system}).
-    			}
-
-    			\item We agree with the reviewer's comment. 
-                In fact, we do not differentiate states of processes between activation and relation.
-Take neural network as an example; the relations between elements are determined by the topology of a network (structure) and its hyperparameters (e.g.
-activation functions).
-We agree that activation and relation of a neural network should be both considered.
-After all, they are all merely the parameters for the process of the neural network.
-The only difference between the two groups of the parameters is the temporal scales of changes.
-States of activation may have more rapid dynamics than states of relation.
-In ICT, the two sets of parameters do not have any qualitative differences.
-
-    		\end{enumerate}
-
-    	\end{ans}
 
@@
     	\begin{ans}
-    		We thank the reviewer for the critical comments. We have replied these comments in details in the following Q\&A. 
+    		We thank the reviewer for these critical comments. We have replied in detail in the following Q\&A. 
     	\end{ans}
@@
     	\begin{ans}
-    		We have invited a native English speaker for proofreading. Please inform us if it is still not clear or unreadable. 
+    		 We have recruited a professional proofreading service to edit the manuscript. Please inform us if it is still not clear or unreadable. 
     	\end{ans}
@@
     		We agree that this point is not clear.
-Even though the Bayesian graphs for the system-environment dependency are different from the one for the micro-macro level dependency, we apply the same definitions of information flow ($J_{t}(X \rightarrow $Y$ )$) and informational closure ($J_{t}(X \rightarrow $Y$ )=0$) to both graphs.
+Even though the Bayesian graphs for the system-environment dependency differ from that for the micro-macro level dependency, we applied the same definitions of information flow ($J_{t}(X \rightarrow $Y$ )$) and informational closure ($J_{t}(X \rightarrow $Y$ )=0$) to both graphs.
 
@@
     			\end{align}
-    			to the system-environment dependency and the micro-macro level dependency
+    			to the system-environment dependency
+    			and the micro-macro scale dependency
     			\begin{align}
@@
     			\end{align}
-                 even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).
+    			even though the Bayesian graphs differ in the two scenarios. Both these settings have been previously used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}.
     		}	
@@
     	\begin{ans}
-        	We understand that this section in the last version is very unclear.
-Therefore, to make this point clear, we have added a new paragraph and made a significant revision of this section.
+    		We appreciate that this section in the previous version was unclear.
+We have therefore added a new paragraph and significantly revised this section.
 In short, we more formally describe how NTIC may change non-monotonically from the finest microscale to the coarsest macroscale.
-Please see our revised manuscript from Line \lineref{line:non-monotonic} to Line \lineref{line:non-monotonic_end}.
+Please see our revised manuscript from Line \lineref{line:non-monotonic} to  \lineref{line:non-monotonic_end}.
     	\end{ans}
@@
     	\begin{question}
-    		on line 263: 'NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.'
+    		on line 263: 'NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.
 
@@
 
-    	    To avoid any confusion to our reader, in this revision, we added a new subsection \ref{sec:causality} to describe the scenario of modelling.
-    		Also, we replaced "simulation" and "encoding" with "modelling" in many places in this revision. We hope that this change can make our point more clear. 
+    	    To avoid reader confusion, we have added a new section, Sec.~\ref{sec:causality}, in this revision to describe the modelling scenario.
+Further, we have replaced "simulation" and "encoding" with "modelling" in many parts of the text.
+We hope that this change clarifies our point.
     	\end{ans}
@@
    			{
-   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.
-(However, in some cases, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}.)
+   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience.(However, in some cases, they may still preserve some forms of conscious experience; See \cite{overgaard2011visual, mazzi2016blind})
    			}
@@
  		\begin{ans}
- 		    The reviewer is correct.
-As we have now made clear in the case of a deterministic observation process a feedforward network (or a copying process) can be informationally closed and also maintain mutual information such that it is conscious according to ICT.
-We call such process passive adaptation processes and introduce this in the new section \ref{sec:causality}.
-We mention the possibility of conscious feedforward networks now in section \ref{sec:reflexive} and add a footnote specific for n-layer feedforward networks at Line \lineref{line:feedforward}.
-Note that most observation processes in the real world are not deterministic so that most passive adaptation processes aren't conscious.
+ 			A: The reviewer is correct.
+As we have now clarified that in the case of a deterministic observation process a feedforward network (or a copying process) can be informationally closed and yet also maintain mutual information such that it is conscious according to ICT.
+We call such processes passive adaptation processes and have introduced this in the new Sec~\ref{sec:causality}.
+We mention the possibility of conscious feedforward networks now in Sec~\ref{sec:reflexive} and have added a footnote specific for n-layer feedforward networks at Line~\lineref{line:feedforward}.
+Note that most observation processes in the real world are not deterministic so that most passive adaptation processes are not conscious.
  		\end{ans}
@@
     	\begin{ans}
-        	We assume that we have one conscious (NTIC) process involving information in both brain hemispheres.
-Namely, the process is informationally closed only when we consider the information in both hemispheres.
-We agree that if both hemispheres have their own NTIC process ICT should predict no change of conscious experience before and after cutting.
+        	We assume that we have one conscious (NTIC) process which involves information in both brain hemispheres.
+This process is informationally closed only when we consider the information in both hemispheres.
+We agree that if both hemispheres each have their own NTIC process ICT should predict no change in conscious experience before and after cutting.
 Cutting should not make any difference because they are informationally closed with respect to each other.
 We also agree that this prediction is relatively premature.
-Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.
-We also weakened our statement by added the following sentence:
+Systematic comparisons between model predictions can be done by rigorous modelling studies in the future.
+We have weakened our statement by added the following sentence:
 
         	\addnew{\lineref{line:r2-cutting}}{Nevertheless, this prediction is relatively premature.
-Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.
-}
+In the future, rigorous modelling studies will allow systematic comparisons between model predictions.}
 
@@
     	\begin{ans}
-    		We appreciate the reviewer to bring up the hard problem of consciousness and dreaming.
-This is a very good question and dreaming really poses a challenge for ICT.
+    		We appreciate the reviewer for bringing up the hard problem of consciousness and dreaming.
+This is a very good question, and dreaming clearly poses a challenge for ICT.
 At the moment we can only speculate about possible solutions.
-One point We want to emphasise is that not all the processes in the neural system are NTIC processes.
+One point we wish to emphasise is that not all the processes in the neural system are NTIC processes.
 To the conscious (NTIC) process, the rest of the neural system should be considered as part of the environment.
-This notion is shortly indicated at line \lineref{line:neu-env} in the original manuscript.
-We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e.
+This notion is briefly indicated at Line \lineref{line:neu-env} in the original manuscript.
+We speculate that, during dreaming, the neural system stably forms the NTIC process with respect to its environment, i.e.
 other parts of the neural system.
 The same idea can be also applied to phenomena like Eigengrau.
-However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our last version of the manuscript.
-However, we thank the reviewer for bringing up this important question.
-We believe that this is still worth mentioning.
-We have added a short paragraph as follows:
+At present, however, this is mere speculation so we refrained from making the statement in our last version of the manuscript.
+However, we again thank the reviewer for raising this important question and believe that it is still worth mentioning.
+Accordingly, we have added a short paragraph as follows:
 
             \addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to theories of consciousness.
-ICT currently does not have a certain answer to dreaming.
-However, we want to emphasise that not all the processes in the neural system are NTIC since some processes are not informationally closed.
+ICT currently does not have a specific answer to dreaming.
+However, we wish to emphasize that not all processes in the neural system are NTIC since some processes are not informationally closed.
 They mainly passively react to sensory inputs or other processes in the neural system.
-To the conscious (NTIC) process, the rest of the neural system and the body should be also considered as part of the environment.
-They retains some degree of activities during sleep and dreaming.
+To the conscious (NTIC) process, the rest of the neural system and the body should also be considered as part of the environment.
+They retain some degree of activity during sleep and dreaming.
 We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
 the other parts of the neural system.
-However, at the current stage, this is mere speculation.
-Searching for the NTIC process(es) during dreaming is a important step to extend the scope of ICT in future research.}
+At present, however, this remains mere speculation.
+Identification of the NTIC process(es) during dreaming is an important milestone in extending the scope of ICT.}
 

### 2020-05-29 Copy of ICT_Frontiers_rev202005.tex
Revision 2

--- 2020-05-15 ICT_Frontiers_rev202001.tex
@@
 In other words, a number of different micro-states correspond to the same value of the macro-variable \citep{price2007causation}.
-Coarse-grainings can therefore form more stable and deterministic state transitions and more often form NTIC processes.
-For neural systems this means that a microscopically noisy neural system may still give rise to an NTIC process on a more macroscopic scale.
+Coarse-grainings can therefore form more stable and deterministic state transitions and more often form processes with positive NTIC.
+For neural systems this means that a microscopically noisy neural system may still give rise to an process with positive NTIC on a more macroscopic scale.
 
@@
         These two examples show that the known coding schemes can be viewed as coarse-graining, and provide stochastic neural systems with the ability to form more stable and deterministic macroscopic processes for encoding and processing information reliably.
-We argue that coarse-graining allows neural systems to form NTIC processes at macroscopic scales.
+We argue that coarse-graining allows neural systems to form processes with positive NTIC at macroscopic scales.
 Based on the merit of coarse-graining in neural systems, we propose a new theory of consciousness in the next section.
@@
         % ---------------------------------------------------------------------------- %
-	    \subsection{Level of Consciousness is Equal to the Degree of NTIC of a Process}\label{sec:cl}
+	    \subsection{Level of Consciousness is Equal to the Degree of NTIC of a C-process}\label{sec:cl}
             According to Eq.~\ref{eq:nticObjective}, \ac{OurTheory} implies that conscious levels are determined by two quantities.
@@
     	    Second, one can minimise the conditional mutual information $I(Y_{t+1};Y_{t}|E_{t})$ to increase the level of NTIC.
-If the mutual information term $I(Y_{t+1};Y_t)$ is supposed to stay large, this quantity suggests that conscious level increases with the amount of information about the environment state $E_t$ that the NTIC process encodes in its own state $Y_t$ and $Y_{t+1}$.
+If the mutual information term $I(Y_{t+1};Y_t)$ is supposed to stay large, this quantity suggests that conscious level increases with the amount of information about the environment state $E_t$ that the process encodes in its own state $Y_t$ and $Y_{t+1}$.
 In other words, $Y_t$ should not contain more information about $Y_{t+1}$ than $E_t$.
@@
 
-		\subsection{Conscious Contents Corresponding to States of an NTIC Process}\label{sec:cc}
+		\subsection{Conscious Contents Corresponding to States of a C-Process}\label{sec:cc}
     	    % richness 
-    		\ac{OurTheory} proposes that conscious contents correspond to the states of NTIC processes (Eq.~\ref{eq:cContent}).
-This implies that the size of the state space of an NTIC process is associated with the richness of the conscious contents that the process can potentially have.
-Accordingly, a complex NTIC process with a high dimensional state space can have richer conscious experience than a simple NTIC process.
+    		\ac{OurTheory} proposes that conscious contents correspond to the states of C-processes (Eq.~\ref{eq:cContent}).
+This implies that the size of the state space of an C-process is associated with the richness of the conscious contents that the process can potentially have.
+Accordingly, a complex C-process with a high dimensional state space can have richer conscious experience than a simple C-process.
 This outcome is consistent with the intuition that the richness of conscious contents is associated with the complexity of a system.
@@
     		Informational closure can happen between scales of coarse-graining within a single system.
-Thus, a macroscopic NTIC process can be ignorant of its microscopic states.
-\ac{OurTheory} argues that human conscious contents do not reflect cellular scale activity because the conscious process which corresponds to a macroscopic NTIC process is informationally closed to the cellular scale in the human neural system.
-Further more, since NTIC processes are informationally closed, each of them can be considered as a reality.
+Thus, a macroscopic C-process can be ignorant of its microscopic states.
+\ac{OurTheory} argues that human conscious contents do not reflect cellular scale activity because the conscious process which corresponds to a macroscopic C-process is informationally closed to the cellular scale in the human neural system.
+Further more, since C-processes are informationally closed, each of them can be considered as a reality.
 When the information flow from its microscopic processes (and from the environment) to it is zero (Eq.~\ref{eq:informationflow2}), the future states of the process can be entirely self-determined by its past states.
 
-    		\linelabel{line:encode}Importantly, in most realistic cases, NTIC processes internalise the environmental dynamics in its states (see Sec.
+    		\linelabel{line:encode}Importantly, in most realistic cases, processes with positive NTIC internalise the environmental dynamics in its states (see Sec.
 \ref{sec:causality} and also \cite{BERTSCHINGER.2006}).
-This suggests that an NTIC process can be considered as a process that models the environmental dynamics.
+This suggests that a process with positive NTIC can be considered as a process that models the environmental dynamics.
 This implication fits well with several theories of consciousness (for example, world simulation metaphor ~\citep{revonsuo2006inner}).
@@
 
-            Finally, a coarse-graining can be a many-to-one map from microscopic to macroscopic states and \ac{OurTheory} proposes that conscious contents $C^{Content}$ is the state of the NTIC process $Y$.
+            Finally, a coarse-graining can be a many-to-one map from microscopic to macroscopic states and \ac{OurTheory} proposes that conscious contents $C^{Content}$ is the state of the C-process $Y$.
 \ac{OurTheory} therefore implies the multiple realisation thesis of consciousness \citep{putnam1967psychological,bechtel1999multiple}, which suggests that different physical implementations could map to the same conscious experience.
@@
     	    While it is useful to distinguish the levels and contents of consciousness at the notion level, whether they can be clearly dissociated has been a matter of debate \citep{bayne2016there, Fazekas2016}.
-In \ac{OurTheory}, conscious levels and conscious contents are simply two different properties of NTIC processes, and the two aspects of consciousness are therefore naturally reconciled.
-In an NTIC process with a large state space, conscious contents should also consist of rich and high dimensional information.
+In \ac{OurTheory}, conscious levels and conscious contents are simply two different properties of C-processes, and the two aspects of consciousness are therefore naturally reconciled.
+In a C-process with a large state space, conscious contents should also consist of rich and high dimensional information.
 This framework therefore integrates the levels and the contents of consciousness in a coherent fashion by providing explicit formal definitions of the two notions.
 
-    	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the state space of an NTIC process $Y$.
+    	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the state space of a C-process $Y$.
 A larger state space of $Y$ contributes conscious levels through the mutual information $I(Y_{t+1};Y_{t})$ and also contributes richer conscious contents by providing a greater number of possible states of conscious processes.
@@
                 \citep{Raymont2006-RAYUOC}.
-Consider an NTIC process $Y$ and an isolated informationally closed process $\hat{Y}$ with only trivial information.
+Consider a process $Y$ with positive NTIC and an isolated informationally closed process $\hat{Y}$ with only trivial information.
 Adding $\hat{Y}$ to $Y$ can still maintain informational closure but does not increase non-trivial information, i.e.,  consciousness is unaffected.
@@
 		\subsection{Conscious Processing}\label{sec:conscious processing}
-		    In accordance with \ac{OurTheory}, we claim that any process, system, or cognitive function which involves any NTIC process should be accompanied by conscious experience.
+		    In accordance with \ac{OurTheory}, we claim that any process, system, or cognitive function which involves any C-process should be accompanied by conscious experience.
 
@@
 \ac{OurTheory} provides an integrated account of why these processes involve conscious experience.
-As mentioned above, an NTIC process can be seen as an internal modelling engine for agent-environmental interactions \citep{BERTSCHINGER.2006}.
-Therefore, information encoded in NTIC processes is essential for several cognitive processes.
+As mentioned above, a process with positive NTIC can be seen as an internal modelling engine for agent-environmental interactions \citep{BERTSCHINGER.2006}.
+Therefore, information encoded in C-processes is essential for several cognitive processes.
 
 		    Among the most valuable types of information are predictions about environmental states.
-Cognitive functions requiring agent-scale environmental predictions are likely to recruit NTIC processes, and to therefore be accompanied by conscious experience; examples include planning and achieving long term goals.
-
-            Second, as a modelling engine, an NTIC process with a given initial state can self-evolve and simulate the environmental transitions.
-Cognitive functions involving simulations are expected to involve NTIC processes.
+Cognitive functions requiring agent-scale environmental predictions are likely to recruit C-processes , and to therefore be accompanied by conscious experience; examples include planning and achieving long term goals.
+
+            Second, as a modelling engine, a C-process with a given initial state can self-evolve and simulate the environmental transitions.
+Cognitive functions involving simulations are expected to involve C-processes.
 Consequently, mental simulation, imagination, computing alternative realities, and generating counterfactuals often come with conscious experience.
 
-    	    Third, as an informationally closed system, an NTIC process can still provide environmental information without new sensory inputs.
+    	    Third, as an informationally closed system, a C-process can still provide environmental information without new sensory inputs.
 This is crucial for many types of off-line processing.
@@
 
-    	    Finally, for agents adapting to complex environments (e.g., human beings), any state of the NTIC process can be seen as an integration of high dimensional information.
-To accurately encode information about complex environmental states and transitions, the NTIC process requires knowledge about the complex causal dependencies involved in the environment.
-Cognitive functions requiring larger scale integration are therefore likely to involve NTIC processes and accompanied by conscious experience.
+    	    Finally, for agents adapting to complex environments (e.g., human beings), any state of the C-process can be seen as an integration of high dimensional information.
+To accurately encode information about complex environmental states and transitions, a process with positive NTIC requires knowledge about the complex causal dependencies involved in the environment.
+Cognitive functions requiring larger scale integration are therefore likely to involve C-processes and accompanied by conscious experience.
 % Furthermore, the high dimensional integrated information is also critical for an agent to learn new behaviours to achieve flexibility and the strategic behavioural controls and decision-making.
@@
 As such, \ac{OurTheory} does not assume any functionalist perspectives of consciousness, which associate specific functions to consciousness.
-That is to say, since \ac{OurTheory} associates information  with consciousness, functional features accompanied by consciousness are collateral consequences of neural systems which utilise NTIC processes for adaptive functions.
-
-    	    In sum, we argue that cognitive functions involving the NTIC process are inevitably accompanied by consciousness.
-Having an NTIC process is potentially an effective approach to increasing fitness in the evolutionary process.
+That is to say, since \ac{OurTheory} associates information  with consciousness, functional features accompanied by consciousness are collateral consequences of neural systems which utilise processes with positive NTIC for adaptive functions.
+
+    	    In sum, we argue that cognitive functions involving the C-process are inevitably accompanied by consciousness.
+Having an C-process is potentially an effective approach to increasing fitness in the evolutionary process.
 It is likely that biological creatures evolve NTIC processes at some point during their evolution.
@@
 The problem of individuality is a significant theoretical weakness of the current version of ICT.
-The notion of integration is a possible remedy for this issue, and we will address it explicitly in our future work using the concept of synergy.
+The notion of integration\footnote{Integration here refers to any high-order dependencies.} is a possible remedy for this issue, and we will address it explicitly in our future work using the concept of synergy.
 

### 2020-05-29 ICT_Frontiers_rev202005.tex
Revision 2

--- 2020-05-15 ICT_Frontiers_rev202001.tex
@@
 
+			\linelabel{line:nticdef}For simplicity, in what follows, we refer to \textit{NTIC processes} as those \textit{processes with positive NTIC}.
+
 			\subsection{Informational Closure Does not Imply Causality}\label{sec:causality}
                 A surprising result from the definition of information flow $J_t(E\rightarrow Y)$ (Eq.~\ref{eq:InformationFlow}) is that information flow does not indicate causal dependency from $E_t$ to $Y_{t+1}$ or from $Y_t$ to $Y_{t+1}$.
-Here we consider two scenarios, called \textit{modelling} and \textit{passive adaptation}, which previously noted by \citet{BERTSCHINGER.2006}.
+Here we consider two scenarios, \textit{modelling} and \textit{passive adaptation}, which were previously noted by \citet{BERTSCHINGER.2006}.
 In both scenarios, a process can form positive NTIC ($NTIC(E\rightarrow Y)> 0$) and informational closure ($J(E\rightarrow Y)=0$), albeit via different causal dependencies.
 
-                In the scenario of \textit{modelling}, to achieve positive NTIC and informational closure, a system can internalise and synchronise with the dynamics of the environment, e.g., model the environment.
+                In the \textit{modelling} scenario, to achieve positive NTIC and informational closure, a system can internalise and synchronise with the dynamics of the environment, e.g., model the environment.
 In this case, the future internal state $Y_{t+1}$ of the system is driven by the current internal state $Y_t$ and the system still retains mutual information with the environment.
-Having high degrees of NTIC then entails having high predictive power about the environment.
+Having high degrees of NTIC then entails high predictive power about the environment.
 This gives biological agents functional and evolutionary advantages.
 
-                In the \textit{passive adaptation} scenario, counterintuitively, the future system states ($Y_{t+1}$) are  entirely driven by the current environment states ($E_t$) but can also have positive NTIC and informational closure.
-This happens under the condition that the sensory process $\hat{e}_t$ is deterministic and the system simply copies the sensory values.
-The system is then a copy of another informationally closed process ($\hat{e}_t$) and is therefore closed itself.
-At the same time it has mutual information with the process that it is copying.
-
-                In most of the realistic cases, however, the environment is partially observable to the system, and thus the sensory process is usually not deterministic.
+                In the \textit{passive adaptation} scenario, the future system states ($Y_{t+1}$) are entirely driven by the current environment states ($E_t$).
+The system, perhaps counterintuitively, can nonetheless achieve positive NTIC and informational closure.
+This happens under the condition that the sensory process $\hat{e}_t$ is deterministic and the system merely copies the sensory values.
+The system is then a copy of another informationally closed process ($\hat{e}_t$) and is therefore closed.
+At the same time, the system has mutual information with the process that it is copying.
+
+                In most of the realistic cases, however, the environment is partially observable from the system's perspective, and thus the sensory process is usually not deterministic.
 Accordingly, it is difficult for the system to be informationally closed and have higher NTIC.
-                More importantly, we argue in the Appendix that whenever the environment has itself more predictable dynamics than the observations, there is the potential exists for a process to achieve higher NTIC by modelling the environment rather than by copying the observations.
+                More importantly, we argue in the Appendix that whenever the environment has itself more predictable dynamics than the observations, it is possible exists for a process to achieve higher NTIC by modelling the environment than by copying the observations.
 
@@
     		\linelabel{line:non-monotonic}It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining.
-At the finest scale we consider the whole universe $X$ as the process $Y$.
+\linelabel{line:sizeAndScale}Since we can quantify the scale of a coarse-grained variable by the size of its state space, therefore, at the finest scale we consider the whole universe $X$ as the process $Y$.
 Then, since $Y$ is a coarse-graining of $S$ we have $Y=S=X$.
@@
 Therefore, processes at intermediate scales of coarse-graining can form higher degrees of NTIC than those at the most microscopic or macroscopic scales (Fig.~\ref{fig:LevelOfConsciousness}).
-\ac{OurTheory} suggests that human consciousness occurs at a scale of coarse-graining where high NTIC is formed within the neural system.
+\ac{OurTheory} suggests that human consciousness occurs at a scale of coarse-graining where high NTIC is formed within the neural system\footnote{In our current setup, the size of the state space $\mathcal{S}$ and $\mathcal{E}$ correspondingly determines the scale of coarse-graining of $S$ and $E$.Further research is needed to reveal the relationship among NTIC, scales of coarse-graining, and different constructions of $S$ and $E$.}.
 \linelabel{line:non-monotonic_end}
@@
 
-		\subsection{Conscious Contents Corresponding to States of an NTIC Process}\label{sec:cc}
+		\subsection{Conscious Contents Corresponding to States of a C-Process}\label{sec:cc}
     	    % richness 
-    		\ac{OurTheory} proposes that conscious contents correspond to the states of NTIC processes (Eq.~\ref{eq:cContent}).
-This implies that the size of the state space of an NTIC process is associated with the richness of the conscious contents that the process can potentially have.
-Accordingly, a complex NTIC process with a high dimensional state space can have richer conscious experience than a simple NTIC process.
+    		\ac{OurTheory} proposes that conscious contents correspond to the states of C-processes (Eq.~\ref{eq:cContent}).
+This implies that the size of the state space of a C-process is associated with the richness of the conscious contents that the process can potentially have.
+Accordingly, a complex C-process with a high dimensional state space can have richer conscious experience than a simple C-process.
 This outcome is consistent with the intuition that the richness of conscious contents is associated with the complexity of a system.
@@
 \ac{OurTheory} argues that human conscious contents do not reflect cellular scale activity because the conscious process which corresponds to a macroscopic NTIC process is informationally closed to the cellular scale in the human neural system.
-Further more, since NTIC processes are informationally closed, each of them can be considered as a reality.
+Further more, since C-processes are informationally closed, each of them can be considered as a reality.
 When the information flow from its microscopic processes (and from the environment) to it is zero (Eq.~\ref{eq:informationflow2}), the future states of the process can be entirely self-determined by its past states.
@@
 
-            Finally, a coarse-graining can be a many-to-one map from microscopic to macroscopic states and \ac{OurTheory} proposes that conscious contents $C^{Content}$ is the state of the NTIC process $Y$.
+            Finally, a coarse-graining can be a many-to-one map from microscopic to macroscopic states and \ac{OurTheory} proposes that conscious contents $C^{Content}$ is the state of the C-process.
 \ac{OurTheory} therefore implies the multiple realisation thesis of consciousness \citep{putnam1967psychological,bechtel1999multiple}, which suggests that different physical implementations could map to the same conscious experience.
@@
 
+		    %Cognitive functions involving simulations are expected to involve NTIC processes.
+Consequently, mental simulation, imagination, computing alternative realities, and generating counterfactuals often come with conscious experience.
+
             Second, as a modelling engine, an NTIC process with a given initial state can self-evolve and simulate the environmental transitions.
-Cognitive functions involving simulations are expected to involve NTIC processes.
-Consequently, mental simulation, imagination, computing alternative realities, and generating counterfactuals often come with conscious experience.
+\linelabel{line:MentalSimulation}Cognitive functions involving internal simulations about agent-environment interactions (e.g.
+imagination, computing alternative realities, and generating counterfactuals) are expected to involve NTIC processes.
+We speculate that, these internal simulations may involve interactions between C-processes and other processes in the neural system.
+Therefore, they often come with conscious experience.
 
@@
 To accurately encode information about complex environmental states and transitions, the NTIC process requires knowledge about the complex causal dependencies involved in the environment.
-Cognitive functions requiring larger scale integration are therefore likely to involve NTIC processes and accompanied by conscious experience.
+Cognitive functions requiring larger scale integration are therefore likely to involve C-processes and accompanied by conscious experience.
 % Furthermore, the high dimensional integrated information is also critical for an agent to learn new behaviours to achieve flexibility and the strategic behavioural controls and decision-making.
@@
 
-    	    In sum, we argue that cognitive functions involving the NTIC process are inevitably accompanied by consciousness.
+    	    In sum, we argue that cognitive functions involving the C-process are inevitably accompanied by consciousness.
 Having an NTIC process is potentially an effective approach to increasing fitness in the evolutionary process.
@@
 Similar to Neurorepresentationalism, the concept of levels in \ac{OurTheory} is relevant to Marr's level of analysis~\citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}.
-    		However, \ac{OurTheory} suggests that coarse-graining is necessary only when the microscopic processes are not NTIC (e.g.
-the neural system).
-An NTIC process can be formed in a noise-free deterministic system without coarse-graining.
-According to \ac{OurTheory}, this NTIC process is sufficient for consciousness.
+    		\linelabel{line:microNTIC}However, ICT suggests that coarse-graining is necessary only when a process is not informationally closed.
+Therefore, if a C-process is formed at a microscopic scale (e.g.
+the scale of individual neurons), according to ICT, this C-process is sufficient for consciousness.
     		Another fundamental difference between \ac{OurTheory} and Neurorepresentationalism is that Neurorepresentationalism takes a functionalist perspective and suggests that consciousness should serve high-level world-modelling and make a best guess about the interaction between the body and the environment.
@@
 		    \textbf{Prediction after system damage}: Prediction after system damage: ICT and IIT lead to different predictions when a system suffers from damage.
-Consider for example a densely connected network whose dynamics forms an NTIC process.
+Consider for example a densely connected network whose dynamics forms a C-process.
 If we cut the network in half, IIT predicts that this would result in two consciousnesses because elements in both networks still maintain high degrees of interaction.
@@
 The problem of individuality is a significant theoretical weakness of the current version of ICT.
-The notion of integration is a possible remedy for this issue, and we will address it explicitly in our future work using the concept of synergy.
+The notion of integration\footnote{Integration here refers to any high-order dependencies.} \linelabel{notIIT}is a possible remedy for this issue, and we will address it explicitly in our future work using the concept of synergy.
 
@@
 They retain some degree of activity during sleep and dreaming.
-We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e.
+We speculate that, during dreaming, the neural system stably forms a C-process with respect to its environment, i.e.
 the other parts of the neural system.
 At present, however, this remains mere speculation.
-Identification of the NTIC process(es) during dreaming is an important milestone in extending the scope of ICT.
+Identification of the C-process(es) during dreaming is an important milestone in extending the scope of ICT.
 
@@
         % finding the coarse-graining function 
-        Empirically, a major challenge to \ac{OurTheory} is to find appropriate coarse-graining functions which map microscopic processes to macroscopic NTIC processes.
+        Empirically, a major challenge to \ac{OurTheory} is to find appropriate coarse-graining functions which map microscopic processes to macroscopic C-processes.
 This issue will become imperative in the search for neurological evidence supporting \ac{OurTheory}.
@@
     In this paper, we introduce the \textbf{\acf{OurTheory}}, a new informational theory of consciousness.
-\ac{OurTheory} proposes that a process which forms \textbf{non-trivial informational closure (NTIC)} is conscious and through coarse-graining the neural system can form NTIC processes, i.e., conscious processes, at certain macroscopic scales.
+\ac{OurTheory} proposes that a process which forms informational closure with non-trivial information, i.e.
+\textbf{non-trivial informational closure (NTIC)} is conscious and through coarse-graining the neural system can form conscious processes, at certain macroscopic scales.
 \ac{OurTheory} considers that information is a common language to bridge the gap between conscious experience and physical reality.

### 2020-05-29 ICT_Frontiers_rev202005_reply.tex
Revision 2

% \input{ICT_Frontiers_rev202001.tex}
\documentclass[utf8]{article}
% \usepackage{RevisionToolsByAcer}
% \ProvidesPackage{RevisionToolsByAcer}
% \documentclass[utf8]{article}
% \ProvidesPackage{RevisionToolsByAcer}
%% Language and font encoding
\usepackage[english]{babel}
\usepackage[round, sort]{natbib}
\usepackage[T1]{fontenc}

% ============================ Sourcing main file ============================ %
\usepackage{xr}
\externaldocument{ICT_Frontiers_rev202005}
\usepackage{lineno}

% Sets page size and margins
% \usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
\usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
\usepackage{titlesec}
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[at]{easylist}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}
\usepackage[threshold=2, autopunct=true, autostyle=true]{csquotes}
\usepackage[colorinlistoftodos]{todonotes}

% =============================== Header style =============================== %
\titlelabel{}

% ============================================================================ %
%                               Macros from Acer                               %
% ============================================================================ %

% --------------------------------- Question --------------------------------- %	
\newcounter{cQuestion}[section]
\newenvironment{question}
    {\refstepcounter{cQuestion}\color{Blue}\noindent\newline Q\thecQuestion:}
    {~\newline}

% ------------------------------------ Ans ----------------------------------- %
\newenvironment{ans}  
    {\color{Black}\noindent A:}
    {~\newline}

\newcommand{\QA}[2]{
    \begin{question}  
        #1
    \end{question}

    \begin{ans}  
        #2
    \end{ans}
}

% ---------------------------------- Revise ---------------------------------- %
% \Revise{Page}{original text}{revised text}
\newcommand{\revise}[3]{
	\newline
	\newline
    \noindent
    \textbf{Line #1:}
    \newline
    Original:\newline
    \textit{"#2"}
    \newline
    \newline
    Revised:\newline
    \textit{"#3"}\newline}

% ---------------------------------- Add New --------------------------------- %
% \addnew{line number}{text}
\newcommand{\addnew}[2]{\blockcquote{}{\textbf{Line #1:}~\newline\textit{"#2"}}
}

% ================================ Annotation ================================ %
\newcommand{\toWrite}[1]{\noindent
	\textcolor{Orange}{\textbf{[[ #1 ]]}}}

% =================================== Title ================================== %
\title{Response to Reviewers (Revision 2)}
\date{\today}
\author{}

% =================================== Begin ================================== % 
\begin{document}

    \maketitle
    \section{Reply to Reviewer 1}
    	\begin{question}
    		The authors should formally define what an "NTIC process" is (l. 155, l. 182). I take it to be "NTIC > 0" but I am not clear on whether the condition $J_t = 0$ also applies at this point. I do understand now that $J_t = 0$ is implied by a C-process.
    	\end{question}

    	\begin{ans}
			The reviewer is correct. We refereed NTIC processes as processes with positive NTIC. To avoid potential ambiguity, we added a sentence to make this explicit at 
			\addnew{\lineref{line:nticdef}}{For simplicity, in what follows, we refer to \textit{NTIC processes} as those \textit{processes with positive NTIC}.}

			Furthermore, we also replaced "NTIC process" with "C-process" in many places in this revision especially when the contexts involve conscious experience and informational closure.     		
    	\end{ans}

    	\begin{question}
    		There are still some language issues and typos, especially in the new sections (2.1 etc). 
    	\end{question}

    	\begin{ans}
    		We have read through this revision. We hope that we have corrected the language issues especially in Sec. 2.1.
    	\end{ans}

    	\begin{question}
    		l. 266-277: This paragraph is a bit confusing. There are two factors mixed together that influence the level of consciousness: the relative size of S and E, and then the coarse-graining scale of Y. Fig. 4 is only about the latter. In understand that the potential for consciousness is highest if X is split into equal parts S and E, but the relative size of S and E is not about coarse-graining per se. This could be made more explicit. Also, it seems like this paragraph contradicts a statement in l. 434-437 where it says that an NTIC micro process is sufficient for consciousness.     		    	
    	\end{question}

    	\begin{ans}
    		The reviewer is correct. In our current setup, the relative size of the state space $\mathcal{S}$ of $S$ and the state space $\mathcal{E}$ of $E$ is intertwined with the scale of coarse-graining. This is because the scale of coarse-graining a coarse-grained variable is quantified by the size of its state space. This means that we consider a coarse-grained variable is finer when we maps a microscopic variable to a coarse-grained variable with a larger state space.

    		In our current setup, the relationship among the state spaces $\mathcal{S}$,  $\mathcal{E}$, and  $\mathcal{X}$ are defined by the Cartesian product $\mathcal{X}=\mathcal{S}\times\mathcal{E}$. As described in Footnote 3, this setup implies that increasing the size of $\mathcal{S}$ inevitably decreases the size of $\mathcal{E}$. Consequently, increasing the relative size of $\mathcal{S}$ moves $S$ (so as $Y$) and $E$ toward a finer and a coarser scale, respectively.

    		We understand that this is not an ideal construction of ICT and is one of the current limitations of ICT (which is also related to an added paragraph in Limitation at Line \lineref{line:individuality} in our last revision). To make this point clear, we made the two following changes:    		    	
    		\revise{\lineref{line:sizeAndScale}}
    		{At the finest scale we consider the whole universe $X$ as the process $Y$}
    		{Since we can quantify the scale of a coarse-grained variable by the size of its state space, therefore, at the finest scale we consider the whole universe $X$ as the process $Y$.}

    		\noindent
    		A footnote is added at
    		\addnew{\lineref{line:non-monotonic_end}}{In our current setup, the size of the state space $\mathcal{S}$ and $\mathcal{E}$ correspondingly determines the scale of coarse-graining of $S$ and $E$. Further research is needed to reveal the relationship among NTIC, scales of coarse-graining, and different constructions of $S$ and $E$. 
    		}

%    		are currently working on this by finding a better definition for $E$
%    		
%    		i.e, a variable with larger state space is considered to be finer, and vice versa )
%    		
%    		($S$, $E$, and $Y$). 
%    		
%    		This problem is one of the current limitations of ICT and is related to what we added in Limitation at Line \lineref{line:individuality} in our last revision.
%    		
%    		In this setup, the relationship among the state spaces $\mathcal{S}$,  $\mathcal{E}$, and  $\mathcal{X}$ are defined by the Cartesian product $\mathcal{X}=\mathcal{S}\times\mathcal{E}$. This implies that if the size of $\mathcal{X}$ is fixed, increasing the size of $\mathcal{S}$ to cover more states in $\mathcal{X}$ inevitably decreases the size of $\mathcal{E}$. , increasing the relative size of $\mathcal{S}$ moves $S$ (so as $Y$,  a coarse-graining of $S$) and $E$ toward a finer and a coarser scale, respectively.

    		We also agree that Line 434-437 is not well expressed. We did not mean to refer to the microscopic process as a process at the finest scale. We revised it as follows:
    		\revise{\lineref{line:microNTIC}}
    		{
    			However, ICT suggests that coarse-graining is necessary only when the microscopic processes are not NTIC (e.g. the neural system). An NTIC process can be formed in a noise-free deterministic system without coarse-graining. According to ICT, this NTIC process is sufficient for consciousness.}
    		{
    			However, ICT suggests that coarse-graining is necessary only when a process is not informationally closed. Therefore, if a C-process is formed at a microscopic scale (e.g. the scale of individual neurons), according to ICT, this C-process is sufficient for consciousness.}

%    		In our setup, the state space $\mathcal{E}$ of $E$ is determined by the state space $\mathcal{X}$ of $X$ and the state space $\mathcal{S}$ of $S$ through the relationship $\mathcal{X}=\mathcal{S}\times\mathcal{E}$. This 
    	\end{ans}

    	\begin{question}
    		l. 388-391: "Consequently, mental simulation, imagination, computing alternative realities, and generating counterfactuals often come with conscious experience" I'm not sure this statement fits with ICT. It seems to me that the internal process $Y_t \rightarrow Y_{t+1}$ has to be deterministic, or at least any uncertainty cannot be uncertainty that could be resolved at a lower level (because then it wouldn't be a C-process, as it would not be informationally closed with respect to S or X). This means that the C-process needs to be a good model of the environment, meaning that the correlation between $Y_{t+1}$ and $E_{t+1}$ needs to be very strong. So I don't see there being room for modeling "alternative realities". Because imagining counterfactuals would mean that $Y_{t+1}$ ultimately does not fit with $ E_t $ and thus $ I(Y_{t+1}; Y_t|E_t) $ would be much larger than if $ Y_{t+1} $ actually fit with $ E_{t+1} $. So correct predictions should be good, but imagining counterfactuals seems bad from an ITC point of view. No?
    	\end{question}

    	\begin{ans}
			If we understand the reviewer's question correctly, this question includes two contradictions to ICT from the paragraph about mental simulations: 
			\begin{enumerate}
				\item The correlation $Y_{t+1}$ and $E_{t+1}$ needs to be strong for a C-process to be a good model of the environment.
				\item During imagining counterfactuals and modelling alternative realities, $Y_{t+1}$ ultimately does not fit with $ E_t $. However, ICT hypothesises that the level of consciousness is contributed by the degrees of mutual information $I(Y_{t+1}:E_t)$.
			\end{enumerate}

    		To the first point, we can consider both NTIC processes (including C-processes) and the "synchronised" processes, which have high mutual information $I(Y_{t+1}:E_{t+1})$ are both good models of the environment. However, to be informationally closed, i.e. $I(Y_{t+1}:E_t|Y_t)=0$, NTIC more emphasises how a process models the influence from the environment to its future states. We consider this as a critical feature for a system which models system-environment interactions.

    		Further more, $Y_t \rightarrow Y_{t+1}$ does not have to be deterministic ($H(Y_{t+1}|Y_t)=0)$ to be a C-process. A C-process needs to be informationally closed meaning that the transfer entropy term
    		\begin{align*}
    			I(Y_{t+1}:E_t|Y_t)&=H(Y_{t+1}|Y_t) - H(Y_{t+1}|E_t, Y_t)\\
    			&=0    			
   			\end{align*}
   			Therefore,
 			\begin{align*}
	   			 H(Y_{t+1}|Y_t)&=H(Y_{t+1}|E_t, Y_t)  			
   			\end{align*}
   			This indicates that when information about $Y_{t+1}$ given $E_t$ is involved in information about $Y_{t+1}$ given $Y_t$, $Y$ is informationally closed with respect to $E$ even though $Y$ is not deterministic. \\

			Regarding the second point, the reviewer is correct that these mental simulations seem to be disentangled from the environment.  However, other processes inside the bodies should also be considered as part of the environment of C-processes. Therefore, similar to our argument about dreaming, we consider that conscious experience happening in these internal simulations is contributed by the mutual information between the C-process and other processes in the neural system.

			We agree that our original statement is too strong. We have revised this paragraph as follows:
   			\revise{\lineref{line:MentalSimulation}}{Cognitive functions involving simulations are expected to involve NTIC processes. Consequently, mental simulation, imagination, computing alternative realities, and generating counterfactuals often come with conscious experience. }{Cognitive functions involving internal simulations about agent-environment interactions (e.g. imagination, computing alternative realities, and generating counterfactuals) are expected to involve NTIC processes. We speculate that, these internal simulations may involve interactions between C-processes and other processes in the neural system. Therefore, they often come with conscious experience.}

    	\end{ans}

    	\begin{question}
    		l. 602: if you mean integration in the IIT sense, IIT should be cited here.    	    		
    	\end{question}
    	\begin{ans}
			Thank the reviewer for clarifying this. We do not intend to refer to the specific notion of integration defined by IIT. More generally, here we refer to any high-order dependencies. 
			This is one of our work in progress and we are still working on potential informational objects that can be well adapted in our current framework.

			We have added a footnote to disambiguate this concept at 
			\addnew{\lineref{notIIT}}{Integration here refers to any high-order dependencies.}
    	\end{ans}

	\bibliography{ref}
\end{document}
